### 2022-01-25 src/text/0-abstract.tex
Add text subfolder

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory

\abstract{
% TODO: the feature are still to detailed and partly copy and pasted form the ICRS abstract...avoid this
% context heading (optional)
% {} leave it empty if necessary  
%{Gammapy context:}
Historically the data as well as analysis software in gamma-ray astronomy is proprietary to the experiments. With the future Cherenkov Telescope Array (CTA), which will be operated as an open gamma-ray observatory with public data, there is a corresponding need for open high-level analysis software. In this article we present the first major version v1.0 of \gammapy, a community-developed open-source Python package for gamma-ray astronomy. 
%
We present its general design and provide an overview of the analysis methods and features it implements. Starting from event lists and a description of the specific instrument response functions (IRF) stored in open FITS based data formats, \gammapy implements . Thereby it handles the dependency of the IRFs with time, energy as well as position on the sky. It offers a variety of background estimation methods for spectral, spatial and spectro-morphological analysis. Counts, background and IRFs data are bundled in datasets and can be serialised, rebinned and stacked.
%
\gammapy supports to model binned data using Poisson maximum likelihood fitting. It comes with built-in spectral, spatial and temporal models as well as support for custom user models, to model e.g. energy dependent morphology of gamma-ray sources. Multiple datasets can be combined in a joint-likelihood approach to either handle time dependent IRFs, different classes of events or combination of data from multiple instruments. Gammapy also implements methods to estimate flux points, including likelihood profiles per energy bin, light curves as well as flux and signficance maps in energy bins.
%
We further describe the general development approach and how \gammapy integrates into ecosystem of other scientific and astronomical Python packages. We also present analysis examples with simulated CTA data and provide results of scientific validation analyses using data of existing instruments such as \hess and \fermi.

% The gamma-ray can be considered as the last frontier 
% In the last two decades the measurement of gamma-ray emission from the universe has 
% evolved from a niche

% aims heading (mandatory)
%{Gammapy aims}
%Reproducible analyses, share algorithms etc.

% methods heading (mandatory)
%{Gammapy methods}

% results heading (mandatory)
%{Gammapy results}

% conclusions heading (optional), leave it empty if necessary 
%{Gammapy conclusions}
}

### 2022-01-25 src/text/0-authors.tex
Add text subfolder

\authorrunning{Deil, Donath, Terrier et al.}

%Opt in solution for the contributor list...

\author{
Christoph Deil\inst{\ref{inst:mpik}}
\and
Axel Donath\inst{\ref{inst:mpik}}
\and
Régis Terrier\inst{\ref{inst:apc}}
\and
Johannes King\inst{\ref{inst:mpik}}
\and
Léa Jouvin\inst{\ref{inst:apc}}
\and
Manuel Paz Arribas\inst{\ref{inst:humboldt}}
\and
Ellis Owen\inst{\ref{inst:ucl}}
\and
Julien Lefaucheur\inst{\ref{inst:obsparis}}
\and
Olga Vorokh\inst{\ref{inst:olga}}
\and
Jonathan Harris\inst{\ref{inst:jon}}
\and
Brigitta Sipocz\inst{\ref{inst:brigitta1}, \ref{inst:brigitta2}}
\and
Dirk Lennarz\inst{\ref{inst:atlanta}}
\and
Helen Poon\inst{\ref{inst:mpik}}
\and
Nachiketa Chakraborty\inst{\ref{inst:mpik}}
\and
Domenico Tiziani\inst{\ref{inst:erlangen}}
\and
Luigi Tibaldo\inst{\ref{inst:mpik}}
\and
Victor Zabalza\inst{\ref{inst:victor}}
\and
Rolf Bühler\inst{\ref{inst:desy}}
\and
Stefan Klepser\inst{\ref{inst:desy}}
\and
Ignasi Reichardt\inst{\ref{inst:padova}}
}

\institute{
Max-Planck-Institut f\"{u}r Kernphysik, Heidelberg, Germany
\label{inst:mpik}
\and
APC, University of Paris 7, France
\label{inst:apc}
\and
LUTH, Observatoire de Paris, Meudon, France
\label{inst:obsparis}
\and
DESY, Zeuthen, Germany
\label{inst:desy}
\and
Humboldt University, Berlin, Germany
\label{inst:humboldt}
\and
UCL-MSSL, Dorking, United Kingdom
\label{inst:ucl}
\and
INFN, Padova, Italy
\label{inst:padova}
\and
Belarusian State University, Belarus, Minsk
\label{inst:olga}
\and
FAU, Erlangen, Germany
\label{inst:erlangen}
\and
School of Physics and Center for Relativistic Astrophysics, Georgia
Institute of Technology, Atlanta, GA, USA
\label{inst:atlanta}
\and
Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, AL10 9AB, UK
\label{inst:brigitta1}
\and
Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK
\label{inst:brigitta2}
\and
Department of Physics, Durham University, South Road, Durham, DH1 3LE, UK
\label{inst:jon}
\and
TODO: Victor address
\label{inst:victor}
}

### 2022-01-25 src/text/1-introduction.tex
Add text subfolder

\section{Introduction}
\label{sec:intro}

\todo{Axel and Regis write this...}

Gamma-ray astronomy is a rather young field of research.
By detecting and reconstructing arrival direction, time and energy
of primary cosmic gamma-rays
The gamma-ray sky is either observed by ground based instruments

, driven by experiments with proprietary software often based
on ROOT, because of the particle physics background. Such 
as HESS, Veritas or Magic.

The Cherenkov Telescope Array will be operated as an open
observatory for the first time. Thus there is a need for
open analysis software as well.

Once the primary photons are reconstructed the format of the data
of all Gamma-ray instrumets can be brought into a common format.
An effort is the gamma-astro data formats \cite{gadf-zenodo}.
The data format is based on FITS  \citep{fits}.

In recent years Python \footnote{\PythonUrl} has established as one of the
standard programming  languages for astronomy \footnote{Citation missing}
as well as data sciences in  general \footnote{Citation missing}.
The success is mostly attributed to the simple and easy to learn syntax,
the ability to act as a "glue" language between different programming
languages, the rich eco-system of packages and the open and supportive
community.

Astronomical data analysis software written in Python existed since 2000.
e.g. sherpa \citep{sherpa-2011, sherpa-2009}, or for gamma-ray even
PyFACT \citep{pyfact}.

The short-term success of Pythion lead to a prolifaration of packages, until
\astropy \citep{astropy} was created in 2012. Astropy is and

Gammapy is a Python package for gamma-ray astronomy.

% TODO: describe Context

% TODO: describe goals

TODO: Figure 1: Data -> Gammapy -> Spectra etc with some details

Basic idea: build on Numpy and Astropy, use Python stack

TODO: Figure 2: Gammapy software stack

Here's a list of references I'd like to cite ... to be incorporated into the
main text somewhere:

\begin{itemize}
\item Gammapy webpage\footnote{\GammapyUrl}
\item Naima\footnote{\NaimaUrl} \citep{Naima}
\item Gammapy use in science publications: \citep{Owen2015}, SNR shell, HGPS
\end{itemize}

* Gammapy – A Python package for gamma-ray astronomy
* Gammapy – A prototype for the CTA science tools 
* Astropy: A community Python package for astronomy
* THE ASTROPY PROJECT: BUILDING AN INCLUSIVE, OPEN-SCIENCE PROJECT AND STATUS OF THE V2.0 CORE PACKAGE
* GammaLib and ctools
* Fermipy proceedings
* SunPy: Python for Solar Physics. An implementation for local correlation tracking
*

\begin{figure}[t]
\centering
\includegraphics[height=0.5\textwidth, angle=270]{figures/gammapy-big-picture}
\caption{
Gammapy is a Python package for high-level gamma-ray data analysis. Using event
lists, exposures and point spread functions as input you can use it to generate
science results such as images, spectra, light curves or source catalogs. So far
it has been used to simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT
data, hopefully it will also be applied to e.g. VERITAS, MAGIC or HAWC data in
the future.
}
\label{fig:big-picture}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{figures/gammapy-dependencies}
\caption{
The Gammapy stack. Required dependencies Numpy and Astropy are illustrated with
solid arrows, optional dependencies (the rest) with dashed arrows.
}
\label{fig:dependencies}
\end{figure}

### 2022-01-25 src/text/2-package.tex
Add text subfolder

\section{Gammapy package}
\label{sec:package}

The \gammapy package is structured into multiple sub-packages
which mostly follow the stages in the data reduction workflow.

\subsection{Overview}
\begin{figure*}[t]
\centering
\includegraphics[width=1.\textwidth]{figures/data-flow-gammapy}
\caption{
Gammapy sub-package structure and data analysis workflow.
}
\label{fig:workflow}
\end{figure*}

\subsection{gammapy.data}
The \verb|gammapy.data| sub-package provides access to
DL3 level data and observation handling.

\begin{listing}
\begin{minted}{python}

from gammapy.data import DataStore

data_store = DataStore.from_dir("$GAMMAPY_DATA")
obs_ids = [1, 2, 3]
observations = data_store.get_observations(obs_ids)

\end{minted}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{listing}

\subsection{gammapy.makers}
\todo{Regis Terrier}
Data reduction

\begin{listing}
\begin{minted}[numbers=right]{python}

from gammapy.makers import MapDatasetMaker

maker = MapDatasetMaker()
dataset = maker.run(dataset, observation)

\end{minted}
\caption{Using gammapy.data to access DL3 level data}
\label{codeexample:maker}
\end{listing}

\subsection{gammapy.datasets}
\todo{Atreyee Sinha}
DL4 level data

\begin{listing}
\begin{minted}{python}

from astropy.coordinates import SkyCoord
from gammapy.maps import WcsGeom
from gammapy.datasets import MapDataset

skydir = SkyCoord("0d", "0d")
geom = WcsGeom.create(
	skydir=skydir, width="5 deg", binsz="0.2 deg"
)

dataset = MapDataset.create(
	geom=geom, name="my-dataset"
)

\end{minted}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{listing}

\subsection{gammapy.modeling}
\todo{Quentin Remy}
Models and fitting

\begin{listing}
\begin{minted}[numbers=right]{python}

from gammapy.modeling.models import (
	SkyModel,
	PowerLawSpectralModel,
	PointSpatialModel
)

pwl = PowerLawSpectralModel()
point = PointSpatialModel()

model = SkyModel(
	spectral_model=pwl,
	spatial_model=point
	name="my-model"
)
\end{minted}
\caption{Using gammapy.data to access DL3 level data}
\label{codeexample:maker}
\end{listing}

\subsection{gammapy.estimators}
\todo{Axel Donath}
Estimators

\subsection{gammapy.visualisation}
Plotters etc.

\subsection{gammapy.analysis}
\todo{Jose Enrique writes this...}
High level analysis API

\subsection{gammapy.astro}
Dark matter models, source population modelling

\subsection{gammapy.data}
\todo{Cosimo Nigro}

\subsection{gammapy.catalog}
Gamma-ray catalog access

\begin{listing}
\begin{minted}{python}

from gammapy.catalog import SOURCE_CATALOGS

\end{minted}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{listing}

\subsection{gammapy.maps}
\todo{Laura Olivera-Nieto}
The \verb|gammapy.maps| sub-package provides classes for representing pixelized
data structures with at least two spatial dimensions representing a set of
coordinates or a region on a sphere. In addition it allows to handle and arbitray
number of non-spatial data axes, such as time or energy.

It provides a uniform API for WCS, HEALPix and region based data structures.

\begin{listing}
\begin{minted}{python}

from gammapy.maps import Map
from astropy.coordinates import SkyCoord

skydir = SkyCoord("0d", "5d", frame="galactic")

# Create a WCS Map
m_wcs = Map.create(
	binsz=0.1, map_type='wcs', skydir=skydir, width=10.0
)

# Create a HPX Map
m_hpx = Map.create(
	binsz=0.1, map_type='hpx', skydir=skydir, width=10.0
)

\end{minted}
\caption{Using gammapy.data to access DL3 level data with a DataStore}
\label{codeexample:data}
\end{listing}

\subsection{gammapy.irf}
\todo{Fabio Pintore}
IRF classes

\subsection{gammapy.stats}
\todo{Regis Terrier}
Statistics methods

\subsection{gammapy.utils}
Utility functions...

Outline:
* List typical analysis use cases
* Can use from Python and Jupyter -> show Figure with Jupyter notebook here.
* Gammapy code structure
* How Numpy and Astropy is used

Figures:
* Add a Figure showing dataflow in a typical application
DL3 at the top, spectrum, map, lightcurve, fit results at the bottom.
Mention major classes in between (DataStore, EventList, Map, MapMaker, MapFit, …)
* Probably not: Figure showing sub-packages and how they relate (gammapy.data and gammapy.irf at the base, then gammapy.maps, etc.
* The code example Figure how to make a counts map, to explain how the package works.

### 2022-01-25 src/text/3-applications.tex
Add text subfolder

\section{Applications}
\label{sec:apps}

Each application example is a notebook in the online material: We could have one
analysis as Python scripts instead of notebook in the online material. At the
start of this section, point to gammapy-paper repo on Github and say that
there’s a Binder where people can try the examples online.

TODO: mention other application examples (joint Crab paper, HESS validation
paper, HGPS, ...) here or in a subsection "other applications" at the end of
this section?

\subsection{Source detection}
\label{apps:detect}

See Figure~\ref{fig:fermi-ts-image}.

Ref: \citep{Stewart2009}

\begin{figure*}[t]
\centering
\includegraphics[width=1.\textwidth]{figures/gammapy-fermi-ts-image}
\caption{
Gammapy application example: A \textit{Fermi} survey TS map of the inner
Galactic plane region.
}
\label{fig:fermi-ts-image}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\textwidth]{figures/gammapy-cube-analysis}
\caption{
Gammapy data model illustration. Binned analysis of lon-lat-energy cube data is
supported via joint likelihood analysis of one image per energy bin.
On-off-region based spectral analysis is supported as well.
}
\label{fig:data-model}
\end{figure*}

\subsection{Multi instrument analysis}

### 2022-01-25 src/text/4-project.tex
Add text subfolder

\section{Gammapy project}
\label{sec:project}

Open development, roadmap, communities,
science tool aspect
Infrastructure etc.

community driven vs. institutional driven

Validation and benchmarks?
Validation as online appendix...

\subsection{Development, testing}

\todo{Jose Enrique writes this...}
-Github, pytest, CI, PIGs?

\subsection{Documentation}

- Notebooks

\subsection{Software distribution and user support}

- Pip, conda, versions, gammapy download

\subsection{Community}

TODO: Figure: Screenshot of Jupyter notebook or docs with notebook, could show the interactive maps view
\begin{verbatim}
m = Map.read(“diffuse.fits”)
m.plot_interactive()        
\end{verbatim}

### 2022-01-25 src/text/5-summary-outlook.tex
Add text subfolder

\section{Summary and Outlook}
\label{sec:so}

\todo{Axel and Regis write this...}

Summary what we have in v0.9 and presented in this paper.

Roadmap to v1.0, about half a page.

Short conclusion: Gammapy has potential to be the Python package for gamma-ray astronomy.

Prospects for HAWC / SWGO? Or speak in general about water Cherenkov observatories...

### 2022-01-25 src/text/6-acknowledgements.tex
Add text subfolder

\begin{acknowledgements}

Mention Christoph here?

We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
\texttt{Matplotlib} communities for providing their packages which are invaluable
to the development of Astropy. We thank the GitHub team for providing us with
an excellent free development platform. We also are grateful to Read the Docs
(\ReadthedocsUrl), and Travis
(\TravisUrl) for providing free documentation
hosting and testing respectively. Finally, we would like to thank all the
Gammapy users that have provided feedback and submitted bug reports.

TODO: copy over stuff from \url{http://docs.gammapy.org/en/latest/about.html#thanks}.
TODO: add the ANR for Luca (and Atreyee in LUPM?)

\end{acknowledgements}

### 2022-01-26 src/snippets/minted.tex
Add minted rule

% comment these out if you already import them in main.tex
%\usepackage{fancyvrb}
%\usepackage{color}
%\usepackage[utf8]{inputenc}

\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax\let\PY@ul=\relax \let\PY@tc=\relax\let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else\PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{\PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

### 2022-01-26 src/snippets/minted.py

@@ -1,0 +1,24 @@
+from pathlib import Path
+import subprocess
+
+PATH = Path(__file__).parent
+
+SNIPPETS = PATH / "input"
+GENERATED = PATH / "generated"
+
+# for example 'frame=single' to frame the code
+OPTIONS = 'frame=single,style=friendly,linenos=1'
+
+if __name__ == '__main__':
+    GENERATED.mkdir(exist_ok=True)
+
+    filenames = SNIPPETS.glob("*.py")
+    for filename in filenames:
+        command = ["pygmentize"]
+        command += ["-O", f"verboptions={OPTIONS}"]
+        command += ["-f", "tex"]
+
+        filename_out = GENERATED / filename.name.replace(".py", ".tex")
+        command += ["-o", f"{filename_out}"]
+        command += [f"{filename}"]
+        subprocess.call(command)

### 2022-01-26 src/code-examples/minted.py
Rename snippets folder

@@ -3,7 +3,7 @@ import subprocess
 
 PATH = Path(__file__).parent
 
-SNIPPETS = PATH / "input"
+SNIPPETS = PATH / "snippets"
 GENERATED = PATH / "generated"
 
 # for example 'frame=single' to frame the code

### 2022-01-26 src/text/2-package.tex
Adapt tex files
Add minted rule
Add more code examples

@@
 \centering
-\includegraphics[width=1.\textwidth]{figures/data-flow-gammapy}
+\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
 \caption{
@@
 
-\begin{listing}
-\begin{minted}{python}
+\begin{figure}
 
-from gammapy.data import DataStore
+\import{code-examples/generated/}{gp_data}
 
-data_store = DataStore.from_dir("$GAMMAPY_DATA")
-obs_ids = [1, 2, 3]
-observations = data_store.get_observations(obs_ids)
-
-\end{minted}
 \caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{codeexample:data}
-\end{listing}
+\label{fig*:minted:gp_data}
+\end{figure}
 
@@
 
-\begin{listing}
-\begin{minted}[numbers=right]{python}
+\begin{figure}
+\import{code-examples/generated/}{gp_makers}
 
-from gammapy.makers import MapDatasetMaker
-
-maker = MapDatasetMaker()
-dataset = maker.run(dataset, observation)
-
-\end{minted}
 \caption{Using gammapy.data to access DL3 level data}
-\label{codeexample:maker}
-\end{listing}
+\label{ig*:minted:gp_makers}
+\end{figure}
 
@@
 
-\begin{listing}
-\begin{minted}{python}
+\begin{figure}
 
-from astropy.coordinates import SkyCoord
-from gammapy.maps import WcsGeom
-from gammapy.datasets import MapDataset
-
-skydir = SkyCoord("0d", "0d")
-geom = WcsGeom.create(
-	skydir=skydir, width="5 deg", binsz="0.2 deg"
-)
-
-dataset = MapDataset.create(
-	geom=geom, name="my-dataset"
-)
-
-\end{minted}
+\import{code-examples/generated/}{gp_datasets}
 \caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{codeexample:data}
-\end{listing}
+\label{fig*:minted:gp_datasets}
+\end{figure}
 
@@
 
-\begin{listing}
-\begin{minted}[numbers=right]{python}
-
-from gammapy.modeling.models import (
-	SkyModel,
-	PowerLawSpectralModel,
-	PointSpatialModel
-)
-
-pwl = PowerLawSpectralModel()
-point = PointSpatialModel()
-
-model = SkyModel(
-	spectral_model=pwl,
-	spatial_model=point
-	name="my-model"
-)
-\end{minted}
-\caption{Using gammapy.data to access DL3 level data}
-\label{codeexample:maker}
-\end{listing}
+\begin{figure}
+\import{code-examples/generated/}{gp_models}
+\caption{Using gammapy.modeling.models}
+\label{fig*:minted:gp_models}
+\end{figure}
 
@@
 
-\begin{listing}
-\begin{minted}{python}
-
-from gammapy.catalog import SOURCE_CATALOGS
-
-\end{minted}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
+\begin{figure}
+\import{code-examples/generated/}{gp_catalogs}
+\caption{Using gammapy.catalogs}
 \label{codeexample:data}
-\end{listing}
+\end{figure}
 
@@
 
-\begin{listing}
-\begin{minted}{python}
+\begin{figure}
 
-from gammapy.maps import Map
-from astropy.coordinates import SkyCoord
-
-skydir = SkyCoord("0d", "5d", frame="galactic")
-
-# Create a WCS Map
-m_wcs = Map.create(
-	binsz=0.1, map_type='wcs', skydir=skydir, width=10.0
-)
-
-# Create a HPX Map
-m_hpx = Map.create(
-	binsz=0.1, map_type='hpx', skydir=skydir, width=10.0
-)
-
-\end{minted}
+    \import{code-examples/generated/}{gp_maps}
 \caption{Using gammapy.data to access DL3 level data with a DataStore}
 \label{codeexample:data}
-\end{listing}
+\end{figure}
 

### 2022-01-26 src/code-examples/snippets/gp_catalogs.py

@@ -1,0 +1,3 @@
+from gammapy.catalog import SOURCE_CATALOGS
+
+catalog = SOURCE_CATALOGS["3fhl"]

### 2022-01-26 src/code-examples/snippets/gp_data.py

@@ -1,0 +1,5 @@
+from gammapy.data import DataStore
+
+data_store = DataStore.from_dir("$GAMMAPY_DATA")
+obs_ids = [1, 2, 3]
+observations = data_store.get_observations(obs_ids)

### 2022-01-26 src/code-examples/snippets/gp_datasets.py

@@ -1,0 +1,12 @@
+from astropy.coordinates import SkyCoord
+from gammapy.maps import WcsGeom
+from gammapy.datasets import MapDataset
+
+skydir = SkyCoord("0d", "0d")
+geom = WcsGeom.create(
+	skydir=skydir, width="5 deg", binsz="0.2 deg"
+)
+
+dataset = MapDataset.create(
+	geom=geom, name="my-dataset"
+)

### 2022-01-26 src/code-examples/snippets/gp_makers.py

@@ -1,0 +1,4 @@
+from gammapy.makers import MapDatasetMaker
+
+maker = MapDatasetMaker()
+dataset = maker.run(dataset, observation)

### 2022-01-26 src/code-examples/snippets/gp_maps.py

@@ -1,0 +1,22 @@
+from gammapy.maps import Map
+from astropy.coordinates import SkyCoord
+from astripy import units as u
+
+skydir = SkyCoord("0d", "5d", frame="galactic")
+
+# Create a WCS Map
+m_wcs = Map.create(
+    binsz=0.1,
+    map_type="wcs",
+    skydir=skydir,
+    width=[10.0, 8.0] * u.deg
+)
+
+
+# Create a HPX Map
+m_hpx = Map.create(
+    binsz=0.1,
+    map_type="hpx",
+    skydir=skydir,
+    width=10.0 * u.deg
+)

### 2022-01-26 src/code-examples/snippets/gp_models.py

@@ -1,0 +1,14 @@
+from gammapy.modeling.models import (
+	SkyModel,
+	PowerLawSpectralModel,
+	PointSpatialModel,
+)
+
+pwl = PowerLawSpectralModel()
+point = PointSpatialModel()
+
+model = SkyModel(
+	spectral_model=pwl,
+	spatial_model=point,
+	name="my-model",
+)

### 2022-01-27 src/text/0-abstract.tex
Reformat tex files

@@
 	%{Gammapy context:}
-Historically the data as well as analysis software in gamma-ray astronomy is proprietary to the experiments.
-With the future Cherenkov Telescope Array (CTA), which will be operated as an open gamma-ray observatory with public data, there is a corresponding need for open high-level analysis software.
-In this article we present the first major version v1.0 of \gammapy, a community-developed open-source Python package for gamma-ray astronomy.
-%
-We present its general design and provide an overview of the analysis methods and features it implements.
-Starting from event lists and a description of the specific instrument response functions (IRF) stored in open FITS based data formats, \gammapy implements .
-Thereby it handles the dependency of the IRFs with time, energy as well as position on the sky.
-It offers a variety of background estimation methods for spectral, spatial and spectro-morphological analysis.
-Counts, background and IRFs data are bundled in datasets and can be serialised, rebinned and stacked.
-%
-\gammapy supports to model binned data using Poisson maximum likelihood fitting.
-It comes with built-in spectral, spatial and temporal models as well as support for custom user models, to model e.g.
-energy dependent morphology of gamma-ray sources.
-Multiple datasets can be combined in a joint-likelihood approach to either handle time dependent IRFs, different classes of events or combination of data from multiple instruments.
-Gammapy also implements methods to estimate flux points, including likelihood profiles per energy bin, light curves as well as flux and signficance maps in energy bins.
-%
-We further describe the general development approach and how \gammapy integrates into ecosystem of other scientific and astronomical Python packages.
-We also present analysis examples with simulated CTA data and provide results of scientific validation analyses using data of existing instruments such as \hess and \fermi.
+	Historically the data as well as analysis software in gamma-ray astronomy is
+	proprietary to the experiments. With the future Cherenkov Telescope Array
+	(CTA), which will be operated as an open gamma-ray observatory with public
+	data, there is a corresponding need for open high-level analysis software. In
+	this article we present the first major version v1.0 of \gammapy, a
+	community-developed open-source Python package for gamma-ray astronomy.
+	 We present its general design and provide an%
+	overview of the analysis methods and features it implements. Starting from
+	event lists and a description of the specific instrument response functions
+	(IRF) stored in open FITS based data formats, \gammapy implements . Thereby it
+	handles the dependency of the IRFs with time, energy as well as position on the
+	sky. It offers a variety of background estimation methods for spectral, spatial
+	and spectro-morphological analysis. Counts, background and IRFs data are
+	bundled in datasets and can be serialised, rebinned and stacked.
+	 \gammapy supports to model binned data using%
+	Poisson maximum likelihood fitting. It comes with built-in spectral, spatial
+	and temporal models as well as support for custom user models, to model e.g.
+	energy dependent morphology of gamma-ray sources. Multiple datasets can be
+	combined in a joint-likelihood approach to either handle time dependent IRFs,
+	different classes of events or combination of data from multiple instruments.
+	Gammapy also implements methods to estimate flux points, including likelihood
+	profiles per energy bin, light curves as well as flux and signficance maps in
+	energy bins.  We further describe the general%
+	development approach and how \gammapy integrates into ecosystem of other
+	scientific and astronomical Python packages. We also present analysis examples
+	with simulated CTA data and provide results of scientific validation analyses
+	using data of existing instruments such as \hess and \fermi.
 

### 2022-01-27 src/text/0-authors.tex
Reformat tex files

@@
 \author{
-Christoph Deil\inst{\ref{inst:mpik}}
-\and
-Axel Donath\inst{\ref{inst:mpik}}
-\and
-Régis Terrier\inst{\ref{inst:apc}}
-\and
-Johannes King\inst{\ref{inst:mpik}}
-\and
-Léa Jouvin\inst{\ref{inst:apc}}
-\and
-Manuel Paz Arribas\inst{\ref{inst:humboldt}}
-\and
-Ellis Owen\inst{\ref{inst:ucl}}
-\and
-Julien Lefaucheur\inst{\ref{inst:obsparis}}
-\and
-Olga Vorokh\inst{\ref{inst:olga}}
-\and
-Jonathan Harris\inst{\ref{inst:jon}}
-\and
-Brigitta Sipocz\inst{\ref{inst:brigitta1}, \ref{inst:brigitta2}}
-\and
-Dirk Lennarz\inst{\ref{inst:atlanta}}
-\and
-Helen Poon\inst{\ref{inst:mpik}}
-\and
-Nachiketa Chakraborty\inst{\ref{inst:mpik}}
-\and
-Domenico Tiziani\inst{\ref{inst:erlangen}}
-\and
-Luigi Tibaldo\inst{\ref{inst:mpik}}
-\and
-Victor Zabalza\inst{\ref{inst:victor}}
-\and
-Rolf Bühler\inst{\ref{inst:desy}}
-\and
-Stefan Klepser\inst{\ref{inst:desy}}
-\and
-Ignasi Reichardt\inst{\ref{inst:padova}}
-}
+	Christoph Deil\inst{\ref{inst:mpik}} \and Axel Donath\inst{\ref{inst:mpik}}
+	\and Régis Terrier\inst{\ref{inst:apc}} \and Johannes
+	King\inst{\ref{inst:mpik}} \and Léa Jouvin\inst{\ref{inst:apc}} \and Manuel Paz
+	Arribas\inst{\ref{inst:humboldt}} \and Ellis Owen\inst{\ref{inst:ucl}} \and
+	Julien Lefaucheur\inst{\ref{inst:obsparis}} \and Olga
+	Vorokh\inst{\ref{inst:olga}} \and Jonathan Harris\inst{\ref{inst:jon}} \and
+	Brigitta Sipocz\inst{\ref{inst:brigitta1}, \ref{inst:brigitta2}} \and Dirk
+	Lennarz\inst{\ref{inst:atlanta}} \and Helen Poon\inst{\ref{inst:mpik}} \and
+	Nachiketa Chakraborty\inst{\ref{inst:mpik}} \and Domenico
+	Tiziani\inst{\ref{inst:erlangen}} \and Luigi Tibaldo\inst{\ref{inst:mpik}} \and
+	Victor Zabalza\inst{\ref{inst:victor}} \and Rolf Bühler\inst{\ref{inst:desy}}
+	\and Stefan Klepser\inst{\ref{inst:desy}} \and Ignasi
+	Reichardt\inst{\ref{inst:padova}} }
 
 \institute{
-Max-Planck-Institut f\"{u}r Kernphysik, Heidelberg, Germany
-\label{inst:mpik}
-\and
-APC, University of Paris 7, France
-\label{inst:apc}
-\and
-LUTH, Observatoire de Paris, Meudon, France
-\label{inst:obsparis}
-\and
-DESY, Zeuthen, Germany
-\label{inst:desy}
-\and
-Humboldt University, Berlin, Germany
-\label{inst:humboldt}
-\and
-UCL-MSSL, Dorking, United Kingdom
-\label{inst:ucl}
-\and
-INFN, Padova, Italy
-\label{inst:padova}
-\and
-Belarusian State University, Belarus, Minsk
-\label{inst:olga}
-\and
-FAU, Erlangen, Germany
-\label{inst:erlangen}
-\and
-School of Physics and Center for Relativistic Astrophysics, Georgia
-Institute of Technology, Atlanta, GA, USA
-\label{inst:atlanta}
-\and
-Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, AL10 9AB, UK
-\label{inst:brigitta1}
-\and
-Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK
-\label{inst:brigitta2}
-\and
-Department of Physics, Durham University, South Road, Durham, DH1 3LE, UK
-\label{inst:jon}
-\and
-TODO: Victor address
-\label{inst:victor}
-}
+Max-Planck-Institut f\"{u}r Kernphysik, Heidelberg, Germany \label{inst:mpik}
+\and APC, University of Paris 7, France \label{inst:apc} \and LUTH,
+Observatoire de Paris, Meudon, France \label{inst:obsparis} \and DESY, Zeuthen,
+Germany \label{inst:desy} \and Humboldt University, Berlin, Germany
+\label{inst:humboldt} \and UCL-MSSL, Dorking, United Kingdom \label{inst:ucl}
+\and INFN, Padova, Italy \label{inst:padova} \and Belarusian State University,
+Belarus, Minsk \label{inst:olga} \and FAU, Erlangen, Germany
+\label{inst:erlangen} \and School of Physics and Center for Relativistic
+Astrophysics, Georgia Institute of Technology, Atlanta, GA, USA
+\label{inst:atlanta} \and Centre for Astrophysics Research, University of
+Hertfordshire, College Lane, Hatfield, AL10 9AB, UK \label{inst:brigitta1} \and
+Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3
+0HA, UK \label{inst:brigitta2} \and Department of Physics, Durham University,
+South Road, Durham, DH1 3LE, UK \label{inst:jon} \and TODO: Victor address
+\label{inst:victor} }

### 2022-01-27 src/text/0-abstract.tex
Run pre commit hook

@@
 	Poisson maximum likelihood fitting. It comes with built-in spectral, spatial
-	and temporal models as well as support for custom user models, to model e.g.
+	and temporal models as well as support for custom user models, to model e.g.,
 	energy dependent morphology of gamma-ray sources. Multiple datasets can be

### 2022-01-27 src/text/2-package.tex
Minor cleanup of tex files
Reformat tex files
Run pre commit hook on all files

@@
+\section{Analysis Workflow Overview}
+\label{sec:analysis-workflow-overview}
+
 \section{Gammapy package}
-\label{sec:package}
+\label{sec:gammapy-package}
 
-The \gammapy package is structured into multiple sub-packages
-which mostly follow the stages in the data reduction workflow.
+The \gammapy package is structured into multiple sub-packages which mostly
+follow the stages in the data reduction workflow.
 
 \subsection{Overview}
+\label{ssec:overview}
 \begin{figure*}[t]
@@
 	\caption{
-Gammapy sub-package structure and data analysis workflow.
-}
-\label{fig:workflow}
-\end{figure*}
+		Gammapy sub-package structure and data analysis workflow. }
+	\label{fig:workflow} \end{figure*}
 
 \subsection{gammapy.data}
-The \verb|gammapy.data| sub-package provides access to
-DL3 level data and observation handling.
+\label{ssec:gammapy-data}
+The \verb|gammapy.data| sub-package provides access to DL3 level data and
+observation handling.
 
@@
 \subsection{gammapy.makers}
+\label{ssec:gammapy-makers}
 \todo{Regis Terrier}
@@
 \subsection{gammapy.datasets}
+\label{ssec:gammapy-datasets}
 \todo{Atreyee Sinha}
@@
 
-\subsection{gammapy.modeling}
+\subsection{gammapy.modeling
+\label{ssec:gammapy-modeling}
 \todo{Quentin Remy}
@@
 \subsection{gammapy.estimators}
+\label{ssec:gammapy-estimators}
 \todo{Axel Donath}
@@
 \subsection{gammapy.visualisation}
+\label{ssec:gammapy-visualisation}
 Plotters etc.
@@
 \subsection{gammapy.analysis}
+\label{ssec:gammapy-analysis}
 \todo{Jose Enrique writes this...}
@@
 \subsection{gammapy.astro}
+\label{ssec:gammapy-astro}
 Dark matter models, source population modelling
@@
 \subsection{gammapy.data}
+\label{ssec:gammapy-data}
 \todo{Cosimo Nigro}
@@
 \subsection{gammapy.catalog}
+\label{ssec:gammapy-catalog}
 Gamma-ray catalog access
@@
 \subsection{gammapy.maps}
+\label{ssec:gammapy-maps}
 \todo{Laura Olivera-Nieto}
@@
 data structures with at least two spatial dimensions representing a set of
-coordinates or a region on a sphere. In addition it allows to handle and arbitray
-number of non-spatial data axes, such as time or energy.
+coordinates or a region on a sphere. In addition it allows to handle and
+arbitray  number of non-spatial data axes, such as time or energy.
 
@@
 \begin{figure}
-
 	\import{code-examples/generated/}{gp_maps}
@@
 \subsection{gammapy.irf}
+\label{ssec:gammapy-irf}
 \todo{Fabio Pintore}
@@
 \subsection{gammapy.stats}
+\label{ssec:gammapy-stats}
 \todo{Regis Terrier}
@@
 \subsection{gammapy.utils}
+\label{ssec:gammapy-utils}
 Utility functions...
 
-Outline:
-* List typical analysis use cases
-* Can use from Python and Jupyter -> show Figure with Jupyter notebook here.
-* Gammapy code structure
-* How Numpy and Astropy is used
+Outline: * List typical analysis use cases * Can use from Python and Jupyter ->
+show Figure with Jupyter notebook here. * Gammapy code structure * How Numpy
+and Astropy is used
 
-Figures:
-* Add a Figure showing dataflow in a typical application
-DL3 at the top, spectrum, map, lightcurve, fit results at the bottom.
-Mention major classes in between (DataStore, EventList, Map, MapMaker, MapFit, …)
-* Probably not: Figure showing sub-packages and how they relate (gammapy.data and gammapy.irf at the base, then gammapy.maps, etc.
-* The code example Figure how to make a counts map, to explain how the package works.
+Figures: * Add a Figure showing dataflow in a typical application DL3 at the
+top, spectrum, map, lightcurve, fit results at the bottom. Mention major
+classes in between (DataStore, EventList, Map, MapMaker, MapFit, …) * Probably
+not: Figure showing sub-packages and how they relate (gammapy.data and
+gammapy.irf at the base, then gammapy.maps, etc. * The code example Figure how
+to make a counts map, to explain how the package works.

### 2022-01-27 src/text/1-introduction.tex
Adapt tex files
Reformat tex files

@@
 \section{Introduction}
-\label{sec:intro}
+\label{sec:introduction}
 
@@
 
-Gamma-ray astronomy is a rather young field of research.
-By detecting and reconstructing arrival direction, time and energy
-of primary cosmic gamma-rays
-The gamma-ray sky is either observed by ground based instruments
+Gamma-ray astronomy is a rather young field of research. By detecting and
+reconstructing arrival direction, time and energy of primary cosmic gamma-rays
+The gamma-ray sky is either observed by ground based instruments, driven by
+experiments with proprietary software often based on ROOT, because of the
+particle physics background. Such as HESS, Veritas or Magic.
 
-, driven by experiments with proprietary software often based
-on ROOT, because of the particle physics background. Such 
-as HESS, Veritas or Magic.
+The Cherenkov Telescope Array will be operated as an open observatory for the
+first time. Thus there is a need for open analysis software as well.
 
-The Cherenkov Telescope Array will be operated as an open
-observatory for the first time. Thus there is a need for
-open analysis software as well.
-
-Once the primary photons are reconstructed the format of the data
-of all Gamma-ray instrumets can be brought into a common format.
-An effort is the gamma-astro data formats \cite{gadf-zenodo}.
-The data format is based on FITS  \citep{fits}.
+Once the primary photons are reconstructed the format of the data of all
+Gamma-ray instrumets can be brought into a common format. An effort is the
+gamma-astro data formats~\cite{gadf-zenodo}. The data format is based on FITS
+\citep{fits}.
 
 In recent years Python \footnote{\PythonUrl} has established as one of the
-standard programming  languages for astronomy \footnote{Citation missing}
-as well as data sciences in  general \footnote{Citation missing}.
-The success is mostly attributed to the simple and easy to learn syntax,
-the ability to act as a "glue" language between different programming
-languages, the rich eco-system of packages and the open and supportive
-community.
+standard programming  languages for astronomy \footnote{Citation missing} as
+well as data sciences in  general \footnote{Citation missing}. The success is
+mostly attributed to the simple and easy to learn syntax, the ability to act as
+a "glue" language between different programming languages, the rich eco-system
+of packages and the open and supportive community.
 
-Astronomical data analysis software written in Python existed since 2000.
-e.g. sherpa \citep{sherpa-2011, sherpa-2009}, or for gamma-ray even
-PyFACT \citep{pyfact}.
+Astronomical data analysis software written in Python existed since 2000. e.g.,
+sherpa~\citep{sherpa-2011, sherpa-2009}, or for gamma-ray even PyFACT
+\citep{pyfact}.
 
 The short-term success of Pythion lead to a prolifaration of packages, until
-\astropy \citep{astropy} was created in 2012. Astropy is and
-
-Gammapy is a Python package for gamma-ray astronomy.
+\astropy~\citep{astropy} was created in 2012. Astropy is and Gammapy is a
+Python package for gamma-ray astronomy.
 
@@
 	\item Gammapy webpage\footnote{\GammapyUrl}
-\item Naima\footnote{\NaimaUrl} \citep{Naima}
-\item Gammapy use in science publications: \citep{Owen2015}, SNR shell, HGPS
+	\item Naima\footnote{\NaimaUrl}~\citep{Naima}
+	\item Gammapy use in science publications:~\citep{Owen2015}, SNR shell, HGPS
 \end{itemize}
@@
 * Astropy: A community Python package for astronomy
-* THE ASTROPY PROJECT: BUILDING AN INCLUSIVE, OPEN-SCIENCE PROJECT AND STATUS OF THE V2.0 CORE PACKAGE
-* GammaLib and ctools
-* Fermipy proceedings
-* SunPy: Python for Solar Physics. An implementation for local correlation tracking
-*
+* THE ASTROPY PROJECT: BUILDING AN INCLUSIVE, OPEN-SCIENCE PROJECT AND STATUS
+OF THE V2.0 CORE PACKAGE * GammaLib and ctools * Fermipy proceedings * SunPy:
+Python for Solar Physics. An implementation for local correlation tracking *
 
@@
 	\centering
-\includegraphics[height=0.5\textwidth, angle=270]{figures/gammapy-big-picture}
+	\includegraphics[height=0.5\textwidth, angle=270]{static/gammapy-big-picture}
 	\caption{
@@
 		lists, exposures and point spread functions as input you can use it to generate
-science results such as images, spectra, light curves or source catalogs. So far
-it has been used to simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT
-data, hopefully it will also be applied to e.g. VERITAS, MAGIC or HAWC data in
-the future.
+		science results such as images, spectra, light curves or source catalogs. So
+		far it has been used to simulate and analyse H.E.S.S., CTA and
+		\textit{Fermi}-LAT data, hopefully it will also be applied to e.g., VERITAS,
+		MAGIC or HAWC data in the future.
 	}
@@
 	\centering
-\includegraphics[width=0.5\textwidth]{figures/gammapy-dependencies}
+	\includegraphics[width=0.5\textwidth]{static/gammapy-dependencies}
 	\caption{

### 2022-01-27 src/text/4-project.tex
Reformat tex files

@@
 \section{Gammapy project}
-\label{sec:project}
+\label{sec:gammapy-project}
 
-Open development, roadmap, communities,
-science tool aspect
-Infrastructure etc.
+Open development, roadmap, communities, science tool aspect Infrastructure etc.
 
@@
 
-Validation and benchmarks?
-Validation as online appendix...
+Validation and benchmarks? Validation as online appendix...
 
 \subsection{Development, testing}
-
+\label{ssec:development-testing}
 \todo{Jose Enrique writes this...}
@@
 \subsection{Documentation}
+\label{ssec:documentation}
 
@@
 \subsection{Software distribution and user support}
-
+\label{ssec:software-distribution-and-user-support}
 - Pip, conda, versions, gammapy download
@@
 \subsection{Community}
-
-TODO: Figure: Screenshot of Jupyter notebook or docs with notebook, could show the interactive maps view
+\label{ssec:community}
+TODO: Figure: Screenshot of Jupyter notebook or docs with notebook, could show
+the interactive maps view
 \begin{verbatim}

### 2022-01-28 scripts/authors.py
Add authors.py script

@@ -1,0 +1,83 @@
+"""Utility script to work with the CITATION.cff file"""
+import logging
+import subprocess
+import click
+from ruamel.yaml import YAML
+from pathlib import Path
+
+log = logging.getLogger(__name__)
+logging.basicConfig(level=logging.DEBUG)
+
+BASE_PATH = Path(__file__).parent.parent
+PATH = Path("/Users/adonath/github/adonath/gammapy")
+CITATION_CFF = PATH / "CITATION.cff"
+
+AUTHOR_TEMPLATE = "{author_name} \inst{\ref{{affiliation_label}}}"
+
+
+def get_full_name(author_data):
+    """Get full name from CITATION.cff parts"""
+    parts = []
+    parts.append(author_data["given-names"])
+
+    name_particle = author_data.get("name-particle", None)
+
+    if name_particle:
+        parts.append(name_particle)
+
+    parts.append(author_data["family-names"])
+    return " ".join(parts)
+
+
+def get_citation_cff_authors_and_affiliations():
+    """Get list of authors from CITATION.cff"""
+    authors, affiliations = [], []
+
+    yaml = YAML()
+
+    with CITATION_CFF.open("r") as stream:
+        data = yaml.load(stream)
+
+    for author_data in data["authors"]:
+        full_name = get_full_name(author_data)
+        authors.append(full_name)
+
+        affiliation = author_data.get("affiliation", "unknown")
+        affiliations.append(affiliation)
+
+    return {
+        "authors": authors,
+        "affiliations": affiliations,
+    }
+
+
+def write_author_file():
+    data = get_citation_cff_authors_and_affiliations()
+
+    author_str = "\\authorrunning{Deil, Donath, Terrier et al.}\n\n"
+    author_str += "\\author{\n"
+
+    for idx, author in enumerate(data["authors"]):
+        label = f"inst:{idx}"
+        author_str += f"\t{author} \\inst{{\\ref{{{label}}}}} \\and\n"
+
+    author_str += "}\n\n"
+
+    author_str += "\institute{\n"
+    for idx, affiliation in enumerate(data["affiliations"]):
+        label = f"inst:{idx}"
+        affiliation = affiliation.replace("&", "\&")
+        author_str += f"\t{affiliation} \\label{{{label}}} \\and\n"
+
+    author_str += "}\n"
+
+    authors_file = BASE_PATH / "src/text/0-authors.tex"
+
+    log.info(f"Writing {authors_file}")
+
[…]

### 2022-01-28 scripts/latexindent.py

@@ -2,6 +2,8 @@ from pathlib import Path
 import subprocess
 import logging
 
+EXCLUDE_FILES = ["0-authors.tex"]
+
 log = logging.getLogger(__file__)
 logging.basicConfig(level=logging.DEBUG)
 
@@ -10,6 +12,9 @@ BASE_PATH = Path(__file__).parent
 filenames = BASE_PATH.glob("src/text/*.tex")
 
 for filename in filenames:
+    if filename.name in EXCLUDE_FILES:
+        continue
+
     command = ["latexindent.pl"]
     command += [f"{filename}"]
     command += ["-s", "-m", "-l", ".latexindent.yaml"]

### 2022-01-28 src/text/0-authors.tex
Update authors.text

--- 2022-01-25 src/text/0-authors.tex
@@
 
-%Opt in solution for the contributor list...
-
 \author{
-Christoph Deil\inst{\ref{inst:mpik}}
-\and
-Axel Donath\inst{\ref{inst:mpik}}
-\and
-Régis Terrier\inst{\ref{inst:apc}}
-\and
-Johannes King\inst{\ref{inst:mpik}}
-\and
-Léa Jouvin\inst{\ref{inst:apc}}
-\and
-Manuel Paz Arribas\inst{\ref{inst:humboldt}}
-\and
-Ellis Owen\inst{\ref{inst:ucl}}
-\and
-Julien Lefaucheur\inst{\ref{inst:obsparis}}
-\and
-Olga Vorokh\inst{\ref{inst:olga}}
-\and
-Jonathan Harris\inst{\ref{inst:jon}}
-\and
-Brigitta Sipocz\inst{\ref{inst:brigitta1}, \ref{inst:brigitta2}}
-\and
-Dirk Lennarz\inst{\ref{inst:atlanta}}
-\and
-Helen Poon\inst{\ref{inst:mpik}}
-\and
-Nachiketa Chakraborty\inst{\ref{inst:mpik}}
-\and
-Domenico Tiziani\inst{\ref{inst:erlangen}}
-\and
-Luigi Tibaldo\inst{\ref{inst:mpik}}
-\and
-Victor Zabalza\inst{\ref{inst:victor}}
-\and
-Rolf Bühler\inst{\ref{inst:desy}}
-\and
-Stefan Klepser\inst{\ref{inst:desy}}
-\and
-Ignasi Reichardt\inst{\ref{inst:padova}}
+	Axel Donath \inst{\ref{inst:0}} \and
+	Christoph Deil \inst{\ref{inst:1}} \and
+	Régis Terrier \inst{\ref{inst:2}} \and
+	Johannes King \inst{\ref{inst:3}} \and
+	Jose Enrique Ruiz \inst{\ref{inst:4}} \and
+	Quentin Remy \inst{\ref{inst:5}} \and
+	Léa Jouvin \inst{\ref{inst:6}} \and
+	Atreyee Sinha \inst{\ref{inst:7}} \and
+	Matthew Wood \inst{\ref{inst:8}} \and
+	Fabio Pintore \inst{\ref{inst:9}} \and
+	Manuel Paz Arribas \inst{\ref{inst:10}} \and
+	Laura Olivera \inst{\ref{inst:11}} \and
+	Luca Giunti \inst{\ref{inst:12}} \and
+	Bruno Khelifi \inst{\ref{inst:13}} \and
+	Ellis Owen \inst{\ref{inst:14}} \and
+	Brigitta Sipőcz \inst{\ref{inst:15}} \and
+	Olga Vorokh \inst{\ref{inst:16}} \and
+	Julien Lefaucheur \inst{\ref{inst:17}} \and
+	Fabio Acero \inst{\ref{inst:18}} \and
+	Thomas Robitaille \inst{\ref{inst:19}} \and
+	David Fidalgo \inst{\ref{inst:20}} \and
+	Jonathan D. Harris \inst{\ref{inst:21}} \and
+	Lars Mohrmann \inst{\ref{inst:22}} \and
+	Cosimo Nigro \inst{\ref{inst:23}} \and
+	Dirk Lennarz \inst{\ref{inst:24}} \and
+	Jalel Eddine Hajlaoui \inst{\ref{inst:25}} \and
+	Alexis de Almeida Coutinho \inst{\ref{inst:26}} \and
+	Matthias Wegenmat \inst{\ref{inst:27}} \and
+	Dimitri Papadopoulos \inst{\ref{inst:28}} \and
+	Maximilian Nöthe \inst{\ref{inst:29}} \and
+	Nachiketa Chakraborty \inst{\ref{inst:30}} \and
+	Michael Droettboom \inst{\ref{inst:31}} \and
+	Jason Watson \inst{\ref{inst:32}} \and
+	Helen Poon \inst{\ref{inst:33}} \and
+	Arjun Voruganti \inst{\ref{inst:34}} \and
+	Vikas Joshi \inst{\ref{inst:35}} \and
+	Thomas Armstrong \inst{\ref{inst:36}} \and
+	Erik Tollerud \inst{\ref{inst:37}} \and
+	Erik M. Bray \inst{\ref{inst:38}} \and
+	Domenico Tiziani \inst{\ref{inst:39}} \and
+	Gabriel Emery \inst{\ref{inst:40}} \and
+	Hubert Siejkowski \inst{\ref{inst:41}} \and
+	Kai Brügge \inst{\ref{inst:42}} \and
+	Luigi Tibaldo \inst{\ref{inst:43}} \and
+	Arpit Gogia \inst{\ref{inst:44}} \and
+	Ignacio Minaya \inst{\ref{inst:45}} \and
+	Marion Spir-Jacob \inst{\ref{inst:46}} \and
+	Yves Gallant \inst{\ref{inst:47}} \and
+	Andrew W. Chen \inst{\ref{inst:48}} \and
+	Roberta Zanin \inst{\ref{inst:49}} \and
+	Jean-Philippe Lenain \inst{\ref{inst:50}} \and
+	Larry Bradley \inst{\ref{inst:51}} \and
+	Kaori Nakashima \inst{\ref{inst:52}} \and
+	Anne Lemière \inst{\ref{inst:53}} \and
+	Mathieu de Bony \inst{\ref{inst:54}} \and
+	Matthew Craig \inst{\ref{inst:55}} \and
+	Lab Saha \inst{\ref{inst:56}} \and
+	Zé Vinicius \inst{\ref{inst:57}} \and
+	Kyle Barbary \inst{\ref{inst:58}} \and
+	Thomas Vuillaume \inst{\ref{inst:59}} \and
+	Adam Ginsburg \inst{\ref{inst:60}} \and
+	Daniel Morcuende \inst{\ref{inst:61}} \and
+	José Luis Contreras \inst{\ref{inst:62}} \and
+	Laura Vega Garcia \inst{\ref{inst:63}} \and
+	Oscar Blanch Bigas \inst{\ref{inst:64}} \and
+	Víctor Zabalza \inst{\ref{inst:65}} \and
+	Wolfgang Kerzendorf \inst{\ref{inst:66}} \and
+	Rolf Buehler \inst{\ref{inst:67}} \and
+	Sebastian Panny \inst{\ref{inst:68}} \and
+	Silvia Manconi \inst{\ref{inst:69}} \and
+	Stefan Klepser \inst{\ref{inst:70}} \and
+	Peter Deiml \inst{\ref{inst:71}} \and
+	Johannes Buchner \inst{\ref{inst:72}} \and
+	Hugo van Kemenade \inst{\ref{inst:73}} \and
+	Eric O. Lebigot \inst{\ref{inst:74}} \and
+	Benjamin Alan Weaver \inst{\ref{inst:75}} \and
+	Debanjan Bose \inst{\ref{inst:76}} \and
+	Rubén López-Coto \inst{\ref{inst:77}} \and
+	Sam Carter \inst{\ref{inst:78}} \and
 }
@@
 \institute{
-Max-Planck-Institut f\"{u}r Kernphysik, Heidelberg, Germany
-\label{inst:mpik}
-\and
-APC, University of Paris 7, France
-\label{inst:apc}
-\and
-LUTH, Observatoire de Paris, Meudon, France
-\label{inst:obsparis}
-\and
-DESY, Zeuthen, Germany
-\label{inst:desy}
-\and
-Humboldt University, Berlin, Germany
-\label{inst:humboldt}
-\and
-UCL-MSSL, Dorking, United Kingdom
-\label{inst:ucl}
-\and
-INFN, Padova, Italy
-\label{inst:padova}
-\and
-Belarusian State University, Belarus, Minsk
-\label{inst:olga}
-\and
-FAU, Erlangen, Germany
-\label{inst:erlangen}
-\and
-School of Physics and Center for Relativistic Astrophysics, Georgia
-Institute of Technology, Atlanta, GA, USA
-\label{inst:atlanta}
-\and
-Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, AL10 9AB, UK
-\label{inst:brigitta1}
-\and
-Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK
-\label{inst:brigitta2}
-\and
-Department of Physics, Durham University, South Road, Durham, DH1 3LE, UK
-\label{inst:jon}
-\and
-TODO: Victor address
-\label{inst:victor}
+	Center for Astrophysics | Harvard \& Smithonian \label{inst:0} \and
+	HeidelbergCement \label{inst:1} \and
+	Astroparticle and Cosmology, CNRS, Université de Paris \label{inst:2} \and
+	Pamyra \label{inst:3} \and
+	Instituto de Astrofísica de Andalucía - CSIC \label{inst:4} \and
+	MPIK \label{inst:5} \and
+	unknown \label{inst:6} \and
+	EMFTEL, UCM \label{inst:7} \and
+	unknown \label{inst:8} \and
+	INAF/IASF Palermo \label{inst:9} \and
+	unknown \label{inst:10} \and
+	MPIK \label{inst:11} \and
+	APC \label{inst:12} \and
+	CNRS \label{inst:13} \and
+	unknown \label{inst:14} \and
+	DIRAC Institute, UW \label{inst:15} \and
+	unknown \label{inst:16} \and
+	unknown \label{inst:17} \and
+	DAp/AIM, CEA-Saclay/CNRS \label{inst:18} \and
+	unknown \label{inst:19} \and
+	unknown \label{inst:20} \and
+	unknown \label{inst:21} \and
+	MPIK, Heidelberg \label{inst:22} \and
+	IFAE \label{inst:23} \and
+	unknown \label{inst:24} \and
+	unknown \label{inst:25} \and
+	unknown \label{inst:26} \and
+	unknown \label{inst:27} \and
+	unknown \label{inst:28} \and
+	unknown \label{inst:29} \and
+	unknown \label{inst:30} \and
+	Mozilla \label{inst:31} \and
+	DESY \label{inst:32} \and
+	unknown \label{inst:33} \and
+	unknown \label{inst:34} \and
+	unknown \label{inst:35} \and
+	unknown \label{inst:36} \and
+	Space Telescope Science Institute \label{inst:37} \and
+	unknown \label{inst:38} \and
+	unknown \label{inst:39} \and
+	unknown \label{inst:40} \and
+	unknown \label{inst:41} \and
+	unknown \label{inst:42} \and
+	unknown \label{inst:43} \and
+	unknown \label{inst:44} \and
+	unknown \label{inst:45} \and
+	unknown \label{inst:46} \and
+	unknown \label{inst:47} \and
+	unknown \label{inst:48} \and
+	unknown \label{inst:49} \and
+	unknown \label{inst:50} \and
+	unknown \label{inst:51} \and
+	unknown \label{inst:52} \and
+	unknown \label{inst:53} \and
+	unknown \label{inst:54} \and
+	unknown \label{inst:55} \and
+	unknown \label{inst:56} \and
+	unknown \label{inst:57} \and
+	unknown \label{inst:58} \and
+	unknown \label{inst:59} \and
+	unknown \label{inst:60} \and
+	unknown \label{inst:61} \and
+	unknown \label{inst:62} \and
+	unknown \label{inst:63} \and
+	unknown \label{inst:64} \and
+	unknown \label{inst:65} \and
+	unknown \label{inst:66} \and
+	unknown \label{inst:67} \and
+	unknown \label{inst:68} \and
+	unknown \label{inst:69} \and
+	unknown \label{inst:70} \and
+	unknown \label{inst:71} \and
+	unknown \label{inst:72} \and
+	unknown \label{inst:73} \and
+	unknown \label{inst:74} \and
+	unknown \label{inst:75} \and
+	unknown \label{inst:76} \and
+	unknown \label{inst:77} \and
+	unknown \label{inst:78} \and
 }

### 2022-01-28 src/text/0-authors.tex
Adapt authors script

--- 2022-01-25 src/text/0-authors.tex
@@
 
-%Opt in solution for the contributor list...
-
 \author{
-Christoph Deil\inst{\ref{inst:mpik}}
-\and
-Axel Donath\inst{\ref{inst:mpik}}
-\and
-Régis Terrier\inst{\ref{inst:apc}}
-\and
-Johannes King\inst{\ref{inst:mpik}}
-\and
-Léa Jouvin\inst{\ref{inst:apc}}
-\and
-Manuel Paz Arribas\inst{\ref{inst:humboldt}}
-\and
-Ellis Owen\inst{\ref{inst:ucl}}
-\and
-Julien Lefaucheur\inst{\ref{inst:obsparis}}
-\and
-Olga Vorokh\inst{\ref{inst:olga}}
-\and
-Jonathan Harris\inst{\ref{inst:jon}}
-\and
-Brigitta Sipocz\inst{\ref{inst:brigitta1}, \ref{inst:brigitta2}}
-\and
-Dirk Lennarz\inst{\ref{inst:atlanta}}
-\and
-Helen Poon\inst{\ref{inst:mpik}}
-\and
-Nachiketa Chakraborty\inst{\ref{inst:mpik}}
-\and
-Domenico Tiziani\inst{\ref{inst:erlangen}}
-\and
-Luigi Tibaldo\inst{\ref{inst:mpik}}
-\and
-Victor Zabalza\inst{\ref{inst:victor}}
-\and
-Rolf Bühler\inst{\ref{inst:desy}}
-\and
-Stefan Klepser\inst{\ref{inst:desy}}
-\and
-Ignasi Reichardt\inst{\ref{inst:padova}}
+	Axel Donath \inst{\ref{inst:3}} \and
+	Christoph Deil \inst{\ref{inst:8}} \and
+	Régis Terrier \inst{\ref{inst:1}} \and
+	Johannes King \inst{\ref{inst:15}} \and
+	Jose Enrique Ruiz \inst{\ref{inst:11}} \and
+	Quentin Remy \inst{\ref{inst:12}} \and
+	Léa Jouvin \inst{\ref{inst:unknown}} \and
+	Atreyee Sinha \inst{\ref{inst:7}} \and
+	Matthew Wood \inst{\ref{inst:unknown}} \and
+	Fabio Pintore \inst{\ref{inst:10}} \and
+	Manuel Paz Arribas \inst{\ref{inst:unknown}} \and
+	Laura Olivera \inst{\ref{inst:12}} \and
+	Luca Giunti \inst{\ref{inst:0}} \and
+	Bruno Khelifi \inst{\ref{inst:2}} \and
+	Ellis Owen \inst{\ref{inst:unknown}} \and
+	Brigitta Sipőcz \inst{\ref{inst:6}} \and
+	Olga Vorokh \inst{\ref{inst:unknown}} \and
+	Julien Lefaucheur \inst{\ref{inst:unknown}} \and
+	Fabio Acero \inst{\ref{inst:4}} \and
+	Thomas Robitaille \inst{\ref{inst:unknown}} \and
+	David Fidalgo \inst{\ref{inst:unknown}} \and
+	Jonathan D. Harris \inst{\ref{inst:unknown}} \and
+	Lars Mohrmann \inst{\ref{inst:13}} \and
+	Cosimo Nigro \inst{\ref{inst:9}} \and
+	Dirk Lennarz \inst{\ref{inst:unknown}} \and
+	Jalel Eddine Hajlaoui \inst{\ref{inst:unknown}} \and
+	Alexis de Almeida Coutinho \inst{\ref{inst:unknown}} \and
+	Matthias Wegenmat \inst{\ref{inst:unknown}} \and
+	Dimitri Papadopoulos \inst{\ref{inst:unknown}} \and
+	Maximilian Nöthe \inst{\ref{inst:unknown}} \and
+	Nachiketa Chakraborty \inst{\ref{inst:unknown}} \and
+	Michael Droettboom \inst{\ref{inst:14}} \and
+	Jason Watson \inst{\ref{inst:5}} \and
+	Helen Poon \inst{\ref{inst:unknown}} \and
+	Arjun Voruganti \inst{\ref{inst:unknown}} \and
+	Vikas Joshi \inst{\ref{inst:unknown}} \and
+	Thomas Armstrong \inst{\ref{inst:unknown}} \and
+	Erik Tollerud \inst{\ref{inst:16}} \and
+	Erik M. Bray \inst{\ref{inst:unknown}} \and
+	Domenico Tiziani \inst{\ref{inst:unknown}} \and
+	Gabriel Emery \inst{\ref{inst:unknown}} \and
+	Hubert Siejkowski \inst{\ref{inst:unknown}} \and
+	Kai Brügge \inst{\ref{inst:unknown}} \and
+	Luigi Tibaldo \inst{\ref{inst:unknown}} \and
+	Arpit Gogia \inst{\ref{inst:unknown}} \and
+	Ignacio Minaya \inst{\ref{inst:unknown}} \and
+	Marion Spir-Jacob \inst{\ref{inst:unknown}} \and
+	Yves Gallant \inst{\ref{inst:unknown}} \and
+	Andrew W. Chen \inst{\ref{inst:unknown}} \and
+	Roberta Zanin \inst{\ref{inst:unknown}} \and
+	Jean-Philippe Lenain \inst{\ref{inst:unknown}} \and
+	Larry Bradley \inst{\ref{inst:unknown}} \and
+	Kaori Nakashima \inst{\ref{inst:unknown}} \and
+	Anne Lemière \inst{\ref{inst:unknown}} \and
+	Mathieu de Bony \inst{\ref{inst:unknown}} \and
+	Matthew Craig \inst{\ref{inst:unknown}} \and
+	Lab Saha \inst{\ref{inst:unknown}} \and
+	Zé Vinicius \inst{\ref{inst:unknown}} \and
+	Kyle Barbary \inst{\ref{inst:unknown}} \and
+	Thomas Vuillaume \inst{\ref{inst:unknown}} \and
+	Adam Ginsburg \inst{\ref{inst:unknown}} \and
+	Daniel Morcuende \inst{\ref{inst:unknown}} \and
+	José Luis Contreras \inst{\ref{inst:unknown}} \and
+	Laura Vega Garcia \inst{\ref{inst:unknown}} \and
+	Oscar Blanch Bigas \inst{\ref{inst:unknown}} \and
+	Víctor Zabalza \inst{\ref{inst:unknown}} \and
+	Wolfgang Kerzendorf \inst{\ref{inst:unknown}} \and
+	Rolf Buehler \inst{\ref{inst:unknown}} \and
+	Sebastian Panny \inst{\ref{inst:unknown}} \and
+	Silvia Manconi \inst{\ref{inst:unknown}} \and
+	Stefan Klepser \inst{\ref{inst:unknown}} \and
+	Peter Deiml \inst{\ref{inst:unknown}} \and
+	Johannes Buchner \inst{\ref{inst:unknown}} \and
+	Hugo van Kemenade \inst{\ref{inst:unknown}} \and
+	Eric O. Lebigot \inst{\ref{inst:unknown}} \and
+	Benjamin Alan Weaver \inst{\ref{inst:unknown}} \and
+	Debanjan Bose \inst{\ref{inst:unknown}} \and
+	Rubén López-Coto \inst{\ref{inst:unknown}} \and
+	Sam Carter \inst{\ref{inst:unknown}}
 }
@@
 \institute{
-Max-Planck-Institut f\"{u}r Kernphysik, Heidelberg, Germany
-\label{inst:mpik}
-\and
-APC, University of Paris 7, France
-\label{inst:apc}
-\and
-LUTH, Observatoire de Paris, Meudon, France
-\label{inst:obsparis}
-\and
-DESY, Zeuthen, Germany
-\label{inst:desy}
-\and
-Humboldt University, Berlin, Germany
-\label{inst:humboldt}
-\and
-UCL-MSSL, Dorking, United Kingdom
-\label{inst:ucl}
-\and
-INFN, Padova, Italy
-\label{inst:padova}
-\and
-Belarusian State University, Belarus, Minsk
-\label{inst:olga}
-\and
-FAU, Erlangen, Germany
-\label{inst:erlangen}
-\and
-School of Physics and Center for Relativistic Astrophysics, Georgia
-Institute of Technology, Atlanta, GA, USA
-\label{inst:atlanta}
-\and
-Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, AL10 9AB, UK
-\label{inst:brigitta1}
-\and
-Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK
-\label{inst:brigitta2}
-\and
-Department of Physics, Durham University, South Road, Durham, DH1 3LE, UK
-\label{inst:jon}
-\and
-TODO: Victor address
-\label{inst:victor}
+	APC \label{inst:0} \and
+	Astroparticle and Cosmology, CNRS, Université de Paris \label{inst:1} \and
+	CNRS \label{inst:2} \and
+	Center for Astrophysics | Harvard \& Smithonian \label{inst:3} \and
+	DAp/AIM, CEA-Saclay/CNRS \label{inst:4} \and
+	DESY \label{inst:5} \and
+	DIRAC Institute, UW \label{inst:6} \and
+	EMFTEL, UCM \label{inst:7} \and
+	HeidelbergCement \label{inst:8} \and
+	IFAE \label{inst:9} \and
+	INAF/IASF Palermo \label{inst:10} \and
+	Instituto de Astrofísica de Andalucía - CSIC \label{inst:11} \and
+	MPIK \label{inst:12} \and
+	MPIK, Heidelberg \label{inst:13} \and
+	Mozilla \label{inst:14} \and
+	Pamyra \label{inst:15} \and
+	Space Telescope Science Institute \label{inst:16} \and
+	unknown \label{inst:unknown}
 }

### 2022-01-28 scripts/authors.py

@@ -4,11 +4,15 @@ import subprocess
 import click
 from ruamel.yaml import YAML
 from pathlib import Path
+from astropy.table import Table, vstack
 
 log = logging.getLogger(__name__)
 logging.basicConfig(level=logging.DEBUG)
 
 BASE_PATH = Path(__file__).parent.parent
+
+# TODO: get rid of the hard coded path, either download the file or
+#  introduce gammapy as sub-module to the paper repo
 PATH = Path("/Users/adonath/github/adonath/gammapy")
 CITATION_CFF = PATH / "CITATION.cff"
 
@@ -45,31 +49,51 @@ def get_citation_cff_authors_and_affiliations():
         affiliation = author_data.get("affiliation", "unknown")
         affiliations.append(affiliation)
 
-    return {
-        "authors": authors,
-        "affiliations": affiliations,
-    }
+    table = Table()
+    table["author"] = authors
+    table["affiliation"] = affiliations
+    table["label"] = "inst:unknown"
+
+    table_grouped = table.group_by("affiliation")
+
+    for idx, group in enumerate(table_grouped.groups):
+        affiliation = group[0]["affiliation"]
+
+        if affiliation == "unknown":
+            continue
+
+        mask = table["affiliation"] == affiliation
+        table["label"][mask] = f"inst:{idx}"
+
+    return table
 
 
 def write_author_file():
-    data = get_citation_cff_authors_and_affiliations()
+    table = get_citation_cff_authors_and_affiliations()
 
     author_str = "\\authorrunning{Deil, Donath, Terrier et al.}\n\n"
     author_str += "\\author{\n"
 
-    for idx, author in enumerate(data["authors"]):
-        label = f"inst:{idx}"
-        author_str += f"\t{author} \\inst{{\\ref{{{label}}}}} \\and\n"
+    for idx, row in enumerate(table):
+        author, label = row["author"], row["label"]
+        author_str += f"\t{author} \\inst{{\\ref{{{label}}}}}"
+        if idx < len(table) - 1:
+            author_str += " \\and\n"
 
-    author_str += "}\n\n"
+    author_str += "\n}\n\n"
 
     author_str += "\institute{\n"
-    for idx, affiliation in enumerate(data["affiliations"]):
-        label = f"inst:{idx}"
-        affiliation = affiliation.replace("&", "\&")
-        author_str += f"\t{affiliation} \\label{{{label}}} \\and\n"
 
-    author_str += "}\n"
[…]

### 2022-01-28 src/figures/config.py
Add data flow figure script

@@ -1,6 +1,6 @@
 """General configuration for mpl plotting scripts"""
 from pathlib import Path
-from astropy import untis as u
+from astropy import units as u
 from astropy.units import imperial
 
 BASE_PATH = Path(__file__).parent.parent

### 2022-01-28 src/figures/data_flow.py

@@ -9,8 +9,10 @@ from matplotlib.patches import Polygon, FancyArrow, PathPatch, FancyArrowPatch
 from matplotlib.text import TextPath
 from matplotlib.ticker import MultipleLocator
 from astropy import units as u
-from gammapy.estimators import LightCurve, FluxPoints
+from astropy.table import Table
+from gammapy.estimators import FluxPoints
 from gammapy.maps import Map
+import config
 
 u.imperial.enable()
 
@@ -18,10 +20,11 @@ logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 
 # Gammapy logo font
-matplotlib.rc("text", usetex=True)
-matplotlib.rc("font", **{"family": "sans-serif"})
-params = {"text.latex.preamble": [r"\usepackage{amsmath}"]}
-plt.rcParams.update(params)
+# matplotlib.rc("text", usetex=True)
+# matplotlib.rc("font", **{"family": "sans-serif"})
+# params = {"text.latex.preamble": [r"\usepackage{amsmath}"]}
+# plt.rcParams.update(params)
+plt.rcParams["mathtext.fontset"] = "cm"
 
 
 FIGSIZE_MM = [180, 131] * u.mm
@@ -77,7 +80,7 @@ def plot_sub_package_icon(
         color=GP_ORANGE,
     )
     ax.text(offset[0] + 6, offset[1] + 5.5, s="$\pi$", size=fontsize_gp, color=color)
-    ax.text(offset[0] + 1, offset[1] + 1.5, s=name, size=12, color=color)
+    ax.text(offset[0] + 1, offset[1] + 1.5, s=name, size=9.5, color=color)
 
     for idx, cls in enumerate(classes):
         ax.text(offset[0], offset[1] - 4 - 4.2 * idx, s=cls, size=8, color=color)
@@ -162,26 +165,27 @@ def plot_catalog(ax):
 
 
 def plot_lightcurve(ax):
-    filename = "data/light_curve.fits"
+    filename = config.BASE_PATH / "data/light_curve.fits"
     log.info(f"Reading: {filename}")
 
-    lc = LightCurve.read(filename)
-    lc.plot(ax=ax, marker="None", label="1 TeV")
+    lc = FluxPoints.read(filename, format="lightcurve")
[…]

### 2022-01-28 src/figures/config.py
Use config for figure size

@@ -13,10 +13,19 @@ FIGURE_WIDTH_AA = {
 }
 
 
-def get_figure_size_aa(aspect_ratio=1, width_aa="single-column"):
-    """Get figure size in inches"""
-    width = FIGURE_WIDTH_AA[width_aa]
-    height = width / aspect_ratio
-    return width.to_value(imperial.inch), height.to_value(imperial.inch)
+class FigureSizeAA:
+    """Figure size A&A"""
+    def __init__(self, aspect_ratio=1, width_aa="single-column"):
+        self.width = FIGURE_WIDTH_AA[width_aa]
+        self.height = self.width / aspect_ratio
 
+    @property
+    def inch(self):
+        """Figure size in inch"""
+        return self.width.to_value(imperial.inch), self.height.to_value(imperial.inch)
+
+    @property
+    def mm(self):
+        """Figure size in mm"""
+        return self.width.value, self.height.value
 

### 2022-01-28 src/figures/data_flow.py

@@ -19,16 +19,9 @@ u.imperial.enable()
 logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 
-# Gammapy logo font
-# matplotlib.rc("text", usetex=True)
-# matplotlib.rc("font", **{"family": "sans-serif"})
-# params = {"text.latex.preamble": [r"\usepackage{amsmath}"]}
-# plt.rcParams.update(params)
 plt.rcParams["mathtext.fontset"] = "cm"
 
-
-FIGSIZE_MM = [180, 131] * u.mm
-FIGSIZE = FIGSIZE_MM.to_value("inch")
+FIGSIZE = config.FigureSizeAA(aspect_ratio=1.3740, width_aa="two-column")
 
 FOLDER_ICON = np.array(
     [(0, 0), (0, 0.8), (0.08, 1), (0.5, 1), (0.58, 0.8), (0.93, 0.8), (0.93, 0)]
@@ -275,11 +268,11 @@ def plot_high_level_interface(fig, ax, ypos=24):
 @click.command()
 @click.option("--draft", is_flag=True)
 def main(draft=True):
-    fig = plt.figure(figsize=FIGSIZE)
+    fig = plt.figure(figsize=FIGSIZE.inch)
 
     ax = fig.add_axes([0, 0, 1, 1])
-    ax.set_xlim(0, FIGSIZE_MM[0].value)
-    ax.set_ylim(0, FIGSIZE_MM[1].value)
+    ax.set_xlim(0, FIGSIZE.mm[0])
+    ax.set_ylim(0, FIGSIZE.mm[1])
 
     ax.tick_params(axis="both", direction="in", pad=-20)
     ax.xaxis.set_minor_locator(MultipleLocator(10))

### 2022-01-31 src/text/0-authors.tex

--- 2022-01-27 src/text/0-authors.tex
@@
 
-%Opt in solution for the contributor list...
-
 \author{
-	Christoph Deil\inst{\ref{inst:mpik}} \and Axel Donath\inst{\ref{inst:mpik}}
-	\and Régis Terrier\inst{\ref{inst:apc}} \and Johannes
-	King\inst{\ref{inst:mpik}} \and Léa Jouvin\inst{\ref{inst:apc}} \and Manuel Paz
-	Arribas\inst{\ref{inst:humboldt}} \and Ellis Owen\inst{\ref{inst:ucl}} \and
-	Julien Lefaucheur\inst{\ref{inst:obsparis}} \and Olga
-	Vorokh\inst{\ref{inst:olga}} \and Jonathan Harris\inst{\ref{inst:jon}} \and
-	Brigitta Sipocz\inst{\ref{inst:brigitta1}, \ref{inst:brigitta2}} \and Dirk
-	Lennarz\inst{\ref{inst:atlanta}} \and Helen Poon\inst{\ref{inst:mpik}} \and
-	Nachiketa Chakraborty\inst{\ref{inst:mpik}} \and Domenico
-	Tiziani\inst{\ref{inst:erlangen}} \and Luigi Tibaldo\inst{\ref{inst:mpik}} \and
-	Victor Zabalza\inst{\ref{inst:victor}} \and Rolf Bühler\inst{\ref{inst:desy}}
-	\and Stefan Klepser\inst{\ref{inst:desy}} \and Ignasi
-	Reichardt\inst{\ref{inst:padova}} }
+	Axel Donath \inst{\ref{inst:6}} \and
+	Christoph Deil \inst{\ref{inst:13}} \and
+	Régis Terrier \inst{\ref{inst:2}} \and
+	Johannes King \inst{\ref{inst:22}} \and
+	Jose Enrique Ruiz \inst{\ref{inst:17}} \and
+	Quentin Remy \inst{\ref{inst:18}} \and
+	Léa Jouvin \inst{\ref{inst:unknown}} \and
+	Atreyee Sinha \inst{\ref{inst:26}} \and
+	Matthew Wood \inst{\ref{inst:11}} \and
+	Fabio Pintore \inst{\ref{inst:14}} \and
+	Manuel Paz Arribas \inst{\ref{inst:unknown}} \and
+	Laura Olivera \inst{\ref{inst:18}} \and
+	Luca Giunti \inst{\ref{inst:2}} \and
+	Bruno Khelifi \inst{\ref{inst:3}} \and
+	Ellis Owen \inst{\ref{inst:21}} \and
+	Brigitta Sipőcz \inst{\ref{inst:5}} \and
+	Olga Vorokh \inst{\ref{inst:unknown}} \and
+	Julien Lefaucheur \inst{\ref{inst:unknown}} \and
+	Fabio Acero \inst{\ref{inst:7}} \and
+	Thomas Robitaille \inst{\ref{inst:1}} \and
+	David Fidalgo \inst{\ref{inst:unknown}} \and
+	Jonathan D. Harris \inst{\ref{inst:unknown}} \and
+	Cosimo Nigro \inst{\ref{inst:15}} \and
+	Lars Mohrmann \inst{\ref{inst:18}} \and
+	Dirk Lennarz \inst{\ref{inst:0}} \and
+	Jalel Eddine Hajlaoui \inst{\ref{inst:2}} \and
+	Alexis de Almeida Coutinho \inst{\ref{inst:27}} \and
+	Matthias Wegenmat \inst{\ref{inst:unknown}} \and
+	Dimitri Papadopoulos \inst{\ref{inst:unknown}} \and
+	Maximilian Nöthe \inst{\ref{inst:25}} \and
+	Nachiketa Chakraborty \inst{\ref{inst:unknown}} \and
+	Michael Droettboom \inst{\ref{inst:20}} \and
+	Helen Poon \inst{\ref{inst:unknown}} \and
+	Arjun Voruganti \inst{\ref{inst:unknown}} \and
+	Jason Watson \inst{\ref{inst:8}} \and
+	Thomas Armstrong \inst{\ref{inst:unknown}} \and
+	Vikas Joshi \inst{\ref{inst:12}} \and
+	Erik Tollerud \inst{\ref{inst:24}} \and
+	Erik M. Bray \inst{\ref{inst:unknown}} \and
+	Domenico Tiziani \inst{\ref{inst:unknown}} \and
+	Gabriel Emery \inst{\ref{inst:unknown}} \and
+	Hubert Siejkowski \inst{\ref{inst:unknown}} \and
+	Kai Brügge \inst{\ref{inst:23}} \and
+	Luigi Tibaldo \inst{\ref{inst:16}} \and
+	Arpit Gogia \inst{\ref{inst:unknown}} \and
+	Ignacio Minaya \inst{\ref{inst:unknown}} \and
+	Marion Spir-Jacob \inst{\ref{inst:unknown}} \and
+	Yves Gallant \inst{\ref{inst:unknown}} \and
+	Andrew W. Chen \inst{\ref{inst:9}} \and
+	Roberta Zanin \inst{\ref{inst:4}} \and
+	Jean-Philippe Lenain \inst{\ref{inst:unknown}} \and
+	Larry Bradley \inst{\ref{inst:24}} \and
+	Kaori Nakashima \inst{\ref{inst:12}} \and
+	Anne Lemière \inst{\ref{inst:2}} \and
+	Mathieu de Bony \inst{\ref{inst:unknown}} \and
+	Matthew Craig \inst{\ref{inst:unknown}} \and
+	Lab Saha \inst{\ref{inst:6}} \and
+	Zé Vinicius \inst{\ref{inst:unknown}} \and
+	Kyle Barbary \inst{\ref{inst:unknown}} \and
+	Thomas Vuillaume \inst{\ref{inst:28}} \and
+	Adam Ginsburg \inst{\ref{inst:unknown}} \and
+	Daniel Morcuende \inst{\ref{inst:unknown}} \and
+	José Luis Contreras \inst{\ref{inst:unknown}} \and
+	Laura Vega Garcia \inst{\ref{inst:unknown}} \and
+	Oscar Blanch Bigas \inst{\ref{inst:unknown}} \and
+	Víctor Zabalza \inst{\ref{inst:unknown}} \and
+	Wolfgang Kerzendorf \inst{\ref{inst:19}} \and
+	Rolf Buehler \inst{\ref{inst:10}} \and
+	Sebastian Panny \inst{\ref{inst:unknown}} \and
+	Silvia Manconi \inst{\ref{inst:unknown}} \and
+	Stefan Klepser \inst{\ref{inst:10}} \and
+	Peter Deiml \inst{\ref{inst:unknown}} \and
+	Johannes Buchner \inst{\ref{inst:unknown}} \and
+	Hugo van Kemenade \inst{\ref{inst:unknown}} \and
+	Eric O. Lebigot \inst{\ref{inst:unknown}} \and
+	Benjamin Alan Weaver \inst{\ref{inst:unknown}} \and
+	Debanjan Bose \inst{\ref{inst:unknown}} \and
+	Rubén López-Coto \inst{\ref{inst:unknown}} \and
+	Sam Carter \inst{\ref{inst:unknown}}
+}
 
 \institute{
-Max-Planck-Institut f\"{u}r Kernphysik, Heidelberg, Germany \label{inst:mpik}
-\and APC, University of Paris 7, France \label{inst:apc} \and LUTH,
-Observatoire de Paris, Meudon, France \label{inst:obsparis} \and DESY, Zeuthen,
-Germany \label{inst:desy} \and Humboldt University, Berlin, Germany
-\label{inst:humboldt} \and UCL-MSSL, Dorking, United Kingdom \label{inst:ucl}
-\and INFN, Padova, Italy \label{inst:padova} \and Belarusian State University,
-Belarus, Minsk \label{inst:olga} \and FAU, Erlangen, Germany
-\label{inst:erlangen} \and School of Physics and Center for Relativistic
-Astrophysics, Georgia Institute of Technology, Atlanta, GA, USA
-\label{inst:atlanta} \and Centre for Astrophysics Research, University of
-Hertfordshire, College Lane, Hatfield, AL10 9AB, UK \label{inst:brigitta1} \and
-Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3
-0HA, UK \label{inst:brigitta2} \and Department of Physics, Durham University,
-South Road, Durham, DH1 3LE, UK \label{inst:jon} \and TODO: Victor address
-\label{inst:victor} }
+	Amazon, Atlanta GA, US \label{inst:0} \and
+	Aperio Software, Insight House, Riverside Business Park, Stoney Common Road, Stansted, Essex, CM24 8PL, UK \label{inst:1} \and
+	Astroparticle and Cosmology Laboratory CNRS, Université de Paris, 10 Rue Alice Domon et Léonie Duquet, 75013 Paris, France \label{inst:2} \and
+	CNRS \label{inst:3} \and
+	CTA Observatory gGmbH, Via Piero Gobetti 93/3 40129 Bologna, Italy \label{inst:4} \and
+	California Institute of Technology, Pasadena CA, US \label{inst:5} \and
+	Center for Astrophysics | Harvard \& Smithsonian, CfA, 60 Garden St., 02138 Cambridge MA, US \label{inst:6} \and
+	DAp/AIM, CEA-Saclay/CNRS, France \label{inst:7} \and
+	DESY \label{inst:8} \and
+	Department of Physics, University of the Free State, PO Box339, Bloemfontein 9300, South Africa \label{inst:9} \and
+	Deutsches Elektronen-Synchrotron, DESY, Platanenallee 6 15738 Zeuthen, Germany \label{inst:10} \and
+	Facebook, 1 Hacker Way, Menlo Park, CA 94025, US \label{inst:11} \and
+	Friedrich-Alexander-Universität Erlangen-Nürnberg, Erlangen Centre for Astroparticle Physics, Erwin-Rommel-Str. 1 91058 Erlangen, Germany \label{inst:12} \and
+	HeidelbergCement AG, Berliner Straße 6, 69120 Heidelberg, Germany \label{inst:13} \and
+	INAF/IASF, via Ugo La Malfa 153,  90146 Palermo, Italy \label{inst:14} \and
+	Institut de Fisica d'altes Energies, IFAE, Edifici Cn, Campus UAB, 08193 Bellaterra (Barcelona), Spain \label{inst:15} \and
+	Institute de Recherche en Astrophysique et Planetologie, IRAP, \label{inst:16} \and
+	Instituto de Astrofísica de Andalucía - CSIC, Gta. de la Astronomía, 18008 Granada, Spain \label{inst:17} \and
+	Max Planck Institut für Kernphysik, MPIK, Saupfercheckweg 1, 69117 Heidelberg, Germany \label{inst:18} \and
+	Michigan State University, Department of Physics and Astronomy, 428 S Shaw Ln East Lansing, MI 48824, US \label{inst:19} \and
+	Mozilla, Mountain View, CA \label{inst:20} \and
+	National Tsing Hua University Institute of Astronomy, Hsinchu, Taiwan \label{inst:21} \and
+	Pamyra \label{inst:22} \and
+	Point 8 GmbH, Rheinlanddamm 201, 44139 Dortmund, Germany \label{inst:23} \and
+	Space Telescope Science Institute, STScI, 3700 San Martin Drive, 21218 Baltimore MD, US \label{inst:24} \and
+	TU Dortmund University, Otto-Hahn-Str. 4a 44227 Dortmund, Germany \label{inst:25} \and
+	Universidad Complutense de Madrid EMFTEL, UCM, Plaza de la Ciencias, 28040 Madrid, Spain \label{inst:26} \and
+	Universidade de São Paulo, Brazil \label{inst:27} \and
+	Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecyde Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:28} \and
+	unknown \label{inst:unknown}
+}

### 2022-01-31 src/text/2-package-subsections/astro.tex
Introduce subfolder for package subsections

\subsection{gammapy.astro}
\label{ssec:gammapy-astro}
\todo{Axel Donath}
Dark matter models, source population modelling

### 2022-01-31 src/text/2-package-subsections/catalog.tex
Introduce subfolder for package subsections

--- 2022-01-26 src/text/2-package.tex
@@
-\section{Gammapy package}
-\label{sec:package}
-
-The \gammapy package is structured into multiple sub-packages
-which mostly follow the stages in the data reduction workflow.
-
-\subsection{Overview}
-\begin{figure*}[t]
-\centering
-\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
-\caption{
-Gammapy sub-package structure and data analysis workflow.
-}
-\label{fig:workflow}
-\end{figure*}
-
-\subsection{gammapy.data}
-The \verb|gammapy.data| sub-package provides access to
-DL3 level data and observation handling.
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_data}
-
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_data}
-\end{figure}
-
-\subsection{gammapy.makers}
-\todo{Regis Terrier}
-Data reduction
-
-\begin{figure}
-\import{code-examples/generated/}{gp_makers}
-
-\caption{Using gammapy.data to access DL3 level data}
-\label{ig*:minted:gp_makers}
-\end{figure}
-
-\subsection{gammapy.datasets}
-\todo{Atreyee Sinha}
-DL4 level data
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_datasets}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_datasets}
-\end{figure}
-
-\subsection{gammapy.modeling}
-\todo{Quentin Remy}
-Models and fitting
-
-\begin{figure}
-\import{code-examples/generated/}{gp_models}
-\caption{Using gammapy.modeling.models}
-\label{fig*:minted:gp_models}
-\end{figure}
-
-\subsection{gammapy.estimators}
+\subsection{gammapy.catalog}
+\label{ssec:gammapy-catalog}
 \todo{Axel Donath}
-Estimators
-
-\subsection{gammapy.visualisation}
-Plotters etc.
-
-\subsection{gammapy.analysis}
-\todo{Jose Enrique writes this...}
-High level analysis API
-
-\subsection{gammapy.astro}
-Dark matter models, source population modelling
-
-\subsection{gammapy.data}
-\todo{Cosimo Nigro}
-
-\subsection{gammapy.catalog}
 Gamma-ray catalog access
@@
 \end{figure}
-
-\subsection{gammapy.maps}
-\todo{Laura Olivera-Nieto}
-The \verb|gammapy.maps| sub-package provides classes for representing pixelized
-data structures with at least two spatial dimensions representing a set of
-coordinates or a region on a sphere. In addition it allows to handle and arbitray
-number of non-spatial data axes, such as time or energy.
-
-It provides a uniform API for WCS, HEALPix and region based data structures.
-
-\begin{figure}
-
-    \import{code-examples/generated/}{gp_maps}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{codeexample:data}
-\end{figure}
-
-\subsection{gammapy.irf}
-\todo{Fabio Pintore}
-IRF classes
-
-\subsection{gammapy.stats}
-\todo{Regis Terrier}
-Statistics methods
-
-\subsection{gammapy.utils}
-Utility functions...
-
-Outline:
-* List typical analysis use cases
-* Can use from Python and Jupyter -> show Figure with Jupyter notebook here.
-* Gammapy code structure
-* How Numpy and Astropy is used
-
-Figures:
-* Add a Figure showing dataflow in a typical application
-DL3 at the top, spectrum, map, lightcurve, fit results at the bottom.
-Mention major classes in between (DataStore, EventList, Map, MapMaker, MapFit, …)
-* Probably not: Figure showing sub-packages and how they relate (gammapy.data and gammapy.irf at the base, then gammapy.maps, etc.
-* The code example Figure how to make a counts map, to explain how the package works.

### 2022-01-31 src/text/2-package-subsections/estimators.tex
Introduce subfolder for package subsections

--- 2022-01-26 src/text/2-package.tex
@@
-\section{Gammapy package}
-\label{sec:package}
-
-The \gammapy package is structured into multiple sub-packages
-which mostly follow the stages in the data reduction workflow.
-
-\subsection{Overview}
-\begin{figure*}[t]
-\centering
-\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
-\caption{
-Gammapy sub-package structure and data analysis workflow.
-}
-\label{fig:workflow}
-\end{figure*}
-
-\subsection{gammapy.data}
-The \verb|gammapy.data| sub-package provides access to
-DL3 level data and observation handling.
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_data}
-
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_data}
-\end{figure}
-
-\subsection{gammapy.makers}
-\todo{Regis Terrier}
-Data reduction
-
-\begin{figure}
-\import{code-examples/generated/}{gp_makers}
-
-\caption{Using gammapy.data to access DL3 level data}
-\label{ig*:minted:gp_makers}
-\end{figure}
-
-\subsection{gammapy.datasets}
-\todo{Atreyee Sinha}
-DL4 level data
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_datasets}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_datasets}
-\end{figure}
-
-\subsection{gammapy.modeling}
-\todo{Quentin Remy}
-Models and fitting
-
-\begin{figure}
-\import{code-examples/generated/}{gp_models}
-\caption{Using gammapy.modeling.models}
-\label{fig*:minted:gp_models}
-\end{figure}
-
 \subsection{gammapy.estimators}
+\label{ssec:gammapy-estimators}
 \todo{Axel Donath}
 Estimators
-
-\subsection{gammapy.visualisation}
-Plotters etc.
-
-\subsection{gammapy.analysis}
-\todo{Jose Enrique writes this...}
-High level analysis API
-
-\subsection{gammapy.astro}
-Dark matter models, source population modelling
-
-\subsection{gammapy.data}
-\todo{Cosimo Nigro}
-
-\subsection{gammapy.catalog}
-Gamma-ray catalog access
-
-\begin{figure}
-\import{code-examples/generated/}{gp_catalogs}
-\caption{Using gammapy.catalogs}
-\label{codeexample:data}
-\end{figure}
-
-\subsection{gammapy.maps}
-\todo{Laura Olivera-Nieto}
-The \verb|gammapy.maps| sub-package provides classes for representing pixelized
-data structures with at least two spatial dimensions representing a set of
-coordinates or a region on a sphere. In addition it allows to handle and arbitray
-number of non-spatial data axes, such as time or energy.
-
-It provides a uniform API for WCS, HEALPix and region based data structures.
-
-\begin{figure}
-
-    \import{code-examples/generated/}{gp_maps}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{codeexample:data}
-\end{figure}
-
-\subsection{gammapy.irf}
-\todo{Fabio Pintore}
-IRF classes
-
-\subsection{gammapy.stats}
-\todo{Regis Terrier}
-Statistics methods
-
-\subsection{gammapy.utils}
-Utility functions...
-
-Outline:
-* List typical analysis use cases
-* Can use from Python and Jupyter -> show Figure with Jupyter notebook here.
-* Gammapy code structure
-* How Numpy and Astropy is used
-
-Figures:
-* Add a Figure showing dataflow in a typical application
-DL3 at the top, spectrum, map, lightcurve, fit results at the bottom.
-Mention major classes in between (DataStore, EventList, Map, MapMaker, MapFit, …)
-* Probably not: Figure showing sub-packages and how they relate (gammapy.data and gammapy.irf at the base, then gammapy.maps, etc.
-* The code example Figure how to make a counts map, to explain how the package works.

### 2022-01-31 src/text/2-package-subsections/maps.tex
Introduce subfolder for package subsections

--- 2022-01-26 src/text/2-package.tex
@@
-\section{Gammapy package}
-\label{sec:package}
-
-The \gammapy package is structured into multiple sub-packages
-which mostly follow the stages in the data reduction workflow.
-
-\subsection{Overview}
-\begin{figure*}[t]
-\centering
-\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
-\caption{
-Gammapy sub-package structure and data analysis workflow.
-}
-\label{fig:workflow}
-\end{figure*}
-
-\subsection{gammapy.data}
-The \verb|gammapy.data| sub-package provides access to
-DL3 level data and observation handling.
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_data}
-
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_data}
-\end{figure}
-
-\subsection{gammapy.makers}
-\todo{Regis Terrier}
-Data reduction
-
-\begin{figure}
-\import{code-examples/generated/}{gp_makers}
-
-\caption{Using gammapy.data to access DL3 level data}
-\label{ig*:minted:gp_makers}
-\end{figure}
-
-\subsection{gammapy.datasets}
-\todo{Atreyee Sinha}
-DL4 level data
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_datasets}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_datasets}
-\end{figure}
-
-\subsection{gammapy.modeling}
-\todo{Quentin Remy}
-Models and fitting
-
-\begin{figure}
-\import{code-examples/generated/}{gp_models}
-\caption{Using gammapy.modeling.models}
-\label{fig*:minted:gp_models}
-\end{figure}
-
-\subsection{gammapy.estimators}
-\todo{Axel Donath}
-Estimators
-
-\subsection{gammapy.visualisation}
-Plotters etc.
-
-\subsection{gammapy.analysis}
-\todo{Jose Enrique writes this...}
-High level analysis API
-
-\subsection{gammapy.astro}
-Dark matter models, source population modelling
-
-\subsection{gammapy.data}
-\todo{Cosimo Nigro}
-
-\subsection{gammapy.catalog}
-Gamma-ray catalog access
-
-\begin{figure}
-\import{code-examples/generated/}{gp_catalogs}
-\caption{Using gammapy.catalogs}
-\label{codeexample:data}
-\end{figure}
-
 \subsection{gammapy.maps}
+\label{ssec:gammapy-maps}
 \todo{Laura Olivera-Nieto}
@@
 data structures with at least two spatial dimensions representing a set of
-coordinates or a region on a sphere. In addition it allows to handle and arbitray
-number of non-spatial data axes, such as time or energy.
+coordinates or a region on a sphere. In addition it allows to handle and
+arbitrary number of non-spatial data axes, such as time or energy.
 
@@
 \end{figure}
-
-\subsection{gammapy.irf}
-\todo{Fabio Pintore}
-IRF classes
-
-\subsection{gammapy.stats}
-\todo{Regis Terrier}
-Statistics methods
-
-\subsection{gammapy.utils}
-Utility functions...
-
-Outline:
-* List typical analysis use cases
-* Can use from Python and Jupyter -> show Figure with Jupyter notebook here.
-* Gammapy code structure
-* How Numpy and Astropy is used
-
-Figures:
-* Add a Figure showing dataflow in a typical application
-DL3 at the top, spectrum, map, lightcurve, fit results at the bottom.
-Mention major classes in between (DataStore, EventList, Map, MapMaker, MapFit, …)
-* Probably not: Figure showing sub-packages and how they relate (gammapy.data and gammapy.irf at the base, then gammapy.maps, etc.
-* The code example Figure how to make a counts map, to explain how the package works.

### 2022-01-31 src/text/2-package-subsections/modeling.tex
Introduce subfolder for package subsections

--- 2022-01-26 src/text/2-package.tex
@@
-\section{Gammapy package}
-\label{sec:package}
-
-The \gammapy package is structured into multiple sub-packages
-which mostly follow the stages in the data reduction workflow.
-
-\subsection{Overview}
-\begin{figure*}[t]
-\centering
-\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
-\caption{
-Gammapy sub-package structure and data analysis workflow.
-}
-\label{fig:workflow}
-\end{figure*}
-
-\subsection{gammapy.data}
-The \verb|gammapy.data| sub-package provides access to
-DL3 level data and observation handling.
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_data}
-
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_data}
-\end{figure}
-
-\subsection{gammapy.makers}
-\todo{Regis Terrier}
-Data reduction
-
-\begin{figure}
-\import{code-examples/generated/}{gp_makers}
-
-\caption{Using gammapy.data to access DL3 level data}
-\label{ig*:minted:gp_makers}
-\end{figure}
-
-\subsection{gammapy.datasets}
-\todo{Atreyee Sinha}
-DL4 level data
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_datasets}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_datasets}
-\end{figure}
-
 \subsection{gammapy.modeling}
+\label{ssec:gammapy-modeling}
 \todo{Quentin Remy}
@@
 \end{figure}
-
-\subsection{gammapy.estimators}
-\todo{Axel Donath}
-Estimators
-
-\subsection{gammapy.visualisation}
-Plotters etc.
-
-\subsection{gammapy.analysis}
-\todo{Jose Enrique writes this...}
-High level analysis API
-
-\subsection{gammapy.astro}
-Dark matter models, source population modelling
-
-\subsection{gammapy.data}
-\todo{Cosimo Nigro}
-
-\subsection{gammapy.catalog}
-Gamma-ray catalog access
-
-\begin{figure}
-\import{code-examples/generated/}{gp_catalogs}
-\caption{Using gammapy.catalogs}
-\label{codeexample:data}
-\end{figure}
-
-\subsection{gammapy.maps}
-\todo{Laura Olivera-Nieto}
-The \verb|gammapy.maps| sub-package provides classes for representing pixelized
-data structures with at least two spatial dimensions representing a set of
-coordinates or a region on a sphere. In addition it allows to handle and arbitray
-number of non-spatial data axes, such as time or energy.
-
-It provides a uniform API for WCS, HEALPix and region based data structures.
-
-\begin{figure}
-
-    \import{code-examples/generated/}{gp_maps}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{codeexample:data}
-\end{figure}
-
-\subsection{gammapy.irf}
-\todo{Fabio Pintore}
-IRF classes
-
-\subsection{gammapy.stats}
-\todo{Regis Terrier}
-Statistics methods
-
-\subsection{gammapy.utils}
-Utility functions...
-
-Outline:
-* List typical analysis use cases
-* Can use from Python and Jupyter -> show Figure with Jupyter notebook here.
-* Gammapy code structure
-* How Numpy and Astropy is used
-
-Figures:
-* Add a Figure showing dataflow in a typical application
-DL3 at the top, spectrum, map, lightcurve, fit results at the bottom.
-Mention major classes in between (DataStore, EventList, Map, MapMaker, MapFit, …)
-* Probably not: Figure showing sub-packages and how they relate (gammapy.data and gammapy.irf at the base, then gammapy.maps, etc.
-* The code example Figure how to make a counts map, to explain how the package works.

### 2022-01-31 src/text/2-package.tex
Replace static data flow figure
Fix typo
Introduce subfolder for package subsections

--- 2022-01-26 src/text/2-package.tex
@@
+\section{Analysis Workflow Overview}
+\label{sec:analysis-workflow-overview}
+
 \section{Gammapy package}
-\label{sec:package}
+\label{sec:gammapy-package}
 
-The \gammapy package is structured into multiple sub-packages
-which mostly follow the stages in the data reduction workflow.
+The \gammapy package is structured into multiple sub-packages which mostly
+follow the stages in the data reduction workflow.
 
 \subsection{Overview}
+\label{ssec:overview}
 \begin{figure*}[t]
 	\centering
-\includegraphics[width=1.\textwidth]{static/data-flow-gammapy}
+	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
 	\caption{
-Gammapy sub-package structure and data analysis workflow.
-}
-\label{fig:workflow}
+		Gammapy sub-package structure and data analysis workflow. }
+	\label{fig:data_flow}
 \end{figure*}
 
-\subsection{gammapy.data}
-The \verb|gammapy.data| sub-package provides access to
-DL3 level data and observation handling.
+Outline: * List typical analysis use cases * Can use from Python and Jupyter ->
+show Figure with Jupyter notebook here. * Gammapy code structure * How Numpy
+and Astropy is used
 
-\begin{figure}
+Figures: * Add a Figure showing dataflow in a typical application DL3 at the
+top, spectrum, map, lightcurve, fit results at the bottom. Mention major
+classes in between (DataStore, EventList, Map, MapMaker, MapFit, …) * Probably
+not: Figure showing sub-packages and how they relate (gammapy.data and
+gammapy.irf at the base, then gammapy.maps, etc. * The code example Figure how
+to make a counts map, to explain how the package works.
 
-\import{code-examples/generated/}{gp_data}
-
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_data}
-\end{figure}
-
-\subsection{gammapy.makers}
-\todo{Regis Terrier}
-Data reduction
-
-\begin{figure}
-\import{code-examples/generated/}{gp_makers}
-
-\caption{Using gammapy.data to access DL3 level data}
-\label{ig*:minted:gp_makers}
-\end{figure}
-
-\subsection{gammapy.datasets}
-\todo{Atreyee Sinha}
-DL4 level data
-
-\begin{figure}
-
-\import{code-examples/generated/}{gp_datasets}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{fig*:minted:gp_datasets}
-\end{figure}
-
-\subsection{gammapy.modeling}
-\todo{Quentin Remy}
-Models and fitting
-
-\begin{figure}
-\import{code-examples/generated/}{gp_models}
-\caption{Using gammapy.modeling.models}
-\label{fig*:minted:gp_models}
-\end{figure}
-
-\subsection{gammapy.estimators}
-\todo{Axel Donath}
-Estimators
-
-\subsection{gammapy.visualisation}
-Plotters etc.
-
-\subsection{gammapy.analysis}
-\todo{Jose Enrique writes this...}
-High level analysis API
-
-\subsection{gammapy.astro}
-Dark matter models, source population modelling
-
-\subsection{gammapy.data}
-\todo{Cosimo Nigro}
-
-\subsection{gammapy.catalog}
-Gamma-ray catalog access
-
-\begin{figure}
-\import{code-examples/generated/}{gp_catalogs}
-\caption{Using gammapy.catalogs}
-\label{codeexample:data}
-\end{figure}
-
-\subsection{gammapy.maps}
-\todo{Laura Olivera-Nieto}
-The \verb|gammapy.maps| sub-package provides classes for representing pixelized
-data structures with at least two spatial dimensions representing a set of
-coordinates or a region on a sphere. In addition it allows to handle and arbitray
-number of non-spatial data axes, such as time or energy.
-
-It provides a uniform API for WCS, HEALPix and region based data structures.
-
-\begin{figure}
-
-    \import{code-examples/generated/}{gp_maps}
-\caption{Using gammapy.data to access DL3 level data with a DataStore}
-\label{codeexample:data}
-\end{figure}
-
-\subsection{gammapy.irf}
-\todo{Fabio Pintore}
-IRF classes
-
-\subsection{gammapy.stats}
-\todo{Regis Terrier}
-Statistics methods
-
-\subsection{gammapy.utils}
-Utility functions...
-
-Outline:
-* List typical analysis use cases
-* Can use from Python and Jupyter -> show Figure with Jupyter notebook here.
-* Gammapy code structure
-* How Numpy and Astropy is used
-
-Figures:
-* Add a Figure showing dataflow in a typical application
-DL3 at the top, spectrum, map, lightcurve, fit results at the bottom.
-Mention major classes in between (DataStore, EventList, Map, MapMaker, MapFit, …)
-* Probably not: Figure showing sub-packages and how they relate (gammapy.data and gammapy.irf at the base, then gammapy.maps, etc.
-* The code example Figure how to make a counts map, to explain how the package works.
+\todo{How to sort the sub-packages? After data flow or alphabetically?}
+\input{text/2-package-subsections/analysis}
+\input{text/2-package-subsections/astro}
+\input{text/2-package-subsections/catalog}
+\input{text/2-package-subsections/data}
+\input{text/2-package-subsections/datasets}
+\input{text/2-package-subsections/estimators}
+\input{text/2-package-subsections/irf}
+\input{text/2-package-subsections/makers}
+\input{text/2-package-subsections/modeling}
+\input{text/2-package-subsections/stats}
+\input{text/2-package-subsections/utils}
+\input{text/2-package-subsections/visualisation}

### 2022-01-31 src/text/2-package-subsections/analysis.tex

\subsection{gammapy.analysis}
\label{ssec:gammapy-analysis}
\todo{Jose Enrique writes this...}
High level analysis API

### 2022-01-31 src/text/2-package-subsections/data.tex

\subsection{gammapy.data}
\label{ssec:gammapy-data}
\todo{Cosimo Nigro}
The \verb|gammapy.data| sub-package provides access to DL3 level data and
observation handling.

\begin{figure}

	\import{code-examples/generated/}{gp_data}

	\caption{Using gammapy.data to access DL3 level data with a DataStore}
	\label{fig*:minted:gp_data}
\end{figure}

### 2022-01-31 src/text/2-package-subsections/datasets.tex

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
\todo{Atreyee Sinha}
DL4 level data

\begin{figure}

	\import{code-examples/generated/}{gp_datasets}
	\caption{Using gammapy.data to access DL3 level data with a DataStore}
	\label{fig*:minted:gp_datasets}
\end{figure}

### 2022-01-31 src/text/2-package-subsections/irf.tex

\subsection{gammapy.irf}
\label{ssec:gammapy-irf}
\todo{Fabio Pintore}
IRF classes

### 2022-01-31 src/text/2-package-subsections/makers.tex

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
\todo{Regis Terrier}
Data reduction

\begin{figure}
	\import{code-examples/generated/}{gp_makers}

	\caption{Using gammapy.data to access DL3 level data}
	\label{ig*:minted:gp_makers}
\end{figure}

### 2022-01-31 src/text/2-package-subsections/stats.tex

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
\todo{Regis Terrier}
Statistics methods

### 2022-01-31 src/text/2-package-subsections/visualisation.tex

\subsection{gammapy.visualisation}
\label{ssec:gammapy-visualisation}
\todo{Axel Donath}
Plotters etc.

### 2022-02-04 src/text/2-package-subsections/datasets.tex
start writing datasets

@@
 \end{figure}
+
+Reduced data, IRFs, and models are bundled together to create a Data Level 4 (DL4).
+This is provide in the Dataset class which computes a likelihood to interface with the Fit class to perform a fitting.
+Corresponding to the different analysis types, five types of datasets are supported in gammapy (\ref{table:datasets_types}).
+3D data cubes (with two spatial and one energy) are represented by MapDatasets, whereas SpectrumDatastes contain binned energy information for a given on region.
+2D images are a special case of MapDatasets, with only one bin in energy.
+The FluxPointsDataset is used to fit pre-computed flux points when no convolution with IRFs are needed.
+
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|l|l|}
+    \hline
+        Dataset Type & Data Type & Reduced IRFs & Geometry & Additional Quantities & Fit Statistic & Purpose \\ \hline
+        MapDataset & counts & background, psf, edisp, exposure, & WcsGeom or RegionGeom & ~ & cash & A full 3D analysis with a field of view background \\ \hline
+        MapDatasetOnOff & counts & psf, edisp, exposure & WcsGeom & acceptance, acceptance\_off, counts\_off & wstat & Sky Images with a Ring Background / Background estimation from off observations \\ \hline
+        SpectrumDataset & counts & background, edisp, exposure & RegionGeom & ~ & cash & 1D spectral extraction with the FoV background \\ \hline
+        SpectrumDatasetOnOff & counts & edisp, exposure & RegionGeom & acceptance, acceptance\_off, counts\_off & wstat & 1D spectral extractions using Reflected regions \\ \hline
+        FluxPointsDataset & flux & None & None & ~ & chi2 & Fitting of precomputed flux points \\ \hline
+    \end{tabular}
+    \caption{table:datasets_types}
+\end{table}
+
+Multiple datasets, or the same or different type, can be contained in a Datasets container.
+The Datasets class adds the likelihood from its constituent members to compute the full likelihood for a joint fitting.
+
+The total number of predicted counts for a dataset are computed as the sum of the predicted counts from all source components, plus the expected counts from the residual hadronic background.
+In case of normal datasets, the predicted counts from the hadronic background are computed directly from the model in reconstructed energy and spatial coordinates, whereas for OnOff datasets, the background is estimated from real off counts.
+The predicted counts from a source are obtained by forward folding with the IRFs, assuming that the IRFs are independent of one another.

### 2022-02-07 src/text/2-package-subsections/makers.tex
Add Makers text.

@@
 \todo{Regis Terrier}
-Data reduction
+
+The data reduction contains all tasks required to process and prepare data at the DL3
+level for modeling and fitting. Events are binned and IRFs are interpolated and
+projected onto the chosen analysis geometry. This produces counts, exposure, background, psf
+and energy dispersion maps.
+The {\tt gammapy.makers} sub-package contains the various classes and functions required.
+
+Because the background models suffer from strong uncertainties it is required to correct
+them from the data themselves. Several techniques are commonly used in gamma-ray astronomy
+such as field-of-view background normalization or background measurement in reflected regions 
+regions, see~\cite{test}. Specific {\tt Makers} such as the {\tt FoVBackgroundMaker} or the
+{\tt ReflectedRegionsBackgroundMaker} are in charge of this step.
+
+Finally, to limit other sources of systematic uncertainties, a data validity domain is
+determined by the {\tt SafeMaskMaker}.
 

### 2022-02-07 src/text/2-package-subsections/makers.tex
Add reference to Berge07

@@
 such as field-of-view background normalization or background measurement in reflected regions 
-regions, see~\cite{test}. Specific {\tt Makers} such as the {\tt FoVBackgroundMaker} or the
+regions, see~\cite{Berge07}. Specific {\tt Makers} such as the {\tt FoVBackgroundMaker} or the
 {\tt ReflectedRegionsBackgroundMaker} are in charge of this step.

### 2022-02-07 src/text/2-package-subsections/makers.tex
Modify code snippet

@@
 The data reduction contains all tasks required to process and prepare data at the DL3
-level for modeling and fitting. Events are binned and IRFs are interpolated and
+level for modeling and fitting. The \texttt{gammapy.makers} sub-package contains the various
+classes and functions required to do so.
+First, events are binned and IRFs are interpolated and
 projected onto the chosen analysis geometry. This produces counts, exposure, background, psf
-and energy dispersion maps.
-The {\tt gammapy.makers} sub-package contains the various classes and functions required.
+and energy dispersion maps. The \texttt{MapDatasetMaker} and \texttt{SpectrumDatasetMaker}
+are responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.
 
@@
 such as field-of-view background normalization or background measurement in reflected regions 
-regions, see~\cite{Berge07}. Specific {\tt Makers} such as the {\tt FoVBackgroundMaker} or the
-{\tt ReflectedRegionsBackgroundMaker} are in charge of this step.
+regions, see~\cite{Berge07}. Specific \texttt{Makers} such as the \texttt{FoVBackgroundMaker}
+or the \texttt{ReflectedRegionsBackgroundMaker} are in charge of this step.
 
 Finally, to limit other sources of systematic uncertainties, a data validity domain is
-determined by the {\tt SafeMaskMaker}.
+determined by the \texttt{SafeMaskMaker}. It can be used to limit the extent of the field
+of view used or to limit the energy range to e.g. a domain where the energy reconstruction
+bias is below a given value.
 
@@
 
-	\caption{Using gammapy.data to access DL3 level data}
+	\caption{Using gammapy.makers to reduce DL3 level data into a \texttt{Dataset}.}
 	\label{ig*:minted:gp_makers}

### 2022-02-07 src/code-examples/snippets/gp_makers.py

@@ -1,4 +1,10 @@
-from gammapy.makers import MapDatasetMaker
+from gammapy.makers import MapDatasetMaker, FoVBackgroundMaker, SafeMaskMaker
 
 maker = MapDatasetMaker()
+bkg_maker = FoVBackgroundMaker()
+mask_maker = SafeMaskMaker()
+
 dataset = maker.run(dataset, observation)
+dataset = mask_maker.run(dataset,observation)
+dataset = bkg_maker.run(dataset,observation)
+

### 2022-02-08 src/text/2-package-subsections/datasets.tex

@@
 Corresponding to the different analysis types, five types of datasets are supported in gammapy (\ref{table:datasets_types}).
-3D data cubes (with two spatial and one energy) are represented by MapDatasets, whereas SpectrumDatastes contain binned energy information for a given on region.
+3D data cubes (with two spatial and one energy) are represented by MapDatasets, whereas SpectrumDatasets contain binned energy information for a given on region.
 2D images are a special case of MapDatasets, with only one bin in energy.
@@
 
-\begin{table}[!ht]
+\begin{table*}[!ht]
     \centering
@@
         Dataset Type & Data Type & Reduced IRFs & Geometry & Additional Quantities & Fit Statistic & Purpose \\ \hline
-        MapDataset & counts & background, psf, edisp, exposure, & WcsGeom or RegionGeom & ~ & cash & A full 3D analysis with a field of view background \\ \hline
+        MapDataset & counts & background, psf, edisp, exposure, & WcsGeom or RegionGeom & -- & cash & A full 3D analysis with a field of view background \\ \hline
         MapDatasetOnOff & counts & psf, edisp, exposure & WcsGeom & acceptance, acceptance\_off, counts\_off & wstat & Sky Images with a Ring Background / Background estimation from off observations \\ \hline
-        SpectrumDataset & counts & background, edisp, exposure & RegionGeom & ~ & cash & 1D spectral extraction with the FoV background \\ \hline
+        SpectrumDataset & counts & background, edisp, exposure & RegionGeom & -- & cash & 1D spectral extraction with the FoV background \\ \hline
         SpectrumDatasetOnOff & counts & edisp, exposure & RegionGeom & acceptance, acceptance\_off, counts\_off & wstat & 1D spectral extractions using Reflected regions \\ \hline
-        FluxPointsDataset & flux & None & None & ~ & chi2 & Fitting of precomputed flux points \\ \hline
+        FluxPointsDataset & flux & None & None & -- & chi2 & Fitting of precomputed flux points \\ \hline
     \end{tabular}
-    \caption{table:datasets_types}
-\end{table}
+    \caption{Some caption.}
+    \label{table:datasets_types}
+\end{table*}
 

### 2022-02-11 src/text/2-package-subsections/maps.tex
start drafting

@@
 \todo{Laura Olivera-Nieto}
-The \verb|gammapy.maps| sub-package provides classes for representing pixelized
-data structures with at least two spatial dimensions representing a set of
-coordinates or a region on a sphere. In addition it allows to handle and
-arbitrary number of non-spatial data axes, such as time or energy.
+The \verb|gammapy.maps| sub-package provides classes for representing data structures associated with a set of coordinates or a region on a sphere.
+In addition it allows to handle an arbitrary number of non-spatial data dimensions, such as time or energy.
+It is organized around three types of structures: geometries, sky-maps and map axes, which inherit from the base classes Geom, Map and MapAxis respectively.
 
-It provides a uniform API for WCS, HEALPix and region based data structures.
+The geometry defines the pixelization scheme and map boundaries.
+It also provides methods to transform between sky and pixel coordinates.
+Maps consist of a geometry instance together with a data array containing the corresponding map values.
+Map axes contain a sequence of ordered values which define bins on a given dimension, spatial or not.
+Map axes can have physical units attached to them, as well as non-linear step sizes.
+
+The sub-package provides a uniform API for the FITS World Coordinate System (WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and region-based data structures:
+
+% itemize because it helps me write, could also just be paragraphs...
+\begin{itemize}
+	\item \textbf{WCS: } The FITS WCS pixelization supports a different number of projections to represent celestial spherical coordinates in a regular rectangular grid.
+	\item \textbf{HEALPix: } This pixelization provides a subdivision of a sphere in which each pixel covers the same surface area as every other pixel.
+As a consequence, however, pixel shapes are no longer rectangular, or regular.
+Gammapy provides limited support to HEALPix-based maps, relying in some cases on projections to a WCS grid.
+	\item \textbf{Region geometries: } In this case, instead of a fine spatial grid on a given sky region, the spatial dimension is reduced to a single bin with an arbitrary shape, describing a region in the sky with that same shape.
+Typically they are is used together with a non-spatial dimension, for example an energy axis to represent how a quantity varies with energy on a given region of the sky.
+\end{itemize}
 

### 2022-02-11 src/text/2-package-subsections/maps.tex
add some to-dos

@@
 As a consequence, however, pixel shapes are no longer rectangular, or regular.
-Gammapy provides limited support to HEALPix-based maps, relying in some cases on projections to a WCS grid.
+\gammapy provides limited support to HEALPix-based maps, relying in some cases on projections to a local WCS grid.
 	\item \textbf{Region geometries: } In this case, instead of a fine spatial grid on a given sky region, the spatial dimension is reduced to a single bin with an arbitrary shape, describing a region in the sky with that same shape.
@@
 
-\begin{figure}
-	\import{code-examples/generated/}{gp_maps}
-	\caption{Using gammapy.data to access DL3 level data with a DataStore}
-	\label{codeexample:data}
-\end{figure}
+\todo{Include example of a sky-map? Perhaps also a region map? Although maybe too much.}
+
+\todo{Code examples of what? Making a geom and filling a map? Transforming coordinates? 3D maps? Would be good to have the code example and the plot be related}

### 2022-02-13 src/text/2-package-subsections/estimators.tex
Reformat and code examples

@@
 \todo{Axel Donath}
-Estimators
+The \verb|gammapy.estimators| sub-module features methods to compute
+flux points, light curves, flux maps, flux profiles from data.
+
+The initial fine binning of \verb|MapDataset| is grouped into larger bins.
+
+Internal representation with a reference spectral model and an array of
+normalisation values given in energy, time and spatial bins.
+
+No unfolding.
+
+\begin{itemize}
+	\item Regrouping of dataset bins in time, energy etc.
+	\item Reference spectral model scaled in energy bin
+	\item "Forward folding" / "Backward folding": but there is no difference between the two, backwards folding is forward folding with one bin
+	\item Likelihood profiles
+	\item Uniform N-dimensional data structure
+	\item Uniform API for plotting etc.
+	\item \verb|FluxMaps| and \verb|FluxPoints|
+	\item Serialisation to multiple formats, Astropy's \verb|Table| and \verb|BinnedTimeSeries|
+	\item Additional quantities for debugging, such as predicted counts, fit convergence, sum of fit statistics
+	\item
+\end{itemize}
+
+\begin{figure}
+	\import{code-examples/generated/}{gp_estimators}
+	\caption{Using the TSMapEstimator from gammapy.estimators to compute a sqrt(TS) map.}
+	\label{fig*:minted:gp_estimators}
+\end{figure}

### 2022-02-13 src/text/2-package-subsections/makers.tex

@@
 level for modeling and fitting. The \texttt{gammapy.makers} sub-package contains the various
-classes and functions required to do so.
-First, events are binned and IRFs are interpolated and
+classes and functions required to do so. First, events are binned and IRFs are interpolated and
 projected onto the chosen analysis geometry. This produces counts, exposure, background, psf
@@
 determined by the \texttt{SafeMaskMaker}. It can be used to limit the extent of the field
-of view used or to limit the energy range to e.g. a domain where the energy reconstruction
+of view used or to limit the energy range to e.g., a domain where the energy reconstruction
 bias is below a given value.

### 2022-02-14 src/text/2-package-subsections/modeling.tex
add models and fit text

@@
 \todo{Quentin Remy}
-Models and fitting
+
+gammapy.modeling contains all the functionality related to modeling and fitting data. This includes spectral, spatial and temporal model classes, as well as the fit and parameter API.
+
+\subsection{Models}
+\label{ssec:models}
+
+The models are grouped into the following categories:
+\begin{itemize}
+\item SpectralModel: models to describe spectral shapes of sources
+\item SpatialModel: models to describe spatial shapes (morphologies) of sources
+\item TemporalModel: models to describe temporal flux evolution of sources, such as light and phase curves
+\end{itemize}
+The models follow a naming scheme which contains the category as a suffix to the class name.
+
+The  Spectral Models include a special class of Normed models, which have a dimension-less normalisation.
+These spectral models feature a norm parameter instead of amplitude and are named using the NormSpectralModel suffix.
+They must be used along with another spectral model, as a multiplicative correction factor according to their spectral shape.
+They can be typically used for adjusting template based models, or adding a EBL correction to some analytic model.
+The analytic Spatial models are all normalized such as they integrate to unity over the sky but the template Spatial models may not, so in that special case they have to be combined with a NormSpectralModel.
+
+The SkyModel is a factorised model that combine the spectral, spatial and temporal model components (by default the spatial and temporal components are optional).
+SkyModel objects represents additive emission components, usually sources or diffuse emission, although a single source can also be modeled by multiple components.
+To handle list of multiple SkyModel components, Gammapy has a Models class.
+
+The model gallery provides a visual overview of the available models in Gammapy.
+Most of the analytic models  commonly used in gamma-ray astronomy are built-in.
+We also offer a wrapper to radiative models implemented in the Naima package \cite{naima}.
+The modeling framework can be easily extended with user-defined models.
+For example agnpy \citep{cosimo_nigro_2021_5762147} models that describe leptonic radiative processes in jetted Active Galactic Nuclei (AGN) can wrapped into gammapy \footnote{as shown in the following tutorial \url{ https://agnpy.readthedocs.io/en/latest/tutorials/ec_dt_gammapy_fit.html}}.
 
@@
 \end{figure}
+
+\subsection{Fit}
+\label{ssec:fit}
+
+The Fit class provides methods to fit, i.e.
+optimise parameters and estimate parameter errors and correlations.
+It interfaces with a Datasets object, which in turn is connected to a Models object containing the model parameters in its Parameters object.
+Models can be unique for a given dataset, or contribute to multiple datasets and thus provide links, allowing e.g.
+to do a joint fit to multiple IACT datasets, or to a joint IACT and \textit{Fermi}-LAT dataset.
+Many examples are given in the tutorials.
+
+The fit class provides a uniform interface to multiple fitting backends: “minuit” \citep{iminuit}, “scipy”, \citep{2020SciPy-NMeth}, and “sherpa” \citep{sherpa-2005,sherpa-2011}, .
+Note that, for now, covaraince matrix and errors are computed only for the fitting with MINUIT.
+However depending on the problem other optimizers can better perform, so sometimes it can be useful to run a pre-fit with alternative optimization methods.
+
+For the “minuit” backend see https://iminuit.readthedocs.io/en/latest/reference.html for a detailed description of the available options.
+For the “scipy” backend the available options are described in detail here:
+\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.optimize.minimize.html}
+For the “sherpa” backend you can choose the optimization algorithm between “simplex”, “levmar”, “moncar”, “gridsearch”.
+Those methods are described and compared on \url{http://cxc.cfa.harvard.edu/sherpa/methods/index.html}.
+The available options of the optimization methods are further described on the following page\url{https://cxc.cfa.harvard.edu/sherpa/methods/opt_methods.html}.
+
+In future we plan to extend the supported Fit backend including for example MCMC solutions.
+\footnote{a prototype is available in gammapy-recipes, \url(https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html)}
+%the sampling code should be moved to the recipe (for now it is imported) because it have been removed from the core package.

### 2022-02-14 src/text/2-package-subsections/data.tex
added preliminary subsection for gammapy.data

@@
 \todo{Cosimo Nigro}
-The \verb|gammapy.data| sub-package provides access to DL3 level data and
-observation handling.
+
+As illustrated in Fig.~\ref{fig:data_flow}, the \verb|gammapy.data| sub-package
+implements the lowest data level, providing the input interface to gamma-ray data.
+The \gammapy data model follows the \gadf specifications (Sec.~\ref{sec:introduction}),
+therefore gamma-ray data compliant with those can be directly read with the package. 
+Version X.X of the \gadf specification is supported in this release version.
+As both the \gadf data model and \gammapy were initially conceived for \iact
+data analysis, input data are typically grouped in \texttt{Observations}, corresponding
+to stable periods of data aquisitions (typically $20 - 30\,{\rm min}$).
+A \texttt{DataStore} object, gathering a collection of observations, can be created
+porviding ancillary files containing information about the telescope observation
+mode and the content of the data unit of each file. The \texttt{DataStore} allows
+for selecting a list of observations based on specific filters.
+As an illustrative example, Fig.~\ref{fig*:minted:gp_data} shows
+how to create a \texttt{datastore} and how to obtain the observations corresponding
+to given identification numbers (IDs).
+
+The so-called DL3 files represented by the \texttt{Observation} class consist of
+two types of elements: a list of gamma-ray events with relevant physical quantities
+for the successive analysis (estimated energy, direction and arrival times) that
+is handled by the \texttt{EventList} class and an instrument response function (IRF),
+providing the response of the system, typically factorised in independent components
+(see the description in Sec.~\ref{ssec:gammapy-irf}).
+The separate handling of event lists and IRFs additionally allows for data from
+other gamma-ray instruments to be read. For example, to read \fermi data, the
+user can read separately their event list (already compliant with the \gadf
+specifications) and then find the appropriate IRF class representing the response
+functions provided by \fermi, see Sec.~\ref{ssec:fermi}.
 

### 2022-02-14 src/text/1-introduction.tex
added preliminary GADF paragraph in the intro and corresponding references

@@
 
-The Cherenkov Telescope Array will be operated as an open observatory for the
+The Cherenkov Telescope Array (CTA) will be operated as an open observatory for the
 first time. Thus there is a need for open analysis software as well.
 
-Once the primary photons are reconstructed the format of the data of all
-Gamma-ray instrumets can be brought into a common format. An effort is the
-gamma-astro data formats~\cite{gadf-zenodo}. The data format is based on FITS
-\citep{fits}.
+Moreover, the operation of CTA as an observatory introduces the necessity of sharing
+its data publicly. The data-reduction workflow of different IACTs of the current
+generation is remarkably similar, resulting in a ``high'' data level that can be
+finally used to derive scientific results (e.g. spectra, sky maps, light curves).
+The information in this high data level is independent on the data reduction,
+and eventually of the detection technique. This implies, for example, that data
+from IACT and WCD can be represented within the same model.
+The efforts to prototype the future CTA data model and to convert current IACT
+data in a format usable with the newly-available science tools converged in the 
+so-called ``Data Format for Gamma-ray Astronomy'' initiative
+\citep{gadf_proc, gadf_universe}, abbreviated in \texttt{gamma-astro-data-format}
+(GADF). The latter proposes prototypical specifications to produce files based
+on the flexible image transport system (FITS) format \citep{fits} encapsulating
+this high-level information. This is realized by storing a list of gamma-like
+events with their measured quantites (energy, direction, arrival time) and a
+parametrisation of the response of the system (see Sec.~\ref{ssec:gammapy-data}
+and Sec.~\ref{ssec:gammapy-irf} for more information).
 

### 2022-02-14 src/text/2-package-subsections/modeling.tex
adapt reference to agnpy

@@
 The modeling framework can be easily extended with user-defined models.
-For example agnpy \citep{cosimo_nigro_2021_5762147} models that describe leptonic radiative processes in jetted Active Galactic Nuclei (AGN) can wrapped into gammapy \footnote{as shown in the following tutorial \url{ https://agnpy.readthedocs.io/en/latest/tutorials/ec_dt_gammapy_fit.html}}.
+For example agnpy models that describe leptonic radiative processes in jetted Active Galactic Nuclei (AGN) can wrapped into gammapy \citep[see section3.5 of ][]{2021arXiv211214573N} .
 

### 2022-02-14 src/figures/fermi_ts_map.py
Adapt Fermi figure script

@@ -13,6 +13,7 @@ from gammapy.modeling.models import (
 from gammapy.irf import PSFMap, EDispKernelMap
 from astropy.coordinates import SkyCoord
 import astropy.units as u
+from astropy.io import fits
 import numpy as np
 import config
 
@@ -20,98 +21,56 @@ logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 
 
-def read_dataset():
-    path = Path(__file__).parent.parent / "data/fermi-ts-map/input"
-    counts = Map.read(path / "fermi-3fhl-gc-counts-cube.fits.gz")
-    background = Map.read(path / "fermi-3fhl-gc-background-cube.fits.gz")
-    exposure = Map.read(path / "fermi-3fhl-gc-exposure-cube.fits.gz")
-    psfmap = PSFMap.read(path / "fermi-3fhl-gc-psf-cube.fits.gz", format="gtpsf")
-
-    edisp = EDispKernelMap.from_diagonal_response(
-        energy_axis=counts.geom.axes["energy"],
-        energy_axis_true=exposure.geom.axes["energy_true"],
-    )
-
-    return MapDataset(
-		counts=counts,
-		background=background,
-		exposure=exposure,
-		psf=psfmap,
-		name="fermi-3fhl-gc",
-		edisp=edisp,
-	)
-
-
-def estimate_ts_map(dataset):
-	spatial_model = PointSpatialModel()
-
-	# We choose units consistent with the map units here...
-	spectral_model = PowerLawSpectralModel(amplitude="1e-22 cm-2 s-1 keV-1", index=2)
-	model = SkyModel(spatial_model=spatial_model, spectral_model=spectral_model)
-
-	estimator = TSMapEstimator(
-		model,
-		kernel_width="3 deg",
-		energy_edges=[10, 50, 2000] * u.GeV,
-		n_jobs=4
-	)
-	return estimator.run(dataset)
-
-
 def plot_sqrt_ts_maps(maps):
-	figsize = config.FigureSizeAA(aspect_ratio=3, width_aa="two-column")
-	fig = plt.figure(figsize=figsize.inch)
+    figsize = config.FigureSizeAA(aspect_ratio=3, width_aa="two-column")
[…]

### 2022-02-14 src/figures/fermi_ts_map.py
Remove unused imports

@@ -1,20 +1,9 @@
 from pathlib import Path
 import logging
 import matplotlib.pyplot as plt
-import matplotlib.cm as cm
-from gammapy.maps import Map
-from gammapy.estimators import TSMapEstimator, FluxMaps
-from gammapy.datasets import MapDataset
-from gammapy.modeling.models import (
-    SkyModel,
-    PowerLawSpectralModel,
-    PointSpatialModel,
-)
-from gammapy.irf import PSFMap, EDispKernelMap
-from astropy.coordinates import SkyCoord
+from gammapy.estimators import FluxMaps
 import astropy.units as u
 from astropy.io import fits
-import numpy as np
 import config
 
 logging.basicConfig(level=logging.INFO)
@@ -70,7 +59,9 @@ def plot_sqrt_ts_maps(maps):
 
 
 if __name__ == "__main__":
-    hdulist = fits.open("../data/fermi-ts-map/fermi-ts-maps.fits")
+    filename = Path("../data/fermi-ts-map/") / "fermi-ts-maps.fits"
+    log.info(f"Reading {filename}")
+    hdulist = fits.open(filename)
     hdulist[0].header["MODEL"] = "../data/fermi-ts-map/fermi-ts-maps.fits_model.yaml"
     maps = FluxMaps.from_hdulist(hdulist=hdulist)
     plot_sqrt_ts_maps(maps=maps)

### 2022-02-14 scripts/download.py
Add more logging

@@ -1,6 +1,10 @@
+import logging
 import click
 from pathlib import Path
 from gammapy.scripts.download import progress_download
+
+log = logging.getLogger(__name__)
+logging.basicConfig(level=logging.DEBUG)
 
 BASE_URL = "https://github.com/gammapy/gammapy-data/raw/master/"
 PATH = Path(__file__).parent.parent
@@ -22,6 +26,7 @@ def download_fermi_data():
     for filename in FILENAMES:
         destination = fermi_path / filename
         source = BASE_URL + "fermi-3fhl-gc/" + filename
+        log.info(f"Downloading {source}")
         progress_download(source, destination)
 
 

### 2022-02-14 scripts/download.py
Adpat filenames and fix cta data download

@@ -4,26 +4,47 @@ from pathlib import Path
 from gammapy.scripts.download import progress_download
 
 log = logging.getLogger(__name__)
-logging.basicConfig(level=logging.DEBUG)
+logging.basicConfig(level=logging.INFO)
 
 BASE_URL = "https://github.com/gammapy/gammapy-data/raw/master/"
 PATH = Path(__file__).parent.parent
 PATH_DATA = PATH / "src/data"
 
 
-FILENAMES = [
+FILENAMES_FERMI = [
     "fermi-3fhl-gc-counts-cube.fits.gz",
     "fermi-3fhl-gc-background-cube.fits.gz",
     "fermi-3fhl-gc-exposure-cube.fits.gz",
     "fermi-3fhl-gc-psf-cube.fits.gz",
 ]
 
+FILENAMES_CTA = [
+    "index/gps/hdu-index.fits.gz",
+    "index/gps/obs-index.fits.gz",
+    "data/baseline/gps/gps_baseline_110380.fits",
+    "data/baseline/gps/gps_baseline_111140.fits",
+    "data/baseline/gps/gps_baseline_111159.fits",
+    "caldb/data/cta/1dc/bcf/South_z20_50h/irf_file.fits",
+]
+
+
+def download_cta_data():
+    cta_path = PATH_DATA / f"cta-galactic-center/input"
+    cta_path.mkdir(exist_ok=True, parents=True)
+
+    for filename in FILENAMES_CTA:
+        destination = cta_path / filename
+        destination.parent.mkdir(exist_ok=True, parents=True)
+        source = BASE_URL + "cta-1dc/" + filename
+        log.info(f"Downloading {source}")
+        progress_download(source, destination)
+
 
 def download_fermi_data():
     fermi_path = PATH_DATA / f"fermi-ts-map/input"
     fermi_path.mkdir(exist_ok=True, parents=True)
 
-    for filename in FILENAMES:
+    for filename in FILENAMES_FERMI:
         destination = fermi_path / filename
         source = BASE_URL + "fermi-3fhl-gc/" + filename
         log.info(f"Downloading {source}")
@@ -32,6 +53,7 @@ def download_fermi_data():
 
 DATASETS_REGISTRY = {
     "fermi-gc": download_fermi_data,
+    "cta-1dc": download_cta_data,
 }
 
 

### 2022-02-14 src/figures/cta_galactic_center.py

@@ -50,95 +50,6 @@ GEOM = WcsGeom.create(
 )
 
 
-def get_observations():
-    # Select observations
-    data_store = DataStore.from_dir("$GAMMAPY_DATA/cta-1dc/index/gps")
-    obs_id = [110380, 111140, 111159]
-    return data_store.get_observations(obs_id)
-
-
-def make_counts_image(observations):
-    # Define map geometry
-    stacked = MapDataset.create(geom=GEOM)
-    maker = MapDatasetMaker(selection=["counts"])
-    maker_safe_mask = SafeMaskMaker(methods=["offset-max"], offset_max=2.5 * u.deg)
-
-    for obs in observations:
-        cutout = stacked.cutout(obs.pointing_radec, width="5 deg")
-        dataset = maker.run(cutout, obs)
-        dataset = maker_safe_mask.run(dataset, obs)
-        stacked.stack(dataset)
-
-    return stacked.counts
-
-
-def make_datasets_spectral(observations):
-    target_position = SkyCoord(0, 0, unit="deg", frame="galactic")
-    on_radius = 0.2 * u.deg
-    on_region = CircleSkyRegion(center=target_position, radius=on_radius)
-
-    exclusion_mask = GEOM.to_image().region_mask([on_region], inside=False)
-
-    energy_axis = MapAxis.from_energy_bounds(
-        0.1, 40, 40, unit="TeV", name="energy"
-    )
-    energy_axis_true = MapAxis.from_energy_bounds(
-        0.05, 100, 200, unit="TeV", name="energy_true"
-    )
-
-    geom = RegionGeom.create(region=on_region, axes=[energy_axis])
-    dataset_empty = SpectrumDataset.create(
-        geom=geom, energy_axis_true=energy_axis_true
-    )
-
-    dataset_maker = SpectrumDatasetMaker(
-        containment_correction=False, selection=["counts", "exposure", "edisp"]
-    )
-    bkg_maker = ReflectedRegionsBackgroundMaker(exclusion_mask=exclusion_mask)
-    safe_mask_masker = SafeMaskMaker(methods=["aeff-max"], aeff_percent=10)
-
-    datasets = Datasets()
-
-    for observation in observations:
-        dataset = dataset_maker.run(
-            dataset_empty.copy(name=f"obs-{observation.obs_id}"), observation
-        )
-        dataset_on_off = bkg_maker.run(dataset, observation)
-        dataset_on_off = safe_mask_masker.run(dataset_on_off, observation)
[…]

### 2022-02-14 src/data/cta-galactic-center/make.py
Add cta dta make script

@@ -1,0 +1,161 @@
+#!/usr/bin/env python
+import logging
+from pathlib import Path
+import matplotlib.pyplot as plt
+import numpy as np
+import astropy.units as u
+from astropy.coordinates import SkyCoord
+from astropy.convolution import Gaussian2DKernel
+from astropy.visualization import simple_norm
+from regions import CircleSkyRegion
+from gammapy.modeling import Fit
+from gammapy.data import DataStore
+from gammapy.datasets import (
+    Datasets,
+    FluxPointsDataset,
+    SpectrumDataset,
+    MapDataset,
+)
+from gammapy.modeling.models import (
+    PowerLawSpectralModel,
+    SkyModel,
+    GaussianSpatialModel,
+)
+from gammapy.maps import MapAxis, WcsNDMap, WcsGeom, RegionGeom, Map
+from gammapy.makers import (
+    MapDatasetMaker,
+    SafeMaskMaker,
+    SpectrumDatasetMaker,
+    ReflectedRegionsBackgroundMaker,
+)
+from gammapy.estimators import FluxPointsEstimator, FluxPoints
+
+
+logging.basicConfig()
+log = logging.getLogger(__name__)
+log.setLevel(logging.INFO)
+
+ENERGY_AXIS = MapAxis.from_edges(
+    np.logspace(-1.0, 1.0, 10), unit="TeV", name="energy", interp="log"
+)
+
+GEOM = WcsGeom.create(
+    skydir=(0, 0), npix=(500, 400), binsz=0.02, frame="galactic", axes=[ENERGY_AXIS.squash()]
+)
+
+
+def get_observations():
+    # Select observations
+    data_store = DataStore.from_dir("input/index/gps")
+    obs_id = [110380, 111140, 111159]
+    return data_store.get_observations(obs_id)
+
+
+def make_counts_image(observations):
+    # Define map geometry
+    stacked = MapDataset.create(geom=GEOM)
+    maker = MapDatasetMaker(selection=["counts"])
+    maker_safe_mask = SafeMaskMaker(methods=["offset-max"], offset_max=2.5 * u.deg)
+
+    for obs in observations:
+        cutout = stacked.cutout(obs.pointing_radec, width="5 deg")
+        dataset = maker.run(cutout, obs)
+        dataset = maker_safe_mask.run(dataset, obs)
+        stacked.stack(dataset)
+
+    return stacked.counts
+
+
+def make_datasets_spectral(observations):
+    target_position = SkyCoord(0, 0, unit="deg", frame="galactic")
[…]

### 2022-02-14 src/data/cta-galactic-center/make.py
Remove unused imports

@@ -1,34 +1,29 @@
 #!/usr/bin/env python
 import logging
 from pathlib import Path
-import matplotlib.pyplot as plt
 import numpy as np
 import astropy.units as u
 from astropy.coordinates import SkyCoord
-from astropy.convolution import Gaussian2DKernel
-from astropy.visualization import simple_norm
 from regions import CircleSkyRegion
 from gammapy.modeling import Fit
 from gammapy.data import DataStore
 from gammapy.datasets import (
     Datasets,
-    FluxPointsDataset,
     SpectrumDataset,
     MapDataset,
 )
 from gammapy.modeling.models import (
     PowerLawSpectralModel,
     SkyModel,
-    GaussianSpatialModel,
 )
-from gammapy.maps import MapAxis, WcsNDMap, WcsGeom, RegionGeom, Map
+from gammapy.maps import MapAxis, WcsGeom, RegionGeom
 from gammapy.makers import (
     MapDatasetMaker,
     SafeMaskMaker,
     SpectrumDatasetMaker,
     ReflectedRegionsBackgroundMaker,
 )
-from gammapy.estimators import FluxPointsEstimator, FluxPoints
+from gammapy.estimators import FluxPointsEstimator
 
 
 logging.basicConfig()

### 2022-02-14 src/figures/cta_galactic_center.py

@@ -1,58 +1,21 @@
-#!/usr/bin/env python
-# coding: utf-8
+import logging
 from pathlib import Path
 import matplotlib.pyplot as plt
-import numpy as np
-import astropy.units as u
-from astropy.coordinates import SkyCoord
-from astropy.convolution import Gaussian2DKernel
 from astropy.visualization import simple_norm
-from regions import CircleSkyRegion
-from gammapy.modeling import Fit
-from gammapy.data import DataStore
-from gammapy.datasets import (
-    Datasets,
-    FluxPointsDataset,
-    SpectrumDataset,
-    MapDataset,
-)
-from gammapy.modeling.models import (
-    PowerLawSpectralModel,
-    SkyModel,
-    GaussianSpatialModel,
-)
-from gammapy.maps import MapAxis, WcsNDMap, WcsGeom, RegionGeom, Map
-from gammapy.makers import (
-    MapDatasetMaker,
-    SafeMaskMaker,
-    SpectrumDatasetMaker,
-    ReflectedRegionsBackgroundMaker,
-)
-from gammapy.estimators import TSMapEstimator, FluxPointsEstimator, FluxPoints
-from gammapy.estimators.utils import find_peaks
+from gammapy.datasets import Datasets
+from gammapy.maps import Map
+from gammapy.estimators import FluxPoints
 from gammapy.visualization import plot_spectrum_datasets_off_regions
 import config
 
-# Configure the logger, so that the spectral analysis
-# isn't so chatty about what it's doing.
-import logging
-
-logging.basicConfig()
+logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
-log.setLevel(logging.INFO)
-
-ENERGY_AXIS = MapAxis.from_edges(
-    np.logspace(-1.0, 1.0, 10), unit="TeV", name="energy", interp="log"
-)
-
-GEOM = WcsGeom.create(
-    skydir=(0, 0), npix=(500, 400), binsz=0.02, frame="galactic", axes=[ENERGY_AXIS.squash()]
-)
 
 
 def plot_spectrum_and_image():
-    counts = Map.read("../data/cta-galactic-center/stacked-counts.fits")
-    datasets = Datasets.read("../data/cta-galactic-center/datasets/datasets.yaml")
+    path = Path("../data/cta-galactic-center/")
+    counts = Map.read(path / "stacked-counts.fits")
[…]

### 2022-02-18 src/text/3-applications.tex
Adapt tex files
Reformat tex files
Minor formatting improvements

@@
 \section{Applications}
-\label{sec:apps}
+\label{sec:applications}
 
-Each application example is a notebook in the online material: We could have one
-analysis as Python scripts instead of notebook in the online material. At the
-start of this section, point to gammapy-paper repo on Github and say that
+Each application example is a notebook in the online material: We could have
+one analysis as Python scripts instead of notebook in the online material. At
+the start of this section, point to gammapy-paper repo on Github and say that
 there’s a Binder where people can try the examples online.
@@
 \subsection{Source detection}
-\label{apps:detect}
+\label{ssec:source-detection}
 
-See Figure~\ref{fig:fermi-ts-image}.
+See Figure~\ref{fig:fermi_ts_map}.
 
-Ref: \citep{Stewart2009}
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=1.\textwidth]{figures/gammapy-fermi-ts-image}
-\caption{
-Gammapy application example: A \textit{Fermi} survey TS map of the inner
-Galactic plane region.
-}
-\label{fig:fermi-ts-image}
-\end{figure*}
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=0.8\textwidth]{figures/gammapy-cube-analysis}
-\caption{
-Gammapy data model illustration. Binned analysis of lon-lat-energy cube data is
-supported via joint likelihood analysis of one image per energy bin.
-On-off-region based spectral analysis is supported as well.
-}
-\label{fig:data-model}
-\end{figure*}
+Ref:~\citep{Stewart2009}
 
 \subsection{Multi instrument analysis}
+\label{ssec:multi-instrument-analysis}

### 2022-02-21 src/text/2-package-subsections/datasets.tex
Reformat and code examples
write datasets api

--- 2022-01-31 src/text/2-package-subsections/datasets.tex
@@
 \todo{Atreyee Sinha}
-DL4 level data
+
+The end product of the data reduction process described in \ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps, at the DL4 level.
+The gammapy.datasets subpackage contains classes to bundle together binned data along with associated models and the likelihood, which provides an interface to the Fit class \ref{ssec:gammapy-modeling} for modeling and fitting purposes.
+Figure \ref{fig*:minted:gp_datasets} Depending upon the type of analysis (3D or only spectral), and the associated statistics (Cash, wstat or chi2), different types of Datasets are supported.
+The predicted counts are computed by convolution of the models with the associate IRFs.
+Fitting of precomputed flux points is enabled through FluxPointsDatasets.
+Multiple datasets of same or different types can be  bundled together in Datasets, where the likelihood from each constituent member is added, thus facilitating joint fitting across different observations, and even different instruments across different wavelengths.
+Datasets also provide functionalities for manipulating reduced data, eg: stacking, sub-grouping, plotting, etc.
+Users can also create their customized datasets for implementing modified likelihood methods.
 
 \begin{figure}
-
 	\import{code-examples/generated/}{gp_datasets}
-	\caption{Using gammapy.data to access DL3 level data with a DataStore}
+	\caption{Using gammapy.datasets for modelling and fitting}
 	\label{fig*:minted:gp_datasets}

### 2022-02-21 src/code-examples/snippets/gp_datasets.py

@@ -1,12 +1,10 @@
-from astropy.coordinates import SkyCoord
-from gammapy.maps import WcsGeom
 from gammapy.datasets import MapDataset
+from gammapy.modeling.models import SkyModel, PowerLawSpectralModel, PointSpatialModel
+from gammapy.modeling import Fit
+dataset = MapDataset.read("$GAMMAPY_DATA/cta-1dc-gc/cta-1dc-gc.fits.gz", name="cta_dataset")
+pwl = PowerLawSpectralModel()
+point = PointSpatialModel()
+model = SkyModel( spectral_model=pwl,spatial_model=point,name=”my-model”)
+fit = Fit()
+result = fit.run(datasets=[datasets])
 
-skydir = SkyCoord("0d", "0d")
-geom = WcsGeom.create(
-	skydir=skydir, width="5 deg", binsz="0.2 deg"
-)
-
-dataset = MapDataset.create(
-	geom=geom, name="my-dataset"
-)

### 2022-02-21 src/text/2-package-subsections/datasets.tex
adapt example

@@
 
-The end product of the data reduction process described in \ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps, at the DL4 level.
-The gammapy.datasets subpackage contains classes to bundle together binned data along with associated models and the likelihood, which provides an interface to the Fit class \ref{ssec:gammapy-modeling} for modeling and fitting purposes.
-Figure \ref{fig*:minted:gp_datasets} Depending upon the type of analysis (3D or only spectral), and the associated statistics (Cash, wstat or chi2), different types of Datasets are supported.
+The end product of the data reduction process described in Section \ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps, at the DL4 level.
+The gammapy.datasets subpackage contains classes to bundle together binned data along with associated models and the likelihood, which provides an interface to the Fit class (Sec \ref{ssec:gammapy-modeling}) for modeling and fitting purposes.
+Depending upon the type of analysis (spectral and morphological, or only spectral), and the associated statistics (Cash, wstat or chi2), different types of Datasets are supported.
 The predicted counts are computed by convolution of the models with the associate IRFs.
 Fitting of precomputed flux points is enabled through FluxPointsDatasets.
-Multiple datasets of same or different types can be  bundled together in Datasets, where the likelihood from each constituent member is added, thus facilitating joint fitting across different observations, and even different instruments across different wavelengths.
+Multiple datasets of same or different types can be  bundled together in Datasets (e.g.: Figure \ref{fig*:minted:gp_datasets}), where the likelihood from each constituent member is added, thus facilitating joint fitting across different observations, and even different instruments across different wavelengths.
 Datasets also provide functionalities for manipulating reduced data, eg: stacking, sub-grouping, plotting, etc.
@@
 	\import{code-examples/generated/}{gp_datasets}
-	\caption{Using gammapy.datasets for modelling and fitting}
+	\caption{A Datasets container with FluxPointsDataset and MapDataset}
 	\label{fig*:minted:gp_datasets}

### 2022-02-21 src/code-examples/snippets/gp_datasets.py

@@ -1,10 +1,11 @@
-from gammapy.datasets import MapDataset
-from gammapy.modeling.models import SkyModel, PowerLawSpectralModel, PointSpatialModel
-from gammapy.modeling import Fit
-dataset = MapDataset.read("$GAMMAPY_DATA/cta-1dc-gc/cta-1dc-gc.fits.gz", name="cta_dataset")
-pwl = PowerLawSpectralModel()
-point = PointSpatialModel()
-model = SkyModel( spectral_model=pwl,spatial_model=point,name=”my-model”)
-fit = Fit()
-result = fit.run(datasets=[datasets])
+from gammapy.datasets import MapDataset, FluxPointsDataset, Datasets
 
+dataset1 = MapDataset.read(
+    "$GAMMAPY_DATA/cta-1dc-gc/cta-1dc-gc.fits.gz", name="map_dataset"
+)
+dataset2 = FluxPointsDataset.read(
+    "$GAMMAPY_DATA/tests/spectrum/flux_points/diff_flux_points.fits",
+    name="fluxpoints_dataset",
+)
+datasets = Datasets([dataset1, dataset2])
+print(datasets)

### 2022-02-22 scripts/download.py
add lightcurve plot

@@ -27,6 +27,24 @@ FILENAMES_CTA = [
     "caldb/data/cta/1dc/bcf/South_z20_50h/irf_file.fits",
 ]
 
+OBS_IDS_PKS2155 = [
+    "33787",
+    "33788",
+    "33789",
+    "33790",
+    "33791",
+    "33792",
+    "33793",
+    "33794",
+    "33795",
+    "33796",
+    "33797",
+    "33798",
+    "33799",
+    "33800",
+    "33801",
+]
+
 
 def download_cta_data():
     cta_path = PATH_DATA / f"cta-galactic-center/input"
@@ -51,9 +69,27 @@ def download_fermi_data():
         progress_download(source, destination)
 
 
+def download_hess_pks2155_data():
+    pks_path = PATH_DATA / f"lightcurve/input"
+    pks_path.mkdir(exist_ok=True, parents=True)
+
+    FILENAMES_PKS2155 = ["obs-index.fits.gz", "hdu-index.fits.gz"]
+    for obs_id in OBS_IDS_PKS2155:
+        filename = "data/hess_dl3_dr1_obs_id_0" + obs_id + ".fits.gz"
+        FILENAMES_PKS2155.append(filename)
+
+    for filename in FILENAMES_PKS2155:
+        destination = pks_path / filename
+        destination.parent.mkdir(exist_ok=True, parents=True)
+        source = BASE_URL + "hess-dl3-dr1/" + filename
+        log.info(f"Downloading {source}")
+        progress_download(source, destination)
+
+
 DATASETS_REGISTRY = {
     "fermi-gc": download_fermi_data,
     "cta-1dc": download_cta_data,
+    "pks-flare": download_hess_pks2155_data(),
 }
 
 

### 2022-02-22 src/data/lightcurve/make.py

@@ -1,0 +1,103 @@
+import astropy.units as u
+import numpy as np
+from astropy.coordinates import SkyCoord
+from astropy.time import Time
+from regions import CircleSkyRegion
+from astropy.coordinates import Angle
+from gammapy.data import DataStore
+from gammapy.datasets import SpectrumDataset, Datasets
+from gammapy.modeling.models import PowerLawSpectralModel, SkyModel
+from gammapy.maps import MapAxis, RegionGeom
+from gammapy.estimators import LightCurveEstimator
+from gammapy.makers import (
+    SpectrumDatasetMaker,
+    ReflectedRegionsBackgroundMaker,
+    SafeMaskMaker,
+)
+logging.basicConfig(level=logging.INFO)
+log = logging.getLogger(__name__)
+
+def get_observations():
+    data_store = DataStore.from_dir("data/")
+    obs_table = data_store.obs_table
+    obs_table_seclected = obs_table[obs_table["TARGET_TAG"]=="pks2155_flare"]
+    obs_ids = obs_table_seclected["OBS_ID"]
+    observations = data_store.get_observations(obs_ids)
+    return observations
+
+def split_observations(observations):
+    t0 = Time("2006-07-29T20:30")
+    duration = 10 * u.min
+    n_time_bins = 35
+    times = t0 + np.arange(n_time_bins) * duration
+    time_intervals = [
+        Time([tstart, tstop]) for tstart, tstop in zip(times[:-1], times[1:])
+    ]
+    short_observations = observations.select_time(time_intervals)
+    return time_intervals, short_observations
+
+
+def data_reduction(short_observations):
+    energy_axis = MapAxis.from_energy_bounds("0.4 TeV", "20 TeV", nbin=10)
+    energy_axis_true = MapAxis.from_energy_bounds(
+        "0.1 TeV", "40 TeV", nbin=20, name="energy_true"
+    )
+
+    target_position = target_position = SkyCoord(
+        329.71693826 * u.deg, -30.2255890 * u.deg, frame="icrs"
+    )
+    on_region_radius = Angle("0.11 deg")
+    on_region = CircleSkyRegion(center=target_position, radius=on_region_radius)
+
+    geom = RegionGeom.create(region=on_region, axes=[energy_axis])
+    dataset_maker = SpectrumDatasetMaker(
+        containment_correction=True, selection=["counts", "exposure", "edisp"]
+    )
[…]

### 2022-02-22 src/figures/lightcurve.py

@@ -1,0 +1,22 @@
+import logging
+from pathlib import Path
+import matplotlib.pyplot as plt
+from gammapy.estimators import FluxPoints
+
+
+logging.basicConfig(level=logging.INFO)
+log = logging.getLogger(__name__)
+
+
+def plot_lightcurve():
+    path = Path(".")
+    filename = path / "pks2155_flare_lc.fits.gz"
+    lc = FluxPoints.read(filename, sed_type="lightcurve")
+    lc.plot(sed_type="eflux", axis_name="time")
+    filename = "lghtcurve-pks.pdf"
+    log.info(f"Writing {filename}")
+    plt.savefig(filename, dpi=300)
+
+
+if __name__ == "__main__":
+    plot_lightcurve()

### 2022-02-22 scripts/download.py
Integrate lightcurve in snakemake workflow

@@ -45,6 +45,8 @@ OBS_IDS_PKS2155 = [
     "33801",
 ]
 
+FILENAMES_PKS2155 = ["obs-index.fits.gz", "hdu-index.fits.gz"]
+
 
 def download_cta_data():
     cta_path = PATH_DATA / f"cta-galactic-center/input"
@@ -73,7 +75,6 @@ def download_hess_pks2155_data():
     pks_path = PATH_DATA / f"lightcurve/input"
     pks_path.mkdir(exist_ok=True, parents=True)
 
-    FILENAMES_PKS2155 = ["obs-index.fits.gz", "hdu-index.fits.gz"]
     for obs_id in OBS_IDS_PKS2155:
         filename = "data/hess_dl3_dr1_obs_id_0" + obs_id + ".fits.gz"
         FILENAMES_PKS2155.append(filename)
@@ -89,7 +90,7 @@ def download_hess_pks2155_data():
 DATASETS_REGISTRY = {
     "fermi-gc": download_fermi_data,
     "cta-1dc": download_cta_data,
-    "pks-flare": download_hess_pks2155_data(),
+    "pks-flare": download_hess_pks2155_data,
 }
 
 

### 2022-02-22 src/data/lightcurve/make.py

@@ -1,3 +1,5 @@
+import logging
+from pathlib import Path
 import astropy.units as u
 import numpy as np
 from astropy.coordinates import SkyCoord
@@ -17,13 +19,15 @@ from gammapy.makers import (
 logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 
+
 def get_observations():
-    data_store = DataStore.from_dir("data/")
+    data_store = DataStore.from_dir("input/")
     obs_table = data_store.obs_table
-    obs_table_seclected = obs_table[obs_table["TARGET_TAG"]=="pks2155_flare"]
+    obs_table_seclected = obs_table[obs_table["TARGET_TAG"] == "pks2155_flare"]
     obs_ids = obs_table_seclected["OBS_ID"]
     observations = data_store.get_observations(obs_ids)
     return observations
+
 
 def split_observations(observations):
     t0 = Time("2006-07-29T20:30")
@@ -69,6 +73,7 @@ def data_reduction(short_observations):
         dataset_on_off = safe_mask_masker.run(dataset_on_off, obs)
         datasets.append(dataset_on_off)
     return datasets
+
 
 def light_curve(datasets, time_intervals):
     spectral_model = PowerLawSpectralModel(

### 2022-02-22 src/figures/hess_lightcurve_pks.py

@@ -2,18 +2,23 @@ import logging
 from pathlib import Path
 import matplotlib.pyplot as plt
 from gammapy.estimators import FluxPoints
-
+import config
 
 logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 
 
 def plot_lightcurve():
-    path = Path(".")
+    figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
+    fig = plt.figure(figsize=figsize.inch)
+
+    ax = fig.add_axes([0.1, 0.22, 0.88, 0.77])
+
+    path = Path("../data/lightcurve")
     filename = path / "pks2155_flare_lc.fits.gz"
-    lc = FluxPoints.read(filename, sed_type="lightcurve")
-    lc.plot(sed_type="eflux", axis_name="time")
-    filename = "lghtcurve-pks.pdf"
+    lc = FluxPoints.read(filename, format="lightcurve")
+    lc.plot(ax=ax, sed_type="eflux", axis_name="time")
+    filename = "hess_lightcurve_pks.pdf"
     log.info(f"Writing {filename}")
     plt.savefig(filename, dpi=300)
 

### 2022-02-24 src/text/2-package-subsections/modeling.tex
remove link to backend docs

@@
 
-The fit class provides a uniform interface to multiple fitting backends: “minuit” \citep{iminuit}, “scipy”, \citep{2020SciPy-NMeth}, and “sherpa” \citep{sherpa-2005,sherpa-2011}, .
-Note that, for now, covaraince matrix and errors are computed only for the fitting with MINUIT.
+The Fit class provides a uniform interface to multiple fitting backends: “minuit” \citep{iminuit}, “scipy”, \citep{2020SciPy-NMeth}, and “sherpa” \citep{sherpa-2005,sherpa-2011}.
+Note that, for now, covariance matrix and errors are computed only for the fitting with MINUIT.
 However depending on the problem other optimizers can better perform, so sometimes it can be useful to run a pre-fit with alternative optimization methods.
-
-For the “minuit” backend see https://iminuit.readthedocs.io/en/latest/reference.html for a detailed description of the available options.
-For the “scipy” backend the available options are described in detail here:
-\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.optimize.minimize.html}
-For the “sherpa” backend you can choose the optimization algorithm between “simplex”, “levmar”, “moncar”, “gridsearch”.
-Those methods are described and compared on \url{http://cxc.cfa.harvard.edu/sherpa/methods/index.html}.
-The available options of the optimization methods are further described on the following page\url{https://cxc.cfa.harvard.edu/sherpa/methods/opt_methods.html}.
-
-In future we plan to extend the supported Fit backend including for example MCMC solutions.
+In future we plan to extend the supported Fit backend, including for example MCMC solutions.
 \footnote{a prototype is available in gammapy-recipes, \url(https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html)}
-%the sampling code should be moved to the recipe (for now it is imported) because it have been removed from the core package.

### 2022-02-24 src/code-examples/snippets/gp_maps.py
fix typos and add to snippet

@@ -1,16 +1,17 @@
-from gammapy.maps import Map
+from gammapy.maps import Map, MapAxis
 from astropy.coordinates import SkyCoord
-from astripy import units as u
+from astropy import units as u
 
 skydir = SkyCoord("0d", "5d", frame="galactic")
+energy_axis = MapAxis.from_bounds(lo_bnd=0.1, hi_bnd=100, nbin=5, unit='TeV', interp='log', name='energy')
 
 # Create a WCS Map
 m_wcs = Map.create(
     binsz=0.1,
     map_type="wcs",
     skydir=skydir,
-    width=[10.0, 8.0] * u.deg
-)
+    width=[10.0, 8.0] * u.deg,
+    axes = [energy_axis])
 
 
 # Create a HPX Map
@@ -18,5 +19,12 @@ m_hpx = Map.create(
     binsz=0.1,
     map_type="hpx",
     skydir=skydir,
-    width=10.0 * u.deg
-)
+    width=10.0 * u.deg,
+    axes = [energy_axis])
+
+# Create a region map
+region = "galactic;circle(0, 5, 1)"
+m_region = Map.create(
+    region = region,
+    map_type='region',
+    axes = [energy_axis])

### 2022-02-24 src/text/2-package-subsections/maps.tex
map axis

@@
 
-The sub-package provides a uniform API for the FITS World Coordinate System (WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and region-based data structures:
+The sub-package provides a uniform API for the FITS World Coordinate System (WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and region-based data structures.
 
@@
 	\item \textbf{WCS: } The FITS WCS pixelization supports a different number of projections to represent celestial spherical coordinates in a regular rectangular grid.
+Gammapy provides full support to data structures using this pixelization scheme.
 	\item \textbf{HEALPix: } This pixelization provides a subdivision of a sphere in which each pixel covers the same surface area as every other pixel.
@@
 \gammapy provides limited support to HEALPix-based maps, relying in some cases on projections to a local WCS grid.
-	\item \textbf{Region geometries: } In this case, instead of a fine spatial grid on a given sky region, the spatial dimension is reduced to a single bin with an arbitrary shape, describing a region in the sky with that same shape.
-Typically they are is used together with a non-spatial dimension, for example an energy axis to represent how a quantity varies with energy on a given region of the sky.
+	\item \textbf{Region geometries: } In this case, instead of a fine spatial grid dividing a rectangular sky region, the spatial dimension is reduced to a single bin with an arbitrary shape, describing a region in the sky with that same shape.
+Typically they are is used together with a non-spatial dimension, for example an energy axis, to represent how a quantity varies in that dimension inside the corresponding region.
 \end{itemize}
 
-\todo{Include example of a sky-map? Perhaps also a region map? Although maybe too much.}
+Additionally, the MapAxis class provides a uniform API for axes representing bins on any physical quantity, such as energy or angular offset.
+The special case of time is covered by the dedicated TimeMapAxis, which allows time bins to be non-contiguous, as it is often the case with observation time-stamps.
+The generic class LabelMapAxis allows the creation of axes for non-numeric entries.
 
-\todo{Code examples of what? Making a geom and filling a map? Transforming coordinates? 3D maps? Would be good to have the code example and the plot be related}
+\begin{figure}
+	\import{code-examples/generated/}{gp_maps}
+
+	\caption{Using gammapy.maps to create a WCS, a HPX and a region map. Note the uniform API for map creation.}
+	\label{ig*:minted:gp_maps}
+\end{figure}

### 2022-02-24 src/code-examples/snippets/gp_maps.py
small changes

@@ -3,7 +3,8 @@ from astropy.coordinates import SkyCoord
 from astropy import units as u
 
 skydir = SkyCoord("0d", "5d", frame="galactic")
-energy_axis = MapAxis.from_bounds(lo_bnd=0.1, hi_bnd=100, nbin=5, unit='TeV', interp='log', name='energy')
+energy_axis = MapAxis.from_bounds(lo_bnd=0.1, hi_bnd=100, 
+              nbin=5, unit='TeV', interp='log', name='energy')
 
 # Create a WCS Map
 m_wcs = Map.create(
@@ -14,7 +15,7 @@ m_wcs = Map.create(
     axes = [energy_axis])
 
 
-# Create a HPX Map
+# Create a HEALPix Map
 m_hpx = Map.create(
     binsz=0.1,
     map_type="hpx",

### 2022-02-24 src/text/3-applications/3.4-survey_pops.tex
Add application/survey and sources populations section

\subsection{Survey, catalogs, and population studies}

Sky surveys have a large potential for new source detections, and new phenomena discovery. They also offer less selection bias to perform source population studies over a large set of coherently detected and modelled objects.
Early versions of \textit{gammapy} where developed in parallel of the preparation of the HESS Galactic plane survey catalog [HGPS]\citep {2018A&A...612A...1H} and the associated PWN and SNR populations studies \citep{2018A&A...612A...2H, 2018A&A...612A...3H}.

The CTA first Data challenge (DC1) proposed a large set of simulated observations covering the programs proposed in the Key science Projects for CTA  {2019scta.book.....C}, including in particular extra-Galactic and Galactic surveys.
The studies performed on these simulations not only offered a first glimpse on what could be the sky seen by CTA, but also the opportunity to test the software, improve its performance and identify the needs in term of parallelisation to process large datasets. Note that the CTA-DC1 simulations were performed with the \textit{ctools}  \citep{2016A&A...593A...1K} package and analysed with both \textit{ctools} and \textit{gammapy} packages in order to cross-validate them. More recently new simulations of the CTA-GPS were analysed  in the view of optimizing the production of the future CTA catalogs and associated populations studies \citep{2021arXiv210903729R}.
Future plans of the CTA observatory include the preparation of a new Data Challenge simulated with \textit{gammapy} that is planed to be released publicly in order to reach a broader community.

### 2022-02-24 src/text/3-applications/3.4-survey_pops.tex
minor corrections

@@
-\subsection{Survey, catalogs, and population studies}
+\subsection{Surveys, catalogs, and population studies}
 
@@
 The CTA first Data challenge (DC1) proposed a large set of simulated observations covering the programs proposed in the Key science Projects for CTA  {2019scta.book.....C}, including in particular extra-Galactic and Galactic surveys.
-The studies performed on these simulations not only offered a first glimpse on what could be the sky seen by CTA, but also the opportunity to test the software, improve its performance and identify the needs in term of parallelisation to process large datasets.
-Note that the CTA-DC1 simulations were performed with the \textit{ctools}  \citep{2016A&A...593A...1K} package and analysed with both \textit{ctools} and \textit{gammapy} packages in order to cross-validate them.
+The studies performed on these simulations not only offered a first glimpse on what could be the sky seen by CTA, but also the opportunity to test the software, improve its performance, and identify the needs in term of parallelisation to process the large datasets provided by the surveys.
+Note that the CTA-DC1 simulations were performed with the \textit{ctools} package \citep{2016A&A...593A...1K} and analysed with both \textit{ctools} and \textit{gammapy} packages in order to cross-validate them.
 More recently new simulations of the CTA-GPS were analysed in the view of optimizing the production of the future CTA catalogs and associated populations studies \citep{2021arXiv210903729R}.
-Future plans of the CTA observatory include the preparation of a new Data Challenge simulated with \textit{gammapy} that is planed to be released publicly in order to reach a broader community.
+Future plans of the CTA observatory include the preparation of a new Data Challenge simulated with \textit{gammapy} that is meant to be released publicly in order to reach a broader community.

### 2022-02-24 src/text/3-applications/3.4-survey_pops.tex
fix ref

@@
 They also offer less selection bias to perform source population studies over a large set of coherently detected and modelled objects.
-Early versions of \textit{gammapy} where developed in parallel of the preparation of the HESS Galactic plane survey catalog [HGPS]\citep {2018A&A...612A...1H} and the associated PWN and SNR populations studies \citep{2018A&A...612A...2H, 2018A&A...612A...3H}.
+Early versions of \textit{gammapy} where developed in parallel of the preparation of the HESS Galactic plane survey catalog \citep[HGPS][]{2018A&A...612A...1H} and the associated PWN and SNR populations studies \citep{2018A&A...612A...2H, 2018A&A...612A...3H}.
 
-The CTA first Data challenge (DC1) proposed a large set of simulated observations covering the programs proposed in the Key science Projects for CTA  {2019scta.book.....C}, including in particular extra-Galactic and Galactic surveys.
+The CTA first Data challenge (DC1) proposed a large set of simulated observations covering the programs proposed in the Key science Projects for CTA  \citep{2019scta.book.....C}, including in particular extra-Galactic and Galactic surveys.
 The studies performed on these simulations not only offered a first glimpse on what could be the sky seen by CTA, but also the opportunity to test the software, improve its performance, and identify the needs in term of parallelisation to process the large datasets provided by the surveys.

### 2022-02-26 src/figures/codestats.py
adapt codestats.py script

@@ -2,14 +2,20 @@
 """Provide code stats for Gammapy project"""
 import argparse
 import logging
+import pathlib
 import subprocess
 from string import Template
-
+from collections import defaultdict
 import matplotlib.pyplot as plt
 import pandas as pd
 
+import config
+
 logging.basicConfig(level=logging.INFO)
 
+CODEBASE = "../../gammapy" 
+TEMPFILE = "results.csv"
+TEXFILE = "../text/tables/codestats.tex"
 LATEX_TEMPLATE = r"""\begin{tabular}{ccccccc}
 \hline
 $labels
@@ -17,14 +23,10 @@ $labels
 $cells\hline
 $summary
 \end{tabular}
-
 """
-
 CSV_TEMPLATE = r"""$labels
 $cells$summary"""
 
-
-# TODO: use pygount here? cloc is not easily installable via conda...
 def run_cloc(args):
     result = subprocess.run(["cloc", args.src], capture_output=True)
     return result.stdout
@@ -61,31 +63,49 @@ def make_files(stats):
     latex = latex.substitute(content_lat)
     csv = csv.substitute(content_csv)
 
-    logging.info("LaTeX OUTPUT TABLE BELOW:\n\n")
-    print(latex)
-    with open("results.csv", "w") as file_csv:
-        file_csv.write(csv)
+    with open(TEXFILE, "w") as file_tex:
+        file_tex.write(latex)
+    logging.info(f"LaTeX output file {TEXFILE} created.")
 
+    with open(TEMPFILE, "w") as file_csv:
+        file_csv.write(csv)
+    logging.info(f"CSV temporary file {TEMPFILE} created.")    
 
 def make_pie():
-    file_data = pd.read_csv("results.csv", sep=", ", engine="python")
 
+    figsize = config.FigureSizeAA()
+    plt.figure(figsize=figsize.inch)
+
+    file_data = pd.read_csv(TEMPFILE, sep=", ", engine="python")
     df = file_data[:-1]
     df = df.set_index("Language")
+
+    # code
     df = df.sort_values(by=["code"])[::-1]
-    df.plot.pie(y="code", figsize=(7, 7), autopct=fix_autopct, labels=None)
+    sdf = shorthen_df(df)
+    sdf.plot.pie(y="code", autopct=fix_autopct, labels=None)
     plt.ylabel("")
     plt.savefig("codestats.pdf")
-    logging.info("PIECHART FILE piecode.png CREATED")
+    logging.info("Piecharf file codestats.pdf created.")
 
[…]

### 2022-02-28 src/figures/codestats.py
make dir tables if does not exist

@@ -2,7 +2,7 @@
 """Provide code stats for Gammapy project"""
 import argparse
 import logging
-import pathlib
+from pathlib import Path
 import subprocess
 from string import Template
 from collections import defaultdict
@@ -63,6 +63,8 @@ def make_files(stats):
     latex = latex.substitute(content_lat)
     csv = csv.substitute(content_csv)
 
+    tex_name = Path(TEXFILE)
+    tex_name.parent.mkdir(parents=True, exist_ok=True)
     with open(TEXFILE, "w") as file_tex:
         file_tex.write(latex)
     logging.info(f"LaTeX output file {TEXFILE} created.")
@@ -124,7 +126,7 @@ def main():
     make_pie()
 
     # remove not needed intermediate file
-    pathlib.Path(TEMPFILE).unlink()
+    Path(TEMPFILE).unlink()
 
 
 if __name__ == "__main__":

### 2022-02-28 src/figures/codestats.py
move latex table to tables/generated

@@ -15,7 +15,7 @@ logging.basicConfig(level=logging.INFO)
 
 CODEBASE = "../../gammapy" 
 TEMPFILE = "results.csv"
-TEXFILE = "../text/tables/codestats.tex"
+TEXFILE = "../tables/generated/codestats.tex"
 LATEX_TEMPLATE = r"""\begin{tabular}{ccccccc}
 \hline
 $labels

### 2022-02-28 src/figures/codestats.py
add rule codestats

@@ -45,7 +45,7 @@ def make_files(stats):
         decoded = decoded.replace("Jupyter Notebook", "Notebook")
         decoded = decoded.replace("DOS Batch", "Batch")
         decoded = decoded.replace("Bourne Shell", "Shell")
-        decoded = decoded.replace("SUM:", "SUM")
+        decoded = decoded.replace("SUM:", "Total")
 
         latex_converted = "\t& ".join(decoded.split()) + " \\\\"
         csv_converted = ", ".join(decoded.split())

### 2022-02-28 src/figures/codestats.py
adapt codestats script to consider tests and docstrings

@@ -28,8 +28,34 @@ CSV_TEMPLATE = r"""$labels
 $cells$summary"""
 
 def run_cloc(args):
-    result = subprocess.run(["cloc", args.src], capture_output=True)
-    return result.stdout
+
+    result_api = subprocess.run(["cloc", "--not-match-d=test", args.src], capture_output=True).stdout
+    result_test = subprocess.run(["cloc", "--match-d=test", args.src], capture_output=True).stdout
+
+    for line in result_api.splitlines():
+        decoded = line.decode("utf-8")
+        if decoded.startswith("Python"):
+            python_api_row = decoded
+            (_, files_api, blank_api, comment_api, code_api) = python_api_row.split()
+    for line in result_test.splitlines():
+        decoded = line.decode("utf-8")
+        if decoded.startswith("Python"):
+            python_test_row = decoded
+            (_, files_test, blank_test, comment_test, code_test) = python_test_row.split()
+
+    PythonAPI  = f"PythonAPI                      {files_api}          {blank_api}          {comment_api}          {code_api}"
+    PythonTests = f"PythonTests                    {files_test}           {blank_test}           {comment_test}          {code_test}"
+    DocStrings = f"DocStrings                     {files_api}              0              0          {comment_api}"
+
+    result_list = []
+    for line in result_api.splitlines():
+        decoded = line.decode("utf-8")
+        if decoded.startswith("Python"):
+            result_list.extend((PythonAPI, PythonTests, DocStrings))
+        else:
+            result_list.append(decoded)
+
+    return "\n".join(result_list)
 
 
 def make_files(stats):
@@ -41,30 +67,33 @@ def make_files(stats):
     content_csv = {"labels": "", "cells": "", "summary": ""}
 
     for idx, line in enumerate(stats.splitlines()):
-        decoded = line.decode("utf-8")
-        decoded = decoded.replace("Jupyter Notebook", "Notebook")
-        decoded = decoded.replace("DOS Batch", "Batch")
-        decoded = decoded.replace("Bourne Shell", "Shell")
-        decoded = decoded.replace("SUM:", "Total")
+        line = line.replace("PythonAPI", "Python~API")
+        line = line.replace("PythonTests", "Python~Tests")
+        line = line.replace("Jupyter Notebook", "Notebooks")
[…]

### 2022-02-28 src/text/2-package-subsections/datasets.tex

@@
 The gammapy.datasets subpackage contains classes to bundle together binned data along with associated models and the likelihood, which provides an interface to the Fit class (Sec \ref{ssec:gammapy-modeling}) for modeling and fitting purposes.
-Depending upon the type of analysis (spectral and morphological, or only spectral), and the associated statistics (Cash, wstat or chi2), different types of Datasets are supported.
+Depending upon the type of analysis and the associated statistics, different types of Datasets are supported.
+MapDataset is used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is done using SpectrumDatastet.
+While the default statistics for both of these is Cash, their corresponding OnOff versions are adapted for the case where the background is measured from real off counts, and support wstat statistics.
 The predicted counts are computed by convolution of the models with the associate IRFs.
-Fitting of precomputed flux points is enabled through FluxPointsDatasets.
+Fitting of precomputed flux points is enabled through FluxPointsDatasets, using chi2 statistics.
 Multiple datasets of same or different types can be  bundled together in Datasets (e.g.: Figure \ref{fig*:minted:gp_datasets}), where the likelihood from each constituent member is added, thus facilitating joint fitting across different observations, and even different instruments across different wavelengths.

### 2022-03-01 src/code-examples/snippets/gp_maps.py
Run pre-commit

@@ -3,7 +3,7 @@ from astropy.coordinates import SkyCoord
 from astropy import units as u
 
 skydir = SkyCoord("0d", "5d", frame="galactic")
-energy_axis = MapAxis.from_bounds(lo_bnd=0.1, hi_bnd=100, 
+energy_axis = MapAxis.from_bounds(lo_bnd=0.1, hi_bnd=100,
               nbin=5, unit='TeV', interp='log', name='energy')
 
 # Create a WCS Map

### 2022-03-01 src/figures/codestats.py

@@ -13,7 +13,7 @@ import config
 
 logging.basicConfig(level=logging.INFO)
 
-CODEBASE = "../../gammapy" 
+CODEBASE = "../../gammapy"
 TEMPFILE = "results.csv"
 TEXFILE = "../tables/generated/codestats.tex"
 LATEX_TEMPLATE = r"""\begin{tabular}{ccccccc}
@@ -100,7 +100,7 @@ def make_files(stats):
 
     with open(TEMPFILE, "w") as file_csv:
         file_csv.write(csv)
-    logging.info(f"CSV temporary file {TEMPFILE} created.")    
+    logging.info(f"CSV temporary file {TEMPFILE} created.")
 
 def make_pie():
 

### 2022-03-01 src/text/2-package-subsections/catalog.tex
write catalog

@@
 \label{ssec:gammapy-catalog}
-\todo{Axel Donath}
+\todo{Atreyee}
 Gamma-ray catalog access
+
+Comprehensive source catalogs are increasingly being provided by many high energy astrophysics experiments.
+gammapy.catalog provides a convenient access to some common gamma-ray catalogs.
+A global catalog table is provided, along with source models flux points and light curves (if available) for individual objects, which are internally created from the supplied FITS tables.
+This module works independently from the rest of teh package, and the required catalogs are supplied in GAMMAPY_DATA.
+Presently, catalogs from Fermi-LAT (standard \citep{3FGL, 4FGL} and high energy \citep{2FHL, 3FHL}), H.E.S.S.
+galactic plane survey \citep{HGPS}, HAWC \citep{2HWC, 3HWC} and gamma-cat (\citep{gamma-cat}; an open source gamma ray catalog combining information from multiple catalogs) are supported.
 
@@
 	\import{code-examples/generated/}{gp_catalogs}
-	\caption{Using gammapy.catalogs}
+	\caption{Using gammapy.catalogs: Accessing underlying model, flux points and lightcurve from the Fermi-LAT 4FGL catalog for the blazar PKS 2155-304}
 	\label{codeexample:data}

### 2022-03-01 src/code-examples/snippets/gp_catalogs.py

@@ -1,3 +1,9 @@
-from gammapy.catalog import SOURCE_CATALOGS
+from gammapy.catalog import SourceCatalog4FGL
 
-catalog = SOURCE_CATALOGS["3fhl"]
+catalog = SourceCatalog4FGL()
+print("Number of sources :", len(catalog.table))
+
+source = catalog["PKS 2155-304"]
+model = source.sky_model()
+flux_points = source.flux_points
+lightcurve = source.lightcurve()

### 2022-03-01 src/text/1-introduction.tex
Run pre-commit
Run tex indentation

@@
 
-The Cherenkov Telescope Array (CTA) will be operated as an open observatory for the
-first time. Thus there is a need for open analysis software as well.
+The Cherenkov Telescope Array (CTA) will be operated as an open observatory for
+the first time. Thus there is a need for open analysis software as well.
 
-Moreover, the operation of CTA as an observatory introduces the necessity of sharing
-its data publicly. The data-reduction workflow of different IACTs of the current
-generation is remarkably similar, resulting in a ``high'' data level that can be
-finally used to derive scientific results (e.g. spectra, sky maps, light curves).
-The information in this high data level is independent on the data reduction,
-and eventually of the detection technique. This implies, for example, that data
-from IACT and WCD can be represented within the same model.
-The efforts to prototype the future CTA data model and to convert current IACT
-data in a format usable with the newly-available science tools converged in the 
-so-called ``Data Format for Gamma-ray Astronomy'' initiative
-\citep{gadf_proc, gadf_universe}, abbreviated in \texttt{gamma-astro-data-format}
-(GADF). The latter proposes prototypical specifications to produce files based
-on the flexible image transport system (FITS) format \citep{fits} encapsulating
-this high-level information. This is realized by storing a list of gamma-like
-events with their measured quantites (energy, direction, arrival time) and a
-parametrisation of the response of the system (see Sec.~\ref{ssec:gammapy-data}
-and Sec.~\ref{ssec:gammapy-irf} for more information).
+Moreover, the operation of CTA as an observatory introduces the necessity of
+sharing its data publicly. The data-reduction workflow of different IACTs of
+the current generation is remarkably similar, resulting in a \textit{high} data
+level that can be finally used to derive scientific results (, spectra, sky
+maps, light curves). The information in this high data level is independent on
+the data reduction, and eventually of the detection technique. This implies,
+for example, that data from IACT and WCD can be represented within the same
+model. The efforts to prototype the future CTA data model and to convert
+current IACT data in a format usable with the newly-available science tools
+converged in the so-called \textit{Data Format for Gamma-ray Astronomy}
+initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
+\texttt{gamma-astro-data-format} (GADF). The latter proposes prototypical
+specifications to produce files based on the flexible image transport system
+(FITS) format~\citep{fits} encapsulating this high-level information. This is
+realized by storing a list of gamma-like events with their measured quantites
+(energy, direction, arrival time) and a parametrisation of the response of the
+system (see Sec.~\ref{ssec:gammapy-data} and Sec.~\ref{ssec:gammapy-irf} for
+more information).
 
@@
 sherpa~\citep{sherpa-2011, sherpa-2009}, or for gamma-ray even PyFACT
-\citep{pyfact}.
+~\citep{pyfact}.
 
@@
 	\centering
-	\includegraphics[height=0.5\textwidth, angle=270]{static/gammapy-big-picture}
-	\caption{
-		Gammapy is a Python package for high-level gamma-ray data analysis. Using event
-		lists, exposures and point spread functions as input you can use it to generate
-		science results such as images, spectra, light curves or source catalogs. So
-		far it has been used to simulate and analyse H.E.S.S., CTA and
-		\textit{Fermi}-LAT data, hopefully it will also be applied to e.g., VERITAS,
-		MAGIC or HAWC data in the future.
-	}
+	\includegraphics[height=0.5\textwidth,
+		angle=270]{static/gammapy-big-picture} \caption{ Gammapy is a Python package
+		for high-level gamma-ray data analysis. Using event lists, exposures and point
+		spread functions as input you can use it to generate science results such as
+		images, spectra, light curves or source catalogs. So far it has been used to
+		simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT data, hopefully it
+		will also be applied to e.g. VERITAS, MAGIC or HAWC data in the future. }
 	\label{fig:big-picture}
+
 \end{figure}
@@
 		The Gammapy stack. Required dependencies Numpy and Astropy are illustrated with
-		solid arrows, optional dependencies (the rest) with dashed arrows.
-	}
+		solid arrows, optional dependencies (the rest) with dashed arrows. }
 	\label{fig:dependencies}
+
 \end{figure}

### 2022-03-01 src/text/2-package-subsections/data.tex
Run pre-commit
Run tex indentation

@@
 As illustrated in Fig.~\ref{fig:data_flow}, the \verb|gammapy.data| sub-package
-implements the lowest data level, providing the input interface to gamma-ray data.
-The \gammapy data model follows the \gadf specifications (Sec.~\ref{sec:introduction}),
-therefore gamma-ray data compliant with those can be directly read with the package. 
-Version X.X of the \gadf specification is supported in this release version.
-As both the \gadf data model and \gammapy were initially conceived for \iact
-data analysis, input data are typically grouped in \texttt{Observations}, corresponding
-to stable periods of data aquisitions (typically $20 - 30\,{\rm min}$).
-A \texttt{DataStore} object, gathering a collection of observations, can be created
-porviding ancillary files containing information about the telescope observation
-mode and the content of the data unit of each file. The \texttt{DataStore} allows
-for selecting a list of observations based on specific filters.
-As an illustrative example, Fig.~\ref{fig*:minted:gp_data} shows
-how to create a \texttt{datastore} and how to obtain the observations corresponding
-to given identification numbers (IDs).
+implements the lowest data level, providing the input interface to gamma-ray
+data. The \gammapy data model follows the \gadf specifications
+(Sec.~\ref{sec:introduction}), therefore gamma-ray data compliant with those
+can be directly read with the package. Version X.X of the \gadf specification
+is supported in this release version. As both the \gadf data model and \gammapy
+were initially conceived for \iact data analysis, input data are typically
+grouped in \texttt{Observations}, corresponding to stable periods of data
+aquisitions (typically $20 - 30\,{\rm min}$). A \texttt{DataStore} object,
+gathering a collection of observations, can be created porviding ancillary
+files containing information about the telescope observation mode and the
+content of the data unit of each file. The \texttt{DataStore} allows for
+selecting a list of observations based on specific filters. As an illustrative
+example, Fig.~\ref{fig*:minted:gp_data} shows how to create a
+\texttt{datastore} and how to obtain the observations corresponding to given
+identification numbers (IDs).
 
-The so-called DL3 files represented by the \texttt{Observation} class consist of
-two types of elements: a list of gamma-ray events with relevant physical quantities
-for the successive analysis (estimated energy, direction and arrival times) that
-is handled by the \texttt{EventList} class and an instrument response function (IRF),
-providing the response of the system, typically factorised in independent components
-(see the description in Sec.~\ref{ssec:gammapy-irf}).
-The separate handling of event lists and IRFs additionally allows for data from
-other gamma-ray instruments to be read. For example, to read \fermi data, the
-user can read separately their event list (already compliant with the \gadf
-specifications) and then find the appropriate IRF class representing the response
-functions provided by \fermi, see Sec.~\ref{ssec:fermi}.
+The so-called DL3 files represented by the \texttt{Observation} class consist
+of two types of elements: a list of gamma-ray events with relevant physical
+quantities for the successive analysis (estimated energy, direction and arrival
+times) that is handled by the \texttt{EventList} class and an instrument
+response function (IRF), providing the response of the system, typically
+factorised in independent components (see the description in
+Sec.~\ref{ssec:gammapy-irf}). The separate handling of event lists and IRFs
+additionally allows for data from other gamma-ray instruments to be read. For
+example, to read \fermi data, the user can read separately their event list
+(already compliant with the \gadf specifications) and then find the appropriate
+IRF class representing the response functions provided by \fermi, see
+Sec.~\ref{ssec:fermi}.
 

### 2022-03-01 src/text/2-package-subsections/datasets.tex
Run pre-commit
Run tex indentation

@@
 
-The end product of the data reduction process described in Section \ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps, at the DL4 level.
-The gammapy.datasets subpackage contains classes to bundle together binned data along with associated models and the likelihood, which provides an interface to the Fit class (Sec \ref{ssec:gammapy-modeling}) for modeling and fitting purposes.
-Depending upon the type of analysis and the associated statistics, different types of Datasets are supported.
-MapDataset is used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is done using SpectrumDatastet.
-While the default statistics for both of these is Cash, their corresponding OnOff versions are adapted for the case where the background is measured from real off counts, and support wstat statistics.
-The predicted counts are computed by convolution of the models with the associate IRFs.
-Fitting of precomputed flux points is enabled through FluxPointsDatasets, using chi2 statistics.
-Multiple datasets of same or different types can be  bundled together in Datasets (e.g.: Figure \ref{fig*:minted:gp_datasets}), where the likelihood from each constituent member is added, thus facilitating joint fitting across different observations, and even different instruments across different wavelengths.
-Datasets also provide functionalities for manipulating reduced data, eg: stacking, sub-grouping, plotting, etc.
-Users can also create their customized datasets for implementing modified likelihood methods.
+The end product of the data reduction process described in Section
+\ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps,
+at the DL4 level. The gammapy.datasets subpackage contains classes to bundle
+together binned data along with associated models and the likelihood, which
+provides an interface to the Fit class (Sec \ref{ssec:gammapy-modeling}) for
+modeling and fitting purposes. Depending upon the type of analysis and the
+associated statistics, different types of Datasets are supported. MapDataset is
+used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
+done using SpectrumDatastet. While the default statistics for both of these is
+Cash, their corresponding OnOff versions are adapted for the case where the
+background is measured from real off counts, and support wstat statistics. The
+predicted counts are computed by convolution of the models with the associate
+IRFs. Fitting of precomputed flux points is enabled through FluxPointsDatasets,
+using chi2 statistics. Multiple datasets of same or different types can be
+bundled together in Datasets (e.g.: Figure \ref{fig*:minted:gp_datasets}),
+where the likelihood from each constituent member is added, thus facilitating
+joint fitting across different observations, and even different instruments
+across different wavelengths. Datasets also provide functionalities for
+manipulating reduced data, eg: stacking, sub-grouping, plotting, etc. Users can
+also create their customized datasets for implementing modified likelihood
+methods.
 

### 2022-03-01 src/text/2-package-subsections/estimators.tex
Run tex indentation

@@
 \todo{Axel Donath}
-The \verb|gammapy.estimators| sub-module features methods to compute
-flux points, light curves, flux maps, flux profiles from data.
+The \verb|gammapy.estimators| sub-module features methods to compute flux
+points, light curves, flux maps, flux profiles from data.
 
@@
 	\item Reference spectral model scaled in energy bin
-	\item "Forward folding" / "Backward folding": but there is no difference between the two, backwards folding is forward folding with one bin
-	\item Likelihood profiles
-	\item Uniform N-dimensional data structure
-	\item Uniform API for plotting etc.
-	\item \verb|FluxMaps| and \verb|FluxPoints|
-	\item Serialisation to multiple formats, Astropy's \verb|Table| and \verb|BinnedTimeSeries|
-	\item Additional quantities for debugging, such as predicted counts, fit convergence, sum of fit statistics
-	\item
-\end{itemize}
+	\item "Forward folding" / "Backward folding": but there is no
+	      difference between the two, backwards folding is forward folding with one bin
+	\item Likelihood profiles \item Uniform N-dimensional data structure \item
+	      Uniform API for plotting etc. \item \verb|FluxMaps| and \verb|FluxPoints| \item
+	      Serialisation to multiple formats, Astropy's \verb|Table| and
+	      \verb|BinnedTimeSeries|
+	\item Additional quantities for debugging, such as predicted counts, fit convergence,
+	      sum of fit statistics \item \end{itemize}
 
@@
 	\import{code-examples/generated/}{gp_estimators}
-	\caption{Using the TSMapEstimator from gammapy.estimators to compute a sqrt(TS) map.}
-	\label{fig*:minted:gp_estimators}
-\end{figure}
+	\caption{Using the TSMapEstimator from gammapy.estimators to compute a
+		sqrt(TS) map.} \label{fig*:minted:gp_estimators} \end{figure}

### 2022-03-01 src/text/2-package-subsections/makers.tex
Run tex indentation

@@
 
-The data reduction contains all tasks required to process and prepare data at the DL3
-level for modeling and fitting. The \texttt{gammapy.makers} sub-package contains the various
-classes and functions required to do so. First, events are binned and IRFs are interpolated and
-projected onto the chosen analysis geometry. This produces counts, exposure, background, psf
-and energy dispersion maps. The \texttt{MapDatasetMaker} and \texttt{SpectrumDatasetMaker}
-are responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.
+The data reduction contains all tasks required to process and prepare data at
+the DL3 level for modeling and fitting. The \texttt{gammapy.makers} sub-package
+contains the various classes and functions required to do so. First, events are
+binned and IRFs are interpolated and projected onto the chosen analysis
+geometry. This produces counts, exposure, background, psf and energy dispersion
+maps. The \texttt{MapDatasetMaker} and \texttt{SpectrumDatasetMaker} are
+responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.
 
-Because the background models suffer from strong uncertainties it is required to correct
-them from the data themselves. Several techniques are commonly used in gamma-ray astronomy
-such as field-of-view background normalization or background measurement in reflected regions
-regions, see~\cite{Berge07}. Specific \texttt{Makers} such as the \texttt{FoVBackgroundMaker}
-or the \texttt{ReflectedRegionsBackgroundMaker} are in charge of this step.
+Because the background models suffer from strong uncertainties it is required
+to correct them from the data themselves. Several techniques are commonly used
+in gamma-ray astronomy such as field-of-view background normalization or
+background measurement in reflected regions regions, see~\cite{Berge07}.
+Specific \texttt{Makers} such as the \texttt{FoVBackgroundMaker} or the
+\texttt{ReflectedRegionsBackgroundMaker} are in charge of this step.
 
-Finally, to limit other sources of systematic uncertainties, a data validity domain is
-determined by the \texttt{SafeMaskMaker}. It can be used to limit the extent of the field
-of view used or to limit the energy range to e.g., a domain where the energy reconstruction
-bias is below a given value.
+Finally, to limit other sources of systematic uncertainties, a data validity
+domain is determined by the \texttt{SafeMaskMaker}. It can be used to limit the
+extent of the field of view used or to limit the energy range to e.g., a domain
+where the energy reconstruction bias is below a given value.
 
@@
 
-	\caption{Using gammapy.makers to reduce DL3 level data into a \texttt{Dataset}.}
+	\caption{Using gammapy.makers to reduce DL3 level data into a
+		\texttt{Dataset}.}
 	\label{ig*:minted:gp_makers}

### 2022-03-01 src/text/2-package-subsections/maps.tex
small changes
Run pre-commit
Run tex indentation

@@
 \todo{Laura Olivera-Nieto}
-The \verb|gammapy.maps| sub-package provides classes for representing data structures associated with a set of coordinates or a region on a sphere.
-In addition it allows to handle an arbitrary number of non-spatial data dimensions, such as time or energy.
-It is organized around three types of structures: geometries, sky-maps and map axes, which inherit from the base classes Geom, Map and MapAxis respectively.
+The \verb|gammapy.maps| sub-package provides classes for representing data
+structures associated with a set of coordinates or a region on a sphere. In
+addition it allows to handle an arbitrary number of non-spatial data
+dimensions, such as time or energy. It is organized around three types of
+structures: geometries, sky-maps and map axes, which inherit from the base
+classes Geom, Map and MapAxis respectively.
 
-The geometry defines the pixelization scheme and map boundaries.
-It also provides methods to transform between sky and pixel coordinates.
-Maps consist of a geometry instance together with a data array containing the corresponding map values.
-Map axes contain a sequence of ordered values which define bins on a given dimension, spatial or not.
-Map axes can have physical units attached to them, as well as non-linear step sizes.
+The geometry defines the pixelization scheme and map boundaries. It also
+provides methods to transform between sky and pixel coordinates. Maps consist
+of a geometry instance together with a data array containing the corresponding
+map values. Map axes contain a sequence of ordered values which define bins on
+a given dimension, spatial or not. Map axes can have physical units attached to
+them, as well as non-linear step sizes.
 
-The sub-package provides a uniform API for the FITS World Coordinate System (WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and region-based data structures.
+The sub-package provides a uniform API for the FITS World Coordinate System
+(WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and
+region-based data structures.
 
@@
 \begin{itemize}
-	\item \textbf{WCS: } The FITS WCS pixelization supports a different number of projections to represent celestial spherical coordinates in a regular rectangular grid.
-Gammapy provides full support to data structures using this pixelization scheme.
-	\item \textbf{HEALPix: } This pixelization provides a subdivision of a sphere in which each pixel covers the same surface area as every other pixel.
-As a consequence, however, pixel shapes are no longer rectangular, or regular.
-\gammapy provides limited support to HEALPix-based maps, relying in some cases on projections to a local WCS grid.
-	\item \textbf{Region geometries: } In this case, instead of a fine spatial grid dividing a rectangular sky region, the spatial dimension is reduced to a single bin with an arbitrary shape, describing a region in the sky with that same shape.
-Typically they are is used together with a non-spatial dimension, for example an energy axis, to represent how a quantity varies in that dimension inside the corresponding region.
-\end{itemize}
+	\item \textbf{WCS: } The FITS WCS pixelization supports a different
+	      number of projections to represent celestial spherical coordinates in a regular
+	      rectangular grid. Gammapy provides full support to data structures using this
+	      pixelization scheme. \item \textbf{HEALPix: } This pixelization provides a
+	      subdivision of a sphere in which each pixel covers the same surface area as
+	      every other pixel. As a consequence, however, pixel shapes are no longer
+	      rectangular, or regular. \gammapy provides limited support to HEALPix-based
+	      maps, relying in some cases on projections to a local WCS grid. \item
+	      \textbf{Region geometries: } In this case, instead of a fine spatial grid
+	      dividing a rectangular sky region, the spatial dimension is reduced to a single
+	      bin with an arbitrary shape, describing a region in the sky with that same
+	      shape. Typically they are is used together with a non-spatial dimension, for
+	      example an energy axis, to represent how a quantity varies in that dimension
+	      inside the corresponding region. \end{itemize}
 
-Additionally, the MapAxis class provides a uniform API for axes representing bins on any physical quantity, such as energy or angular offset.
-The special case of time is covered by the dedicated TimeMapAxis, which allows time bins to be non-contiguous, as it is often the case with observation time-stamps.
-The generic class LabelMapAxis allows the creation of axes for non-numeric entries.
+Additionally, the MapAxis class provides a uniform API for axes representing
+bins on any physical quantity, such as energy or angular offset. The special
+case of time is covered by the dedicated TimeMapAxis, which allows time bins to
+be non-contiguous, as it is often the case with observation time-stamps. The
+generic class LabelMapAxis allows the creation of axes for non-numeric entries.
 
@@
 
-	\caption{Using gammapy.maps to create a WCS, a HPX and a region map. Note the uniform API for map creation.}
-	\label{ig*:minted:gp_maps}
+	\caption{Using gammapy.maps to create a WCS, a HEALPix and a region
+		map. Note the uniform API for map creation.} \label{ig*:minted:gp_maps}
 \end{figure}

### 2022-03-01 src/text/2-package-subsections/modeling.tex
Run pre-commit
Run tex indentation

@@
 
-gammapy.modeling contains all the functionality related to modeling and fitting data. This includes spectral, spatial and temporal model classes, as well as the fit and parameter API.
+gammapy.modeling contains all the functionality related to modeling and fitting
+data. This includes spectral, spatial and temporal model classes, as well as
+the fit and parameter API.
 
@@
 The models are grouped into the following categories:
+
 \begin{itemize}
@@
 	\item SpatialModel: models to describe spatial shapes (morphologies) of sources
-\item TemporalModel: models to describe temporal flux evolution of sources, such as light and phase curves
+	\item TemporalModel: models to describe temporal flux evolution of sources, such as
+	      light and phase curves
+
 \end{itemize}
-The models follow a naming scheme which contains the category as a suffix to the class name.
 
-The  Spectral Models include a special class of Normed models, which have a dimension-less normalisation.
-These spectral models feature a norm parameter instead of amplitude and are named using the NormSpectralModel suffix.
-They must be used along with another spectral model, as a multiplicative correction factor according to their spectral shape.
-They can be typically used for adjusting template based models, or adding a EBL correction to some analytic model.
-The analytic Spatial models are all normalized such as they integrate to unity over the sky but the template Spatial models may not, so in that special case they have to be combined with a NormSpectralModel.
+The models follow a naming scheme which contains the category as a suffix to
+the class name.
 
-The SkyModel is a factorised model that combine the spectral, spatial and temporal model components (by default the spatial and temporal components are optional).
-SkyModel objects represents additive emission components, usually sources or diffuse emission, although a single source can also be modeled by multiple components.
-To handle list of multiple SkyModel components, Gammapy has a Models class.
+The  Spectral Models include a special class of Normed models, which have a
+dimension-less normalisation. These spectral models feature a norm parameter
+instead of amplitude and are named using the NormSpectralModel suffix. They
+must be used along with another spectral model, as a multiplicative correction
+factor according to their spectral shape. They can be typically used for
+adjusting template based models, or adding a EBL correction to some analytic
+model. The analytic Spatial models are all normalized such as they integrate to
+unity over the sky but the template Spatial models may not, so in that special
+case they have to be combined with a NormSpectralModel.
 
-The model gallery provides a visual overview of the available models in Gammapy.
-Most of the analytic models  commonly used in gamma-ray astronomy are built-in.
-We also offer a wrapper to radiative models implemented in the Naima package \cite{naima}.
-The modeling framework can be easily extended with user-defined models.
-For example agnpy models that describe leptonic radiative processes in jetted Active Galactic Nuclei (AGN) can wrapped into gammapy \citep[see section3.5 of ][]{2021arXiv211214573N} .
+The SkyModel is a factorised model that combine the spectral, spatial and
+temporal model components (by default the spatial and temporal components are
+optional). SkyModel objects represents additive emission components, usually
+sources or diffuse emission, although a single source can also be modeled by
+multiple components. To handle list of multiple SkyModel components, Gammapy
+has a Models class.
+
+The model gallery provides a visual overview of the available models in
+Gammapy. Most of the analytic models  commonly used in gamma-ray astronomy are
+built-in. We also offer a wrapper to radiative models implemented in the Naima
+package~\cite{naima}. The modeling framework can be easily extended with
+user-defined models. For example agnpy models that describe leptonic radiative
+processes in jetted Active Galactic Nuclei (AGN) can wrapped into
+gammapy~\citep[see section3.5 of ][]{2021arXiv211214573N} .
 
@@
 
-The Fit class provides methods to fit, i.e.
-optimise parameters and estimate parameter errors and correlations.
-It interfaces with a Datasets object, which in turn is connected to a Models object containing the model parameters in its Parameters object.
-Models can be unique for a given dataset, or contribute to multiple datasets and thus provide links, allowing e.g.
-to do a joint fit to multiple IACT datasets, or to a joint IACT and \textit{Fermi}-LAT dataset.
-Many examples are given in the tutorials.
+The Fit class provides methods to fit, i.e. optimise parameters and estimate
+parameter errors and correlations. It interfaces with a Datasets object, which
+in turn is connected to a Models object containing the model parameters in its
+Parameters object.  Models can be unique for a given dataset, or contribute to
+multiple datasets and thus provide links, allowing e.g. to do a joint fit to
+multiple IACT datasets, or to a joint IACT and \textit{Fermi}-LAT dataset. Many
+examples are given in the tutorials.
 
-The Fit class provides a uniform interface to multiple fitting backends: “minuit” \citep{iminuit}, “scipy”, \citep{2020SciPy-NMeth}, and “sherpa” \citep{sherpa-2005,sherpa-2011}.
-Note that, for now, covariance matrix and errors are computed only for the fitting with MINUIT.
-However depending on the problem other optimizers can better perform, so sometimes it can be useful to run a pre-fit with alternative optimization methods.
-In future we plan to extend the supported Fit backend, including for example MCMC solutions.
-\footnote{a prototype is available in gammapy-recipes, \url(https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html)}
+The Fit class provides a uniform interface to multiple fitting backends:
+“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
+“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
+and errors are computed only for the fitting with MINUIT. However depending on
+the problem other optimizers can better perform, so sometimes it can be useful
+to run a pre-fit with alternative optimization methods. In future we plan to
+extend the supported Fit backend, including for example MCMC solutions.
+\footnote{a prototype is available in gammapy-recipes,
+
+	\url(https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html)}

### 2022-03-01 scripts/latexindent.py

@@ -17,7 +17,7 @@ for filename in filenames:
 
     command = ["latexindent.pl"]
     command += [f"{filename}"]
-    command += ["-s", "-m", "-l", ".latexindent.yaml"]
+    command += ["-s", "-m", "-l", ".latex-indent-config.yaml"]
     command += ["-o", f"{filename}"]
 
     log.info(f"Reformatting {filename}")

### 2022-03-07 src/text/3-applications.tex
Update 3-applications.tex
reorder applications sections

@@
 
-Each application example is a notebook in the online material: We could have
-one analysis as Python scripts instead of notebook in the online material. At
-the start of this section, point to gammapy-paper repo on Github and say that
-there’s a Binder where people can try the examples online.
+Show some typical and advanced science cases, and refer to published papers
 
-TODO: mention other application examples (joint Crab paper, HESS validation
-paper, HGPS, ...) here or in a subsection "other applications" at the end of
-this section?
+\subsection{Computing Flux points and significance maps}
+\label{ssec:1D-3D-analysis}
+\input{3.1-std-analysis}
 
-\subsection{Source detection}
-\label{ssec:source-detection}
+- standard 1D and 3D analysis
 
@@
 
+\subsection{Temporal analysis}
+\label{ssec:temporal-analysis}
+\input{3.2-temporal}
+lightcurves and temporal models
+
 \subsection{Multi instrument analysis}
 \label{ssec:multi-instrument-analysis}
+\todo{Cosimo Nigro}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
+	\caption{A multi-instrument analysis of the Crab Nebula}
+	\label{fig:multi_instrument_analysis} 
+\end{figure*}
+
+\subsection{Fitting using physical models}
+\label{ssec:naima-models-analysis}
+\todo{Cosimo}
+\begin{figure*}[t]
+(added section in the text requesting multi-insturment figure)
+
+\end{figure}
+
+\subsection{Population studies}
+\label{ssec:population-studies}
+\todo{Quentin Remy}
+
+Talk about simulations here? Or open a new section

### 2022-03-07 src/data/multi-instrument/make_magic.py
added installation via pip of gammapy-dev

@@ -1,0 +1,64 @@
+# reduce the MAGIC data to OGIP files for the 1D analysis
+import logging
+from pathlib import Path
+from astropy.coordinates import SkyCoord
+from regions import PointSkyRegion
+
+# gammapy imports
+from gammapy.data import DataStore
+from gammapy.maps import MapAxis
+from gammapy.maps import RegionGeom
+from gammapy.datasets import SpectrumDataset
+from gammapy.makers import (
+    SpectrumDatasetMaker,
+    WobbleRegionsFinder,
+    ReflectedRegionsBackgroundMaker,
+    SafeMaskMaker
+)
+logging.basicConfig(level=logging.INFO)
+log = logging.getLogger(__name__)
+
+
+# reduce the MAGIC data to OGIP files
+data_store = DataStore.from_dir("input/magic")
+observations = data_store.get_observations(required_irf=["aeff", "edisp"])
+
+# adopt the same energy axes used for flute and DL3 production
+energy_axis = MapAxis.from_energy_bounds(
+    10, 1e5, nbin=20, per_decade=False, unit="GeV", name="energy"
+)
+energy_true_axis = MapAxis.from_energy_bounds(
+    10, 1e5, nbin=28, per_decade=False, unit="GeV", name="energy_true"
+)
+
+# create a point-like geometry for the centre of the ON region
+target_position = SkyCoord(ra=83.63, dec=22.01, unit="deg", frame="icrs")
+on_center = PointSkyRegion(target_position)
+geom = RegionGeom.create(region=on_center, axes=[energy_axis])
+
+# spectrum dataset and its maker
+dataset_empty = SpectrumDataset.create(
+    geom=geom, energy_axis_true=energy_true_axis
+)
+dataset_maker = SpectrumDatasetMaker(
+    containment_correction=False, selection=["counts", "exposure", "edisp"]
+)
+
+# background and safe mask makers
+region_finder = WobbleRegionsFinder(n_off_regions=1)
+bkg_maker = ReflectedRegionsBackgroundMaker(region_finder=region_finder)
+safe_mask_maker = SafeMaskMaker(method=["aeff-default"])
+
+for obs in observations:
+
+    # fill the ON counts
+    dataset = dataset_maker.run(dataset_empty.copy(name=f"{obs.obs_id}"), obs)
+
+    # fill the OFF counts and set threshold
+    dataset_on_off = bkg_maker.run(dataset, obs)
[…]

### 2022-03-07 src/figures/multi_instrument_analysis.py

@@ -1,0 +1,9 @@
+import config
+import matplotlib.pyplot as plt
+
+figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="one-column")
+fig, ax  = plt.subplots(figsize=figsize)
+
+
+
+fig.savefig("multi_instrument_analysis.pdf")

### 2022-03-07 src/data/multi-instrument/make_magic.py
added script for MAGIC data reduction

@@ -19,46 +19,55 @@ logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 
 
-# reduce the MAGIC data to OGIP files
-data_store = DataStore.from_dir("input/magic")
-observations = data_store.get_observations(required_irf=["aeff", "edisp"])
+def reduce_magic():
+    # reduce the MAGIC data to OGIP files
+    data_store = DataStore.from_dir("input/data/magic")
+    observations = data_store.get_observations(required_irf=["aeff", "edisp"])
 
-# adopt the same energy axes used for flute and DL3 production
-energy_axis = MapAxis.from_energy_bounds(
-    10, 1e5, nbin=20, per_decade=False, unit="GeV", name="energy"
-)
-energy_true_axis = MapAxis.from_energy_bounds(
-    10, 1e5, nbin=28, per_decade=False, unit="GeV", name="energy_true"
-)
+    # adopt the same energy axes used for flute and DL3 production
+    energy_axis = MapAxis.from_energy_bounds(
+        10, 1e5, nbin=20, per_decade=False, unit="GeV", name="energy"
+    )
+    energy_true_axis = MapAxis.from_energy_bounds(
+        10, 1e5, nbin=28, per_decade=False, unit="GeV", name="energy_true"
+    )
 
-# create a point-like geometry for the centre of the ON region
-target_position = SkyCoord(ra=83.63, dec=22.01, unit="deg", frame="icrs")
-on_center = PointSkyRegion(target_position)
-geom = RegionGeom.create(region=on_center, axes=[energy_axis])
+    # create a point-like geometry for the centre of the ON region
+    target_position = SkyCoord(ra=83.63, dec=22.01, unit="deg", frame="icrs")
+    on_center = PointSkyRegion(target_position)
+    geom = RegionGeom.create(region=on_center, axes=[energy_axis])
 
-# spectrum dataset and its maker
-dataset_empty = SpectrumDataset.create(
-    geom=geom, energy_axis_true=energy_true_axis
-)
-dataset_maker = SpectrumDatasetMaker(
-    containment_correction=False, selection=["counts", "exposure", "edisp"]
-)
+    # spectrum dataset and its maker
+    dataset_empty = SpectrumDataset.create(
+        geom=geom, energy_axis_true=energy_true_axis
+    )
+    dataset_maker = SpectrumDatasetMaker(
[…]

### 2022-03-07 src/figures/multi_instrument_analysis.py
added script to generate dummy multi-instrument figure

@@ -1,9 +1,11 @@
 import config
+import numpy as np
 import matplotlib.pyplot as plt
 
-figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="one-column")
-fig, ax  = plt.subplots(figsize=figsize)
+figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="single-column")
+fig, ax  = plt.subplots(1, 1, figsize=figsize.inch)
 
-
+x = np.ones(5)
+ax.plot(x, x, marker="o")
 
 fig.savefig("multi_instrument_analysis.pdf")

### 2022-03-08 src/data/multi-instrument/make.py
completed multi-instrument spectra reduction and fitting

@@ -1,0 +1,145 @@
+# reduce the MAGIC data to OGIP files for the 1D analysis
+import logging
+from pathlib import Path
+from astropy.coordinates import SkyCoord
+from regions import PointSkyRegion
+
+# gammapy imports
+from gammapy.data import DataStore
+from gammapy.maps import MapAxis
+from gammapy.maps import RegionGeom
+from gammapy.makers import (
+    SpectrumDatasetMaker,
+    WobbleRegionsFinder,
+    ReflectedRegionsBackgroundMaker,
+    SafeMaskMaker,
+)
+from gammapy.estimators import FluxPoints, FluxPointsEstimator
+from gammapy.datasets import Datasets, SpectrumDataset, FluxPointsDataset
+from gammapy.modeling import Fit
+from gammapy.modeling.models import Models, create_crab_spectral_model
+
+
+logging.basicConfig(level=logging.INFO)
+log = logging.getLogger(__name__)
+
+
+def load_fermi_datasets():
+    """Load the `MapDataset` already prepared for the Fermi-LAT data"""
+    return Datasets.read("input/data/fermi/Fermi-LAT-3FHL_datasets.yaml")
+
+
+def reduce_magic_data():
+    """Reduce the MAGIC DL3 files to `SpectrumDatasetOnOff`"""
+    data_store = DataStore.from_dir("input/data/magic")
+    observations = data_store.get_observations(required_irf=["aeff", "edisp"])
+
+    # adopt the same energy axes used for flute and DL3 production
+    energy_axis = MapAxis.from_energy_bounds(
+        10, 1e5, nbin=20, per_decade=False, unit="GeV", name="energy"
+    )
+    energy_true_axis = MapAxis.from_energy_bounds(
+        10, 1e5, nbin=28, per_decade=False, unit="GeV", name="energy_true"
+    )
+
+    # create a point-like geometry for the centre of the ON region
+    target_position = SkyCoord(ra=83.63, dec=22.01, unit="deg", frame="icrs")
+    on_center = PointSkyRegion(target_position)
+    geom = RegionGeom.create(region=on_center, axes=[energy_axis])
+
+    # spectrum dataset and its maker
+    dataset_empty = SpectrumDataset.create(geom=geom, energy_axis_true=energy_true_axis)
+    dataset_maker = SpectrumDatasetMaker(
+        containment_correction=False, selection=["counts", "exposure", "edisp"]
+    )
+
+    # background and safe mask makers
[…]

### 2022-03-08 src/data/multi-instrument/make_magic.py

@@ -1,73 +1,0 @@
-# reduce the MAGIC data to OGIP files for the 1D analysis
-import logging
-from pathlib import Path
-from astropy.coordinates import SkyCoord
-from regions import PointSkyRegion
-
-# gammapy imports
-from gammapy.data import DataStore
-from gammapy.maps import MapAxis
-from gammapy.maps import RegionGeom
-from gammapy.datasets import SpectrumDataset
-from gammapy.makers import (
-    SpectrumDatasetMaker,
-    WobbleRegionsFinder,
-    ReflectedRegionsBackgroundMaker,
-    SafeMaskMaker
-)
-logging.basicConfig(level=logging.INFO)
-log = logging.getLogger(__name__)
-
-
-def reduce_magic():
-    # reduce the MAGIC data to OGIP files
-    data_store = DataStore.from_dir("input/data/magic")
-    observations = data_store.get_observations(required_irf=["aeff", "edisp"])
-
-    # adopt the same energy axes used for flute and DL3 production
-    energy_axis = MapAxis.from_energy_bounds(
-        10, 1e5, nbin=20, per_decade=False, unit="GeV", name="energy"
-    )
-    energy_true_axis = MapAxis.from_energy_bounds(
-        10, 1e5, nbin=28, per_decade=False, unit="GeV", name="energy_true"
-    )
-
-    # create a point-like geometry for the centre of the ON region
-    target_position = SkyCoord(ra=83.63, dec=22.01, unit="deg", frame="icrs")
-    on_center = PointSkyRegion(target_position)
-    geom = RegionGeom.create(region=on_center, axes=[energy_axis])
-
-    # spectrum dataset and its maker
-    dataset_empty = SpectrumDataset.create(
-        geom=geom, energy_axis_true=energy_true_axis
-    )
-    dataset_maker = SpectrumDatasetMaker(
-        containment_correction=False, selection=["counts", "exposure", "edisp"]
-    )
-
-    # background and safe mask makers
-    region_finder = WobbleRegionsFinder(n_off_regions=1)
-    bkg_maker = ReflectedRegionsBackgroundMaker(region_finder=region_finder)
-    safe_mask_maker = SafeMaskMaker(method=["aeff-default"])
-
-    for obs in observations:
-
-        # fill the ON counts
-        dataset = dataset_maker.run(dataset_empty.copy(name=f"{obs.obs_id}"), obs)
-
[…]

### 2022-03-08 src/figures/multi_instrument_analysis.py
added plotting script to make the multi-instrument Crab Nebula plot

@@ -1,11 +1,40 @@
 import config
-import numpy as np
+import astropy.units as u
+from gammapy.estimators import FluxPoints
+from gammapy.modeling.models import Models
 import matplotlib.pyplot as plt
 
+sed_x_label = r"$E\,/\,{\rm TeV}$"
+sed_y_label = r"$E^2\,{\rm d}\phi/{\rm d}\phi\,/\,({\rm erg}\,{\rm cm}^{-2}\,{\rm s}^{-1})$"
+
 figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="single-column")
-fig, ax  = plt.subplots(1, 1, figsize=figsize.inch)
+fig, ax = plt.figure(figsize=figsize.inch)
 
-x = np.ones(5)
-ax.plot(x, x, marker="o")
+# load the flux points and plot them
+fermi_flux_points = FluxPoints.read("../data/multi-instrument/datasets/flux_points/crab_fermi_flux_points.fits")
+magic_flux_points = FluxPoints.read("../data/multi-instrument/datasets/flux_points/crab_magic_flux_points.fits")
+hawc_flux_points = FluxPoints.read("../data/multi-instrument/input/data/hawc/HAWC19_flux_points.fits")
 
+# load the best-fit model
+models = Models.read("../data/multi-instrument/results/crab_multi_instrument_fit.yaml")
+crab_lp = models["Crab Nebula"].spectral_model
+
+plot_kwargs = {
+   "energy_bounds": [0.01, 300] * u.TeV,
+   "sed_type": "e2dnde",
+   "yunits": u.Unit("erg cm-2 s-1"),
+   "xunits": u.TeV,
+}
+
+crab_lp.plot(ax=ax, ls="-", lw=1.5, color="crimson", label="joint fit", **plot_kwargs)
+crab_lp.plot_error(ax=ax, facecolor="crimson", alpha=0.4, **plot_kwargs)
+
+fermi_flux_points.plot(ax=ax, sed_type="e2dnde", color="k", label="Fermi-LAT")
+magic_flux_points.plot(ax=ax, sed_type="e2dnde", color="dodgerblue", label="MAGIC")
+hawc_flux_points.plot(ax=ax, sed_type="e2dnde", color="goldenrod", label="HAWC")
+
+ax.set_xlim(plot_kwargs["energy_bounds"])
+ax.set_xlabel(sed_x_label)
+ax.set_ylabel(sed_y_label)
[…]

### 2022-03-09 src/text/3-applications.tex
reorder applications sections
added section in the text requesting multi-insturment figure
reduced multi-instrument figure width to one column
updated subsections

@@
 
-Show some typical and advanced science cases, and refer to published papers
+Gammapy can be used for a variety of science cases by different IACT experiments.
+In this section, we show a non-exhaustive list of some typical analysis that be performed.
 
-\subsection{Computing Flux points and significance maps}
-\label{ssec:1D-3D-analysis}
-\input{3.1-std-analysis}
+\subsection{Classical spectral analysis}
+\label{ssec:1D-analysis}
+\input{3-applications-subsections/3.1-1D-analysis}
+\todo{Axel}
+A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data
 
-- standard 1D and 3D analysis
+\subsection{A 3D likelihood analysis}
+\label{ssec:1D-analysis}
+\input{3-applications-subsections/3.2-3D-analysis}
+\todo{Laura}
 
-See Figure~\ref{fig:fermi_ts_map}.
+Simulation of overlapping sources, 3D fitting, npred map, TS maps
 
+\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
 Ref:~\citep{Stewart2009}
@@
 \label{ssec:temporal-analysis}
-\input{3.2-temporal}
-lightcurves and temporal models
+\input{3-applications-subsections/3.3-temporal-analysis}
+\todo{Atreyee}
+lightcurves and temporal models using the HESS PKS2155
 
@@
 \label{ssec:multi-instrument-analysis}
+\input{3-applications-subsections/3.4-multi-instrument-analysis}
 \todo{Cosimo Nigro}
@@
 \subsection{Fitting using physical models}
-\label{ssec:naima-models-analysis}
+\label{ssec:naima-analysis}
+\input{3-applications-subsections/3.5-naima-analysis}
 \todo{Cosimo}
-\begin{figure*}[t]
-(added section in the text requesting multi-insturment figure)
 
-\end{figure}
+Figure \ref{fig:multi_instrument_analysis}. Add explanation text.
 
@@
 \todo{Quentin Remy}
-
-Talk about simulations here? Or open a new section

### 2022-03-09 src/text/3-applications.tex
reorder subsection

@@
 
-Gammapy can be used for a variety of science cases by different IACT experiments.
+Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
 In this section, we show a non-exhaustive list of some typical analysis that be performed.
@@
 \subsection{A 3D likelihood analysis}
-\label{ssec:1D-analysis}
+\label{ssec:3D-analysis}
 \input{3-applications-subsections/3.2-3D-analysis}
@@
 Ref:~\citep{Stewart2009}
+\begin{figure*}[t]
+        \centering
+        \includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
+        \caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
+\end{figure*}
 

### 2022-03-09 src/text/3-applications-subsections/1D-analysis.tex
Adapt filenames and input commands

--- 2022-03-07 src/text/3-applications.tex
@@
-\section{Applications}
-\label{sec:applications}
+\subsection{Classical spectral analysis}
+\label{ssec:1D-analysis}
+\todo{Axel}
+A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data
 
-Show some typical and advanced science cases, and refer to published papers
-
-\subsection{Computing Flux points and significance maps}
-\label{ssec:1D-3D-analysis}
-\input{3.1-std-analysis}
-
-- standard 1D and 3D analysis
-
-See Figure~\ref{fig:fermi_ts_map}.
-
-Ref:~\citep{Stewart2009}
-
-\subsection{Temporal analysis}
-\label{ssec:temporal-analysis}
-\input{3.2-temporal}
-lightcurves and temporal models
-
-\subsection{Multi instrument analysis}
-\label{ssec:multi-instrument-analysis}
-\todo{Cosimo Nigro}
-\begin{figure}[t]
+\begin{figure*}[t]
 	\centering
-	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
-	\caption{A multi-instrument analysis of the Crab Nebula}
-	\label{fig:multi_instrument_analysis} 
+	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
+	\caption{CTA Galactic Center example}
+	\label{fig:cta_galactic_center}
 \end{figure*}
-
-\subsection{Fitting using physical models}
-\label{ssec:naima-models-analysis}
-\todo{Cosimo}
-\begin{figure*}[t]
-(added section in the text requesting multi-insturment figure)
-
-\end{figure}
-
-\subsection{Population studies}
-\label{ssec:population-studies}
-\todo{Quentin Remy}
-
-Talk about simulations here? Or open a new section

### 2022-03-09 src/text/3-applications-subsections/3D-analysis.tex
Adapt filenames and input commands

--- 2022-03-07 src/text/3-applications.tex
@@
-\section{Applications}
-\label{sec:applications}
+\subsection{A 3D likelihood analysis}
+\label{ssec:3D-analysis}
 
-Show some typical and advanced science cases, and refer to published papers
+\todo{Laura}
 
-\subsection{Computing Flux points and significance maps}
-\label{ssec:1D-3D-analysis}
-\input{3.1-std-analysis}
+Simulation of overlapping sources, 3D fitting, npred map, TS maps
 
-- standard 1D and 3D analysis
-
-See Figure~\ref{fig:fermi_ts_map}.
-
+\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
 Ref:~\citep{Stewart2009}
-
-\subsection{Temporal analysis}
-\label{ssec:temporal-analysis}
-\input{3.2-temporal}
-lightcurves and temporal models
-
-\subsection{Multi instrument analysis}
-\label{ssec:multi-instrument-analysis}
-\todo{Cosimo Nigro}
-\begin{figure}[t]
+\begin{figure*}[t]
         \centering
-	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
-	\caption{A multi-instrument analysis of the Crab Nebula}
-	\label{fig:multi_instrument_analysis} 
+        \includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
+        \caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
 \end{figure*}
-
-\subsection{Fitting using physical models}
-\label{ssec:naima-models-analysis}
-\todo{Cosimo}
-\begin{figure*}[t]
-(added section in the text requesting multi-insturment figure)
-
-\end{figure}
-
-\subsection{Population studies}
-\label{ssec:population-studies}
-\todo{Quentin Remy}
-
-Talk about simulations here? Or open a new section

### 2022-03-09 src/text/3-applications-subsections/multi-instrument-analysis.tex
Adapt filenames and input commands

--- 2022-03-07 src/text/3-applications.tex
@@
-\section{Applications}
-\label{sec:applications}
-
-Show some typical and advanced science cases, and refer to published papers
-
-\subsection{Computing Flux points and significance maps}
-\label{ssec:1D-3D-analysis}
-\input{3.1-std-analysis}
-
-- standard 1D and 3D analysis
-
-See Figure~\ref{fig:fermi_ts_map}.
-
-Ref:~\citep{Stewart2009}
-
-\subsection{Temporal analysis}
-\label{ssec:temporal-analysis}
-\input{3.2-temporal}
-lightcurves and temporal models
-
 \subsection{Multi instrument analysis}
@@
 \todo{Cosimo Nigro}
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
+
+\begin{figure*}[t]
+	\sidecaption
+	\includegraphics[width=0.666\textwidth]{figures/multi_instrument_analysis.pdf}
 	\caption{A multi-instrument analysis of the Crab Nebula}
@@
 \end{figure*}
-
-\subsection{Fitting using physical models}
-\label{ssec:naima-models-analysis}
-\todo{Cosimo}
-\begin{figure*}[t]
-(added section in the text requesting multi-insturment figure)
-
-\end{figure}
-
-\subsection{Population studies}
-\label{ssec:population-studies}
-\todo{Quentin Remy}
-
-Talk about simulations here? Or open a new section

### 2022-03-09 src/text/3-applications-subsections/population-studies.tex
Adapt filenames and input commands

--- 2022-03-07 src/text/3-applications.tex
@@
-\section{Applications}
-\label{sec:applications}
-
-Show some typical and advanced science cases, and refer to published papers
-
-\subsection{Computing Flux points and significance maps}
-\label{ssec:1D-3D-analysis}
-\input{3.1-std-analysis}
-
-- standard 1D and 3D analysis
-
-See Figure~\ref{fig:fermi_ts_map}.
-
-Ref:~\citep{Stewart2009}
-
-\subsection{Temporal analysis}
-\label{ssec:temporal-analysis}
-\input{3.2-temporal}
-lightcurves and temporal models
-
-\subsection{Multi instrument analysis}
-\label{ssec:multi-instrument-analysis}
-\todo{Cosimo Nigro}
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
-	\caption{A multi-instrument analysis of the Crab Nebula}
-	\label{fig:multi_instrument_analysis} 
-\end{figure*}
-
-\subsection{Fitting using physical models}
-\label{ssec:naima-models-analysis}
-\todo{Cosimo}
-\begin{figure*}[t]
-(added section in the text requesting multi-insturment figure)
-
-\end{figure}
-
 \subsection{Population studies}

### 2022-03-09 src/text/3-applications-subsections/temporal-analysis.tex
Adapt filenames and input commands

\subsection{Temporal analysis}
\label{ssec:temporal-analysis}
\todo{Atreyee}

Lightcurve in two energy bands (600 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) for
PKS2155-304 flare seen by H.E.S.S. as in our notebooks.

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/hess_lightcurve_pks.pdf}
	\caption{
		H.E.S.S. PKS~2155-304 flare in two energy bands}
	\label{fig:hess_lightcurve_pks}
\end{figure*}

### 2022-03-09 src/text/3-applications.tex
Adapt filenames and input commands

--- 2022-03-07 src/text/3-applications.tex
@@
 
-Show some typical and advanced science cases, and refer to published papers
+Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
+In this section, we show a non-exhaustive list of some typical analysis that can be performed.
+In general from the \gammapy side there is not limitation on which kind of analysis can be
+done with wich instrument, however in practice it is limited by the availability of public data.
 
-\subsection{Computing Flux points and significance maps}
-\label{ssec:1D-3D-analysis}
-\input{3.1-std-analysis}
-
-- standard 1D and 3D analysis
-
-See Figure~\ref{fig:fermi_ts_map}.
-
-Ref:~\citep{Stewart2009}
-
-\subsection{Temporal analysis}
-\label{ssec:temporal-analysis}
-\input{3.2-temporal}
-lightcurves and temporal models
-
-\subsection{Multi instrument analysis}
-\label{ssec:multi-instrument-analysis}
-\todo{Cosimo Nigro}
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
-	\caption{A multi-instrument analysis of the Crab Nebula}
-	\label{fig:multi_instrument_analysis} 
-\end{figure*}
-
-\subsection{Fitting using physical models}
-\label{ssec:naima-models-analysis}
-\todo{Cosimo}
-\begin{figure*}[t]
-(added section in the text requesting multi-insturment figure)
-
-\end{figure}
-
-\subsection{Population studies}
-\label{ssec:population-studies}
-\todo{Quentin Remy}
-
-Talk about simulations here? Or open a new section
+\input{text/3-applications-subsections/1D-analysis}
+\input{text/3-applications-subsections/3D-analysis}
+\input{text/3-applications-subsections/temporal-analysis}
+\input{text/3-applications-subsections/multi-instrument-analysis}
+\input{text/3-applications-subsections/sed-modelling-analysis}
+\input{text/3-applications-subsections/population-studies}

### 2022-03-09 src/text/1-introduction.tex
Fix pre commit hooks

@@
 		simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT data, hopefully it
-		will also be applied to e.g. VERITAS, MAGIC or HAWC data in the future. }
+		will also be applied to e.g., VERITAS, MAGIC or HAWC data in the future. }
 	\label{fig:big-picture}

### 2022-03-09 src/text/2-package-subsections/catalog.tex
fix test fails
Fix pre commit hooks

@@
 
-Comprehensive source catalogs are increasingly being provided by many high energy astrophysics experiments.
-gammapy.catalog provides a convenient access to some common gamma-ray catalogs.
-A global catalog table is provided, along with source models flux points and light curves (if available) for individual objects, which are internally created from the supplied FITS tables.
-This module works independently from the rest of teh package, and the required catalogs are supplied in GAMMAPY_DATA.
-Presently, catalogs from Fermi-LAT (standard \citep{3FGL, 4FGL} and high energy \citep{2FHL, 3FHL}), H.E.S.S.
-galactic plane survey \citep{HGPS}, HAWC \citep{2HWC, 3HWC} and gamma-cat (\citep{gamma-cat}; an open source gamma ray catalog combining information from multiple catalogs) are supported.
+Comprehensive source catalogs are increasingly being provided by many high
+energy astrophysics experiments. gammapy.catalog provides a convenient access
+to some common gamma-ray catalogs. A global catalog table is provided, along
+with source models flux points and light curves (if available) for individual
+objects, which are internally created from the supplied FITS tables. This
+module works independently from the rest of the package, and the required
+catalogs are supplied in GAMMAPY\_DATA. Presently, catalogs from Fermi-LAT
+(standard~\citep{3FGL, 4FGL} and high energy~\citep{2FHL, 3FHL}), H.E.S.S.
+galactic plane survey~\citep{HGPS}, HAWC~\citep{2HWC, 3HWC} and gamma-cat
+~\citep{gamma-cat}; an open source gamma ray catalog combining information from
+multiple catalogs) are supported.
 
@@
 	\import{code-examples/generated/}{gp_catalogs}
-	\caption{Using gammapy.catalogs: Accessing underlying model, flux points and lightcurve from the Fermi-LAT 4FGL catalog for the blazar PKS 2155-304}
-	\label{codeexample:data}
-\end{figure}
+	\caption{Using gammapy.catalogs: Accessing underlying model, flux points and
+		lightcurve from the Fermi-LAT 4FGL catalog for the blazar PKS 2155-304}
+	\label{codeexample:data} \end{figure}

### 2022-03-09 src/text/2-package-subsections/datasets.tex
Fix pre commit hooks

@@
 using chi2 statistics. Multiple datasets of same or different types can be
-bundled together in Datasets (e.g.: Figure \ref{fig*:minted:gp_datasets}),
+bundled together in Datasets (e.g., Figure \ref{fig*:minted:gp_datasets}),
 where the likelihood from each constituent member is added, thus facilitating

### 2022-03-09 src/text/2-package-subsections/modeling.tex
Fix footnote
Fix pre commit hooks

@@
 
-The Fit class provides methods to fit, i.e. optimise parameters and estimate
+The Fit class provides methods to fit i.e., optimise parameters and estimate
 parameter errors and correlations. It interfaces with a Datasets object, which
@@
 Parameters object.  Models can be unique for a given dataset, or contribute to
-multiple datasets and thus provide links, allowing e.g. to do a joint fit to
+multiple datasets and thus provide links, allowing e.g., to do a joint fit to
 multiple IACT datasets, or to a joint IACT and \textit{Fermi}-LAT dataset. Many
@@
 \footnote{a prototype is available in gammapy-recipes,
-
-	\url(https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html)}
+	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
+}

### 2022-03-09 src/text/3-applications-subsections/sed-modelling-analysis.tex
Fix pre commit hooks

\subsection{Broadband SED Modeling}
\label{ssec:broadband-sed-modeling}

Figure \ref{fig:multi_instrument_analysis}. Add explanation text.

### 2022-03-09 src/text/3-applications.tex
Fix pre commit hooks

@@
 
-Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
-In this section, we show a non-exhaustive list of some typical analysis that can be performed.
-In general from the \gammapy side there is not limitation on which kind of analysis can be
-done with wich instrument, however in practice it is limited by the availability of public data.
+Gammapy can be used for a variety of science cases by different IACT
+experiments. (Refer to publications) In this section, we show a non-exhaustive
+list of some typical analysis that can be performed. In general from the
+\gammapy side there is not limitation on which kind of analysis can be done
+with which instrument, however in practice it is limited by the availability of
+public data.
 

### 2022-03-12 src/text/3-applications-subsections/1D-analysis.tex
Fix pre commit hooks
Add some draft text for the 1D analysis example

@@
-\subsection{Classical spectral analysis}
-\label{ssec:1D-analysis}
+\subsection{1D Analysis}
+\label{ssec:1d-analysis}
 \todo{Axel}
-A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data
+One of the most common analysis cases in gamma-ray astronomy is measuring the
+spectrum of a source in a given region defined on the sky, in conventional
+astronomy also called aperture photometry.
+The spectrum is typically measured in two steps: first a parametric
+spectral model is fitted to the data and secondly flux points are computed
+in a pre-defined set of energy bins.
+The result of such an analysis performed on three simulated CTA observations
+is shown in Fig.~\ref{fig:cta_galactic_center}.
+In this case the spectrum was measured in a circular aperture centered
+on the Galactic Center, in \gammaray~astronomy often called "on region".
+For such analysis the users first chooses a region of interest
+and energy binning, both defined by a `RegionGeom`.
+In a second step the events and instrument response are binned into
+maps of this geometry, by the `SpectrumDatasetMaker`.
+All the data and reduced instrument response are bundled into a
+`SpectrumDataset`.
+To estimate the expected background in the on region a "reflected regions"
+background method was used~\cite{Berge07}, represented in \gammapy
+by the `ReflectedRegionsBackgroundMaker` class.
+The resulting reflected regions are illustrated for all three observations
+on top of the map of counts.
+After reduction of the data it was modelled using a forward-folding
+method and a power-law spectral shape, using the `PowerLawSpectralModel`
+and `Fit` class.
+Based on this best fit model the final flux points and
+corresponding log-likleihood profiles are computed using
+the `FluxPointsEstimator`.
 
@@
 	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
-	\caption{CTA Galactic Center example}
+	\caption{
+        Example spectral analysis of the Galactic Center for three simulated CTA observations.
+        The left image shows the maps of counts with the measurement region and background
+        regions overlaid in different colors. The right image shows the resulting spectral
+        points and their corresponding log-likelihood profiles.
+    }
 	\label{fig:cta_galactic_center}

### 2022-03-21 src/text/2-package-subsections/stats.tex
First addition

@@
 Statistics methods
+
+In Gammapy, the fit statistics are log-likelihood functions normalized like chi-squares,
+i.e. they follow the expression $2 \times log L$, where $L$ is the likelihood function used.
+To account for the event nature of gamma-ray data, the likelihood functions implemented
+in Gammapy for Poisson distribution the Cash

### 2022-03-21 src/text/3-applications-subsections/multi-instrument-analysis.tex
Fix pre commit hooks
added text for the section on the multi-instrument application

@@
 \label{ssec:multi-instrument-analysis}
-\todo{Cosimo Nigro}
 
@@
 	\caption{A multi-instrument analysis of the Crab Nebula}
-	\label{fig:multi_instrument_analysis}
+	multi_instrument_analysismulti_instrument_analysis}
 \end{figure*}
+
+%% should we mention the joint-crab here or in the intro, where we talk about
+%% DL3, multi-instrument analysis and so forth...
+%% cite Laura's DL3 HAWC paper with the updated version of the joint-crab spectrum?
+
+In this multi-instrument analysis example we showcase the capabilities of \gammapy
+to perform a simultaneous likelihood fit incorporating data from different instruments
+and at different levels of reduction.
+We estimate the spectrum of the Crab Nebula combining data from \fermi, \magic and \hawc.
+Maps of \fermi data are prepared selecting a region of $X^{\rm deg}$ around the
+position of the Crab Nebula applying the same selection criteria of the 3FHL
+catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$, \citalt{3FHL}).
+%% shall we explain exactly which type of Map is created?
+The \MAGIC data are two observations of $20\,{\rm min}$ each, chosen from the
+dataset used to estimate the performance of the upgraded stereo system \citep{magic_performance}
+and already included in \cite{joint_crab}. The observations were taken at small
+zenith angles ($<30^{\circ}$) in wobble mode \citep{fomin_1994}, with the source
+sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy range spans
+$80\,{\rm GeV} -- 20\,{\rm TeV}$. They are reduced to ON/OFF dataset before being fitted.
+\hawc flux points data are estimated in \cite{hawc_crab_2019} with $2.5\,{\rm years}$
+of data and span an energy range $300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.
+
+\gammapy automatically generates a likelihood including three different types of
+terms. Two poissonian likelihoods: one for the \fermi map and one for the ON/OFF
+counts, and a $\Chi^2$ accounting for the flux points. For \fermi, a
+a three-dimensional forward folding of the sky model with the IRF is performed,
+in order to compute the predicted counts in each sky-coordinate and energy bin.
+For \magic, a one-dimensional forward folding of the spectral model with the IRF
+is performed to predict the counts in each estimated energy bin.
+A log parabola is fitted to the almost fived decades in energy $10\,{\rm GeV} -- 300\,{\rm TeV}$.
+%% is the LP formula specified elsewhere?
+
+The result of the joint fit is displayed in Fig.~\ref{multi_instrument_analysis}.
+We remark that the objective of this exercise is to show the interoperability of data
+
+%% eventual part for physical modelling with naima

### 2022-03-21 src/text/3-applications-subsections/multi-instrument-analysis.tex
added disclaimer about the spectral measurement

@@
 The result of the joint fit is displayed in Fig.~\ref{multi_instrument_analysis}.
-We remark that the objective of this exercise is to show the interoperability of data
+We remark that the objective of this exercise is illsutrative, we display the
+flexibility of \gammapy in simultaneously fitting multi-isntrument data even at
+different levels of reduction, we do not aim to privide a new measurement of the
+Crab Nebula spectrum.
 

### 2022-03-21 src/text/3-applications-subsections/multi-instrument-analysis.tex
fixed errors preventing compilation

--- 2022-03-21 src/text/3-applications-subsections/multi-instrument-analysis.tex
@@
 	\caption{A multi-instrument analysis of the Crab Nebula}
-	multi_instrument_analysismulti_instrument_analysis}
+	\label{fig:multi_instrument_analysismulti_instrument_analysis}
 \end{figure*}
@@
 We estimate the spectrum of the Crab Nebula combining data from \fermi, \magic and \hawc.
-Maps of \fermi data are prepared selecting a region of $X^{\rm deg}$ around the
+Maps of \fermi data are prepared selecting a region of $X^{\circ}$ around the
 position of the Crab Nebula applying the same selection criteria of the 3FHL
-catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$, \citalt{3FHL}).
+catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$, \citealt{3FHL}).
 %% shall we explain exactly which type of Map is created?
-The \MAGIC data are two observations of $20\,{\rm min}$ each, chosen from the
+The \magic data are two observations of $20\,{\rm min}$ each, chosen from the
 dataset used to estimate the performance of the upgraded stereo system \citep{magic_performance}
@@
 terms. Two poissonian likelihoods: one for the \fermi map and one for the ON/OFF
-counts, and a $\Chi^2$ accounting for the flux points. For \fermi, a
+counts, and a $\chi^2$ accounting for the flux points. For \fermi, a
 a three-dimensional forward folding of the sky model with the IRF is performed,
@@
 The result of the joint fit is displayed in Fig.~\ref{multi_instrument_analysis}.
-We remark that the objective of this exercise is to show the interoperability of data
+We remark that the objective of this exercise is illustrative, we display the
+flexibility of \gammapy in simultaneously fitting multi-isntrument data even at
+different levels of reduction, we do not aim to provide a new measurement of the
+Crab Nebula spectrum.
 

### 2022-03-21 src/text/6-acknowledgements.tex
Reformat tex files

@@
 	We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
-\texttt{Matplotlib} communities for providing their packages which are invaluable
-to the development of Astropy. We thank the GitHub team for providing us with
-an excellent free development platform. We also are grateful to Read the Docs
-(\ReadthedocsUrl), and Travis
-(\TravisUrl) for providing free documentation
-hosting and testing respectively. Finally, we would like to thank all the
-Gammapy users that have provided feedback and submitted bug reports.
+	\texttt{Matplotlib} communities for providing their packages which are
+	invaluable to the development of Astropy. We thank the GitHub team for
+	providing us with an excellent free development platform. We also are grateful
+	to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
+	documentation hosting and testing respectively. Finally, we would like to thank
+	all the Gammapy users that have provided feedback and submitted bug reports.
 
-TODO: copy over stuff from \url{http://docs.gammapy.org/en/latest/about.html#thanks}.
+	TODO: copy over stuff from
+	\url{http://docs.gammapy.org/en/latest/about.html#thanks}.
+
 	TODO: add the ANR for Luca (and Atreyee in LUPM?)
 
+	J.E.
+Ruiz acknowledges financial support from the State Agency for Research of the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709)
+
 \end{acknowledgements}

### 2022-03-23 src/text/2-package-subsections/stats.tex
Added ref

--- 2022-01-31 src/text/2-package-subsections/stats.tex
@@
 \todo{Regis Terrier}
-Statistics methods
+
+The gammapy.stats subpackage contains the fit statistics and associated statistical estimators
+that are commonly used in gamma-ray astronomy.
+In general, gamma-ray observations count Poisson-distributed events at various sky positions,
+and contain both signal and background events. Estimation of the number of signal events is done
+through likelihood maximization. In Gammapy, the fit statistics are Poisson log-likelihood functions
+normalized like chi-squares, i.e. they follow the expression $2 \times log L$, where $L$ is the
+likelihood function used.
+
+The statistic function used when the expected number of background events is known
+is \emph{Cash}. It used When the number of background events is unknown, one has to
+use a background estimate :math:`n_{bkg}` taken from an off measurement where only background events
+are expected. In this case, the statistic function is ``WStat`` (see :ref:`wstat`).

### 2022-03-23 src/text/2-package-subsections/stats.tex
Add wstat

@@
 likelihood function used.
-
 The statistic function used when the expected number of background events is known
-is \emph{Cash}. It used When the number of background events is unknown, one has to
-use a background estimate :math:`n_{bkg}` taken from an off measurement where only background events
-are expected. In this case, the statistic function is ``WStat`` (see :ref:`wstat`).
+is the \emph{Cash} statistic ~\citep{Cash}. It is used by datasets using background
+templates such as the MapDataset. When the number of background events is unknown and
+an off measurement where only background events are expected is used, the statistic function
+is WStat. It is a profile log-likelihood statistic where background counts are
+marginalized parameters. It is used by datasets containing off counts measurements
+such as the SpectrumDatasetOnOff, used for classical spectral analysis.

### 2022-03-23 src/text/2-package-subsections/stats.tex
[skip ci] Add counts statisitics

@@
 such as the SpectrumDatasetOnOff, used for classical spectral analysis.
+
+To perform simple statistical estimations on counts measurements, CountsStatistic classes
+encapsulate the aforementioned statistic functions to measure excess counts and estimate the
+associated statistical significance, errors and upper limits. They perform maximum likelihood
+ratio tests to estimate significance (the square root of the statistic difference) and compute
+likelihood profiles to measure errors and upper limits. The following example allows to compute
+the Li \& Ma significance~\citep{LiMa} of a set of measurements:

### 2022-03-23 src/code-examples/snippets/gp_stats.py
Add code example

@@ -1,0 +1,11 @@
+from gammapy.stats import WStatCountsStatistic
+
+n_on = [13, 5, 3]
+n_off = [11, 9, 20]
+alpha = [0.8, 0.5, 0.1]
+stat = WStatCountsStatistic(n_on=13, n_off=11, alpha=1. / 2)
+print(f"Excess  : {stat.n_sig:.2f}")
+print(f"sqrt(TS): {stat.sqrt_ts:.2f}")
+print(f"Errors (1 sigma): {stat.compute_errn(1.):.2f} -- {stat.compute_errp(1.):.2f}")
+print(f"Errors (2 sigma): {stat.compute_errn(2.):.2f} -- {stat.compute_errp(2.):.2f}")
+

### 2022-03-23 src/code-examples/snippets/gp_stats.py
cleaner snippet

@@ -3,9 +3,12 @@ from gammapy.stats import WStatCountsStatistic
 n_on = [13, 5, 3]
 n_off = [11, 9, 20]
 alpha = [0.8, 0.5, 0.1]
-stat = WStatCountsStatistic(n_on=13, n_off=11, alpha=1. / 2)
-print(f"Excess  : {stat.n_sig:.2f}")
-print(f"sqrt(TS): {stat.sqrt_ts:.2f}")
-print(f"Errors (1 sigma): {stat.compute_errn(1.):.2f} -- {stat.compute_errp(1.):.2f}")
-print(f"Errors (2 sigma): {stat.compute_errn(2.):.2f} -- {stat.compute_errp(2.):.2f}")
+stat = WStatCountsStatistic(n_on, n_off, alpha)
+# Excess
+stat.n_sig
+# Significance
+stat.sqrt_ts
+# Asymmetrical rrors
+stat.compute_errn(1.)
+stat.compute_errp(1.)
 

### 2022-03-23 src/text/2-package.tex
Changed subsection order and add label in datasets
add maps section
Run tex indentation
Fix input references
First addition of workflow part

@@
 \label{sec:analysis-workflow-overview}
+\todo{Regis and Fabio F.}
+
+\subsection{Data access and selection (DL3)}
+
+The analysis of gamma-ray data with Gammapy starts at the Data Level 3 where the data consists
+in lists of gamma-like events and their corresponding instrument response functions (IRFs).
+The latter include effective area, point spread function (PSF), energy dispersion and
+residual hadronic background. In addition there is associated meta data including information
+on the observation such as pointing direction, observation time and observation conditions.
+
+\subsection{Data reduction (DL3 to DL4)}
+
+In the next stage of the analysis the user selects a coordinates system, region or
+energy binning and events are binned into multidimensional data structures (maps)
+with the selected geometry. The instrument response is projected onto the
+same geometry as well. At this stage users can select additional background
+estimation methods, such as ring background or reflected regions and
+exclude parts of the data with high associated IRF systematics by defining
+a "safe" data range. The counts data and the reduced IRFs are bundled into
+datasets. Those datasets can be optionally grouped and stacked and are
+typically written to disk to allow users to read them back at any time later
+for modeling and fitting.
 
@@
 		Gammapy sub-package structure and data analysis workflow. }
-	\label{fig:data_flow}
-\end{figure*}
+	\label{fig:data_flow} \end{figure*}
 
@@
 
-\todo{How to sort the sub-packages? After data flow or alphabetically?}
+\todo{How to sort the sub-packages? After data flow or alphabetically? What
+	about maps?}
+\input{text/2-package-subsections/data}
+\input{text/2-package-subsections/irf}
+\input{text/2-package-subsections/maps}
+\input{text/2-package-subsections/makers}
+\input{text/2-package-subsections/datasets}
+\input{text/2-package-subsections/modeling}
+\input{text/2-package-subsections/stats}
+\input{text/2-package-subsections/estimators}
 \input{text/2-package-subsections/analysis}
+\input{text/2-package-subsections/visualisation}
 \input{text/2-package-subsections/astro}
 \input{text/2-package-subsections/catalog}
-\input{text/2-package-subsections/data}
-\input{text/2-package-subsections/datasets}
-\input{text/2-package-subsections/estimators}
-\input{text/2-package-subsections/irf}
-\input{text/2-package-subsections/makers}
-\input{text/2-package-subsections/modeling}
-\input{text/2-package-subsections/stats}
 \input{text/2-package-subsections/utils}
-\input{text/2-package-subsections/visualisation}

### 2022-03-23 src/text/2-package.tex
Second addition of workflow part

@@
 for modeling and fitting.
+
+\subsection{Datasets (DL4)}
+
+The datasets classes bundle reduced data in form of maps, reduced IRFs, models and
+fit statistics. Different sub-classes support different analysis methods
+and fit statistics (e.g. Poisson statistics with known background or
+with OFF background measurements). The datasets are used to perform joint-likelihood
+fitting allowing to combine different measurements, e.g. from different observations
+but also from different instruments or event classes. They can also be used for binned
+simulation as well as event sampling to simulate DL3 events data.
+
+\subsection{Modeling and Fitting (DL4 to DL5)}
+
+The next step is then typically to model and fit the datasets, either
+individually, or in a joint likelihood analysis. For this purpose Gammapy
+provides a uniform interface to multiple fitting backends. It also provides
+a variety of :ref:`built in models <model-gallery>`. This includes spectral,
+spatial and temporal model classes to describe the gamma-ray emission in the sky.
+Independently or subsequently to the global modelling, the data can be
+re-grouped to compute flux points, light curves and flux as well as significance
+maps in energy bands.
 

### 2022-03-24 src/text/3-applications-subsections/3D-analysis.tex
Fix pre commit hooks
start draft of 3d analysis section

@@
-\subsection{A 3D likelihood analysis}
-\label{ssec:3D-analysis}
+\subsection{3D Analysis}
+\label{ssec:3d-analysis}
+\todo{Laura}
+The 1D analysis approach is a powerful tool to measure the spectrum of an isolated source.
+However, more complicated situations, such as field of views containing several overlapping sources, can no longer be treated this way.
+Since it is based on integration over a region, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region.
+Similarly, sources with extended or complex morphology can result in the measured flux being underestimated, and heavily dependent on the choice of extraction region.
 
-\todo{Laura}
+For such situations a more complex approach is needed, the so-called 3D analysis.
+The three relevant dimensions are the two spatial angular coordinates and an energy axis.
+In this framework, a combined spatial and spectral model (that is, a SkyModel, see Section~\ref{ssec:gammapy-modeling}) is fitted to the sky-maps that were previously derived from the data and bundled into a MapDataset (see Sections~\ref{ssec:gammapy-makers,ssec:gammapy-datasets}).
 
-Simulation of overlapping sources, 3D fitting, npred map, TS maps
+Starting from the \irfs corresponding to the same three simulated \cta observations used in Section~\ref{ssec:1d-analysis}, we can create a MapDataset via the MapDatasetMaker.
+However, we will not use the simulated event lists provided by \cta but instead, use the method MapDataset.fake() to simulate measured counts from the combination of several SkyModel instances.
+In particular we simulate:
+\begin{enumerate}
+	\item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law spectral shape.
+	\item An extended source with Gaussian morphology located at (l=0.4\textdegree, b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log-parabola spectral shape.
+	\item A large shell-like structure centered around (l=0.06\textdegree, b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree respectively and a power-law spectral shape.
+\end{enumerate}
+The position and sizes of the sources have been selected so that their contributions overlap.
+This can be clearly seen in the significance map shown in the left panel of Figure \todo{X}.
+This map was produced with the ExcessMapEstimator (see Section~\ref{ssec:gammapy-estimators}) with a correlation radius of 0.1\textdegree.
 
-\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
-Ref:~\citep{Stewart2009}
-\begin{figure*}[t]
-        \centering
-        \includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
-        \caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
-\end{figure*}
+We can now fit the same model shapes to the simulated data and retrieve the best-fit parameters, which are in all cases well within 1$\sigma$ of the simulated parameters.
+We can now compute the residual significance map after removing the contribution from each model.
+This is done again via the ExcessMapEstimator.
+As can be seen in Figure \todo{X}, there are no regions above or below 5$\sigma$.
+
+As the example above shows, the 3D analysis allows to characterize the morphology of the emission and fit it together with the spectral properties of the source.
+Among the advantages that this provides is the fact that this allows to disentangle the contribution from overlapping sources to the same spatial region.
+To highlight this, we define a circular RegionGeom of radius 0.5\textdegree centered around the position of the point source.
+We can now compare the measured excess counts integrated in that region to the relative contribution from each of the three source models.
+This can be seen in Figure~\todo{X}.
+
+%
+%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
+%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering
+%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
+%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
+%\end{figure*}

### 2022-03-24 src/text/3-applications-subsections/3D-analysis.tex
some rephrasing

@@
 The 1D analysis approach is a powerful tool to measure the spectrum of an isolated source.
-However, more complicated situations, such as field of views containing several overlapping sources, can no longer be treated this way.
-Since it is based on integration over a region, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region.
+However, more complicated situations, such as field of views containing several overlapping sources, require a more careful treatment.
+Because it is based on integration over a region, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region.
 Similarly, sources with extended or complex morphology can result in the measured flux being underestimated, and heavily dependent on the choice of extraction region.
@@
 As the example above shows, the 3D analysis allows to characterize the morphology of the emission and fit it together with the spectral properties of the source.
-Among the advantages that this provides is the fact that this allows to disentangle the contribution from overlapping sources to the same spatial region.
+Among the advantages that this provides is the ability to disentangle the contribution from overlapping sources to the same spatial region.
 To highlight this, we define a circular RegionGeom of radius 0.5\textdegree centered around the position of the point source.
-We can now compare the measured excess counts integrated in that region to the relative contribution from each of the three source models.
+We can now compare the measured excess counts integrated in that region to the expected relative contribution from each of the three source models.
 This can be seen in Figure~\todo{X}.

### 2022-03-26 src/text/4-project.tex
add table and figures to tex file
add generated codestats table to .gitignore
make dir tables if does not exist
move latex table to tables/generated
add rule codestats
remove files figure
Run pre-commit
Run tex indentation
add organizational structure

--- 2022-01-25 src/text/4-project.tex
@@
 \section{Gammapy project}
-\label{sec:project}
+\label{sec:gammapy-project}
 
-Open development, roadmap, communities,
-science tool aspect
-Infrastructure etc.
+In this section, we provide an overview of the organization of the Gammapy project.
+We briefly describe the main roles and responsibilities, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality open source software.
+We also describe how we tackle with the software distribution, our solution for a versioned thoroughly tested documentation in the form of user-friendly playable recipes, and the tools we use to foster the Gammapy community and to provide user support.
+This section concludes with an outlook on the roadmap for future directions.
 
-community driven vs. institutional driven
+\subsection{Organizational structure}
+\label{ssec:organizational-structure}
 
-Validation and benchmarks?
-Validation as online appendix...
+Gammapy is a well-organised international open-source project with a broad developer base and the presence of commitments from strong groups and institutes in the very high-energies astrophysics domain \footnote{\url{https://gammapy.org/team.html}}.
+The main development roadmaps are discussed and validated by a Coordination Committee, composed of representatives of the main contributing laboratories.
+This committee is chaired by a Project Manager and his deputy while two Lead Developers manage the development strategy and organise technical activities.
+Because of this institutionally driven characteristic, the permanent staff and commitment of supporting institutes ensure the continuity of the executive teams.
+A core team of developers from the contributing laboratories is in charge of the regular development, which benefits from punctual contributions of the community at large.
 
-\subsection{Development, testing}
+\subsection{Technical infrastructure}
+\label{ssec:technical-infrastructure}
 
-\todo{Jose Enrique writes this...}
--Github, pytest, CI, PIGs?
+\begin{itemize}
+	\item GitHub repositories 
+	\begin{itemize}
+		\item gammapy (describe gammapy codebase)
+		\item docs
+		\item web
+		\item data
+		\item benchmarks
+		\item recipes
+		\item extra
+		\item meetings
+		\item conferences contributions
+		\item catalogs? (i.e. gamma-cat)
+		\item paper
+	\end{itemize}
+	\item github actions and automated tasks 
+	\begin{itemize}
+		\item ci
+		\item docs
+		\item benchmarks-slack
+		\item codemeta.json and zenodo
+		\item release-web
+	\end{itemize}	
+	\item pytest and code coverage in ci
+	\item tests on docstrings and on code in rst files
+	\item code quality services (codecov, lgtm, codacy)
+	\item validation and benchmarks -validation as online appendix...?
+\end{itemize}
+
+\begin{table}
+	\import{tables/generated/}{codestats}
+	\caption{Coding languages statistics in Gammapy project}
+	\label{table:codestats:data}
+\end{table}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/codestats.pdf}
+	\caption{
+		Percentage of lines of code in Gammapy project} \label{fig:codestats:lang}
+\end{figure}
+
+\subsection{Software distribution}
+\label{ssec:software-distribution}
+
+\begin{itemize}
+	\item pip, conda, versions
+	\item gammapy download
+	\item automated release process with Zenodo publishing linking
+	\item escape 2020 software platform
+	\item ascl
+\end{itemize}
 
 \subsection{Documentation}
+\label{ssec:documentation}
 
-- Notebooks
+\begin{itemize}
+	\item rst, sphinx, api
+	\item versioned notebooks building and testing
+	\item versioned binder
+\end{itemize}
 
-\subsection{Software distribution and user support}
-
-- Pip, conda, versions, gammapy download
-
-\subsection{Community}
-
-TODO: Figure: Screenshot of Jupyter notebook or docs with notebook, could show the interactive maps view
+Figure: Screenshot of Jupyter notebook or docs with notebook, could show the interactive maps view
 \begin{verbatim}
@@
 \end{verbatim}
+
+\subsection{Community and user-support}
+\label{ssec:community-and-user-support}
+
+\begin{itemize}
+	\item weekly developers calls
+	\item coding sprints 
+	\item slack
+	\item github discussions
+	\item gammapy recipes repo
+	\item mailing lists 
+		\begin{verbatim}
+		gammapy-coordination-l@in2p3.fr 
+		gammapy@googlegroups.com 
+		gammapy-cta-l@in2p3.fr
+		\end{verbatim}
+	\item twitter
+\end{itemize}
+
+\subsection{Roadmap}
+\label{ssec:roadmap}
+\todo{Axel, Regis}
+
+\begin{itemize}
+	\item pigs
+	\item roadmap
+\end{itemize}

### 2022-03-28 src/text/2-package-subsections/analysis.tex
analysis submodule text

@@
 \label{ssec:gammapy-analysis}
-\todo{Jose Enrique writes this...}
-High level analysis API
+\todo{Quentin, Axel...}
+
+The gammapy.analysis sub-module provides a  high-level interface for the most common use cases identified in gamma-ray analyses.
+The classes and methods included can be used in Python scripts, notebooks or as commands within IPython sessions.
+The high-level user interface can also be used to automatise workflows driven by parameters declared in a configuration file in YAML format.
+This way a full analysis can be executed via a single command line taking the configuration file as input.
+
+The Analysis class has the responsability of orchestrating of the workflow defined in the configuration (AnalysisConfig) and triggering the execution of the AnalysisStep classes that defines the common use cases identified.
+These steps include the following:
+ observations selection from the DataStore,  data reduction, excess map computation, model fitting, flux-points estimation, and light-curves production.
+The structure of the Analysis class allows to define custom AnalysisStep,  so ones could design and configure arbitrarily complex wokflows.

### 2022-03-28 src/text/2-package-subsections/irf.tex
add IRF section

@@
 \todo{Fabio Pintore}
-IRF classes
+The {\it gammapy.irf} sub-package contains all classes and functionalities able to handle Instrument Response Functions (\irf) in a wide variety of formats.
+Usually, \irfs store instrument properties in the form of multi-dimension tables, with quantities expressed in terms of energy (true or reconstructed), off-axis angles, detector coordinates and so on.
+The main information stored in the common \gammaray \irfs are the effective area (Aeff), energy dispersion (Edisp), point spread function (PSF) and background (BKG).
+The {\it gammapy.irf} sub-package can open and access specific \irf extensions, interpolate and evaluate the quantities of interest on both energy and spatial axes, convert their format or units in different kinds, plot or write them into output files.
+In the following, we list the main sub-classes of the sub-package:
+
+\begin{itemize}
+\item Effective area: \gammapy provides the class {\it EffectiveAreaTable2D} to manage Aeff, which is usually defined in terms of true energy and offset angle.
+The class functionalities offer the possibility to read from files or to create it from scratch.
+{\it EffectiveAreaTable2D} can also convert, interpolate, write, and evaluate the effective area for a given energy and offset angles, or even plot the multi-dimensional Aeff table.
+
+\item Point spread function: \gammapy allows user to treat different kinds of PSFs, in particular, multi-dimensional gaussians ({\it EnergyDependentMultiGaussPSF}), King functions ({\it PSFKing}), or a parametric one.
+The {\it EnergyDependentMultiGaussPSF} class is able to handle up to three gaussians, defined in terms of amplitudes and sigma given for each true energy and offset angle bin.
+Similarly, {\it PSFKing takes} into account the gamma and sigma parameters as defined here.
+The {\it ParametricPSF} allows to create a PSF with a representation different from gaussian(s) or King profile(s).
+Finally, the user can take advantage from the {\it PSFMap} class, which creates a multi-dimensional map of the PSF in WCS coordinates.
+At each position, a PSF kernel map ({\it PSFKernel}) provides a PSF as a function of the true energy.
+The creation of PSF kernel maps, where the PSF is defined for each sky-position, is also given to the user.
+The latter two can speed up analyses.
+
+\item Energy dispersion: Edisp, in \iact, is generally given in terms of the so called migration parameter ($\mu$), which is defined as the ratio between the reconstructed energy
+and the true energy. This ratio should be as close as one and its dispersion can assume the shape of a gaussian (or even more complex distributions). Migration parameter
+is given at each offset angle and reconstructed energy. The main sub-classes are {\it EnergyDispersion2D}, designed to interpret Edisp, {\it EDispKernelMap}, which builds an
+Edisp kernel map, i.e.
+a 4-dimensional WCS map where at each sky-position is associated an Edisp kernel.
+The latter is a representation of the Edisp as a function of the true energy only thanks to the sub-class {\it EDispKernel}.
+
+\item Background: the BKG can be represented in \gammapy as either 1) a 2D map ({\it Background2D}) of count rate normalised per steradians and energy at different energies
+and offset-angles or 2) as rate per steradians and energy, as a function of reconstructed energy and detector coordinates ({\it Background3D}).
+In the former, the background is expected to follow a radially symmetric shape, while in the latter, it can be more complex.
+\end{itemize}
+
+\begin{figure}
+%	\import{code-examples/generated/}{gp_makers}
+
+	\caption{In Fig.~\ref{ig*:minted:irf_examples}, we show some example of Aeff, PSF, Edisp and BKG read and plotted from a typical \irf.}
+	\label{ig*:minted:irf_examples}
+\end{figure}

### 2022-03-29 src/text/4-project.tex
add technical infrastructure

@@
 In this section, we provide an overview of the organization of the Gammapy project.
-We briefly describe the main roles and responsibilities, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality open source software.
-We also describe how we tackle with the software distribution, our solution for a versioned thoroughly tested documentation in the form of user-friendly playable recipes, and the tools we use to foster the Gammapy community and to provide user support.
+We briefly describe the main roles and responsibilities within the team, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality software.
+We use common tools and services for software development of Python open-source projects, code review, testing, package distribution and user support, with a customized solution for a versioned thoroughly tested documentation in the form of user-friendly playable recipes.
 This section concludes with an outlook on the roadmap for future directions.
@@
 
-\begin{itemize}
-	\item GitHub repositories 
-	\begin{itemize}
-		\item gammapy (describe gammapy codebase)
-		\item docs
-		\item web
-		\item data
-		\item benchmarks
-		\item recipes
-		\item extra
-		\item meetings
-		\item conferences contributions
-		\item catalogs? (i.e. gamma-cat)
-		\item paper
-	\end{itemize}
-	\item github actions and automated tasks 
-	\begin{itemize}
-		\item ci
-		\item docs
-		\item benchmarks-slack
-		\item codemeta.json and zenodo
-		\item release-web
-	\end{itemize}	
-	\item pytest and code coverage in ci
-	\item tests on docstrings and on code in rst files
-	\item code quality services (codecov, lgtm, codacy)
-	\item validation and benchmarks -validation as online appendix...?
-\end{itemize}
+Gammapy follows an open-source and open-contribution development model based on the cloud repository service GitHub.
+A GitHub organization \textit{gammapy} \footnote{\url{https://github.com/gammapy}} hosts different repositories related with the project.
+The software codebase may be found in the \textit{gammapy} repository (see Table~\ref{table:codestats:data} and Figure~\ref{fig:codestats:lang} for code lines statistics).
+We make extensive use of the pull request system to discuss and review code contributions.
 
@@
 \end{figure}
+
+Several automatized tasks are set as GitHub actions \footnote{\url{https://github.com/features/actions}}, blocking the processes and alerting developers when fails occur.
+This is the case of the content integration workflow, which monitors the execution of the test coverage suite \footnote{\url{https://pytest.org}} using datasets from the \textit{gammapy-data} repository.
+Tests scan not only the codebase but also the code snippets present in docstrings of the scripts and in the RST documentation files, as well as in the tutorials provided in the form of Jupyter notebooks.
+
+Other automatized tasks, executing in the \textit{gammapy-benchmarks} repository, are responsible for numerical validation tests and benchmarks monitoring.
+Also tasks related with the release process are partially automatized, and every contribution to the codebase repository triggers the documentation building and publishing workflow within the \textit{gammapy-docs} repository (see Sec.
+~\ref{ssec:software-distribution} and Sec.
+~\ref{ssec:documentation}).
+
+This small ecosystem of interconnected up-to-date repositories, automatized tasks and alerts, is just a part of a bigger set of GitHub repositories, where most of them are related with the project but not necessary for the development of the software (i.e.
+project webpage, complementary high-energy astrophysics object catalogs, coding sprints and weekly developer calls minutes, contributions to conferences, other digital assets, etc.) Finally, third-party services for code quality metrics are also set and may be found as status shields in the codebase repository.
 
@@
 
-Figure: Screenshot of Jupyter notebook or docs with notebook, could show the interactive maps view
-\begin{verbatim}
-m = Map.read(“diffuse.fits”)
-m.plot_interactive()
-\end{verbatim}
-
 \subsection{Community and user-support}
@@
 \begin{itemize}
+	\item web and on-line documentation 	
+	\item slack
+	\item github discussions
 	\item weekly developers calls
 	\item coding sprints 
-	\item slack
-	\item github discussions
 	\item gammapy recipes repo

### 2022-03-30 src/text/4-project.tex
add software distribution

@@
 We briefly describe the main roles and responsibilities within the team, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality software.
-We use common tools and services for software development of Python open-source projects, code review, testing, package distribution and user support, with a customized solution for a versioned thoroughly tested documentation in the form of user-friendly playable recipes.
+We use common tools and services for software development of Python open-source projects, code review, testing, package distribution and user support, with a customized solution for a versioned thoroughly tested documentation in the form of user-friendly playable tutorials.
 This section concludes with an outlook on the roadmap for future directions.
@@
 
-\begin{itemize}
-	\item pip, conda, versions
-	\item gammapy download
-	\item automated release process with Zenodo publishing linking
-	\item escape 2020 software platform
-	\item ascl
-\end{itemize}
+Gammapy is distributed and installed in the usual way for Python packages.
+Each stable release is uploaded to the Python package index \footnote{\url{https://pypi.org}} and as a binary package to the \textit{conda-forge} and \textit{astropy} Anaconda repository \footnote{\url{https://anaconda.org/anaconda/repo}} channels.
+At this time, Gammapy is also available as a Debian Linux package \footnote{\url{https://packages.debian.org/sid/python3-gammapy}}.
+We recommend installing the software using the \textit{conda} installation process with an environment definition file that we provide, so to work within a virtual isolated environment with additional useful packages and ensure reproducibility.
+Once installed users may download datasets and playable executable tutorials in the form of Jupyter notebooks using the \textit{gammapy download} command.
+
+Gammapy is indexed in Astronomy Source Code Library \footnote{\url{https://ascl.net/1711.014}} and Zenodo \footnote{\url{https://zenodo.org/record/5721467o}} digital libraries for software.
+The Zenodo record is synchronised with the codebase GitHub repository so that every release triggers the update of the versioned record.
+In addition, the next release of Gammapy will be added to the Open-source scientific Software and Service Repository \footnote{\url{https://projectescape.eu/ossr}} and indexed in the European Open Science Cloud catalog \footnote{\url{https://eosc-portal.eu}}.
 

### 2022-03-30 src/text/4-project.tex
add documentation

@@
 
-Gammapy is distributed and installed in the usual way for Python packages.
+Gammapy is distributed for Linux, Windows and Mac environments, and installed in the usual way for Python packages.
 Each stable release is uploaded to the Python package index \footnote{\url{https://pypi.org}} and as a binary package to the \textit{conda-forge} and \textit{astropy} Anaconda repository \footnote{\url{https://anaconda.org/anaconda/repo}} channels.
@@
 We recommend installing the software using the \textit{conda} installation process with an environment definition file that we provide, so to work within a virtual isolated environment with additional useful packages and ensure reproducibility.
-Once installed users may download datasets and playable executable tutorials in the form of Jupyter notebooks using the \textit{gammapy download} command.
 
@@
 \label{ssec:documentation}
+Gammapy provides its user community with a tested and versioned up-to-date on-line documentation \footnote{\url{https://docs.gammapy.org}}~\citep{2019ASPC..523..357B} built with Sphinx \footnote{\url{https://www.sphinx-doc.org}} scanning the codebase Python scripts, as well as a set of RST files and Jupyter notebooks.
+The documentation includes a handwritten user guide, a set of executable tutorials, and a reference to the API automatically extracted from the code and docstrings.
+The Gammapy code snippets present in the documentation are tested in different environments using our continuous integration (CI) workflow based on GitHub actions.
 
-\begin{itemize}
-	\item rst, sphinx, api
-	\item versioned notebooks building and testing
-	\item versioned binder
-\end{itemize}
+The Jupyter notebooks tutorials are stored stripped of their output cells, which greatly helps in identifying differences in the contribution review.
+During the CI these are executed, the output cells parsed and, in case an error is found in one of the output cells then validation fails.
+Code formatting of the input cells is also done, parsing their content and using a particular syntax to provide links to the API documentation pages.
+The resulting web published tutorials also provide links to playground spaces in myBinder~\citep{project_jupyter-proc-scipy-2018}, where they may be executed on-line in versioned virtual environments hosted in the myBinder infrastructure.
+
+Users may also play with the tutorials locally in their laptops.
+They can download a specific version of the tutorials together with the associated datasets needed and the specific conda computing environment, using the \textit{gammapy download} command.
 

### 2022-03-30 src/text/4-project.tex

--- 2022-03-29 src/text/4-project.tex
@@
 
+\todo{Jose Enrique}
+
 In this section, we provide an overview of the organization of the Gammapy project.
-We briefly describe the main roles and responsibilities within the team, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality software.
-We use common tools and services for software development of Python open-source projects, code review, testing, package distribution and user support, with a customized solution for a versioned thoroughly tested documentation in the form of user-friendly playable recipes.
+We briefly describe the main roles and responsibilities in the Gammapy team, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality open source software.
+We also describe how we tackle with the software distribution, our solution for a versioned thoroughly tested documentation in the form user-friendly playable recipes, and the tools we use to foster the Gammapy community and to provide user support.
 This section concludes with an outlook on the roadmap for future directions.
 
-\subsection{Organizational structure}
-\label{ssec:organizational-structure}
+\subsection{Gammapy Team}
+\label{ssec:gammapy-team}
 
-Gammapy is a well-organised international open-source project with a broad developer base and the presence of commitments from strong groups and institutes in the very high-energies astrophysics domain \footnote{\url{https://gammapy.org/team.html}}.
-The main development roadmaps are discussed and validated by a Coordination Committee, composed of representatives of the main contributing laboratories.
-This committee is chaired by a Project Manager and his deputy while two Lead Developers manage the development strategy and organise technical activities.
-Because of this institutionally driven characteristic, the permanent staff and commitment of supporting institutes ensure the continuity of the executive teams.
-A core team of developers from the contributing laboratories is in charge of the regular development, which benefits from punctual contributions of the community at large.
+\begin{itemize}
+	\item open development
+	\item community driven vs. institutional driven
+	\item communities
+\end{itemize}
+
+\begin{itemize}
+	\item coordination committee
+	\item project manager
+	\item lead developers
+	\item contributors
+\end{itemize}
 
@@
 
-Gammapy follows an open-source and open-contribution development model based on the cloud repository service GitHub.
-A GitHub organization \textit{gammapy} \footnote{\url{https://github.com/gammapy}} hosts different repositories related with the project.
-The software codebase may be found in the \textit{gammapy} repository (see Table~\ref{table:codestats:data} and Figure~\ref{fig:codestats:lang} for code lines statistics).
-We make extensive use of the pull request system to discuss and review code contributions.
+\begin{itemize}
+	\item Github repositories 
+	\begin{itemize}
+		\item gammapy (describe gammapy codebase)
+		\item docs
+		\item web
+		\item data
+		\item benchmarks
+		\item recipes
+		\item extra
+		\item meetings
+		\item conferences contributions
+		\item catalogs? (i.e. gamma-cat)
+		\item paper
+	\end{itemize}
+	\item github actions and automated tasks 
+	\begin{itemize}
+		\item ci
+		\item docs
+		\item benchmarks-slack
+		\item codemeta.json and zenodo
+		\item release-web
+	\end{itemize}	
+	\item pytest and code coverage in ci
+	\item tests on docstrings and on code in rst files
+	\item code quality services (codecov, lgtm, codacy)
+	\item validation and benchmarks -validation as online appendix...?
+\end{itemize}
 
@@
 \end{figure}
-
-Several automatized tasks are set as GitHub actions \footnote{\url{https://github.com/features/actions}}, blocking the processes and alerting developers when fails occur.
-This is the case of the content integration workflow, which monitors the execution of the test coverage suite \footnote{\url{https://pytest.org}} using datasets from the \textit{gammapy-data} repository.
-Tests scan not only the codebase but also the code snippets present in docstrings of the scripts and in the RST documentation files, as well as in the tutorials provided in the form of Jupyter notebooks.
-
-Other automatized tasks, executing in the \textit{gammapy-benchmarks} repository, are responsible for numerical validation tests and benchmarks monitoring.
-Also tasks related with the release process are partially automatized, and every contribution to the codebase repository triggers the documentation building and publishing workflow within the \textit{gammapy-docs} repository (see Sec.
-~\ref{ssec:software-distribution} and Sec.
-~\ref{ssec:documentation}).
-
-This small ecosystem of interconnected up-to-date repositories, automatized tasks and alerts, is just a part of a bigger set of GitHub repositories, where most of them are related with the project but not necessary for the development of the software (i.e.
-project webpage, complementary high-energy astrophysics object catalogs, coding sprints and weekly developer calls minutes, contributions to conferences, other digital assets, etc.) Finally, third-party services for code quality metrics are also set and may be found as status shields in the codebase repository.
 
@@
 
+Figure: Screenshot of Jupyter notebook or docs with notebook, could show the interactive maps view
+\begin{verbatim}
+m = Map.read(“diffuse.fits”)
+m.plot_interactive()
+\end{verbatim}
+
 \subsection{Community and user-support}
@@
 \begin{itemize}
-	\item web and on-line documentation 	
+	\item weekly developers calls
+	\item coding sprints 
 	\item slack
 	\item github discussions
-	\item weekly developers calls
-	\item coding sprints 
 	\item gammapy recipes repo

### 2022-03-30 src/text/2-package.tex
More test on the workflow

--- 2022-01-31 src/text/2-package.tex
@@
 \label{sec:analysis-workflow-overview}
+
+% This might not be the bast place compared to introduction
+The data processing workflow in Gamma-ray astronomy is usually split in two sequences.
+The first one deals with the data processing from camera measurement, calibration, event
+reconstruction and selection to yield a list of reconstructed gamma-ray event candidates.
+This sequence, sometimes referred to as low-level analysis, is usually very specific to
+a given observation technique if not a given instrument.
+
+The other sequence, referred to as high-level analysis, deals with the extraction of physical
+quantities related to gamma-ray sources and the production of high-level products such as spectra,
+lightcurves and catalogs. The methods and tools applied here are more generic and are broadly
+shared across the field. They also frequently imply joint analysis of multi-instrument data.
+
+Gamma-ray data at the Data Level 3 consists in lists of gamma-like events and their
+corresponding instrument response functions (IRFs). The latter include effective area,
+point spread function (PSF), energy dispersion and residual hadronic background.
+The handling of DL3 data is performed by classes and methods
+in the gammapy.data  (see \ref{ssec:gammapy-data}) and the gammapy.irf
+(see \ref{ssec:gammapy-irf}) subpackages.
+
+The first step in the analysis is the selection and extraction of observations
+based of their meta data including information such as pointing direction, observation
+time and observation conditions.
+
+The next step of the analysis is the data reduction on a user-defined geometry.
+A typical geometry consists in a spectral representation with a measured
+energy axis, and in a spatial representation, either a coordinates system  with a projection
+(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
+The gammapy.maps subpackage provides general multidimensional geometry objects
+(Geom) and the associated data structures (Maps), see \ref{ssec:gammapy-maps}.
+
+All observation events and instrument responses are projected onto the
+target geometry. Because residual hadronic background models can be subject
+to significant uncertainties background correction must be applied,
+such as the ring or the fied-of-view background techniques or
+background measurements must be performed within, e.g. reflected regions~\citep{Berge07}.
+Parts of the data with high associated IRF systematics must also be excluded by defining
+a "safe" data range. These data reduction steps are performed by classes and functions
+implemented in the gammapy.makers subpackage (see \ref{ssec:gammapy-makers}).
+
+The counts data and the reduced IRFs in the form of maps are bundled into dataset objects
+that represent the data level 4 (DL4). They can be written to
+disk, in a format specific to Gammapy to allow users to read them back at any time later
+for modeling and fitting.
+
+This latter step 
+ datasets classes bundle reduced data in form of maps, reduced IRFs, models and
+fit statistics. Different sub-classes support different analysis methods
+and fit statistics (e.g. Poisson statistics with known background or
+with OFF background measurements). The datasets are used to perform joint-likelihood
+fitting allowing to combine different measurements, e.g. from different observations
+but also from different instruments or event classes. They can also be used for binned
+simulation as well as event sampling to simulate DL3 events data.
+
+The next step is then typically to model and fit the datasets, either
+individually, or in a joint likelihood analysis. For this purpose Gammapy
+provides a uniform interface to multiple fitting backends. It also provides
+a variety of :ref:`built in models <model-gallery>`. This includes spectral,
+spatial and temporal model classes to describe the gamma-ray emission in the sky.
+Independently or subsequently to the global modelling, the data can be
+re-grouped to compute flux points, light curves and flux as well as significance
+maps in energy bands.
 

### 2022-03-30 src/text/2-package.tex
Add IRF formulae

@@
 shared across the field. They also frequently imply joint analysis of multi-instrument data.
+To extract physically relevant information, the measured data are usually compared to a
+model of the expected gamma-ray emitters in the instrument field-of-view using statistical
+techniques such as maximum likelihood.
 
-Gamma-ray data at the Data Level 3 consists in lists of gamma-like events and their
-corresponding instrument response functions (IRFs). The latter include effective area,
-point spread function (PSF), energy dispersion and residual hadronic background.
+We can write the expected number of detected events at measured position $p$ and energy $E$:
+\begin{align}
+   N(p, E) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
+   &\times \Phi(p_{\rm true}, E_{\rm true}) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
+\end{align}
+where
+\begin{itemize}
+\item $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response
+\item $\Phi(p_{\rm true}, E_{\rm true})$ is the sky flux model
+\item $t_{\rm obs}$ is the observation time
+\end{itemize}
+
+A common assumption is that the instrument response can be simplified as the product
+of three independent functions:
+
+\begin{align}
+   R(p, E|p_{\rm true}, E_{\rm true}) = &A_{\rm eff}(p_{\rm true}, E_{\rm true}) \times\\
+    &PSF(p|p_{\rm true}, E_{\rm true}) \times\\
+    &E_{\rm disp}(E|p_{\rm true}, E_{\rm true})
+\end{align}
+where:
+\begin{itemize}
+\item $A_{\rm eff}(p_{\rm true}, E_{\rm true})$ is the effective collection area of the detector. It is the product
+  of the detector collection area times its detection efficiency at true energy $E_{\rm true}$ and position $p_{\rm true}$.
+\item $PSF(p|p_{\rm true}, E_{\rm true})$ is the point spread function. It gives the probability of
+  measuring a direction $p$ when the true direction is $p_{\rm true}$ and the true energy is $E_{\rm true}$.
+  Gamma-ray instruments consider the probability density of the angular separation between true and reconstructed directions
+  $\delta p = p_{\rm true} - p$, i.e. $PSF(\delta p|p_{\rm true}, E_{\rm true})$.
+\item $E_{\rm disp}(E|p_{\rm true}, E_{\rm true})$ is the energy dispersion. It gives the probability to
+  reconstruct the photon at energy $E$ when the true energy is $E_{\rm true}$ and the true position :$p_{\rm true}$.
+  Gamma-ray instruments consider the probability density of the migration $\mu=\frac{E}{E_{\rm true}}$,
+  i.e. $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$.
+\end{itemize}
+
+Gamma-ray data at the Data Level 3 therefore consists in lists of gamma-like events and their
+corresponding instrument response functions (IRFs). The latter include the aforementioned
+effective area, point spread function (PSF), energy dispersion and residual hadronic background.
 The handling of DL3 data is performed by classes and methods

### 2022-04-04 src/text/3-applications-subsections/temporal-analysis.tex
Fix pre commit hooks
write temporal section

@@
 \todo{Atreyee}
+
+A common use case in most astrophysical scenarios is to study the temporal variability of the source.
+The most basic way to do this is to construct a lightcurve, ie, the flux of the source in each given time bin.
+In gammapy, this is done by using the `LightCurveEstimator` which fits the normalisation of the source in each energy band per observation.
+For custom time binning, an observation needs to be split into finer ones using the `Observation.select_time` method.
+Figure \ref{fig:hess_lightcurve_pks} shows the lightcurve of the blazar PKS 2155-304 in different energy bands as observed by the H.E.S.S.
+telescope during an exceptional flare on the night of July 29 - 30, 2006 \cite{2009A&A...502..749A}.
+The data is available publicly as a part of the HESS-DL3-DR1 \cite{HESS-DL3-DR1}, and shipped with GAMMAPY_DATA.
+Each observation is first split into 10 min smaller observations, and spectra extracted for each of these within a 0.11 deg radius around the source.
+A PowerLawSpectralModel with an index of 3.4 is assumed for all the datasets, and the `LightCurveEstimator` run for two energy bands, 0.5 - 1.5 TeV, and 1.5 - 20 TeV, resp.
 
@@
 	\includegraphics[width=1.\textwidth]{figures/hess_lightcurve_pks.pdf}
-	\caption{
-		H.E.S.S. PKS~2155-304 flare in two energy bands}
+	\caption{10 min binned lightcurve for PKS~2155-304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in 2006.}
 	\label{fig:hess_lightcurve_pks} 
 \end{figure*}
+
+Instead of extracting a lightcurve, it is also possible to directly fit temporal models to the reduced datasets.
+By associating an appropriate SkyModel, consisting of both temporal and spectral components, to each dataset, a joint fitting across the datasets will directly return the best fit temporal and spectral parameters.

### 2022-04-08 src/text/4-project.tex

--- 2022-03-30 src/text/4-project.tex
@@
 
-Gammapy is a well-organised international open-source project with a broad developer base and the presence of commitments from strong groups and institutes in the very high-energies astrophysics domain \footnote{\url{https://gammapy.org/team.html}}.
+Gammapy is a well-organised international open-source project with a broad developer base and the presence of commitments from strong groups and institutes in the very high-energies astrophysics domain\footnote{\url{https://gammapy.org/team.html}}.
 The main development roadmaps are discussed and validated by a Coordination Committee, composed of representatives of the main contributing laboratories.
@@
 Gammapy follows an open-source and open-contribution development model based on the cloud repository service GitHub.
-A GitHub organization \textit{gammapy} \footnote{\url{https://github.com/gammapy}} hosts different repositories related with the project.
+A GitHub organization \textit{gammapy}\footnote{\url{https://github.com/gammapy}} hosts different repositories related with the project.
 The software codebase may be found in the \textit{gammapy} repository (see Table~\ref{table:codestats:data} and Figure~\ref{fig:codestats:lang} for code lines statistics).
@@
 
-Several automatized tasks are set as GitHub actions \footnote{\url{https://github.com/features/actions}}, blocking the processes and alerting developers when fails occur.
-This is the case of the content integration workflow, which monitors the execution of the test coverage suite \footnote{\url{https://pytest.org}} using datasets from the \textit{gammapy-data} repository.
+Several automatized tasks are set as GitHub actions\footnote{\url{https://github.com/features/actions}}, blocking the processes and alerting developers when fails occur.
+This is the case of the content integration workflow, which monitors the execution of the test coverage suite\footnote{\url{https://pytest.org}} using datasets from the \textit{gammapy-data} repository.
 Tests scan not only the codebase but also the code snippets present in docstrings of the scripts and in the RST documentation files, as well as in the tutorials provided in the form of Jupyter notebooks.
@@
 Gammapy is distributed for Linux, Windows and Mac environments, and installed in the usual way for Python packages.
-Each stable release is uploaded to the Python package index \footnote{\url{https://pypi.org}} and as a binary package to the \textit{conda-forge} and \textit{astropy} Anaconda repository \footnote{\url{https://anaconda.org/anaconda/repo}} channels.
-At this time, Gammapy is also available as a Debian Linux package \footnote{\url{https://packages.debian.org/sid/python3-gammapy}}.
+Each stable release is uploaded to the Python package index\footnote{\url{https://pypi.org}} and as a binary package to the \textit{conda-forge} and \textit{astropy} Anaconda repository\footnote{\url{https://anaconda.org/anaconda/repo}} channels.
+At this time, Gammapy is also available as a Debian Linux package\footnote{\url{https://packages.debian.org/sid/python3-gammapy}}.
 We recommend installing the software using the \textit{conda} installation process with an environment definition file that we provide, so to work within a virtual isolated environment with additional useful packages and ensure reproducibility.
 
-Gammapy is indexed in Astronomy Source Code Library \footnote{\url{https://ascl.net/1711.014}} and Zenodo \footnote{\url{https://zenodo.org/record/5721467o}} digital libraries for software.
+Gammapy is indexed in Astronomy Source Code Library\footnote{\url{https://ascl.net/1711.014}} and Zenodo\footnote{\url{https://zenodo.org/record/5721467o}} digital libraries for software.
 The Zenodo record is synchronised with the codebase GitHub repository so that every release triggers the update of the versioned record.
-In addition, the next release of Gammapy will be added to the Open-source scientific Software and Service Repository \footnote{\url{https://projectescape.eu/ossr}} and indexed in the European Open Science Cloud catalog \footnote{\url{https://eosc-portal.eu}}.
+In addition, the next release of Gammapy will be added to the Open-source scientific Software and Service Repository\footnote{\url{https://projectescape.eu/ossr}} and indexed in the European Open Science Cloud catalog\footnote{\url{https://eosc-portal.eu}}.
 
-\subsection{Documentation}
-\label{ssec:documentation}
-Gammapy provides its user community with a tested and versioned up-to-date on-line documentation \footnote{\url{https://docs.gammapy.org}}~\citep{2019ASPC..523..357B} built with Sphinx \footnote{\url{https://www.sphinx-doc.org}} scanning the codebase Python scripts, as well as a set of RST files and Jupyter notebooks.
+\subsection{Documentation and user-support}
+\label{ssec:documentation-and-user-support}
+Gammapy provides its user community with a tested and versioned up-to-date on-line documentation\footnote{\url{https://docs.gammapy.org}}~\citep{2019ASPC..523..357B} built with Sphinx\footnote{\url{https://www.sphinx-doc.org}} scanning the codebase Python scripts, as well as a set of RST files and Jupyter notebooks.
 The documentation includes a handwritten user guide, a set of executable tutorials, and a reference to the API automatically extracted from the code and docstrings.
@@
 The resulting web published tutorials also provide links to playground spaces in myBinder~\citep{project_jupyter-proc-scipy-2018}, where they may be executed on-line in versioned virtual environments hosted in the myBinder infrastructure.
-
 Users may also play with the tutorials locally in their laptops.
@@
 
-\subsection{Community and user-support}
-\label{ssec:community-and-user-support}
+We have also set up a solution for users to share recipes as Jupyter notebooks that do not fit in the Gammapy core documentation but which may be relevant as specific use cases.
+Contributions happen via pull requests to the \textit{gammapy-recipes} GitHub repository and merged after a short review.
+All notebooks in the repository are tested and published in the Gammapy recipes webpage\footnote{\url{https://gammapy.github.io/gammapy-recipes}} automatically using GitHub actions.
 
-\begin{itemize}
-	\item web and on-line documentation 	
-	\item slack
-	\item github discussions
-	\item weekly developers calls
-	\item coding sprints 
-	\item gammapy recipes repo
-	\item mailing lists 
-		\begin{verbatim}
-		gammapy-coordination-l@in2p3.fr 
-		gammapy@googlegroups.com 
-		gammapy-cta-l@in2p3.fr
-		\end{verbatim}
-	\item twitter
-\end{itemize}
+A growing community of users is gathering around the Slack messaging\footnote{\url{https://gammapy.slack.com}} and GitHub discussions\footnote{\url{https://github.com/gammapy/gammapy/discussions}} support forums, providing valuable feedback on the Gammapy functionalities, interface and documentation.
+Other communication channels have been set like mailing lists, a Twitter account\footnote{\url{https://twitter.com/gammapyST}}, regular public coding sprint meetings, hands-on session within collaborations, weekly development meetings, etc.
 
 \subsection{Roadmap}
-\label{ssec:roadmap}
 \todo{Axel, Regis}

### 2022-04-08 src/figures/cube_analysis.py
try as one figure

@@ -19,51 +19,55 @@ npred_3 =Map.read(path / "npred_3.fits", format="ogip")
 
 models = Models.read(path / "best-fit-model.yaml")
 
-figsize = config.FigureSizeAA(aspect_ratio=2.8, width_aa="two-column")
+fontsize_labels = 8
+fontsize_ticks = 8
+pad_ticks = 1
+length_ticks = 2
+
+figsize = config.FigureSizeAA(aspect_ratio=3.3, width_aa="two-column")
 fig = plt.figure(figsize=figsize.inch)
 
 wcs = significance.geom.wcs
 region = excess.geom.region
 
-# rect = (0.05, 0.2, 0.28, 0.75)
-rect = (0.05, 0.2, 0.4, 0.75)
+rect = (0.06, 0.2, 0.27, 0.75)
 ax = fig.add_axes(rect=rect, projection=wcs)
 significance.plot(ax=ax, stretch='sqrt', add_cbar=True)
-ax.images[-1].colorbar.set_label('Significance ($\sigma$)', rotation=270, labelpad=25, fontsize=12)
+# ax.images[-1].colorbar.set_label('Significance ($\sigma$)', rotation=270, labelpad=25, fontsize=6)
+ax.set_xlabel('Galactic Longitude', fontsize=fontsize_labels)
+ax.set_ylabel('Galactic Latitude', fontsize=fontsize_labels)
+ax.tick_params(labelsize=fontsize_ticks, pad=1, length=2)
+ax.images[-1].colorbar.ax.tick_params(labelsize=6, pad=pad_ticks, length=length_ticks)
 region.to_pixel(wcs).plot(ax=ax, fill=False, lw=1, color='blue', ls='--')
 
-# rect = (0.40, 0.2, 0.28, 0.75)
-rect = (0.55, 0.2, 0.4, 0.75)
-
+rect = (0.39, 0.2, 0.27, 0.75)
 ax = fig.add_axes(rect=rect, projection=wcs)
 residual.plot(ax=ax,cmap='coolwarm', vmin=-5, vmax=5, add_cbar=True)
-ax.images[-1].colorbar.set_label('Significance ($\sigma$)', rotation=270, labelpad=25, fontsize=12)
-
+# ax.images[-1].colorbar.set_label('Significance ($\sigma$)', rotation=270, labelpad=25, fontsize=6)
+ax.images[-1].colorbar.ax.tick_params(labelsize=6, pad=pad_ticks, length=length_ticks)
[…]

### 2022-04-08 src/figures/cube_analysis.py
fix typo

@@ -58,7 +58,6 @@ models[2].spatial_model.to_region().to_pixel(wcs).plot(ax=ax, fill=False, lw=1, 
 rect = (0.72, 0.23, 0.26, 0.7)
 ax = fig.add_axes(rect=rect)
 ax.tick_params(labelsize=fontsize_ticks, pad=1, length=2)
-ax = fig.add_axes(rect=rect)
 excess.plot(ax=ax, color='blue', label='excess counts')
 npred_1.plot_hist(ax=ax, label='source 1', lw=1, color='C0')
 npred_2.plot_hist(ax=ax, label='source 2', lw=1, color='C1')

### 2022-04-11 src/text/3-applications-subsections/3D-analysis.tex
add figure to text
figure caption

@@
 The position and sizes of the sources have been selected so that their contributions overlap.
-This can be clearly seen in the significance map shown in the left panel of Figure \todo{X}.
+This can be clearly seen in the significance map shown in the left panel of Figure~\ref{fig:cube_analysis}.
 This map was produced with the ExcessMapEstimator (see Section~\ref{ssec:gammapy-estimators}) with a correlation radius of 0.1\textdegree.
@@
 This is done again via the ExcessMapEstimator.
-As can be seen in Figure \todo{X}, there are no regions above or below 5$\sigma$.
+As can be seen in the middle panel of Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$.
 
@@
 Among the advantages that this provides is the ability to disentangle the contribution from overlapping sources to the same spatial region.
-To highlight this, we define a circular RegionGeom of radius 0.5\textdegree centered around the position of the point source.
+To highlight this, we define a circular RegionGeom of radius 0.5\textdegree centered around the position of the point source, which is drawn in the left panel of Figure~\ref{fig:cube_analysis}.
 We can now compare the measured excess counts integrated in that region to the expected relative contribution from each of the three source models.
-This can be seen in Figure~\todo{X}.
+This can be seen in the left panel of Figure~\ref{fig:cube_analysis}.
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/cube_analysis.pdf}
+	\caption{Example 3D analysis for simulated sources using the \cta \irfs.
+The left image shows a significance map where the three simulated sources can be seen.
+The middle figure shows another significance map, but this time after subtracting the best-fit model for each of the sources, which are displayed in black.
+The right figure shows the contribution of each source model to the circular region of radius 0.5\textdegree drawn in the left image, together with the excess counts inside that region.
+	}
+	\label{fig:cube_analysis}
+\end{figure*}
 

### 2022-04-11 src/text/3-applications-subsections/3D-analysis.tex
some requested changes

@@
 
+\cite{Mohrmann2019}
+
 For such situations a more complex approach is needed, the so-called 3D analysis.
@@
 However, we will not use the simulated event lists provided by \cta but instead, use the method MapDataset.fake() to simulate measured counts from the combination of several SkyModel instances.
+In this way, a DL4 dataset can directly be simulated.
 In particular we simulate:
@@
 
-We can now fit the same model shapes to the simulated data and retrieve the best-fit parameters, which are in all cases well within 1$\sigma$ of the simulated parameters.
-We can now compute the residual significance map after removing the contribution from each model.
+We can now fit the same model shapes to the simulated data and retrieve the best-fit parameters.
+To check the model agreement, we compute the residual significance map after removing the contribution from each model.
 This is done again via the ExcessMapEstimator.
-As can be seen in the middle panel of Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$.
+As can be seen in the middle panel of Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$, meaning that the models describe the data sufficiently well.
 

### 2022-04-11 src/text/3-applications-subsections/3D-analysis.tex
add Lars, mention flux points

@@
 The 1D analysis approach is a powerful tool to measure the spectrum of an isolated source.
-However, more complicated situations, such as field of views containing several overlapping sources, require a more careful treatment.
-Because it is based on integration over a region, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region.
-Similarly, sources with extended or complex morphology can result in the measured flux being underestimated, and heavily dependent on the choice of extraction region.
-
-\cite{Mohrmann2019}
+However, more complicated situations require a more careful treatment.
+In fields of view containing several overlapping sources, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region.
+Sources with extended or complex morphology can result in the measured flux being underestimated, and heavily dependent on the choice of extraction region.
+Additionally, the 1D approach neglects the energy-dependence of the PSF.
 
@@
 In this framework, a combined spatial and spectral model (that is, a SkyModel, see Section~\ref{ssec:gammapy-modeling}) is fitted to the sky-maps that were previously derived from the data and bundled into a MapDataset (see Sections~\ref{ssec:gammapy-makers,ssec:gammapy-datasets}).
+
+A thorough description of the 3D analysis approach and multiple examples that use \gammapy can be found in~\cite{Mohrmann2019}. Here we present a short example to highlight some of its advantages.
 
@@
 
+Note that all the models fitted also have a spectral component, from which flux points can be derived in a similar way as described in~\ref{ssec:1d-analysis}.
 %

### 2022-04-11 src/text/3-applications-subsections/temporal-analysis.tex
fitting stacked for lc

@@
 The most basic way to do this is to construct a lightcurve, ie, the flux of the source in each given time bin.
-In gammapy, this is done by using the `LightCurveEstimator` which fits the normalisation of the source in each energy band per observation.
+In gammapy, this is done by using the LightCurveEstimator which fits the normalisation of the source in each energy band per observation, keeping other parameters constant.
 For custom time binning, an observation needs to be split into finer ones using the `Observation.select_time` method.
-Figure \ref{fig:hess_lightcurve_pks} shows the lightcurve of the blazar PKS 2155-304 in different energy bands as observed by the H.E.S.S.
+Figure \ref{fig:hess_lightcurve_pks} shows the lightcurve of the blazar PKS 2155$-$304 in different energy bands as observed by the H.E.S.S.
 telescope during an exceptional flare on the night of July 29 - 30, 2006 \cite{2009A&A...502..749A}.
-The data is available publicly as a part of the HESS-DL3-DR1 \cite{HESS-DL3-DR1}, and shipped with GAMMAPY_DATA.
+The data is available publicly as a part of the HESS$-$DL3$-$DR1 \cite{HESS-DL3-DR1}, and shipped with GAMMAPY$_$DATA.
 Each observation is first split into 10 min smaller observations, and spectra extracted for each of these within a 0.11 deg radius around the source.
-A PowerLawSpectralModel with an index of 3.4 is assumed for all the datasets, and the `LightCurveEstimator` run for two energy bands, 0.5 - 1.5 TeV, and 1.5 - 20 TeV, resp.
-
-Lightcurve in two energy bands (600 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) for
-PKS2155-304 flare seen by H.E.S.S. as in our notebooks.
+A PowerLawSpectralModel is fit to all the datasets, leading to a reconstructed index of $3.54 \pm 0.02$.
+With this assumed spectral model the `LightCurveEstimator` run directly for two energy bands, 0.5 - 1.5 TeV, and 1.5 - 20 TeV,  respectively.
 
@@
 	\includegraphics[width=1.\textwidth]{figures/hess_lightcurve_pks.pdf}
-	\caption{10 min binned lightcurve for PKS~2155-304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in 2006.}
+	\caption{10 min binned lightcurve for PKS~2155$-$304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in 2006.}
 	\label{fig:hess_lightcurve_pks} 
@@
 
-Instead of extracting a lightcurve, it is also possible to directly fit temporal models to the reduced datasets.
+The obtained flux points can be modelled using any of the available temporal and spectral models, or even using custom temporal models with spectroscopic variability.
+Alternatively, instead of  extracting a lightcurve, it is also possible to directly fit temporal models to the reduced datasets.
 By associating an appropriate SkyModel, consisting of both temporal and spectral components, to each dataset, a joint fitting across the datasets will directly return the best fit temporal and spectral parameters.

### 2022-04-11 src/data/lightcurve/make.py

@@ -9,6 +9,7 @@ from astropy.coordinates import Angle
 from gammapy.data import DataStore
 from gammapy.datasets import SpectrumDataset, Datasets
 from gammapy.modeling.models import PowerLawSpectralModel, SkyModel
+from gammapy.modeling import Fit
 from gammapy.maps import MapAxis, RegionGeom
 from gammapy.estimators import LightCurveEstimator
 from gammapy.makers import (
@@ -75,7 +76,7 @@ def data_reduction(short_observations):
     return datasets
 
 
-def light_curve(datasets, time_intervals):
+def fit_stacked(datasets):
     spectral_model = PowerLawSpectralModel(
         index=3.4, amplitude=2e-11 * u.Unit("1 / (cm2 s TeV)"), reference=1 * u.TeV
     )
@@ -84,6 +85,15 @@ def light_curve(datasets, time_intervals):
     sky_model = SkyModel(
         spatial_model=None, spectral_model=spectral_model, name="pks2155"
     )
+
+    stacked = datasets.stack_reduce()
+    stacked.models = sky_model
+    fit = Fit(optimize_opts={"print_level": 0})
+    fit.run([stacked])
+    return sky_model
+
+
+def light_curve(datasets, time_intervals, sky_model):
     datasets.models = sky_model
     lc_maker_1d = LightCurveEstimator(
         energy_edges=[0.5, 1.5, 20] * u.TeV,
@@ -102,7 +112,8 @@ if __name__ == "__main__":
     observations = get_observations()
     time_intervals, short_observations = split_observations(observations)
     datasets = data_reduction(short_observations)
-    lc = light_curve(datasets, time_intervals)
+    sky_model = fit_stacked(datasets)
+    lc = light_curve(datasets, time_intervals, sky_model)
     log.info(f"Writing {filename}")
     lc.write(filename, format="lightcurve", overwrite=True)
 

### 2022-04-12 src/text/3-applications/3.4-survey_pops.tex
mote text

--- 2022-02-24 src/text/3-applications/3.4-survey_pops.tex
@@
 They also offer less selection bias to perform source population studies over a large set of coherently detected and modelled objects.
-Early versions of \textit{gammapy} where developed in parallel of the preparation of the HESS Galactic plane survey catalog [HGPS]\citep {2018A&A...612A...1H} and the associated PWN and SNR populations studies \citep{2018A&A...612A...2H, 2018A&A...612A...3H}.
+Early versions of \textit{gammapy} were developed in parallel of the preparation of the HESS Galactic plane survey catalog \citep[HGPS][]{2018A&A...612A...1H} and the associated PWN and SNR populations studies \citep{2018A&A...612A...2H, 2018A&A...612A...3H}.
 
-The CTA first Data challenge (DC1) proposed a large set of simulated observations covering the programs proposed in the Key science Projects for CTA  {2019scta.book.....C}, including in particular extra-Galactic and Galactic surveys.
-The studies performed on these simulations not only offered a first glimpse on what could be the sky seen by CTA, but also the opportunity to test the software, improve its performance, and identify the needs in term of parallelisation to process the large datasets provided by the surveys.
-Note that the CTA-DC1 simulations were performed with the \textit{ctools} package \citep{2016A&A...593A...1K} and analysed with both \textit{ctools} and \textit{gammapy} packages in order to cross-validate them.
-More recently new simulations of the CTA-GPS were analysed in the view of optimizing the production of the future CTA catalogs and associated populations studies \citep{2021arXiv210903729R}.
-Future plans of the CTA observatory include the preparation of a new Data Challenge simulated with \textit{gammapy} that is meant to be released publicly in order to reach a broader community.
+The increase in sensitivity  and resolution provided by new generation of instruments scale up the number of sources detectable and the complexity of the models needed to represent them accurately.
+As an example If we compare the results of the HGPS to the expectations from the CTA Galactic Plane survey simulations we jump from 78 sources detected by HESS to about 500 detectable by CTA  \citep{2021arXiv210903729R}.
+
+Studies performed on simulations not only offer a first glimpse on what could be the sky seen by CTA (according to our current knowledge on source populations), but also give us the opportunity to test the software on complex use cases\footnote{Note that the CTA-GPS simulations were performed with the \textit{ctools} package \citep{2016A&A...593A...1K} and analysed with both \textit{ctools} and \textit{gammapy} packages in order to cross-validate them.}.
+So we can  improve performances, optimize our analyses strategies, and identify the needs in term of parallelisation to process the large datasets provided by the surveys.
+
+In short the production of catalogs from gamma-ray surveys can be divided in four main steps : data-reduction; object detection; model fitting and model selection; associations and classification.
+The IACTs data-reduction step is done in the same way than described in the previous sections but scale-up to few thousand of observations.
+The object detection step consists a minima in finding local maxima in the significance, or TS maps,  given by the ExcessMapEstimator, or TSMapEstimator, respectively.
+Further refinements can include for example  filtering  and detection on these maps with techniques from scikit-image package  \citep{scikit-image} and outlier detection from scikit-learn package  \citep{scikit-learn} .
+Tests on simulations shown that this helps to reduce the spurious detections at this stage and then speed up the next step as less objects will have to be fitted simultaneously.
+During the modelling step each object is alternatively fitted with different models in order to determine their optimal parameters and the best-candidate model.
+The subpackage gammapy.modeling.models offers a large variety of choice and the possibility to add custom models.
+Several spatial models (point-source, disk, gaussian...), and spectral models (power-law, log-parabola...) may be tested for each object, so the complexity of the problem increases rapidly in regions crowded with multiple extended sources.
+Finally an object is discarded if its best-fit model is not is significantly preferred over the null hypothesis (no source) comparing the difference in log-Likelihood between these two hypotheses.
+For the association and classification step that is tightly connected to the population studies we can a minima compare the fitted models to the set of gammapy-ray catalogs available in gammapy.catalog but further multi-wavelength cross-matches are usually required to characterize the sources.

### 2022-05-02 src/text/3-applications/3.4-survey_pops.tex

@@
 The object detection step consists a minima in finding local maxima in the significance, or TS maps,  given by the ExcessMapEstimator, or TSMapEstimator, respectively.
-Further refinements can include for example  filtering  and detection on these maps with techniques from scikit-image package  \citep{scikit-image} and outlier detection from scikit-learn package  \citep{scikit-learn} .
-Tests on simulations shown that this helps to reduce the spurious detections at this stage and then speed up the next step as less objects will have to be fitted simultaneously.
-During the modelling step each object is alternatively fitted with different models in order to determine their optimal parameters and the best-candidate model.
-The subpackage gammapy.modeling.models offers a large variety of choice and the possibility to add custom models.
+Further refinements can include for example  filtering  and detection on these maps with techniques from scikit-image package  \citep{scikit-image}, and outlier detection from scikit-learn package \citep{scikit-learn}.
+Tests on simulations shown that it reduces the spurious detections at this stage and then speed up the next step as less objects will have to be fitted simultaneously.
+During the modelling step each object is alternatively fitted with different models in order to determine their optimal parameters, and the best-candidate model.
+The subpackage gammapy.modeling.models offers a large variety of choice, and the possibility to add custom models.
 Several spatial models (point-source, disk, gaussian...), and spectral models (power-law, log-parabola...) may be tested for each object, so the complexity of the problem increases rapidly in regions crowded with multiple extended sources.
-Finally an object is discarded if its best-fit model is not is significantly preferred over the null hypothesis (no source) comparing the difference in log-Likelihood between these two hypotheses.
-For the association and classification step that is tightly connected to the population studies we can a minima compare the fitted models to the set of gammapy-ray catalogs available in gammapy.catalog but further multi-wavelength cross-matches are usually required to characterize the sources.
+Finally an object is discarded if its best-fit model is not significantly preferred over the null hypothesis (no source) comparing the difference in log-Likelihood between these two hypotheses.
+For the association and classification step, that is tightly connected to the population studies, we can a minima compare the fitted models to the set of gammapy-ray catalogs available in gammapy.catalog.
+However further multi-wavelength cross-matches are usually required to characterize the sources.

### 2022-05-02 src/text/3-applications-subsections/temporal-analysis.tex

@@
 
-The obtained flux points can be modelled using any of the available temporal and spectral models, or even using custom temporal models with spectroscopic variability.
+The obtained flux points can be analytically modelled using the available, or user-implemented temporal models.
 Alternatively, instead of  extracting a lightcurve, it is also possible to directly fit temporal models to the reduced datasets.
-By associating an appropriate SkyModel, consisting of both temporal and spectral components, to each dataset, a joint fitting across the datasets will directly return the best fit temporal and spectral parameters.
+By associating an appropriate SkyModel, consisting of both temporal and spectral components, or using custom temporal models with spectroscopic variability, to each dataset, a joint fitting across the datasets will directly return the best fit temporal and spectral parameters.

### 2022-05-02 src/figures/cube_analysis.py
make points smaller

@@ -58,7 +58,7 @@ models[2].spatial_model.to_region().to_pixel(wcs).plot(ax=ax, fill=False, lw=1, 
 rect = (0.72, 0.23, 0.26, 0.7)
 ax = fig.add_axes(rect=rect)
 ax.tick_params(labelsize=fontsize_ticks, pad=1, length=2)
-excess.plot(ax=ax, color='blue', label='excess counts')
+excess.plot(ax=ax, color='blue', label='excess counts',markersize=2)
 npred_1.plot_hist(ax=ax, label='source 1', lw=1, color='C0')
 npred_2.plot_hist(ax=ax, label='source 2', lw=1, color='C1')
 npred_3.plot_hist(ax=ax, label='source 3', lw=1, color='C2')

### 2022-05-02 src/text/2-package-subsections/estimators.tex
Add estimators bullet points

@@
 \todo{Axel Donath}
-The \verb|gammapy.estimators| sub-module features methods to compute flux
-points, light curves, flux maps, flux profiles from data.
+The \verb|gammapy.estimators| sub-module contains methods to compute flux
+points, light curves, flux profiles, flux maps and  from data.
+
+The light curve and flux profile estimation are based on the
+flux points estimation.
+
+The spectral energy distribution (SED)...
+
+There are four common quantities used for the representation of
+\gammaray spectra and flux points.
+
+\begin{table*}
+    \begin{center}
+        \begin{tabular}{lll}
+         \hline
+         Type & Description & Unit Equivalency \\
+         \hline
+         dnde & Differential flux at a given energy & $\mathrm{TeV^{-1}~cm^{2}~s^{-1}}$ \\
+         e2dnde & Differential flux at a given energy  & $\mathrm{TeV~cm^{2}~s^{-1}}$ \\
+         flux & Integrated flux in agiven energy range & $\mathrm{cm^{2}~s^{-1}}$ \\
+         eflux & Integrated energy flux in agiven energy range & $\mathrm{erg~cm^{2}~s^{-1}}$
+        \end{tabular}
+    \end{center}
+    \label{tab:sed_types}
+    \caption{Definition of sed types.}
+\end{table*}
+
+The main data structure for the result of is the `FluxMaps` class.
+The internal representation is based on a reference spectral model
+and an array of normalisation values given in energy, time and spatial bins,
+the so called "norm".
+The actual flux values are obtained by mutiplication of the norm with the
+reference flux.
+This models allows for a representation of flux values, wich are idependent
+of the SED type.
 
 The initial fine binning of \verb|MapDataset| is grouped into larger bins.
-
-Internal representation with a reference spectral model and an array of
-normalisation values given in energy, time and spatial bins.
 

### 2022-05-02 src/text/3-applications-subsections/population-studies.tex
Fix latex build

@@
-\subsection{Population studies}
+\subsection{Surveys, catalogs, and population studies}
 \label{ssec:population-studies}
-\todo{Quentin Remy}
+
+Sky surveys have a large potential for new source detections, and new phenomena discovery.
+They also offer less selection bias to perform source population studies over a large set of coherently detected and modelled objects.
+Early versions of \textit{gammapy} were developed in parallel of the preparation of the HESS Galactic plane survey catalog \citep[HGPS][]{2018A&A...612A...1H} and the associated PWN and SNR populations studies \citep{2018A&A...612A...2H, 2018A&A...612A...3H}.
+
+The increase in sensitivity  and resolution provided by new generation of instruments scale up the number of sources detectable and the complexity of the models needed to represent them accurately.
+As an example If we compare the results of the HGPS to the expectations from the CTA Galactic Plane survey simulations we jump from 78 sources detected by HESS to about 500 detectable by CTA  \citep{2021arXiv210903729R}.
+
+Studies performed on simulations not only offer a first glimpse on what could be the sky seen by CTA (according to our current knowledge on source populations), but also give us the opportunity to test the software on complex use cases\footnote{Note that the CTA-GPS simulations were performed with the \textit{ctools} package \citep{2016A&A...593A...1K} and analysed with both \textit{ctools} and \textit{gammapy} packages in order to cross-validate them.}.
+So we can  improve performances, optimize our analyses strategies, and identify the needs in term of parallelisation to process the large datasets provided by the surveys.
+
+In short the production of catalogs from gamma-ray surveys can be divided in four main steps : data-reduction; object detection; model fitting and model selection; associations and classification.
+The IACTs data-reduction step is done in the same way than described in the previous sections but scale-up to few thousand of observations.
+The object detection step consists a minima in finding local maxima in the significance, or TS maps,  given by the ExcessMapEstimator, or TSMapEstimator, respectively.
+Further refinements can include for example  filtering  and detection on these maps with techniques from scikit-image package  \citep{scikit-image}, and outlier detection from scikit-learn package \citep{scikit-learn}.
+Tests on simulations shown that it reduces the spurious detections at this stage and then speed up the next step as less objects will have to be fitted simultaneously.
+During the modelling step each object is alternatively fitted with different models in order to determine their optimal parameters, and the best-candidate model.
+The subpackage gammapy.modeling.models offers a large variety of choice, and the possibility to add custom models.
+Several spatial models (point-source, disk, gaussian...), and spectral models (power-law, log-parabola...) may be tested for each object, so the complexity of the problem increases rapidly in regions crowded with multiple extended sources.
+Finally an object is discarded if its best-fit model is not significantly preferred over the null hypothesis (no source) comparing the difference in log-Likelihood between these two hypotheses.
+For the association and classification step, that is tightly connected to the population studies, we can a minima compare the fitted models to the set of gammapy-ray catalogs available in gammapy.catalog.
+However further multi-wavelength cross-matches are usually required to characterize the sources.

### 2022-05-02 src/text/3-applications-subsections/temporal-analysis.tex
Fix latex build

@@
 In gammapy, this is done by using the LightCurveEstimator which fits the normalisation of the source in each energy band per observation, keeping other parameters constant.
-For custom time binning, an observation needs to be split into finer ones using the `Observation.select_time` method.
-Figure \ref{fig:hess_lightcurve_pks} shows the lightcurve of the blazar PKS 2155$-$304 in different energy bands as observed by the H.E.S.S.
+For custom time binning, an observation needs to be split into finer ones using the \verb"Observation.select_time method".
+Figure \ref{fig:hess_lightcurve_pks} shows the lightcurve of the blazar PKS~2155-304 in different energy bands as observed by the H.E.S.S.
 telescope during an exceptional flare on the night of July 29 - 30, 2006 \cite{2009A&A...502..749A}.
-The data is available publicly as a part of the HESS$-$DL3$-$DR1 \cite{HESS-DL3-DR1}, and shipped with GAMMAPY$_$DATA.
+The data is available publicly as a part of the HESS-DL3-DR1 \cite{HESS-DL3-DR1}, and shipped with \verb"GAMMAPY_DATA".
 Each observation is first split into 10 min smaller observations, and spectra extracted for each of these within a 0.11 deg radius around the source.
 A PowerLawSpectralModel is fit to all the datasets, leading to a reconstructed index of $3.54 \pm 0.02$.
-With this assumed spectral model the `LightCurveEstimator` run directly for two energy bands, 0.5 - 1.5 TeV, and 1.5 - 20 TeV,  respectively.
+With this assumed spectral model the \verb"LightCurveEstimator" run directly for two energy bands, 0.5 - 1.5 TeV, and 1.5 - 20 TeV,  respectively.
 
@@
 	\includegraphics[width=1.\textwidth]{figures/hess_lightcurve_pks.pdf}
-	\caption{10 min binned lightcurve for PKS~2155$-$304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in 2006.}
+	\caption{10 min binned lightcurve for PKS~2155-304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in 2006.}
 	\label{fig:hess_lightcurve_pks}

### 2022-05-02 src/data/cube-analysis/make.py

@@ -47,6 +47,7 @@ GEOM = WcsGeom.create(
 
 REGION = CircleSkyRegion(center = SkyCoord(0,0,frame='galactic', unit='deg'), radius= 0.5*u.deg)
 
+
 def get_observations():
     # Select observations
     data_store = DataStore.from_dir("../cta-galactic-center/input/index/gps")
@@ -55,7 +56,7 @@ def get_observations():
 
 
 def make_map_dataset(observations):
-    stacked = MapDataset.create(geom=GEOM,energy_axis_true=ENERGY_AXIS_TRUE)
+    stacked = MapDataset.create(geom=GEOM, energy_axis_true=ENERGY_AXIS_TRUE)
     dataset_maker = MapDatasetMaker(selection=["background", "exposure", "psf", "edisp"])
     safe_mask_masker = SafeMaskMaker(methods=["offset-max", "aeff-default"], offset_max=2.5 * u.deg)
 
@@ -66,6 +67,7 @@ def make_map_dataset(observations):
         stacked.stack(dataset)
 
     return stacked
+
 
 def simulate_counts(stacked):
 
@@ -87,11 +89,13 @@ def simulate_counts(stacked):
 
     return stacked
 
+
 def make_significance_map(stacked):
     stacked.models = []
     e = ExcessMapEstimator("0.1deg")
     result = e.run(stacked)
     return result['sqrt_ts']
+
 
 def fit_models(stacked):
     spectral_model_fit_1 = PowerLawSpectralModel(index = 2, amplitude="0.5e-12 cm-2 s-1 TeV-1", reference="1 TeV")
@@ -116,11 +120,13 @@ def fit_models(stacked):
     result = fit.run(stacked)
     return stacked.models
 
+
 def make_residual_map(stacked, models):
     stacked.models = models
     e = ExcessMapEstimator("0.1deg")
     result = e.run(stacked)
     return result['sqrt_ts']
+
 
 def make_contribution_to_region(stacked, models, region):
     spec = stacked.to_spectrum_dataset(region, containment_correction=True)

### 2022-05-02 src/text/2-package.tex
Reformat text files

--- 2022-03-23 src/text/2-package.tex
@@
 \todo{Regis and Fabio F.}
-
-\subsection{Data access and selection (DL3)}
-
-The analysis of gamma-ray data with Gammapy starts at the Data Level 3 where the data consists
-in lists of gamma-like events and their corresponding instrument response functions (IRFs).
-The latter include effective area, point spread function (PSF), energy dispersion and
-residual hadronic background. In addition there is associated meta data including information
-on the observation such as pointing direction, observation time and observation conditions.
-
-\subsection{Data reduction (DL3 to DL4)}
-
-In the next stage of the analysis the user selects a coordinates system, region or
-energy binning and events are binned into multidimensional data structures (maps)
-with the selected geometry. The instrument response is projected onto the
-same geometry as well. At this stage users can select additional background
-estimation methods, such as ring background or reflected regions and
-exclude parts of the data with high associated IRF systematics by defining
-a "safe" data range. The counts data and the reduced IRFs are bundled into
-datasets. Those datasets can be optionally grouped and stacked and are
-typically written to disk to allow users to read them back at any time later
-for modeling and fitting.
-
-\subsection{Datasets (DL4)}
-
-The datasets classes bundle reduced data in form of maps, reduced IRFs, models and
-fit statistics. Different sub-classes support different analysis methods
-and fit statistics (e.g. Poisson statistics with known background or
-with OFF background measurements). The datasets are used to perform joint-likelihood
-fitting allowing to combine different measurements, e.g. from different observations
-but also from different instruments or event classes. They can also be used for binned
-simulation as well as event sampling to simulate DL3 events data.
-
-\subsection{Modeling and Fitting (DL4 to DL5)}
-
-The next step is then typically to model and fit the datasets, either
-individually, or in a joint likelihood analysis. For this purpose Gammapy
-provides a uniform interface to multiple fitting backends. It also provides
-a variety of :ref:`built in models <model-gallery>`. This includes spectral,
-spatial and temporal model classes to describe the gamma-ray emission in the sky.
-Independently or subsequently to the global modelling, the data can be
-re-grouped to compute flux points, light curves and flux as well as significance
-maps in energy bands.
 
@@
 \todo{How to sort the sub-packages? After data flow or alphabetically? What
-	about maps?}
-\input{text/2-package-subsections/data}
-\input{text/2-package-subsections/irf}
-\input{text/2-package-subsections/maps}
+	about maps?} \input{text/2-package-subsections/data}
+\input{text/2-package-subsections/irf} \input{text/2-package-subsections/maps}
 \input{text/2-package-subsections/makers}

### 2022-05-02 src/text/3-applications-subsections/multi-instrument-analysis.tex
fixed wrong reference to figure
Reformat text files

@@
 	\caption{A multi-instrument analysis of the Crab Nebula}
-	\label{fig:multi_instrument_analysismulti_instrument_analysis}
+	\label{fig:multi_instrument_analysis}
 \end{figure*}
@@
 
-In this multi-instrument analysis example we showcase the capabilities of \gammapy
-to perform a simultaneous likelihood fit incorporating data from different instruments
-and at different levels of reduction.
-We estimate the spectrum of the Crab Nebula combining data from \fermi, \magic and \hawc.
-Maps of \fermi data are prepared selecting a region of $X^{\circ}$ around the
+In this multi-instrument analysis example we showcase the capabilities of
+\gammapy to perform a simultaneous likelihood fit incorporating data from
+different instruments and at different levels of reduction. We estimate the
+spectrum of the Crab Nebula combining data from \fermi, \magic and \hawc. Maps
+of \fermi data are prepared selecting a region of $X^{\circ}$ around the
 position of the Crab Nebula applying the same selection criteria of the 3FHL
-catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$, \citealt{3FHL}).
-%% shall we explain exactly which type of Map is created?
-The \magic data are two observations of $20\,{\rm min}$ each, chosen from the
-dataset used to estimate the performance of the upgraded stereo system \citep{magic_performance}
-and already included in \cite{joint_crab}. The observations were taken at small
-zenith angles ($<30^{\circ}$) in wobble mode \citep{fomin_1994}, with the source
-sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy range spans
-$80\,{\rm GeV} -- 20\,{\rm TeV}$. They are reduced to ON/OFF dataset before being fitted.
-\hawc flux points data are estimated in \cite{hawc_crab_2019} with $2.5\,{\rm years}$
-of data and span an energy range $300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.
+catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$,
+\citealt{3FHL}).  The \magic data are two%% shall we explain exactly which type of Map is created?
+observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
+the performance of the upgraded stereo system \citep{magic_performance} and
+already included in \cite{joint_crab}. The observations were taken at small
+zenith angles ($<30^{\circ}$) in wobble mode \citep{fomin_1994}, with the
+source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
+range spans $80\,{\rm GeV} -- 20\,{\rm TeV}$. They are reduced to ON/OFF
+dataset before being fitted. \hawc flux points data are estimated in
+\cite{hawc_crab_2019} with $2.5\,{\rm years}$ of data and span an energy range
+$300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.
 
-\gammapy automatically generates a likelihood including three different types of
-terms. Two poissonian likelihoods: one for the \fermi map and one for the ON/OFF
-counts, and a $\chi^2$ accounting for the flux points. For \fermi, a
-a three-dimensional forward folding of the sky model with the IRF is performed,
+\gammapy automatically generates a likelihood including three different types
+of terms. Two poissonian likelihoods: one for the \fermi map and one for the
+ON/OFF counts, and a $\chi^2$ accounting for the flux points. For \fermi, a a
+three-dimensional forward folding of the sky model with the IRF is performed,
 in order to compute the predicted counts in each sky-coordinate and energy bin.
-For \magic, a one-dimensional forward folding of the spectral model with the IRF
-is performed to predict the counts in each estimated energy bin.
-A log parabola is fitted to the almost fived decades in energy $10\,{\rm GeV} -- 300\,{\rm TeV}$.
-%% is the LP formula specified elsewhere?
+For \magic, a one-dimensional forward folding of the spectral model with the
+IRF is performed to predict the counts in each estimated energy bin. A log
+parabola is fitted to the almost fived decades in energy $10\,{\rm GeV} --
+	300\,{\rm TeV}$. %% is the LP formula specified elsewhere?
 
-The result of the joint fit is displayed in Fig.~\ref{multi_instrument_analysis}.
-We remark that the objective of this exercise is illustrative, we display the
-flexibility of \gammapy in simultaneously fitting multi-isntrument data even at
-different levels of reduction, we do not aim to provide a new measurement of the
-Crab Nebula spectrum.
+The result of the joint fit is displayed in
+Fig.~\ref{fig:multi_instrument_analysis}. We remark that the objective of this
+exercise is illustrative, we display the flexibility of \gammapy in
+simultaneously fitting multi-isntrument data even at different levels of
+reduction, we do not aim to provide a new measurement of the Crab Nebula
+spectrum.
 

### 2022-05-02 src/text/3-applications-subsections/population-studies.tex
Reformat text files

@@
 
-Sky surveys have a large potential for new source detections, and new phenomena discovery.
-They also offer less selection bias to perform source population studies over a large set of coherently detected and modelled objects.
-Early versions of \textit{gammapy} were developed in parallel of the preparation of the HESS Galactic plane survey catalog \citep[HGPS][]{2018A&A...612A...1H} and the associated PWN and SNR populations studies \citep{2018A&A...612A...2H, 2018A&A...612A...3H}.
+Sky surveys have a large potential for new source detections, and new phenomena
+discovery. They also offer less selection bias to perform source population
+studies over a large set of coherently detected and modelled objects. Early
+versions of \textit{gammapy} were developed in parallel of the preparation of
+the HESS Galactic plane survey catalog \citep[HGPS][]{2018A&A...612A...1H} and
+the associated PWN and SNR populations studies \citep{2018A&A...612A...2H,
+	2018A&A...612A...3H}.
 
-The increase in sensitivity  and resolution provided by new generation of instruments scale up the number of sources detectable and the complexity of the models needed to represent them accurately.
-As an example If we compare the results of the HGPS to the expectations from the CTA Galactic Plane survey simulations we jump from 78 sources detected by HESS to about 500 detectable by CTA  \citep{2021arXiv210903729R}.
+The increase in sensitivity  and resolution provided by new generation of
+instruments scale up the number of sources detectable and the complexity of the
+models needed to represent them accurately. As an example If we compare the
+results of the HGPS to the expectations from the CTA Galactic Plane survey
+simulations we jump from 78 sources detected by HESS to about 500 detectable by
+CTA  \citep{2021arXiv210903729R}.
 
-Studies performed on simulations not only offer a first glimpse on what could be the sky seen by CTA (according to our current knowledge on source populations), but also give us the opportunity to test the software on complex use cases\footnote{Note that the CTA-GPS simulations were performed with the \textit{ctools} package \citep{2016A&A...593A...1K} and analysed with both \textit{ctools} and \textit{gammapy} packages in order to cross-validate them.}.
-So we can  improve performances, optimize our analyses strategies, and identify the needs in term of parallelisation to process the large datasets provided by the surveys.
+Studies performed on simulations not only offer a first glimpse on what could
+be the sky seen by CTA (according to our current knowledge on source
+populations), but also give us the opportunity to test the software on complex
+use cases\footnote{Note that the CTA-GPS simulations were performed with the
+	\textit{ctools} package \citep{2016A&A...593A...1K} and analysed with both
+	\textit{ctools} and \textit{gammapy} packages in order to cross-validate
+	them.}. So we can  improve performances, optimize our analyses strategies, and
+identify the needs in term of parallelisation to process the large datasets
+provided by the surveys.
 
-In short the production of catalogs from gamma-ray surveys can be divided in four main steps : data-reduction; object detection; model fitting and model selection; associations and classification.
-The IACTs data-reduction step is done in the same way than described in the previous sections but scale-up to few thousand of observations.
-The object detection step consists a minima in finding local maxima in the significance, or TS maps,  given by the ExcessMapEstimator, or TSMapEstimator, respectively.
-Further refinements can include for example  filtering  and detection on these maps with techniques from scikit-image package  \citep{scikit-image}, and outlier detection from scikit-learn package \citep{scikit-learn}.
-Tests on simulations shown that it reduces the spurious detections at this stage and then speed up the next step as less objects will have to be fitted simultaneously.
-During the modelling step each object is alternatively fitted with different models in order to determine their optimal parameters, and the best-candidate model.
-The subpackage gammapy.modeling.models offers a large variety of choice, and the possibility to add custom models.
-Several spatial models (point-source, disk, gaussian...), and spectral models (power-law, log-parabola...) may be tested for each object, so the complexity of the problem increases rapidly in regions crowded with multiple extended sources.
-Finally an object is discarded if its best-fit model is not significantly preferred over the null hypothesis (no source) comparing the difference in log-Likelihood between these two hypotheses.
-For the association and classification step, that is tightly connected to the population studies, we can a minima compare the fitted models to the set of gammapy-ray catalogs available in gammapy.catalog.
-However further multi-wavelength cross-matches are usually required to characterize the sources.
+In short the production of catalogs from gamma-ray surveys can be divided in
+four main steps : data-reduction; object detection; model fitting and model
+selection; associations and classification. The IACTs data-reduction step is
+done in the same way than described in the previous sections but scale-up to
+few thousand of observations. The object detection step consists a minima in
+finding local maxima in the significance, or TS maps,  given by the
+ExcessMapEstimator, or TSMapEstimator, respectively.  Further refinements can
+include for example  filtering				and detection on these
+maps with techniques from scikit-image package	\citep{scikit-image}, and
+outlier detection from scikit-learn package \citep{scikit-learn}. Tests on
+simulations shown that it reduces the spurious detections at this stage and
+then speed up the next step as less objects will have to be fitted
+simultaneously. During the modelling step each object is alternatively fitted
+with different models in order to determine their optimal parameters, and the
+best-candidate model. The subpackage gammapy.modeling.models offers a large
+variety of choice, and the possibility to add custom models.  Several spatial
+models (point-source, disk, gaussian...), and spectral models (power-law,
+log-parabola...) may be tested for each object, so the complexity of the
+problem increases rapidly in regions crowded with multiple extended sources.
+Finally an object is discarded if its best-fit model is not significantly
+preferred over the null hypothesis (no source) comparing the difference in
+log-Likelihood between these two hypotheses. For the association and
+classification step, that is tightly connected to the population studies, we
+can a minima compare the fitted models to the set of gammapy-ray catalogs
+available in gammapy.catalog. However further multi-wavelength cross-matches
+are usually required to characterize the sources.

### 2022-05-02 src/text/4-project.tex
Reformat text files

@@
 
-In this section, we provide an overview of the organization of the Gammapy project.
-We briefly describe the main roles and responsibilities within the team, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality software.
-We use common tools and services for software development of Python open-source projects, code review, testing, package distribution and user support, with a customized solution for a versioned thoroughly tested documentation in the form of user-friendly playable tutorials.
-This section concludes with an outlook on the roadmap for future directions.
+In this section, we provide an overview of the organization of the Gammapy
+project. We briefly describe the main roles and responsibilities within the
+team, as well as the technical infrastructure designed to facilitate the
+development and maintenance of Gammapy as a high quality software. We use
+common tools and services for software development of Python open-source
+projects, code review, testing, package distribution and user support, with a
+customized solution for a versioned thoroughly tested documentation in the form
+of user-friendly playable tutorials. This section concludes with an outlook on
+the roadmap for future directions.
 
@@
 
-Gammapy is a well-organised international open-source project with a broad developer base and the presence of commitments from strong groups and institutes in the very high-energies astrophysics domain\footnote{\url{https://gammapy.org/team.html}}.
-The main development roadmaps are discussed and validated by a Coordination Committee, composed of representatives of the main contributing laboratories.
-This committee is chaired by a Project Manager and his deputy while two Lead Developers manage the development strategy and organise technical activities.
-Because of this institutionally driven characteristic, the permanent staff and commitment of supporting institutes ensure the continuity of the executive teams.
-A core team of developers from the contributing laboratories is in charge of the regular development, which benefits from punctual contributions of the community at large.
+Gammapy is a well-organised international open-source project with a broad
+developer base and the presence of commitments from strong groups and
+institutes in the very high-energies astrophysics
+domain\footnote{\url{https://gammapy.org/team.html}}. The main development
+roadmaps are discussed and validated by a Coordination Committee, composed of
+representatives of the main contributing laboratories. This committee is
+chaired by a Project Manager and his deputy while two Lead Developers manage
+the development strategy and organise technical activities. Because of this
+institutionally driven characteristic, the permanent staff and commitment of
+supporting institutes ensure the continuity of the executive teams. A core team
+of developers from the contributing laboratories is in charge of the regular
+development, which benefits from punctual contributions of the community at
+large.
 
@@
 
-Gammapy follows an open-source and open-contribution development model based on the cloud repository service GitHub.
-A GitHub organization \textit{gammapy}\footnote{\url{https://github.com/gammapy}} hosts different repositories related with the project.
-The software codebase may be found in the \textit{gammapy} repository (see Table~\ref{table:codestats:data} and Figure~\ref{fig:codestats:lang} for code lines statistics).
-We make extensive use of the pull request system to discuss and review code contributions.
+Gammapy follows an open-source and open-contribution development model based on
+the cloud repository service GitHub. A GitHub organization
+\textit{gammapy}\footnote{\url{https://github.com/gammapy}} hosts different
+repositories related with the project. The software codebase may be found in
+the \textit{gammapy} repository (see Table~\ref{table:codestats:data} and
+Figure~\ref{fig:codestats:lang} for code lines statistics). We make extensive
+use of the pull request system to discuss and review code contributions.
 
@@
 
-Several automatized tasks are set as GitHub actions\footnote{\url{https://github.com/features/actions}}, blocking the processes and alerting developers when fails occur.
-This is the case of the content integration workflow, which monitors the execution of the test coverage suite\footnote{\url{https://pytest.org}} using datasets from the \textit{gammapy-data} repository.
-Tests scan not only the codebase but also the code snippets present in docstrings of the scripts and in the RST documentation files, as well as in the tutorials provided in the form of Jupyter notebooks.
+Several automatized tasks are set as GitHub
+actions\footnote{\url{https://github.com/features/actions}}, blocking the
+processes and alerting developers when fails occur. This is the case of the
+content integration workflow, which monitors the execution of the test coverage
+suite\footnote{\url{https://pytest.org}} using datasets from the
+\textit{gammapy-data} repository. Tests scan not only the codebase but also the
+code snippets present in docstrings of the scripts and in the RST documentation
+files, as well as in the tutorials provided in the form of Jupyter notebooks.
 
-Other automatized tasks, executing in the \textit{gammapy-benchmarks} repository, are responsible for numerical validation tests and benchmarks monitoring.
-Also tasks related with the release process are partially automatized, and every contribution to the codebase repository triggers the documentation building and publishing workflow within the \textit{gammapy-docs} repository (see Sec.
-~\ref{ssec:software-distribution} and Sec.
+Other automatized tasks, executing in the \textit{gammapy-benchmarks}
+repository, are responsible for numerical validation tests and benchmarks
+monitoring. Also tasks related with the release process are partially
+automatized, and every contribution to the codebase repository triggers the
+documentation building and publishing workflow within the \textit{gammapy-docs}
+repository (see Sec. ~\ref{ssec:software-distribution} and Sec.
 ~\ref{ssec:documentation}).
 
-This small ecosystem of interconnected up-to-date repositories, automatized tasks and alerts, is just a part of a bigger set of GitHub repositories, where most of them are related with the project but not necessary for the development of the software (i.e.
-project webpage, complementary high-energy astrophysics object catalogs, coding sprints and weekly developer calls minutes, contributions to conferences, other digital assets, etc.) Finally, third-party services for code quality metrics are also set and may be found as status shields in the codebase repository.
+This small ecosystem of interconnected up-to-date repositories, automatized
+tasks and alerts, is just a part of a bigger set of GitHub repositories, where
+most of them are related with the project but not necessary for the development
+of the software (i.e. project webpage, complementary high-energy astrophysics
+object catalogs, coding sprints and weekly developer calls minutes,
+contributions to conferences, other digital assets, etc.) Finally, third-party
+services for code quality metrics are also set and may be found as status
+shields in the codebase repository.
 
@@
 
-Gammapy is distributed for Linux, Windows and Mac environments, and installed in the usual way for Python packages.
-Each stable release is uploaded to the Python package index\footnote{\url{https://pypi.org}} and as a binary package to the \textit{conda-forge} and \textit{astropy} Anaconda repository\footnote{\url{https://anaconda.org/anaconda/repo}} channels.
-At this time, Gammapy is also available as a Debian Linux package\footnote{\url{https://packages.debian.org/sid/python3-gammapy}}.
-We recommend installing the software using the \textit{conda} installation process with an environment definition file that we provide, so to work within a virtual isolated environment with additional useful packages and ensure reproducibility.
+Gammapy is distributed for Linux, Windows and Mac environments, and installed
+in the usual way for Python packages. Each stable release is uploaded to the
+Python package index\footnote{\url{https://pypi.org}} and as a binary package
+to the \textit{conda-forge} and \textit{astropy} Anaconda
+repository\footnote{\url{https://anaconda.org/anaconda/repo}} channels. At this
+time, Gammapy is also available as a Debian Linux
+package\footnote{\url{https://packages.debian.org/sid/python3-gammapy}}. We
+recommend installing the software using the \textit{conda} installation process
+with an environment definition file that we provide, so to work within a
+virtual isolated environment with additional useful packages and ensure
+reproducibility.
 
-Gammapy is indexed in Astronomy Source Code Library\footnote{\url{https://ascl.net/1711.014}} and Zenodo\footnote{\url{https://zenodo.org/record/5721467o}} digital libraries for software.
-The Zenodo record is synchronised with the codebase GitHub repository so that every release triggers the update of the versioned record.
-In addition, the next release of Gammapy will be added to the Open-source scientific Software and Service Repository\footnote{\url{https://projectescape.eu/ossr}} and indexed in the European Open Science Cloud catalog\footnote{\url{https://eosc-portal.eu}}.
+Gammapy is indexed in Astronomy Source Code
+Library\footnote{\url{https://ascl.net/1711.014}} and
+Zenodo\footnote{\url{https://zenodo.org/record/5721467o}} digital libraries for
+software. The Zenodo record is synchronised with the codebase GitHub repository
+so that every release triggers the update of the versioned record. In addition,
+the next release of Gammapy will be added to the Open-source scientific
+Software and Service Repository\footnote{\url{https://projectescape.eu/ossr}}
+and indexed in the European Open Science Cloud
+catalog\footnote{\url{https://eosc-portal.eu}}.
 
@@
 \label{ssec:documentation-and-user-support}
-Gammapy provides its user community with a tested and versioned up-to-date on-line documentation\footnote{\url{https://docs.gammapy.org}}~\citep{2019ASPC..523..357B} built with Sphinx\footnote{\url{https://www.sphinx-doc.org}} scanning the codebase Python scripts, as well as a set of RST files and Jupyter notebooks.
-The documentation includes a handwritten user guide, a set of executable tutorials, and a reference to the API automatically extracted from the code and docstrings.
-The Gammapy code snippets present in the documentation are tested in different environments using our continuous integration (CI) workflow based on GitHub actions.
+Gammapy provides its user community with a tested and versioned up-to-date
+on-line
+documentation\footnote{\url{https://docs.gammapy.org}}~\citep{2019ASPC..523..357B}
+built with Sphinx\footnote{\url{https://www.sphinx-doc.org}} scanning the
+codebase Python scripts, as well as a set of RST files and Jupyter notebooks.
+The documentation includes a handwritten user guide, a set of executable
+tutorials, and a reference to the API automatically extracted from the code and
+docstrings. The Gammapy code snippets present in the documentation are tested
+in different environments using our continuous integration (CI) workflow based
+on GitHub actions.
 
-The Jupyter notebooks tutorials are stored stripped of their output cells, which greatly helps in identifying differences in the contribution review.
-During the CI these are executed, the output cells parsed and, in case an error is found in one of the output cells then validation fails.
-Code formatting of the input cells is also done, parsing their content and using a particular syntax to provide links to the API documentation pages.
-The resulting web published tutorials also provide links to playground spaces in myBinder~\citep{project_jupyter-proc-scipy-2018}, where they may be executed on-line in versioned virtual environments hosted in the myBinder infrastructure.
-Users may also play with the tutorials locally in their laptops.
-They can download a specific version of the tutorials together with the associated datasets needed and the specific conda computing environment, using the \textit{gammapy download} command.
+The Jupyter notebooks tutorials are stored stripped of their output cells,
+which greatly helps in identifying differences in the contribution review.
+During the CI these are executed, the output cells parsed and, in case an error
+is found in one of the output cells then validation fails. Code formatting of
+the input cells is also done, parsing their content and using a particular
+syntax to provide links to the API documentation pages. The resulting web
+published tutorials also provide links to playground spaces in
+myBinder~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
+on-line in versioned virtual environments hosted in the myBinder
+infrastructure. Users may also play with the tutorials locally in their
+laptops. They can download a specific version of the tutorials together with
+the associated datasets needed and the specific conda computing environment,
+using the \textit{gammapy download} command.
 
-We have also set up a solution for users to share recipes as Jupyter notebooks that do not fit in the Gammapy core documentation but which may be relevant as specific use cases.
-Contributions happen via pull requests to the \textit{gammapy-recipes} GitHub repository and merged after a short review.
-All notebooks in the repository are tested and published in the Gammapy recipes webpage\footnote{\url{https://gammapy.github.io/gammapy-recipes}} automatically using GitHub actions.
+We have also set up a solution for users to share recipes as Jupyter notebooks
+that do not fit in the Gammapy core documentation but which may be relevant as
+specific use cases. Contributions happen via pull requests to the
+\textit{gammapy-recipes} GitHub repository and merged after a short review. All
+notebooks in the repository are tested and published in the Gammapy recipes
+webpage\footnote{\url{https://gammapy.github.io/gammapy-recipes}} automatically
+using GitHub actions.
 
-A growing community of users is gathering around the Slack messaging\footnote{\url{https://gammapy.slack.com}} and GitHub discussions\footnote{\url{https://github.com/gammapy/gammapy/discussions}} support forums, providing valuable feedback on the Gammapy functionalities, interface and documentation.
-Other communication channels have been set like mailing lists, a Twitter account\footnote{\url{https://twitter.com/gammapyST}}, regular public coding sprint meetings, hands-on session within collaborations, weekly development meetings, etc.
+A growing community of users is gathering around the Slack
+messaging\footnote{\url{https://gammapy.slack.com}} and GitHub
+discussions\footnote{\url{https://github.com/gammapy/gammapy/discussions}}
+support forums, providing valuable feedback on the Gammapy functionalities,
+interface and documentation. Other communication channels have been set like
+mailing lists, a Twitter account\footnote{\url{https://twitter.com/gammapyST}},
+regular public coding sprint meetings, hands-on session within collaborations,
+weekly development meetings, etc.
 

### 2022-05-02 src/text/2-package-subsections/analysis.tex
Reformat text files
Fix pre-commit hooks

@@
 
-The gammapy.analysis sub-module provides a  high-level interface for the most common use cases identified in gamma-ray analyses.
-The classes and methods included can be used in Python scripts, notebooks or as commands within IPython sessions.
-The high-level user interface can also be used to automatise workflows driven by parameters declared in a configuration file in YAML format.
-This way a full analysis can be executed via a single command line taking the configuration file as input.
+The gammapy.analysis sub-module provides a  high-level interface for the most
+common use cases identified in gamma-ray analyses. The classes and methods
+included can be used in Python scripts, notebooks or as commands within IPython
+sessions. The high-level user interface can also be used to automatise
+workflows driven by parameters declared in a configuration file in YAML format.
+This way a full analysis can be executed via a single command line taking the
+configuration file as input.
 
-The Analysis class has the responsability of orchestrating of the workflow defined in the configuration (AnalysisConfig) and triggering the execution of the AnalysisStep classes that defines the common use cases identified.
-These steps include the following:
- observations selection from the DataStore,  data reduction, excess map computation, model fitting, flux-points estimation, and light-curves production.
-The structure of the Analysis class allows to define custom AnalysisStep,  so ones could design and configure arbitrarily complex wokflows.
+The Analysis class has the responsibility of orchestrating of the workflow
+defined in the configuration (AnalysisConfig) and triggering the execution of
+the AnalysisStep classes that defines the common use cases identified. These
+steps include the following: observations selection from the DataStore,  data
+reduction, excess map computation, model fitting, flux-points estimation, and
+light-curves production. The structure of the Analysis class allows to define
+custom AnalysisStep,  so ones could design and configure arbitrarily complex
+wokflows.

### 2022-05-02 src/text/2-package-subsections/irf.tex
Reformat text files
Fix pre-commit hooks

@@
 \todo{Fabio Pintore}
-The {\it gammapy.irf} sub-package contains all classes and functionalities able to handle Instrument Response Functions (\irf) in a wide variety of formats.
-Usually, \irfs store instrument properties in the form of multi-dimension tables, with quantities expressed in terms of energy (true or reconstructed), off-axis angles, detector coordinates and so on.
-The main information stored in the common \gammaray \irfs are the effective area (Aeff), energy dispersion (Edisp), point spread function (PSF) and background (BKG).
-The {\it gammapy.irf} sub-package can open and access specific \irf extensions, interpolate and evaluate the quantities of interest on both energy and spatial axes, convert their format or units in different kinds, plot or write them into output files.
-In the following, we list the main sub-classes of the sub-package:
+The {\it gammapy.irf} sub-package contains all classes and functionalities able
+to handle Instrument Response Functions (\irf) in a wide variety of formats.
+Usually, \irfs store instrument properties in the form of multi-dimension
+tables, with quantities expressed in terms of energy (true or reconstructed),
+off-axis angles, detector coordinates and so on. The main information stored in
+the common \gammaray \irfs are the effective area (Aeff), energy dispersion
+(Edisp), point spread function (PSF) and background (BKG). The {\it
+		gammapy.irf} sub-package can open and access specific \irf extensions,
+interpolate and evaluate the quantities of interest on both energy and spatial
+axes, convert their format or units in different kinds, plot or write them into
+output files. In the following, we list the main sub-classes of the
+sub-package:
 
 \begin{itemize}
-\item Effective area: \gammapy provides the class {\it EffectiveAreaTable2D} to manage Aeff, which is usually defined in terms of true energy and offset angle.
-The class functionalities offer the possibility to read from files or to create it from scratch.
-{\it EffectiveAreaTable2D} can also convert, interpolate, write, and evaluate the effective area for a given energy and offset angles, or even plot the multi-dimensional Aeff table.
+	\item Effective area: \gammapy provides the class {\it EffectiveAreaTable2D} to
+	      manage Aeff, which is usually defined in terms of true energy and offset angle.
+	      The class functionalities offer the possibility to read from files or to create
+	      it from scratch. {\it EffectiveAreaTable2D} can also convert, interpolate,
+	      write, and evaluate the effective area for a given energy and offset angles, or
+	      even plot the multi-dimensional Aeff table.
 
-\item Point spread function: \gammapy allows user to treat different kinds of PSFs, in particular, multi-dimensional gaussians ({\it EnergyDependentMultiGaussPSF}), King functions ({\it PSFKing}), or a parametric one.
-The {\it EnergyDependentMultiGaussPSF} class is able to handle up to three gaussians, defined in terms of amplitudes and sigma given for each true energy and offset angle bin.
-Similarly, {\it PSFKing takes} into account the gamma and sigma parameters as defined here.
-The {\it ParametricPSF} allows to create a PSF with a representation different from gaussian(s) or King profile(s).
-Finally, the user can take advantage from the {\it PSFMap} class, which creates a multi-dimensional map of the PSF in WCS coordinates.
-At each position, a PSF kernel map ({\it PSFKernel}) provides a PSF as a function of the true energy.
-The creation of PSF kernel maps, where the PSF is defined for each sky-position, is also given to the user.
-The latter two can speed up analyses.
+	\item Point spread function: \gammapy allows user to treat different kinds of PSFs,
+	      in particular, multi-dimensional gaussians ({\it
+			      EnergyDependentMultiGaussPSF}), King functions ({\it PSFKing}), or a parametric
+	      one. The {\it EnergyDependentMultiGaussPSF} class is able to handle up to three
+	      gaussians, defined in terms of amplitudes and sigma given for each true energy
+	      and offset angle bin. Similarly, {\it PSFKing takes} into account the gamma and
+	      sigma parameters as defined here. The {\it ParametricPSF} allows to create a
+	      PSF with a representation different from gaussian(s) or King profile(s).
+	      Finally, the user can take advantage from the {\it PSFMap} class, which creates
+	      a multi-dimensional map of the PSF in WCS coordinates. At each position, a PSF
+	      kernel map ({\it PSFKernel}) provides a PSF as a function of the true energy.
+	      The creation of PSF kernel maps, where the PSF is defined for each
+	      sky-position, is also given to the user. The latter two can speed up analyses.
 
-\item Energy dispersion: Edisp, in \iact, is generally given in terms of the so called migration parameter ($\mu$), which is defined as the ratio between the reconstructed energy
-and the true energy. This ratio should be as close as one and its dispersion can assume the shape of a gaussian (or even more complex distributions). Migration parameter
-is given at each offset angle and reconstructed energy. The main sub-classes are {\it EnergyDispersion2D}, designed to interpret Edisp, {\it EDispKernelMap}, which builds an
-Edisp kernel map, i.e.
-a 4-dimensional WCS map where at each sky-position is associated an Edisp kernel.
-The latter is a representation of the Edisp as a function of the true energy only thanks to the sub-class {\it EDispKernel}.
+	\item Energy dispersion: Edisp, in \iact, is generally given in terms of the so
+	      called migration parameter ($\mu$), which is defined as the ratio between the
+	      reconstructed energy and the true energy. This ratio should be as close as one
+	      and its dispersion can assume the shape of a gaussian (or even more complex
+	      distributions). Migration parameter is given at each offset angle and
+	      reconstructed energy. The main sub-classes are {\it EnergyDispersion2D},
+	      designed to interpret Edisp, {\it EDispKernelMap}, which builds an Edisp kernel
+	      map, i.e., a 4-dimensional WCS map where at each sky-position is associated an
+	      Edisp kernel. The latter is a representation of the Edisp as a function of the
+	      true energy only thanks to the sub-class {\it EDispKernel}.
 
-\item Background: the BKG can be represented in \gammapy as either 1) a 2D map ({\it Background2D}) of count rate normalised per steradians and energy at different energies
-and offset-angles or 2) as rate per steradians and energy, as a function of reconstructed energy and detector coordinates ({\it Background3D}).
-In the former, the background is expected to follow a radially symmetric shape, while in the latter, it can be more complex.
+	\item Background: the BKG can be represented in \gammapy as either 1) a 2D map ({\it
+			      Background2D}) of count rate normalised per steradians and energy at different
+	      energies and offset-angles or 2) as rate per steradians and energy, as a
+	      function of reconstructed energy and detector coordinates ({\it Background3D}).
+	      In the former, the background is expected to follow a radially symmetric shape,
+	      while in the latter, it can be more complex.
+
 \end{itemize}
@@
 
-	\caption{In Fig.~\ref{ig*:minted:irf_examples}, we show some example of Aeff, PSF, Edisp and BKG read and plotted from a typical \irf.}
-	\label{ig*:minted:irf_examples}
-\end{figure}
+	\caption{In Fig.~\ref{ig*:minted:irf_examples}, we show some example of Aeff,
+		PSF, Edisp and BKG read and plotted from a typical \irf.}
+	\label{ig*:minted:irf_examples} \end{figure}

### 2022-05-02 src/text/2-package-subsections/stats.tex
Reformat text files
Fix pre-commit hooks

@@
 
-The gammapy.stats subpackage contains the fit statistics and associated statistical estimators
-that are commonly used in gamma-ray astronomy.
-In general, gamma-ray observations count Poisson-distributed events at various sky positions,
-and contain both signal and background events. Estimation of the number of signal events is done
-through likelihood maximization. In Gammapy, the fit statistics are Poisson log-likelihood functions
-normalized like chi-squares, i.e. they follow the expression $2 \times log L$, where $L$ is the
-likelihood function used.
-The statistic function used when the expected number of background events is known
-is the \emph{Cash} statistic ~\citep{Cash}. It is used by datasets using background
-templates such as the MapDataset. When the number of background events is unknown and
-an off measurement where only background events are expected is used, the statistic function
-is WStat. It is a profile log-likelihood statistic where background counts are
-marginalized parameters. It is used by datasets containing off counts measurements
-such as the SpectrumDatasetOnOff, used for classical spectral analysis.
+The gammapy.stats subpackage contains the fit statistics and associated
+statistical estimators that are commonly used in gamma-ray astronomy. In
+general, gamma-ray observations count Poisson-distributed events at various sky
+positions, and contain both signal and background events. Estimation of the
+number of signal events is done through likelihood maximization. In Gammapy,
+the fit statistics are Poisson log-likelihood functions normalized like
+chi-squares, i.e., they follow the expression $2 \times log L$, where $L$ is
+the likelihood function used. The statistic function used when the expected
+number of background events is known is the \emph{Cash} statistic
+~\citep{Cash}. It is used by datasets using background templates such as the
+MapDataset. When the number of background events is unknown and an off
+measurement where only background events are expected is used, the statistic
+function is WStat. It is a profile log-likelihood statistic where background
+counts are marginalized parameters. It is used by datasets containing off
+counts measurements such as the SpectrumDatasetOnOff, used for classical
+spectral analysis.
 
-To perform simple statistical estimations on counts measurements, CountsStatistic classes
-encapsulate the aforementioned statistic functions to measure excess counts and estimate the
-associated statistical significance, errors and upper limits. They perform maximum likelihood
-ratio tests to estimate significance (the square root of the statistic difference) and compute
-likelihood profiles to measure errors and upper limits. The following example allows to compute
-the Li \& Ma significance~\citep{LiMa} of a set of measurements:
+To perform simple statistical estimations on counts measurements,
+CountsStatistic classes encapsulate the aforementioned statistic functions to
+measure excess counts and estimate the associated statistical significance,
+errors and upper limits. They perform maximum likelihood ratio tests to
+estimate significance (the square root of the statistic difference) and compute
+likelihood profiles to measure errors and upper limits. The code example
+\ref{codeexample:stats} shows how to compute the Li \& Ma
+significance~\citep{LiMa} of a set of measurements.
+
+\begin{figure}
+	\import{code-examples/generated/}{gp_stats}
+	\caption{}
+	\label{codeexample:stats} \end{figure}

### 2022-05-02 src/text/3-applications-subsections/multi-instrument-analysis.tex
Fix pre-commit hooks

@@
 catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$,
-\citealt{3FHL}).  The \magic data are two%% shall we explain exactly which type of Map is created?
+~\citealt{3FHL}).  The \magic data are two%% shall we explain exactly which type of Map is created?
 observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
-the performance of the upgraded stereo system \citep{magic_performance} and
-already included in \cite{joint_crab}. The observations were taken at small
-zenith angles ($<30^{\circ}$) in wobble mode \citep{fomin_1994}, with the
+the performance of the upgraded stereo system~\citep{magic_performance} and
+already included in~\cite{joint_crab}. The observations were taken at small
+zenith angles ($<30^{\circ}$) in wobble mode~\citep{fomin_1994}, with the
 source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
 range spans $80\,{\rm GeV} -- 20\,{\rm TeV}$. They are reduced to ON/OFF
-dataset before being fitted. \hawc flux points data are estimated in
-\cite{hawc_crab_2019} with $2.5\,{\rm years}$ of data and span an energy range
-$300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.
+dataset before being fitted. \hawc flux points data are estimated
+in~\cite{hawc_crab_2019} with $2.5\,{\rm years}$ of data and span an energy
+range $300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.
 

### 2022-05-02 src/text/3-applications-subsections/population-studies.tex
Fix pre-commit hooks

@@
 \subsection{Surveys, catalogs, and population studies}
-\label{ssec:population-studies}
+\label{ssec:surveys-catalogs-and-population-studies}
 
@@
 versions of \textit{gammapy} were developed in parallel of the preparation of
-the HESS Galactic plane survey catalog \citep[HGPS][]{2018A&A...612A...1H} and
-the associated PWN and SNR populations studies \citep{2018A&A...612A...2H,
+the HESS Galactic plane survey catalog~\citep[HGPS][]{2018A&A...612A...1H} and
+the associated PWN and SNR populations studies~\citep{2018A&A...612A...2H,
 	2018A&A...612A...3H}.
@@
 simulations we jump from 78 sources detected by HESS to about 500 detectable by
-CTA  \citep{2021arXiv210903729R}.
+CTA~\citep{2021arXiv210903729R}.
 
@@
 use cases\footnote{Note that the CTA-GPS simulations were performed with the
-	\textit{ctools} package \citep{2016A&A...593A...1K} and analysed with both
+	\textit{ctools} package~\citep{2016A&A...593A...1K} and analysed with both
 	\textit{ctools} and \textit{gammapy} packages in order to cross-validate
@@
 ExcessMapEstimator, or TSMapEstimator, respectively.  Further refinements can
-include for example  filtering				and detection on these
-maps with techniques from scikit-image package	\citep{scikit-image}, and
-outlier detection from scikit-learn package \citep{scikit-learn}. Tests on
-simulations shown that it reduces the spurious detections at this stage and
-then speed up the next step as less objects will have to be fitted
-simultaneously. During the modelling step each object is alternatively fitted
-with different models in order to determine their optimal parameters, and the
-best-candidate model. The subpackage gammapy.modeling.models offers a large
-variety of choice, and the possibility to add custom models.  Several spatial
-models (point-source, disk, gaussian...), and spectral models (power-law,
-log-parabola...) may be tested for each object, so the complexity of the
-problem increases rapidly in regions crowded with multiple extended sources.
-Finally an object is discarded if its best-fit model is not significantly
-preferred over the null hypothesis (no source) comparing the difference in
-log-Likelihood between these two hypotheses. For the association and
-classification step, that is tightly connected to the population studies, we
-can a minima compare the fitted models to the set of gammapy-ray catalogs
-available in gammapy.catalog. However further multi-wavelength cross-matches
-are usually required to characterize the sources.
+include for example  filtering and detection on these maps with techniques from
+scikit-image package~\citep{scikit-image}, and outlier detection from
+scikit-learn package~\citep{scikit-learn}. Tests on simulations shown that it
+reduces the spurious detections at this stage and then speed up the next step
+as less objects will have to be fitted simultaneously. During the modelling
+step each object is alternatively fitted with different models in order to
+determine their optimal parameters, and the best-candidate model. The
+subpackage gammapy.modeling.models offers a large variety of choice, and the
+possibility to add custom models.  Several spatial models (point-source, disk,
+gaussian...), and spectral models (power-law, log-parabola...) may be tested
+for each object, so the complexity of the problem increases rapidly in regions
+crowded with multiple extended sources. Finally an object is discarded if its
+best-fit model is not significantly preferred over the null hypothesis (no
+source) comparing the difference in log-Likelihood between these two
+hypotheses. For the association and classification step, that is tightly
+connected to the population studies, we can a minima compare the fitted models
+to the set of gammapy-ray catalogs available in gammapy.catalog. However
+further multi-wavelength cross-matches are usually required to characterize the
+sources.

### 2022-05-02 src/text/3-applications-subsections/temporal-analysis.tex
Reformat text files
Fix pre-commit hooks

@@
 
-A common use case in most astrophysical scenarios is to study the temporal variability of the source.
-The most basic way to do this is to construct a lightcurve, ie, the flux of the source in each given time bin.
-In gammapy, this is done by using the LightCurveEstimator which fits the normalisation of the source in each energy band per observation, keeping other parameters constant.
-For custom time binning, an observation needs to be split into finer ones using the \verb"Observation.select_time method".
-Figure \ref{fig:hess_lightcurve_pks} shows the lightcurve of the blazar PKS~2155-304 in different energy bands as observed by the H.E.S.S.
-telescope during an exceptional flare on the night of July 29 - 30, 2006 \cite{2009A&A...502..749A}.
-The data is available publicly as a part of the HESS-DL3-DR1 \cite{HESS-DL3-DR1}, and shipped with \verb"GAMMAPY_DATA".
-Each observation is first split into 10 min smaller observations, and spectra extracted for each of these within a 0.11 deg radius around the source.
-A PowerLawSpectralModel is fit to all the datasets, leading to a reconstructed index of $3.54 \pm 0.02$.
-With this assumed spectral model the \verb"LightCurveEstimator" run directly for two energy bands, 0.5 - 1.5 TeV, and 1.5 - 20 TeV,  respectively.
+A common use case in most astrophysical scenarios is to study the temporal
+variability of the source. The most basic way to do this is to construct a
+lightcurve, ie, the flux of the source in each given time bin. In gammapy, this
+is done by using the LightCurveEstimator which fits the normalisation of the
+source in each energy band per observation, keeping other parameters constant.
+For custom time binning, an observation needs to be split into finer ones using
+the \verb"Observation.select_time method". Figure \ref{fig:hess_lightcurve_pks}
+shows the lightcurve of the blazar PKS~2155-304 in different energy bands as
+observed by the H.E.S.S. telescope during an exceptional flare on the night of
+July 29 - 30, 2006~\cite{2009A&A...502..749A}. The data is available publicly
+as a part of the HESS-DL3-DR1~\cite{HESS-DL3-DR1}, and shipped with
+\verb"GAMMAPY_DATA". Each observation is first split into 10 min smaller
+observations, and spectra extracted for each of these within a 0.11 deg radius
+around the source. A PowerLawSpectralModel is fit to all the datasets, leading
+to a reconstructed index of $3.54 \pm 0.02$. With this assumed spectral model
+the \verb"LightCurveEstimator" run directly for two energy bands, 0.5 - 1.5
+TeV, and 1.5 - 20 TeV,	respectively.
 
@@
 	\includegraphics[width=1.\textwidth]{figures/hess_lightcurve_pks.pdf}
-	\caption{10 min binned lightcurve for PKS~2155-304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in 2006.}
-	\label{fig:hess_lightcurve_pks}
-\end{figure*}
+	\caption{10 min binned lightcurve for PKS~2155-304 in two energy bands, (500
+		GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in
+		2006.} \label{fig:hess_lightcurve_pks} \end{figure*}
 
-The obtained flux points can be analytically modelled using the available, or user-implemented temporal models.
-Alternatively, instead of  extracting a lightcurve, it is also possible to directly fit temporal models to the reduced datasets.
-By associating an appropriate SkyModel, consisting of both temporal and spectral components, or using custom temporal models with spectroscopic variability, to each dataset, a joint fitting across the datasets will directly return the best fit temporal and spectral parameters.
+The obtained flux points can be analytically modelled using the available, or
+user-implemented temporal models. Alternatively, instead of  extracting a
+lightcurve, it is also possible to directly fit temporal models to the reduced
+datasets. By associating an appropriate SkyModel, consisting of both temporal
+and spectral components, or using custom temporal models with spectroscopic
+variability, to each dataset, a joint fitting across the datasets will directly
+return the best fit temporal and spectral parameters.

### 2022-05-02 src/text/4-project.tex
Fix pre-commit hooks

@@
-\section{Gammapy project}
-\label{sec:gammapy-project}
+# Custom rule to prepare multi-instrument datasets
+rule prepare_multi_instrument: input:
+"src/data/multi-instrument/input/fermi/Fermi-LAT-3FHL_data_Fermi-LAT.fits",
+"src/data/multi-instrument/input/fermi/Fermi-LAT-3FHL_iem.fits",
+"src/data/multi-instrument/input/fermi/Fermi-LAT-3FHL_datasets.yaml",
+"src/data/multi-instrument/input/fermi/Fermi-LAT-3FHL_models.yaml",
+"src/data/multi-instrument/input/magic/hdu-index.fits.gz",
+"src/data/multi-instrument/input/magic/obs-index.fits.gz",
+"src/data/multi-instrument/input/magic/20131004_05029747_DL3_CrabNebula-W0.40+035.fits",
+"src/data/multi-instrument/input/magic/20131004_05029748_DL3_CrabNebula-W0.40+215.fits",
+"src/data/multi-instrument/input/hawc/HAWC19_flux_points.fits", output:
+"src/data/multi-instrument/datasets/flux_points/crab_magic_flux_points.fits",
+"src/data/multi-instrument/datasets/flux_points/crab_fermi_flux_points.fits",
+"src/data/multi-instrument/results/crab_multi_instrument_fit.yaml", conda:
+"environment.yml" shell: "cd src/data/multi-instrument && python make.py"
+\section{Gammapy project} \label{sec:gammapy-project}
 
@@
 
-Several automatized tasks are set as GitHub
+Several automated tasks are set as GitHub
 actions\footnote{\url{https://github.com/features/actions}}, blocking the
@@
 
-Other automatized tasks, executing in the \textit{gammapy-benchmarks}
-repository, are responsible for numerical validation tests and benchmarks
-monitoring. Also tasks related with the release process are partially
-automatized, and every contribution to the codebase repository triggers the
-documentation building and publishing workflow within the \textit{gammapy-docs}
-repository (see Sec. ~\ref{ssec:software-distribution} and Sec.
-~\ref{ssec:documentation}).
+Other automated tasks, executing in the \textit{gammapy-benchmarks} repository,
+are responsible for numerical validation tests and benchmarks monitoring. Also
+tasks related with the release process are partially automated, and every
+contribution to the codebase repository triggers the documentation building and
+publishing workflow within the \textit{gammapy-docs} repository (see Sec.
+~\ref{ssec:software-distribution} and Sec. ~\ref{ssec:documentation}).
 
-This small ecosystem of interconnected up-to-date repositories, automatized
-tasks and alerts, is just a part of a bigger set of GitHub repositories, where
-most of them are related with the project but not necessary for the development
-of the software (i.e. project webpage, complementary high-energy astrophysics
+This small ecosystem of interconnected up-to-date repositories, automated tasks
+and alerts, is just a part of a bigger set of GitHub repositories, where most
+of them are related with the project but not necessary for the development of
+the software (i.e., project webpage, complementary high-energy astrophysics
 object catalogs, coding sprints and weekly developer calls minutes,
@@
 \subsection{Roadmap}
+\label{ssec:roadmap}
 \todo{Axel, Regis}

### 2022-05-02 src/text/4-project.tex
Fix tex file

@@
-# Custom rule to prepare multi-instrument datasets
-rule prepare_multi_instrument: input:
-"src/data/multi-instrument/input/fermi/Fermi-LAT-3FHL_data_Fermi-LAT.fits",
-"src/data/multi-instrument/input/fermi/Fermi-LAT-3FHL_iem.fits",
-"src/data/multi-instrument/input/fermi/Fermi-LAT-3FHL_datasets.yaml",
-"src/data/multi-instrument/input/fermi/Fermi-LAT-3FHL_models.yaml",
-"src/data/multi-instrument/input/magic/hdu-index.fits.gz",
-"src/data/multi-instrument/input/magic/obs-index.fits.gz",
-"src/data/multi-instrument/input/magic/20131004_05029747_DL3_CrabNebula-W0.40+035.fits",
-"src/data/multi-instrument/input/magic/20131004_05029748_DL3_CrabNebula-W0.40+215.fits",
-"src/data/multi-instrument/input/hawc/HAWC19_flux_points.fits", output:
-"src/data/multi-instrument/datasets/flux_points/crab_magic_flux_points.fits",
-"src/data/multi-instrument/datasets/flux_points/crab_fermi_flux_points.fits",
-"src/data/multi-instrument/results/crab_multi_instrument_fit.yaml", conda:
-"environment.yml" shell: "cd src/data/multi-instrument && python make.py"
 \section{Gammapy project} \label{sec:gammapy-project}

### 2022-05-15 src/text/2-package-subsections/estimators.tex
Write estimator sub-sectionb

@@
 \todo{Axel Donath}
-The \verb|gammapy.estimators| sub-module contains methods to compute flux
-points, light curves, flux profiles, flux maps and  from data.
+By fitting parametric models to the data, the total integrated
+flux and overall temporal, spectral and morphological shape of the
+\gammaray emission can be constrained. In many cases it useful
+to make a more detailed follow-up analysis by measuring the
+flux in smaller spectral, temporal or spatial bins. This
+possibly reveals more detailed emission features, which
+are relevant for studying correlation with counterpart emissions.
 
-The light curve and flux profile estimation are based on the
-flux points estimation.
+The \verb|gammapy.estimators| sub-module features methods to compute flux
+points, light curves, flux maps, flux profiles from data.
+The basic method for all these measurements is equivalent.
+The initial fine bins of \verb|MapDataset| are grouped into
+larger bins. The norm of the best fit "reference" spectral
+model is fitted ("scaled") in the  restricted data range only.
 
-The spectral energy distribution (SED)...
+The base class of all algorithms is the `Estimator`  class.
 
-There are four common quantities used for the representation of
-\gammaray spectra and flux points.
+Signifiance is estimated based on hypothesis \
+testing agains the background only model. This allows
+to assign a significance to the given flux bin.
+In addition to the best fit flux norm all estimators compute
+quantities corresponding to this flux. This includes
+the predicted number of total, signal and background
+counts per flux bin. The total fit statistics
+of the best fit model, the fit statistics of the
+null hypothesis and the difference between both.
+From the difference in test statistics the significance
+of the flux can be derived.
+
+Optionally it can also compute more advanced qunatities
+such as assymmetric flux errors, flux upper limits
+and one dimensional profiles of the fit statistic,
+which show how the likelihood surface varies with
+the flux norm parameter around the fit minimum.
+This information is useful  for inspecting the quality
+of the fit, where for  sane fir a parabolic
+shape of the profile is expected (see modeling / fitting section).
+
+The result of the flux point estimation are either stored in a
+\verb|FluxMaps| or \verb|FluxPoints| object. Both objects
+are based on an internal representation of the flux which is
+independent of the SED type. The flux is represented by a
+the reference spectral model and an array of
+normalisation values given in energy, time and spatial bins,
+which factorise the deviation of the flux in the given
+bin form the reference spectral model. This allows
+user to conveniently transform between different
+SED types. See Table \ref{tab:sed_types}.
+The actual flux values are obtained by mutiplication of the norm with the
+reference flux.
 
@@
 
-The main data structure for the result of is the `FluxMaps` class.
-The internal representation is based on a reference spectral model
-and an array of normalisation values given in energy, time and spatial bins,
-the so called "norm".
-The actual flux values are obtained by mutiplication of the norm with the
-reference flux.
-This models allows for a representation of flux values, wich are idependent
-of the SED type.
+Both result objects support the possibility to serialise
+the data into multiple formats. This includes the
+GADF SED (reference?) format, FITS based ND sky-maps
+and formats compatible with Astropy's \verb|Table| and
+\verb|BinnedTimeSeries| data structures. This allows
+users to directly further analyse the results, e.g.
+standard algorithms for time analysis such as
+computing Lomb-Scargle periodograms or Bayesian
+blocks for time series.
 
-The initial fine binning of \verb|MapDataset| is grouped into larger bins.
-
-No unfolding.
+So far \gammapy does not support "unfolding" of \gammaray spectra.
+Methods for this will be implement in future version of \gammapy.
 
@@
 	\item Regrouping of dataset bins in time, energy etc.
-	\item Reference spectral model scaled in energy bin
 	\item "Forward folding" / "Backward folding": but there is no
@@
 
+Code example ~\ref{fig*:minted:gp_estimators} shows how to use
+the \verb|TSMapEstimator| with a given input `MapDataset`.
+In addition to the model it allows to specify the energy
+bisn of the resulting flux and TS maps.
+
 \begin{figure}

### 2022-05-30 src/text/2-package-subsections/astro.tex
write astro

@@
 \label{ssec:gammapy-astro}
-\todo{Axel Donath}
-Dark matter models, source population modelling
+\todo{Atreyee}
+
+The gammapy.astro sub-package contains utility functions for studying physical scenarios in high energy astrophysics.
+The dark matter module computes the so called J-factors and the gamma-ray spectra expected from annihilation of dark matter in different channels according to the recipe described in \cite{2011JCAP...03..051C}.
+In the source sub-module, dedicated classes exist for modeling galactic sources according to some come physical models, eg: SNR evolution models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of PWN during the free expansion phase \citep{2006ARA&A..44...17G} or computation of physical parameters in a pulsar assumed to be a simple dipole.
+There are also dedicated tools for simulating synthetic populations based on physical models derived from observational or theoretical considerations for different classes of Galactic VHE gamma-ray emitters: PWNe, SNRs \cite{1998ApJ...504..761C}, pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y} and gamma-ray binaries.
+The gammapy.astro sub-package is currently incomplete in its description of physical scenarios, but since it works independently of the rest of the package, new classes can be added as an when required.

### 2022-05-31 src/text/2-package-subsections/astro.tex
address bruno commnts

@@
 There are also dedicated tools for simulating synthetic populations based on physical models derived from observational or theoretical considerations for different classes of Galactic VHE gamma-ray emitters: PWNe, SNRs \cite{1998ApJ...504..761C}, pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y} and gamma-ray binaries.
-The gammapy.astro sub-package is currently incomplete in its description of physical scenarios, but since it works independently of the rest of the package, new classes can be added as an when required.
+While the present list of use cases is rather preliminary, this can be enriched with time with by users and/or developers according to future needs.

### 2022-06-01 src/text/2-package-subsections/estimators.tex

@@
 Signifiance is estimated based on hypothesis \
-testing agains the background only model. This allows
+testing against the background only model. This allows
 to assign a significance to the given flux bin.
@@
 of the best fit model, the fit statistics of the
-null hypothesis and the difference between both.
-From the difference in test statistics the significance
-of the flux can be derived.
+null hypothesis and the difference between both,
+the so-called TS value.
+From the TS value the significance of the
+significance of the measured signal and associated flux
+can be derived.
 
-Optionally it can also compute more advanced qunatities
+Optionally it can also compute more advanced quantities
 such as assymmetric flux errors, flux upper limits
 and one dimensional profiles of the fit statistic,
-which show how the likelihood surface varies with
+which show how the likelihood functions varies with
 the flux norm parameter around the fit minimum.
 This information is useful for inspecting the quality
-of the fit, where for  sane fir a parabolic
-shape of the profile is expected (see modeling / fitting section).
+of the fit, where assumptoticcally a parabolic
+shape of the profile is expected at the best fit
+values (\todo{Reference to modeling / fitting section?}).
 
@@
 So far \gammapy does not support "unfolding" of \gammaray spectra.
-Methods for this will be implement in future version of \gammapy.
+Methods for this will be implemented in future version of \gammapy.
 

### 2022-06-07 src/text/2-package-subsections/maps.tex
minor changes to maps

--- 2022-02-24 src/text/2-package-subsections/maps.tex
@@
 \todo{Laura Olivera-Nieto}
-The \verb|gammapy.maps| sub-package provides classes for representing data structures associated with a set of coordinates or a region on a sphere.
-In addition it allows to handle an arbitrary number of non-spatial data dimensions, such as time or energy.
-It is organized around three types of structures: geometries, sky-maps and map axes, which inherit from the base classes Geom, Map and MapAxis respectively.
+The \verb|gammapy.maps| sub-package provides classes that represent data
+structures associated with a set of coordinates or a region on a sphere. In
+addition it allows to handle an arbitrary number of non-spatial data
+dimensions, such as time or energy. It is organized around three types of
+structures: geometries, sky-maps and map axes, which inherit from the base
+classes Geom, Map and MapAxis respectively.
 
-The geometry defines the pixelization scheme and map boundaries.
-It also provides methods to transform between sky and pixel coordinates.
-Maps consist of a geometry instance together with a data array containing the corresponding map values.
-Map axes contain a sequence of ordered values which define bins on a given dimension, spatial or not.
-Map axes can have physical units attached to them, as well as non-linear step sizes.
+The geometry object defines the pixelization scheme and map boundaries. It also
+provides methods to transform between sky and pixel coordinates. Maps consist
+of a geometry instance together with a data array containing the corresponding
+map values. Map axes contain a sequence of ordered values which define bins on
+a given dimension, spatial or not. Map axes can have physical units attached to
+them, as well as non-linear step sizes.
 
-The sub-package provides a uniform API for the FITS World Coordinate System (WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and region-based data structures.
+The sub-package provides a uniform API for the FITS World Coordinate System
+(WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and
+region-based data structure (see Figure~\cite{ig*:minted:gp_maps}).
 
@@
 \begin{itemize}
-	\item \textbf{WCS: } The FITS WCS pixelization supports a different number of projections to represent celestial spherical coordinates in a regular rectangular grid.
-Gammapy provides full support to data structures using this pixelization scheme.
-	\item \textbf{HEALPix: } This pixelization provides a subdivision of a sphere in which each pixel covers the same surface area as every other pixel.
-As a consequence, however, pixel shapes are no longer rectangular, or regular.
-\gammapy provides limited support to HEALPix-based maps, relying in some cases on projections to a local WCS grid.
-	\item \textbf{Region geometries: } In this case, instead of a fine spatial grid dividing a rectangular sky region, the spatial dimension is reduced to a single bin with an arbitrary shape, describing a region in the sky with that same shape.
-Typically they are is used together with a non-spatial dimension, for example an energy axis, to represent how a quantity varies in that dimension inside the corresponding region.
-\end{itemize}
+	\item \textbf{WCS: } The FITS WCS pixelization supports a different
+	      number of projections to represent celestial spherical coordinates in a regular
+	      rectangular grid. Gammapy provides full support to data structures using this
+	      pixelization scheme.
+	 \item \textbf{HEALPix: } This pixelization provides a
+	      subdivision of a sphere in which each pixel covers the same surface area as
+	      every other pixel. As a consequence, however, pixel shapes are no longer
+	      rectangular, or regular. \gammapy provides limited support to HEALPix-based
+	      maps, relying in some cases on projections to a local WCS grid. 
+   \item \textbf{Region geometries: } In this case, instead of a fine spatial grid
+	      dividing a rectangular sky region, the spatial dimension is reduced to a single
+	      bin with an arbitrary shape, describing a region in the sky with that same
+	      shape. Typically they are is used together with a non-spatial dimension, for
+	      example an energy axis, to represent how a quantity varies in that dimension
+	      inside the corresponding region. \end{itemize}
 
-Additionally, the MapAxis class provides a uniform API for axes representing bins on any physical quantity, such as energy or angular offset.
-The special case of time is covered by the dedicated TimeMapAxis, which allows time bins to be non-contiguous, as it is often the case with observation time-stamps.
-The generic class LabelMapAxis allows the creation of axes for non-numeric entries.
+Additionally, the MapAxis class provides a uniform API for axes representing
+bins on any physical quantity, such as energy or angular offset. The special
+case of time is covered by the dedicated TimeMapAxis, which allows time bins to
+be non-contiguous, as it is often the case with observation time-stamps. The
+generic class LabelMapAxis allows the creation of axes for non-numeric entries.
 

### 2022-06-07 src/text/2-package-subsections/maps.tex
ref not cite

@@
 (WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and
-region-based data structure (see Figure~\cite{ig*:minted:gp_maps}).
+region-based data structure (see Figure~\ref{ig*:minted:gp_maps}).
 

### 2022-06-07 src/text/3-applications-subsections/3D-analysis.tex
Reformat text files

@@
 \todo{Laura}
-The 1D analysis approach is a powerful tool to measure the spectrum of an isolated source.
-However, more complicated situations require a more careful treatment.
-In fields of view containing several overlapping sources, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region.
-Sources with extended or complex morphology can result in the measured flux being underestimated, and heavily dependent on the choice of extraction region.
-Additionally, the 1D approach neglects the energy-dependence of the PSF.
+The 1D analysis approach is a powerful tool to measure the spectrum of an
+isolated source. However, more complicated situations require a more careful
+treatment. In a field of view containing several overlapping sources, the 1D
+approach can't disentangle the contribution of each source to the total flux in
+the selected region. Sources with extended or complex morphology can result in
+the measured flux being underestimated, and heavily dependent on the choice of
+extraction region. Additionally, the 1D approach neglects the energy-dependence
+of the PSF.
 
-For such situations a more complex approach is needed, the so-called 3D analysis.
-The three relevant dimensions are the two spatial angular coordinates and an energy axis.
-In this framework, a combined spatial and spectral model (that is, a SkyModel, see Section~\ref{ssec:gammapy-modeling}) is fitted to the sky-maps that were previously derived from the data and bundled into a MapDataset (see Sections~\ref{ssec:gammapy-makers,ssec:gammapy-datasets}).
+For such situations a more complex approach is needed, the so-called 3D
+analysis. The three relevant dimensions are the two spatial angular coordinates
+and an energy axis. In this framework, a combined spatial and spectral model
+(that is, a SkyModel, see Section~\ref{ssec:gammapy-modeling}) is fitted to the
+sky-maps that were previously derived from the data and bundled into a
+MapDataset (see Sections~\ref{ssec:gammapy-makers} and~\ref{ssec:gammapy-datasets}).
 
-A thorough description of the 3D analysis approach and multiple examples that use \gammapy can be found in~\cite{Mohrmann2019}. Here we present a short example to highlight some of its advantages.
+A thorough description of the 3D analysis approach and multiple examples that
+use \gammapy can be found in~\cite{Mohrmann2019}. Here we present a short
+example to highlight some of its advantages.
 
-Starting from the \irfs corresponding to the same three simulated \cta observations used in Section~\ref{ssec:1d-analysis}, we can create a MapDataset via the MapDatasetMaker.
-However, we will not use the simulated event lists provided by \cta but instead, use the method MapDataset.fake() to simulate measured counts from the combination of several SkyModel instances.
-In this way, a DL4 dataset can directly be simulated.
-In particular we simulate:
-\begin{enumerate}
-	\item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law spectral shape.
-	\item An extended source with Gaussian morphology located at (l=0.4\textdegree, b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log-parabola spectral shape.
-	\item A large shell-like structure centered around (l=0.06\textdegree, b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree respectively and a power-law spectral shape.
-\end{enumerate}
-The position and sizes of the sources have been selected so that their contributions overlap.
-This can be clearly seen in the significance map shown in the left panel of Figure~\ref{fig:cube_analysis}.
-This map was produced with the ExcessMapEstimator (see Section~\ref{ssec:gammapy-estimators}) with a correlation radius of 0.1\textdegree.
+Starting from the \irfs corresponding to the same three simulated \cta
+observations used in Section~\ref{ssec:1d-analysis}, we can create a MapDataset
+via the MapDatasetMaker. However, we will not use the simulated event lists
+provided by \cta but instead, use the method MapDataset.fake() to simulate
+measured counts from the combination of several SkyModel instances. In this
+way, a DL4 dataset can directly be simulated. In particular we simulate:
+\begin{enumerate} \item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law
+	      spectral shape. \item An extended source with Gaussian morphology located at (l=0.4\textdegree,
+	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log-parabola spectral
+	      shape. \item A large shell-like structure centered around (l=0.06\textdegree,
+	      b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree
+	      respectively and a power-law spectral shape. \end{enumerate} The position and sizes of the sources
+have been selected so that their contributions overlap. This can be clearly
+seen in the significance map shown in the left panel of
+Figure~\ref{fig:cube_analysis}. This map was produced with the
+ExcessMapEstimator (see Section~\ref{ssec:gammapy-estimators}) with a
+correlation radius of 0.1\textdegree.
 
-We can now fit the same model shapes to the simulated data and retrieve the best-fit parameters.
-To check the model agreement, we compute the residual significance map after removing the contribution from each model.
-This is done again via the ExcessMapEstimator.
-As can be seen in the middle panel of Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$, meaning that the models describe the data sufficiently well.
+We can now fit the same model shapes to the simulated data and retrieve the
+best-fit parameters. To check the model agreement, we compute the residual
+significance map after removing the contribution from each model. This is done
+again via the ExcessMapEstimator. As can be seen in the middle panel of
+Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$,
+meaning that the models describe the data sufficiently well.
 
-As the example above shows, the 3D analysis allows to characterize the morphology of the emission and fit it together with the spectral properties of the source.
-Among the advantages that this provides is the ability to disentangle the contribution from overlapping sources to the same spatial region.
-To highlight this, we define a circular RegionGeom of radius 0.5\textdegree centered around the position of the point source, which is drawn in the left panel of Figure~\ref{fig:cube_analysis}.
-We can now compare the measured excess counts integrated in that region to the expected relative contribution from each of the three source models.
-This can be seen in the left panel of Figure~\ref{fig:cube_analysis}.
+As the example above shows, the 3D analysis allows to characterize the
+morphology of the emission and fit it together with the spectral properties of
+the source.  Among the advantages that this provides is the ability to
+disentangle the contribution from overlapping sources to the same spatial
+region. To highlight this, we define a circular RegionGeom of radius
+0.5\textdegree~ centered around the position of the point source, which is drawn
+in the left panel of Figure~\ref{fig:cube_analysis}. We can now compare the
+measured excess counts integrated in that region to the expected relative
+contribution from each of the three source models. The result can be seen in the left
+panel of Figure~\ref{fig:cube_analysis}.
 
@@
 	\includegraphics[width=1.\textwidth]{figures/cube_analysis.pdf}
-	\caption{Example 3D analysis for simulated sources using the \cta \irfs.
-The left image shows a significance map where the three simulated sources can be seen.
-The middle figure shows another significance map, but this time after subtracting the best-fit model for each of the sources, which are displayed in black.
-The right figure shows the contribution of each source model to the circular region of radius 0.5\textdegree drawn in the left image, together with the excess counts inside that region.
-	}
-	\label{fig:cube_analysis}
-\end{figure*}
+	\caption{Example 3D analysis for simulated sources using the \cta \irfs. The
+		left image shows a significance map where the three simulated sources can be
+		seen. The middle figure shows another significance map, but this time after
+		subtracting the best-fit model for each of the sources, which are displayed in
+		black. The right figure shows the contribution of each source model to the
+		circular region of radius 0.5\textdegree drawn in the left image, together with
+		the excess counts inside that region. } \label{fig:cube_analysis} \end{figure*}
 
-Note that all the models fitted also have a spectral component, from which flux points can be derived in a similar way as described in~\ref{ssec:1d-analysis}.
-%
-%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
-%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering
-%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
-%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
-%\end{figure*}
+Note that all the models fitted also have a spectral component, from which flux
+points can be derived in a similar way as described in~\ref{ssec:1d-analysis}.
+%\end{figure*}%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?%

### 2022-06-07 src/text/2-package.tex
Address more comments

--- 2022-03-30 src/text/2-package.tex
@@
 This sequence, sometimes referred to as low-level analysis, is usually very specific to
-a given observation technique if not a given instrument.
+a given observation technique and even to a given instrument.
 
@@
 
-The next step of the analysis is the data reduction on a user-defined geometry.
-A typical geometry consists in a spectral representation with a measured
+The next step of the analysis is the data reduction where all observation events and instrument
+responses are projected onto a user-defined geometry.A typical geometry consists in a spectral representation with a measured
 energy axis, and in a spatial representation, either a coordinates system  with a projection
@@
 All observation events and instrument responses are projected onto the
-target geometry. Because residual hadronic background models can be subject
-to significant uncertainties background correction must be applied,
-such as the ring or the fied-of-view background techniques or
+user defined geometry. Because residual hadronic background models can be subject
+to significant uncertainties, background correction must be applied,
+such as the ring or the field-of-view background techniques or
 background measurements must be performed within, e.g. reflected regions~\citep{Berge07}.
@@
 spatial and temporal model classes to describe the gamma-ray emission in the sky.
+Where spectral models can be simple analytical models or more complex ones from radiation
+mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{o}$ decay).
 Independently or subsequently to the global modelling, the data can be

### 2022-06-07 src/text/4-project.tex
Add section about PIGs

@@
 
-\subsection{Roadmap}
-\label{ssec:roadmap}
+\subsection{Proposals for improving \gammapy}
+\label{ssec:pigs}
 \todo{Axel, Regis}
+An important part of \gammapy's development organisation is the support
+for "Proposals for improving Gammapy" (PIG). This system is very much
+inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}
+system. PIG are self-contained documents which outline a set of larger
+changes to the \gammapy code base. This includes larger feature additions,
+code and package restructuring and maitenance as well as changes related
+to the organisational structure of the \gammapy project. PIGs can be proposed
+by any person in or outside the project and by multiple authors. They
+are presented to the \gammapy developer community in a pull request
+on GitHub and the undergo a review phase in which changes and
+improvements to the document are proposed and implemented. Once the PIG
+document is in a final state it is presented to the \gammapy
+coordination committee, which take the final decision on the
+acceptance or rejection of the proposal. Once accepted, the proposed
+change are implemented by \gammapy developers in a series of
+individual contributions via pull requests. A list of all proposed
+PIG documents is available in the \gammapy online documentation
+\footnote{\url{https://docs.gammapy.org/0.20/development/pigs/index.html}}.
 
-\begin{itemize}
-	\item pigs
-	\item roadmap
-\end{itemize}
+A special category of PIGs are long-term "roadmaps". To develop a common
+vision for all \gammapy project members on the future of the
+project, the main goals regarding planned features, maintenance and
+project organisation are written up as an overview and presented to the
+\gammapy community for discussion. The review and acceptance process
+follows the nornal PIG guidelines. Typically roadmaps are written
+to outline and agree on a common vision for the next long term
+support release of \gammapy.

### 2022-06-07 src/text/5-summary-outlook.tex
Run pre commit hook on all files
Add latexindent pre commit hook
Run tex indentation
Add draft for summary and outlook

@@
 \section{Summary and Outlook}
-\label{sec:so}
-
+\label{sec:summary-and-outlook}
 \todo{Axel and Regis write this...}
 
-Summary what we have in v0.9 and presented in this paper.
+In this manuscript we presented the first long term support  version of \gammapy.
+\gammapy is a Python package for \gammaray astronomy, which is build on the
+scientific Python ecosystem, including Numpy, Scipy and Astropy as
+main dependencies. It supports high-level analysis of astronomical \gammaray
+data from intermediate level data formats, such as the FITS based
+\gadf. Starting from lists of \gammaray events and corresponding description
+of the instrument response users can reduce and project the data
+to WCS, HEALPix and region based data structures. The reduced data is bundled
+into datasets, which serve as a basis for Poisson maximum likelihood
+modelling of the data. For this purpose \gammapy provides a wide selection
+of built-in, spectral, spatial and temporal models as well as unified
+fitting interface with connection to multiple optimization backends.
 
-Roadmap to v1.0, about half a page.
+Around the core Python package a large diverse community of
+users and contributors has developed. With regular developer meetings,
+coding sprints and in-person user tutorials at relevant conferences
+and collaboration meetings, the community has constantly grown.
+So far \gammapy has seen O(100) contributors from ~10 different countries.
+With typically ~10 regular contributors at any given time of the
+project, the code base has constantly improved its range of features
+and code quality. With \gammapy being selected as the base library
+for the future science tools for CTA, we expect the community to grow
+even further, providing a stable perspective for further usage,
+development and maintenance of the project.
 
-Short conclusion: Gammapy has potential to be the Python package for gamma-ray astronomy.
+Besides the future use by the CTA community \gammapy has already
+been used for analysis of data from the \hess and \magic instruments
+With the availability of more \gammaray data from existing Cherenkov
+telescopes, \gammaray
 
-Prospects for HAWC / SWGO? Or speak in general about water Cherenkov observatories...
+While \gammapy was mainly developed for the science community around
+IACT instruments, the data model and software design is general
+enough to be applied to other \gammaray instruments as well.
+The use of \gammapy for the analysis of data from the High Altitude
+Water Cherenkov Observatory (HAWC) has been successfully
+demonstrated by \todo{Olivera et al.}. This makes \gammapy
+a viable choice for the base library for the science tools
+of the future Southern Widefield Gamma Ray Observatory
+(SWGO) as well. \gammapy has the potential to further unify the community
+of \gammaray astronomers, by sharing common tools and
+a common vision of open and reproducible science for the future.

### 2022-06-07 src/text/5-summary-outlook.tex
Add feature outlook

@@
 fitting interface with connection to multiple optimization backends.
+
+With the v1.0 milestone the \gammapy project enters a new development
+phase. Future work will not only include maintenance of the v1.0 release,
+but also parallel development of new features, improved API and data
+model support. While v1.0 provides all the features required for
+standard and advanced astronomical \gammaray data analysis,
+we already identified specific improvements to be considered in the
+roadmap for a future v2.0 release. This includes the support for
+scalable analyses via distributed computing. This will allow
+users to scale an analysis from a few observations to multiple
+hundreds of observations as expected by deep surveys of the CTA
+observatory. In addition the high level interface
+of \gammapy is planned to be developed into a fully configurable
+API design. This will allow users to define arbitrary complex analysis
+scenarios as YAML files and even extend their workflows by user defined
+analysis steps via a registry system.
 

### 2022-06-08 src/text/5-summary-outlook.tex
Add reproducibility section

@@
+\section{Reproducibility}
+\label{sec:reproducibility}
+One of the most important goals of the \gammapy project is to support open and
+reproducible science results. Thus we decided to write this manuscript
+completely openly and publish the Latex source code and associated
+scripts in \url{https://github.com/gammapy/gammapy-v1.0-paper}.
+This GitHub repository also documents the history of the creation
+and evolution of the manuscript with time. To simplify the reproducibility
+of this manuscript including figures and text, we relied on the tool
+"showyourwork" (\todo{citation?}). This tool coordinates the building
+process and software as well as data dependencies such, that the complete
+manuscript can be reproduced with a single "make" command, after
+downloading the source repository. See \todo{reference?} for detailed
+instructions. Almost all figures in this manuscript provide a link
+to a Pythin script, that was used to produce it. This means all
+example analyses presented in Sec.\ref{sec:applications} link to
+actuallly working Python source code.
+
 \section{Summary and Outlook}

### 2022-06-08 src/text/4-project.tex
Fix typos and add APE citation

@@
 inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}
-system. PIG are self-contained documents which outline a set of larger
+and Astropy's APE \citep{greenfield_perry_2013} system.
+PIG are self-contained documents which outline a set of larger
 changes to the \gammapy code base. This includes larger feature additions,
-code and package restructuring and maitenance as well as changes related
+code and package restructuring and maintenance as well as changes related
 to the organisational structure of the \gammapy project. PIGs can be proposed
@@
 document is in a final state it is presented to the \gammapy
-coordination committee, which take the final decision on the
+coordination committee, which takes the final decision on the
 acceptance or rejection of the proposal. Once accepted, the proposed
@@
 \gammapy community for discussion. The review and acceptance process
-follows the nornal PIG guidelines. Typically roadmaps are written
+follows the normal PIG guidelines. Typically roadmaps are written
 to outline and agree on a common vision for the next long term

### 2022-06-09 src/text/5-summary-outlook.tex

@@
 reproducible science results. Thus we decided to write this manuscript
-completely openly and publish the Latex source code and associated
-scripts in \url{https://github.com/gammapy/gammapy-v1.0-paper}.
+openly and publish the Latex source code along with the associated
+Python scripts to create the figures
+in \url{https://github.com/gammapy/gammapy-v1.0-paper}.
 This GitHub repository also documents the history of the creation
@@
 of this manuscript including figures and text, we relied on the tool
-"showyourwork" (\todo{citation?}). This tool coordinates the building
+"showyourwork"~\citep{Luger2021}. This tool coordinates the building
 process and software as well as data dependencies such, that the complete
@@
 instructions. Almost all figures in this manuscript provide a link
-to a Pythin script, that was used to produce it. This means all
+to a Python script, that was used to produce it. This means all
 example analyses presented in Sec.\ref{sec:applications} link to
-actuallly working Python source code.
+actually working Python source code.
 
@@
 In this manuscript we presented the first long term support version of \gammapy.
-\gammapy is a Python package for \gammaray astronomy, which is build on the
-scientific Python ecosystem, including Numpy, Scipy and Astropy as
-main dependencies. It supports high-level analysis of astronomical \gammaray
+\gammapy is a Python package for \gammaray astronomy, which relies on the
+scientific Python ecosystem, including Numpy and Scipy and Astropy as
+main dependencies. It also holds the status of an Astropy affiliated
+package. It supports high-level analysis of astronomical \gammaray
 data from intermediate level data formats, such as the FITS based
@@
 scenarios as YAML files and even extend their workflows by user defined
-analysis steps via a registry system.
+analysis steps via a registry system. Another important topic will
+be to improve the support of handling meta data for data structures
+and provenance information to track the history of the data reduction
+process from the DL3 to the highest DL5/DL6 data levels.
 
@@
 and collaboration meetings, the community has constantly grown.
-So far \gammapy has seen O(100) contributors from ~10 different countries.
+So far \gammapy has seen ~80 contributors from ~10 different countries.
 With typically ~10 regular contributors at any given time of the
-project, the code base has constantly improved its range of features
-and code quality. With \gammapy being selected as the base library
+project, the code base has constantly grown its range of features
+and improved its code quality. With \gammapy being selected as the base library
 for the future science tools for CTA, we expect the community to grow

### 2022-06-29 src/text/1-introduction.tex
Start updating Intro

@@
 
-\todo{Axel and Regis write this...}
+Very high energy cosmic gamma-ray reaching Earth interact in the atmosphere and
+create a large shower of secondary particles that can be observed from the ground.
+Ground-based gamma-ray astronomy relies on this phenomenon to detect the
+primary gamma-ray photons and measure their direction and energy.
+It covers the energy range from fews tens of GeV up to the PeV.
+Two main instrument categories exist. Imaging Atmospheric Cherenkov
+Telescopes (IACT) make images of atmospheric showers by detecting the Cherenkov radiation
+emitted by the cascading charged particles and use these images to reconstruct
+the properties of the incident particle.
 
-Gamma-ray astronomy is a rather young field of research. By detecting and
-reconstructing arrival direction, time and energy of primary cosmic gamma-rays
-The gamma-ray sky is either observed by ground based instruments, driven by
-experiments with proprietary software often based on ROOT, because of the
-particle physics background. Such as HESS, Veritas or Magic.
+Particle samplers detect directly particles from the tail of the shower when it reaches
+the ground. These instruments have very large field-of-view, large duty-cycle but higher
+energy threshold and usually have lower signal to noise ratios compared to IACTs.
+
+Ground based gamma-ray astronomy has been historically structured
+by experiments run by independent collaborations relying
+on their own proprietary data and analysis software developed as part of the
+instrument. While this model has been very successful so far, it does not
+permit easy combination of data from several instruments and is therefore
+a limitation for interoperability of existing facilities.
 
@@
 \end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.5\textwidth]{static/gammapy-dependencies}
-	\caption{
-		The Gammapy stack. Required dependencies Numpy and Astropy are illustrated with
-		solid arrows, optional dependencies (the rest) with dashed arrows. }
-	\label{fig:dependencies}
-
-\end{figure}

### 2022-07-08 src/code-examples/snippets/gp_catalogs.py
Improve code example formatting

@@ -5,5 +5,6 @@ print("Number of sources :", len(catalog.table))
 
 source = catalog["PKS 2155-304"]
 model = source.sky_model()
-flux_points = source.flux_points
-lightcurve = source.lightcurve()
+source.flux_points.plot()
+
+source.lightcurve().plot()

### 2022-07-08 src/code-examples/snippets/gp_datasets.py

@@ -1,11 +1,16 @@
-from gammapy.datasets import MapDataset, FluxPointsDataset, Datasets
+from gammapy.datasets import (
+    MapDataset, FluxPointsDataset, Datasets
+)
 
 dataset1 = MapDataset.read(
-    "$GAMMAPY_DATA/cta-1dc-gc/cta-1dc-gc.fits.gz", name="map_dataset"
+    "$GAMMAPY_DATA/cta-1dc-gc/cta-1dc-gc.fits.gz",
+    name="map-dataset"
 )
+
 dataset2 = FluxPointsDataset.read(
     "$GAMMAPY_DATA/tests/spectrum/flux_points/diff_flux_points.fits",
-    name="fluxpoints_dataset",
+    name="flux-points-dataset",
 )
+
 datasets = Datasets([dataset1, dataset2])
 print(datasets)

### 2022-07-08 src/code-examples/snippets/gp_makers.py

@@ -1,10 +1,21 @@
-from gammapy.makers import MapDatasetMaker, FoVBackgroundMaker, SafeMaskMaker
+from gammapy.makers import (
+    MapDatasetMaker,
+    FoVBackgroundMaker,
+    SafeMaskMaker,
+)
+from gammapy.data import Observation
+
+observation = Observation.read()
 
 maker = MapDatasetMaker()
+
 bkg_maker = FoVBackgroundMaker()
-mask_maker = SafeMaskMaker()
+
+mask_maker = SafeMaskMaker(
+    method=["offset-max"], max_offset="2.5 deg"
+)
 
 dataset = maker.run(dataset, observation)
-dataset = mask_maker.run(dataset,observation)
-dataset = bkg_maker.run(dataset,observation)
-
+dataset = mask_maker.run(dataset, observation)
+dataset = bkg_maker.run(dataset, observation)
+print(dataset)

### 2022-07-08 src/code-examples/snippets/gp_maps.py

@@ -3,8 +3,10 @@ from astropy.coordinates import SkyCoord
 from astropy import units as u
 
 skydir = SkyCoord("0d", "5d", frame="galactic")
-energy_axis = MapAxis.from_bounds(lo_bnd=0.1, hi_bnd=100,
-              nbin=5, unit='TeV', interp='log', name='energy')
+
+energy_axis = MapAxis.from_energy_bounds(
+    energy_min="1 TeV", energy_max="10 TeV", nbin=10
+)
 
 # Create a WCS Map
 m_wcs = Map.create(
@@ -12,7 +14,7 @@ m_wcs = Map.create(
     map_type="wcs",
     skydir=skydir,
     width=[10.0, 8.0] * u.deg,
-    axes = [energy_axis])
+    axes=[energy_axis])
 
 
 # Create a HEALPix Map
@@ -21,11 +23,13 @@ m_hpx = Map.create(
     map_type="hpx",
     skydir=skydir,
     width=10.0 * u.deg,
-    axes = [energy_axis])
+    axes=[energy_axis]
+)
 
 # Create a region map
 region = "galactic;circle(0, 5, 1)"
 m_region = Map.create(
-    region = region,
-    map_type='region',
-    axes = [energy_axis])
+    region=region,
+    map_type="region",
+    axes=[energy_axis]
+)

### 2022-07-08 src/code-examples/snippets/gp_stats.py

@@ -4,10 +4,13 @@ n_on = [13, 5, 3]
 n_off = [11, 9, 20]
 alpha = [0.8, 0.5, 0.1]
 stat = WStatCountsStatistic(n_on, n_off, alpha)
+
 # Excess
 stat.n_sig
+
 # Significance
 stat.sqrt_ts
+
 # Asymmetrical rrors
 stat.compute_errn(1.)
 stat.compute_errp(1.)

### 2022-07-08 src/text/2-package.tex
Add package overview section

@@
 
-The \gammapy package is structured into multiple sub-packages which mostly
-follow the stages in the data reduction workflow.
-
 \subsection{Overview}
 \label{ssec:overview}
+The \gammapy package is structured into multiple sub-packages. The definition
+of the content of the different sub-packages follows mostly the stages in the
+data reduction workflow described in the previous section. Sub-packages
+either contain data structures representing data at different data reduction
+levels or contain algorithms to transition between the different data reduction
+levels.
+
+Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
+their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
+sub-packages define data objects to represent DL3 data, such as
+event lists and instrument response functions as well as functionality
+to the DL3 data from disk into memory.
+
+The \code{gammapy.makers} sub-package contains the functionality to reduce
+the data to binned maps.
+
 \begin{figure*}[t]
@@
 	\caption{
-		Gammapy sub-package structure and data analysis workflow. }
+		Gammapy sub-package structure and data analysis workflow. The top row
+        defines the groups for the different data levels and reduction steps
+        from raw gamma-like events on the left, to high level science products
+        on the right. The direction of the data flow is illustrated with the
+        grey circles. The gray folder icons represent the different sub-packages
+        in Gammapy and their names. Below each icon there is an overview of the most
+        important objects defined in the sub-package.
+    }
 	\label{fig:data_flow} \end{figure*}
 
-Outline: * List typical analysis use cases * Can use from Python and Jupyter ->
-show Figure with Jupyter notebook here. * Gammapy code structure * How Numpy
-and Astropy is used
-
-Figures: * Add a Figure showing dataflow in a typical application DL3 at the
-top, spectrum, map, lightcurve, fit results at the bottom. Mention major
-classes in between (DataStore, EventList, Map, MapMaker, MapFit, …) * Probably
-not: Figure showing sub-packages and how they relate (gammapy.data and
-gammapy.irf at the base, then gammapy.maps, etc. * The code example Figure how
-to make a counts map, to explain how the package works.
-
-\todo{How to sort the sub-packages? After data flow or alphabetically? What
-	about maps?}
 \input{text/2-package-subsections/data}

### 2022-07-08 src/code-examples/snippets/gp_data.py
Further extend code examples

@@ -1,5 +1,14 @@
 from gammapy.data import DataStore
 
-data_store = DataStore.from_dir("$GAMMAPY_DATA")
-obs_ids = [1, 2, 3]
+data_store = DataStore.from_dir(
+    "$GAMMAPY_DATA/hess-dl3-dr1"
+)
+
+obs_ids = [23523, 23526, 23559, 23592]
+
 observations = data_store.get_observations(obs_ids)
+
+for obs in observations:
+    print(f"Observation id: {obs.obs_id}")
+    print(f"Number of events: {len(obs.events)}")
+    print(f"Max. area: {obs.aeff.quantity.max()}")

### 2022-07-08 src/text/2-package-subsections/datasets.tex
Adapt sub-package descriptiosn to use code shortcut

@@
 
+\begin{figure}
+	\import{code-examples/generated/}{gp_datasets}
+	\caption{A Datasets container with a \code{FluxPointsDataset} and \code{MapDataset}}
+	\label{fig*:minted:gp_datasets}
+\end{figure}
+
 The end product of the data reduction process described in Section
 \ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps,
-at the DL4 level. The gammapy.datasets subpackage contains classes to bundle
+at the DL4 level. The \code{gammapy.datasets} subpackage contains classes to bundle
 together binned data along with associated models and the likelihood, which
@@
 modeling and fitting purposes. Depending upon the type of analysis and the
-associated statistics, different types of Datasets are supported. MapDataset is
+associated statistics, different types of Datasets are supported. \code{MapDataset} is
 used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
-done using SpectrumDatastet. While the default statistics for both of these is
-Cash, their corresponding OnOff versions are adapted for the case where the
+done using \code{SpectrumDataset}. While the default statistics for both of these is
+Cash, their corresponding on off versions are adapted for the case where the
 background is measured from real off counts, and support wstat statistics. The
-predicted counts are computed by convolution of the models with the associate
-IRFs. Fitting of precomputed flux points is enabled through FluxPointsDatasets,
+predicted counts are computed by convolution of the models with the associated
+IRFs. Fitting of precomputed flux points is enabled through \code{FluxPointsDataset},
 using chi2 statistics. Multiple datasets of same or different types can be
-bundled together in Datasets (e.g., Figure \ref{fig*:minted:gp_datasets}),
+bundled together in \code{Datasets} (e.g., Figure \ref{fig*:minted:gp_datasets}),
 where the likelihood from each constituent member is added, thus facilitating
@@
 methods.
-
-\begin{figure}
-	\import{code-examples/generated/}{gp_datasets}
-	\caption{A Datasets container with FluxPointsDataset and MapDataset}
-	\label{fig*:minted:gp_datasets}
-\end{figure}

### 2022-07-08 src/text/2-package-subsections/irf.tex
Adapt sub-package descriptiosn to use code shortcut

--- 2022-01-31 src/text/2-package-subsections/irf.tex
@@
 \todo{Fabio Pintore}
-IRF classes
+
+\begin{figure}
+	%	\import{code-examples/generated/}{gp_makers}
+
+	\caption{In Fig.~\ref{ig*:minted:irf_examples}, we show some example of Aeff,
+		PSF, Edisp and BKG read and plotted from a typical \irf.}
+	\label{ig*:minted:irf_examples}
+\end{figure}
+
+The \code{gammapy.irf} sub-package contains all classes and functionality
+to handle IRFs in a variety of formats.
+Usually, \irfs store instrument properties in the form of multi-dimension
+tables, with quantities expressed in terms of energy (true or reconstructed),
+off-axis angles, detector coordinates and so on. The main information stored in
+the common \gammaray \irfs are the effective area (Aeff), energy dispersion
+(Edisp), point spread function (PSF) and background (BKG). The \code{gammapy.irf}
+sub-package can open and access specific \irf extensions,
+interpolate and evaluate the quantities of interest on both energy and spatial
+axes, convert their format or units in different kinds, plot or write them into
+output files. In the following, we list the main sub-classes of the
+sub-package:
+
+\paragraph{Effective area:}
+\gammapy provides the class \code{EffectiveAreaTable2D} to
+manage Aeff, which is usually defined in terms of true energy and offset angle.
+The class functionalities offer the possibility to read from files or to create
+it from scratch. {\code{EffectiveAreaTable2D} can also convert, interpolate,
+write, and evaluate the effective area for a given energy and offset angles, or
+even plot the multi-dimensional Aeff table.
+
+\paragraph{Point spread function:}
+\gammapy allows user to treat different kinds of PSFs,
+in particular, parametric multi-dimensional gaussians (\code{EnergyDependentMultiGaussPSF})
+or King profile functions (\code{PSFKing})
+one. The \code{EnergyDependentMultiGaussPSF} class is able to handle up to three
+gaussians, defined in terms of amplitudes and sigma given for each true energy
+and offset angle bin. Similarly, \code{PSFKing takes} into account the gamma and
+sigma parameters as defined here. The \code{ParametricPSF} allows to create a
+PSF with a representation different from gaussian(s) or King profile(s).
+Finally, the user can take advantage from the \code{PSFMap} class, which creates
+a multi-dimensional map of the PSF in WCS coordinates. At each position, a PSF
+kernel map (\code{PSFKernel}) provides a PSF as a function of the true energy.
+The creation of PSF kernel maps, where the PSF is defined for each
+sky-position, is also given to the user. The latter two can speed up analyses.
+
+\paragraph{Energy dispersion:}
+Edisp, in \iact, is generally given in terms of the so
+called migration parameter ($\mu$), which is defined as the ratio between the
+reconstructed energy and the true energy. This ratio should be as close as one
+and its dispersion can assume the shape of a gaussian (or even more complex
+distributions). Migration parameter is given at each offset angle and
+reconstructed energy. The main sub-classes are \code{EnergyDispersion2D},
+designed to interpret Edisp, \code{EDispKernelMap}, which builds an Edisp kernel
+map, i.e., a 4-dimensional WCS map where at each sky-position is associated an
+Edisp kernel. The latter is a representation of the Edisp as a function of the
+true energy only thanks to the sub-class \code{EDispKernel}.
+
+\paragraph{Background model:}
+The BKG can be represented in \gammapy as either 1) a 2D map (\code{Background2D})
+of count rate normalised per steradians and energy at different
+energies and offset-angles or 2) as rate per steradians and energy, as a
+function of reconstructed energy and detector coordinates (\code{Background3D}).
+In the former, the background is expected to follow a radially symmetric shape,
+while in the latter, it can be more complex.

### 2022-07-08 src/text/2-package-subsections/makers.tex
Adapt sub-package descriptiosn to use code shortcut

@@
 
+\begin{figure}
+	\import{code-examples/generated/}{gp_makers}
+
+	\caption{Using gammapy.makers to reduce DL3 level data into a
+		\code{MapDataset}.}
+	\label{ig*:minted:gp_makers}
+\end{figure}
+
 The data reduction contains all tasks required to process and prepare data at
-the DL3 level for modeling and fitting. The \texttt{gammapy.makers} sub-package
+the DL3 level for modeling and fitting. The \code{gammapy.makers} sub-package
 contains the various classes and functions required to do so. First, events are
@@
 geometry. This produces counts, exposure, background, psf and energy dispersion
-maps. The \texttt{MapDatasetMaker} and \texttt{SpectrumDatasetMaker} are
+maps. The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
 responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.
@@
 background measurement in reflected regions regions, see~\cite{Berge07}.
-Specific \texttt{Makers} such as the \texttt{FoVBackgroundMaker} or the
-\texttt{ReflectedRegionsBackgroundMaker} are in charge of this step.
+Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
+\code{ReflectedRegionsBackgroundMaker} are in charge of this step.
 
 Finally, to limit other sources of systematic uncertainties, a data validity
-domain is determined by the \texttt{SafeMaskMaker}. It can be used to limit the
+domain is determined by the \code{SafeMaskMaker}. It can be used to limit the
 extent of the field of view used or to limit the energy range to e.g., a domain
 where the energy reconstruction bias is below a given value.
-
-\begin{figure}
-	\import{code-examples/generated/}{gp_makers}
-
-	\caption{Using gammapy.makers to reduce DL3 level data into a
-		\texttt{Dataset}.}
-	\label{ig*:minted:gp_makers}
-\end{figure}

### 2022-07-08 src/text/3-applications-subsections/3D-analysis.tex
Adapt application description

@@
 treatment. In a field of view containing several overlapping sources, the 1D
-approach can't disentangle the contribution of each source to the total flux in
+approach cannot disentangle the contribution of each source to the total flux in
 the selected region. Sources with extended or complex morphology can result in
@@
 and an energy axis. In this framework, a combined spatial and spectral model
-(that is, a SkyModel, see Section~\ref{ssec:gammapy-modeling}) is fitted to the
+(that is, a \code{SkyModel}, see Section~\ref{ssec:gammapy-modeling}) is fitted to the
 sky-maps that were previously derived from the data and bundled into a
-MapDataset (see Sections~\ref{ssec:gammapy-makers} and~\ref{ssec:gammapy-datasets}).
+\code{MapDataset} (see Sections~\ref{ssec:gammapy-makers} and~\ref{ssec:gammapy-datasets}).
 
@@
 Starting from the \irfs corresponding to the same three simulated \cta
-observations used in Section~\ref{ssec:1d-analysis}, we can create a MapDataset
-via the MapDatasetMaker. However, we will not use the simulated event lists
+observations used in Section~\ref{ssec:1d-analysis}, we can create a \code{MapDataset}
+via the \code{MapDatasetMaker}. However, we will not use the simulated event lists
 provided by \cta but instead, use the method MapDataset.fake() to simulate
@@
 way, a DL4 dataset can directly be simulated. In particular we simulate:
-\begin{enumerate} \item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law
-	      spectral shape. \item An extended source with Gaussian morphology located at (l=0.4\textdegree,
+
+\begin{enumerate}
+    \item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law
+	      spectral shape.
+    \item An extended source with Gaussian morphology located at (l=0.4\textdegree,
 	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log-parabola spectral
-	      shape. \item A large shell-like structure centered around (l=0.06\textdegree,
+	      shape.
+    \item A large shell-like structure centered around (l=0.06\textdegree,
 	      b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree
-	      respectively and a power-law spectral shape. \end{enumerate} The position and sizes of the sources
+	      respectively and a power-law spectral shape.
+\end{enumerate}
+
+The position and sizes of the sources
 have been selected so that their contributions overlap. This can be clearly
@@
 Figure~\ref{fig:cube_analysis}. This map was produced with the
-ExcessMapEstimator (see Section~\ref{ssec:gammapy-estimators}) with a
+\code{ExcessMapEstimator} (see Section~\ref{ssec:gammapy-estimators}) with a
 correlation radius of 0.1\textdegree.
@@
 significance map after removing the contribution from each model. This is done
-again via the ExcessMapEstimator. As can be seen in the middle panel of
+again via the \code{ExcessMapEstimator}. As can be seen in the middle panel of
 Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$,
@@
 		circular region of radius 0.5\textdegree drawn in the left image, together with
-		the excess counts inside that region. } \label{fig:cube_analysis} \end{figure*}
+		the excess counts inside that region. } \label{fig:cube_analysis}
+\end{figure*}
 

### 2022-07-08 src/text/3-applications-subsections/multi-instrument-analysis.tex
Adapt application description

@@
 exercise is illustrative, we display the flexibility of \gammapy in
-simultaneously fitting multi-isntrument data even at different levels of
+simultaneously fitting multi-instrument data even at different levels of
 reduction, we do not aim to provide a new measurement of the Crab Nebula

### 2022-07-08 src/text/3-applications-subsections/temporal-analysis.tex
Adapt application description

@@
 variability of the source. The most basic way to do this is to construct a
-lightcurve, ie, the flux of the source in each given time bin. In gammapy, this
-is done by using the LightCurveEstimator which fits the normalisation of the
+lightcurve, i.e., the flux of the source in each given time bin. In \gammapy, this
+is done by using the \code{LightCurveEstimator} which fits the normalisation of the
 source in each energy band per observation, keeping other parameters constant.
-For custom time binning, an observation needs to be split into finer ones using
-the \verb"Observation.select_time method". Figure \ref{fig:hess_lightcurve_pks}
+For custom time binning, an observation needs to be split into finer time bins using
+the \code{Observation.select\_time} method. Figure~\ref{fig:hess_lightcurve_pks}
 shows the lightcurve of the blazar PKS~2155-304 in different energy bands as
@@
 observations, and spectra extracted for each of these within a 0.11 deg radius
-around the source. A PowerLawSpectralModel is fit to all the datasets, leading
+around the source. A \code{PowerLawSpectralModel} is fit to all the datasets, leading
 to a reconstructed index of $3.54 \pm 0.02$. With this assumed spectral model
-the \verb"LightCurveEstimator" run directly for two energy bands, 0.5 - 1.5
+the \code{LightCurveEstimator} runs directly for two energy bands, 0.5 - 1.5
 TeV, and 1.5 - 20 TeV, respectively.
@@
 		GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in
-		2006.} \label{fig:hess_lightcurve_pks} \end{figure*}
+		2006.} \label{fig:hess_lightcurve_pks}
+\end{figure*}
 
@@
 lightcurve, it is also possible to directly fit temporal models to the reduced
-datasets. By associating an appropriate SkyModel, consisting of both temporal
+datasets. By associating an appropriate \code{SkyModel}, consisting of both temporal
 and spectral components, or using custom temporal models with spectroscopic

### 2022-07-08 src/text/2-package-subsections/analysis.tex

@@
 
-The gammapy.analysis sub-module provides a  high-level interface for the most
+The \code{gammapy.analysis} sub-module provides a  high-level interface for the most
 common use cases identified in gamma-ray analyses. The classes and methods
@@
 
-The Analysis class has the responsibility of orchestrating of the workflow
-defined in the configuration (AnalysisConfig) and triggering the execution of
-the AnalysisStep classes that defines the common use cases identified. These
+The \code{Analysis} class has the responsibility of orchestrating of the workflow
+defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
+the \code{AnalysisStep} classes that defines the common use cases identified. These
 steps include the following: observations selection from the DataStore,  data
 reduction, excess map computation, model fitting, flux-points estimation, and
-light-curves production. The structure of the Analysis class allows to define
+light-curves production. The structure of the \code{Analysis} class allows to define
 custom AnalysisStep, so ones could design and configure arbitrarily complex
-wokflows.
+wokflows. \todo{the latter is not true for v1.0...}

### 2022-07-08 src/text/2-package-subsections/astro.tex

--- 2022-01-31 src/text/2-package-subsections/astro.tex
@@
 \label{ssec:gammapy-astro}
-\todo{Axel Donath}
-Dark matter models, source population modelling
+\todo{Atreyee}
+
+The \code{gammapy.astro} sub-package contains utility functions for studying physical
+scenarios in high energy astrophysics. The \code{gammapy.astro.darkmatter} module
+computes the so  called J-factors and the associated gamma-ray spectra expected
+from annihilation of dark matter in different channels according to the recipe
+described in \cite{2011JCAP...03..051C}.
+
+In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modeling
+galactic \gammaray sources according to simplified physical models, eg: SNR evolution
+models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of PWN during the
+free expansion phase \citep{2006ARA&A..44...17G} or computation
+of physical parameters in a pulsar assumed to be a simple dipole.
+
+In the \code{gammapy.astro.population} sub-module there are dedicated tools
+for simulating synthetic populations based on physical models derived from
+observational or theoretical considerations for different classes of Galactic
+VHE gamma-ray emitters: PWNe, SNRs \cite{1998ApJ...504..761C},
+pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y}
+and gamma-ray binaries.
+
+While the present list of use cases is rather preliminary, this can be enriched
+with time with by users and/or developers according to future needs.

### 2022-07-08 src/text/2-package-subsections/catalog.tex

@@
 module works independently from the rest of the package, and the required
-catalogs are supplied in GAMMAPY\_DATA. Presently, catalogs from Fermi-LAT
-(standard~\citep{3FGL, 4FGL} and high energy~\citep{2FHL, 3FHL}), H.E.S.S.
-galactic plane survey~\citep{HGPS}, HAWC~\citep{2HWC, 3HWC} and gamma-cat
-~\citep{gamma-cat}; an open source gamma ray catalog combining information from
-multiple catalogs) are supported.
+catalogs are supplied in GAMMAPY\_DATA. The overview of currenly supported
+catalogs and the correponding \gammapy classes is shown in Table~\ref{tab:catalogs}.
+Newly released relevant catalogs will be added in future.
+
+\begin{table*}
+    \begin{center}
+        \begin{tabular}{llll}
+         \hline
+         Class & Shortcut & Description & Reference\\
+         \hline
+         \code{SourceCatalog3FGL} & \code{"3fgl"} & Third catalog of \fermi sources & \cite{3FGL} \\
+         \code{SourceCatalog4FGL} & \code{"4fgl"} & Fourth catalog of \fermi  sources & \cite{4FGL} \\
+         \code{SourceCatalog2FHL} & \code{"2fhl"} & Second catalog high energy \fermi  sources & \cite{2FHL} \\
+         \code{SourceCatalog3FHL} & \code{"3fhl"} & Third catalog high energy \fermi  sources & \cite{3FHL} \\
+         \code{SourceCatalog2HWC} & \code{"2hwc"} & Second catalog of \hawc sources & \cite{2HWC} \\
+         \code{SourceCatalog3HWC} & \code{"3hwc"} & Third catalog of \hawc sources & \cite{3HWC} \\
+         \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
+         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \citep{gamma-cat} \\
+         \hline
+         \end{tabular}
+    \end{center}
+    \label{tab:catalogs}
+    \caption{Built-in catalogs.}
+\end{table*}
 
@@
 		lightcurve from the Fermi-LAT 4FGL catalog for the blazar PKS 2155-304}
-	\label{codeexample:data} \end{figure}
+	\label{codeexample:data}
+\end{figure}

### 2022-07-08 src/text/2-package-subsections/data.tex

--- 2022-01-31 src/text/2-package-subsections/data.tex
@@
 \todo{Cosimo Nigro}
-The \verb|gammapy.data| sub-package provides access to DL3 level data and
-observation handling.
 
@@
 
-	\caption{Using gammapy.data to access DL3 level data with a DataStore}
+	\caption{Using \code{gammapy.data} to access DL3 level data with a \code{DataStore} object.
+    Individual observations can be accessed by their unique integer observation id number.
+    The actual events and instrument response functions can be accessed
+    as attributes on the \code{Observation} object, such as \code{.events}
+    or \code{.aeff} for the effective area information.
+    }
 	\label{fig*:minted:gp_data}
 \end{figure}
+
+As illustrated in Fig.~\ref{fig:data_flow}, the \code{gammapy.data} sub-package
+implements the interface to the lowest data level, providing the input interface to gamma-ray
+data. The \gammapy data model follows the \gadf specifications
+(Sec.~\ref{sec:introduction}), therefore gamma-ray data compliant with those
+can be directly read with the package. Version X.X of the \gadf specification
+is supported in this release version. As both the \gadf data model and \gammapy
+were initially conceived for \iact data analysis, input data are typically
+grouped in \code{Observations}, corresponding to stable periods of data
+aquisitions (typically $20 - 30\,{\rm min}$). A \code{DataStore} object,
+gathering a collection of observations, can be created providing ancillary
+files containing information about the telescope observation mode and the
+content of the data unit of each file. The \code{DataStore} allows for
+selecting a list of observations based on specific filters. As an illustrative
+example, Fig.~\ref{fig*:minted:gp_data} shows how to create a
+\code{DataStore} and how to obtain the observations corresponding to given
+identification numbers (IDs).
+
+The so-called DL3 files represented by the \code{Observation} class consist
+of two types of elements: a list of gamma-ray events with relevant physical
+quantities for the successive analysis (estimated energy, direction and arrival
+times) that is handled by the \code{EventList} class and an instrument
+response function (IRF), providing the response of the system, typically
+factorised in independent components (see the description in
+Sec.~\ref{ssec:gammapy-irf}). The separate handling of event lists and IRFs
+additionally allows for data from other gamma-ray instruments to be read. For
+example, to read \fermi data, the user can read separately their event list
+(already compliant with the \gadf specifications) and then find the appropriate
+IRF class representing the response functions provided by \fermi, see
+Sec.~\ref{ssec:fermi}.

### 2022-07-08 src/text/2-package-subsections/estimators.tex

@@
 
-The \verb|gammapy.estimators| sub-module features methods to compute flux
+The \code{gammapy.estimators} sub-module features methods to compute flux
 points, light curves, flux maps, flux profiles from data.
 The basic method for all these measurements is equivalent.
-The initial fine bins of \verb|MapDataset| are grouped into
+The initial fine bins of \code{MapDataset} are grouped into
 larger bins. The norm of the best fit "reference" spectral
@@
 
-The base class of all algorithms is the `Estimator`  class.
+The base class of all algorithms is the \code{Estimator}  class.
 
-Signifiance is estimated based on hypothesis \
+Signifiance is estimated based on hypothesis
 testing against the background only model. This allows
@@
 The result of the flux point estimation are either stored in a
-\verb|FluxMaps| or \verb|FluxPoints| object. Both objects
+\code{FluxMaps} or \code{FluxPoints} object. Both objects
 are based on an internal representation of the flux which is
@@
 GADF SED (reference?) format, FITS based ND sky-maps
-and formats compatible with Astropy's \verb|Table| and
-\verb|BinnedTimeSeries| data structures. This allows
+and formats compatible with Astropy's \code{Table} and
+\code{BinnedTimeSeries} data structures. This allows
 users to directly further analyse the results, e.g.
@@
 computing Lomb-Scargle periodograms or Bayesian
-blocks for time series.
-
-So far \gammapy does not support "unfolding" of \gammaray spectra.
+blocks for time series. So far \gammapy does not
+support "unfolding" of \gammaray spectra.
 Methods for this will be implemented in future version of \gammapy.
 
-\begin{itemize}
-	\item Regrouping of dataset bins in time, energy etc.
-	\item "Forward folding" / "Backward folding": but there is no
-	      difference between the two, backwards folding is forward folding with one bin
-	\item Likelihood profiles \item Uniform N-dimensional data structure \item
-	      Uniform API for plotting etc. \item \verb|FluxMaps| and \verb|FluxPoints| \item
-	      Serialisation to multiple formats, Astropy's \verb|Table| and
-	      \verb|BinnedTimeSeries|
-	\item Additional quantities for debugging, such as predicted counts, fit convergence,
-	      sum of fit statistics \item \end{itemize}
-
 Code example ~\ref{fig*:minted:gp_estimators} shows how to use
-the \verb|TSMapEstimator| with a given input `MapDataset`.
+the \code{TSMapEstimator} objects with a given input \code{MapDataset}.
 In addition to the model it allows to specify the energy
-bisn of the resulting flux and TS maps.
+bins of the resulting flux and TS maps.
 
@@
 	\import{code-examples/generated/}{gp_estimators}
-	\caption{Using the TSMapEstimator from gammapy.estimators to compute a
-		sqrt(TS) map.} \label{fig*:minted:gp_estimators} \end{figure}
+	\caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
+        a flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
+        and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
+        of the flux error and and flux upper limit maps respectively.
+    }
+    \label{fig*:minted:gp_estimators}
+\end{figure}

### 2022-07-08 src/text/2-package-subsections/maps.tex

@@
 \todo{Laura Olivera-Nieto}
-The \verb|gammapy.maps| sub-package provides classes that represent data
+
+\begin{figure}
+	\import{code-examples/generated/}{gp_maps}
+
+	\caption{Using \code{gammapy.maps} to create a WCS, a HEALPix and a region
+		based data structures. The initialisation parameters include
+        consistently the positions of the center of the map, the pixel
+        size, the extend of the map as well as the energy axis definition.
+        } \label{ig*:minted:gp_maps}
+\end{figure}
+
+The \code{gammapy.maps} sub-package provides classes that represent data
 structures associated with a set of coordinates or a region on a sphere. In
@@
 structures: geometries, sky-maps and map axes, which inherit from the base
-classes Geom, Map and MapAxis respectively.
+classes \code{Geom}, \code{Map} and \code{MapAxis} respectively.
 
@@
 provides methods to transform between sky and pixel coordinates. Maps consist
-of a geometry instance together with a data array containing the corresponding
+of a geometry instance together with a Numpy data array containing the corresponding
 map values. Map axes contain a sequence of ordered values which define bins on
 a given dimension, spatial or not. Map axes can have physical units attached to
-them, as well as non-linear step sizes.
+them, as well as define non-linear spaced bins.
 
@@
 % itemize because it helps me write, could also just be paragraphs...
-\begin{itemize}
-	\item \textbf{WCS: } The FITS WCS pixelization supports a different
+\paragraph{WCS:}
+The FITS WCS pixelization supports a different
 number of projections to represent celestial spherical coordinates in a regular
@@
 pixelization scheme.
-	 \item \textbf{HEALPix: } This pixelization provides a
+
+\paragraph{HEALPix:}
+This pixelization provides a
 subdivision of a sphere in which each pixel covers the same surface area as
@@
 maps, relying in some cases on projections to a local WCS grid.
-   \item \textbf{Region geometries: } In this case, instead of a fine spatial grid
+
+\paragraph{Region:} In this case, instead of a fine spatial grid
 dividing a rectangular sky region, the spatial dimension is reduced to a single
@@
 example an energy axis, to represent how a quantity varies in that dimension
-	      inside the corresponding region. \end{itemize}
+inside the corresponding region.
 
-Additionally, the MapAxis class provides a uniform API for axes representing
+Additionally, the \code{MapAxis} class provides a uniform API for axes representing
 bins on any physical quantity, such as energy or angular offset. The special
-case of time is covered by the dedicated TimeMapAxis, which allows time bins to
+case of time is covered by the dedicated \code{TimeMapAxis}, which allows time bins to
 be non-contiguous, as it is often the case with observation time-stamps. The
-generic class LabelMapAxis allows the creation of axes for non-numeric entries.
-
-\begin{figure}
-	\import{code-examples/generated/}{gp_maps}
-
-	\caption{Using gammapy.maps to create a WCS, a HEALPix and a region
-		map. Note the uniform API for map creation.} \label{ig*:minted:gp_maps}
-\end{figure}
+generic class \code{LabelMapAxis} allows the creation of axes for non-numeric
+entries.

### 2022-07-08 src/text/2-package-subsections/modeling.tex
Fix section level for modeling section
Fix pre-commit hooks

@@
 
-gammapy.modeling contains all the functionality related to modeling and fitting
+\code{gammapy.modeling} contains all the functionality related to modeling and fitting
 data. This includes spectral, spatial and temporal model classes, as well as
@@
 
-\subsection{Models}
-\label{ssec:models}
+\subsubsection{Models}
+\label{sssec:models}
 
@@
 \begin{itemize}
-	\item SpectralModel: models to describe spectral shapes of sources
-	\item SpatialModel: models to describe spatial shapes (morphologies) of sources
-	\item TemporalModel: models to describe temporal flux evolution of sources, such as
+	\item \code{SpectralModel}: models to describe spectral shapes of sources
+	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
+	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
 	      light and phase curves
@@
 
-The  Spectral Models include a special class of Normed models, which have a
+The spectral models include a special class of normed models, which have a
 dimension-less normalisation. These spectral models feature a norm parameter
@@
 adjusting template based models, or adding a EBL correction to some analytic
-model. The analytic Spatial models are all normalized such as they integrate to
-unity over the sky but the template Spatial models may not, so in that special
-case they have to be combined with a NormSpectralModel.
+model. The analytic spatial models are all normalized such as they integrate to
+unity over the sky but the template spatial models may not, so in that special
+case they have to be combined with a \code{NormSpectralModel}.
 
-The SkyModel is a factorised model that combine the spectral, spatial and
-temporal model components (by default the spatial and temporal components are
+The \code{SkyModel} object represents factorised model that combine the spectral,
+spatial and temporal model components (by default the spatial and temporal components are
 optional). SkyModel objects represents additive emission components, usually
 sources or diffuse emission, although a single source can also be modeled by
-multiple components. To handle list of multiple SkyModel components, Gammapy
-has a Models class.
+multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
+has a \code{Models} class.
 
 The model gallery provides a visual overview of the available models in
-Gammapy. Most of the analytic models  commonly used in gamma-ray astronomy are
+\gammapy. Most of the analytic models  commonly used in gamma-ray astronomy are
 built-in. We also offer a wrapper to radiative models implemented in the Naima
@@
 processes in jetted Active Galactic Nuclei (AGN) can wrapped into
-gammapy~\citep[see section3.5 of ][]{2021arXiv211214573N} .
+\gammapy~\citep[see section3.5 of ][]{2021arXiv211214573N} .
 
@@
 	\import{code-examples/generated/}{gp_models}
-	\caption{Using gammapy.modeling.models}
+	\caption{Using \code{gammapy.modeling.models} to define a source model with a
+    spectral, spatial and temporal component. For convenience the model
+    parameters can be defined as strings with attached units. The spatial model
+    takes an addtional \code{frame} parameter which allow users to define
+    the coordinate frame of the position of the model.
+    }
 	\label{fig*:minted:gp_models}
@@
 
-\subsection{Fit}
-\label{ssec:fit}
+\subsubsection{Fit}
+\label{sssec:fit}
 
-The Fit class provides methods to fit i.e., optimise parameters and estimate
+The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
 parameter errors and correlations. It interfaces with a Datasets object, which
@@
 multiple datasets and thus provide links, allowing e.g., to do a joint fit to
-multiple IACT datasets, or to a joint IACT and \textit{Fermi}-LAT dataset. Many
+multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
 examples are given in the tutorials.
+
+\todo{Add fit code example...}
 

### 2022-07-08 src/text/3-applications-subsections/1D-analysis.tex
Reformat text files

@@
 spectrum of a source in a given region defined on the sky, in conventional
-astronomy also called aperture photometry.
-The spectrum is typically measured in two steps: first a parametric
-spectral model is fitted to the data and secondly flux points are computed
-in a pre-defined set of energy bins.
-The result of such an analysis performed on three simulated CTA observations
-is shown in Fig.~\ref{fig:cta_galactic_center}.
-In this case the spectrum was measured in a circular aperture centered
-on the Galactic Center, in \gammaray~astronomy often called "on region".
-For such analysis the users first chooses a region of interest
-and energy binning, both defined by a `RegionGeom`.
-In a second step the events and instrument response are binned into
-maps of this geometry, by the `SpectrumDatasetMaker`.
-All the data and reduced instrument response are bundled into a
-`SpectrumDataset`.
-To estimate the expected background in the on region a "reflected regions"
-background method was used~\cite{Berge07}, represented in \gammapy
-by the `ReflectedRegionsBackgroundMaker` class.
-The resulting reflected regions are illustrated for all three observations
-on top of the map of counts.
-After reduction of the data it was modelled using a forward-folding
-method and a power-law spectral shape, using the `PowerLawSpectralModel`
-and `Fit` class.
-Based on this best fit model the final flux points and
-corresponding log-likleihood profiles are computed using
-the `FluxPointsEstimator`.
+astronomy also called aperture photometry. The spectrum is typically measured
+in two steps: first a parametric spectral model is fitted to the data and
+secondly flux points are computed in a pre-defined set of energy bins. The
+result of such an analysis performed on three simulated CTA observations is
+shown in Fig.~\ref{fig:cta_galactic_center}. In this case the spectrum was
+measured in a circular aperture centered on the Galactic Center, in
+\gammaray~astronomy often called "on region". For such analysis the users first
+chooses a region of interest and energy binning, both defined by a
+\code{RegionGeom}. In a second step the events and instrument response are binned
+into maps of this geometry, by the \code{SpectrumDatasetMaker}. All the data and
+reduced instrument response are bundled into a \code{SpectrumDataset}. To estimate
+the expected background in the on region a "reflected regions" background
+method was used~\cite{Berge07}, represented in \gammapy by the
+\code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
+illustrated for all three observations on top of the map of counts. After
+reduction of the data it was modelled using a forward-folding method and a
+power-law spectral shape, using the \code{PowerLawSpectralModel} and \code{Fit} class.
+Based on this best fit model the final flux points and corresponding
+log-likelihood profiles are computed using the \code{FluxPointsEstimator}.
 
@@
 	\caption{
-        Example spectral analysis of the Galactic Center for three simulated CTA observations.
-        The left image shows the maps of counts with the measurement region and background
-        regions overlaid in different colors. The right image shows the resulting spectral
-        points and their corresponding log-likelihood profiles.
-    }
-	\label{fig:cta_galactic_center}
-\end{figure*}
+		Example spectral analysis of the Galactic Center for three simulated CTA
+		observations. The left image shows the maps of counts with the measurement
+		region and background regions overlaid in different colors. The right image
+		shows the resulting spectral points and their corresponding log-likelihood
+		profiles.} \label{fig:cta_galactic_center} \end{figure*}

### 2022-07-11 src/text/1-introduction.tex
Update introduction

@@
 It covers the energy range from fews tens of GeV up to the PeV.
-Two main instrument categories exist. Imaging Atmospheric Cherenkov
-Telescopes (IACT) make images of atmospheric showers by detecting the Cherenkov radiation
-emitted by the cascading charged particles and use these images to reconstruct
-the properties of the incident particle.
+Two main instrument categories exist \citep{2015CRPhy..16..610D}.
+Imaging Atmospheric Cherenkov Telescopes (IACT) make images of atmospheric showers
+by detecting the Cherenkov radiation emitted by the cascading charged particles and
+use these images to reconstruct the properties of the incident particle.
 
@@
 
-The Cherenkov Telescope Array (CTA) will be operated as an open observatory for
-the first time. Thus there is a need for open analysis software as well.
+The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
+as an open observatory in the domain. Its data will be shared Thus there is a need for open analysis software as well.
 

### 2022-07-21 src/text/1-introduction.tex
Additions

@@
 The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
-as an open observatory in the domain. Its data will be shared Thus there is a need for open analysis software as well.
+as an open observatory in the domain. Its data will be shared
+Thus there is a need for open analysis software as well.
 
@@
 
-In recent years Python \footnote{\PythonUrl} has established as one of the
-standard programming  languages for astronomy \footnote{Citation missing} as
-well as data sciences in  general \footnote{Citation missing}. The success is
+Python has become extremely popular as a scientific programming language
+in particular in the field of data sciences. The success is
 mostly attributed to the simple and easy to learn syntax, the ability to act as
@@
 of packages and the open and supportive community.
+
+ one of the
+standard programming  languages for astronomy \footnote{Citation missing} as
+well as data sciences in  general \footnote{Citation missing}.
 
@@
 
-The short-term success of Pythion lead to a prolifaration of packages, until
+The short-term success of Python lead to a prolifaration of packages, until
 \astropy~\citep{astropy} was created in 2012. Astropy is and Gammapy is a

### 2022-07-21 src/text/1-introduction.tex
Further modifications

@@
 
-The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
-as an open observatory in the domain. Its data will be shared
-Thus there is a need for open analysis software as well.
-
-Moreover, the operation of CTA as an observatory introduces the necessity of
-sharing its data publicly. The data-reduction workflow of different IACTs of
-the current generation is remarkably similar, resulting in a \textit{high} data
-level that can be finally used to derive scientific results (, spectra, sky
-maps, light curves). The information in this high data level is independent on
+Yet, the data-reduction workflow of different IACTs of the current generation is
+remarkably similar. After data calibration, shower events are reconstructed and
+gamma/hadron separation is applied to build lists of gamma-ray like events.
+The latter are then used to derive scientific results, such as spectra, sky maps
+or light curves, taking into account the Instrument Response Functions (IRF).
+The information in this high data level is independent on
 the data reduction, and eventually of the detection technique. This implies,
 for example, that data from IACT and WCD can be represented within the same
-model. The efforts to prototype the future CTA data model and to convert
-current IACT data in a format usable with the newly-available science tools
+model. The efforts to prototype a format usable by various instruments
 converged in the so-called \textit{Data Format for Gamma-ray Astronomy}
@@
 (energy, direction, arrival time) and a parametrisation of the response of the
-system (see Sec.~\ref{ssec:gammapy-data} and Sec.~\ref{ssec:gammapy-irf} for
+system. (see Sec.~\ref{ssec:gammapy-data} and Sec.~\ref{ssec:gammapy-irf} for
 more information).
+
+The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
+as an open observatory in the domain. Its high level data will be shared publicly after
+some proprietary period and the software required to analyze it will be distributed
+as well.
 
@@
 % TODO: describe goals
+The H.E.S.S. collaboration released a limited test dataset (about 50 hours of
+observations taken between 2004 and 2008) based  on the GADF DL3 format \citep{HESS_DR1}.
+This data release served as a basis for analysis tools validation \cite[see e.g.]{Mohrmann2019}.
+% TODO : discuss joint crab paper?
 
@@
 TODO: Figure 2: Gammapy software stack
-
-Here's a list of references I'd like to cite ... to be incorporated into the
-main text somewhere:
-
-\begin{itemize}
-	\item Gammapy webpage\footnote{\GammapyUrl}
-	\item Naima\footnote{\NaimaUrl}~\citep{Naima}
-	\item Gammapy use in science publications:~\citep{Owen2015}, SNR shell, HGPS
-\end{itemize}
-
-* Gammapy – A Python package for gamma-ray astronomy
-* Gammapy – A prototype for the CTA science tools
-* Astropy: A community Python package for astronomy
-* THE ASTROPY PROJECT: BUILDING AN INCLUSIVE, OPEN-SCIENCE PROJECT AND STATUS
-OF THE V2.0 CORE PACKAGE * GammaLib and ctools * Fermipy proceedings * SunPy:
-Python for Solar Physics. An implementation for local correlation tracking *
 

### 2022-07-22 src/text/1-introduction.tex

@@
 
+%% Gamma-ray astronomy
 Very high energy cosmic gamma-ray reaching Earth interact in the atmosphere and
@@
 
+%% Context
 Ground based gamma-ray astronomy has been historically structured
@@
 
-Yet, the data-reduction workflow of different IACTs of the current generation is
-remarkably similar. After data calibration, shower events are reconstructed and
+%TODO: better transition into context
+The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
+as an open observatory in the domain. Its high level data will be shared publicly after
+some proprietary period and the software required to analyze it will be distributed
+as well. To allow the re-usability of existing instruments and their interoperability
+requires open data formats and open tools that can support the various analysis methods
+commonly used in the field.
+
+%% Context : formats
+In practice, the data-reduction workflow of IACTs is remarkably similar.
+After data calibration, shower events are reconstructed and
 gamma/hadron separation is applied to build lists of gamma-ray like events.
@@
 the data reduction, and eventually of the detection technique. This implies,
-for example, that data from IACT and WCD can be represented within the same
-model. The efforts to prototype a format usable by various instruments
+for example, that data from IACT and particle samplers can be represented
+within the same model. The efforts to prototype a format usable by various instruments
 converged in the so-called \textit{Data Format for Gamma-ray Astronomy}
@@
 
-The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
-as an open observatory in the domain. Its high level data will be shared publicly after
-some proprietary period and the software required to analyze it will be distributed
-as well.
-
+%% Context: develoment of open software
 Python has become extremely popular as a scientific programming language
@@
 mostly attributed to the simple and easy to learn syntax, the ability to act as
-a "glue" language between different programming languages, the rich eco-system
-of packages and the open and supportive community.
+a "glue" language between different programming languages and last but not least
+the rich eco-system of packages and its open and supportive community, from
+core numerical analysis packages such as numpy \citep{numpy} and
+scipy \citep{2020SciPy-NMeth}, visualization libraries,e.g. matplotlib \citep{matplotlib},
+or optimization packages such as iminuit \citep{iminuit}.
 
- one of the
-standard programming  languages for astronomy \footnote{Citation missing} as
-well as data sciences in  general \footnote{Citation missing}.
+The \astropy~\citep{astropy} was created in 2012 to build a community-developed
+ python package for astronomical reasearch. Among other things, the it offers functionality for
+transforming and representing astronomical coordinates, manipulating physical quantities
+and their units as well as reading and writing FITS files.
 
-Astronomical data analysis software written in Python existed since 2000. e.g.,
-sherpa~\citep{sherpa-2011, sherpa-2009}, or for gamma-ray even PyFACT
-~\citep{pyfact}.
+%% Gammapy: concept and goals
+%%% Question: starting date? Is is relevant, what is the real start?
+The Gammapy project started in 2015 with the objective of building a flexible and
+efficient software library for very high energy gamma-ray data analysis \citep{gammapy_2015}.
+This is possible thanks to the definition of a common data format such as GADF, and thanks to
+an open development with a broad community of contributors.
 
-The short-term success of Python lead to a prolifaration of packages, until
-\astropy~\citep{astropy} was created in 2012. Astropy is and Gammapy is a
-Python package for gamma-ray astronomy.
+%Gammapy is built on the scientific Python stack and makes use of Astropy.
 
-% TODO: describe Context
-
-% TODO: describe goals
+%% Gammapy: from first developments to validation and selection
 The H.E.S.S. collaboration released a limited test dataset (about 50 hours of
@@
 This data release served as a basis for analysis tools validation \cite[see e.g.]{Mohrmann2019}.
-% TODO : discuss joint crab paper?
 
@@
 
-Basic idea: build on Numpy and Astropy, use Python stack
-
-TODO: Figure 2: Gammapy software stack
+%% Paper outline
+In this article, we describe the general structure of the Gammapy package and
+its main concepts. In Section \ref{sec:analysis-workflow-overview}, we present
+the data analysis workflow in very high energy gamma-ray astronomy. Then we
+show how this workflow is reflected in the structure of the Gammapy package and
+describe the various subpackages it contains. Section \ref{sec:applications}
+presents a number of applications, while Section \ref{sec:gammapy-project}
+discusses the project organization.
 
@@
 		images, spectra, light curves or source catalogs. So far it has been used to
-		simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT data, hopefully it
-		will also be applied to e.g., VERITAS, MAGIC or HAWC data in the future. }
+		simulate and analyse H.E.S.S., CTA,  and \textit{Fermi}-LAT data. As demonstrated
+		by several studies, it will also be applied to e.g., VERITAS, MAGIC or HAWC data
+		in the future. }
 	\label{fig:big-picture}

### 2022-07-22 src/text/2-package-subsections/visualisation.tex

@@
-\subsection{gammapy.visualisation}
-\label{ssec:gammapy-visualisation}
+\subsection{gammapy.visualization}
+\label{ssec:gammapy-visualization}
 \todo{Axel Donath}
-Plotters etc.
+The \code{gammapy.visualization} sub-package contains helper functions
+for plotting and visualizing analysis results and \gammapy~data structures.
+This includes for example the visualization of reflected background regions across
+multiple observations or plotting large parameter correlation matrices of
+\gammapy models. It also includes a helper class to split
+wide field Galactic survey images across multiple panels to fit a standard
+paper size.
+
+The sub-package also provides matplotlib implementations of specific
+colormaps for false color image representation. Those colormaps have
+been used historically larger collaborations in the very high energy
+domain (such as \milagro or \hess) as "trademark" colormaps.
+While we explicitly discourage the use of those colormaps for publication
+of new results, because they do not follow modern visualization
+standards, such as linear brightness gradients and accessibility
+for visually impaired people, we still consider the colormaps
+useful for reproducibility of past results.

### 2022-07-22 src/text/0-authors.tex

@@
 	Bruno Khelifi \inst{\ref{inst:3}} \and
+	Christopher van Eldik \inst{\ref{inst:12}} \and
 	Ellis Owen \inst{\ref{inst:21}} \and

### 2022-07-25 src/code-examples/snippets/gp_data.py
Update code examples

@@ -1,14 +1,16 @@
 from gammapy.data import DataStore
 
 data_store = DataStore.from_dir(
-    "$GAMMAPY_DATA/hess-dl3-dr1"
+    based_dir="$GAMMAPY_DATA/hess-dl3-dr1"
 )
 
 obs_ids = [23523, 23526, 23559, 23592]
 
-observations = data_store.get_observations(obs_ids)
+observations = data_store.get_observations(
+    obs_ids=obs_id, skip_missing=True
+)
 
 for obs in observations:
     print(f"Observation id: {obs.obs_id}")
-    print(f"Number of events: {len(obs.events.table)}")
+    print(f"N events: {len(obs.events.table)}")
     print(f"Max. area: {obs.aeff.quantity.max()}")

### 2022-07-25 src/code-examples/snippets/gp_datasets.py

@@ -1,16 +1,31 @@
+from pathlib import Path
 from gammapy.datasets import (
-    MapDataset, FluxPointsDataset, Datasets
+    MapDataset,
+    SpectrumDatasetOnOff,
+    FluxPointsDataset,
+    Datasets
 )
 
-dataset1 = MapDataset.read(
-    "$GAMMAPY_DATA/cta-1dc-gc/cta-1dc-gc.fits.gz",
-    name="map-dataset"
+path = Path("$GAMMAPY_DATA")
+
+map_dataset = MapDataset.read(
+    path / "/cta-1dc-gc/cta-1dc-gc.fits.gz",
+    name="map-dataset",
 )
 
-dataset2 = FluxPointsDataset.read(
+spectrum_dataset = SpectrumDatasetOnOff.read(
+    path / "joint-crab/spectra/hess/pha_obs23523.fits",
+    name="spectrum-datasets",
+)
+
+flux_points_dataset = FluxPointsDataset.read(
     "$GAMMAPY_DATA/tests/spectrum/flux_points/diff_flux_points.fits",
     name="flux-points-dataset",
 )
 
-datasets = Datasets([dataset1, dataset2])
-print(datasets)
+
+datasets = Datasets([
+    map_dataset, spectrum_dataset, flux_points_dataset
+])
+
+print(datasets["map-dataset"])

### 2022-07-25 src/code-examples/snippets/gp_makers.py

@@ -1,39 +1,43 @@
+import astropy.units as u
+from gammapy.data import DataStore
+from gammapy.maps import MapAxis, WcsGeom
+from gammapy.datasets import MapDataset
 from gammapy.makers import (
     MapDatasetMaker,
     FoVBackgroundMaker,
     SafeMaskMaker,
 )
-from gammapy.data import DataStore
-from gammapy.maps import MapAxis, WcsGeom
-from gammapy.datasets import MapDataset
-from regions import CircleSkyRegion
-import astropy.units as u
 
-data_store = DataStore.from_dir("$GAMMAPY_DATA/hess-dl3-dr1")
+data_store = DataStore.from_dir(
+    base_dir="$GAMMAPY_DATA/hess-dl3-dr1"
+)
 
 obs = data_store.obs(23523)
 
-energy_axis = MapAxis.from_energy_bounds(1.0, 10.0, 6, unit="TeV")
-geom = WcsGeom.create(
-    skydir=(83.633, 22.014),
-    width=(2, 2),
-    axes=[energy_axis],
+energy_axis = MapAxis.from_energy_bounds(
+    energy_min="1 TeV", energy_max="10 TeV", nbin=6,
 )
 
-circle = CircleSkyRegion(
-    center=geom.center_skydir, radius=0.2 * u.deg
+geom = WcsGeom.create(
+    skydir=(83.633, 22.014),
+    width=3 * u.deg,
+    axes=[energy_axis],
 )
-exclusion_mask = ~geom.region_mask(regions=[circle],
-                                   inside=False)
 
 empty = MapDataset.create(geom=geom)
 
 maker = MapDatasetMaker()
-mask_maker = SafeMaskMaker(methods=["offset-max", "aeff-default"],
-                           offset_max="2.3 deg")
-bkg_maker = FoVBackgroundMaker(method="scale",
-                               exclusion_mask=exclusion_mask)
 
-dataset = maker.run(empty, obs)
-dataset = mask_maker.run(dataset, obs)
+mask_maker = SafeMaskMaker(
+    methods=["offset-max", "aeff-default"],
+    offset_max="2.3 deg",
+)
+
+bkg_maker = FoVBackgroundMaker(
+    method="scale",
+)
+
+dataset = maker.run(empty, observation=obs)
+dataset = bkg_maker.run(dataset, observation=obs)
+dataset = mask_maker.run(dataset, observation=obs)
 print(dataset)

### 2022-07-25 src/figures/hess_lightcurve_pks.py
Update lightcurve figure

@@ -9,7 +9,7 @@ log = logging.getLogger(__name__)
 
 
 def plot_lightcurve():
-    figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
+    figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="intermediate")
     fig = plt.figure(figsize=figsize.inch)
 
     ax = fig.add_axes([0.1, 0.22, 0.88, 0.77])

### 2022-07-25 src/text/3-applications-subsections/temporal-analysis.tex
Update lightcurve figure size

@@
 \label{ssec:temporal-analysis}
-\todo{Atreyee}
-
 A common use case in most astrophysical scenarios is to study the temporal
@@
 TeV, and 1.5 - 20 TeV, respectively.
-
+%
 \begin{figure*}[t]
 	\centering
-	\includegraphics[width=1.\textwidth]{figures/hess_lightcurve_pks.pdf}
+	\includegraphics[width=0.6666\textwidth]{figures/hess_lightcurve_pks.pdf}
 	\caption{10 min binned lightcurve for PKS~2155-304 in two energy bands, (500
@@
 \end{figure*}
-
+%
 The obtained flux points can be analytically modelled using the available, or

### 2022-07-25 src/text/5-summary-outlook.tex
Update summary and outlook

@@
 process and software as well as data dependencies such, that the complete
-manuscript can be reproduced with a single "make" command, after
+manuscript can be reproduced with a single \code{make} command, after
 downloading the source repository. See \todo{reference?} for detailed
@@
 \label{sec:summary-and-outlook}
-\todo{Axel and Regis write this...}
-
-In this manuscript we presented the first long term support version of \gammapy.
+%
+In this manuscript we presented the first LTS version of \gammapy.
 \gammapy is a Python package for \gammaray astronomy, which relies on the
@@
 even further, providing a stable perspective for further usage,
-development and maintenance of the project.
-
-Besides the future use by the CTA community \gammapy has already
+development and maintenance of the project. Besides the future use
+by the CTA community \gammapy has already
 been used for analysis of data from the \hess and \magic instruments
-With the availability of more \gammaray data from existing Cherenkov
-telescopes, \gammaray
 
@@
 of the future Southern Widefield Gamma Ray Observatory
-(SWGO) as well. \gammapy has the potential to further unify the community
+(SWGO) and use with data from LHAASO as well. \gammapy
+has the potential to further unify the community
 of \gammaray astronomers, by sharing common tools and

### 2022-07-25 src/text/3-applications-subsections/1D-analysis.tex
Update 1D analysis section

@@
 \label{ssec:1d-analysis}
-\todo{Axel}
 One of the most common analysis cases in gamma-ray astronomy is measuring the

### 2022-07-25 src/text/3-applications-subsections/multi-instrument-analysis.tex
Update multi instrument analysis section

@@
 \label{ssec:multi-instrument-analysis}
-
+%
 \begin{figure*}[t]
@@
 	\includegraphics[width=0.666\textwidth]{figures/multi_instrument_analysis.pdf}
-	\caption{A multi-instrument analysis of the Crab Nebula}
+	\caption{
+        A multi-instrument spectral energy distribution (SED) and combined model fit
+        of the Crab Nebula. The  colored markers show the flux points computed from
+        the data of the different listed instruments. The horizontal error bar
+        illustrates the width of the chosen energy band $E_{Min}, E_{Max}$.
+        The marker is set to the log-center energy of the band, which is
+        defined by $\sqrt{E_{Min} \cdot E_{Max}}$. The vertical errors bars
+        indicate the $1\sigma$ error of the measurement. The downward
+        facing arrows indicate the value of $2\sigma$ upper flux limits
+        for the given energy range. The red solid line shows the best
+        fit model and transparent error band.
+    }
 	\label{fig:multi_instrument_analysis}
 \end{figure*}
-
+%
 %% should we mention the joint-crab here or in the intro, where we talk about
@@
 %% cite Laura's DL3 HAWC paper with the updated version of the joint-crab spectrum?
-
 In this multi-instrument analysis example we showcase the capabilities of

### 2022-07-25 src/text/2-package.tex
Adapt sub-package descriptiosn to use code shortcut
Update package overview section

@@
-\section{Analysis Workflow Overview}
-\label{sec:analysis-workflow-overview}
+\section{Gamma-ray Data Analysis}
+\label{sec:gamma-ray-data-analysis}
 
 % This might not be the bast place compared to introduction
-The data processing workflow in Gamma-ray astronomy is usually split in two sequences.
+The data reduction process in \gammaray astronomy is usually split into two parts.
 The first one deals with the data processing from camera measurement, calibration, event
-reconstruction and selection to yield a list of reconstructed gamma-ray event candidates.
+reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
 This sequence, sometimes referred to as low-level analysis, is usually very specific to
@@
 
-\section{Gammapy package}
+\section{Gammapy Package}
 \label{sec:gammapy-package}
-
 \subsection{Overview}
 \label{ssec:overview}
+%
+\begin{figure*}[ht!]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
+	\caption{
+		Gammapy sub-package structure and data analysis workflow. The top row
+        defines the groups for the different data levels and reduction steps
+        from raw gamma-like events on the left, to high level science products
+        on the right. The direction of the data flow is illustrated with the
+        grey arrows. The gray folder icons represent the different sub-packages
+        in \gammapy and their names. Below each icon there is a list of the most
+        important objects defined in the sub-package.
+    }
+	\label{fig:data_flow}
+\end{figure*}
+%
 The \gammapy package is structured into multiple sub-packages. The definition
@@
 event lists and instrument response functions as well as functionality
-to the DL3 data from disk into memory.
-
-The \code{gammapy.makers} sub-package contains the functionality to reduce
-the data to binned maps.
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
-	\caption{
-		Gammapy sub-package structure and data analysis workflow. The top row
-        defines the groups for the different data levels and reduction steps
-        from raw gamma-like events on the left, to high level science products
-        on the right. The direction of the data flow is illustrated with the
-        grey circles. The gray folder icons represent the different sub-packages
-        in Gammapy and their names. Below each icon there is an overview of the most
-        important objects defined in the sub-package.
-    }
-	\label{fig:data_flow} \end{figure*}
+to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
+contains the functionality to reduce the DL3 data to binned maps.
+Binned maps and datasets, which represent a collection of binned
+maps are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
+sub-packages respectively. Parametric models, which are defined in
+\code{gammapy.modeling}, are used to jointly model a combination
+of datasets for example to create source catalogs. Estimator classes,
+which are contained in \code{gammapy.estinators} are used to
+compute higher level science products such as flux and signficance maps,
+light curves or flux points. Finally there is a \code{gammapy.analysis}
+sub-package which provides a high level interface for executing analyses
+defined from configuration files. In the following sections we will
+introduce all sub-packages and their functionality in more detail.
 
@@
 \input{text/2-package-subsections/maps}
+\input{text/2-package-subsections/datasets}
 \input{text/2-package-subsections/makers}
-\input{text/2-package-subsections/datasets}
 \input{text/2-package-subsections/modeling}
-\input{text/2-package-subsections/stats}
 \input{text/2-package-subsections/estimators}
 \input{text/2-package-subsections/analysis}
+\input{text/2-package-subsections/stats}
 \input{text/2-package-subsections/visualisation}
@@
 \input{text/2-package-subsections/catalog}
-\input{text/2-package-subsections/utils}
+%\input{text/2-package-subsections/utils}

### 2022-07-25 src/text/2-package-subsections/catalog.tex
Update catalog sub-package description

--- 2022-03-01 src/text/2-package-subsections/catalog.tex
@@
 \label{ssec:gammapy-catalog}
-\todo{Atreyee}
-Gamma-ray catalog access
+Comprehensive source catalogs are increasingly being provided by many high
+energy astrophysics experiments. The \code{gammapy.catalog} sub-packages
+provides a convenient access to the most important \gammaray catalogs.
+Catalogs are represented by the \code{SourceCatalog} object, which
+contains the actual catalog as an Astropy \code{Table} object.
+Objects in the catalog can be accesed by row index, name of the
+object or any association or alias name listed in the catalog.
 
-Comprehensive source catalogs are increasingly being provided by many high energy astrophysics experiments.
-gammapy.catalog provides a convenient access to some common gamma-ray catalogs.
-A global catalog table is provided, along with source models flux points and light curves (if available) for individual objects, which are internally created from the supplied FITS tables.
-This module works independently from the rest of teh package, and the required catalogs are supplied in GAMMAPY_DATA.
-Presently, catalogs from Fermi-LAT (standard \citep{3FGL, 4FGL} and high energy \citep{2FHL, 3FHL}), H.E.S.S.
-galactic plane survey \citep{HGPS}, HAWC \citep{2HWC, 3HWC} and gamma-cat (\citep{gamma-cat}; an open source gamma ray catalog combining information from multiple catalogs) are supported.
+Sources are represented in \gammapy by the \code{SourceCatalogObject}
+class, which has the responsibility to translate the information
+contained in the catalog to other \gammapy objects. This includes
+the spatial and spectral model of the source, flux points and
+light curves (if available) for individual objects. This
+module works independently from the rest of the package, and the required
+catalogs are supplied in \code{GAMMAPY\_DATA} repository.
+The overview of currenly supported catalogs, the corresponding
+\gammapy classes and references are shown in Table~\ref{tab:catalogs}.
+Newly released relevant catalogs will be added in future.
+
+\begin{table*}
+    \begin{center}
+        \begin{tabular}{llll}
+         \hline
+         Class Name & Shortcut & Description & Reference\\
+         \hline
+         \code{SourceCatalog3FGL} & \code{"3fgl"} & 3\textsuperscript{rd} catalog of \fermi sources & \cite{3FGL} \\
+         \code{SourceCatalog4FGL} & \code{"4fgl"} & 4\textsuperscript{th} catalog of \fermi  sources & \cite{4FGL} \\
+         \code{SourceCatalog2FHL} & \code{"2fhl"} & 2\textsuperscript{nd} catalog high energy \fermi  sources & \cite{2FHL} \\
+         \code{SourceCatalog3FHL} & \code{"3fhl"} & 3\textsuperscript{rd} catalog high energy \fermi  sources & \cite{3FHL} \\
+         \code{SourceCatalog2HWC} & \code{"2hwc"} & 2\textsuperscript{nd} catalog of \hawc sources & \cite{2HWC} \\
+         \code{SourceCatalog3HWC} & \code{"3hwc"} & 3\textsuperscript{rd} catalog of \hawc sources & \cite{3HWC} \\
+         \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
+         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \citep{gamma-cat} \\
+         \hline
+         \end{tabular}
+    \end{center}
+    \label{tab:catalogs}
+    \caption{Overview of supported catalogs in \code{gammapy.catalog}.}
+\end{table*}
 
@@
 	\import{code-examples/generated/}{gp_catalogs}
-	\caption{Using gammapy.catalogs: Accessing underlying model, flux points and lightcurve from the Fermi-LAT 4FGL catalog for the blazar PKS 2155-304}
+	\caption{Using gammapy.catalogs: Accessing underlying model, flux points and
+		lightcurve from the Fermi-LAT 4FGL catalog for the blazar PKS 2155-304}
 	\label{codeexample:data}

### 2022-07-25 src/text/2-package-subsections/data.tex
Update data sub-package description

@@
 \label{ssec:gammapy-data}
-\todo{Cosimo Nigro}
+The \code{gammapy.data} sub-package implements the functionality to select,
+read and represent DL3 \gammaray data in memory. It provides the main user
+interface to access the lowest data level. \gammapy currently only
+supports data that is compliant with v0.2 of the \gadf data format.
+As both the \gadf data model and \gammapy were initially conceived for
+\iact data analysis, DL3 data are typically bundled into individual
+observations, which correspond to stable periods of data
+aquisitions (typically $20 - 30\,{\rm min}$) for a given instrument.
+Each observation is assigned a unique integer ID for reference.
 
-\begin{figure}
-
-	\import{code-examples/generated/}{gp_data}
-
-	\caption{Using \code{gammapy.data} to access DL3 level data with a \code{DataStore} object.
-    Individual observations can be accessed by their unique integer observation id number.
-    The actual events and instrument response functions can be accessed
-    as attributes on the \code{Observation} object, such as \code{.events}
-    or \code{.aeff} for the effective area information.
-    }
-	\label{fig*:minted:gp_data}
-\end{figure}
-
-As illustrated in Fig.~\ref{fig:data_flow}, the \code{gammapy.data} sub-package
-implements the interface to the lowest data level, providing the input interface to gamma-ray
-data. The \gammapy data model follows the \gadf specifications
-(Sec.~\ref{sec:introduction}), therefore gamma-ray data compliant with those
-can be directly read with the package. Version X.X of the \gadf specification
-is supported in this release version. As both the \gadf data model and \gammapy
-were initially conceived for \iact data analysis, input data are typically
-grouped in \code{Observations}, corresponding to stable periods of data
-aquisitions (typically $20 - 30\,{\rm min}$). A \code{DataStore} object,
-gathering a collection of observations, can be created providing ancillary
+A typical usage example is shown in Figure~\ref{fig*:minted:gp_data}.
+First a \code{DataStore} object is created from the path of the data
+directory, which contains the DL3 data index file. The \code{DataStore}
+object gathers a collection of observations and providing ancillary
 files containing information about the telescope observation mode and the
 content of the data unit of each file. The \code{DataStore} allows for
-selecting a list of observations based on specific filters. As an illustrative
-example, Fig.~\ref{fig*:minted:gp_data} shows how to create a
-\code{DataStore} and how to obtain the observations corresponding to given
-identification numbers (IDs).
+selecting a list of observations based on specific filters.
 
@@
 Sec.~\ref{ssec:fermi}.
+%
+\begin{figure}[ht!]
+	\import{code-examples/generated/}{gp_data}
+	\caption{
+        Using \code{gammapy.data} to access DL3 level data with a \code{DataStore} object.
+        Individual observations can be accessed by their unique integer observation id number.
+        The actual events and instrument response functions can be accessed
+        as attributes on the \code{Observation} object, such as \code{.events}
+        or \code{.aeff} for the effective area information.
+    }
+	\label{fig*:minted:gp_data}
+\end{figure}
+%

### 2022-07-25 src/text/2-package-subsections/datasets.tex
Update datasets sub-package description

@@
 \label{ssec:gammapy-datasets}
-\todo{Atreyee Sinha}
-
+%
 \begin{figure}
 	\import{code-examples/generated/}{gp_datasets}
-	\caption{A Datasets container with a \code{FluxPointsDataset} and \code{MapDataset}}
+	\caption{
+        Using \code{gammapy.datasets} to read existing reduced binned datasets.
+        After the different datasets are read from disk they are collected into a
+        common \code{Datasets} container. All dataset types have an associated
+        name attribute to allow access by name later in the code. The
+        environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
+        by \gammapy.
+    }
 	\label{fig*:minted:gp_datasets}
 \end{figure}
-
+%
 The end product of the data reduction process described in Section

### 2022-07-25 src/text/2-package-subsections/estimators.tex
Update estimators sub-package description

@@
 \label{ssec:gammapy-estimators}
-\todo{Axel Donath}
 By fitting parametric models to the data, the total integrated
@@
 user to conveniently transform between different
-SED types. See Table \ref{tab:sed_types}.
-The actual flux values are obtained by mutiplication of the norm with the
-reference flux.
+SED types. Table~\ref{tab:sed_types} shows an
+overview and definitions of the supported SED types.
+The actual flux values for each SED type are obtained
+by mutiplication of the norm with the  reference flux.
 
@@
          flux & Integrated flux in agiven energy range & $\mathrm{cm^{2}~s^{-1}}$ \\
-         eflux & Integrated energy flux in agiven energy range & $\mathrm{erg~cm^{2}~s^{-1}}$
+         eflux & Integrated energy flux in agiven energy range & $\mathrm{erg~cm^{2}~s^{-1}}$\\
+         \hline
         \end{tabular}

### 2022-07-25 src/text/2-package-subsections/irf.tex
Update irf sub-package description

@@
 \label{ssec:gammapy-irf}
-\todo{Fabio Pintore}
-
-\begin{figure}
-	%	\import{code-examples/generated/}{gp_makers}
-
-	\caption{In Fig.~\ref{ig*:minted:irf_examples}, we show some example of Aeff,
-		PSF, Edisp and BKG read and plotted from a typical \irf.}
-	\label{ig*:minted:irf_examples}
-\end{figure}
-
+%
+%\begin{figure}
+%	%	\import{code-examples/generated/}{gp_makers}
+%
+%	\caption{In Fig.~\ref{ig*:minted:irf_examples}, we show some example of Aeff,
+%		PSF, Edisp and BKG read and plotted from a typical \irf.}
+%	\label{ig*:minted:irf_examples}
+%\end{figure}
+%
 The \code{gammapy.irf} sub-package contains all classes and functionality
 to handle IRFs in a variety of formats.
-Usually, \irfs store instrument properties in the form of multi-dimension
+Usually, \irfs store instrument properties in the form of multi-dimensional
 tables, with quantities expressed in terms of energy (true or reconstructed),
-off-axis angles, detector coordinates and so on. The main information stored in
+off-axis angles or cartesian detector coordinates. The main information stored in
 the common \gammaray \irfs are the effective area (Aeff), energy dispersion
-(Edisp), point spread function (PSF) and background (BKG). The \code{gammapy.irf}
+(Edisp), point spread function (PSF) and background rate (BKG). The \code{gammapy.irf}
 sub-package can open and access specific \irf extensions,
@@
 axes, convert their format or units in different kinds, plot or write them into
-output files. In the following, we list the main sub-classes of the
+output files. In the following, we list the main classes of the
 sub-package:

### 2022-07-25 src/text/2-package-subsections/makers.tex
Update makers sub-package description

@@
 \label{ssec:gammapy-makers}
-\todo{Regis Terrier}
-
+%
 \begin{figure}
@@
 
-	\caption{Using gammapy.makers to reduce DL3 level data into a
-		\code{MapDataset}.}
+	\caption{
+        Using \code{gammapy.makers} to reduce DL3 level data into a
+		\code{MapDataset}. All \code{Maker} classes take
+        the configuration on initialisation of the class.
+    }
 	\label{ig*:minted:gp_makers}
 \end{figure}
-
-The data reduction contains all tasks required to process and prepare data at
-the DL3 level for modeling and fitting. The \code{gammapy.makers} sub-package
+%
+The data reduction step includes all tasks required to process and prepare
+\gammaray data from the DL3 level to modeling and fitting. The \code{gammapy.makers} sub-package
 contains the various classes and functions required to do so. First, events are

### 2022-07-25 src/text/2-package-subsections/maps.tex
Update maps sub-package description

@@
 \label{ssec:gammapy-maps}
-\todo{Laura Olivera-Nieto}
-
-\begin{figure}
-	\import{code-examples/generated/}{gp_maps}
-
-	\caption{Using \code{gammapy.maps} to create a WCS, a HEALPix and a region
-		based data structures. The initialisation parameters include
-        consistently the positions of the center of the map, the pixel
-        size, the extend of the map as well as the energy axis definition.
-        } \label{ig*:minted:gp_maps}
-\end{figure}
-
 The \code{gammapy.maps} sub-package provides classes that represent data
@@
 region-based data structure (see Figure~\ref{ig*:minted:gp_maps}).
+
+\begin{figure}
+	\import{code-examples/generated/}{gp_maps}
+
+	\caption{
+        Using \code{gammapy.maps} to create a WCS, a HEALPix and a region
+		based data structures. The initialisation parameters include
+        consistently the positions of the center of the map, the pixel
+        size, the extend of the map as well as the energy axis definition.
+        The energy minimum and maximum values for the creation of the
+        \code{MapAxis} object can be defined as strings also specifying the
+        unit. Region definitions can be passed as strings following
+        the DS9 region specifications \url{http://ds9.si.edu/doc/ref/region.html}.
+        }
+    \label{ig*:minted:gp_maps}
+\end{figure}
 

### 2022-07-25 src/text/2-package-subsections/modeling.tex
Update modeling  sub-package description

@@
 \label{ssec:gammapy-modeling}
-\todo{Quentin Remy}
-
+%
 \code{gammapy.modeling} contains all the functionality related to modeling and fitting
@@
 \label{sssec:models}
+Source models in \gammapy are four dimensional models which support two
+spatial dimensions $\ell, b$, and energy dimension $E$ as well as
+the time dimension $t$. To simplify the the definition of the
+models, \gammapy uses a factorised representation of the total source
+model:
 
-The models are grouped into the following categories:
+\begin{equation}
+    f(l, b, E, t) = F(E)  \cdot G(l, b, E) \cdot  H(t, E)
+\end{equation}
+
+Where the spectral model $F$ implicitly carries the total flux
+norm of the model. The spatial model $G$ optionally depends
+on energy and allows to support e.g. energy dependent
+morphology models. The temporal model component $H$
+optionally also supports an energy variable to
+allow for spectral variations of the model with time.
+
+Following the factorisation The models objects are grouped
+into the following categories:
 
@@
 	      light and phase curves
-
 \end{itemize}
@@
 
-\todo{Add fit code example...}
+\todo{Add fit code example...?}
 
@@
 to run a pre-fit with alternative optimization methods. In future we plan to
-extend the supported Fit backend, including for example MCMC solutions.
+extend the supported fitting backends, including for example MCMC solutions.
 \footnote{a prototype is available in gammapy-recipes,

### 2022-07-25 src/text/2-package-subsections/stats.tex
Update stats sub-package description

@@
 \label{ssec:gammapy-stats}
-\todo{Regis Terrier}
-
-The gammapy.stats subpackage contains the fit statistics and associated
+The \code{gammapy.stats} subpackage contains the fit statistics and associated
 statistical estimators that are commonly used in gamma-ray astronomy. In
@@
 	\import{code-examples/generated/}{gp_stats}
-	\caption{}
+	\caption{
+        Using \code{gammapy.stats} to compute statistical quantities
+        such as excess, signficance and assymetric errors
+        from counts based data. The data is passed on initialisation
+        of the \code{WStatCountsStatistic} class. The quantities
+        are the computed on access of the corresponding class
+        attributes such as \code{.n\_sig} and \code{.sqrt\_ts}.
+    }
 	\label{codeexample:stats} \end{figure}

### 2022-07-25 src/text/3-applications-subsections/temporal-analysis.tex
Update figures

@@
 \begin{figure*}[t]
-	\centering
+    \sidecaption
 	\includegraphics[width=0.6666\textwidth]{figures/hess_lightcurve_pks.pdf}
-	\caption{10 min binned lightcurve for PKS~2155-304 in two energy bands, (500
-		GeV - 1.5 TeV, and 1.5 TeV to 20 TeV) as observed by the H.E.S.S. telescopes in
-		2006.} \label{fig:hess_lightcurve_pks}
+	\caption{
+        Binned light-curves in two different energy bands differ for the source
+        PKS~2155-304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV)
+        as observed by the H.E.S.S. telescopes in 2006. The colored markers
+        show the flux points in the different energy bands. The horizontal
+        error illustrates the width of the time bin of 10~min. The vertical
+        error bars show the associated assymetrical flux errors. The marker
+        is set to the center of the time bin.
+    }
+    \label{fig:hess_lightcurve_pks}
 \end{figure*}

### 2022-07-25 src/text/4-project.tex
Update project description section
Update figures

@@
 	\import{tables/generated/}{codestats}
-	\caption{Coding languages statistics in Gammapy project}
+	\caption{
+        Overview of used programming languages and distribution of code across the different file
+        categories in the \gammapy code base. The most right column list the total number of lines
+        in a file. The \textit{comment} column lists the number of comments in the files
+        (including method and class docstrings), the \textit{blank} column lists the
+        number of blank lines in the file. The uppermost rows distinguish between
+        code that implements actual functionality and code the implements tests.
+        All documentataion in \gammapy is implemented as dosctrings, \text{reStructuredText} (RST)
+        files or notebooks.
+    }
 	\label{table:codestats:data}
@@
 	\caption{
-		Percentage of lines of code in Gammapy project} \label{fig:codestats:lang}
+		Overview of used programming languages and distribution of code across the different file
+        categories in the \gammapy code base.
+    } \label{fig:codestats:lang}
 \end{figure}
@@
 \label{ssec:pigs}
-\todo{Axel, Regis}
 An important part of \gammapy's development organisation is the support
@@
 support release of \gammapy.
+
+\subsection{Release Cycle, Versioning, and Long-term Support}
+With the first long term support (LTS) releases v1.0, the \gammapy project
+enters a new development phase.
+\todo{To be written...summarise and reference PIG 24}

### 2022-07-25 src/figures/codestats.py

@@ -27,8 +27,8 @@ $summary
 CSV_TEMPLATE = r"""$labels
 $cells$summary"""
 
-def run_cloc(args):
 
+def run_cloc(args):
     result_api = subprocess.run(["cloc", "--not-match-d=test", args.src], capture_output=True).stdout
     result_test = subprocess.run(["cloc", "--match-d=test", args.src], capture_output=True).stdout
 
@@ -59,7 +59,6 @@ def run_cloc(args):
 
 
 def make_files(stats):
-
     latex = Template(LATEX_TEMPLATE)
     csv = Template(CSV_TEMPLATE)
 
@@ -102,10 +101,12 @@ def make_files(stats):
         file_csv.write(csv)
     logging.info(f"CSV temporary file {TEMPFILE} created.")
 
-def make_pie():
 
+def make_pie():
     figsize = config.FigureSizeAA()
-    plt.figure(figsize=figsize.inch)
+    fig = plt.figure(figsize=figsize.inch)
+
+    ax = fig.add_axes([0, 0, 0.95, 0.95])
 
     file_data = pd.read_csv(TEMPFILE, sep=", ", engine="python")
     df = file_data[:-1]
@@ -114,7 +115,7 @@ def make_pie():
     # code
     df = df.sort_values(by=["code"])[::-1]
     sdf = shorthen_df(df)
-    sdf.plot(kind="pie", y="code", autopct=fix_autopct, legend=False)
+    sdf.plot(ax=ax, kind="pie", y="code", autopct=fix_autopct, legend=False, fontsize=8)
     plt.ylabel("")
     plt.savefig("codestats.pdf")
     logging.info("Piecharf file codestats.pdf created.")
@@ -127,6 +128,7 @@ def make_pie():
     # plt.savefig("filestats.pdf")
     # logging.info("Piecharf file filestats.pdf created.")
 
+
 def shorthen_df(df):
     # group others
     others = defaultdict(int)
@@ -138,8 +140,9 @@ def shorthen_df(df):
     odf = pd.DataFrame(data=others, index=["Others"])
     return pd.concat([df.head(5), odf], axis=0)
 
+
 def fix_autopct(pct):
-    return ("%.2f" % pct) if pct > 3 else ""
+    return "{pct:.0f} %".format(pct=pct)
 
 
 def main():

### 2022-07-25 src/figures/hess_lightcurve_pks.py

@@ -12,7 +12,7 @@ def plot_lightcurve():
     figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="intermediate")
     fig = plt.figure(figsize=figsize.inch)
 
-    ax = fig.add_axes([0.1, 0.22, 0.88, 0.77])
+    ax = fig.add_axes([0.13, 0.33, 0.86, 0.66])
 
     path = Path("../data/lightcurve")
     filename = path / "pks2155_flare_lc.fits.gz"
@@ -20,6 +20,7 @@ def plot_lightcurve():
     lc.plot(ax=ax, sed_type="eflux", axis_name="time")
     filename = "hess_lightcurve_pks.pdf"
     log.info(f"Writing {filename}")
+    plt.legend(loc="lower left")
     plt.savefig(filename, dpi=300)
 
 

### 2022-07-25 src/figures/multi_instrument_analysis.py

@@ -11,7 +11,7 @@ sed_y_label = (
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="intermediate")
 fig = plt.figure(figsize=figsize.inch)
-ax = fig.add_axes([0.1, 0.1, 0.9, 0.9])
+ax = fig.add_axes([0.15, 0.15, 0.84, 0.84])
 
 # load the flux points and plot them
 fermi_flux_points = FluxPoints.read(
@@ -45,6 +45,5 @@ hawc_flux_points.plot(ax=ax, sed_type="e2dnde", color="goldenrod", label="HAWC")
 ax.set_xlim(plot_kwargs["energy_bounds"])
 ax.set_xlabel(sed_x_label)
 ax.set_ylabel(sed_y_label)
-ax.legend()
+ax.legend(loc="lower left")
 fig.savefig("multi_instrument_analysis.pdf")
-fig.savefig("multi_instrument_analysis.png")

### 2022-07-25 src/text/1-introduction.tex
Extend introduction

@@
 %% Gamma-ray astronomy
-Very high energy cosmic gamma-ray reaching Earth interact in the atmosphere and
+Gamma-ray astronomy is a rather young field of research. The \gammaray~
+range of the electromagnetic spectrum provides us with insight to the
+most energetic process in the universe such as surroundings of
+black holes and remnants of supernova explosions. As in other
+branches of astronomy \gammarays can be observed by both
+satellite as well as ground based instruments.
+Very high energy cosmic gamma-rays reaching Earth interact in the atmosphere and
 create a large shower of secondary particles that can be observed from the ground.
@@
 It covers the energy range from fews tens of GeV up to the PeV.
-Two main instrument categories exist \citep{2015CRPhy..16..610D}.
+There are two main categories of instrument \citep{2015CRPhy..16..610D}.
 Imaging Atmospheric Cherenkov Telescopes (IACT) make images of atmospheric showers
@@
 use these images to reconstruct the properties of the incident particle.
+Those instruments have a limited field of view (FoV) and duty cycle, but
+good energy and angular resolution.
 
-Particle samplers detect directly particles from the tail of the shower when it reaches
-the ground. These instruments have very large field-of-view, large duty-cycle but higher
-energy threshold and usually have lower signal to noise ratios compared to IACTs.
+Water Cherenkov observatories detect directly particles from the tail of the
+shower when it reaches the ground. These instruments have very
+large field-of-view, large duty-cycle but higher energy threshold and
+usually have lower signal to noise ratios compared to IACTs.
 
@@
 permit easy combination of data from several instruments and is therefore
-a limitation for interoperability of existing facilities.
+a limitation for interoperability of existing facilities. Especially
+because the different detection techniques have complementary
+properties.
 
@@
 %% Context : formats
-In practice, the data-reduction workflow of IACTs is remarkably similar.
+In practice, the data-reduction workflow of all gamma-ray observatories
+is remarkably similar.
 After data calibration, shower events are reconstructed and
@@
 The latter are then used to derive scientific results, such as spectra, sky maps
-or light curves, taking into account the Instrument Response Functions (IRF).
+or light curves, taking into account the specific instrument response functions (IRF).
 The information in this high data level is independent on

### 2022-07-26 src/code-examples/snippets/gp_catalogs.py
Further adapt figures

@@ -1,6 +1,6 @@
-from gammapy.catalog import SourceCatalog4FGL
+from gammapy.catalog import SOURCE_CATALOGS
 
-catalog = SourceCatalog4FGL()
+catalog = SOURCE_CATALOGS.get_cls("4fgl")()
 print("Number of sources :", len(catalog.table))
 
 source = catalog["PKS 2155-304"]

### 2022-07-26 src/figures/codestats.py

@@ -115,7 +115,9 @@ def make_pie():
     # code
     df = df.sort_values(by=["code"])[::-1]
     sdf = shorthen_df(df)
-    sdf.plot(ax=ax, kind="pie", y="code", autopct=fix_autopct, legend=False, fontsize=8)
+    sdf.plot(
+        ax=ax, kind="pie", y="code", autopct=fix_autopct, legend=False, fontsize=8
+    )
     plt.ylabel("")
     plt.savefig("codestats.pdf")
     logging.info("Piecharf file codestats.pdf created.")

### 2022-07-26 src/figures/multi_instrument_analysis.py

@@ -35,12 +35,12 @@ plot_kwargs = {
     "xunits": u.TeV,
 }
 
-crab_lp.plot(ax=ax, ls="-", lw=1.5, color="crimson", label="joint fit", **plot_kwargs)
-crab_lp.plot_error(ax=ax, facecolor="crimson", alpha=0.4, **plot_kwargs)
+fermi_flux_points.plot(ax=ax, sed_type="e2dnde", label="Fermi-LAT")
+magic_flux_points.plot(ax=ax, sed_type="e2dnde", label="MAGIC", marker="v")
+hawc_flux_points.plot(ax=ax, sed_type="e2dnde", label="HAWC", marker="s")
 
-fermi_flux_points.plot(ax=ax, sed_type="e2dnde", color="k", label="Fermi-LAT")
-magic_flux_points.plot(ax=ax, sed_type="e2dnde", color="dodgerblue", label="MAGIC")
-hawc_flux_points.plot(ax=ax, sed_type="e2dnde", color="goldenrod", label="HAWC")
+crab_lp.plot(ax=ax, ls="-", lw=1.5, color="k", label="joint fit", **plot_kwargs)
+crab_lp.plot_error(ax=ax, facecolor="k", alpha=0.4, **plot_kwargs)
 
 ax.set_xlim(plot_kwargs["energy_bounds"])
 ax.set_xlabel(sed_x_label)

### 2022-07-26 src/text/2-package-subsections/maps.tex
Add some more detail to maps section

@@
 a given dimension, spatial or not. Map axes can have physical units attached to
-them, as well as define non-linear spaced bins.
+them, as well as define non-linear spaced bins. All map classes support operations such
+as arithmetic operations with unit support, up- and downsampling along
+extra axes, interpolation, resampling of extra axes, interactive visualisation
+in notebooks and interpolation onto different geometries.
 
 The sub-package provides a uniform API for the FITS World Coordinate System
-(WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and
-region-based data structure (see Figure~\ref{ig*:minted:gp_maps}).
+(WCS), the HEALPix pixelization and region-based data structure
+(see Figure~\ref{ig*:minted:gp_maps}).
 
@@
 % itemize because it helps me write, could also just be paragraphs...
-\paragraph{WCS:}
-The FITS WCS pixelization supports a different
-number of projections to represent celestial spherical coordinates in a regular
-rectangular grid. Gammapy provides full support to data structures using this
-pixelization scheme.
+\subsubsection{WCS Maps}
+The FITS WCS pixelization supports a different number of projections to
+represent celestial spherical coordinates in a regular rectangular grid.
+Gammapy provides full support to data structures using this pixelization
+scheme. For details see ~\cite{Calabretta2002}. This pixelisation
+is typically used for smaller regions of interests, such as pointed
+observations.
 
-\paragraph{HEALPix:}
-This pixelization provides a
+\subsubsection{HEALPix Maps}
+This pixelization scheme ~\citep{Calabretta2002} provides a
 subdivision of a sphere in which each pixel covers the same surface area as
 every other pixel. As a consequence, however, pixel shapes are no longer
-rectangular, or regular. \gammapy provides limited support to HEALPix-based
-maps, relying in some cases on projections to a local WCS grid.
+rectangular, or regular.
+This pixelisation is typically used for all-sky data, such as data
+from the \hawc or \fermi observatory. \gammapy natively supports
+the multiscale definiton of the HEALPix pixelisation and thus
+allows for easy up and downsampling of the data. In addition to
+the all-sky map, \gammapy also supports a local HEALPix
+pixelisation where the size of the map is constrained to a given
+radius.
+For local nighbourhood operations, such as convolution \gammapy relies
+on projecting the HEALPix data to a local tangential WCS grid.
 
-\paragraph{Region:} In this case, instead of a fine spatial grid
+\subsubsection{Region Maps}
+In this case, instead of a fine spatial grid
 dividing a rectangular sky region, the spatial dimension is reduced to a single
@@
 example an energy axis, to represent how a quantity varies in that dimension
-inside the corresponding region.
+inside the corresponding region. The region is represented on the local
+tangential projection see \cite{Astropy regions}.
 

### 2022-07-26 src/text/4-project.tex
Add release cycle description

@@
 \subsection{Release Cycle, Versioning, and Long-term Support}
-With the first long term support (LTS) releases v1.0, the \gammapy project
-enters a new development phase.
-\todo{To be written...summarise and reference PIG 24}
+With the first long term support (LTS) release v1.0, the \gammapy project
+enters a new development phase. The development will change from
+quick feature driven development to more stable maintenance
+and user support driven developement. After v1.0 we foresee
+a developement cycle with major, minor and bugfix releases.
+We basically followg the development cycle of the Astropy
+project. Thus we expect a major LTS release approximately
+every two years, minor releases are planned every 6~months,
+while bug-fix releases will happen as needed. While
+bug-fix releases will not introduce API breaking changes,
+we will work with a deprecation system for minor releases.
+API breaking changes will be announced to user by runtime
+warnings first and then implemented in the subsequent
+minor release. This approach we consider a fair
+compromise between the interests of users in a stable
+package and the interest of developers to improve
+and develop \gammapy in future. The developemnt cycle is described
+in more detail in PIG 24 \todo{reference}.

### 2022-07-26 src/text/1-introduction.tex
Minor fixes

@@
 good energy and angular resolution.
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[height=\textwidth, angle=270]{static/gammapy-big-picture}
+    \caption{ Gammapy is a Python package
+		for high-level gamma-ray data analysis. Using event lists, exposures and point
+		spread functions as input you can use it to generate science results such as
+		images, spectra, light curves or source catalogs. So far it has been used to
+		simulate and analyse H.E.S.S., CTA,  and \textit{Fermi}-LAT data. As demonstrated
+		by several studies, it will also be applied to e.g., VERITAS, MAGIC or HAWC data
+		in the future. }
+	\label{fig:big-picture}
+
+\end{figure*}
 
@@
 discusses the project organization.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[height=0.5\textwidth,
-		angle=270]{static/gammapy-big-picture} \caption{ Gammapy is a Python package
-		for high-level gamma-ray data analysis. Using event lists, exposures and point
-		spread functions as input you can use it to generate science results such as
-		images, spectra, light curves or source catalogs. So far it has been used to
-		simulate and analyse H.E.S.S., CTA,  and \textit{Fermi}-LAT data. As demonstrated
-		by several studies, it will also be applied to e.g., VERITAS, MAGIC or HAWC data
-		in the future. }
-	\label{fig:big-picture}
-
-\end{figure}

### 2022-07-26 src/text/2-package-subsections/makers.tex
Update figures
Minor fixes

@@
     \import{code-examples/generated/}{gp_makers}
-
 	\caption{
@@
 to correct them from the data themselves. Several techniques are commonly used
-in gamma-ray astronomy such as field-of-view background normalization or
-background measurement in reflected regions regions, see~\cite{Berge07}.
+in \gammaray astronomy such as field-of-view background normalization or
+background measurement in reflected regions, see~\cite{Berge07}.
 Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the

### 2022-07-26 src/text/0-abstract.tex
Add latexindent pre commit hook
Run tex indentation
Use shortcuts more consistently

--- 2022-01-27 src/text/0-abstract.tex
@@
 	%{Gammapy context:}
-	Historically the data as well as analysis software in gamma-ray astronomy is
+	Historically the data as well as analysis software in \gammaray astronomy is
 	proprietary to the experiments. With the future Cherenkov Telescope Array
-	(CTA), which will be operated as an open gamma-ray observatory with public
+	(CTA), which will be operated as an open \gammaray observatory with public
 	data, there is a corresponding need for open high-level analysis software. In
 	this article we present the first major version v1.0 of \gammapy, a
-	community-developed open-source Python package for gamma-ray astronomy.
-	 We present its general design and provide an%
+	community-developed open-source Python package for \gammaray astronomy. We
+	present its general design and provide an%
 	overview of the analysis methods and features it implements. Starting from
@@
 	and spectro-morphological analysis. Counts, background and IRFs data are
-	bundled in datasets and can be serialised, rebinned and stacked.
-	 \gammapy supports to model binned data using%
-	Poisson maximum likelihood fitting. It comes with built-in spectral, spatial
-	and temporal models as well as support for custom user models, to model e.g.
-	energy dependent morphology of gamma-ray sources. Multiple datasets can be
+	bundled in datasets and can be serialised, rebinned and stacked. \gammapy
+	supports to model binned data using Poisson%
+	maximum likelihood fitting. It comes with built-in spectral, spatial and
+	temporal models as well as support for custom user models, to model e.g.,
+	energy dependent morphology of \gammaray sources. Multiple datasets can be
 	combined in a joint-likelihood approach to either handle time dependent IRFs,
@@
 
-	% The gamma-ray can be considered as the last frontier 
-	% In the last two decades the measurement of gamma-ray emission from the universe has 
+	% The \gammaray can be considered as the last frontier
+	% In the last two decades the measurement of \gammaray emission from the universe has
 	% evolved from a niche

### 2022-07-26 src/text/1-introduction.tex
Use shortcuts more consistently

@@
 
-%% Gamma-ray astronomy
-Gamma-ray astronomy is a rather young field of research. The \gammaray~
+%% \gammaray astronomy
+\gammaray astronomy is a rather young field of research. The \gammaray~
 range of the electromagnetic spectrum provides us with insight to the
@@
 satellite as well as ground based instruments.
-Very high energy cosmic gamma-rays reaching Earth interact in the atmosphere and
+Very high energy cosmic \gammarays reaching Earth interact in the atmosphere and
 create a large shower of secondary particles that can be observed from the ground.
-Ground-based gamma-ray astronomy relies on this phenomenon to detect the
-primary gamma-ray photons and measure their direction and energy.
+Ground-based \gammaray astronomy relies on this phenomenon to detect the
+primary \gammaray photons and measure their direction and energy.
 It covers the energy range from fews tens of GeV up to the PeV.
@@
     \caption{ Gammapy is a Python package
-		for high-level gamma-ray data analysis. Using event lists, exposures and point
+		for high-level \gammaray data analysis. Using event lists, exposures and point
 		spread functions as input you can use it to generate science results such as
 		images, spectra, light curves or source catalogs. So far it has been used to
-		simulate and analyse H.E.S.S., CTA,  and \textit{Fermi}-LAT data. As demonstrated
-		by several studies, it will also be applied to e.g., VERITAS, MAGIC or HAWC data
+		simulate and analyse \hess, \cta,  and \fermi data. As demonstrated
+		by several studies, it will also be applied to e.g., \veritas, \magic or \hawc data
 		in the future. }
@@
 %% Context
-Ground based gamma-ray astronomy has been historically structured
+Ground based \gammaray astronomy has been historically structured
 by experiments run by independent collaborations relying
@@
 %% Context : formats
-In practice, the data-reduction workflow of all gamma-ray observatories
+In practice, the data-reduction workflow of all \gammaray observatories
 is remarkably similar.
 After data calibration, shower events are reconstructed and
-gamma/hadron separation is applied to build lists of gamma-ray like events.
+gamma/hadron separation is applied to build lists of \gammaray like events.
 The latter are then used to derive scientific results, such as spectra, sky maps
@@
 within the same model. The efforts to prototype a format usable by various instruments
-converged in the so-called \textit{Data Format for Gamma-ray Astronomy}
+converged in the so-called \textit{Data Format for \gammaray Astronomy}
 initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
-\texttt{gamma-astro-data-format} (GADF). The latter proposes prototypical
+\texttt{gamma-astro-data-format} (\gadf). The latter proposes prototypical
 specifications to produce files based on the flexible image transport system
@@
 The Gammapy project started in 2015 with the objective of building a flexible and
-efficient software library for very high energy gamma-ray data analysis \citep{gammapy_2015}.
-This is possible thanks to the definition of a common data format such as GADF, and thanks to
+efficient software library for very high energy \gammaray data analysis \citep{gammapy_2015}.
+This is possible thanks to the definition of a common data format such as \gadf, and thanks to
 an open development with a broad community of contributors.
@@
 The H.E.S.S. collaboration released a limited test dataset (about 50 hours of
-observations taken between 2004 and 2008) based  on the GADF DL3 format \citep{HESS_DR1}.
+observations taken between 2004 and 2008) based  on the \gadf DL3 format \citep{HESS_DR1}.
 This data release served as a basis for analysis tools validation \cite[see e.g.]{Mohrmann2019}.
@@
 its main concepts. In Section \ref{sec:analysis-workflow-overview}, we present
-the data analysis workflow in very high energy gamma-ray astronomy. Then we
+the data analysis workflow in very high energy \gammaray astronomy. Then we
 show how this workflow is reflected in the structure of the Gammapy package and

### 2022-07-26 src/text/2-package-subsections/stats.tex
Minor fixes
Use shortcuts more consistently

@@
 The \code{gammapy.stats} subpackage contains the fit statistics and associated
-statistical estimators that are commonly used in gamma-ray astronomy. In
-general, gamma-ray observations count Poisson-distributed events at various sky
+statistical estimators that are commonly used in \gammaray astronomy. In
+general, \gammaray observations count Poisson-distributed events at various sky
 positions, and contain both signal and background events. Estimation of the
@@
 ~\citep{Cash}. It is used by datasets using background templates such as the
-MapDataset. When the number of background events is unknown and an off
+\code{MapDataset}. When the number of background events is unknown and an off
 measurement where only background events are expected is used, the statistic

### 2022-07-26 src/text/2-package.tex
Use shortcuts more consistently

@@
-\section{Gamma-ray Data Analysis}
-\label{sec:gamma-ray-data-analysis}
+\section{\gammaray Data Analysis}
+\label{sec:gammaray-data-analysis}
 
@@
 The other sequence, referred to as high-level analysis, deals with the extraction of physical
-quantities related to gamma-ray sources and the production of high-level products such as spectra,
+quantities related to \gammaray sources and the production of high-level products such as spectra,
 lightcurves and catalogs. The methods and tools applied here are more generic and are broadly
@@
 To extract physically relevant information, the measured data are usually compared to a
-model of the expected gamma-ray emitters in the instrument field-of-view using statistical
+model of the expected \gammaray emitters in the instrument field-of-view using statistical
 techniques such as maximum likelihood.
@@
   measuring a direction $p$ when the true direction is $p_{\rm true}$ and the true energy is $E_{\rm true}$.
-  Gamma-ray instruments consider the probability density of the angular separation between true and reconstructed directions
+  \gammaray instruments consider the probability density of the angular separation between true and reconstructed directions
   $\delta p = p_{\rm true} - p$, i.e. $PSF(\delta p|p_{\rm true}, E_{\rm true})$.
@@
   reconstruct the photon at energy $E$ when the true energy is $E_{\rm true}$ and the true position :$p_{\rm true}$.
-  Gamma-ray instruments consider the probability density of the migration $\mu=\frac{E}{E_{\rm true}}$,
+  \gammaray instruments consider the probability density of the migration $\mu=\frac{E}{E_{\rm true}}$,
   i.e. $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$.
@@
 
-Gamma-ray data at the Data Level 3 therefore consists in lists of gamma-like events and their
+\gammaray data at the Data Level 3 therefore consists in lists of gamma-like events and their
 corresponding instrument response functions (IRFs). The latter include the aforementioned
@@
 a variety of :ref:`built in models <model-gallery>`. This includes spectral,
-spatial and temporal model classes to describe the gamma-ray emission in the sky.
+spatial and temporal model classes to describe the \gammaray emission in the sky.
 Where spectral models can be simple analytical models or more complex ones from radiation

### 2022-07-26 src/text/3-applications-subsections/1D-analysis.tex
Use shortcuts more consistently

@@
 \label{ssec:1d-analysis}
-One of the most common analysis cases in gamma-ray astronomy is measuring the
+One of the most common analysis cases in \gammaray astronomy is measuring the
 spectrum of a source in a given region defined on the sky, in conventional

### 2022-07-26 src/text/3-applications-subsections/population-studies.tex
Use shortcuts more consistently

@@
 versions of \textit{gammapy} were developed in parallel of the preparation of
-the HESS Galactic plane survey catalog~\citep[HGPS][]{2018A&A...612A...1H} and
+the \hess Galactic plane survey catalog~\citep[HGPS][]{2018A&A...612A...1H} and
 the associated PWN and SNR populations studies~\citep{2018A&A...612A...2H,
@@
 models needed to represent them accurately. As an example If we compare the
-results of the HGPS to the expectations from the CTA Galactic Plane survey
-simulations we jump from 78 sources detected by HESS to about 500 detectable by
+results of the HGPS to the expectations from the \cta Galactic Plane survey
+simulations we jump from 78 sources detected by \hess to about 500 detectable by
 CTA~\citep{2021arXiv210903729R}.
@@
 
-In short the production of catalogs from gamma-ray surveys can be divided in
+In short the production of catalogs from \gammaray surveys can be divided in
 four main steps : data-reduction; object detection; model fitting and model

### 2022-07-26 src/text/4-project.tex
Use shortcuts more consistently

@@
 
-Gammapy is indexed in Astronomy Source Code
+\gammapy is indexed in Astronomy Source Code
 Library\footnote{\url{https://ascl.net/1711.014}} and
@@
 \subsection{Release Cycle, Versioning, and Long-term Support}
+\label{ssec:release-cycle}
 With the first long term support (LTS) release v1.0, the \gammapy project

### 2022-07-26 src/text/4-project.tex
Introduce GtiHub shortcut

@@
 Gammapy follows an open-source and open-contribution development model based on
-the cloud repository service GitHub. A GitHub organization
-\textit{gammapy}\footnote{\url{https://github.com/gammapy}} hosts different
+the cloud repository service \github. A \github organization
+\textit{gammapy}\footnote{\url{https://\github.com/gammapy}} hosts different
 repositories related with the project. The software codebase may be found in
@@
 
-Several automated tasks are set as GitHub
-actions\footnote{\url{https://github.com/features/actions}}, blocking the
+Several automated tasks are set as \github
+actions\footnote{\url{https://\github.com/features/actions}}, blocking the
 processes and alerting developers when fails occur. This is the case of the
@@
 This small ecosystem of interconnected up-to-date repositories, automated tasks
-and alerts, is just a part of a bigger set of GitHub repositories, where most
+and alerts, is just a part of a bigger set of \github repositories, where most
 of them are related with the project but not necessary for the development of
@@
 Zenodo\footnote{\url{https://zenodo.org/record/5721467o}} digital libraries for
-software. The Zenodo record is synchronised with the codebase GitHub repository
+software. The Zenodo record is synchronised with the codebase \github repository
 so that every release triggers the update of the versioned record. In addition,
@@
 in different environments using our continuous integration (CI) workflow based
-on GitHub actions.
+on \github actions.
 
@@
 specific use cases. Contributions happen via pull requests to the
-\textit{gammapy-recipes} GitHub repository and merged after a short review. All
+\textit{gammapy-recipes} \github repository and merged after a short review. All
 notebooks in the repository are tested and published in the Gammapy recipes
-webpage\footnote{\url{https://gammapy.github.io/gammapy-recipes}} automatically
-using GitHub actions.
+webpage\footnote{\url{https://gammapy.\github.io/gammapy-recipes}} automatically
+using \github actions.
 
 A growing community of users is gathering around the Slack
-messaging\footnote{\url{https://gammapy.slack.com}} and GitHub
-discussions\footnote{\url{https://github.com/gammapy/gammapy/discussions}}
+messaging\footnote{\url{https://gammapy.slack.com}} and \github
+discussions\footnote{\url{https://\github.com/gammapy/gammapy/discussions}}
 support forums, providing valuable feedback on the Gammapy functionalities,
@@
 are presented to the \gammapy developer community in a pull request
-on GitHub and the undergo a review phase in which changes and
+on \github and the undergo a review phase in which changes and
 improvements to the document are proposed and implemented. Once the PIG

### 2022-07-26 src/text/5-summary-outlook.tex
Introduce GtiHub shortcut

@@
 Python scripts to create the figures
-in \url{https://github.com/gammapy/gammapy-v1.0-paper}.
-This GitHub repository also documents the history of the creation
+in \url{https://\github.com/gammapy/gammapy-v1.0-paper}.
+This \github repository also documents the history of the creation
 and evolution of the manuscript with time. To simplify the reproducibility

### 2022-07-26 src/text/1-introduction.tex
Consistently use Gammapy shortcut

@@
 	\includegraphics[height=\textwidth, angle=270]{static/gammapy-big-picture}
-    \caption{ Gammapy is a Python package
+    \caption{ \gammapy is a Python package
 		for high-level \gammaray data analysis. Using event lists, exposures and point
@@
 
-%% Gammapy: concept and goals
+%% \gammapy: concept and goals
 %%% Question: starting date? Is is relevant, what is the real start?
-The Gammapy project started in 2015 with the objective of building a flexible and
+The \gammapy project started in 2015 with the objective of building a flexible and
 efficient software library for very high energy \gammaray data analysis \citep{gammapy_2015}.
@@
 
-%Gammapy is built on the scientific Python stack and makes use of Astropy.
+%\gammapy is built on the scientific Python stack and makes use of Astropy.
 
-%% Gammapy: from first developments to validation and selection
-The H.E.S.S. collaboration released a limited test dataset (about 50 hours of
+%% \gammapy: from first developments to validation and selection
+The \hess collaboration released a limited test dataset (about 50 hours of
 observations taken between 2004 and 2008) based  on the \gadf DL3 format \citep{HESS_DR1}.
@@
 
-TODO: Figure 1: Data -> Gammapy -> Spectra etc with some details
+TODO: Figure 1: Data -> \gammapy -> Spectra etc with some details
 
 %% Paper outline
-In this article, we describe the general structure of the Gammapy package and
+In this article, we describe the general structure of the \gammapy package and
 its main concepts. In Section \ref{sec:analysis-workflow-overview}, we present
 the data analysis workflow in very high energy \gammaray astronomy. Then we
-show how this workflow is reflected in the structure of the Gammapy package and
+show how this workflow is reflected in the structure of the \gammapy package and
 describe the various subpackages it contains. Section \ref{sec:applications}

### 2022-07-26 src/text/2-package-subsections/estimators.tex
Use shortcuts more consistently
Consistently use Gammapy shortcut

@@
     \label{tab:sed_types}
-    \caption{Definition of sed types.}
+    \caption{Definition of the different SED types supported in \gammapy.}
 \end{table*}
@@
 the data into multiple formats. This includes the
-GADF SED (reference?) format, FITS based ND sky-maps
+\gadf SED (reference?) format, FITS based ND sky-maps
 and formats compatible with Astropy's \code{Table} and

### 2022-07-26 src/text/2-package.tex
Use title case consistently
Consistently use Gammapy shortcut

@@
-\section{\gammaray Data Analysis}
+\section{Gamma-ray Data Analysis}
 \label{sec:gammaray-data-analysis}
@@
 that represent the data level 4 (DL4). They can be written to
-disk, in a format specific to Gammapy to allow users to read them back at any time later
+disk, in a format specific to \gammapy to allow users to read them back at any time later
 for modeling and fitting.
@@
 The next step is then typically to model and fit the datasets, either
-individually, or in a joint likelihood analysis. For this purpose Gammapy
+individually, or in a joint likelihood analysis. For this purpose \gammapy
 provides a uniform interface to multiple fitting backends. It also provides
@@
 
-\section{Gammapy Package}
+\section{\gammapy Package}
 \label{sec:gammapy-package}
@@
 	\caption{
-		Gammapy sub-package structure and data analysis workflow. The top row
+		\gammapy sub-package structure and data analysis workflow. The top row
         defines the groups for the different data levels and reduction steps

### 2022-07-26 src/text/4-project.tex
Use title case consistently
Consistently use Gammapy shortcut

@@
-\section{Gammapy project} \label{sec:gammapy-project}
+\section{\gammapy Project} \label{sec:gammapy-project}
 
-In this section, we provide an overview of the organization of the Gammapy
+In this section, we provide an overview of the organization of the \gammapy
 project. We briefly describe the main roles and responsibilities within the
 team, as well as the technical infrastructure designed to facilitate the
-development and maintenance of Gammapy as a high quality software. We use
+development and maintenance of \gammapy as a high quality software. We use
 common tools and services for software development of Python open-source
@@
 
-\subsection{Organizational structure}
+\subsection{Organizational Structure}
 \label{ssec:organizational-structure}
 
-Gammapy is a well-organised international open-source project with a broad
+\gammapy is a well-organised international open-source project with a broad
 developer base and the presence of commitments from strong groups and
@@
 
-\subsection{Technical infrastructure}
+\subsection{Technical Infrastructure}
 \label{ssec:technical-infrastructure}
 
-Gammapy follows an open-source and open-contribution development model based on
+\gammapy follows an open-source and open-contribution development model based on
 the cloud repository service \github. A \github organization
@@
 
-\subsection{Software distribution}
+\subsection{Software Distribution}
 \label{ssec:software-distribution}
 
-Gammapy is distributed for Linux, Windows and Mac environments, and installed
+\gammapy is distributed for Linux, Windows and Mac environments, and installed
 in the usual way for Python packages. Each stable release is uploaded to the
@@
 repository\footnote{\url{https://anaconda.org/anaconda/repo}} channels. At this
-time, Gammapy is also available as a Debian Linux
+time, \gammapy is also available as a Debian Linux
 package\footnote{\url{https://packages.debian.org/sid/python3-gammapy}}. We
@@
 so that every release triggers the update of the versioned record. In addition,
-the next release of Gammapy will be added to the Open-source scientific
+the next release of \gammapy will be added to the Open-source scientific
 Software and Service Repository\footnote{\url{https://projectescape.eu/ossr}}
@@
 
-\subsection{Documentation and user-support}
+\subsection{Documentation and User-support}
 \label{ssec:documentation-and-user-support}
-Gammapy provides its user community with a tested and versioned up-to-date
+\gammapy provides its user community with a tested and versioned up-to-date
 on-line
@@
 tutorials, and a reference to the API automatically extracted from the code and
-docstrings. The Gammapy code snippets present in the documentation are tested
+docstrings. The \gammapy code snippets present in the documentation are tested
 in different environments using our continuous integration (CI) workflow based
@@
 We have also set up a solution for users to share recipes as Jupyter notebooks
-that do not fit in the Gammapy core documentation but which may be relevant as
+that do not fit in the \gammapy core documentation but which may be relevant as
 specific use cases. Contributions happen via pull requests to the
 \textit{gammapy-recipes} \github repository and merged after a short review. All
-notebooks in the repository are tested and published in the Gammapy recipes
+notebooks in the repository are tested and published in the \gammapy recipes
 webpage\footnote{\url{https://gammapy.\github.io/gammapy-recipes}} automatically
@@
 discussions\footnote{\url{https://\github.com/gammapy/gammapy/discussions}}
-support forums, providing valuable feedback on the Gammapy functionalities,
+support forums, providing valuable feedback on the \gammapy functionalities,
 interface and documentation. Other communication channels have been set like
@@
 
-\subsection{Proposals for improving \gammapy}
+\subsection{Proposals for Improving \gammapy}
 \label{ssec:pigs}
 An important part of \gammapy's development organisation is the support
-for "Proposals for improving Gammapy" (PIG). This system is very much
+for "Proposals for improving \gammapy" (PIG). This system is very much
 inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}

### 2022-07-26 src/text/6-acknowledgements.tex
Reformat text files
Introduce GtiHub shortcut
Consistently use Gammapy shortcut

@@
 	\texttt{Matplotlib} communities for providing their packages which are
-	invaluable to the development of Astropy. We thank the GitHub team for
+	invaluable to the development of Astropy. We thank the \github team for
 	providing us with an excellent free development platform. We also are grateful
@@
 	documentation hosting and testing respectively. Finally, we would like to thank
-	all the Gammapy users that have provided feedback and submitted bug reports.
+	all the \gammapy users that have provided feedback and submitted bug reports.
 
@@
 
-	J.E.
-Ruiz acknowledges financial support from the State Agency for Research of the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709)
+	J.E. Ruiz acknowledges financial support from the State Agency for Research of
+	the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the
+	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709)
 

### 2022-07-26 src/text/2-package-subsections/analysis.tex
Update analysis sub-package description
Use shortcuts more consistently
Add instruments IRF plot

@@
 \label{ssec:gammapy-analysis}
-\todo{Quentin, Axel...}
-
 The \code{gammapy.analysis} sub-module provides a  high-level interface for the most
-common use cases identified in gamma-ray analyses. The classes and methods
+common use cases identified in \gammaray analyses. The classes and methods
 included can be used in Python scripts, notebooks or as commands within IPython
@@
 custom AnalysisStep, so ones could design and configure arbitrarily complex
-wokflows. \todo{the latter is not true for v1.0...}
+wokflows. \todo{the latter is not true for v1.0..., include example YAML file?}

### 2022-07-26 src/text/2-package-subsections/catalog.tex
Use shortcuts more consistently
Add instruments IRF plot

@@
 
-\begin{table*}
+\begin{table*}[ht!]
     \begin{center}
@@
 	\import{code-examples/generated/}{gp_catalogs}
-	\caption{Using gammapy.catalogs: Accessing underlying model, flux points and
-		lightcurve from the Fermi-LAT 4FGL catalog for the blazar PKS 2155-304}
+	\caption{Using \code{gammapy.catalogs} to access the underlying model, flux points and
+		light-curve from the \fermi 4FGL catalog for the blazar PKS 2155-304}
 	\label{codeexample:data}

### 2022-07-26 src/text/2-package.tex
Add instruments IRF plot

@@
 \label{sec:gammaray-data-analysis}
-
+%
+\begin{figure*}[ht!]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/irfs.pdf}
+	\caption{
+		Example instrument response functions of some experiments and
+        observatories for which \gammapy can analyse data. The \cta IRFs
+        are from the prod5 production. The \hess IRFs are from the DL3 DR1,
+        using observation ID 033787. The point spread function shows the 65\&
+        containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
+        \todo{Add more instruments? HAWC? MAGIC?}
+    }
+	\label{fig:irfs}
+\end{figure*}
+%
 % This might not be the bast place compared to introduction

### 2022-07-26 src/text/3-applications-subsections/population-studies.tex
Use title case consistently
Add instruments IRF plot

@@
-\subsection{Surveys, catalogs, and population studies}
+\subsection{Surveys, Catalogs, and Population Studies}
 \label{ssec:surveys-catalogs-and-population-studies}
@@
 studies over a large set of coherently detected and modelled objects. Early
-versions of \textit{gammapy} were developed in parallel of the preparation of
+versions of \gammapy were developed in parallel of the preparation of
 the \hess Galactic plane survey catalog~\citep[HGPS][]{2018A&A...612A...1H} and
@@
 finding local maxima in the significance, or TS maps,  given by the
-ExcessMapEstimator, or TSMapEstimator, respectively.  Further refinements can
+\code{ExcessMapEstimator}, or \code{TSMapEstimator}, respectively.  Further refinements can
 include for example  filtering and detection on these maps with techniques from

### 2022-07-26 src/figures/irfs.py

@@ -1,0 +1,86 @@
+import logging
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy import units as u
+from gammapy.data import DataStore
+from gammapy.irf import PSFMap
+from gammapy.maps import Map
+import matplotlib.ticker as ticker
+import config
+
+logging.basicConfig(level=logging.INFO)
+log = logging.getLogger(__name__)
+
+fermi_livetime = 5e7 * u.s
+
+offset = [1] * u.deg
+
+data_store = DataStore.from_dir("../data/cta-galactic-center/input/index/gps")
+obs_cta = data_store.obs(110380)
+
+data_store = DataStore.from_dir("../data/lightcurve/input/")
+obs_hess = data_store.obs(33787)
+
+
+figsize = config.FigureSizeAA(aspect_ratio=2.6, width_aa="two-column")
+
+xlim = 0.008, 500
+
+gridspec = {
+    "top": 0.92,
+    "right": 0.98,
+    "left": 0.08,
+    "bottom": 0.15
+}
+fig, axes = plt.subplots(
+    figsize=figsize.inch, nrows=1, ncols=2, gridspec_kw=gridspec
+)
+
+exposure_fermi = Map.read("../data/fermi-ts-map/input/fermi-3fhl-gc-exposure-cube.fits.gz")
+aeff_fermi = exposure_fermi.to_region_nd_map(func=np.mean) / fermi_livetime
+
+ax_aeff = axes[0]
+ax_aeff.set_title("Effective Area")
+obs_cta.aeff.plot_energy_dependence(ax=ax_aeff, offset=offset, label="CTA")
+obs_hess.aeff.plot_energy_dependence(ax=ax_aeff, offset=offset, label="H.E.S.S.")
+aeff_fermi.plot(ax=ax_aeff, marker="None", label="Fermi-LAT")
+
+ax_aeff.set_xlim(*xlim)
+ax_aeff.set_yscale("log")
+ax_aeff.set_ylim(1e-1, 8e6)
+ax_aeff.legend()
+
+psf_hess = obs_hess.psf
+
+ax_psf = axes[1]
+ax_psf.set_title("Point Spread Function")
+obs_cta.psf.plot_containment_radius_vs_energy(
+    ax=ax_psf, offset=offset, fraction=[0.68], label="CTA"
+)
[…]

### 2022-07-26 src/text/3-applications-subsections/population-studies.tex
Write minimal SED modelling section

@@
 four main steps : data-reduction; object detection; model fitting and model
-selection; associations and classification. The IACTs data-reduction step is
-done in the same way than described in the previous sections but scale-up to
+selection; associations and classification. The \iacts data-reduction step is
+done in the same way than described in the previous sections but scale up to
 few thousand of observations. The object detection step consists a minima in
@@
 determine their optimal parameters, and the best-candidate model. The
-subpackage gammapy.modeling.models offers a large variety of choice, and the
+subpackage \code{gammapy.modeling.models} offers a large variety of choice, and the
 possibility to add custom models.  Several spatial models (point-source, disk,

### 2022-07-26 src/text/3-applications-subsections/sed-modelling-analysis.tex
Update sed-modelling-analysis.tex
Update sed modeling section
Write minimal SED modelling section

@@
 \label{ssec:broadband-sed-modeling}
-
-Figure \ref{fig:multi_instrument_analysis}. Add explanation text.
+By combining \gammapy with astrophysical modelling codes users can also fit
+astrophysical spectral models to \gammaray data. In \gammaray
+astronomy what typically observes two radiation production
+mechanisms., the so called hadronic and leptonic scenarios.
+There are mutiple Python packages that are able to model
+the \gammaray emission, given a physical scenario. Among those
+packages are  \cite{agnpy}, \cite{naima}, \cite{jetset} or \cite{gamera}.
+Tyically those emission models predict broadband emission from
+radio waves up to the very high energy \gammaray range.
+By relying on the multiple dataset types in \gammapy those
+data can be combined to constrain such a broadband emission model.
+\gammapy provides a built-in \code{NaimaSpectralModel} whch allows
+users to wrap a given astrophysical emission model from the
+Naima package and fit it directly to \gammaray data.

### 2022-07-28 src/text/1-introduction.tex
Add big picture illustration

@@
 black holes and remnants of supernova explosions. As in other
-branches of astronomy \gammarays can be observed by both
+branches of astronomy, \gammarays can be observed by both
 satellite as well as ground based instruments.
-Very high energy cosmic \gammarays reaching Earth interact in the atmosphere and
+Ground based instrument use the Earth's atmosphere as a particle detector.
+Very high energy cosmic \gammarays interact in the atmosphere and
 create a large shower of secondary particles that can be observed from the ground.
@@
 	\centering
-	\includegraphics[height=\textwidth, angle=270]{static/gammapy-big-picture}
-    \caption{ \gammapy is a Python package
-		for high-level \gammaray data analysis. Using event lists, exposures and point
-		spread functions as input you can use it to generate science results such as
-		images, spectra, light curves or source catalogs. So far it has been used to
-		simulate and analyse \hess, \cta,  and \fermi data. As demonstrated
-		by several studies, it will also be applied to e.g., \veritas, \magic or \hawc data
-		in the future. }
-	\label{fig:big-picture}
+	\includegraphics[width=\textwidth]{figures/big-picture.pdf}
+    \caption{
+        Relation of \gammapy to different \gammaray instruments and the data formats.
+        \gammapy provide access to the data stored in GADF format and the
+        high-level data analysis functionality.}
+	\label{fig:big_picture}
 
@@
 In practice, the data-reduction workflow of all \gammaray observatories
-is remarkably similar.
-After data calibration, shower events are reconstructed and
+is remarkably similar. After data calibration, shower events are reconstructed and
 gamma/hadron separation is applied to build lists of \gammaray like events.
@@
 (FITS) format~\citep{fits} encapsulating this high-level information. This is
-realized by storing a list of gamma-like events with their measured quantites
+realized by storing a list of gamma-like events with their measured quantities
 (energy, direction, arrival time) and a parametrisation of the response of the
-system. (see Sec.~\ref{ssec:gammapy-data} and Sec.~\ref{ssec:gammapy-irf} for
-more information).
+system.
 
@@
 the rich eco-system of packages and its open and supportive community, from
-core numerical analysis packages such as numpy \citep{numpy} and
-scipy \citep{2020SciPy-NMeth}, visualization libraries,e.g. matplotlib \citep{matplotlib},
-or optimization packages such as iminuit \citep{iminuit}.
+core numerical analysis packages such as \numpy~\citep{numpy} and
+\scipy~\citep{2020SciPy-NMeth}, visualization libraries,e.g. Matplotlib \citep{matplotlib},
+or optimization packages such as Iminuit \citep{iminuit}.
 
 The \astropy~\citep{astropy} was created in 2012 to build a community-developed
-python package for astronomical reasearch. Among other things, the it offers functionality for
+Python package for astronomical reasearch. Among other things, the it offers functionality for
 transforming and representing astronomical coordinates, manipulating physical quantities
@@
 This is possible thanks to the definition of a common data format such as \gadf, and thanks to
-an open development with a broad community of contributors.
+an open development with a broad community of contributors. The relation of \gammapy to the
+different instruments the \gadf data format is illustarted in Figure~\ref{fig:big_picture}.
 
@@
 This data release served as a basis for analysis tools validation \cite[see e.g.]{Mohrmann2019}.
-
-TODO: Figure 1: Data -> \gammapy -> Spectra etc with some details
 

### 2022-07-28 src/text/2-package-subsections/astro.tex
Update astro sub-package description

@@
 \label{ssec:gammapy-astro}
-\todo{Atreyee}
-
 The \code{gammapy.astro} sub-package contains utility functions for studying physical
 scenarios in high energy astrophysics. The \code{gammapy.astro.darkmatter} module
-computes the so  called J-factors and the associated gamma-ray spectra expected
+computes the so  called J-factors and the associated \gammaray spectra expected
 from annihilation of dark matter in different channels according to the recipe
@@
 observational or theoretical considerations for different classes of Galactic
-VHE gamma-ray emitters: PWNe, SNRs \cite{1998ApJ...504..761C},
+VHE \gammaray emitters: PWNe, SNRs \cite{1998ApJ...504..761C},
 pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y}
-and gamma-ray binaries.
+and \gammaray binaries.
 

### 2022-07-28 src/text/2-package-subsections/data.tex

@@
 The so-called DL3 files represented by the \code{Observation} class consist
-of two types of elements: a list of gamma-ray events with relevant physical
+of two types of elements: a list of \gammaray events with relevant physical
 quantities for the successive analysis (estimated energy, direction and arrival
@@
 Sec.~\ref{ssec:gammapy-irf}). The separate handling of event lists and IRFs
-additionally allows for data from other gamma-ray instruments to be read. For
+additionally allows for data from other \gammaray instruments to be read. For
 example, to read \fermi data, the user can read separately their event list

### 2022-07-28 src/text/2-package-subsections/stats.tex

@@
 positions, and contain both signal and background events. Estimation of the
-number of signal events is done through likelihood maximization. In Gammapy,
+number of signal events is done through likelihood maximization. In \gammapy,
 the fit statistics are Poisson log-likelihood functions normalized like
-chi-squares, i.e., they follow the expression $2 \times log L$, where $L$ is
+chi-squares, i.e., they follow the expression $2 \time\cdot \log{\mathcal{L}}$,
+where $\mathcal{L}$ is
 the likelihood function used. The statistic function used when the expected
@@
 counts are marginalized parameters. It is used by datasets containing off
-counts measurements such as the SpectrumDatasetOnOff, used for classical
+counts measurements such as the \code{SpectrumDatasetOnOff}, used for classical
 spectral analysis.
@@
         are the computed on access of the corresponding class
-        attributes such as \code{.n\_sig} and \code{.sqrt\_ts}.
+        attributes such as \code{stat.n\_sig} and \code{stat.sqrt\_ts}.
     }

### 2022-07-28 src/text/2-package-subsections/visualisation.tex

@@
 \label{ssec:gammapy-visualization}
-\todo{Axel Donath}
 The \code{gammapy.visualization} sub-package contains helper functions

### 2022-07-28 src/text/3-applications-subsections/sed-modelling-analysis.tex

@@
 data can be combined to constrain such a broadband emission model.
-\gammapy provides a built-in \code{NaimaSpectralModel} whch allows
+\gammapy provides a built-in \code{NaimaSpectralModel} which allows
 users to wrap a given astrophysical emission model from the

### 2022-07-28 scripts/merge.py
Add merge script

@@ -1,0 +1,35 @@
+from pathlib import Path
+
+TEMPLATE = "\\input{{{0}}}"
+PATH_TEXT = Path("src/text")
+
+
+def merge_text_files(text, filenames):
+    """Merge tex files"""
+    for filename in filenames:
+        path = filename.parent.relative_to(PATH_TEXT.parent)
+        file = str(path) + "/" + filename.stem
+        template = TEMPLATE.format(file)
+
+        with open(filename, "r") as f_sub:
+            file_content = f_sub.read()
+            text = text.replace(template, file_content)
+
+    return text
+
+
+if __name__ == "__main__":
+    with (PATH_TEXT / "../ms.tex").open("r") as f:
+        text = f.read()
+
+    filenames = PATH_TEXT.glob("*.tex")
+    text = merge_text_files(text=text, filenames=filenames)
+
+    filenames = (PATH_TEXT / "2-package-subsections").glob("*.tex")
+    text = merge_text_files(text=text, filenames=filenames)
+
+    filenames = (PATH_TEXT / "3-applications-subsections").glob("*.tex")
+    text = merge_text_files(text=text, filenames=filenames)
+
+    with (PATH_TEXT / "../ms.tex").open("w") as f:
+        f.write(text)

### 2022-07-28 src/ms-review.tex

%                                                                 aa.dem
% AA vers. 9.0, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column
%\documentclass[longauth]{aa} % for the long lists of affiliations
%\documentclass[rnote]{aa} % for the research notes
%\documentclass[letter]{aa} % for the letters
%\documentclass[bibyear]{aa} % if the references are not structured
%                              according to the author-year natbib style

% \documentclass[]{aa}
\documentclass[traditabstract, longauth]{aa}

\usepackage{graphicx}
\usepackage{url}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{import}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage[utf8]{inputenc}

\input{code-examples/minted.tex}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

\newcommand{\code}[1]{\texttt{#1}}

\begin{document}
\newcommand{\PythonUrl}{\url{http://fits.gsfc.nasa.gov/}\xspace}
\newcommand{\FitsUrl}{\url{http://fits.gsfc.nasa.gov/}\xspace}
\newcommand{\GammapyUrl}{\url{http://gammapy.org}\xspace}
\newcommand{\GadfUrl}{\url{http://gamma-astro-data-formats.readthedocs.io/}\xspace}
\newcommand{\ReadthedocsUrl}{\url{https://readthedocs.org/}\xspace}
\newcommand{\TravisUrl}{\url{https://www.travis-ci.org/}\xspace}

\newcommand{\NaimaUrl}{\url{https://github.com/zblz/naima}\xspace}

% Note: not sure if we want to use that ... doesn't look too pretty
\newcommand{\astropy}{Astropy\xspace}
\newcommand{\gammapy}{Gammapy\xspace}
\newcommand{\scipy}{Scipy\xspace}
\newcommand{\numpy}{Numpy\xspace}

\newcommand{\hess}{H.E.S.S.\xspace}
\newcommand{\hawc}{HAWC\xspace}
\newcommand{\veritas}{VERITAS\xspace}
\newcommand{\magic}{MAGIC\xspace}
\newcommand{\iact}{IACT\xspace}
\newcommand{\iacts}{IACTs\xspace}
\newcommand{\cta}{CTA\xspace}
\newcommand{\swgo}{SWGO\xspace}
\newcommand{\irf}{IRF\xspace}
\newcommand{\irfs}{IRFs\xspace}
\newcommand{\fermi}{\textit{Fermi}-LAT\xspace}
\newcommand{\gammaray}{$\gamma$-ray\xspace}
\newcommand{\gammarays}{$\gamma$-rays\xspace}
\newcommand{\gadf}{GADF\xspace}
\newcommand{\milagro}{MILAGRO\xspace}
\newcommand{\github}{GitHub\xspace}

% Front matter
\title{Gammapy: A Python package for gamma-ray astronomy}
\titlerunning{Gammapy}
\authorrunning{Deil, Donath, Terrier et al.}

\author{
	Axel Donath \inst{\ref{inst:6}} \and
	Christoph Deil \inst{\ref{inst:13}} \and
	Régis Terrier \inst{\ref{inst:2}} \and
	Johannes King \inst{\ref{inst:22}} \and
	Jose Enrique Ruiz \inst{\ref{inst:17}} \and
	Quentin Remy \inst{\ref{inst:18}} \and
	Léa Jouvin \inst{\ref{inst:unknown}} \and
	Atreyee Sinha \inst{\ref{inst:26}} \and
	Matthew Wood \inst{\ref{inst:11}} \and
	Fabio Pintore \inst{\ref{inst:14}} \and
	Manuel Paz Arribas \inst{\ref{inst:unknown}} \and
	Laura Olivera \inst{\ref{inst:18}} \and
	Luca Giunti \inst{\ref{inst:2}} \and
	Bruno Khelifi \inst{\ref{inst:3}} \and
	Ellis Owen \inst{\ref{inst:21}} \and
	Brigitta Sipőcz \inst{\ref{inst:5}} \and
	Olga Vorokh \inst{\ref{inst:unknown}} \and
	Julien Lefaucheur \inst{\ref{inst:unknown}} \and
	Fabio Acero \inst{\ref{inst:7}} \and
	Thomas Robitaille \inst{\ref{inst:1}} \and
	David Fidalgo \inst{\ref{inst:unknown}} \and
	Jonathan D. Harris \inst{\ref{inst:unknown}} \and
	Cosimo Nigro \inst{\ref{inst:15}} \and
	Lars Mohrmann \inst{\ref{inst:18}} \and
	Dirk Lennarz \inst{\ref{inst:0}} \and
	Jalel Eddine Hajlaoui \inst{\ref{inst:2}} \and
	Alexis de Almeida Coutinho \inst{\ref{inst:27}} \and
	Matthias Wegenmat \inst{\ref{inst:unknown}} \and
	Dimitri Papadopoulos \inst{\ref{inst:unknown}} \and
	Maximilian Nöthe \inst{\ref{inst:25}} \and
	Nachiketa Chakraborty \inst{\ref{inst:unknown}} \and
	Michael Droettboom \inst{\ref{inst:20}} \and
	Helen Poon \inst{\ref{inst:unknown}} \and
	Arjun Voruganti \inst{\ref{inst:unknown}} \and
	Jason Watson \inst{\ref{inst:8}} \and
	Thomas Armstrong \inst{\ref{inst:unknown}} \and
	Vikas Joshi \inst{\ref{inst:12}} \and
	Erik Tollerud \inst{\ref{inst:24}} \and
	Erik M. Bray \inst{\ref{inst:unknown}} \and
	Domenico Tiziani \inst{\ref{inst:unknown}} \and
	Gabriel Emery \inst{\ref{inst:unknown}} \and
	Hubert Siejkowski \inst{\ref{inst:unknown}} \and
	Kai Brügge \inst{\ref{inst:23}} \and
	Luigi Tibaldo \inst{\ref{inst:16}} \and
	Arpit Gogia \inst{\ref{inst:unknown}} \and
	Ignacio Minaya \inst{\ref{inst:unknown}} \and
	Marion Spir-Jacob \inst{\ref{inst:unknown}} \and
	Yves Gallant \inst{\ref{inst:unknown}} \and
	Andrew W. Chen \inst{\ref{inst:9}} \and
	Roberta Zanin \inst{\ref{inst:4}} \and
	Jean-Philippe Lenain \inst{\ref{inst:unknown}} \and
	Larry Bradley \inst{\ref{inst:24}} \and
	Kaori Nakashima \inst{\ref{inst:12}} \and
	Anne Lemière \inst{\ref{inst:2}} \and
	Mathieu de Bony \inst{\ref{inst:unknown}} \and
	Matthew Craig \inst{\ref{inst:unknown}} \and
	Lab Saha \inst{\ref{inst:6}} \and
	Zé Vinicius \inst{\ref{inst:unknown}} \and
	Kyle Barbary \inst{\ref{inst:unknown}} \and
	Thomas Vuillaume \inst{\ref{inst:28}} \and
	Adam Ginsburg \inst{\ref{inst:unknown}} \and
	Daniel Morcuende \inst{\ref{inst:unknown}} \and
	José Luis Contreras \inst{\ref{inst:unknown}} \and
	Laura Vega Garcia \inst{\ref{inst:unknown}} \and
	Oscar Blanch Bigas \inst{\ref{inst:unknown}} \and
	Víctor Zabalza \inst{\ref{inst:unknown}} \and
	Wolfgang Kerzendorf \inst{\ref{inst:19}} \and
	Rolf Buehler \inst{\ref{inst:10}} \and
	Sebastian Panny \inst{\ref{inst:unknown}} \and
	Silvia Manconi \inst{\ref{inst:unknown}} \and
	Stefan Klepser \inst{\ref{inst:10}} \and
	Peter Deiml \inst{\ref{inst:unknown}} \and
	Johannes Buchner \inst{\ref{inst:unknown}} \and
	Hugo van Kemenade \inst{\ref{inst:unknown}} \and
	Eric O. Lebigot \inst{\ref{inst:unknown}} \and
	Benjamin Alan Weaver \inst{\ref{inst:unknown}} \and
	Debanjan Bose \inst{\ref{inst:unknown}} \and
	Rubén López-Coto \inst{\ref{inst:unknown}} \and
	Sam Carter \inst{\ref{inst:unknown}}
}

\institute{
	Amazon, Atlanta GA, US \label{inst:0} \and
	Aperio Software, Insight House, Riverside Business Park, Stoney Common Road, Stansted, Essex, CM24 8PL, UK \label{inst:1} \and
	Astroparticle and Cosmology Laboratory CNRS, Université de Paris, 10 Rue Alice Domon et Léonie Duquet, 75013 Paris, France \label{inst:2} \and
	CNRS \label{inst:3} \and
	CTA Observatory gGmbH, Via Piero Gobetti 93/3 40129 Bologna, Italy \label{inst:4} \and
	California Institute of Technology, Pasadena CA, US \label{inst:5} \and
	Center for Astrophysics | Harvard \& Smithsonian, CfA, 60 Garden St., 02138 Cambridge MA, US \label{inst:6} \and
	DAp/AIM, CEA-Saclay/CNRS, France \label{inst:7} \and
	DESY \label{inst:8} \and
	Department of Physics, University of the Free State, PO Box339, Bloemfontein 9300, South Africa \label{inst:9} \and
	Deutsches Elektronen-Synchrotron, DESY, Platanenallee 6 15738 Zeuthen, Germany \label{inst:10} \and
	Facebook, 1 Hacker Way, Menlo Park, CA 94025, US \label{inst:11} \and
	Friedrich-Alexander-Universität Erlangen-Nürnberg, Erlangen Centre for Astroparticle Physics, Erwin-Rommel-Str. 1 91058 Erlangen, Germany \label{inst:12} \and
	HeidelbergCement AG, Berliner Straße 6, 69120 Heidelberg, Germany \label{inst:13} \and
	INAF/IASF, via Ugo La Malfa 153,  90146 Palermo, Italy \label{inst:14} \and
	Institut de Fisica d'altes Energies, IFAE, Edifici Cn, Campus UAB, 08193 Bellaterra (Barcelona), Spain \label{inst:15} \and
	Institute de Recherche en Astrophysique et Planetologie, IRAP, \label{inst:16} \and
	Instituto de Astrofísica de Andalucía - CSIC, Gta. de la Astronomía, 18008 Granada, Spain \label{inst:17} \and
	Max Planck Institut für Kernphysik, MPIK, Saupfercheckweg 1, 69117 Heidelberg, Germany \label{inst:18} \and
	Michigan State University, Department of Physics and Astronomy, 428 S Shaw Ln East Lansing, MI 48824, US \label{inst:19} \and
	Mozilla, Mountain View, CA \label{inst:20} \and
	National Tsing Hua University Institute of Astronomy, Hsinchu, Taiwan \label{inst:21} \and
	Pamyra \label{inst:22} \and
	Point 8 GmbH, Rheinlanddamm 201, 44139 Dortmund, Germany \label{inst:23} \and
	Space Telescope Science Institute, STScI, 3700 San Martin Drive, 21218 Baltimore MD, US \label{inst:24} \and
	TU Dortmund University, Otto-Hahn-Str. 4a 44227 Dortmund, Germany \label{inst:25} \and
	Universidad Complutense de Madrid EMFTEL, UCM, Plaza de la Ciencias, 28040 Madrid, Spain \label{inst:26} \and
	Universidade de São Paulo, Brazil \label{inst:27} \and
	Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecyde Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:28} \and
	unknown \label{inst:unknown}
}

% \abstract{}{}{}{}{}
% 5 {} token are mandatory

\abstract{
	% TODO: the feature are still to detailed and partly copy and pasted form the ICRS abstract...avoid this
	% context heading (optional)
	% {} leave it empty if necessary
	%{Gammapy context:}
	Historically the data as well as analysis software in \gammaray astronomy is
	proprietary to the experiments. With the future Cherenkov Telescope Array
	(CTA), which will be operated as an open \gammaray observatory with public
	data, there is a corresponding need for open high-level analysis software. In
	this article we present the first major version v1.0 of \gammapy, a
	community-developed open-source Python package for \gammaray astronomy. We
	present its general design and provide an%
	overview of the analysis methods and features it implements. Starting from
	event lists and a description of the specific instrument response functions
	(IRF) stored in open FITS based data formats, \gammapy implements . Thereby it
	handles the dependency of the IRFs with time, energy as well as position on the
	sky. It offers a variety of background estimation methods for spectral, spatial
	and spectro-morphological analysis. Counts, background and IRFs data are
	bundled in datasets and can be serialised, rebinned and stacked. \gammapy
	supports to model binned data using Poisson%
	maximum likelihood fitting. It comes with built-in spectral, spatial and
	temporal models as well as support for custom user models, to model e.g.,
	energy dependent morphology of \gammaray sources. Multiple datasets can be
	combined in a joint-likelihood approach to either handle time dependent IRFs,
	different classes of events or combination of data from multiple instruments.
	Gammapy also implements methods to estimate flux points, including likelihood
	profiles per energy bin, light curves as well as flux and signficance maps in
	energy bins.  We further describe the general%
	development approach and how \gammapy integrates into ecosystem of other
	scientific and astronomical Python packages. We also present analysis examples
	with simulated CTA data and provide results of scientific validation analyses
	using data of existing instruments such as \hess and \fermi.

	% The \gammaray can be considered as the last frontier
	% In the last two decades the measurement of \gammaray emission from the universe has
	% evolved from a niche

	% aims heading (mandatory)
	%{Gammapy aims}
	%Reproducible analyses, share algorithms etc.

	% methods heading (mandatory)
	%{Gammapy methods}

	% results heading (mandatory)
	%{Gammapy results}

	% conclusions heading (optional), leave it empty if necessary
	%{Gammapy conclusions}
}

% \date{Received September 15, 1996; accepted March 16, 1997}
\keywords{
	Gamma rays: general -
	Astronomical instrumentation, methods and techniques -
	Methods: data analysis
}

\maketitle

% Main part
\section{Introduction}
\label{sec:introduction}

%% \gammaray astronomy
\gammaray astronomy is a rather young field of research. The \gammaray~
range of the electromagnetic spectrum provides us with insight to the
most energetic process in the universe such as surroundings of
black holes and remnants of supernova explosions. As in other
branches of astronomy, \gammarays can be observed by both
satellite as well as ground based instruments.
Ground based instrument use the Earth's atmosphere as a particle detector.
Very high energy cosmic \gammarays interact in the atmosphere and
create a large shower of secondary particles that can be observed from the ground.
Ground-based \gammaray astronomy relies on this phenomenon to detect the
primary \gammaray photons and measure their direction and energy.
It covers the energy range from fews tens of GeV up to the PeV.
There are two main categories of instrument \citep{2015CRPhy..16..610D}.
Imaging Atmospheric Cherenkov Telescopes (IACT) make images of atmospheric showers
by detecting the Cherenkov radiation emitted by the cascading charged particles and
use these images to reconstruct the properties of the incident particle.
Those instruments have a limited field of view (FoV) and duty cycle, but
good energy and angular resolution.

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/big-picture.pdf}
    \caption{
        Relation of \gammapy to different \gammaray instruments and the data formats.
        \gammapy provide access to the data stored in GADF format and the
        high-level data analysis functionality.}
	\label{fig:big_picture}

\end{figure*}

Water Cherenkov observatories detect directly particles from the tail of the
shower when it reaches the ground. These instruments have very
large field-of-view, large duty-cycle but higher energy threshold and
usually have lower signal to noise ratios compared to IACTs.

%% Context
Ground based \gammaray astronomy has been historically structured
by experiments run by independent collaborations relying
on their own proprietary data and analysis software developed as part of the
instrument. While this model has been very successful so far, it does not
permit easy combination of data from several instruments and is therefore
a limitation for interoperability of existing facilities. Especially
because the different detection techniques have complementary
properties.

%TODO: better transition into context
The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
as an open observatory in the domain. Its high level data will be shared publicly after
some proprietary period and the software required to analyze it will be distributed
as well. To allow the re-usability of existing instruments and their interoperability
requires open data formats and open tools that can support the various analysis methods
commonly used in the field.

%% Context : formats
In practice, the data-reduction workflow of all \gammaray observatories
is remarkably similar. After data calibration, shower events are reconstructed and
gamma/hadron separation is applied to build lists of \gammaray like events.
The latter are then used to derive scientific results, such as spectra, sky maps
or light curves, taking into account the specific instrument response functions (IRF).
The information in this high data level is independent on
the data reduction, and eventually of the detection technique. This implies,
for example, that data from IACT and particle samplers can be represented
within the same model. The efforts to prototype a format usable by various instruments
converged in the so-called \textit{Data Format for \gammaray Astronomy}
initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
\texttt{gamma-astro-data-format} (\gadf). The latter proposes prototypical
specifications to produce files based on the flexible image transport system
(FITS) format~\citep{fits} encapsulating this high-level information. This is
realized by storing a list of gamma-like events with their measured quantities
(energy, direction, arrival time) and a parametrisation of the response of the
system.

%% Context: develoment of open software
Python has become extremely popular as a scientific programming language
in particular in the field of data sciences. The success is
mostly attributed to the simple and easy to learn syntax, the ability to act as
a "glue" language between different programming languages and last but not least
the rich eco-system of packages and its open and supportive community, from
core numerical analysis packages such as \numpy~\citep{numpy} and
\scipy~\citep{2020SciPy-NMeth}, visualization libraries,e.g. Matplotlib \citep{matplotlib},
or optimization packages such as Iminuit \citep{iminuit}.

The \astropy~\citep{astropy} was created in 2012 to build a community-developed
Python package for astronomical reasearch. Among other things, the it offers functionality for
transforming and representing astronomical coordinates, manipulating physical quantities
and their units as well as reading and writing FITS files.

%% \gammapy: concept and goals
%%% Question: starting date? Is is relevant, what is the real start?
The \gammapy project started in 2015 with the objective of building a flexible and
efficient software library for very high energy \gammaray data analysis \citep{gammapy_2015}.
This is possible thanks to the definition of a common data format such as \gadf, and thanks to
an open development with a broad community of contributors. The relation of \gammapy to the
different instruments the \gadf data format is illustarted in Figure~\ref{fig:big_picture}.

%\gammapy is built on the scientific Python stack and makes use of Astropy.

%% \gammapy: from first developments to validation and selection
The \hess collaboration released a limited test dataset (about 50 hours of
observations taken between 2004 and 2008) based  on the \gadf DL3 format \citep{HESS_DR1}.
This data release served as a basis for analysis tools validation \cite[see e.g.]{Mohrmann2019}.

%% Paper outline
In this article, we describe the general structure of the \gammapy package and
its main concepts. In Section \ref{sec:analysis-workflow-overview}, we present
the data analysis workflow in very high energy \gammaray astronomy. Then we
show how this workflow is reflected in the structure of the \gammapy package and
describe the various subpackages it contains. Section \ref{sec:applications}
presents a number of applications, while Section \ref{sec:gammapy-project}
discusses the project organization.

\section{Gamma-ray Data Analysis}
\label{sec:gammaray-data-analysis}
%
\begin{figure*}[ht!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/irfs.pdf}
	\caption{
		Example instrument response functions of some experiments and
        observatories for which \gammapy can analyse data. The \cta IRFs
        are from the prod5 production. The \hess IRFs are from the DL3 DR1,
        using observation ID 033787. The point spread function shows the 65\&
        containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
        \todo{Add more instruments? HAWC? MAGIC?}
    }
	\label{fig:irfs}
\end{figure*}
%
% This might not be the bast place compared to introduction
The data reduction process in \gammaray astronomy is usually split into two parts.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique and even to a given instrument.

The other sequence, referred to as high-level analysis, deals with the extraction of physical
quantities related to \gammaray sources and the production of high-level products such as spectra,
lightcurves and catalogs. The methods and tools applied here are more generic and are broadly
shared across the field. They also frequently imply joint analysis of multi-instrument data.
To extract physically relevant information, the measured data are usually compared to a
model of the expected \gammaray emitters in the instrument field-of-view using statistical
techniques such as maximum likelihood.

We can write the expected number of detected events at measured position $p$ and energy $E$:
\begin{align}
   N(p, E) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
   &\times \Phi(p_{\rm true}, E_{\rm true}) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
\end{align}
where
\begin{itemize}
\item $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response
\item $\Phi(p_{\rm true}, E_{\rm true})$ is the sky flux model
\item $t_{\rm obs}$ is the observation time
\end{itemize}

A common assumption is that the instrument response can be simplified as the product
of three independent functions:

\begin{align}
   R(p, E|p_{\rm true}, E_{\rm true}) = &A_{\rm eff}(p_{\rm true}, E_{\rm true}) \times\\
    &PSF(p|p_{\rm true}, E_{\rm true}) \times\\
    &E_{\rm disp}(E|p_{\rm true}, E_{\rm true})
\end{align}
where:
\begin{itemize}
\item $A_{\rm eff}(p_{\rm true}, E_{\rm true})$ is the effective collection area of the detector. It is the product
  of the detector collection area times its detection efficiency at true energy $E_{\rm true}$ and position $p_{\rm true}$.
\item $PSF(p|p_{\rm true}, E_{\rm true})$ is the point spread function. It gives the probability of
  measuring a direction $p$ when the true direction is $p_{\rm true}$ and the true energy is $E_{\rm true}$.
  \gammaray instruments consider the probability density of the angular separation between true and reconstructed directions
  $\delta p = p_{\rm true} - p$, i.e. $PSF(\delta p|p_{\rm true}, E_{\rm true})$.
\item $E_{\rm disp}(E|p_{\rm true}, E_{\rm true})$ is the energy dispersion. It gives the probability to
  reconstruct the photon at energy $E$ when the true energy is $E_{\rm true}$ and the true position :$p_{\rm true}$.
  \gammaray instruments consider the probability density of the migration $\mu=\frac{E}{E_{\rm true}}$,
  i.e. $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$.
\end{itemize}

\gammaray data at the Data Level 3 therefore consists in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the aforementioned
effective area, point spread function (PSF), energy dispersion and residual hadronic background.
The handling of DL3 data is performed by classes and methods
in the gammapy.data  (see \ref{ssec:gammapy-data}) and the gammapy.irf
(see \ref{ssec:gammapy-irf}) subpackages.

The first step in the analysis is the selection and extraction of observations
based of their meta data including information such as pointing direction, observation
time and observation conditions.

The next step of the analysis is the data reduction where all observation events and instrument
responses are projected onto a user-defined geometry.A typical geometry consists in a spectral representation with a measured
energy axis, and in a spatial representation, either a coordinates system  with a projection
(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
The gammapy.maps subpackage provides general multidimensional geometry objects
(Geom) and the associated data structures (Maps), see \ref{ssec:gammapy-maps}.

All observation events and instrument responses are projected onto the
user defined geometry. Because residual hadronic background models can be subject
to significant uncertainties, background correction must be applied,
such as the ring or the field-of-view background techniques or
background measurements must be performed within, e.g. reflected regions~\citep{Berge07}.
Parts of the data with high associated IRF systematics must also be excluded by defining
a "safe" data range. These data reduction steps are performed by classes and functions
implemented in the gammapy.makers subpackage (see \ref{ssec:gammapy-makers}).

The counts data and the reduced IRFs in the form of maps are bundled into dataset objects
that represent the data level 4 (DL4). They can be written to
disk, in a format specific to \gammapy to allow users to read them back at any time later
for modeling and fitting.

This latter step datasets classes bundle reduced data in form of maps, reduced IRFs, models and
fit statistics. Different sub-classes support different analysis methods
and fit statistics (e.g. Poisson statistics with known background or
with OFF background measurements). The datasets are used to perform joint-likelihood
fitting allowing to combine different measurements, e.g. from different observations
but also from different instruments or event classes. They can also be used for binned
simulation as well as event sampling to simulate DL3 events data.

The next step is then typically to model and fit the datasets, either
individually, or in a joint likelihood analysis. For this purpose \gammapy
provides a uniform interface to multiple fitting backends. It also provides
a variety of :ref:`built in models <model-gallery>`. This includes spectral,
spatial and temporal model classes to describe the \gammaray emission in the sky.
Where spectral models can be simple analytical models or more complex ones from radiation
mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{o}$ decay).
Independently or subsequently to the global modelling, the data can be
re-grouped to compute flux points, light curves and flux as well as significance
maps in energy bands.

\section{\gammapy Package}
\label{sec:gammapy-package}
\subsection{Overview}
\label{ssec:overview}
%
\begin{figure*}[ht!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
	\caption{
		\gammapy sub-package structure and data analysis workflow. The top row
        defines the groups for the different data levels and reduction steps
        from raw gamma-like events on the left, to high level science products
        on the right. The direction of the data flow is illustrated with the
        grey arrows. The gray folder icons represent the different sub-packages
        in \gammapy and their names. Below each icon there is a list of the most
        important objects defined in the sub-package.
    }
	\label{fig:data_flow}
\end{figure*}
%
The \gammapy package is structured into multiple sub-packages. The definition
of the content of the different sub-packages follows mostly the stages in the
data reduction workflow described in the previous section. Sub-packages
either contain data structures representing data at different data reduction
levels or contain algorithms to transition between the different data reduction
levels.

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and instrument response functions as well as functionality
to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets for example to create source catalogs. Estimator classes,
which are contained in \code{gammapy.estinators} are used to
compute higher level science products such as flux and signficance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high level interface for executing analyses
defined from configuration files. In the following sections we will
introduce all sub-packages and their functionality in more detail.

\subsection{gammapy.data}
\label{ssec:gammapy-data}
The \code{gammapy.data} sub-package implements the functionality to select,
read and represent DL3 \gammaray data in memory. It provides the main user
interface to access the lowest data level. \gammapy currently only
supports data that is compliant with v0.2 of the \gadf data format.
As both the \gadf data model and \gammapy were initially conceived for
\iact data analysis, DL3 data are typically bundled into individual
observations, which correspond to stable periods of data
aquisitions (typically $20 - 30\,{\rm min}$) for a given instrument.
Each observation is assigned a unique integer ID for reference.

A typical usage example is shown in Figure~\ref{fig*:minted:gp_data}.
First a \code{DataStore} object is created from the path of the data
directory, which contains the DL3 data index file. The \code{DataStore}
object gathers a collection of observations and providing ancillary
files containing information about the telescope observation mode and the
content of the data unit of each file. The \code{DataStore} allows for
selecting a list of observations based on specific filters.

The so-called DL3 files represented by the \code{Observation} class consist
of two types of elements: a list of \gammaray events with relevant physical
quantities for the successive analysis (estimated energy, direction and arrival
times) that is handled by the \code{EventList} class and an instrument
response function (IRF), providing the response of the system, typically
factorised in independent components (see the description in
Sec.~\ref{ssec:gammapy-irf}). The separate handling of event lists and IRFs
additionally allows for data from other \gammaray instruments to be read. For
example, to read \fermi data, the user can read separately their event list
(already compliant with the \gadf specifications) and then find the appropriate
IRF class representing the response functions provided by \fermi, see
Sec.~\ref{ssec:fermi}.
%
\begin{figure}[ht!]
	\import{code-examples/generated/}{gp_data}
	\caption{
        Using \code{gammapy.data} to access DL3 level data with a \code{DataStore} object.
        Individual observations can be accessed by their unique integer observation id number.
        The actual events and instrument response functions can be accessed
        as attributes on the \code{Observation} object, such as \code{.events}
        or \code{.aeff} for the effective area information.
    }
	\label{fig*:minted:gp_data}
\end{figure}
%

\subsection{gammapy.irf}
\label{ssec:gammapy-irf}
%
%\begin{figure}
%	%	\import{code-examples/generated/}{gp_makers}
%
%	\caption{In Fig.~\ref{ig*:minted:irf_examples}, we show some example of Aeff,
%		PSF, Edisp and BKG read and plotted from a typical \irf.}
%	\label{ig*:minted:irf_examples}
%\end{figure}
%
The \code{gammapy.irf} sub-package contains all classes and functionality
to handle IRFs in a variety of formats.
Usually, \irfs store instrument properties in the form of multi-dimensional
tables, with quantities expressed in terms of energy (true or reconstructed),
off-axis angles or cartesian detector coordinates. The main information stored in
the common \gammaray \irfs are the effective area (Aeff), energy dispersion
(Edisp), point spread function (PSF) and background rate (BKG). The \code{gammapy.irf}
sub-package can open and access specific \irf extensions,
interpolate and evaluate the quantities of interest on both energy and spatial
axes, convert their format or units in different kinds, plot or write them into
output files. In the following, we list the main classes of the
sub-package:

\paragraph{Effective area:}
\gammapy provides the class \code{EffectiveAreaTable2D} to
manage Aeff, which is usually defined in terms of true energy and offset angle.
The class functionalities offer the possibility to read from files or to create
it from scratch. {\code{EffectiveAreaTable2D} can also convert, interpolate,
write, and evaluate the effective area for a given energy and offset angles, or
even plot the multi-dimensional Aeff table.

\paragraph{Point spread function:}
\gammapy allows user to treat different kinds of PSFs,
in particular, parametric multi-dimensional gaussians (\code{EnergyDependentMultiGaussPSF})
or King profile functions (\code{PSFKing})
one. The \code{EnergyDependentMultiGaussPSF} class is able to handle up to three
gaussians, defined in terms of amplitudes and sigma given for each true energy
and offset angle bin. Similarly, \code{PSFKing takes} into account the gamma and
sigma parameters as defined here. The \code{ParametricPSF} allows to create a
PSF with a representation different from gaussian(s) or King profile(s).
Finally, the user can take advantage from the \code{PSFMap} class, which creates
a multi-dimensional map of the PSF in WCS coordinates. At each position, a PSF
kernel map (\code{PSFKernel}) provides a PSF as a function of the true energy.
The creation of PSF kernel maps, where the PSF is defined for each
sky-position, is also given to the user. The latter two can speed up analyses.

\paragraph{Energy dispersion:}
Edisp, in \iact, is generally given in terms of the so
called migration parameter ($\mu$), which is defined as the ratio between the
reconstructed energy and the true energy. This ratio should be as close as one
and its dispersion can assume the shape of a gaussian (or even more complex
distributions). Migration parameter is given at each offset angle and
reconstructed energy. The main sub-classes are \code{EnergyDispersion2D},
designed to interpret Edisp, \code{EDispKernelMap}, which builds an Edisp kernel
map, i.e., a 4-dimensional WCS map where at each sky-position is associated an
Edisp kernel. The latter is a representation of the Edisp as a function of the
true energy only thanks to the sub-class \code{EDispKernel}.

\paragraph{Background model:}
The BKG can be represented in \gammapy as either 1) a 2D map (\code{Background2D})
of count rate normalised per steradians and energy at different
energies and offset-angles or 2) as rate per steradians and energy, as a
function of reconstructed energy and detector coordinates (\code{Background3D}).
In the former, the background is expected to follow a radially symmetric shape,
while in the latter, it can be more complex.

\subsection{gammapy.maps}
\label{ssec:gammapy-maps}
The \code{gammapy.maps} sub-package provides classes that represent data
structures associated with a set of coordinates or a region on a sphere. In
addition it allows to handle an arbitrary number of non-spatial data
dimensions, such as time or energy. It is organized around three types of
structures: geometries, sky-maps and map axes, which inherit from the base
classes \code{Geom}, \code{Map} and \code{MapAxis} respectively.

The geometry object defines the pixelization scheme and map boundaries. It also
provides methods to transform between sky and pixel coordinates. Maps consist
of a geometry instance together with a Numpy data array containing the corresponding
map values. Map axes contain a sequence of ordered values which define bins on
a given dimension, spatial or not. Map axes can have physical units attached to
them, as well as define non-linear spaced bins. All map classes support operations such
as arithmetic operations with unit support, up- and downsampling along
extra axes, interpolation, resampling of extra axes, interactive visualisation
in notebooks and interpolation onto different geometries.

The sub-package provides a uniform API for the FITS World Coordinate System
(WCS), the HEALPix pixelization and region-based data structure
(see Figure~\ref{ig*:minted:gp_maps}).

\begin{figure}
	\import{code-examples/generated/}{gp_maps}

	\caption{
        Using \code{gammapy.maps} to create a WCS, a HEALPix and a region
		based data structures. The initialisation parameters include
        consistently the positions of the center of the map, the pixel
        size, the extend of the map as well as the energy axis definition.
        The energy minimum and maximum values for the creation of the
        \code{MapAxis} object can be defined as strings also specifying the
        unit. Region definitions can be passed as strings following
        the DS9 region specifications \url{http://ds9.si.edu/doc/ref/region.html}.
        }
    \label{ig*:minted:gp_maps}
\end{figure}

% itemize because it helps me write, could also just be paragraphs...
\subsubsection{WCS Maps}
The FITS WCS pixelization supports a different number of projections to
represent celestial spherical coordinates in a regular rectangular grid.
\gammapy provides full support to data structures using this pixelization
scheme. For details see ~\cite{Calabretta2002}. This pixelisation
is typically used for smaller regions of interests, such as pointed
observations.

\subsubsection{HEALPix Maps}
This pixelization scheme ~\citep{Calabretta2002} provides a
subdivision of a sphere in which each pixel covers the same surface area as
every other pixel. As a consequence, however, pixel shapes are no longer
rectangular, or regular.
This pixelisation is typically used for all-sky data, such as data
from the \hawc or \fermi observatory. \gammapy natively supports
the multiscale definiton of the HEALPix pixelisation and thus
allows for easy up and downsampling of the data. In addition to
the all-sky map, \gammapy also supports a local HEALPix
pixelisation where the size of the map is constrained to a given
radius.
For local nighbourhood operations, such as convolution \gammapy relies
on projecting the HEALPix data to a local tangential WCS grid.

\subsubsection{Region Maps}
In this case, instead of a fine spatial grid
dividing a rectangular sky region, the spatial dimension is reduced to a single
bin with an arbitrary shape, describing a region in the sky with that same
shape. Typically they are is used together with a non-spatial dimension, for
example an energy axis, to represent how a quantity varies in that dimension
inside the corresponding region. The region is represented on the local
tangential projection see \cite{Astropy regions}.

Additionally, the \code{MapAxis} class provides a uniform API for axes representing
bins on any physical quantity, such as energy or angular offset. The special
case of time is covered by the dedicated \code{TimeMapAxis}, which allows time bins to
be non-contiguous, as it is often the case with observation time-stamps. The
generic class \code{LabelMapAxis} allows the creation of axes for non-numeric
entries.

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
%
\begin{figure}
	\import{code-examples/generated/}{gp_datasets}
	\caption{
        Using \code{gammapy.datasets} to read existing reduced binned datasets.
        After the different datasets are read from disk they are collected into a
        common \code{Datasets} container. All dataset types have an associated
        name attribute to allow access by name later in the code. The
        environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
        by \gammapy.
    }
	\label{fig*:minted:gp_datasets}
\end{figure}
%
The end product of the data reduction process described in Section
\ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps,
at the DL4 level. The \code{gammapy.datasets} subpackage contains classes to bundle
together binned data along with associated models and the likelihood, which
provides an interface to the Fit class (Sec \ref{ssec:gammapy-modeling}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistics, different types of Datasets are supported. \code{MapDataset} is
used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
done using \code{SpectrumDataset}. While the default statistics for both of these is
Cash, their corresponding on off versions are adapted for the case where the
background is measured from real off counts, and support wstat statistics. The
predicted counts are computed by convolution of the models with the associated
IRFs. Fitting of precomputed flux points is enabled through \code{FluxPointsDataset},
using chi2 statistics. Multiple datasets of same or different types can be
bundled together in \code{Datasets} (e.g., Figure \ref{fig*:minted:gp_datasets}),
where the likelihood from each constituent member is added, thus facilitating
joint fitting across different observations, and even different instruments
across different wavelengths. Datasets also provide functionalities for
manipulating reduced data, eg: stacking, sub-grouping, plotting, etc. Users can
also create their customized datasets for implementing modified likelihood
methods.

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
%
\begin{figure}
    \import{code-examples/generated/}{gp_makers}
	\caption{
        Using \code{gammapy.makers} to reduce DL3 level data into a
		\code{MapDataset}. All \code{Maker} classes take
        the configuration on initialisation of the class.
    }
	\label{ig*:minted:gp_makers}
\end{figure}
%
The data reduction step includes all tasks required to process and prepare
\gammaray data from the DL3 level to modeling and fitting. The \code{gammapy.makers} sub-package
contains the various classes and functions required to do so. First, events are
binned and IRFs are interpolated and projected onto the chosen analysis
geometry. This produces counts, exposure, background, psf and energy dispersion
maps. The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.

Because the background models suffer from strong uncertainties it is required
to correct them from the data themselves. Several techniques are commonly used
in \gammaray astronomy such as field-of-view background normalization or
background measurement in reflected regions, see~\cite{Berge07}.
Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
\code{ReflectedRegionsBackgroundMaker} are in charge of this step.

Finally, to limit other sources of systematic uncertainties, a data validity
domain is determined by the \code{SafeMaskMaker}. It can be used to limit the
extent of the field of view used or to limit the energy range to e.g., a domain
where the energy reconstruction bias is below a given value.

\subsection{gammapy.modeling}
\label{ssec:gammapy-modeling}
%
\code{gammapy.modeling} contains all the functionality related to modeling and fitting
data. This includes spectral, spatial and temporal model classes, as well as
the fit and parameter API.

\subsubsection{Models}
\label{sssec:models}
Source models in \gammapy are four dimensional models which support two
spatial dimensions $\ell, b$, and energy dimension $E$ as well as
the time dimension $t$. To simplify the the definition of the
models, \gammapy uses a factorised representation of the total source
model:

\begin{equation}
    f(l, b, E, t) = F(E)  \cdot G(l, b, E) \cdot  H(t, E)
\end{equation}

Where the spectral model $F$ implicitly carries the total flux
norm of the model. The spatial model $G$ optionally depends
on energy and allows to support e.g. energy dependent
morphology models. The temporal model component $H$
optionally also supports an energy variable to
allow for spectral variations of the model with time.

Following the factorisation The models objects are grouped
into the following categories:

\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves
\end{itemize}

The models follow a naming scheme which contains the category as a suffix to
the class name.

The spectral models include a special class of normed models, which have a
dimension-less normalisation. These spectral models feature a norm parameter
instead of amplitude and are named using the NormSpectralModel suffix. They
must be used along with another spectral model, as a multiplicative correction
factor according to their spectral shape. They can be typically used for
adjusting template based models, or adding a EBL correction to some analytic
model. The analytic spatial models are all normalized such as they integrate to
unity over the sky but the template spatial models may not, so in that special
case they have to be combined with a \code{NormSpectralModel}.

The \code{SkyModel} object represents factorised model that combine the spectral,
spatial and temporal model components (by default the spatial and temporal components are
optional). SkyModel objects represents additive emission components, usually
sources or diffuse emission, although a single source can also be modeled by
multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
has a \code{Models} class.

The model gallery provides a visual overview of the available models in
\gammapy. Most of the analytic models  commonly used in \gammaray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\cite{naima}. The modeling framework can be easily extended with
user-defined models. For example agnpy models that describe leptonic radiative
processes in jetted Active Galactic Nuclei (AGN) can wrapped into
\gammapy~\citep[see section3.5 of ][]{2021arXiv211214573N} .

\begin{figure}
	\import{code-examples/generated/}{gp_models}
	\caption{Using \code{gammapy.modeling.models} to define a source model with a
    spectral, spatial and temporal component. For convenience the model
    parameters can be defined as strings with attached units. The spatial model
    takes an addtional \code{frame} parameter which allow users to define
    the coordinate frame of the position of the model.
    }
	\label{fig*:minted:gp_models}
\end{figure}

\subsubsection{Fit}
\label{sssec:fit}

The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
parameter errors and correlations. It interfaces with a Datasets object, which
in turn is connected to a Models object containing the model parameters in its
Parameters object. Models can be unique for a given dataset, or contribute to
multiple datasets and thus provide links, allowing e.g., to do a joint fit to
multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
examples are given in the tutorials.

\todo{Add fit code example...?}

The Fit class provides a uniform interface to multiple fitting backends:
“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
and errors are computed only for the fitting with MINUIT. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported fitting backends, including for example MCMC solutions.
\footnote{a prototype is available in gammapy-recipes,
	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
}

\subsection{gammapy.estimators}
\label{ssec:gammapy-estimators}
By fitting parametric models to the data, the total integrated
flux and overall temporal, spectral and morphological shape of the
\gammaray emission can be constrained. In many cases it useful
to make a more detailed follow-up analysis by measuring the
flux in smaller spectral, temporal or spatial bins. This
possibly reveals more detailed emission features, which
are relevant for studying correlation with counterpart emissions.

The \code{gammapy.estimators} sub-module features methods to compute flux
points, light curves, flux maps, flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \code{MapDataset} are grouped into
larger bins. The norm of the best fit "reference" spectral
model is fitted ("scaled") in the  restricted data range only.

The base class of all algorithms is the \code{Estimator}  class.

Signifiance is estimated based on hypothesis
testing against the background only model. This allows
to assign a significance to the given flux bin.
In addition to the best fit flux norm all estimators compute
quantities corresponding to this flux. This includes
the predicted number of total, signal and background
counts per flux bin. The total fit statistics
of the best fit model, the fit statistics of the
null hypothesis and the difference between both,
the so-called TS value.
From the TS value the significance of the
significance of the measured signal and associated flux
can be derived.

Optionally it can also compute more advanced quantities
such as assymmetric flux errors, flux upper limits
and one dimensional profiles of the fit statistic,
which show how the likelihood functions varies with
the flux norm parameter around the fit minimum.
This information is useful for inspecting the quality
of the fit, where assumptoticcally a parabolic
shape of the profile is expected at the best fit
values (\todo{Reference to modeling / fitting section?}).

The result of the flux point estimation are either stored in a
\code{FluxMaps} or \code{FluxPoints} object. Both objects
are based on an internal representation of the flux which is
independent of the SED type. The flux is represented by a
the reference spectral model and an array of
normalisation values given in energy, time and spatial bins,
which factorise the deviation of the flux in the given
bin form the reference spectral model. This allows
user to conveniently transform between different
SED types. Table~\ref{tab:sed_types} shows an
overview and definitions of the supported SED types.
The actual flux values for each SED type are obtained
by mutiplication of the norm with the  reference flux.

\begin{table*}
    \begin{center}
        \begin{tabular}{lll}
         \hline
         Type & Description & Unit Equivalency \\
         \hline
         dnde & Differential flux at a given energy & $\mathrm{TeV^{-1}~cm^{2}~s^{-1}}$ \\
         e2dnde & Differential flux at a given energy  & $\mathrm{TeV~cm^{2}~s^{-1}}$ \\
         flux & Integrated flux in agiven energy range & $\mathrm{cm^{2}~s^{-1}}$ \\
         eflux & Integrated energy flux in agiven energy range & $\mathrm{erg~cm^{2}~s^{-1}}$\\
         \hline
        \end{tabular}
    \end{center}
    \label{tab:sed_types}
    \caption{Definition of the different SED types supported in \gammapy.}
\end{table*}

Both result objects support the possibility to serialise
the data into multiple formats. This includes the
\gadf SED (reference?) format, FITS based ND sky-maps
and formats compatible with Astropy's \code{Table} and
\code{BinnedTimeSeries} data structures. This allows
users to directly further analyse the results, e.g.
standard algorithms for time analysis such as
computing Lomb-Scargle periodograms or Bayesian
blocks for time series. So far \gammapy does not
support "unfolding" of \gammaray spectra.
Methods for this will be implemented in future version of \gammapy.

Code example ~\ref{fig*:minted:gp_estimators} shows how to use
the \code{TSMapEstimator} objects with a given input \code{MapDataset}.
In addition to the model it allows to specify the energy
bins of the resulting flux and TS maps.

\begin{figure}
	\import{code-examples/generated/}{gp_estimators}
	\caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
        a flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
        and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
        of the flux error and and flux upper limit maps respectively.
    }
    \label{fig*:minted:gp_estimators}
\end{figure}

\subsection{gammapy.analysis}
\label{ssec:gammapy-analysis}
The \code{gammapy.analysis} sub-module provides a  high-level interface for the most
common use cases identified in \gammaray analyses. The classes and methods
included can be used in Python scripts, notebooks or as commands within IPython
sessions. The high-level user interface can also be used to automatise
workflows driven by parameters declared in a configuration file in YAML format.
This way a full analysis can be executed via a single command line taking the
configuration file as input.

The \code{Analysis} class has the responsibility of orchestrating of the workflow
defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
the \code{AnalysisStep} classes that defines the common use cases identified. These
steps include the following: observations selection from the DataStore,  data
reduction, excess map computation, model fitting, flux-points estimation, and
light-curves production. The structure of the \code{Analysis} class allows to define
custom AnalysisStep, so ones could design and configure arbitrarily complex
wokflows. \todo{the latter is not true for v1.0..., include example YAML file?}

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
The \code{gammapy.stats} subpackage contains the fit statistics and associated
statistical estimators that are commonly used in \gammaray astronomy. In
general, \gammaray observations count Poisson-distributed events at various sky
positions, and contain both signal and background events. Estimation of the
number of signal events is done through likelihood maximization. In \gammapy,
the fit statistics are Poisson log-likelihood functions normalized like
chi-squares, i.e., they follow the expression $2 \time\cdot \log{\mathcal{L}}$,
where $\mathcal{L}$ is
the likelihood function used. The statistic function used when the expected
number of background events is known is the \emph{Cash} statistic
~\citep{Cash}. It is used by datasets using background templates such as the
\code{MapDataset}. When the number of background events is unknown and an off
measurement where only background events are expected is used, the statistic
function is WStat. It is a profile log-likelihood statistic where background
counts are marginalized parameters. It is used by datasets containing off
counts measurements such as the \code{SpectrumDatasetOnOff}, used for classical
spectral analysis.

To perform simple statistical estimations on counts measurements,
CountsStatistic classes encapsulate the aforementioned statistic functions to
measure excess counts and estimate the associated statistical significance,
errors and upper limits. They perform maximum likelihood ratio tests to
estimate significance (the square root of the statistic difference) and compute
likelihood profiles to measure errors and upper limits. The code example
\ref{codeexample:stats} shows how to compute the Li \& Ma
significance~\citep{LiMa} of a set of measurements.

\begin{figure}
	\import{code-examples/generated/}{gp_stats}
	\caption{
        Using \code{gammapy.stats} to compute statistical quantities
        such as excess, signficance and assymetric errors
        from counts based data. The data is passed on initialisation
        of the \code{WStatCountsStatistic} class. The quantities
        are the computed on access of the corresponding class
        attributes such as \code{stat.n\_sig} and \code{stat.sqrt\_ts}.
    }
	\label{codeexample:stats} \end{figure}

\subsection{gammapy.visualization}
\label{ssec:gammapy-visualization}
The \code{gammapy.visualization} sub-package contains helper functions
for plotting and visualizing analysis results and \gammapy~data structures.
This includes for example the visualization of reflected background regions across
multiple observations or plotting large parameter correlation matrices of
\gammapy models. It also includes a helper class to split
wide field Galactic survey images across multiple panels to fit a standard
paper size.

The sub-package also provides matplotlib implementations of specific
colormaps for false color image representation. Those colormaps have
been used historically larger collaborations in the very high energy
domain (such as \milagro or \hess) as "trademark" colormaps.
While we explicitly discourage the use of those colormaps for publication
of new results, because they do not follow modern visualization
standards, such as linear brightness gradients and accessibility
for visually impaired people, we still consider the colormaps
useful for reproducibility of past results.

\subsection{gammapy.astro}
\label{ssec:gammapy-astro}
The \code{gammapy.astro} sub-package contains utility functions for studying physical
scenarios in high energy astrophysics. The \code{gammapy.astro.darkmatter} module
computes the so  called J-factors and the associated \gammaray spectra expected
from annihilation of dark matter in different channels according to the recipe
described in \cite{2011JCAP...03..051C}.

In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modeling
galactic \gammaray sources according to simplified physical models, eg: SNR evolution
models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of PWN during the
free expansion phase \citep{2006ARA&A..44...17G} or computation
of physical parameters in a pulsar assumed to be a simple dipole.

In the \code{gammapy.astro.population} sub-module there are dedicated tools
for simulating synthetic populations based on physical models derived from
observational or theoretical considerations for different classes of Galactic
VHE \gammaray emitters: PWNe, SNRs \cite{1998ApJ...504..761C},
pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y}
and \gammaray binaries.

While the present list of use cases is rather preliminary, this can be enriched
with time with by users and/or developers according to future needs.

\subsection{gammapy.catalog}
\label{ssec:gammapy-catalog}
Comprehensive source catalogs are increasingly being provided by many high
energy astrophysics experiments. The \code{gammapy.catalog} sub-packages
provides a convenient access to the most important \gammaray catalogs.
Catalogs are represented by the \code{SourceCatalog} object, which
contains the actual catalog as an Astropy \code{Table} object.
Objects in the catalog can be accesed by row index, name of the
object or any association or alias name listed in the catalog.

Sources are represented in \gammapy by the \code{SourceCatalogObject}
class, which has the responsibility to translate the information
contained in the catalog to other \gammapy objects. This includes
the spatial and spectral model of the source, flux points and
light curves (if available) for individual objects. This
module works independently from the rest of the package, and the required
catalogs are supplied in \code{GAMMAPY\_DATA} repository.
The overview of currenly supported catalogs, the corresponding
\gammapy classes and references are shown in Table~\ref{tab:catalogs}.
Newly released relevant catalogs will be added in future.

\begin{table*}[ht!]
    \begin{center}
        \begin{tabular}{llll}
         \hline
         Class Name & Shortcut & Description & Reference\\
         \hline
         \code{SourceCatalog3FGL} & \code{"3fgl"} & 3\textsuperscript{rd} catalog of \fermi sources & \cite{3FGL} \\
         \code{SourceCatalog4FGL} & \code{"4fgl"} & 4\textsuperscript{th} catalog of \fermi  sources & \cite{4FGL} \\
         \code{SourceCatalog2FHL} & \code{"2fhl"} & 2\textsuperscript{nd} catalog high energy \fermi  sources & \cite{2FHL} \\
         \code{SourceCatalog3FHL} & \code{"3fhl"} & 3\textsuperscript{rd} catalog high energy \fermi  sources & \cite{3FHL} \\
         \code{SourceCatalog2HWC} & \code{"2hwc"} & 2\textsuperscript{nd} catalog of \hawc sources & \cite{2HWC} \\
         \code{SourceCatalog3HWC} & \code{"3hwc"} & 3\textsuperscript{rd} catalog of \hawc sources & \cite{3HWC} \\
         \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \citep{gamma-cat} \\
         \hline
         \end{tabular}
    \end{center}
    \label{tab:catalogs}
    \caption{Overview of supported catalogs in \code{gammapy.catalog}.}
\end{table*}

\begin{figure}
	\import{code-examples/generated/}{gp_catalogs}
	\caption{Using \code{gammapy.catalogs} to access the underlying model, flux points and
		light-curve from the \fermi 4FGL catalog for the blazar PKS 2155-304}
	\label{codeexample:data}
\end{figure}

%\subsection{gammapy.utils}
\label{ssec:gammapy-utils}
Utility functions...

\section{Applications}
\label{sec:applications}

\gammapy can be used for a variety of science cases by different IACT
experiments. (Refer to publications) In this section, we show a non-exhaustive
list of some typical analysis that can be performed. In general from the
\gammapy side there is not limitation on which kind of analysis can be done
with which instrument, however in practice it is limited by the availability of
public data.

\subsection{1D Analysis}
\label{ssec:1d-analysis}
One of the most common analysis cases in \gammaray astronomy is measuring the
spectrum of a source in a given region defined on the sky, in conventional
astronomy also called aperture photometry. The spectrum is typically measured
in two steps: first a parametric spectral model is fitted to the data and
secondly flux points are computed in a pre-defined set of energy bins. The
result of such an analysis performed on three simulated CTA observations is
shown in Fig.~\ref{fig:cta_galactic_center}. In this case the spectrum was
measured in a circular aperture centered on the Galactic Center, in
\gammaray~astronomy often called "on region". For such analysis the users first
chooses a region of interest and energy binning, both defined by a
\code{RegionGeom}. In a second step the events and instrument response are binned
into maps of this geometry, by the \code{SpectrumDatasetMaker}. All the data and
reduced instrument response are bundled into a \code{SpectrumDataset}. To estimate
the expected background in the on region a "reflected regions" background
method was used~\cite{Berge07}, represented in \gammapy by the
\code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
illustrated for all three observations on top of the map of counts. After
reduction of the data it was modelled using a forward-folding method and a
power-law spectral shape, using the \code{PowerLawSpectralModel} and \code{Fit} class.
Based on this best fit model the final flux points and corresponding
log-likelihood profiles are computed using the \code{FluxPointsEstimator}.

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
	\caption{
		Example spectral analysis of the Galactic Center for three simulated CTA
		observations. The left image shows the maps of counts with the measurement
		region and background regions overlaid in different colors. The right image
		shows the resulting spectral points and their corresponding log-likelihood
		profiles.} \label{fig:cta_galactic_center} \end{figure*}

\subsection{3D Analysis}
\label{ssec:3d-analysis}
The 1D analysis approach is a powerful tool to measure the spectrum of an
isolated source. However, more complicated situations require a more careful
treatment. In a field of view containing several overlapping sources, the 1D
approach cannot disentangle the contribution of each source to the total flux in
the selected region. Sources with extended or complex morphology can result in
the measured flux being underestimated, and heavily dependent on the choice of
extraction region. Additionally, the 1D approach neglects the energy-dependence
of the PSF.

For such situations a more complex approach is needed, the so-called 3D
analysis. The three relevant dimensions are the two spatial angular coordinates
and an energy axis. In this framework, a combined spatial and spectral model
(that is, a \code{SkyModel}, see Section~\ref{ssec:gammapy-modeling}) is fitted to the
sky-maps that were previously derived from the data and bundled into a
\code{MapDataset} (see Sections~\ref{ssec:gammapy-makers} and~\ref{ssec:gammapy-datasets}).

A thorough description of the 3D analysis approach and multiple examples that
use \gammapy can be found in~\cite{Mohrmann2019}. Here we present a short
example to highlight some of its advantages.

Starting from the \irfs corresponding to the same three simulated \cta
observations used in Section~\ref{ssec:1d-analysis}, we can create a \code{MapDataset}
via the \code{MapDatasetMaker}. However, we will not use the simulated event lists
provided by \cta but instead, use the method MapDataset.fake() to simulate
measured counts from the combination of several SkyModel instances. In this
way, a DL4 dataset can directly be simulated. In particular we simulate:

\begin{enumerate}
    \item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law
	      spectral shape.
    \item An extended source with Gaussian morphology located at (l=0.4\textdegree,
	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log-parabola spectral
	      shape.
    \item A large shell-like structure centered around (l=0.06\textdegree,
	      b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree
	      respectively and a power-law spectral shape.
\end{enumerate}

The position and sizes of the sources
have been selected so that their contributions overlap. This can be clearly
seen in the significance map shown in the left panel of
Figure~\ref{fig:cube_analysis}. This map was produced with the
\code{ExcessMapEstimator} (see Section~\ref{ssec:gammapy-estimators}) with a
correlation radius of 0.1\textdegree.

We can now fit the same model shapes to the simulated data and retrieve the
best-fit parameters. To check the model agreement, we compute the residual
significance map after removing the contribution from each model. This is done
again via the \code{ExcessMapEstimator}. As can be seen in the middle panel of
Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$,
meaning that the models describe the data sufficiently well.

As the example above shows, the 3D analysis allows to characterize the
morphology of the emission and fit it together with the spectral properties of
the source.  Among the advantages that this provides is the ability to
disentangle the contribution from overlapping sources to the same spatial
region. To highlight this, we define a circular RegionGeom of radius
0.5\textdegree~ centered around the position of the point source, which is drawn
in the left panel of Figure~\ref{fig:cube_analysis}. We can now compare the
measured excess counts integrated in that region to the expected relative
contribution from each of the three source models. The result can be seen in the left
panel of Figure~\ref{fig:cube_analysis}.

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cube_analysis.pdf}
	\caption{Example 3D analysis for simulated sources using the \cta \irfs. The
		left image shows a significance map where the three simulated sources can be
		seen. The middle figure shows another significance map, but this time after
		subtracting the best-fit model for each of the sources, which are displayed in
		black. The right figure shows the contribution of each source model to the
		circular region of radius 0.5\textdegree drawn in the left image, together with
		the excess counts inside that region. } \label{fig:cube_analysis}
\end{figure*}

Note that all the models fitted also have a spectral component, from which flux
points can be derived in a similar way as described in~\ref{ssec:1d-analysis}.
%\end{figure*}%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?%

\subsection{Temporal Analysis}
\label{ssec:temporal-analysis}
A common use case in most astrophysical scenarios is to study the temporal
variability of the source. The most basic way to do this is to construct a
lightcurve, i.e., the flux of the source in each given time bin. In \gammapy, this
is done by using the \code{LightCurveEstimator} which fits the normalisation of the
source in each energy band per observation, keeping other parameters constant.
For custom time binning, an observation needs to be split into finer time bins using
the \code{Observation.select\_time} method. Figure~\ref{fig:hess_lightcurve_pks}
shows the lightcurve of the blazar PKS~2155-304 in different energy bands as
observed by the H.E.S.S. telescope during an exceptional flare on the night of
July 29 - 30, 2006~\cite{2009A&A...502..749A}. The data is available publicly
as a part of the HESS-DL3-DR1~\cite{HESS-DL3-DR1}, and shipped with
\verb"GAMMAPY_DATA". Each observation is first split into 10 min smaller
observations, and spectra extracted for each of these within a 0.11 deg radius
around the source. A \code{PowerLawSpectralModel} is fit to all the datasets, leading
to a reconstructed index of $3.54 \pm 0.02$. With this assumed spectral model
the \code{LightCurveEstimator} runs directly for two energy bands, 0.5 - 1.5
TeV, and 1.5 - 20 TeV, respectively.
%
\begin{figure*}[t]
    \sidecaption
	\includegraphics[width=0.6666\textwidth]{figures/hess_lightcurve_pks.pdf}
	\caption{
        Binned light-curves in two different energy bands differ for the source
        PKS~2155-304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV)
        as observed by the H.E.S.S. telescopes in 2006. The colored markers
        show the flux points in the different energy bands. The horizontal
        error illustrates the width of the time bin of 10~min. The vertical
        error bars show the associated assymetrical flux errors. The marker
        is set to the center of the time bin.
    }
    \label{fig:hess_lightcurve_pks}
\end{figure*}
%
The obtained flux points can be analytically modelled using the available, or
user-implemented temporal models. Alternatively, instead of  extracting a
lightcurve, it is also possible to directly fit temporal models to the reduced
datasets. By associating an appropriate \code{SkyModel}, consisting of both temporal
and spectral components, or using custom temporal models with spectroscopic
variability, to each dataset, a joint fitting across the datasets will directly
return the best fit temporal and spectral parameters.

\subsection{Multi Instrument Analysis}
\label{ssec:multi-instrument-analysis}
%
\begin{figure*}[t]
	\sidecaption
	\includegraphics[width=0.666\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{
        A multi-instrument spectral energy distribution (SED) and combined model fit
        of the Crab Nebula. The  colored markers show the flux points computed from
        the data of the different listed instruments. The horizontal error bar
        illustrates the width of the chosen energy band $E_{Min}, E_{Max}$.
        The marker is set to the log-center energy of the band, which is
        defined by $\sqrt{E_{Min} \cdot E_{Max}}$. The vertical errors bars
        indicate the $1\sigma$ error of the measurement. The downward
        facing arrows indicate the value of $2\sigma$ upper flux limits
        for the given energy range. The red solid line shows the best
        fit model and transparent error band.
    }
	\label{fig:multi_instrument_analysis}
\end{figure*}
%
%% should we mention the joint-crab here or in the intro, where we talk about
%% DL3, multi-instrument analysis and so forth...
%% cite Laura's DL3 HAWC paper with the updated version of the joint-crab spectrum?
In this multi-instrument analysis example we showcase the capabilities of
\gammapy to perform a simultaneous likelihood fit incorporating data from
different instruments and at different levels of reduction. We estimate the
spectrum of the Crab Nebula combining data from \fermi, \magic and \hawc. Maps
of \fermi data are prepared selecting a region of $X^{\circ}$ around the
position of the Crab Nebula applying the same selection criteria of the 3FHL
catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$,
~\citealt{3FHL}).  The \magic data are two%% shall we explain exactly which type of Map is created?
observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
the performance of the upgraded stereo system~\citep{magic_performance} and
already included in~\cite{joint_crab}. The observations were taken at small
zenith angles ($<30^{\circ}$) in wobble mode~\citep{fomin_1994}, with the
source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
range spans $80\,{\rm GeV} -- 20\,{\rm TeV}$. They are reduced to ON/OFF
dataset before being fitted. \hawc flux points data are estimated
in~\cite{hawc_crab_2019} with $2.5\,{\rm years}$ of data and span an energy
range $300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.

\gammapy automatically generates a likelihood including three different types
of terms. Two poissonian likelihoods: one for the \fermi map and one for the
ON/OFF counts, and a $\chi^2$ accounting for the flux points. For \fermi, a a
three-dimensional forward folding of the sky model with the IRF is performed,
in order to compute the predicted counts in each sky-coordinate and energy bin.
For \magic, a one-dimensional forward folding of the spectral model with the
IRF is performed to predict the counts in each estimated energy bin. A log
parabola is fitted to the almost fived decades in energy $10\,{\rm GeV} --
	300\,{\rm TeV}$. %% is the LP formula specified elsewhere?

The result of the joint fit is displayed in
Fig.~\ref{fig:multi_instrument_analysis}. We remark that the objective of this
exercise is illustrative, we display the flexibility of \gammapy in
simultaneously fitting multi-instrument data even at different levels of
reduction, we do not aim to provide a new measurement of the Crab Nebula
spectrum.

%% eventual part for physical modelling with naima

\subsection{Broadband SED Modeling}
\label{ssec:broadband-sed-modeling}
By combining \gammapy with astrophysical modelling codes users can also fit
astrophysical spectral models to \gammaray data. In \gammaray
astronomy what typically observes two radiation production
mechanisms., the so called hadronic and leptonic scenarios.
There are mutiple Python packages that are able to model
the \gammaray emission, given a physical scenario. Among those
packages are  \cite{agnpy}, \cite{naima}, \cite{jetset} or \cite{gamera}.
Tyically those emission models predict broadband emission from
radio waves up to the very high energy \gammaray range.
By relying on the multiple dataset types in \gammapy those
data can be combined to constrain such a broadband emission model.
\gammapy provides a built-in \code{NaimaSpectralModel} which allows
users to wrap a given astrophysical emission model from the
Naima package and fit it directly to \gammaray data.

\subsection{Surveys, Catalogs, and Population Studies}
\label{ssec:surveys-catalogs-and-population-studies}

Sky surveys have a large potential for new source detections, and new phenomena
discovery. They also offer less selection bias to perform source population
studies over a large set of coherently detected and modelled objects. Early
versions of \gammapy were developed in parallel of the preparation of
the \hess Galactic plane survey catalog~\citep[HGPS][]{2018A&A...612A...1H} and
the associated PWN and SNR populations studies~\citep{2018A&A...612A...2H,
	2018A&A...612A...3H}.

The increase in sensitivity  and resolution provided by new generation of
instruments scale up the number of sources detectable and the complexity of the
models needed to represent them accurately. As an example If we compare the
results of the HGPS to the expectations from the \cta Galactic Plane survey
simulations we jump from 78 sources detected by \hess to about 500 detectable by
CTA~\citep{2021arXiv210903729R}.

Studies performed on simulations not only offer a first glimpse on what could
be the sky seen by CTA (according to our current knowledge on source
populations), but also give us the opportunity to test the software on complex
use cases\footnote{Note that the CTA-GPS simulations were performed with the
	\textit{ctools} package~\citep{2016A&A...593A...1K} and analysed with both
	\textit{ctools} and \textit{gammapy} packages in order to cross-validate
	them.}. So we can  improve performances, optimize our analyses strategies, and
identify the needs in term of parallelisation to process the large datasets
provided by the surveys.

In short the production of catalogs from \gammaray surveys can be divided in
four main steps : data-reduction; object detection; model fitting and model
selection; associations and classification. The \iacts data-reduction step is
done in the same way than described in the previous sections but scale up to
few thousand of observations. The object detection step consists a minima in
finding local maxima in the significance, or TS maps,  given by the
\code{ExcessMapEstimator}, or \code{TSMapEstimator}, respectively.  Further refinements can
include for example  filtering and detection on these maps with techniques from
scikit-image package~\citep{scikit-image}, and outlier detection from
scikit-learn package~\citep{scikit-learn}. Tests on simulations shown that it
reduces the spurious detections at this stage and then speed up the next step
as less objects will have to be fitted simultaneously. During the modelling
step each object is alternatively fitted with different models in order to
determine their optimal parameters, and the best-candidate model. The
subpackage \code{gammapy.modeling.models} offers a large variety of choice, and the
possibility to add custom models.  Several spatial models (point-source, disk,
gaussian...), and spectral models (power-law, log-parabola...) may be tested
for each object, so the complexity of the problem increases rapidly in regions
crowded with multiple extended sources. Finally an object is discarded if its
best-fit model is not significantly preferred over the null hypothesis (no
source) comparing the difference in log-Likelihood between these two
hypotheses. For the association and classification step, that is tightly
connected to the population studies, we can a minima compare the fitted models
to the set of gammapy-ray catalogs available in gammapy.catalog. However
further multi-wavelength cross-matches are usually required to characterize the
sources.

\section{\gammapy Project} \label{sec:gammapy-project}

In this section, we provide an overview of the organization of the \gammapy
project. We briefly describe the main roles and responsibilities within the
team, as well as the technical infrastructure designed to facilitate the
development and maintenance of \gammapy as a high quality software. We use
common tools and services for software development of Python open-source
projects, code review, testing, package distribution and user support, with a
customized solution for a versioned thoroughly tested documentation in the form
of user-friendly playable tutorials. This section concludes with an outlook on
the roadmap for future directions.

\subsection{Organizational Structure}
\label{ssec:organizational-structure}

\gammapy is a well-organised international open-source project with a broad
developer base and the presence of commitments from strong groups and
institutes in the very high-energies astrophysics
domain\footnote{\url{https://gammapy.org/team.html}}. The main development
roadmaps are discussed and validated by a Coordination Committee, composed of
representatives of the main contributing laboratories. This committee is
chaired by a Project Manager and his deputy while two Lead Developers manage
the development strategy and organise technical activities. Because of this
institutionally driven characteristic, the permanent staff and commitment of
supporting institutes ensure the continuity of the executive teams. A core team
of developers from the contributing laboratories is in charge of the regular
development, which benefits from punctual contributions of the community at
large.

\subsection{Technical Infrastructure}
\label{ssec:technical-infrastructure}

\gammapy follows an open-source and open-contribution development model based on
the cloud repository service \github. A \github organization
\textit{gammapy}\footnote{\url{https://\github.com/gammapy}} hosts different
repositories related with the project. The software codebase may be found in
the \textit{gammapy} repository (see Table~\ref{table:codestats:data} and
Figure~\ref{fig:codestats:lang} for code lines statistics). We make extensive
use of the pull request system to discuss and review code contributions.

\begin{table}
	\import{tables/generated/}{codestats}
	\caption{
        Overview of used programming languages and distribution of code across the different file
        categories in the \gammapy code base. The most right column list the total number of lines
        in a file. The \textit{comment} column lists the number of comments in the files
        (including method and class docstrings), the \textit{blank} column lists the
        number of blank lines in the file. The uppermost rows distinguish between
        code that implements actual functionality and code the implements tests.
        All documentataion in \gammapy is implemented as dosctrings, \text{reStructuredText} (RST)
        files or notebooks.
    }
	\label{table:codestats:data}
\end{table}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.5\textwidth]{figures/codestats.pdf}
	\caption{
		Overview of used programming languages and distribution of code across the different file
        categories in the \gammapy code base.
    } \label{fig:codestats:lang}
\end{figure}

Several automated tasks are set as \github
actions\footnote{\url{https://\github.com/features/actions}}, blocking the
processes and alerting developers when fails occur. This is the case of the
content integration workflow, which monitors the execution of the test coverage
suite\footnote{\url{https://pytest.org}} using datasets from the
\textit{gammapy-data} repository. Tests scan not only the codebase but also the
code snippets present in docstrings of the scripts and in the RST documentation
files, as well as in the tutorials provided in the form of Jupyter notebooks.

Other automated tasks, executing in the \textit{gammapy-benchmarks} repository,
are responsible for numerical validation tests and benchmarks monitoring. Also
tasks related with the release process are partially automated, and every
contribution to the codebase repository triggers the documentation building and
publishing workflow within the \textit{gammapy-docs} repository (see Sec.
~\ref{ssec:software-distribution} and Sec. ~\ref{ssec:documentation}).

This small ecosystem of interconnected up-to-date repositories, automated tasks
and alerts, is just a part of a bigger set of \github repositories, where most
of them are related with the project but not necessary for the development of
the software (i.e., project webpage, complementary high-energy astrophysics
object catalogs, coding sprints and weekly developer calls minutes,
contributions to conferences, other digital assets, etc.) Finally, third-party
services for code quality metrics are also set and may be found as status
shields in the codebase repository.

\subsection{Software Distribution}
\label{ssec:software-distribution}

\gammapy is distributed for Linux, Windows and Mac environments, and installed
in the usual way for Python packages. Each stable release is uploaded to the
Python package index\footnote{\url{https://pypi.org}} and as a binary package
to the \textit{conda-forge} and \textit{astropy} Anaconda
repository\footnote{\url{https://anaconda.org/anaconda/repo}} channels. At this
time, \gammapy is also available as a Debian Linux
package\footnote{\url{https://packages.debian.org/sid/python3-gammapy}}. We
recommend installing the software using the \textit{conda} installation process
with an environment definition file that we provide, so to work within a
virtual isolated environment with additional useful packages and ensure
reproducibility.

\gammapy is indexed in Astronomy Source Code
Library\footnote{\url{https://ascl.net/1711.014}} and
Zenodo\footnote{\url{https://zenodo.org/record/5721467o}} digital libraries for
software. The Zenodo record is synchronised with the codebase \github repository
so that every release triggers the update of the versioned record. In addition,
the next release of \gammapy will be added to the Open-source scientific
Software and Service Repository\footnote{\url{https://projectescape.eu/ossr}}
and indexed in the European Open Science Cloud
catalog\footnote{\url{https://eosc-portal.eu}}.

\subsection{Documentation and User-support}
\label{ssec:documentation-and-user-support}
\gammapy provides its user community with a tested and versioned up-to-date
on-line
documentation\footnote{\url{https://docs.gammapy.org}}~\citep{2019ASPC..523..357B}
built with Sphinx\footnote{\url{https://www.sphinx-doc.org}} scanning the
codebase Python scripts, as well as a set of RST files and Jupyter notebooks.
The documentation includes a handwritten user guide, a set of executable
tutorials, and a reference to the API automatically extracted from the code and
docstrings. The \gammapy code snippets present in the documentation are tested
in different environments using our continuous integration (CI) workflow based
on \github actions.

The Jupyter notebooks tutorials are stored stripped of their output cells,
which greatly helps in identifying differences in the contribution review.
During the CI these are executed, the output cells parsed and, in case an error
is found in one of the output cells then validation fails. Code formatting of
the input cells is also done, parsing their content and using a particular
syntax to provide links to the API documentation pages. The resulting web
published tutorials also provide links to playground spaces in
myBinder~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
on-line in versioned virtual environments hosted in the myBinder
infrastructure. Users may also play with the tutorials locally in their
laptops. They can download a specific version of the tutorials together with
the associated datasets needed and the specific conda computing environment,
using the \textit{gammapy download} command.

We have also set up a solution for users to share recipes as Jupyter notebooks
that do not fit in the \gammapy core documentation but which may be relevant as
specific use cases. Contributions happen via pull requests to the
\textit{gammapy-recipes} \github repository and merged after a short review. All
notebooks in the repository are tested and published in the \gammapy recipes
webpage\footnote{\url{https://gammapy.\github.io/gammapy-recipes}} automatically
using \github actions.

A growing community of users is gathering around the Slack
messaging\footnote{\url{https://gammapy.slack.com}} and \github
discussions\footnote{\url{https://\github.com/gammapy/gammapy/discussions}}
support forums, providing valuable feedback on the \gammapy functionalities,
interface and documentation. Other communication channels have been set like
mailing lists, a Twitter account\footnote{\url{https://twitter.com/gammapyST}},
regular public coding sprint meetings, hands-on session within collaborations,
weekly development meetings, etc.

\subsection{Proposals for Improving \gammapy}
\label{ssec:pigs}
An important part of \gammapy's development organisation is the support
for "Proposals for improving \gammapy" (PIG). This system is very much
inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}
and Astropy's APE \citep{greenfield_perry_2013} system.
PIG are self-contained documents which outline a set of larger
changes to the \gammapy code base. This includes larger feature additions,
code and package restructuring and maintenance as well as changes related
to the organisational structure of the \gammapy project. PIGs can be proposed
by any person in or outside the project and by multiple authors. They
are presented to the \gammapy developer community in a pull request
on \github and the undergo a review phase in which changes and
improvements to the document are proposed and implemented. Once the PIG
document is in a final state it is presented to the \gammapy
coordination committee, which takes the final decision on the
acceptance or rejection of the proposal. Once accepted, the proposed
change are implemented by \gammapy developers in a series of
individual contributions via pull requests. A list of all proposed
PIG documents is available in the \gammapy online documentation
\footnote{\url{https://docs.gammapy.org/0.20/development/pigs/index.html}}.

A special category of PIGs are long-term "roadmaps". To develop a common
vision for all \gammapy project members on the future of the
project, the main goals regarding planned features, maintenance and
project organisation are written up as an overview and presented to the
\gammapy community for discussion. The review and acceptance process
follows the normal PIG guidelines. Typically roadmaps are written
to outline and agree on a common vision for the next long term
support release of \gammapy.

\subsection{Release Cycle, Versioning, and Long-term Support}
\label{ssec:release-cycle}
With the first long term support (LTS) release v1.0, the \gammapy project
enters a new development phase. The development will change from
quick feature driven development to more stable maintenance
and user support driven developement. After v1.0 we foresee
a developement cycle with major, minor and bugfix releases.
We basically followg the development cycle of the Astropy
project. Thus we expect a major LTS release approximately
every two years, minor releases are planned every 6~months,
while bug-fix releases will happen as needed. While
bug-fix releases will not introduce API breaking changes,
we will work with a deprecation system for minor releases.
API breaking changes will be announced to user by runtime
warnings first and then implemented in the subsequent
minor release. This approach we consider a fair
compromise between the interests of users in a stable
package and the interest of developers to improve
and develop \gammapy in future. The developemnt cycle is described
in more detail in PIG 24 \todo{reference}.

\section{Reproducibility}
\label{sec:reproducibility}
One of the most important goals of the \gammapy project is to support open and
reproducible science results. Thus we decided to write this manuscript
openly and publish the Latex source code along with the associated
Python scripts to create the figures
in \url{https://\github.com/gammapy/gammapy-v1.0-paper}.
This \github repository also documents the history of the creation
and evolution of the manuscript with time. To simplify the reproducibility
of this manuscript including figures and text, we relied on the tool
"showyourwork"~\citep{Luger2021}. This tool coordinates the building
process and software as well as data dependencies such, that the complete
manuscript can be reproduced with a single \code{make} command, after
downloading the source repository. See \todo{reference?} for detailed
instructions. Almost all figures in this manuscript provide a link
to a Python script, that was used to produce it. This means all
example analyses presented in Sec.\ref{sec:applications} link to
actually working Python source code.

\section{Summary and Outlook}
\label{sec:summary-and-outlook}
%
In this manuscript we presented the first LTS version of \gammapy.
\gammapy is a Python package for \gammaray astronomy, which relies on the
scientific Python ecosystem, including Numpy and Scipy and Astropy as
main dependencies. It also holds the status of an Astropy affiliated
package. It supports high-level analysis of astronomical \gammaray
data from intermediate level data formats, such as the FITS based
\gadf. Starting from lists of \gammaray events and corresponding description
of the instrument response users can reduce and project the data
to WCS, HEALPix and region based data structures. The reduced data is bundled
into datasets, which serve as a basis for Poisson maximum likelihood
modelling of the data. For this purpose \gammapy provides a wide selection
of built-in, spectral, spatial and temporal models as well as unified
fitting interface with connection to multiple optimization backends.

With the v1.0 milestone the \gammapy project enters a new development
phase. Future work will not only include maintenance of the v1.0 release,
but also parallel development of new features, improved API and data
model support. While v1.0 provides all the features required for
standard and advanced astronomical \gammaray data analysis,
we already identified specific improvements to be considered in the
roadmap for a future v2.0 release. This includes the support for
scalable analyses via distributed computing. This will allow
users to scale an analysis from a few observations to multiple
hundreds of observations as expected by deep surveys of the CTA
observatory. In addition the high level interface
of \gammapy is planned to be developed into a fully configurable
API design. This will allow users to define arbitrary complex analysis
scenarios as YAML files and even extend their workflows by user defined
analysis steps via a registry system. Another important topic will
be to improve the support of handling meta data for data structures
and provenance information to track the history of the data reduction
process from the DL3 to the highest DL5/DL6 data levels.

Around the core Python package a large diverse community of
users and contributors has developed. With regular developer meetings,
coding sprints and in-person user tutorials at relevant conferences
and collaboration meetings, the community has constantly grown.
So far \gammapy has seen ~80 contributors from ~10 different countries.
With typically ~10 regular contributors at any given time of the
project, the code base has constantly grown its range of features
and improved its code quality. With \gammapy being selected as the base library
for the future science tools for CTA, we expect the community to grow
even further, providing a stable perspective for further usage,
development and maintenance of the project. Besides the future use
by the CTA community \gammapy has already
been used for analysis of data from the \hess and \magic instruments

While \gammapy was mainly developed for the science community around
IACT instruments, the data model and software design is general
enough to be applied to other \gammaray instruments as well.
The use of \gammapy for the analysis of data from the High Altitude
Water Cherenkov Observatory (HAWC) has been successfully
demonstrated by \todo{Olivera et al.}. This makes \gammapy
a viable choice for the base library for the science tools
of the future Southern Widefield Gamma Ray Observatory
(SWGO) and use with data from LHAASO as well. \gammapy
has the potential to further unify the community
of \gammaray astronomers, by sharing common tools and
a common vision of open and reproducible science for the future.

\begin{acknowledgements}

	Mention Christoph here?

	We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
	\texttt{Matplotlib} communities for providing their packages which are
	invaluable to the development of Astropy. We thank the \github team for
	providing us with an excellent free development platform. We also are grateful
	to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
	documentation hosting and testing respectively. Finally, we would like to thank
	all the \gammapy users that have provided feedback and submitted bug reports.

	TODO: copy over stuff from
	\url{http://docs.gammapy.org/en/latest/about.html#thanks}.

	TODO: add the ANR for Luca (and Atreyee in LUPM?)

	J.E. Ruiz acknowledges financial support from the State Agency for Research of
	the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the
	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709)

\end{acknowledgements}

% Back matter
\bibliographystyle{aa}
\bibliography{bib.bib}

\end{document}

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 	%{Gammapy context:}
-	Historically the data as well as analysis software in \gammaray astronomy is
+	Historically the data as well as analysis software in \gammaray astronomy are
 	proprietary to the experiments. With the future Cherenkov Telescope Array
@@
 	data, there is a corresponding need for open high-level analysis software. In
-	this article we present the first major version v1.0 of \gammapy, a
+	this article we present the first major of \gammapy, the Long-term Support (LTS) v1.0, a
 	community-developed open-source Python package for \gammaray astronomy. We

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 	community-developed open-source Python package for \gammaray astronomy. We
-	present its general design and provide an%
+	present its general design and provide an
 	overview of the analysis methods and features it implements. Starting from
@@
 	bundled in datasets and can be serialised, rebinned and stacked. \gammapy
-	supports to model binned data using Poisson%
+	supports to model binned data using Poisson
 	maximum likelihood fitting. It comes with built-in spectral, spatial and

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 together binned data along with associated models and the likelihood, which
-provides an interface to the Fit class (Sec \ref{ssec:gammapy-modeling}) for
+provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
 modeling and fitting purposes. Depending upon the type of analysis and the

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 	profiles per energy bin, light curves as well as flux and signficance maps in
-	energy bins.  We further describe the general%
+	energy bins.  We further describe the general
 	development approach and how \gammapy integrates into ecosystem of other
@@
 across different wavelengths. Datasets also provide functionalities for
-manipulating reduced data, eg: stacking, sub-grouping, plotting, etc. Users can
+manipulating reduced data, e.g. stacking, sub-grouping, plotting. Users can
 also create their customized datasets for implementing modified likelihood

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 to correct them from the data themselves. Several techniques are commonly used
-in \gammaray astronomy such as field-of-view background normalization or
+in TeV \gammaray astronomy such as field-of-view background normalization or
 background measurement in reflected regions, see~\cite{Berge07}.

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 domain is determined by the \code{SafeMaskMaker}. It can be used to limit the
-extent of the field of view used or to limit the energy range to e.g., a domain
+extent of the field of view used or to limit the energy range to, e.g., a domain
 where the energy reconstruction bias is below a given value.
@@
 \begin{itemize}
-	\item \code{SpectralModel}: models to describe spectral shapes of sources
+	\item \code{SpectralModel}: models to describe spectral shapes of sources,
 	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
         Relation of \gammapy to different \gammaray instruments and the data formats.
-        \gammapy provide access to the data stored in GADF format and the
+        \gammapy provides access to the data stored in GADF format and the
         high-level data analysis functionality.}
@@
 The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
-as an open observatory in the domain. Its high level data will be shared publicly after
+as an open observatory in the domain. Its high level data (e.g. the event list) will be shared publicly after
 some proprietary period and the software required to analyze it will be distributed

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 core numerical analysis packages such as \numpy~\citep{numpy} and
-\scipy~\citep{2020SciPy-NMeth}, visualization libraries,e.g. Matplotlib \citep{matplotlib},
+\scipy~\citep{2020SciPy-NMeth}, visualization libraries, e.g. Matplotlib \citep{matplotlib},
 or optimization packages such as Iminuit \citep{iminuit}.
@@
 The \astropy~\citep{astropy} was created in 2012 to build a community-developed
-Python package for astronomical reasearch. Among other things, the it offers functionality for
+Python package for astronomical reasearch. Among other things, it offers functionalities for
 transforming and representing astronomical coordinates, manipulating physical quantities
@@
 	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
-	      light and phase curves
+	      light and phase curves.
 \end{itemize}

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 \item $E_{\rm disp}(E|p_{\rm true}, E_{\rm true})$ is the energy dispersion. It gives the probability to
-  reconstruct the photon at energy $E$ when the true energy is $E_{\rm true}$ and the true position :$p_{\rm true}$.
+  reconstruct the photon at energy $E$ when the true energy is $E_{\rm true}$ and the true position $p_{\rm true}$.
   \gammaray instruments consider the probability density of the migration $\mu=\frac{E}{E_{\rm true}}$,
@@
 
-\gammaray data at the Data Level 3 therefore consists in lists of gamma-like events and their
+\gammaray data at the Data Level 3 (DL3) therefore consists in lists of gamma-like events and their
 corresponding instrument response functions (IRFs). The latter include the aforementioned

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 best-fit model is not significantly preferred over the null hypothesis (no
-source) comparing the difference in log-Likelihood between these two
+source) comparing the difference in log likelihood between these two
 hypotheses. For the association and classification step, that is tightly

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 The handling of DL3 data is performed by classes and methods
-in the gammapy.data  (see \ref{ssec:gammapy-data}) and the gammapy.irf
+in the \code{gammapy.data} (see \ref{ssec:gammapy-data}) and the \code{gammapy.irf}
 (see \ref{ssec:gammapy-irf}) subpackages.

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 The next step of the analysis is the data reduction where all observation events and instrument
-responses are projected onto a user-defined geometry.A typical geometry consists in a spectral representation with a measured
+responses are projected onto a user-defined geometry. A typical geometry consists in a spectral representation with a measured
 energy axis, and in a spatial representation, either a coordinates system  with a projection

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 (for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
-The gammapy.maps subpackage provides general multidimensional geometry objects
+The \code{gammapy.maps} subpackage provides general multidimensional geometry objects
 (Geom) and the associated data structures (Maps), see \ref{ssec:gammapy-maps}.

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

--- 2022-08-08 src/ms-review.tex
@@
 (for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
-The gammapy.maps subpackage provides general multidimensional geometry objects
-(Geom) and the associated data structures (Maps), see \ref{ssec:gammapy-maps}.
+The \code{gammapy.maps} subpackage provides general multidimensional geometry objects
+(Geom) and the associated data structures (Maps) (see \ref{ssec:gammapy-maps}).
 

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 a "safe" data range. These data reduction steps are performed by classes and functions
-implemented in the gammapy.makers subpackage (see \ref{ssec:gammapy-makers}).
+implemented in the \code{gammapy.makers} subpackage (see \ref{ssec:gammapy-makers}).
 
@@
 	\item \code{SpectralModel}: models to describe spectral shapes of sources,
-	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
+	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources,
 	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 To perform simple statistical estimations on counts measurements,
-CountsStatistic classes encapsulate the aforementioned statistic functions to
+\code{CountsStatistic} classes encapsulate the aforementioned statistic functions to
 measure excess counts and estimate the associated statistical significance,

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 
-The \code{SkyModel} object represents factorised model that combine the spectral,
+The \code{SkyModel} object represents factorised model that combines the spectral,
 spatial and temporal model components (by default the spatial and temporal components are

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 sub-packages define data objects to represent DL3 data, such as
-event lists and instrument response functions as well as functionality
+event lists and IRFs as well as functionality
 to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 \paragraph{Energy dispersion:}
-Edisp, in \iact, is generally given in terms of the so
-called migration parameter ($\mu$), which is defined as the ratio between the
+for \iact, it is generally given in terms of the so-called
+ migration parameter ($\mu$), which is defined as the ratio between the
 reconstructed energy and the true energy. This ratio should be as close as one

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 of count rate normalised per steradians and energy at different
-energies and offset-angles or 2) as rate per steradians and energy, as a
+reconstructed energies and offset angles or 2) as rate per steradians and energy, as a
 function of reconstructed energy and detector coordinates (\code{Background3D}).

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 the \code{AnalysisStep} classes that defines the common use cases identified. These
-steps include the following: observations selection from the DataStore,  data
+steps include the following: observations selection with the \code{DataStore},  data
 reduction, excess map computation, model fitting, flux-points estimation, and

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

--- 2022-08-08 src/ms-review.tex
@@
 the \code{AnalysisStep} classes that defines the common use cases identified. These
-steps include the following: observations selection from the DataStore,  data
-reduction, excess map computation, model fitting, flux-points estimation, and
+steps include the following: observations selection with the \code{DataStore},  data
+reduction, excess map computation, model fitting, flux points estimation, and
 light-curves production. The structure of the \code{Analysis} class allows to define

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

--- 2022-08-08 src/ms-review.tex
@@
 the \code{AnalysisStep} classes that defines the common use cases identified. These
-steps include the following: observations selection from the DataStore,  data
-reduction, excess map computation, model fitting, flux-points estimation, and
-light-curves production. The structure of the \code{Analysis} class allows to define
-custom AnalysisStep, so ones could design and configure arbitrarily complex
+steps include the following: observations selection with the \code{DataStore},  data
+reduction, excess map computation, model fitting, flux points estimation, and
+light curves production. The structure of the \code{Analysis} class allows to define
+custom AnalysisStep, so one could design and configure arbitrarily complex
 wokflows. \todo{the latter is not true for v1.0..., include example YAML file?}

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 spatial and temporal model components (by default the spatial and temporal components are
-optional). SkyModel objects represents additive emission components, usually
+optional). \code{SkyModel} objects represents additive emission components, usually
 sources or diffuse emission, although a single source can also be modeled by
@@
 where $\mathcal{L}$ is
-the likelihood function used. The statistic function used when the expected
-number of background events is known is the \emph{Cash} statistic
+the likelihood function used. When the expected number of background events is known, the used statistic function 
+ is the \emph{Cash} statistic
 ~\citep{Cash}. It is used by datasets using background templates such as the

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 custom AnalysisStep, so one could design and configure arbitrarily complex
-wokflows. \todo{the latter is not true for v1.0..., include example YAML file?}
+workflows. \todo{the latter is not true for v1.0..., include example YAML file?}
 
@@
 measurement where only background events are expected is used, the statistic
-function is WStat. It is a profile log-likelihood statistic where background
+function is \emph{WStat}. It is a profile log-likelihood statistic where background
 counts are marginalized parameters. It is used by datasets containing off

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

@@
 The \code{SkyModel} object represents factorised model that combines the spectral,
-spatial and temporal model components (by default the spatial and temporal components are
+spatial and temporal model components (the spatial and temporal components being
 optional). \code{SkyModel} objects represents additive emission components, usually
@@
 processes in jetted Active Galactic Nuclei (AGN) can wrapped into
-\gammapy~\citep[see section3.5 of ][]{2021arXiv211214573N} .
+\gammapy~\citep[see Section 3.5 of ][]{2021arXiv211214573N} .
 
@@
 finding local maxima in the significance, or TS maps,  given by the
-\code{ExcessMapEstimator}, or \code{TSMapEstimator}, respectively.  Further refinements can
+\code{ExcessMapEstimator} (or \code{TSMapEstimator} respectively).  Further refinements can
 include for example  filtering and detection on these maps with techniques from

### 2022-08-08 src/ms-review.tex
Apply suggestions from code review
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>
Co-authored-by: Quentin Remy <quentin.remy@live.fr>

@@
 Ground based instrument use the Earth's atmosphere as a particle detector.
-Very high energy cosmic \gammarays interact in the atmosphere and
+Very high-energy cosmic \gammarays interact in the atmosphere and
 create a large shower of secondary particles that can be observed from the ground.
@@
 %% Context : formats
-In practice, the data-reduction workflow of all \gammaray observatories
+In practice, the data reduction workflow of all \gammaray observatories
 is remarkably similar. After data calibration, shower events are reconstructed and
@@
 mostly attributed to the simple and easy to learn syntax, the ability to act as
-a "glue" language between different programming languages and last but not least
+a 'glue' language between different programming languages and last but not least
 the rich eco-system of packages and its open and supportive community, from
@@
 The \gammapy project started in 2015 with the objective of building a flexible and
-efficient software library for very high energy \gammaray data analysis \citep{gammapy_2015}.
+efficient software library for very high-energy \gammaray data analysis \citep{gammapy_2015}.
 This is possible thanks to the definition of a common data format such as \gadf, and thanks to
@@
 its main concepts. In Section \ref{sec:analysis-workflow-overview}, we present
-the data analysis workflow in very high energy \gammaray astronomy. Then we
+the data analysis workflow in very high-energy \gammaray astronomy. Then we
 show how this workflow is reflected in the structure of the \gammapy package and
@@
 Parts of the data with high associated IRF systematics must also be excluded by defining
-a "safe" data range. These data reduction steps are performed by classes and functions
+a 'safe' data range. These data reduction steps are performed by classes and functions
 implemented in the \code{gammapy.makers} subpackage (see \ref{ssec:gammapy-makers}).
@@
 \gammapy allows user to treat different kinds of PSFs,
-in particular, parametric multi-dimensional gaussians (\code{EnergyDependentMultiGaussPSF})
+in particular, parametric multi-dimensional Gaussians (\code{EnergyDependentMultiGaussPSF})
 or King profile functions (\code{PSFKing})
 one. The \code{EnergyDependentMultiGaussPSF} class is able to handle up to three
-gaussians, defined in terms of amplitudes and sigma given for each true energy
+Gaussians, defined in terms of amplitudes and sigma given for each true energy
 and offset angle bin. Similarly, \code{PSFKing takes} into account the gamma and
 sigma parameters as defined here. The \code{ParametricPSF} allows to create a
-PSF with a representation different from gaussian(s) or King profile(s).
+PSF with a representation different from Gaussian(s) or King profile(s).
 Finally, the user can take advantage from the \code{PSFMap} class, which creates
@@
 reconstructed energy and the true energy. This ratio should be as close as one
-and its dispersion can assume the shape of a gaussian (or even more complex
+and its dispersion can assume the shape of a Gaussian (or even more complex
 distributions). Migration parameter is given at each offset angle and
@@
 dimensions, such as time or energy. It is organized around three types of
-structures: geometries, sky-maps and map axes, which inherit from the base
+structures: geometries, sky maps and map axes, which inherit from the base
 classes \code{Geom}, \code{Map} and \code{MapAxis} respectively.
@@
 radius.
-For local nighbourhood operations, such as convolution \gammapy relies
+For local neighbourhood operations, such as convolution \gammapy relies
 on projecting the HEALPix data to a local tangential WCS grid.
@@
 The end product of the data reduction process described in Section
-\ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps,
+\ref{sec:gammaray-data-analysis} (and in detail in \ref{ssec:gammapy-makers}) are a set of binned counts, background and IRF maps,
 at the DL4 level. The \code{gammapy.datasets} subpackage contains classes to bundle
@@
 user-defined models. For example agnpy models that describe leptonic radiative
-processes in jetted Active Galactic Nuclei (AGN) can wrapped into
+processes in jetted Active Galactic Nuclei (AGN) can be wrapped into
 \gammapy~\citep[see Section 3.5 of ][]{2021arXiv211214573N} .
@@
 The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
-parameter errors and correlations. It interfaces with a Datasets object, which
-in turn is connected to a Models object containing the model parameters in its
-Parameters object. Models can be unique for a given dataset, or contribute to
+parameter errors and correlations. It interfaces with a \code{Datasets} object, which
+in turn is connected to a \code{Models} object containing the model parameters in its
+\code{Parameters} object. Models can be unique for a given dataset, or contribute to
 multiple datasets and thus provide links, allowing e.g., to do a joint fit to
@@
 flux and overall temporal, spectral and morphological shape of the
-\gammaray emission can be constrained. In many cases it useful
+\gammaray emission can be constrained. In many cases it is useful
 to make a more detailed follow-up analysis by measuring the
@@
 larger bins. The norm of the best fit "reference" spectral
-model is fitted ("scaled") in the  restricted data range only.
+model is fitted (or 'scaled') in the  restricted data range only.
 
@@
 This information is useful for inspecting the quality
-of the fit, where assumptoticcally a parabolic
+of a fit, for which asymptomatically a parabolic
 shape of the profile is expected at the best fit
@@
 are based on an internal representation of the flux which is
-independent of the SED type. The flux is represented by a
+independent of the Spectral Energy Distribution (SED) type. The flux is represented by a
 the reference spectral model and an array of
 normalisation values given in energy, time and spatial bins,
-which factorise the deviation of the flux in the given
-bin form the reference spectral model. This allows
+which factorises the deviation of the flux in a given
+bin from the reference spectral model. This allows
 user to conveniently transform between different
@@
          \hline
-         dnde & Differential flux at a given energy & $\mathrm{TeV^{-1}~cm^{2}~s^{-1}}$ \\
-         e2dnde & Differential flux at a given energy  & $\mathrm{TeV~cm^{2}~s^{-1}}$ \\
-         flux & Integrated flux in agiven energy range & $\mathrm{cm^{2}~s^{-1}}$ \\
-         eflux & Integrated energy flux in agiven energy range & $\mathrm{erg~cm^{2}~s^{-1}}$\\
+         dnde & Differential flux at a given energy & $\mathrm{TeV^{-1}~cm^{-2}~s^{-1}}$ \\
+         e2dnde & Differential flux at a given energy  & $\mathrm{TeV~cm^{-2}~s^{-1}}$ \\
+         flux & Integrated flux in a given energy range & $\mathrm{cm^{-2}~s^{-1}}$ \\
+         eflux & Integrated energy flux in a given energy range & $\mathrm{erg~cm^{-2}~s^{-1}}$\\
          \hline
@@
 blocks for time series. So far \gammapy does not
-support "unfolding" of \gammaray spectra.
-Methods for this will be implemented in future version of \gammapy.
+support 'unfolding' of \gammaray spectra.
+Methods for this will be implemented in a future version of \gammapy.
 
@@
 \label{ssec:gammapy-analysis}
-The \code{gammapy.analysis} sub-module provides a  high-level interface for the most
-common use cases identified in \gammaray analyses. The classes and methods
-included can be used in Python scripts, notebooks or as commands within IPython
-sessions. The high-level user interface can also be used to automatise
+The \code{gammapy.analysis} sub-module provides a high-level interface (HLI) for the most
+common use cases identified in \gammaray analyses. The included classes and methods
+ can be used in Python scripts, notebooks or as commands within IPython
+sessions. The HLI can also be used to automatise
 workflows driven by parameters declared in a configuration file in YAML format.
-This way a full analysis can be executed via a single command line taking the
+This way, a full analysis can be executed via a single command line taking the
 configuration file as input.
@@
 defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
-the \code{AnalysisStep} classes that defines the common use cases identified. These
+the \code{AnalysisStep} classes that define the identified common use cases. These
 steps include the following: observations selection with the \code{DataStore},  data
@@
 
-The sub-package also provides matplotlib implementations of specific
+The sub-package also provides "matplotlib" implementations of specific
 colormaps for false color image representation. Those colormaps have
-been used historically larger collaborations in the very high energy
-domain (such as \milagro or \hess) as "trademark" colormaps.
+been used historically by larger collaborations in the very high-energy
+domain (such as \milagro or \hess) as 'trademark' colormaps.
 While we explicitly discourage the use of those colormaps for publication
@@
 The \code{gammapy.astro} sub-package contains utility functions for studying physical
-scenarios in high energy astrophysics. The \code{gammapy.astro.darkmatter} module
+scenarios in high-energy astrophysics. The \code{gammapy.astro.darkmatter} module
 computes the so called J-factors and the associated \gammaray spectra expected
@@
 In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modeling
-galactic \gammaray sources according to simplified physical models, eg: SNR evolution
-models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of PWN during the
+galactic \gammaray sources according to simplified physical models, e.g. SuperNova Remnant (SNR) evolution
+models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of Pulsar Wind Nebula (PWN) during the
 free expansion phase \citep{2006ARA&A..44...17G} or computation
@@
 observational or theoretical considerations for different classes of Galactic
-VHE \gammaray emitters: PWNe, SNRs \cite{1998ApJ...504..761C},
+very high-energy \gammaray emitters: PWNe, SNRs \cite{1998ApJ...504..761C},
 pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y}
@@
 \label{ssec:gammapy-catalog}
-Comprehensive source catalogs are increasingly being provided by many high
-energy astrophysics experiments. The \code{gammapy.catalog} sub-packages
+Comprehensive source catalogs are increasingly being provided by many high-energy
+ astrophysics experiments. The \code{gammapy.catalog} sub-packages
 provides a convenient access to the most important \gammaray catalogs.
@@
 contained in the catalog to other \gammapy objects. This includes
-the spatial and spectral model of the source, flux points and
-light curves (if available) for individual objects. This
+the spatial and spectral models of the source, flux points and
+light curves (if available) for each individual object. This
 module works independently from the rest of the package, and the required
@@
          \code{SourceCatalog4FGL} & \code{"4fgl"} & 4\textsuperscript{th} catalog of \fermi  sources & \cite{4FGL} \\
-         \code{SourceCatalog2FHL} & \code{"2fhl"} & 2\textsuperscript{nd} catalog high energy \fermi  sources & \cite{2FHL} \\
-         \code{SourceCatalog3FHL} & \code{"3fhl"} & 3\textsuperscript{rd} catalog high energy \fermi  sources & \cite{3FHL} \\
+         \code{SourceCatalog2FHL} & \code{"2fhl"} & 2\textsuperscript{nd} catalog high-energy \fermi  sources & \cite{2FHL} \\
+         \code{SourceCatalog3FHL} & \code{"3fhl"} & 3\textsuperscript{rd} catalog high-energy \fermi  sources & \cite{3FHL} \\
          \code{SourceCatalog2HWC} & \code{"2hwc"} & 2\textsuperscript{nd} catalog of \hawc sources & \cite{2HWC} \\
@@
 chooses a region of interest and energy binning, both defined by a
-\code{RegionGeom}. In a second step the events and instrument response are binned
+\code{RegionGeom}. In a second step the events and the IRFs are binned
 into maps of this geometry, by the \code{SpectrumDatasetMaker}. All the data and
-reduced instrument response are bundled into a \code{SpectrumDataset}. To estimate
-the expected background in the on region a "reflected regions" background
+reduced IRFs are bundled into a \code{SpectrumDataset}. To estimate
+the expected background in the ON region a 'reflected regions' background
 method was used~\cite{Berge07}, represented in \gammapy by the
@@
 reduction of the data it was modelled using a forward-folding method and a
-power-law spectral shape, using the \code{PowerLawSpectralModel} and \code{Fit} class.
+power law spectral shape, using the \code{PowerLawSpectralModel} and \code{Fit} class.
 Based on this best fit model the final flux points and corresponding
@@
 	\caption{
-		Example spectral analysis of the Galactic Center for three simulated CTA
+		Example of 1D spectral analysis of the Galactic Center for three simulated CTA
 		observations. The left image shows the maps of counts with the measurement
@@
 (that is, a \code{SkyModel}, see Section~\ref{ssec:gammapy-modeling}) is fitted to the
-sky-maps that were previously derived from the data and bundled into a
+sky maps that were previously derived from the data reduction step and bundled into a
 \code{MapDataset} (see Sections~\ref{ssec:gammapy-makers} and~\ref{ssec:gammapy-datasets}).
@@
 via the \code{MapDatasetMaker}. However, we will not use the simulated event lists
-provided by \cta but instead, use the method MapDataset.fake() to simulate
-measured counts from the combination of several SkyModel instances. In this
+provided by \cta but instead, use the method \code{MapDataset.fake()} to simulate
+measured counts from the combination of several \code{SkyModel} instances. In this
 way, a DL4 dataset can directly be simulated. In particular we simulate:
@@
 \begin{enumerate}
-    \item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law
+    \item A point source located at (l=0\textdegree, b=0\textdegree) with a power law
 	      spectral shape.
     \item An extended source with Gaussian morphology located at (l=0.4\textdegree,
-	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log-parabola spectral
+	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log parabola spectral
 	      shape.
@@
 	      b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree
-	      respectively and a power-law spectral shape.
+	      respectively and a power law spectral shape.
 \end{enumerate}
@@
 disentangle the contribution from overlapping sources to the same spatial
-region. To highlight this, we define a circular RegionGeom of radius
+region. To highlight this, we define a circular \code{RegionGeom} of radius
 0.5\textdegree~ centered around the position of the point source, which is drawn
@@
 	\includegraphics[width=1.\textwidth]{figures/cube_analysis.pdf}
-	\caption{Example 3D analysis for simulated sources using the \cta \irfs. The
+	\caption{Example of a 3D analysis for simulated sources using the \cta \irfs. The
 		left image shows a significance map where the three simulated sources can be
@@
 A common use case in most astrophysical scenarios is to study the temporal
-variability of the source. The most basic way to do this is to construct a
-lightcurve, i.e., the flux of the source in each given time bin. In \gammapy, this
-is done by using the \code{LightCurveEstimator} which fits the normalisation of the
+variability of a source. The most basic way to do this is to construct a
+light curve, i.e., the flux of a source in each given time bin. In \gammapy, this
+is done by using the \code{LightCurveEstimator} that fits the normalisation of a
 source in each energy band per observation, keeping other parameters constant.
@@
 the \code{Observation.select\_time} method. Figure~\ref{fig:hess_lightcurve_pks}
-shows the lightcurve of the blazar PKS~2155-304 in different energy bands as
-observed by the H.E.S.S. telescope during an exceptional flare on the night of
-July 29 - 30, 2006~\cite{2009A&A...502..749A}. The data is available publicly
+shows the light curve of the blazar PKS~2155-304 in different energy bands as
+observed by the \hess telescope during an exceptional flare on the night of
+July 29 - 30, 2006~\cite{2009A&A...502..749A}. The data are publicly available 
 as a part of the HESS-DL3-DR1~\cite{HESS-DL3-DR1}, and shipped with
 \verb"GAMMAPY_DATA". Each observation is first split into 10 min smaller
-observations, and spectra extracted for each of these within a 0.11 deg radius
+observations, and spectra extracted for each of these within a 0.11\textdegree radius
 around the source. A \code{PowerLawSpectralModel} is fit to all the datasets, leading
-to a reconstructed index of $3.54 \pm 0.02$. With this assumed spectral model
+to a reconstructed index of $3.54 \pm 0.02$. With this adjusted spectral model
 the \code{LightCurveEstimator} runs directly for two energy bands, 0.5 - 1.5
@@
 	\caption{
-        Binned light-curves in two different energy bands differ for the source
+        Binned light curves in two different energy bands for the source
         PKS~2155-304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV)
-        as observed by the H.E.S.S. telescopes in 2006. The colored markers
+        as observed by the \hess telescopes in 2006. The coloured markers
         show the flux points in the different energy bands. The horizontal
@@
 %
-The obtained flux points can be analytically modelled using the available, or
+The obtained flux points can be analytically modelled using the available or
 user-implemented temporal models. Alternatively, instead of  extracting a
-lightcurve, it is also possible to directly fit temporal models to the reduced
+light curve, it is also possible to directly fit temporal models to the reduced
 datasets. By associating an appropriate \code{SkyModel}, consisting of both temporal
 and spectral components, or using custom temporal models with spectroscopic
-variability, to each dataset, a joint fitting across the datasets will directly
+variability, to each dataset, a joint fit across the datasets will directly
 return the best fit temporal and spectral parameters.
 
-\subsection{Multi Instrument Analysis}
+\subsection{Multi-instrument Analysis}
 \label{ssec:multi-instrument-analysis}
@@
         illustrates the width of the chosen energy band $E_{Min}, E_{Max}$.
-        The marker is set to the log-center energy of the band, which is
+        The marker is set to the log-center energy of the band, that is
         defined by $\sqrt{E_{Min} \cdot E_{Max}}$. The vertical errors bars
@@
         for the given energy range. The red solid line shows the best
-        fit model and transparent error band.
+        fit model and the transparent band its $1\sigma$ error range.
     }
@@
 \gammapy automatically generates a likelihood including three different types
-of terms. Two poissonian likelihoods: one for the \fermi map and one for the
-ON/OFF counts, and a $\chi^2$ accounting for the flux points. For \fermi, a a
+of terms, two Poissonian likelihoods for the \fermi map and the
+ON/OFF counts, and a $\chi^2$ accounting for the flux points. For \fermi, a 
 three-dimensional forward folding of the sky model with the IRF is performed,
 in order to compute the predicted counts in each sky-coordinate and energy bin.
-For \magic, a one-dimensional forward folding of the spectral model with the
-IRF is performed to predict the counts in each estimated energy bin. A log
-parabola is fitted to the almost fived decades in energy $10\,{\rm GeV} --
+For \magic, a one-dimensional forward-folding of the spectral model with the
+\irfs is performed to predict the counts in each estimated energy bin. A log
+parabola is fitted to the almost five decades in energy $10\,{\rm GeV} --
 	300\,{\rm TeV}$. %% is the LP formula specified elsewhere?
@@
 Fig.~\ref{fig:multi_instrument_analysis}. We remark that the objective of this
-exercise is illustrative, we display the flexibility of \gammapy in
+exercise is illustrative. We display the flexibility of \gammapy in
 simultaneously fitting multi-instrument data even at different levels of
-reduction, we do not aim to provide a new measurement of the Crab Nebula
+reduction, without aiming to provide a new measurement of the Crab Nebula
 spectrum.
@@
 astrophysical spectral models to \gammaray data. In \gammaray
-astronomy what typically observes two radiation production
-mechanisms., the so called hadronic and leptonic scenarios.
+astronomy one typically observes two radiation production
+mechanisms, the so-called hadronic and leptonic scenarios.
 There are mutiple Python packages that are able to model
@@
 Tyically those emission models predict broadband emission from
-radio waves up to the very high energy \gammaray range.
+radio waves up to the very high-energy \gammaray range.
 By relying on the multiple dataset types in \gammapy those
 data can be combined to constrain such a broadband emission model.
-\gammapy provides a built-in \code{NaimaSpectralModel} which allows
+\gammapy provides a built-in \code{NaimaSpectralModel} that allows
 users to wrap a given astrophysical emission model from the
-Naima package and fit it directly to \gammaray data.
+"naima" package and fit it directly to \gammaray data.
 
@@
 versions of \gammapy were developed in parallel of the preparation of
-the \hess Galactic plane survey catalog~\citep[HGPS][]{2018A&A...612A...1H} and
+the \hess Galactic plane survey catalog~\citep[HGPS, ][]{2018A&A...612A...1H} and
 the associated PWN and SNR populations studies~\citep{2018A&A...612A...2H,
@@
 
-The increase in sensitivity  and resolution provided by new generation of
-instruments scale up the number of sources detectable and the complexity of the
-models needed to represent them accurately. As an example If we compare the
+The increase in sensitivity  and resolution provided by the new generation of
+instruments scales up the number of detectable sources and the complexity of 
+models needed to represent them accurately. As an example, if we compare the
 results of the HGPS to the expectations from the \cta Galactic Plane survey
-simulations we jump from 78 sources detected by \hess to about 500 detectable by
+simulations, we jump from 78 sources detected by \hess to about 500 detectable by
 CTA~\citep{2021arXiv210903729R}.
@@
 In short the production of catalogs from \gammaray surveys can be divided in
-four main steps : data-reduction; object detection; model fitting and model
-selection; associations and classification. The \iacts data-reduction step is
+four main steps : data reduction; object detection; model fitting and model
+selection; associations and classification. The \iacts data reduction step is
 done in the same way than described in the previous sections but scale up to
-few thousand of observations. The object detection step consists a minima in
-finding local maxima in the significance, or TS maps,  given by the
+few thousands of observations. The object detection step consists a minima in
+finding local maxima in the significance (or TS) maps,  given by the
 \code{ExcessMapEstimator} (or \code{TSMapEstimator} respectively).  Further refinements can
@@
 possibility to add custom models.  Several spatial models (point-source, disk,
-gaussian...), and spectral models (power-law, log-parabola...) may be tested
+Gaussian...), and spectral models (power law, log parabola...) may be tested
 for each object, so the complexity of the problem increases rapidly in regions
@@
 connected to the population studies, we can a minima compare the fitted models
-to the set of gammapy-ray catalogs available in gammapy.catalog. However
+to the set of \gammaray catalogs available in \code{gammapy.catalog}. However
 further multi-wavelength cross-matches are usually required to characterize the

### 2022-08-08 src/ms-review.tex
Apply suggestions from code review
Co-authored-by: Quentin Remy <quentin.remy@live.fr>

@@
 of datasets for example to create source catalogs. Estimator classes,
-which are contained in \code{gammapy.estinators} are used to
+which are contained in \code{gammapy.estimators} are used to
 compute higher level science products such as flux and signficance maps,
@@
 Finally, the user can take advantage from the \code{PSFMap} class, which creates
-a multi-dimensional map of the PSF in WCS coordinates. At each position, a PSF
+a multi-dimensional map of the PSF in sky coordinates. At each position, a PSF
 kernel map (\code{PSFKernel}) provides a PSF as a function of the true energy.
@@
 
-Following the factorisation The models objects are grouped
+Following the factorisation the models objects are grouped
 into the following categories:
@@
 the class name.
-
-The spectral models include a special class of normed models, which have a
-dimension-less normalisation. These spectral models feature a norm parameter
-instead of amplitude and are named using the NormSpectralModel suffix. They
+The spectral models include a special class of normed models, named using the NormSpectralModel suffix.
+normalisation. These spectral models feature a dimension-less norm parameter
+instead of a physical amplitude parameter. They
 must be used along with another spectral model, as a multiplicative correction
@@
 \code{Parameters} object. Models can be unique for a given dataset, or contribute to
-multiple datasets and thus provide links, allowing e.g., to do a joint fit to
+multiple datasets, allowing e.g., to do a joint fit to
 multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
@@
 to run a pre-fit with alternative optimization methods. In future we plan to
-extend the supported fitting backends, including for example MCMC solutions.
+extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo.
 \footnote{a prototype is available in gammapy-recipes,
@@
          \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
-         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \citep{gamma-cat} \\
+         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \cite{gamma-cat} \\
          \hline
@@
 %\subsection{gammapy.utils}
-\label{ssec:gammapy-utils}
-Utility functions...
+%\label{ssec:gammapy-utils}
+%Utility functions...
 

### 2022-10-24 src/ms-review.tex
Apply suggestions from code review
Co-authored-by: Quentin Remy <quentin.remy@live.fr>
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 an open development with a broad community of contributors. The relation of \gammapy to the
-different instruments the \gadf data format is illustarted in Figure~\ref{fig:big_picture}.
+different instruments and the \gadf data format is illustrated in Figure~\ref{fig:big_picture}.
 
@@
 developer base and the presence of commitments from strong groups and
-institutes in the very high-energies astrophysics
+institutes in the very high-energy astrophysics
 domain\footnote{\url{https://gammapy.org/team.html}}. The main development

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 published tutorials also provide links to playground spaces in
-myBinder~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
+"myBinder"~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
 on-line in versioned virtual environments hosted in the myBinder

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 While \gammapy was mainly developed for the science community around
-IACT instruments, the data model and software design is general
+IACT instruments, the internal data model and software design are general
 enough to be applied to other \gammaray instruments as well.

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>

@@
 	%{Gammapy context:}
-	Historically the data as well as analysis software in \gammaray astronomy are
+	Historically, the data and the analysis software of \gammaray astronomy experiments are
 	proprietary to the experiments. With the future Cherenkov Telescope Array
 	(CTA), which will be operated as an open \gammaray observatory with public
-	data, there is a corresponding need for open high-level analysis software. In
+	data. This introduces the need to have a high-level analysis software available to the astronomical community. In
 	this article we present the first major of \gammapy, the Long-term Support (LTS) v1.0, a

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 ~\citep{Cash}. It is used by datasets using background templates such as the
-\code{MapDataset}. When the number of background events is unknown and an off
+\code{MapDataset}. When the number of background events is unknown and an OFF
 measurement where only background events are expected is used, the statistic

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
         of the \code{WStatCountsStatistic} class. The quantities
-        are the computed on access of the corresponding class
+        are the computed ON excess of the corresponding class
         attributes such as \code{stat.n\_sig} and \code{stat.sqrt\_ts}.
@@
 include for example  filtering and detection on these maps with techniques from
-scikit-image package~\citep{scikit-image}, and outlier detection from
+the "scikit-image" package~\citep{scikit-image}, and outlier detection from
 scikit-learn package~\citep{scikit-learn}. Tests on simulations shown that it

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 \gammapy provides its user community with a tested and versioned up-to-date
-on-line
+online
 documentation\footnote{\url{https://docs.gammapy.org}}~\citep{2019ASPC..523..357B}

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 of the future Southern Widefield Gamma Ray Observatory
-(SWGO) and use with data from LHAASO as well. \gammapy
+(SWGO) and use with data from Large High Altitude Air Shower Observatory (LHAASO) as well. \gammapy
 has the potential to further unify the community

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>

@@
 	Historically, the data and the analysis software of \gammaray astronomy experiments are
-	proprietary to the experiments. With the future Cherenkov Telescope Array
+	proprietary to the collaborations operating them. The next generation of \gammaray instruments, as the Cherenkov Telescope Array
 	(CTA), which will be operated as an open \gammaray observatory with public

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>

@@
 \label{ssec:broadband-sed-modeling}
-By combining \gammapy with astrophysical modelling codes users can also fit
+By combining \gammapy with astrophysical modelling codes, users can also fit
 astrophysical spectral models to \gammaray data. In \gammaray

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>

@@
 	proprietary to the collaborations operating them. The next generation of \gammaray instruments, as the Cherenkov Telescope Array
-	(CTA), which will be operated as an open \gammaray observatory with public
+	(CTA) will be operated as open observatories, with public
 	data. This introduces the need to have a high-level analysis software available to the astronomical community. In

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 the "scikit-image" package~\citep{scikit-image}, and outlier detection from
-scikit-learn package~\citep{scikit-learn}. Tests on simulations shown that it
+the "scikit-learn" package~\citep{scikit-learn}. Tests on simulations shown that it
 reduces the spurious detections at this stage and then speed up the next step

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>

@@
 in~\cite{hawc_crab_2019} with $2.5\,{\rm years}$ of data and span an energy
-range $300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.
+range $300\,{\rm GeV} - 300\,{\rm TeV}$, and directly read with \gammapy.
 

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>

@@
 \irfs is performed to predict the counts in each estimated energy bin. A log
-parabola is fitted to the almost five decades in energy $10\,{\rm GeV} --
+parabola is fitted to the almost five decades in energy $10\,{\rm GeV} -
 	300\,{\rm TeV}$. %% is the LP formula specified elsewhere?
@@
 users to wrap a given astrophysical emission model from the
-"naima" package and fit it directly to \gammaray data.
+naima package and fit it directly to \gammaray data.
 

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>
Address more comments

@@
 \newcommand{\magic}{MAGIC\xspace}
+\newcommand{\astri}{ASTRI\xspace}
 \newcommand{\iact}{IACT\xspace}
@@
 	event lists and a description of the specific instrument response functions
-	(IRF) stored in open FITS based data formats, \gammapy implements . Thereby it
+	(IRF) stored in open FITS based data formats, \gammapy implements the reduction
+	of the input data and instrument response to binned WCS, HEALPix or region based
+	data structures. Thereby it
 	handles the dependency of the IRFs with time, energy as well as position on the
@@
 	different classes of events or combination of data from multiple instruments.
-	Gammapy also implements methods to estimate flux points, including likelihood
+	Gammapy also implements methods to estimate flux points, likelihood
 	profiles per energy bin, light curves as well as flux and signficance maps in
@@
 instrument. While this model has been very successful so far, it does not
-permit easy combination of data from several instruments and is therefore
-a limitation for interoperability of existing facilities. Especially
-because the different detection techniques have complementary
-properties.
+permit easy combination of data from several instruments and therefore
+limits the interoperability of existing facilities. This lack of
+interoperability currently limits the full explotation of the
+available \gammaray data, especially because the different detection
+techniques have complementary properties in terms of covered energy rage,
+dutu cycle and spatial resolution.
 
@@
 gamma/hadron separation is applied to build lists of \gammaray like events.
-The latter are then used to derive scientific results, such as spectra, sky maps
-or light curves, taking into account the specific instrument response functions (IRF).
-The information in this high data level is independent on
-the data reduction, and eventually of the detection technique. This implies,
+The lists of \gammary events are then used to derive scientific results, such as spectra, sky maps
+or light curves, taking into account the observatory specific instrument response functions (IRF).
+One the data is present in the form of a list of events, the information is independent on
+the data reduction process, and eventually of the detection technique. This implies,
 for example, that data from IACT and particle samplers can be represented
@@
 quantities related to \gammaray sources and the production of high-level products such as spectra,
-lightcurves and catalogs. The methods and tools applied here are more generic and are broadly
+light curves and catalogs. The methods and tools applied here are more generic and are broadly
 shared across the field. They also frequently imply joint analysis of multi-instrument data.
@@
 the class name.
-The spectral models include a special class of normed models, named using the NormSpectralModel suffix.
-normalisation. These spectral models feature a dimension-less norm parameter
-instead of a physical amplitude parameter. They
+The spectral models include a special class of normed models, named using the \code{NormSpectralModel} suffix.
+These spectral models feature a dimension-less norm parameter
+instead of an amplitude parameter with physical units. They
 must be used along with another spectral model, as a multiplicative correction
 factor according to their spectral shape. They can be typically used for
-adjusting template based models, or adding a EBL correction to some analytic
-model. The analytic spatial models are all normalized such as they integrate to
+adjusting template based models, or adding taking into account
+the absorbtion effect on 
+\gammaray spectra caused by the extra-galactic background light (EBL) (\code{EBLAbsorptionNormSpectralModel})
+model. \gammapy supports a variety of EBL absorbtion models, such as
+
+\cite{Franceschini2008}, \cite{Finke2010} and \cite{Dominguez2011}.
+
+The analytic spatial models are all normalized such as they integrate to
 unity over the sky but the template spatial models may not, so in that special
@@
 In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modeling
-galactic \gammaray sources according to simplified physical models, e.g. SuperNova Remnant (SNR) evolution
+galactic \gammaray sources according to simplified physical models, e.g. Supernova Remnant (SNR) evolution
 models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of Pulsar Wind Nebula (PWN) during the
 free expansion phase \citep{2006ARA&A..44...17G} or computation
-of physical parameters in a pulsar assumed to be a simple dipole.
+of physical parameters of a pulsar using a simplified dipole spin-down model.
 
@@
 is done by using the \code{LightCurveEstimator} that fits the normalisation of a
-source in each energy band per observation, keeping other parameters constant.
+source in each time (and optionally energy) band per observation, keeping other parameters constant.
 For custom time binning, an observation needs to be split into finer time bins using
@@
 Tyically those emission models predict broadband emission from
-radio waves up to the very high-energy \gammaray range.
+radio, up to the very high-energy \gammaray range.
 By relying on the multiple dataset types in \gammapy those
@@
 
-The Jupyter notebooks tutorials are stored stripped of their output cells,
-which greatly helps in identifying differences in the contribution review.
-During the CI these are executed, the output cells parsed and, in case an error
-is found in one of the output cells then validation fails. Code formatting of
-the input cells is also done, parsing their content and using a particular
-syntax to provide links to the API documentation pages. The resulting web
-published tutorials also provide links to playground spaces in
+The Jupyter notebooks tutorials are generated using the sphinx-gallery
+package \citep{sphinx-gallery}.
+The resulting web published tutorials also provide links to playground spaces in
 "myBinder"~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
@@
 by the CTA community \gammapy has already
-been used for analysis of data from the \hess and \magic instruments
+been used for analysis of data from the \hess, \magic
+\hawc, \astri and \veritas instruments.
 

### 2022-10-29 src/ms-review.tex
Move gammapy.stats section

@@
 
-\subsection{gammapy.modeling}
-\label{ssec:gammapy-modeling}
-%
-\code{gammapy.modeling} contains all the functionality related to modeling and fitting
-data. This includes spectral, spatial and temporal model classes, as well as
-the fit and parameter API.
-
-\subsubsection{Models}
-\label{sssec:models}
-Source models in \gammapy are four dimensional models which support two
-spatial dimensions $\ell, b$, and energy dimension $E$ as well as
-the time dimension $t$. To simplify the the definition of the
-models, \gammapy uses a factorised representation of the total source
-model:
-
-\begin{equation}
-    f(l, b, E, t) = F(E)  \cdot G(l, b, E) \cdot  H(t, E)
-\end{equation}
-
-Where the spectral model $F$ implicitly carries the total flux
-norm of the model. The spatial model $G$ optionally depends
-on energy and allows to support e.g. energy dependent
-morphology models. The temporal model component $H$
-optionally also supports an energy variable to
-allow for spectral variations of the model with time.
-
-Following the factorisation the models objects are grouped
-into the following categories:
-
-\begin{itemize}
-	\item \code{SpectralModel}: models to describe spectral shapes of sources,
-	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources,
-	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
-	      light and phase curves.
-\end{itemize}
-
-The models follow a naming scheme which contains the category as a suffix to
-the class name.
-The spectral models include a special class of normed models, named using the \code{NormSpectralModel} suffix.
-These spectral models feature a dimension-less norm parameter
-instead of an amplitude parameter with physical units. They
-must be used along with another spectral model, as a multiplicative correction
-factor according to their spectral shape. They can be typically used for
-adjusting template based models, or adding taking into account
-the absorbtion effect on 
-\gammaray spectra caused by the extra-galactic background light (EBL) (\code{EBLAbsorptionNormSpectralModel})
-model. \gammapy supports a variety of EBL absorbtion models, such as
-
-\cite{Franceschini2008}, \cite{Finke2010} and \cite{Dominguez2011}.
-
-The analytic spatial models are all normalized such as they integrate to
-unity over the sky but the template spatial models may not, so in that special
-case they have to be combined with a \code{NormSpectralModel}.
-
-The \code{SkyModel} object represents factorised model that combines the spectral,
-spatial and temporal model components (the spatial and temporal components being
-optional). \code{SkyModel} objects represents additive emission components, usually
-sources or diffuse emission, although a single source can also be modeled by
-multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
-has a \code{Models} class.
-
-The model gallery provides a visual overview of the available models in
-\gammapy. Most of the analytic models  commonly used in \gammaray astronomy are
-built-in. We also offer a wrapper to radiative models implemented in the Naima
-package~\cite{naima}. The modeling framework can be easily extended with
-user-defined models. For example agnpy models that describe leptonic radiative
-processes in jetted Active Galactic Nuclei (AGN) can be wrapped into
-\gammapy~\citep[see Section 3.5 of ][]{2021arXiv211214573N} .
-
-\begin{figure}
-	\import{code-examples/generated/}{gp_models}
-	\caption{Using \code{gammapy.modeling.models} to define a source model with a
-    spectral, spatial and temporal component. For convenience the model
-    parameters can be defined as strings with attached units. The spatial model
-    takes an addtional \code{frame} parameter which allow users to define
-    the coordinate frame of the position of the model.
-    }
-	\label{fig*:minted:gp_models}
-\end{figure}
-
-\subsubsection{Fit}
-\label{sssec:fit}
-
-The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
-parameter errors and correlations. It interfaces with a \code{Datasets} object, which
-in turn is connected to a \code{Models} object containing the model parameters in its
-\code{Parameters} object. Models can be unique for a given dataset, or contribute to
-multiple datasets, allowing e.g., to do a joint fit to
-multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
-examples are given in the tutorials.
-
-\todo{Add fit code example...?}
-
-The Fit class provides a uniform interface to multiple fitting backends:
-“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
-“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
-and errors are computed only for the fitting with MINUIT. However depending on
-the problem other optimizers can better perform, so sometimes it can be useful
-to run a pre-fit with alternative optimization methods. In future we plan to
-extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo.
-\footnote{a prototype is available in gammapy-recipes,
-	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
-}
-
-\subsection{gammapy.estimators}
-\label{ssec:gammapy-estimators}
-By fitting parametric models to the data, the total integrated
-flux and overall temporal, spectral and morphological shape of the
-\gammaray emission can be constrained. In many cases it is useful
-to make a more detailed follow-up analysis by measuring the
-flux in smaller spectral, temporal or spatial bins. This
-possibly reveals more detailed emission features, which
-are relevant for studying correlation with counterpart emissions.
-
-The \code{gammapy.estimators} sub-module features methods to compute flux
-points, light curves, flux maps, flux profiles from data.
-The basic method for all these measurements is equivalent.
-The initial fine bins of \code{MapDataset} are grouped into
-larger bins. The norm of the best fit "reference" spectral
-model is fitted (or 'scaled') in the  restricted data range only.
-
-The base class of all algorithms is the \code{Estimator}  class.
-
-Signifiance is estimated based on hypothesis
-testing against the background only model. This allows
-to assign a significance to the given flux bin.
-In addition to the best fit flux norm all estimators compute
-quantities corresponding to this flux. This includes
-the predicted number of total, signal and background
-counts per flux bin. The total fit statistics
-of the best fit model, the fit statistics of the
-null hypothesis and the difference between both,
-the so-called TS value.
-From the TS value the significance of the
-significance of the measured signal and associated flux
-can be derived.
-
-Optionally it can also compute more advanced quantities
-such as assymmetric flux errors, flux upper limits
-and one dimensional profiles of the fit statistic,
-which show how the likelihood functions varies with
-the flux norm parameter around the fit minimum.
-This information is useful for inspecting the quality
-of a fit, for which asymptomatically a parabolic
-shape of the profile is expected at the best fit
-values (\todo{Reference to modeling / fitting section?}).
-
-The result of the flux point estimation are either stored in a
-\code{FluxMaps} or \code{FluxPoints} object. Both objects
-are based on an internal representation of the flux which is
-independent of the Spectral Energy Distribution (SED) type. The flux is represented by a
-the reference spectral model and an array of
-normalisation values given in energy, time and spatial bins,
-which factorises the deviation of the flux in a given
-bin from the reference spectral model. This allows
-user to conveniently transform between different
-SED types. Table~\ref{tab:sed_types} shows an
-overview and definitions of the supported SED types.
-The actual flux values for each SED type are obtained
-by mutiplication of the norm with the  reference flux.
-
-\begin{table*}
-    \begin{center}
-        \begin{tabular}{lll}
-         \hline
-         Type & Description & Unit Equivalency \\
-         \hline
-         dnde & Differential flux at a given energy & $\mathrm{TeV^{-1}~cm^{-2}~s^{-1}}$ \\
-         e2dnde & Differential flux at a given energy  & $\mathrm{TeV~cm^{-2}~s^{-1}}$ \\
-         flux & Integrated flux in a given energy range & $\mathrm{cm^{-2}~s^{-1}}$ \\
-         eflux & Integrated energy flux in a given energy range & $\mathrm{erg~cm^{-2}~s^{-1}}$\\
-         \hline
-        \end{tabular}
-    \end{center}
-    \label{tab:sed_types}
-    \caption{Definition of the different SED types supported in \gammapy.}
-\end{table*}
-
-Both result objects support the possibility to serialise
-the data into multiple formats. This includes the
-\gadf SED (reference?) format, FITS based ND sky-maps
-and formats compatible with Astropy's \code{Table} and
-\code{BinnedTimeSeries} data structures. This allows
-users to directly further analyse the results, e.g.
-standard algorithms for time analysis such as
-computing Lomb-Scargle periodograms or Bayesian
-blocks for time series. So far \gammapy does not
-support 'unfolding' of \gammaray spectra.
-Methods for this will be implemented in a future version of \gammapy.
-
-Code example ~\ref{fig*:minted:gp_estimators} shows how to use
-the \code{TSMapEstimator} objects with a given input \code{MapDataset}.
-In addition to the model it allows to specify the energy
-bins of the resulting flux and TS maps.
-
-\begin{figure}
-	\import{code-examples/generated/}{gp_estimators}
-	\caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
-        a flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
-        and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
-        of the flux error and and flux upper limit maps respectively.
-    }
-    \label{fig*:minted:gp_estimators}
-\end{figure}
-
-\subsection{gammapy.analysis}
-\label{ssec:gammapy-analysis}
-The \code{gammapy.analysis} sub-module provides a high-level interface (HLI) for the most
-common use cases identified in \gammaray analyses. The included classes and methods
- can be used in Python scripts, notebooks or as commands within IPython
-sessions. The HLI can also be used to automatise
-workflows driven by parameters declared in a configuration file in YAML format.
-This way, a full analysis can be executed via a single command line taking the
-configuration file as input.
-
-The \code{Analysis} class has the responsibility of orchestrating of the workflow
-defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
-the \code{AnalysisStep} classes that define the identified common use cases. These
-steps include the following: observations selection with the \code{DataStore},  data
-reduction, excess map computation, model fitting, flux points estimation, and
-light curves production. The structure of the \code{Analysis} class allows to define
-custom AnalysisStep, so one could design and configure arbitrarily complex
-workflows. \todo{the latter is not true for v1.0..., include example YAML file?}
-
 \subsection{gammapy.stats}
@@
 	\label{codeexample:stats} \end{figure}
+
+\subsection{gammapy.modeling}
+\label{ssec:gammapy-modeling}
+%
+\code{gammapy.modeling} contains all the functionality related to modeling and fitting
+data. This includes spectral, spatial and temporal model classes, as well as
+the fit and parameter API.
+
+\subsubsection{Models}
+\label{sssec:models}
+Source models in \gammapy are four dimensional models which support two
+spatial dimensions $\ell, b$, and energy dimension $E$ as well as
+the time dimension $t$. To simplify the the definition of the
+models, \gammapy uses a factorised representation of the total source
+model:
+
+\begin{equation}
+    f(l, b, E, t) = F(E)  \cdot G(l, b, E) \cdot  H(t, E)
+\end{equation}
+
+Where the spectral model $F$ implicitly carries the total flux
+norm of the model. The spatial model $G$ optionally depends
+on energy and allows to support e.g. energy dependent
+morphology models. The temporal model component $H$
+optionally also supports an energy variable to
+allow for spectral variations of the model with time.
+
+Following the factorisation the models objects are grouped
+into the following categories:
+
+\begin{itemize}
+	\item \code{SpectralModel}: models to describe spectral shapes of sources,
+	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources,
+	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
+	      light and phase curves.
+\end{itemize}
+
+The models follow a naming scheme which contains the category as a suffix to
+the class name.
+The spectral models include a special class of normed models, named using the \code{NormSpectralModel} suffix.
+These spectral models feature a dimension-less norm parameter
+instead of an amplitude parameter with physical units. They
+must be used along with another spectral model, as a multiplicative correction
+factor according to their spectral shape. They can be typically used for
+adjusting template based models, or adding taking into account
+the absorbtion effect on 
+\gammaray spectra caused by the extra-galactic background light (EBL) (\code{EBLAbsorptionNormSpectralModel})
+model. \gammapy supports a variety of EBL absorbtion models, such as
+
+\cite{Franceschini2008}, \cite{Finke2010} and \cite{Dominguez2011}.
+
+The analytic spatial models are all normalized such as they integrate to
+unity over the sky but the template spatial models may not, so in that special
+case they have to be combined with a \code{NormSpectralModel}.
+
+The \code{SkyModel} object represents factorised model that combines the spectral,
+spatial and temporal model components (the spatial and temporal components being
+optional). \code{SkyModel} objects represents additive emission components, usually
+sources or diffuse emission, although a single source can also be modeled by
+multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
+has a \code{Models} class.
+
+The model gallery provides a visual overview of the available models in
+\gammapy. Most of the analytic models  commonly used in \gammaray astronomy are
+built-in. We also offer a wrapper to radiative models implemented in the Naima
+package~\cite{naima}. The modeling framework can be easily extended with
+user-defined models. For example agnpy models that describe leptonic radiative
+processes in jetted Active Galactic Nuclei (AGN) can be wrapped into
+\gammapy~\citep[see Section 3.5 of ][]{2021arXiv211214573N} .
+
+\begin{figure}
+	\import{code-examples/generated/}{gp_models}
+	\caption{Using \code{gammapy.modeling.models} to define a source model with a
+    spectral, spatial and temporal component. For convenience the model
+    parameters can be defined as strings with attached units. The spatial model
+    takes an addtional \code{frame} parameter which allow users to define
+    the coordinate frame of the position of the model.
+    }
+	\label{fig*:minted:gp_models}
+\end{figure}
+
+\subsubsection{Fit}
+\label{sssec:fit}
+
+The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
+parameter errors and correlations. It interfaces with a \code{Datasets} object, which
+in turn is connected to a \code{Models} object containing the model parameters in its
+\code{Parameters} object. Models can be unique for a given dataset, or contribute to
+multiple datasets, allowing e.g., to do a joint fit to
+multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
+examples are given in the tutorials.
+
+\todo{Add fit code example...?}
+
+The Fit class provides a uniform interface to multiple fitting backends:
+“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
+“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
+and errors are computed only for the fitting with MINUIT. However depending on
+the problem other optimizers can better perform, so sometimes it can be useful
+to run a pre-fit with alternative optimization methods. In future we plan to
+extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo.
+\footnote{a prototype is available in gammapy-recipes,
+	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
+}
+
+\subsection{gammapy.estimators}
+\label{ssec:gammapy-estimators}
+By fitting parametric models to the data, the total integrated
+flux and overall temporal, spectral and morphological shape of the
+\gammaray emission can be constrained. In many cases it is useful
+to make a more detailed follow-up analysis by measuring the
+flux in smaller spectral, temporal or spatial bins. This
+possibly reveals more detailed emission features, which
+are relevant for studying correlation with counterpart emissions.
+
+The \code{gammapy.estimators} sub-module features methods to compute flux
+points, light curves, flux maps, flux profiles from data.
+The basic method for all these measurements is equivalent.
+The initial fine bins of \code{MapDataset} are grouped into
+larger bins. The norm of the best fit "reference" spectral
+model is fitted (or 'scaled') in the  restricted data range only.
+
+The base class of all algorithms is the \code{Estimator}  class.
+
+Signifiance is estimated based on hypothesis
+testing against the background only model. This allows
+to assign a significance to the given flux bin.
+In addition to the best fit flux norm all estimators compute
+quantities corresponding to this flux. This includes
+the predicted number of total, signal and background
+counts per flux bin. The total fit statistics
+of the best fit model, the fit statistics of the
+null hypothesis and the difference between both,
+the so-called TS value.
+From the TS value the significance of the
+significance of the measured signal and associated flux
+can be derived.
+
+Optionally it can also compute more advanced quantities
+such as assymmetric flux errors, flux upper limits
+and one dimensional profiles of the fit statistic,
+which show how the likelihood functions varies with
+the flux norm parameter around the fit minimum.
+This information is useful for inspecting the quality
+of a fit, for which asymptomatically a parabolic
+shape of the profile is expected at the best fit
+values (\todo{Reference to modeling / fitting section?}).
+
+The result of the flux point estimation are either stored in a
+\code{FluxMaps} or \code{FluxPoints} object. Both objects
+are based on an internal representation of the flux which is
+independent of the Spectral Energy Distribution (SED) type. The flux is represented by a
+the reference spectral model and an array of
+normalisation values given in energy, time and spatial bins,
+which factorises the deviation of the flux in a given
+bin from the reference spectral model. This allows
+user to conveniently transform between different
+SED types. Table~\ref{tab:sed_types} shows an
+overview and definitions of the supported SED types.
+The actual flux values for each SED type are obtained
+by mutiplication of the norm with the  reference flux.
+
+\begin{table*}
+    \begin{center}
+        \begin{tabular}{lll}
+         \hline
+         Type & Description & Unit Equivalency \\
+         \hline
+         dnde & Differential flux at a given energy & $\mathrm{TeV^{-1}~cm^{-2}~s^{-1}}$ \\
+         e2dnde & Differential flux at a given energy  & $\mathrm{TeV~cm^{-2}~s^{-1}}$ \\
+         flux & Integrated flux in a given energy range & $\mathrm{cm^{-2}~s^{-1}}$ \\
+         eflux & Integrated energy flux in a given energy range & $\mathrm{erg~cm^{-2}~s^{-1}}$\\
+         \hline
+        \end{tabular}
+    \end{center}
+    \label{tab:sed_types}
+    \caption{Definition of the different SED types supported in \gammapy.}
+\end{table*}
+
+Both result objects support the possibility to serialise
+the data into multiple formats. This includes the
+\gadf SED (reference?) format, FITS based ND sky-maps
+and formats compatible with Astropy's \code{Table} and
+\code{BinnedTimeSeries} data structures. This allows
+users to directly further analyse the results, e.g.
+standard algorithms for time analysis such as
+computing Lomb-Scargle periodograms or Bayesian
+blocks for time series. So far \gammapy does not
+support 'unfolding' of \gammaray spectra.
+Methods for this will be implemented in a future version of \gammapy.
+
+Code example ~\ref{fig*:minted:gp_estimators} shows how to use
+the \code{TSMapEstimator} objects with a given input \code{MapDataset}.
+In addition to the model it allows to specify the energy
+bins of the resulting flux and TS maps.
+
+\begin{figure}
+	\import{code-examples/generated/}{gp_estimators}
+	\caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
+        a flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
+        and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
+        of the flux error and and flux upper limit maps respectively.
+    }
+    \label{fig*:minted:gp_estimators}
+\end{figure}
+
+\subsection{gammapy.analysis}
+\label{ssec:gammapy-analysis}
+The \code{gammapy.analysis} sub-module provides a high-level interface (HLI) for the most
+common use cases identified in \gammaray analyses. The included classes and methods
+ can be used in Python scripts, notebooks or as commands within IPython
+sessions. The HLI can also be used to automatise
+workflows driven by parameters declared in a configuration file in YAML format.
+This way, a full analysis can be executed via a single command line taking the
+configuration file as input.
+
+The \code{Analysis} class has the responsibility of orchestrating of the workflow
+defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
+the \code{AnalysisStep} classes that define the identified common use cases. These
+steps include the following: observations selection with the \code{DataStore},  data
+reduction, excess map computation, model fitting, flux points estimation, and
+light curves production. The structure of the \code{Analysis} class allows to define
+custom AnalysisStep, so one could design and configure arbitrarily complex
+workflows. \todo{the latter is not true for v1.0..., include example YAML file?}
 
@@
 is done by using the \code{LightCurveEstimator} that fits the normalisation of a
-source in each time (and optionally energy) band per observation, keeping other parameters constant.
+source in each time (and optionally energy) band per observation, keeping constant
+other parameters.
 For custom time binning, an observation needs to be split into finer time bins using

### 2022-10-30 src/ms-review.tex
Minor rewrite of the survey section

@@
 \gammapy can be used for a variety of science cases by different IACT
-experiments. (Refer to publications) In this section, we show a non-exhaustive
-list of some typical analysis that can be performed. In general from the
-\gammapy side there is not limitation on which kind of analysis can be done
-with which instrument, however in practice it is limited by the availability of
-public data.
+experiments. (Refer to publications). The analysis examples shown in
+the following section are limited by the availability
+of public data. In general, there is no limitation on performing a specific analysis
+on data from a given instrument.
 
@@
 spectrum of a source in a given region defined on the sky, in conventional
-astronomy also called aperture photometry. The spectrum is typically measured
+astronomy also called \textit{aperture photometry}. The spectrum is typically measured
 in two steps: first a parametric spectral model is fitted to the data and
@@
 Sky surveys have a large potential for new source detections, and new phenomena
-discovery. They also offer less selection bias to perform source population
-studies over a large set of coherently detected and modelled objects. Early
-versions of \gammapy were developed in parallel of the preparation of
+discovery in \gammaray astronomy. They also offer less selection bias to perform
+source population studies over a large set of coherently detected and modelled objects.
+Early versions of \gammapy were developed in parallel of the preparation of
 the \hess Galactic plane survey catalog~\citep[HGPS, ][]{2018A&A...612A...1H} and
@@
 simulations, we jump from 78 sources detected by \hess to about 500 detectable by
-CTA~\citep{2021arXiv210903729R}.
-
-Studies performed on simulations not only offer a first glimpse on what could
-be the sky seen by CTA (according to our current knowledge on source
-populations), but also give us the opportunity to test the software on complex
-use cases\footnote{Note that the CTA-GPS simulations were performed with the
-	\textit{ctools} package~\citep{2016A&A...593A...1K} and analysed with both
-	\textit{ctools} and \textit{gammapy} packages in order to cross-validate
-	them.}. So we can  improve performances, optimize our analyses strategies, and
-identify the needs in term of parallelisation to process the large datasets
-provided by the surveys.
+CTA~\citep{2021arXiv210903729R}. This large increase in the amount of data to analyse
+and increase in complexity of modelling scenarios, requires the high level
+analysis software to be both scalabale as well as performant.
 
 In short the production of catalogs from \gammaray surveys can be divided in
-four main steps : data reduction; object detection; model fitting and model
-selection; associations and classification. The \iacts data reduction step is
-done in the same way than described in the previous sections but scale up to
-few thousands of observations. The object detection step consists a minima in
+four main steps: data reduction; object detection; model fitting and model
+selection; associations and classification. All steps can be either be done
+with \gammapy directly or by relying on the seemless integration 
+of \gammapy with the scientific Python ecosystem. This allows to rely
+on 3rd functionality wherever needed.
+
+The \iacts data reduction step is done in the same way than described in the 
+previous sections but scale up to few thousands of observations. The object
+ detection step consists a minima in
 finding local maxima in the significance (or TS) maps,  given by the
@@
 the "scikit-image" package~\citep{scikit-image}, and outlier detection from
-the "scikit-learn" package~\citep{scikit-learn}. Tests on simulations shown that it
-reduces the spurious detections at this stage and then speed up the next step
+the "scikit-learn" package~\citep{scikit-learn}. This allows e.g., to 
+reduce the number of spurious detections at this stage using standard
+classification algorithms and then speed up the next step
 as less objects will have to be fitted simultaneously. During the modelling
@@
 sources.
+
+Studies performed on simulations not only offer a first glimpse on what could
+be the sky seen by CTA (according to our current knowledge on source
+populations), but also give us the opportunity to test the software on complex
+use cases\footnote{Note that the CTA-GPS simulations were performed with the
+	\textit{ctools} package~\citep{2016A&A...593A...1K} and analysed with both
+	\textit{ctools} and \textit{gammapy} packages in order to cross-validate
+	them.}. So we can  improve performances, optimize our analyses strategies, and
+identify the needs in term of parallelisation to process the large datasets
+provided by the surveys.
 

### 2022-10-30 src/ms-review.tex
Fix caption and clarify MWL data levels

@@
         facing arrows indicate the value of $2\sigma$ upper flux limits
-        for the given energy range. The red solid line shows the best
+        for the given energy range. The black solid line shows the best
         fit model and the transparent band its $1\sigma$ error range.
+		The band is to small be visible.
     }
@@
 different instruments and at different levels of reduction. We estimate the
-spectrum of the Crab Nebula combining data from \fermi, \magic and \hawc. Maps
-of \fermi data are prepared selecting a region of $X^{\circ}$ around the
+spectrum of the Crab Nebula combining data from the \fermi, \magic and \hawc
+instruments.
+
+The \fermi data is introduced at the data level DL4. It is prepared 
+using the standard \textit{fermitools} \citep{Fermitools2019} and
+selecting a region of $X^{\circ}$ around the
 position of the Crab Nebula applying the same selection criteria of the 3FHL
 catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$,
-~\citealt{3FHL}).  The \magic data are two%% shall we explain exactly which type of Map is created?
+~\citealt{3FHL}).
+
+The \magic data is included from the data level DL3. It consists of %% shall we explain exactly which type of Map is created?
 observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
@@
 
+In the case the \hawc data is included from the DL5 data level, meaning
+flux points and associated errors provided by \cite{hawc_crab_2019}.
+
 \gammapy automatically generates a likelihood including three different types
 of terms, two Poissonian likelihoods for the \fermi map and the
-ON/OFF counts, and a $\chi^2$ accounting for the flux points. For \fermi, a 
+ON/OFF counts, and a $\chi^2$ accounting for the \hawc flux points. For \fermi, a 
 three-dimensional forward folding of the sky model with the IRF is performed,

### 2022-10-30 src/ms-review.tex
Address comment by @facero

@@
 \newcommand{\github}{GitHub\xspace}
+\newcommand{\imimuit}{IMinuit}
 
@@
 	data. This introduces the need to have a high-level analysis software available to the astronomical community. In
-	this article we present the first major of \gammapy, the Long-term Support (LTS) v1.0, a
+	this article we present the first major release of \gammapy, the Long-term Support (LTS) v1.0, a
 	community-developed open-source Python package for \gammaray astronomy. We
@@
 	maximum likelihood fitting. It comes with built-in spectral, spatial and
-	temporal models as well as support for custom user models, to model e.g.,
+	temporal models, support for particle radiation emission spectra as well as
+	support for custom user models, to model e.g.,
 	energy dependent morphology of \gammaray sources. Multiple datasets can be
@@
 It covers the energy range from fews tens of GeV up to the PeV.
-There are two main categories of instrument \citep{2015CRPhy..16..610D}.
-Imaging Atmospheric Cherenkov Telescopes (IACT) make images of atmospheric showers
+There are two main categories of ground based instruments: 
+Imaging Atmospheric Cherenkov Telescopes (IACT) and 
+Water Cherenkov observatories. IACTs make images of atmospheric showers
 by detecting the Cherenkov radiation emitted by the cascading charged particles and
@@
 Those instruments have a limited field of view (FoV) and duty cycle, but
-good energy and angular resolution.
+good energy and angular resolution \citep{2015CRPhy..16..610D}.
 
@@
 \scipy~\citep{2020SciPy-NMeth}, visualization libraries, e.g. Matplotlib \citep{matplotlib},
-or optimization packages such as Iminuit \citep{iminuit}.
+or optimization packages such as \iminuit \citep{iminuit}.
 
@@
 example an energy axis, to represent how a quantity varies in that dimension
-inside the corresponding region. The region is represented on the local
-tangential projection see \cite{Astropy regions}.
+inside the corresponding region. Technically the region is represented on the local
+tangential projection, as implement by \cite{AstropyRegions2022}.
 
@@
 The Fit class provides a uniform interface to multiple fitting backends:
-“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
+\iminuit~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
 “sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
-and errors are computed only for the fitting with MINUIT. However depending on
+and errors are computed only for the fitting with \iminuit. However depending on
 the problem other optimizers can better perform, so sometimes it can be useful
@@
 		Example of 1D spectral analysis of the Galactic Center for three simulated CTA
-		observations. The left image shows the maps of counts with the measurement
-		region and background regions overlaid in different colors. The right image
+		observations for the 1DC dataset. The left image shows the maps of counts with the measurement
+		region in white and background regions overlaid in different colors. The right image
 		shows the resulting spectral points and their corresponding log-likelihood
@@
 source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
-range spans $80\,{\rm GeV} -- 20\,{\rm TeV}$. They are reduced to ON/OFF
+range spans $80\,{\rm GeV} - 20\,{\rm TeV}$. They are reduced to ON/OFF
 dataset before being fitted. \hawc flux points data are estimated
@@
 the \gammaray emission, given a physical scenario. Among those
-packages are  \cite{agnpy}, \cite{naima}, \cite{jetset} or \cite{gamera}.
+packages are  Agnpy \citep{agnpy}, Naima \citep{naima}, Jetset \citep{jetset}
+and Gamera \citep{gamera}.
 Tyically those emission models predict broadband emission from

### 2022-11-01 src/ms-review.tex
Improve definition of norm

@@
 
-Where the spectral model $F$ implicitly carries the total flux
-norm of the model. The spatial model $G$ optionally depends
+Where the spectral model $F$ implicitly includes an \textit{amplitude} parameter
+for the total flux of the model. The spatial model $G$ optionally depends
 on energy and allows to support e.g. energy dependent
@@
 The models follow a naming scheme which contains the category as a suffix to
-the class name.
-The spectral models include a special class of normed models, named using the \code{NormSpectralModel} suffix.
-These spectral models feature a dimension-less norm parameter
-instead of an amplitude parameter with physical units. They
+the class name. The spectral models include a special class of normed models,
+named using the \code{NormSpectralModel} suffix.
+These spectral models feature a dimension-less \textit{norm} parameter
+instead of an \text{amplitude} parameter with physical units. They
 must be used along with another spectral model, as a multiplicative correction
@@
 The initial fine bins of \code{MapDataset} are grouped into
-larger bins. The norm of the best fit "reference" spectral
-model is fitted (or 'scaled') in the  restricted data range only.
+larger bins. A multiplicative correction factor (the \textit{norm})
+is applied to the best fit "reference" spectral
+model and is fitted in the restricted data range, defined by the 
+bin group, only.
 
@@
 	\includegraphics[width=1.\textwidth]{figures/cube_analysis.pdf}
-	\caption{Example of a 3D analysis for simulated sources using the \cta \irfs. The
-		left image shows a significance map where the three simulated sources can be
+	\caption{Example of a 3D analysis for simulated sources with point-like, Gaussian
+		and shell-like morphology. The simulation uses \textit{prod5} \irfs from \cta.
+		The left image shows a significance map where the three simulated sources can be
 		seen. The middle figure shows another significance map, but this time after

### 2022-11-01 src/figures/cube_analysis.py

@@ -59,9 +59,9 @@ rect = (0.72, 0.23, 0.26, 0.7)
 ax = fig.add_axes(rect=rect)
 ax.tick_params(labelsize=fontsize_ticks, pad=1, length=2)
 excess.plot(ax=ax, color='blue', label='excess counts',markersize=2)
-npred_1.plot_hist(ax=ax, label='source 1', lw=1, color='C0')
-npred_2.plot_hist(ax=ax, label='source 2', lw=1, color='C1')
-npred_3.plot_hist(ax=ax, label='source 3', lw=1, color='C2')
+npred_1.plot_hist(ax=ax, label='Point source', lw=1, color='C0')
+npred_2.plot_hist(ax=ax, label='Gaussian', lw=1, color='C1')
+npred_3.plot_hist(ax=ax, label='Shell', lw=1, color='C2')
 (npred_1 + npred_2 + npred_3).plot_hist(ax=ax, label='total', lw=1, color='k')
 ax.legend(fontsize=5, ncol=2)
 ax.set_ylabel('Counts', fontsize=fontsize_labels)

### 2022-11-01 src/ms-review.tex
Address comments from Laura Olivera's PDF

@@
 %% Paper outline
-In this article, we describe the general structure of the \gammapy package and
-its main concepts. In Section \ref{sec:analysis-workflow-overview}, we present
-the data analysis workflow in very high-energy \gammaray astronomy. Then we
-show how this workflow is reflected in the structure of the \gammapy package and
-describe the various subpackages it contains. Section \ref{sec:applications}
-presents a number of applications, while Section \ref{sec:gammapy-project}
-discusses the project organization.
+In this article, we describe the general structure of the \gammapy package,
+its main concepts and organisational structure. We start in
+Section~\ref{sec:gammaray-data-analysis} with a general overview
+of the data analysis workflow in very high-energy \gammaray astronomy. Then we
+show how this workflow is reflected in the structure of the \gammapy package 
+in Section~\ref{sec:gammapy-package} and also
+describe the various subpackages it contains. Section~\ref{sec:applications}
+presents a number of applications, while Section~\ref{sec:gammapy-project}
+finally discusses the project organization.
 
@@
 quantities related to \gammaray sources and the production of high-level products such as spectra,
-light curves and catalogs. The methods and tools applied here are more generic and are broadly
+light curves and catalogs. The methods applied here are more generic and are broadly
 shared across the field. They also frequently imply joint analysis of multi-instrument data.
-To extract physically relevant information, the measured data are usually compared to a
-model of the expected \gammaray emitters in the instrument field-of-view using statistical
-techniques such as maximum likelihood.
-
-We can write the expected number of detected events at measured position $p$ and energy $E$:
+To extract physically relevant information, the measured counts on an instrument are usually
+compared to a parametrised model of the true intensity distribution of \gammaray source in a given
+field-of-view, which is "forward folded" through a model of the instrument repsonse
+to get a prediction for the expected counts measured by the instrument. Parameters
+of the model are then estimated using statistical techniques such as maximum likelihood
+estimation (MLE).
+
+In the most general way we can write the expected number of detected events at measured
+position $p$ and energy $E$:
 \begin{align}
@@
 \item $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response
-\item $\Phi(p_{\rm true}, E_{\rm true})$ is the sky flux model
+\item $\Phi(p_{\rm true}, E_{\rm true})$ is the parametrised sky flux model
 \item $t_{\rm obs}$ is the observation time
@@
 The handling of DL3 data is performed by classes and methods
-in the \code{gammapy.data} (see \ref{ssec:gammapy-data}) and the \code{gammapy.irf}
-(see \ref{ssec:gammapy-irf}) subpackages.
+in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
+(see Section~\ref{ssec:gammapy-irf}) subpackages.
 
 The first step in the analysis is the selection and extraction of observations
-based of their meta data including information such as pointing direction, observation
+based of their metadata including information such as pointing direction, observation
 time and observation conditions.
 
-The next step of the analysis is the data reduction where all observation events and instrument
-responses are projected onto a user-defined geometry. A typical geometry consists in a spectral representation with a measured
-energy axis, and in a spatial representation, either a coordinates system  with a projection
+The next step of the analysis is the data reduction, where all observation events and instrument
+responses are filled into or projected onto a common physical coordinate system, defined by
+a map geometry. The definition of the map geometry typically consists of a spectral dimension
+defined by a binned energy axis and of a spatial dimension, which either defines 
+a spherical projection from celestial coordinates to an pixelised image space
 (for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
 The \code{gammapy.maps} subpackage provides general multidimensional geometry objects
-(Geom) and the associated data structures (Maps) (see \ref{ssec:gammapy-maps}).
-
-All observation events and instrument responses are projected onto the
-user defined geometry. Because residual hadronic background models can be subject
-to significant uncertainties, background correction must be applied,
+(\code{Geom}) and the associated data structures (\code{Maps}) (see Section~\ref{ssec:gammapy-maps}).
+
+After all data has been projected into the same coordinate system, it is typically
+required to improve the residual hadronic background estimate. As residual hadronic
+background models can be subject to significant systematic uncertainties,
+the background estimated can be improved by taking into account actual data
+from regions without known \gammaray sources. This includes methods 
 such as the ring or the field-of-view background techniques or
-background measurements must be performed within, e.g. reflected regions~\citep{Berge07}.
-Parts of the data with high associated IRF systematics must also be excluded by defining
-a 'safe' data range. These data reduction steps are performed by classes and functions
-implemented in the \code{gammapy.makers} subpackage (see \ref{ssec:gammapy-makers}).
-
-The counts data and the reduced IRFs in the form of maps are bundled into dataset objects
-that represent the data level 4 (DL4). They can be written to
-disk, in a format specific to \gammapy to allow users to read them back at any time later
-for modeling and fitting.
-
-This latter step datasets classes bundle reduced data in form of maps, reduced IRFs, models and
-fit statistics. Different sub-classes support different analysis methods
-and fit statistics (e.g. Poisson statistics with known background or
+background measurements performed within, e.g. reflected regions~\citep{Berge07}.
+Data measured at the field-of-view or energy boundaries of the instrument is typically
+associated with a sytematic uncertainty in the IRF. For this reason this part 
+of the data is often excluded from subsequent analysis by defining regions of
+ "safe" data in the spatial as well as energy dimension.
+All of these data reduction steps are performed by classes and functions
+implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).
+
+The counts data and the reduced IRFs in the form of maps are bundled into datasets
+that represent the data level 4 (DL4). Those reduced datasets can be written to disk,
+in a format specific to \gammapy to allow users to read them back at any time later
+for modeling and fitting. Different variations of such datasets support different 
+analysis methods and fit statistics (e.g. Poisson statistics with known background or
 with OFF background measurements). The datasets are used to perform joint-likelihood
@@
 provides a uniform interface to multiple fitting backends. It also provides
-a variety of :ref:`built in models <model-gallery>`. This includes spectral,
+a variety of built in models. This includes spectral,
 spatial and temporal model classes to describe the \gammaray emission in the sky.
@@
 supports data that is compliant with v0.2 of the \gadf data format.
-As both the \gadf data model and \gammapy were initially conceived for
-\iact data analysis, DL3 data are typically bundled into individual
-observations, which correspond to stable periods of data
-aquisitions (typically $20 - 30\,{\rm min}$) for a given instrument.
+DL3 data are typically bundled into individual observations, which
+corresponds to stable periods of data aqusition. For IACT data analysis,
+for which the GADF data model and Gammapy were initially conceived for,
+these are usually $20 - 30\,{\rm min}$ long.
 Each observation is assigned a unique integer ID for reference.
@@
 
-The so-called DL3 files represented by the \code{Observation} class consist
-of two types of elements: a list of \gammaray events with relevant physical
-quantities for the successive analysis (estimated energy, direction and arrival
-times) that is handled by the \code{EventList} class and an instrument
-response function (IRF), providing the response of the system, typically
-factorised in independent components (see the description in
-Sec.~\ref{ssec:gammapy-irf}). The separate handling of event lists and IRFs
-additionally allows for data from other \gammaray instruments to be read. For
+The DL3 level data represented by the \code{Observation} class consist
+of two types of elements: first a list of \gammaray events with relevant physical
+quantities such as estimated energy, direction and arrival
+times, which is represented by the \code{EventList} class/. Second a set of
+associated IRFs, providing the response of the system, typically
+factorised in independent components as described in
+Section~\ref{ssec:gammapy-irf}. The separate handling of event lists and IRFs
+additionally allows for data from non-IACT \gammaray instruments to be read. For
 example, to read \fermi data, the user can read separately their event list
@@
 IRF class representing the response functions provided by \fermi, see
-Sec.~\ref{ssec:fermi}.
+example in Section~\ref{ssec:multi-instrument-analysis}.
 %
@@
 
-\paragraph{Effective area:}
+\subsubsection{Effective Area}
 \gammapy provides the class \code{EffectiveAreaTable2D} to
@@
 
-\paragraph{Point spread function:}
+\subsubsection{Point Spread Function}
 \gammapy allows user to treat different kinds of PSFs,
@@
 and offset angle bin. Similarly, \code{PSFKing takes} into account the gamma and
-sigma parameters as defined here. The \code{ParametricPSF} allows to create a
-PSF with a representation different from Gaussian(s) or King profile(s).
-Finally, the user can take advantage from the \code{PSFMap} class, which creates
-a multi-dimensional map of the PSF in sky coordinates. At each position, a PSF
-kernel map (\code{PSFKernel}) provides a PSF as a function of the true energy.
-The creation of PSF kernel maps, where the PSF is defined for each
-sky-position, is also given to the user. The latter two can speed up analyses.
-
-\paragraph{Energy dispersion:}
+sigma parameters. The general \code{ParametricPSF} class allows users to create a
+custom PSF with a parametric representation different from Gaussian(s) or King profile(s).
+The generic \code{PSF3D} class stores a radial symmetric profile of a
+PSF to represent non-parametric shapes, againa depending on true energy 
+of offset form the poiting position.
+
+To handle the change of the PSF with the observational offset during the analysis 
+the \code{PSFMap} class is used. It stores the radial profile of the PSF
+depending on the true energy and position on the sky. During the modeling
+step in the analysis, the PSF profile for each model component is 
+looked up at its current position and converted into a 3d convolution kernel
+which used for the prediction of counts from that model component.
+
+\subsubsection{Energy Dispersion}
 for \iact, it is generally given in terms of the so-called
@@
 
-\paragraph{Background model:}
+\subsubsection{Background model}
 The BKG can be represented in \gammapy as either 1) a 2D map (\code{Background2D})
@@
 a given dimension, spatial or not. Map axes can have physical units attached to
-them, as well as define non-linear spaced bins. All map classes support operations such
-as arithmetic operations with unit support, up- and downsampling along
+them, as well as define non-linear spaced bins. All map classes support a basic
+set of arithmetic and boolean operations with unit support, up- and downsampling along
 extra axes, interpolation, resampling of extra axes, interactive visualisation
@@
 analysis steps via a registry system. Another important topic will
-be to improve the support of handling meta data for data structures
+be to improve the support of handling metadata for data structures
 and provenance information to track the history of the data reduction

### 2022-11-01 src/ms-review.tex
Address comments in maps and makers section

@@
 provides methods to transform between sky and pixel coordinates. Maps consist
-of a geometry instance together with a Numpy data array containing the corresponding
-map values. Map axes contain a sequence of ordered values which define bins on
-a given dimension, spatial or not. Map axes can have physical units attached to
-them, as well as define non-linear spaced bins. All map classes support a basic
-set of arithmetic and boolean operations with unit support, up- and downsampling along
-extra axes, interpolation, resampling of extra axes, interactive visualisation
+of a geometry instance defining the coordinate system together with a
+Numpy array containing the associated data. All map classes support a basic
+set of arithmetic and boolean operations with  unit support, up- and downsampling
+along extra axes, interpolation, resampling of extra axes, interactive visualisation
 in notebooks and interpolation onto different geometries.
 
-The sub-package provides a uniform API for the FITS World Coordinate System
-(WCS), the HEALPix pixelization and region-based data structure
-(see Figure~\ref{ig*:minted:gp_maps}).
+The \code{MapAxis} class provides a uniform API for axes representing
+bins on any physical quantity, such as energy or angular offset.
+Map axes can have physical units attached to them, as well as define
+non-lineary spaced bins. The special case of time is covered by the
+dedicated \code{TimeMapAxis}, which allows time bins to be non-contiguous,
+as it is often the case with observation time-stamps. The generic
+class \code{LabelMapAxis} allows the creation of axes for non-numeric entries.
+
+To handle the spatial dimension the sub-package exposes a uniform API for
+the FITS World Coordinate System (WCS), the HEALPix pixelization and
+region-based data structure (see Figure~\ref{ig*:minted:gp_maps}).
+This allows uses to perform the same higher level operations on maps
+independent of the underlying pixelisation scheme.
 
@@
 example an energy axis, to represent how a quantity varies in that dimension
-inside the corresponding region. Technically the region is represented on the local
-tangential projection, as implement by \cite{AstropyRegions2022}.
-
-Additionally, the \code{MapAxis} class provides a uniform API for axes representing
-bins on any physical quantity, such as energy or angular offset. The special
-case of time is covered by the dedicated \code{TimeMapAxis}, which allows time bins to
-be non-contiguous, as it is often the case with observation time-stamps. The
-generic class \code{LabelMapAxis} allows the creation of axes for non-numeric
-entries.
+inside the corresponding region. To avoid the complexity of handling
+spherical geometry for regions, the regions are projected onto the local
+tangential plane using a WCS transform. This approach follows Astropy's "regions"
+package \citep{AstropyRegions2022}, which is both used as an API to define regions
+for users as well as handling the underlying geometric operations.
 
@@
         Using \code{gammapy.makers} to reduce DL3 level data into a
-		\code{MapDataset}. All \code{Maker} classes take
-        the configuration on initialisation of the class.
+		\code{MapDataset}. All \code{Maker} classes represent 
+		a step in the data reduction process. They take
+        the configuration on initialisation of the class. They 
+		also consitently define \code{.run()} methods, which take 
+		a dataset object and and optionally \an code{Observation} 
+		object. This way \code{Maker} classes can be chained
+		to define more complex data reduction "pipelines".
     }

### 2022-11-21 src/ms-review.tex
Fix control sequence errors

@@
 \newcommand{\github}{GitHub\xspace}
-\newcommand{\imimuit}{IMinuit}
+\newcommand{\iminuit}{IMinuit}
 
@@
 gamma/hadron separation is applied to build lists of \gammaray like events.
-The lists of \gammary events are then used to derive scientific results, such as spectra, sky maps
+The lists of \gammaray events are then used to derive scientific results, such as spectra, sky maps
 or light curves, taking into account the observatory specific instrument response functions (IRF).
@@
 		also consitently define \code{.run()} methods, which take 
-		a dataset object and and optionally \an code{Observation} 
+		a dataset object and optionally an \code{Observation} 
 		object. This way \code{Maker} classes can be chained

### 2022-11-28 src/ms-review.tex
Address final comments by L.Olivera

@@
 %
-The end product of the data reduction process described in Section
-\ref{sec:gammaray-data-analysis} (and in detail in \ref{ssec:gammapy-makers}) are a set of binned counts, background and IRF maps,
-at the DL4 level. The \code{gammapy.datasets} subpackage contains classes to bundle
+The \code{gammapy.datasets} subpackage contains classes to bundle
 together binned data along with associated models and the likelihood, which
@@
 done using \code{SpectrumDataset}. While the default statistics for both of these is
-Cash, their corresponding on off versions are adapted for the case where the
-background is measured from real off counts, and support wstat statistics. The
+\emph{Cash}}, their corresponding on off versions are adapted for the case where the
+background is measured from real off counts, and support \emph{WStat} statistics. The
 predicted counts are computed by convolution of the models with the associated
@@
 binned and IRFs are interpolated and projected onto the chosen analysis
-geometry. This produces counts, exposure, background, psf and energy dispersion
-maps. The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
+geometry. The end product of the data reduction process are a set of binned counts,
+background exposure, psf and energy dispersion maps at the DL4 level. 
+The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
 responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.
@@
 Source models in \gammapy are four dimensional models which support two
-spatial dimensions $\ell, b$, and energy dimension $E$ as well as
+spatial dimensions define by the sky coordinates $\ell, b$, and energy dimension $E$ as well as
 the time dimension $t$. To simplify the the definition of the
@@
 The \code{gammapy.estimators} sub-module features methods to compute flux
-points, light curves, flux maps, flux profiles from data.
+points, light curves, flux maps and flux profiles from data.
 The basic method for all these measurements is equivalent.
@@
 
-The base class of all algorithms is the \code{Estimator}  class.
-
-Signifiance is estimated based on hypothesis
-testing against the background only model. This allows
-to assign a significance to the given flux bin.
 In addition to the best fit flux norm all estimators compute
@@
 
+The base class of all algorithms is the \code{Estimator}  class.
 The result of the flux point estimation are either stored in a
@@
 using the standard \textit{fermitools} \citep{Fermitools2019} and
-selecting a region of $X^{\circ}$ around the
+selecting a region of $5^{\circ} \mathrm{x} 4^{\circ}$ around the
 position of the Crab Nebula applying the same selection criteria of the 3FHL
@@
 contribution to the codebase repository triggers the documentation building and
-publishing workflow within the \textit{gammapy-docs} repository (see Sec.
-~\ref{ssec:software-distribution} and Sec. ~\ref{ssec:documentation}).
+publishing workflow within the \textit{gammapy-docs} repository
+(see Sec.~\ref{ssec:software-distribution} and Sec.~\ref{ssec:documentation-and-user-support}).
 
@@
 Water Cherenkov Observatory (HAWC) has been successfully
-demonstrated by \todo{Olivera et al.}. This makes \gammapy
+demonstrated by \cite{Olivera2022}. This makes \gammapy
 a viable choice for the base library for the science tools

### 2022-11-30 src/ms-review.tex
Address more comments by C.Nigro

@@
 mechanisms, the so-called hadronic and leptonic scenarios.
-There are mutiple Python packages that are able to model
+There are several Python packages that are able to model
 the \gammaray emission, given a physical scenario. Among those
@@
 naima package and fit it directly to \gammaray data.
+
+As an example of this application, we use the same multi-instrument
+dataset described in the previous section and we fit it with an inverse
+Compton model computed with naima and wrapped in the \gammapy fitting
+ routine with the NaimaSpectraModel class. We consider a log-parabolic
+electron distribution scattering: the synchrotron radiation produced by
+the same electrons; near and far infrared photon fields and the cosmic
+microwave background (CMB). We adopted the prescription on the target
+photon fields provided in the naima 
+documentation \footnote{\url{https://naima.readthedocs.io/en/latest/examples.html#crab-nebula-ssc-model}}.
+The best-fit inverse Compton spectrum is represented with a red dashed line in
+Fig.~\ref{fig:multi_instrument_analysis}.
 
@@
 team, as well as the technical infrastructure designed to facilitate the
-development and maintenance of \gammapy as a high quality software. We use
+development and maintenance of \gammapy as a high-quality software. We use
 common tools and services for software development of Python open-source
 projects, code review, testing, package distribution and user support, with a
-customized solution for a versioned thoroughly tested documentation in the form
+customized solution for a versioned and thoroughly-tested documentation in the form
 of user-friendly playable tutorials. This section concludes with an outlook on
@@
 
-\gammapy is a well-organised international open-source project with a broad
-developer base and the presence of commitments from strong groups and
-institutes in the very high-energy astrophysics
+\gammapy is an international open-source project with a broad
+developer base and contributions and commitments from mutiple groups and
+leading institutes in the very high-energy astrophysics
 domain\footnote{\url{https://gammapy.org/team.html}}. The main development
-roadmaps are discussed and validated by a Coordination Committee, composed of
-representatives of the main contributing laboratories. This committee is
-chaired by a Project Manager and his deputy while two Lead Developers manage
-the development strategy and organise technical activities. Because of this
-institutionally driven characteristic, the permanent staff and commitment of
-supporting institutes ensure the continuity of the executive teams. A core team
-of developers from the contributing laboratories is in charge of the regular
+roadmaps are discussed and validated by a \textit{Coordination Committee}, composed of
+representatives of the main contributing institutions and observatories.
+This committee is
+chaired by a \textit{Project Manager} and his deputy while two \textit{Lead Developers} manage
+the development strategy and organise technical activities. This
+institutionally driven organisation, the permanent staff and commitment of
+supporting institutes, ensures the continuity of the executive teams. A core team
+of developers from the contributing institutions is in charge of the regular
 development, which benefits from punctual contributions of the community at
@@
 processes and alerting developers when fails occur. This is the case of the
-content integration workflow, which monitors the execution of the test coverage
+continuous integration workflow, which monitors the execution of the test coverage
 suite\footnote{\url{https://pytest.org}} using datasets from the
@@
 enters a new development phase. The development will change from
-quick feature driven development to more stable maintenance
+quick feature-driven development to more stable maintenance
 and user support driven developement. After v1.0 we foresee
-a developement cycle with major, minor and bugfix releases.
-We basically followg the development cycle of the Astropy
+a developement cycle with major, minor and bugfix releases;
+we basically follow the development cycle of the Astropy
 project. Thus we expect a major LTS release approximately
@@
 we will work with a deprecation system for minor releases.
-API breaking changes will be announced to user by runtime
+API-breaking changes will be announced to user by runtime
 warnings first and then implemented in the subsequent
@@
 package and the interest of developers to improve
-and develop \gammapy in future. The developemnt cycle is described
-in more detail in PIG 24 \todo{reference}.
+and develop \gammapy in future. The development cycle is described
+in more detail in PIG 23 \citep{gammapy_pig_23}.
 
@@
 Python scripts to create the figures
-in \url{https://\github.com/gammapy/gammapy-v1.0-paper}.
+in \url{https://github.com/gammapy/gammapy-v1.0-paper}.
 This \github repository also documents the history of the creation
@@
 of this manuscript including figures and text, we relied on the tool
-"showyourwork"~\citep{Luger2021}. This tool coordinates the building
+\textit{showyourwork}~\citep{Luger2021}. This tool coordinates the building
 process and software as well as data dependencies such, that the complete
 manuscript can be reproduced with a single \code{make} command, after
-downloading the source repository. See \todo{reference?} for detailed
+downloading the source repository. See \url{https://github.com/gammapy/gammapy-v1.0-paper/blob/main/README.md} for detailed
 instructions. Almost all figures in this manuscript provide a link
@@
 modelling of the data. For this purpose \gammapy provides a wide selection
-of built-in, spectral, spatial and temporal models as well as unified
+of built-in spectral, spatial and temporal models, as well as unified
 fitting interface with connection to multiple optimization backends.

### 2022-11-30 src/ms-review.tex
Add astroml andastroquery references

@@
 source) comparing the difference in log likelihood between these two
-hypotheses. For the association and classification step, that is tightly
-connected to the population studies, we can a minima compare the fitted models
-to the set of \gammaray catalogs available in \code{gammapy.catalog}. However
-further multi-wavelength cross-matches are usually required to characterize the
-sources.
+hypotheses.
+
+For the association and classification step, that is tightly connected to the
+population studies, we can easily compare the fitted models to the set of
+existing \gammaray catalogs available in \code{gammapy.catalog}. Further
+multi-wavelength cross-matches are usually required to characterize the
+sources. This an e.g. easily be achieved by relying on coordinate
+handling from Astropy or affiliated packages such as \textit{AstroML}~\citep{astroML}
+or \textit{Astroquery}~\citep{astroquery}.
 

### 2022-11-30 src/ms-review.tex

@@
 microwave background (CMB). We adopted the prescription on the target
-photon fields provided in the naima 
-documentation \footnote{\url{https://naima.readthedocs.io/en/latest/examples.html#crab-nebula-ssc-model}}.
+photon fields provided in the
+documentation of the \textit{Naima} package \url{https://naima.readthedocs.io/en/latest/examples.html#crab-nebula-ssc-model}.
 The best-fit inverse Compton spectrum is represented with a red dashed line in
@@
 the cloud repository service \github. A \github organization
-\textit{gammapy}\footnote{\url{https://\github.com/gammapy}} hosts different
+\textit{gammapy}\footnote{\url{https://github.com/gammapy}} hosts different
 repositories related with the project. The software codebase may be found in
@@
 Several automated tasks are set as \github
-actions\footnote{\url{https://\github.com/features/actions}}, blocking the
+actions\footnote{\url{https://github.com/features/actions}}, blocking the
 processes and alerting developers when fails occur. This is the case of the

### 2022-12-03 src/text/4-project.tex
Add a paragraph about SWH (#67)
* Add the SWH reference

Signed-off-by: Bruno Khelifi <khelifi@in2p3.fr>

* Add the archive in SWH

Signed-off-by: Bruno Khelifi <khelifi@in2p3.fr>

* Delete gammapy-v1.0-paper.iml

* Delete .gitignore

* Delete profiles_settings.xml

* Delete vcs.xml

* Delete Project_Default.xml

* Delete misc.xml

* Delete modules.xml

Signed-off-by: Bruno Khelifi <khelifi@in2p3.fr>

@@
 
+As many other softwares, \gammapy is also indexed in the SoftWare
+Heritage\footenote{\url{https://www.softwareheritage.org/}} (SWH) archive~\cite{DBLP:conf/icms/Cosmo20},
+whom ambition is to collect, preserve, and share all software that is publicly available in source code form.
+SWH automatically scans open software repositories, like e.g. GitHub, and projects are archived in SWH by the
+means of SoftWare Heritage persistent IDentifiers (SWHID), that are guaranteed to remain stable (persistent)
+over time. The French open publication archive, HAL~\footenote{\url{https://hal.archives-ouvertes.fr/}},
+is using the \gammapy SWHIDs to register our releases as scientific
+product\footenote{\url{https://hal.archives-ouvertes.fr/hal-03713410v1}} of open science.
+
 \subsection{Documentation and User-support}

### 2022-12-03 src/ms-review.tex
Move SWH paragraph

--- 2022-11-30 src/ms-review.tex
@@
 
+In addition \gammapy is also listed in the Software
+Heritage\footenote{\url{https://www.softwareheritage.org/}} (SWH) archive~\cite{DBLP:conf/icms/Cosmo20}.
+The archive  collects, preserves, and shares the source code of publicly available software.
+SWH automatically scans open software repositories, like e.g. GitHub, and projects are archived in SWH by the
+means of SoftWare Heritage persistent IDentifiers (SWHID), that are guaranteed to remain stable (persistent)
+over time. The French open publication archive, HAL~\footenote{\url{https://hal.archives-ouvertes.fr/}},
+is using the \gammapy SWHIDs to register the releases as scientific
+products \footenote{\url{https://hal.archives-ouvertes.fr/hal-03713410v1}} of open science.
+
 \subsection{Documentation and User-support}

### 2022-12-03 src/ms-review.tex
Fix latex build

--- 2022-11-30 src/ms-review.tex
@@
 and indexed in the European Open Science Cloud
-catalog\footnote{\url{https://eosc-portal.eu}}.
+catalog \footnote{\url{https://eosc-portal.eu}}.
+
+In addition \gammapy is also listed in the \textit{SoftWare
+Heritage}~\footnote{\url{https://softwareheritage.org}} (SWH) archive~\cite{DiCosmo2020}.
+The archive collects, preserves, and shares the source code of publicly available software.
+SWH automatically scans open software repositories, like e.g. GitHub, and projects are archived in SWH by the
+means of SoftWare Heritage persistent IDentifiers (SWHID), that are guaranteed to remain stable (persistent)
+over time. The French open publication archive, HAL~\footnote{\url{https://hal.archives-ouvertes.fr}},
+is using the \gammapy SWHIDs to register the releases as scientific
+products~\footnote{\url{https://hal.archives-ouvertes.fr/hal-03713410v1}} of open science.
 

### 2022-12-06 src/ms-review.tex

@@
 quantities such as estimated energy, direction and arrival
-times, which is represented by the \code{EventList} class/. Second a set of
+times, which is represented by the \code{EventList} class. Second a set of
 associated IRFs, providing the response of the system, typically
@@
 %
-%	\caption{In Fig.~\ref{ig*:minted:irf_examples}, we show some example of Aeff,
+%	\caption{In Figure~\ref{ig*:minted:irf_examples}, we show some example of Aeff,
 %		PSF, Edisp and BKG read and plotted from a typical \irf.}
@@
 off-axis angles or cartesian detector coordinates. The main information stored in
-the common \gammaray \irfs are the effective area (Aeff), energy dispersion
-(Edisp), point spread function (PSF) and background rate (BKG). The \code{gammapy.irf}
+the common \gammaray \irfs are the effective area, energy dispersion,
+point spread function and background rate. The \code{gammapy.irf}
 sub-package can open and access specific \irf extensions,
@@
 \gammapy provides the class \code{EffectiveAreaTable2D} to
-manage Aeff, which is usually defined in terms of true energy and offset angle.
+manage the effective area, which is usually defined in terms of true energy and offset angle.
 The class functionalities offer the possibility to read from files or to create
-it from scratch. {\code{EffectiveAreaTable2D} can also convert, interpolate,
+it from scratch. {The \code{EffectiveAreaTable2D} class can also convert, interpolate,
 write, and evaluate the effective area for a given energy and offset angles, or
-even plot the multi-dimensional Aeff table.
+even plot the multi-dimensional effective area table.
 
@@
 in particular, parametric multi-dimensional Gaussians (\code{EnergyDependentMultiGaussPSF})
-or King profile functions (\code{PSFKing})
-one. The \code{EnergyDependentMultiGaussPSF} class is able to handle up to three
+or King profile functions (\code{PSFKing}). The \code{EnergyDependentMultiGaussPSF}
+ class is able to handle up to three
 Gaussians, defined in terms of amplitudes and sigma given for each true energy
-and offset angle bin. Similarly, \code{PSFKing takes} into account the gamma and
+and offset angle bin. Similarly, \code{PSFKing} takes into account the gamma and
 sigma parameters. The general \code{ParametricPSF} class allows users to create a
@@
 \subsubsection{Energy Dispersion}
-for \iact, it is generally given in terms of the so-called
+For \iacts, the energy dispersion is typically parameterised in terms of the so-called
 migration parameter ($\mu$), which is defined as the ratio between the
-reconstructed energy and the true energy. This ratio should be as close as one
-and its dispersion can assume the shape of a Gaussian (or even more complex
-distributions). Migration parameter is given at each offset angle and
-reconstructed energy. The main sub-classes are \code{EnergyDispersion2D},
-designed to interpret Edisp, \code{EDispKernelMap}, which builds an Edisp kernel
-map, i.e., a 4-dimensional WCS map where at each sky-position is associated an
-Edisp kernel. The latter is a representation of the Edisp as a function of the
-true energy only thanks to the sub-class \code{EDispKernel}.
+reconstructed energy and the true energy. By definition the mean of this ratio is
+close to unity for a small energy bias and its distribution can 
+be typically described by a Gaussian, however more complex
+shapes are also common. The migration parameter is given at each offset angle and
+reconstructed energy. The main sub-classes are the \code{EnergyDispersion2D} which is
+designed to handle the raw instrument description. Then there is the \code{EDispKernelMap},
+which contains an energy disperion matrix per sky position. I.e., a 4-dimensional WCS map
+where at each sky-position is associated an energy dispersion matrix.
+The latter is a representation of the energy resolution as a function of the
+true energy only repesented by the sub-class \code{EDispKernel}.
 
 \subsubsection{Background model}
-The BKG can be represented in \gammapy as either 1) a 2D map (\code{Background2D})
-of count rate normalised per steradians and energy at different
-reconstructed energies and offset angles or 2) as rate per steradians and energy, as a
+The backgropund rate can be represented in \gammapy as either a 2-dimensional
+data structure (\code{Background2D}) of count rate normalised per steradians and energy at different
+reconstructed energies and offset angles or as rate per steradians and energy, as a
 function of reconstructed energy and detector coordinates (\code{Background3D}).
@@
 model. \gammapy supports a variety of EBL absorbtion models, such as
-
 \cite{Franceschini2008}, \cite{Finke2010} and \cite{Dominguez2011}.
@@
 built-in. We also offer a wrapper to radiative models implemented in the Naima
-package~\cite{naima}. The modeling framework can be easily extended with
+package~\citep{naima}. The modeling framework can be easily extended with
 user-defined models. For example agnpy models that describe leptonic radiative
@@
 The Fit class provides a uniform interface to multiple fitting backends:
-\iminuit~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
-“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
-and errors are computed only for the fitting with \iminuit. However depending on
+
+\begin{itemize}
+	\item \iminuit~\citep{iminuit}
+	\item \code{scipy.optimize}~\citep{2020SciPy-NMeth}
+	\item Sherpa~\citep{sherpa-2011}
+\end{itemize}
+
+Note that, for now, covariance matrixand errors are computed only for the fitting with 
+\iminuit. However depending on
 the problem other optimizers can better perform, so sometimes it can be useful
@@
 shape of the profile is expected at the best fit
-values (\todo{Reference to modeling / fitting section?}).
+values.
 
@@
 
-Code example ~\ref{fig*:minted:gp_estimators} shows how to use
+The code example shown in Figure~\ref{fig*:minted:gp_estimators} shows how to use
 the \code{TSMapEstimator} objects with a given input \code{MapDataset}.
@@
 common use cases identified in \gammaray analyses. The included classes and methods
- can be used in Python scripts, notebooks or as commands within IPython
+ can be used in Python scripts, notebooks or as commands within \texttt{IPython}
 sessions. The HLI can also be used to automatise
@@
 reduction, excess map computation, model fitting, flux points estimation, and
-light curves production. The structure of the \code{Analysis} class allows to define
-custom AnalysisStep, so one could design and configure arbitrarily complex
-workflows. \todo{the latter is not true for v1.0..., include example YAML file?}
+light curves production.
 
@@
 result of such an analysis performed on three simulated CTA observations is
-shown in Fig.~\ref{fig:cta_galactic_center}. In this case the spectrum was
+shown in Figure~\ref{fig:cta_galactic_center}. In this case the spectrum was
 measured in a circular aperture centered on the Galactic Center, in
@@
 The result of the joint fit is displayed in
-Fig.~\ref{fig:multi_instrument_analysis}. We remark that the objective of this
+Figure~\ref{fig:multi_instrument_analysis}. We remark that the objective of this
 exercise is illustrative. We display the flexibility of \gammapy in
@@
 the \gammaray emission, given a physical scenario. Among those
-packages are  Agnpy \citep{agnpy}, Naima \citep{naima}, Jetset \citep{jetset}
-and Gamera \citep{gamera}.
+packages are  Agnpy~\citep{agnpy}, Naima~\citep{naima}, Jetset~\citep{jetset}
+and Gamera~\citep{gamera}.
 Tyically those emission models predict broadband emission from
@@
 photon fields provided in the
-documentation of the \textit{Naima} package \url{https://naima.readthedocs.io/en/latest/examples.html#crab-nebula-ssc-model}.
+documentation of the \textit{Naima} package \footnote{\url{https://naima.readthedocs.io/en/stable/examples.html\#crab-nebula-ssc-model}}.
 The best-fit inverse Compton spectrum is represented with a red dashed line in
-Fig.~\ref{fig:multi_instrument_analysis}.
+Figure~\ref{fig:multi_instrument_analysis}.
 
@@
 suite\footnote{\url{https://pytest.org}} using datasets from the
-\textit{gammapy-data} repository. Tests scan not only the codebase but also the
+\textit{gammapy-data} repository\footnote{\url{https://github.com/gammapy/gammapy-data}}. Tests scan not only the codebase but also the
 code snippets present in docstrings of the scripts and in the RST documentation
@@
 
-Other automated tasks, executing in the \textit{gammapy-benchmarks} repository,
+Other automated tasks, executing in the \textit{gammapy-benchmarks}\footnote{\url{https://github.com/gammapy/gammapy-benchmarks}} repository,
 are responsible for numerical validation tests and benchmarks monitoring. Also
@@
 contribution to the codebase repository triggers the documentation building and
-publishing workflow within the \textit{gammapy-docs} repository
+publishing workflow within the \textit{gammapy-docs} repository\footnote{\url{https://github.com/gammapy/gammapy-docs}}
 (see Sec.~\ref{ssec:software-distribution} and Sec.~\ref{ssec:documentation-and-user-support}).
@@
 notebooks in the repository are tested and published in the \gammapy recipes
-webpage\footnote{\url{https://gammapy.\github.io/gammapy-recipes}} automatically
+webpage\footnote{\url{https://gammapy.github.io/gammapy-recipes}} automatically
 using \github actions.
@@
 messaging\footnote{\url{https://gammapy.slack.com}} and \github
-discussions\footnote{\url{https://\github.com/gammapy/gammapy/discussions}}
+discussions\footnote{\url{https://github.com/gammapy/gammapy/discussions}}
 support forums, providing valuable feedback on the \gammapy functionalities,
@@
 Python scripts to create the figures
-in \url{https://github.com/gammapy/gammapy-v1.0-paper}.
+in an open repository~\footnote{\url{https://github.com/gammapy/gammapy-v1.0-paper}}.
 This \github repository also documents the history of the creation
@@
 manuscript can be reproduced with a single \code{make} command, after
-downloading the source repository. See \url{https://github.com/gammapy/gammapy-v1.0-paper/blob/main/README.md} for detailed
-instructions. Almost all figures in this manuscript provide a link
+downloading the source repository. For this we provide
+detailed instructions online\footnote{\url{https://github.com/gammapy/gammapy-v1.0-paper/blob/main/README.md}}.
+Almost all figures in this manuscript provide a link
 to a Python script, that was used to produce it. This means all

### 2022-12-07 src/ms-review.tex
Remove Fig 1 from paper (#75)

@@
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{figures/big-picture.pdf}
-    \caption{
-        Relation of \gammapy to different \gammaray instruments and the data formats.
-        \gammapy provides access to the data stored in GADF format and the
-        high-level data analysis functionality.}
-	\label{fig:big_picture}
-
-\end{figure*}
-
 Water Cherenkov observatories detect directly particles from the tail of the
@@
 The generic \code{PSF3D} class stores a radial symmetric profile of a
-PSF to represent non-parametric shapes, againa depending on true energy 
+PSF to represent non-parametric shapes, again depending on true energy
 of offset form the poiting position.

### 2022-12-07 src/ms-review.tex
Split section 2 in two subsections

--- 2022-12-06 src/ms-review.tex
@@
 
-In the most general way we can write the expected number of detected events at measured
-position $p$ and energy $E$:
+\subsection{Events and Instrument Response Functions: the Data Level 3}
+
+\gammaray data at the Data Level 3 (DL3) consists in lists of gamma-like events and their
+corresponding instrument response functions (IRFs). The latter include the effective area,
+point spread function (PSF), energy dispersion and residual hadronic background.
+
+In the most general way we can write the expected number of detected events from a given astrophysical source
+of \gammaray at measured position $p$ and energy $E$:
 \begin{align}
@@
 
-\gammaray data at the Data Level 3 (DL3) therefore consists in lists of gamma-like events and their
-corresponding instrument response functions (IRFs). The latter include the aforementioned
-effective area, point spread function (PSF), energy dispersion and residual hadronic background.
-The handling of DL3 data is performed by classes and methods
+An additional component of DL3 IRFs is the residual hadronic background model $$.
+It represents the  intensity of mis-identified charged particles events that are expected
+during an observation. It is defined as a function of the measured position in the field-of-view
+and measured energy.
+
+In total, the expected number of events in a \gammaray observation is given by:
+\begin{align}
+N(p, E) {\rm d}p {\rm d}E =  E_{\rm disp} \star (PSF \star A_{\rm eff} t_{\rm obs} t_{\rm obs}) + Bkg(p, E)
+\end{align}
+
+\subsection{Data analysis workflow}
+
+In Gammapy, the handling of DL3 data is performed by classes and methods
 in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
@@
 a map geometry. The definition of the map geometry typically consists of a spectral dimension
-defined by a binned energy axis and of a spatial dimension, which either defines 
-a spherical projection from celestial coordinates to an pixelised image space
+defined by a binned energy axis and of spatial dimensions, which either define 
+a spherical projection from celestial coordinates to a pixelised image space
 (for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).

### 2022-12-07 src/ms-review.tex
Added links to other subpackages

@@
 
-An additional component of DL3 IRFs is the residual hadronic background model $$.
+An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
 It represents the  intensity of mis-identified charged particles events that are expected
@@
 \begin{align}
-N(p, E) {\rm d}p {\rm d}E =  E_{\rm disp} \star (PSF \star A_{\rm eff} t_{\rm obs} t_{\rm obs}) + Bkg(p, E)
+N(p, E) {\rm d}p {\rm d}E =  E_{\rm disp} \star (PSF \star A_{\rm eff} t_{\rm obs} \Phi) + Bkg(p, E)
 \end{align}
@@
 simulation as well as event sampling to simulate DL3 events data.
+The various DL4 objects and the associated functionalities are
+implemented in the \code{gammapy.datasets} subpackage (see Section~\ref{ssec:gammapy-datasets}).
 
@@
 maps in energy bands.
+The modelling and fitting functionalities are implemented in the \code{gammapy.modeling},
+\code{gammapy.estimators} and \code{gammapy.stats} subpackages (see respectively
+Section~\ref{ssec:gammapy-modeling}, \ref{ssec:gammapy-estimators} and \ref{ssec:gammapy-stats}).
 

### 2022-12-07 src/ms-review.tex
Modified title

@@
 compared to a parametrised model of the true intensity distribution of \gammaray source in a given
-field-of-view, which is "forward folded" through a model of the instrument repsonse
+field-of-view, which is "forward folded" through a model of the instrument response
 to get a prediction for the expected counts measured by the instrument. Parameters
@@
 
-\subsection{Events and Instrument Response Functions: the Data Level 3}
-
-\gammaray data at the Data Level 3 (DL3) consists in lists of gamma-like events and their
-corresponding instrument response functions (IRFs). The latter include the effective area,
-point spread function (PSF), energy dispersion and residual hadronic background.
+\subsection{Predicted counts and Instrument Response Functions}
 
@@
 
+\gammaray data at the Data Level 3 (DL3) therefore consist in lists of gamma-like events and their
+corresponding instrument response functions (IRFs). The latter include the effective area,
+point spread function (PSF) and energy dispersion.
+
 An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
@@
 \end{align}
+
+In practice, the background model is subject to numerous uncertainties and needs to be corrected on the data.
+Frequently, a background model is not even available and the background contribution has to be estimated
+directly from the data.
 
@@
 
-After all data has been projected into the same coordinate system, it is typically
+After all data has been projected into the same geometry, it is typically
 required to improve the residual hadronic background estimate. As residual hadronic

### 2022-12-07 src/ms-review.tex
Correct typo
modify abstract

--- 2022-12-07 src/ms-review.tex
@@
 \abstract{
-	% TODO: the feature are still to detailed and partly copy and pasted form the ICRS abstract...avoid this
-	% context heading (optional)
-	% {} leave it empty if necessary
-	%{Gammapy context:}
-	Historically, the data and the analysis software of \gammaray astronomy experiments are
-	proprietary to the collaborations operating them. The next generation of \gammaray instruments, as the Cherenkov Telescope Array
-	(CTA) will be operated as open observatories, with public
-	data. This introduces the need to have a high-level analysis software available to the astronomical community. In
-	this article we present the first major release of \gammapy, the Long-term Support (LTS) v1.0, a
-	community-developed open-source Python package for \gammaray astronomy. We
-	present its general design and provide an
-	overview of the analysis methods and features it implements. Starting from
-	event lists and a description of the specific instrument response functions
-	(IRF) stored in open FITS based data formats, \gammapy implements the reduction
-	of the input data and instrument response to binned WCS, HEALPix or region based
-	data structures. Thereby it
-	handles the dependency of the IRFs with time, energy as well as position on the
-	sky. It offers a variety of background estimation methods for spectral, spatial
-	and spectro-morphological analysis. Counts, background and IRFs data are
-	bundled in datasets and can be serialised, rebinned and stacked. \gammapy
-	supports to model binned data using Poisson
-	maximum likelihood fitting. It comes with built-in spectral, spatial and
-	temporal models, support for particle radiation emission spectra as well as
-	support for custom user models, to model e.g.,
-	energy dependent morphology of \gammaray sources. Multiple datasets can be
-	combined in a joint-likelihood approach to either handle time dependent IRFs,
-	different classes of events or combination of data from multiple instruments.
-	Gammapy also implements methods to estimate flux points, likelihood
-	profiles per energy bin, light curves as well as flux and signficance maps in
-	energy bins.  We further describe the general
-	development approach and how \gammapy integrates into ecosystem of other
-	scientific and astronomical Python packages. We also present analysis examples
-	with simulated CTA data and provide results of scientific validation analyses
-	using data of existing instruments such as \hess and \fermi.
-
-	% The \gammaray can be considered as the last frontier
-	% In the last two decades the measurement of \gammaray emission from the universe has
-	% evolved from a niche
-
-	% aims heading (mandatory)
-	%{Gammapy aims}
-	%Reproducible analyses, share algorithms etc.
-
-	% methods heading (mandatory)
-	%{Gammapy methods}
-
-	% results heading (mandatory)
-	%{Gammapy results}
-
-	% conclusions heading (optional), leave it empty if necessary
-	%{Gammapy conclusions}
+
+	{Context} In the last two decades the measurement of \gammaray emission from the universe has
+	evolved from a niche area of closed collaborations operating with proprietary data and software into
+	an active and exciting field of astrophysics. The next generation of \gammaray instruments,
+	such as the Cherenkov Telescope Array (CTA), will be operated as open observatories with publicly available
+	data, which will require open high-level astronomy software customised for high energy astrophysics.
+
+	{Aims} In this article, we present the first the Long-term Support (LTS) release of \gammapy v1.0. \gammapy
+	is a community-developed, open-source Python package for \gammaray astronomy. Integrated into the general
+	python eco-system, it is built on Numpy, Scipy and Astropy and uses open FITS based data formats for serialisation.
+	It provides a uniform platform for reduction and modelling of data from many \gammaray instruments.
+
+	{Methods} Starting from event list and instrument response functions at the so called "Data Level 3",
+	\gammapy provides pipelines for reduction of the input data to binned WCS, HEALPix or region based data structures.
+	A variety of background reduction methods, including traditional techniques like the Reflected and Ring regions,
+	as well as novel 3D Field of View Likelihood techniques, are supported. The binned data can then be modelled
+	using Poisson maximum likelihood fitting. While a variety of in-built spectral, temporal and spatial models
+	are supplied, it also supports implementation of custom user defined models. Estimation of flux points, likelihood
+	profiles and light curves are also implemented.
+
+	{Results} The flexible API allows a joint likelihood analysis between different datasets,
+	thus providing a simple platform for handling time dependent instrument responses,
+	different events classes, or combining data from multiple separate instruments. The results are continuously
+	validated with previously published ones. We show analysis examples using open data from various observatories: \fermi., \hess , MAGIC, CTA (simulated),
+	and HAWC. 
 }
@@
 
-\subsection{Events and Instrument Response Functions: the Data Level 3}
-
-\gammaray data at the Data Level 3 (DL3) consists in lists of gamma-like events and their
-corresponding instrument response functions (IRFs). The latter include the effective area,
-point spread function (PSF), energy dispersion and residual hadronic background.
-
-In the most general way we can write the expected number of detected events from a given astrophysical source
-of \gammaray at measured position $p$ and energy $E$:
+In the most general way we can write the expected number of detected events at measured
+position $p$ and energy $E$:
 \begin{align}
@@
 
-An additional component of DL3 IRFs is the residual hadronic background model $$.
-It represents the  intensity of mis-identified charged particles events that are expected
-during an observation. It is defined as a function of the measured position in the field-of-view
-and measured energy.
-
-In total, the expected number of events in a \gammaray observation is given by:
-\begin{align}
-N(p, E) {\rm d}p {\rm d}E =  E_{\rm disp} \star (PSF \star A_{\rm eff} t_{\rm obs} t_{\rm obs}) + Bkg(p, E)
-\end{align}
-
-\subsection{Data analysis workflow}
-
-In Gammapy, the handling of DL3 data is performed by classes and methods
+\gammaray data at the Data Level 3 (DL3) therefore consists in lists of gamma-like events and their
+corresponding instrument response functions (IRFs). The latter include the aforementioned
+effective area, point spread function (PSF), energy dispersion and residual hadronic background.
+The handling of DL3 data is performed by classes and methods
 in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
@@
 a map geometry. The definition of the map geometry typically consists of a spectral dimension
-defined by a binned energy axis and of spatial dimensions, which either define 
-a spherical projection from celestial coordinates to a pixelised image space
+defined by a binned energy axis and of a spatial dimension, which either defines 
+a spherical projection from celestial coordinates to an pixelised image space
 (for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).

### 2023-01-09 src/ms-review.tex
implement cosimo comments
Signed-off-by: Atreyee Sinha <asinha@ucm.es>

@@
 
-	{Context} In the last two decades the measurement of \gammaray emission from the universe has
-	evolved from a niche area of closed collaborations operating with proprietary data and software into
-	an active and exciting field of astrophysics. The next generation of \gammaray instruments,
-	such as the Cherenkov Telescope Array (CTA), will be operated as open observatories with publicly available
-	data, which will require open high-level astronomy software customised for high energy astrophysics.
-
-	{Aims} In this article, we present the first the Long-term Support (LTS) release of \gammapy v1.0. \gammapy
-	is a community-developed, open-source Python package for \gammaray astronomy. Integrated into the general
-	python eco-system, it is built on Numpy, Scipy and Astropy and uses open FITS based data formats for serialisation.
-	It provides a uniform platform for reduction and modelling of data from many \gammaray instruments.
+	{Context} Traditionally, the \gammaray universe has been probed
+	 by small collaborations of scientists employing proprietary data and analysis software.
+	 However, the next generation of \gammaray instruments,
+	 such as the the Cherenkov Telescope Array (CTA), will be operated as open observatories.
+	 Alongside the data, the observatories will make available to the astronomical community
+	 software tools for their analysis. This necessity prompted the development, in the last decade,
+	 of open high-level astronomy software customised for high energy astrophysics.
+
+	{Aims} In this article, we present \gammapy, an open-source python package for the analysis of \gammaray data,
+	and illustrate the functionalities of the first long-term release of the software, version 1.0.
+	Built on the modern python scientific ecosystem, \gammapy provides a uniform platform for reducing and
+	modelling data from different gamma-ray instruments. \gammapy complies with several well-established
+	data conventions in high-energy astrophysics, providing serialised data products that are interoperable
+	with other software.
 
 	{Methods} Starting from event list and instrument response functions at the so called "Data Level 3",
-	\gammapy provides pipelines for reduction of the input data to binned WCS, HEALPix or region based data structures.
-	A variety of background reduction methods, including traditional techniques like the Reflected and Ring regions,
-	as well as novel 3D Field of View Likelihood techniques, are supported. The binned data can then be modelled
-	using Poisson maximum likelihood fitting. While a variety of in-built spectral, temporal and spatial models
-	are supplied, it also supports implementation of custom user defined models. Estimation of flux points, likelihood
-	profiles and light curves are also implemented.
-
-	{Results} The flexible API allows a joint likelihood analysis between different datasets,
-	thus providing a simple platform for handling time dependent instrument responses,
-	different events classes, or combining data from multiple separate instruments. The results are continuously
-	validated with previously published ones. We show analysis examples using open data from various observatories: \fermi., \hess , MAGIC, CTA (simulated),
-	and HAWC. 
+	\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
+	To facilitate the rejection of the hadronic background, several techniques for background estimation
+	 are implemented in the package.
+	 After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
+	 using Poisson maximum likelihood fitting
+	 and assuming a variety of spectral, temporal, and spatial models.
+	  Estimation of flux points, likelihood profiles and light curves are also implemented.
+
+	{Results} After describing the structure of the package, we demonstrate the capabilities of \gammapy
+	performing several traditional analyses in gamma-ray astronomy with publicly available data:
+	spectral and spectro-morphological analyses, estimation of the light curve of a source.
+	The flexibility and power of the software is displayed in a final multi-instrument example,
+	where data sets from different instruments, at different stages of data reduction,
+	are simultaneously fitted with a flux model produced by another astrophysical software.
 }

### 2023-01-16 src/ms-review.tex
Include comments

--- 2022-12-07 src/ms-review.tex
@@
 
-\gammaray data at the Data Level 3 (DL3) therefore consist in lists of gamma-like events and their
-corresponding instrument response functions (IRFs). The latter include the effective area,
-point spread function (PSF) and energy dispersion.
+\gammaray data at the Data Level 3 (DL3) therefore consist of lists of gamma-like events and their
+corresponding instrument response functions (IRFs). The latter include the effective area ($A_{\rm eff}$),
+point spread function (PSF) and energy dispersion ($E_{\rm disp}$).
 
 An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
-It represents the  intensity of mis-identified charged particles events that are expected
+It represents the intensity of charged particles misidentified as gamma-rays that are expected
 during an observation. It is defined as a function of the measured position in the field-of-view
@@
 In practice, the background model is subject to numerous uncertainties and needs to be corrected on the data.
-Frequently, a background model is not even available and the background contribution has to be estimated
+More frequently, a background model is not even available and the background contribution has to be estimated
 directly from the data.
@@
 Data measured at the field-of-view or energy boundaries of the instrument is typically
-associated with a sytematic uncertainty in the IRF. For this reason this part 
+associated with a systematic uncertainty in the IRF. For this reason this part 
 of the data is often excluded from subsequent analysis by defining regions of

### 2023-01-16 src/ms-review.tex
Include Cosimo s suggestions

@@
 shared across the field. They also frequently imply joint analysis of multi-instrument data.
-To extract physically relevant information, the measured counts on an instrument are usually
-compared to a parametrised model of the true intensity distribution of \gammaray source in a given
-field-of-view, which is "forward folded" through a model of the instrument response
-to get a prediction for the expected counts measured by the instrument. Parameters
-of the model are then estimated using statistical techniques such as maximum likelihood
-estimation (MLE).
-
-\subsection{Predicted counts and Instrument Response Functions}
-
-In the most general way we can write the expected number of detected events from a given astrophysical source
-of \gammaray at measured position $p$ and energy $E$:
+
+%\subsection{Predicted counts and Instrument Response Functions}
+
+To extract physically relevant information, such as the flux, spatial or spectral shape of one or more sources,
+an analytical model is commonly adopted to describe the intensity of gamma-ray sources as a function of the energy,
+$E_{true}$, and of the position in the field of view, $p_{true}$:
+$$ \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]} $$
+where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. To convert this analytical flux model
+into a prediction on the number of gamma-ray events, $N_{pred}$, with their estimated energy $E$  and position $p$, the model
+is convolved through the response function of the instrument.
+
+In the most general way we can write the expected number of detected events from the sky model $\Phi$ at measured position $p$ and energy $E$, for
+a given set of parameters $\hat{\theta}$:
 \begin{align}
-   N(p, E) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
-   &\times \Phi(p_{\rm true}, E_{\rm true}) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
+   N(p, E, \hat{\theta}) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
+   &\times \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} )) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
 \end{align}
-where
-\begin{itemize}
-\item $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response
-\item $\Phi(p_{\rm true}, E_{\rm true})$ is the parametrised sky flux model
-\item $t_{\rm obs}$ is the observation time
-\end{itemize}
+where $R(p, E| p_{\rm true}, E_{\rm true}$ is the instrument response and $t_{\rm obs}$ is the observation time
 
@@
 \begin{align}
-N(p, E) {\rm d}p {\rm d}E =  E_{\rm disp} \star (PSF \star A_{\rm eff} t_{\rm obs} \Phi) + Bkg(p, E)
+  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \star \left[ PSF \star \left( A_{\rm eff} \times t_{\rm obs} \times \Phi(\hat{\theta}) \right) \right]\\
+                       & + Bkg(p, E)
 \end{align}
 
-In practice, the background model is subject to numerous uncertainties and needs to be corrected on the data.
-More frequently, a background model is not even available and the background contribution has to be estimated
-directly from the data.
+Finally, predicted and observed events, $N_{obs}$, can be then combined in a likelihood function, $\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\bar{\theta}$.
 

### 2023-01-20 src/ms-review.tex
Apply suggestions from code review
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

--- 2023-01-16 src/ms-review.tex
@@
 \abstract{
-	% TODO: the feature are still to detailed and partly copy and pasted form the ICRS abstract...avoid this
-	% context heading (optional)
-	% {} leave it empty if necessary
-	%{Gammapy context:}
-	Historically, the data and the analysis software of \gammaray astronomy experiments are
-	proprietary to the collaborations operating them. The next generation of \gammaray instruments, as the Cherenkov Telescope Array
-	(CTA) will be operated as open observatories, with public
-	data. This introduces the need to have a high-level analysis software available to the astronomical community. In
-	this article we present the first major release of \gammapy, the Long-term Support (LTS) v1.0, a
-	community-developed open-source Python package for \gammaray astronomy. We
-	present its general design and provide an
-	overview of the analysis methods and features it implements. Starting from
-	event lists and a description of the specific instrument response functions
-	(IRF) stored in open FITS based data formats, \gammapy implements the reduction
-	of the input data and instrument response to binned WCS, HEALPix or region based
-	data structures. Thereby it
-	handles the dependency of the IRFs with time, energy as well as position on the
-	sky. It offers a variety of background estimation methods for spectral, spatial
-	and spectro-morphological analysis. Counts, background and IRFs data are
-	bundled in datasets and can be serialised, rebinned and stacked. \gammapy
-	supports to model binned data using Poisson
-	maximum likelihood fitting. It comes with built-in spectral, spatial and
-	temporal models, support for particle radiation emission spectra as well as
-	support for custom user models, to model e.g.,
-	energy dependent morphology of \gammaray sources. Multiple datasets can be
-	combined in a joint-likelihood approach to either handle time dependent IRFs,
-	different classes of events or combination of data from multiple instruments.
-	Gammapy also implements methods to estimate flux points, likelihood
-	profiles per energy bin, light curves as well as flux and signficance maps in
-	energy bins.  We further describe the general
-	development approach and how \gammapy integrates into ecosystem of other
-	scientific and astronomical Python packages. We also present analysis examples
-	with simulated CTA data and provide results of scientific validation analyses
-	using data of existing instruments such as \hess and \fermi.
-
-	% The \gammaray can be considered as the last frontier
-	% In the last two decades the measurement of \gammaray emission from the universe has
-	% evolved from a niche
-
-	% aims heading (mandatory)
-	%{Gammapy aims}
-	%Reproducible analyses, share algorithms etc.
-
-	% methods heading (mandatory)
-	%{Gammapy methods}
-
-	% results heading (mandatory)
-	%{Gammapy results}
-
-	% conclusions heading (optional), leave it empty if necessary
-	%{Gammapy conclusions}
+
+	{Context} Traditionally, the \gammaray universe has been probed
+	 by small collaborations of scientists employing proprietary data and analysis software.
+	 However, the next generation of \gammaray instruments,
+	 such as the the Cherenkov Telescope Array (CTA), will be operated as open observatories.
+	 Alongside the data, the observatories will make available to the astronomical community
+	 software tools for their analysis. This necessity prompted the development, in the last decade,
+	 of open high-level astronomy software customised for high energy astrophysics.
+
+	{Aims} In this article, we present \gammapy, an open-source python package for the analysis of \gammaray data,
+	and illustrate the functionalities of the first long-term release of the software, version 1.0.
+	Built on the modern python scientific ecosystem, \gammapy provides a uniform platform for reducing and
+	modelling data from different gamma-ray instruments. \gammapy complies with several well-established
+	data conventions in high-energy astrophysics, providing serialised data products that are interoperable
+	with other software.
+
+	{Methods} Starting from event list and instrument response functions",
+	\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
+	To facilitate the handling of the hadronic background, several techniques for background estimation
+	 are implemented in the package.
+	 After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
+	 using Poisson maximum likelihood fitting
+	 and assuming a variety of spectral, temporal, and spatial models.
+	  Estimation of flux points, likelihood profiles and light curves are also implemented.
+
+	{Results} After describing the structure of the package, we demonstrate the capabilities of \gammapy
+	performing several traditional analyses in gamma-ray astronomy with publicly available data:
+	spectral and spectro-morphological analyses, estimation of the light curve of a source.
+	The flexibility and power of the software are displayed in a final multi-instrument example,
+	where data sets from different instruments, at different stages of data reduction,
+	are simultaneously fitted with a flux model produced by another astrophysical software.
 }
@@
 compared to a parametrised model of the true intensity distribution of \gammaray source in a given
-field-of-view, which is "forward folded" through a model of the instrument response
+field-of-view, which is "forward folded" through a model of the instrument repsonse
 to get a prediction for the expected counts measured by the instrument. Parameters
@@
 
-\subsection{Predicted counts and Instrument Response Functions}
-
-In the most general way we can write the expected number of detected events from a given astrophysical source
-of \gammaray at measured position $p$ and energy $E$:
+In the most general way we can write the expected number of detected events at measured
+position $p$ and energy $E$:
 \begin{align}
@@
 
-\gammaray data at the Data Level 3 (DL3) therefore consist of lists of gamma-like events and their
-corresponding instrument response functions (IRFs). The latter include the effective area ($A_{\rm eff}$),
-point spread function (PSF) and energy dispersion ($E_{\rm disp}$).
-
-An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
-It represents the intensity of charged particles misidentified as gamma-rays that are expected
-during an observation. It is defined as a function of the measured position in the field-of-view
-and measured energy.
-
-In total, the expected number of events in a \gammaray observation is given by:
-\begin{align}
-N(p, E) {\rm d}p {\rm d}E =  E_{\rm disp} \star (PSF \star A_{\rm eff} t_{\rm obs} \Phi) + Bkg(p, E)
-\end{align}
-
-In practice, the background model is subject to numerous uncertainties and needs to be corrected on the data.
-More frequently, a background model is not even available and the background contribution has to be estimated
-directly from the data.
-
-\subsection{Data analysis workflow}
-
-In Gammapy, the handling of DL3 data is performed by classes and methods
+\gammaray data at the Data Level 3 (DL3) therefore consists in lists of gamma-like events and their
+corresponding instrument response functions (IRFs). The latter include the aforementioned
+effective area, point spread function (PSF), energy dispersion and residual hadronic background.
+The handling of DL3 data is performed by classes and methods
 in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
@@
 
-After all data has been projected into the same geometry, it is typically
+After all data has been projected into the same coordinate system, it is typically
 required to improve the residual hadronic background estimate. As residual hadronic
@@
 Data measured at the field-of-view or energy boundaries of the instrument is typically
-associated with a systematic uncertainty in the IRF. For this reason this part 
+associated with a sytematic uncertainty in the IRF. For this reason this part 
 of the data is often excluded from subsequent analysis by defining regions of
@@
 simulation as well as event sampling to simulate DL3 events data.
-The various DL4 objects and the associated functionalities are
-implemented in the \code{gammapy.datasets} subpackage (see Section~\ref{ssec:gammapy-datasets}).
 
@@
 maps in energy bands.
-The modelling and fitting functionalities are implemented in the \code{gammapy.modeling},
-\code{gammapy.estimators} and \code{gammapy.stats} subpackages (see respectively
-Section~\ref{ssec:gammapy-modeling}, \ref{ssec:gammapy-estimators} and \ref{ssec:gammapy-stats}).
 

### 2023-01-20 src/code-examples/snippets/gp_datasets.py
Adapt dataset code example

@@ -1,9 +1,10 @@
 from pathlib import Path
+
 from gammapy.datasets import (
+    Datasets,
+    FluxPointsDataset,
     MapDataset,
     SpectrumDatasetOnOff,
-    FluxPointsDataset,
-    Datasets
 )
 
 path = Path("$GAMMAPY_DATA")
@@ -19,13 +20,11 @@ spectrum_dataset = SpectrumDatasetOnOff.read(
 )
 
 flux_points_dataset = FluxPointsDataset.read(
-    path / "tests/spectrum/flux_points/diff_flux_points.fits",
+    path / "hawc_crab/HAWC19_flux_points.fits",
     name="flux-points-dataset",
 )
 
 
-datasets = Datasets([
-    map_dataset, spectrum_dataset, flux_points_dataset
-])
+datasets = Datasets([map_dataset, spectrum_dataset, flux_points_dataset])
 
 print(datasets["map-dataset"])

### 2023-01-20 src/ms-review.tex
Adjust code example font size
Remove fit section todo

@@
 \newcommand{\numpy}{Numpy\xspace}
+\newcommand{\iminuit}{IMinuit\xspace}
+\newcommand{\sherpa}{Sherpa\xspace}
 
@@
 \newcommand{\github}{GitHub\xspace}
-\newcommand{\iminuit}{IMinuit}
 
@@
 %
-\begin{figure}[ht!]
+\begin{figure}
+	\small
 	\import{code-examples/generated/}{gp_data}
@@
 \begin{figure}
+	\small
 	\import{code-examples/generated/}{gp_maps}
@@
 \begin{figure}
+	\small
 	\import{code-examples/generated/}{gp_datasets}
@@
 \begin{figure}
+	\small
     \import{code-examples/generated/}{gp_makers}
@@
 \begin{figure}
+	\small
 	\import{code-examples/generated/}{gp_stats}
@@
 \begin{figure}
+	\small
 	\import{code-examples/generated/}{gp_models}
@@
 
-The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
+The \code{Fit} class provides methods to fit i.e., optimise model parameters and estimate
 parameter errors and correlations. It interfaces with a \code{Datasets} object, which
@@
 
-\todo{Add fit code example...?}
-
-The Fit class provides a uniform interface to multiple fitting backends:
+The \code{Fit} class provides a uniform interface to multiple fitting backends:
 
@@
 	\item \code{scipy.optimize}~\citep{2020SciPy-NMeth}
-	\item Sherpa~\citep{sherpa-2011}
+	\item \sherpa~\citep{sherpa-2011}
 \end{itemize}
 
-Note that, for now, covariance matrixand errors are computed only for the fitting with 
+Note that, for now, covariance matrix and errors are computed only for the fitting with 
 \iminuit. However depending on
@@
 to run a pre-fit with alternative optimization methods. In future we plan to
-extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo.
+extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo methods.
 \footnote{a prototype is available in gammapy-recipes,
@@
 \begin{figure}
+	\small
 	\import{code-examples/generated/}{gp_estimators}
@@
 \begin{figure}
+	\small
 	\import{code-examples/generated/}{gp_catalogs}

### 2023-01-20 src/ms-review.tex
Remov code stats table as it duplicates info from pie chart

@@
 \label{sec:gammaray-data-analysis}
-%
-\begin{figure*}[ht!]
-	\centering
-	\includegraphics[width=1.\textwidth]{figures/irfs.pdf}
-	\caption{
-		Example instrument response functions of some experiments and
-        observatories for which \gammapy can analyse data. The \cta IRFs
-        are from the prod5 production. The \hess IRFs are from the DL3 DR1,
-        using observation ID 033787. The point spread function shows the 65\&
-        containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
-        \todo{Add more instruments? HAWC? MAGIC?}
-    }
-	\label{fig:irfs}
-\end{figure*}
-%
 % This might not be the bast place compared to introduction
@@
 
-Finally, predicted and observed events, $N_{obs}$, can be then combined in a likelihood function, $\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\bar{\theta}$.
+Finally, predicted and observed events, $N_{obs}$, can be then combined in a likelihood function,
+$\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\bar{\theta}$.
 
 \subsection{Data analysis workflow}
-
-In Gammapy, the handling of DL3 data is performed by classes and methods
+%
+\begin{figure*}[h!]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
+	\caption{
+		\gammapy sub-package structure and data analysis workflow. The top row
+        defines the groups for the different data levels and reduction steps
+        from raw gamma-like events on the left, to high level science products
+        on the right. The direction of the data flow is illustrated with the
+        grey arrows. The gray folder icons represent the different sub-packages
+        in \gammapy and their names. Below each icon there is a list of the most
+        important objects defined in the sub-package.
+    }
+	\label{fig:data_flow}
+\end{figure*}
+%
+
+The first step in \gammaray data analysis is the selection and extraction of observations
+based of their metadata including information such as pointing direction, observation
+time and observation conditions. The access to the events data and instrument 
+reponse per observation is supported by classes and methods
 in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
 (see Section~\ref{ssec:gammapy-irf}) subpackages.
-
-The first step in the analysis is the selection and extraction of observations
-based of their metadata including information such as pointing direction, observation
-time and observation conditions.
 
@@
 a spherical projection from celestial coordinates to a pixelised image space
-(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
-The \code{gammapy.maps} subpackage provides general multidimensional geometry objects
-(\code{Geom}) and the associated data structures (\code{Maps}) (see Section~\ref{ssec:gammapy-maps}).
+or a single region on the sky. The \code{gammapy.maps} subpackage provides
+general multidimensional geometry objects and the associated data structures
+(see Section~\ref{ssec:gammapy-maps}).
 
@@
 The counts data and the reduced IRFs in the form of maps are bundled into datasets
-that represent the data level 4 (DL4). Those reduced datasets can be written to disk,
+that represent the fourth data level (DL4). Those reduced datasets can be written to disk,
 in a format specific to \gammapy to allow users to read them back at any time later
 for modeling and fitting. Different variations of such datasets support different 
-analysis methods and fit statistics (e.g. Poisson statistics with known background or
-with OFF background measurements). The datasets are used to perform joint-likelihood
+analysis methods and fit statistics. The datasets are used to perform joint-likelihood
 fitting allowing to combine different measurements, e.g. from different observations
@@
 %
-\begin{figure*}[ht!]
-	\centering
-	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
-	\caption{
-		\gammapy sub-package structure and data analysis workflow. The top row
-        defines the groups for the different data levels and reduction steps
-        from raw gamma-like events on the left, to high level science products
-        on the right. The direction of the data flow is illustrated with the
-        grey arrows. The gray folder icons represent the different sub-packages
-        in \gammapy and their names. Below each icon there is a list of the most
-        important objects defined in the sub-package.
-    }
-	\label{fig:data_flow}
-\end{figure*}
 %
@@
 %
-%\begin{figure}
-%	%	\import{code-examples/generated/}{gp_makers}
-%
-%	\caption{In Figure~\ref{ig*:minted:irf_examples}, we show some example of Aeff,
-%		PSF, Edisp and BKG read and plotted from a typical \irf.}
-%	\label{ig*:minted:irf_examples}
-%\end{figure}
+%
+\begin{figure*}[ht!]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/irfs.pdf}
+	\caption{
+		Using \code{gammapy.irf} to read and plot instrument repsonse functions.
+		Here we show example instrument response functions of some experiments and
+        observatories for which \gammapy can analyse data. The \cta IRFs
+        are from the prod5 production. The \hess IRFs are from the DL3 DR1,
+        using observation ID 033787. The point spread function shows the 65\&
+        containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
+    }
+	\label{fig:irfs}
+\end{figure*}
+%
 %
@@
 
-\subsubsection{Background model}
-The backgropund rate can be represented in \gammapy as either a 2-dimensional
+\subsubsection{Instrumental Background}
+The instrumental backgropund rate can be represented in \gammapy as either a 2-dimensional
 data structure (\code{Background2D}) of count rate normalised per steradians and energy at different
@@
 while in the latter, it can be more complex.
+
+Some example IRFs that are read and plotted with \gammapy are show in Figure~\ref{fig:irfs}.
 
@@
 
-\begin{figure*}[t]
+\begin{figure*}
 	\centering
@@
 \label{ssec:3d-analysis}
-The 1D analysis approach is a powerful tool to measure the spectrum of an
-isolated source. However, more complicated situations require a more careful
-treatment. In a field of view containing several overlapping sources, the 1D
-approach cannot disentangle the contribution of each source to the total flux in
-the selected region. Sources with extended or complex morphology can result in
-the measured flux being underestimated, and heavily dependent on the choice of
-extraction region. Additionally, the 1D approach neglects the energy-dependence
-of the PSF.
-
-For such situations a more complex approach is needed, the so-called 3D
-analysis. The three relevant dimensions are the two spatial angular coordinates
-and an energy axis. In this framework, a combined spatial and spectral model
-(that is, a \code{SkyModel}, see Section~\ref{ssec:gammapy-modeling}) is fitted to the
-sky maps that were previously derived from the data reduction step and bundled into a
-\code{MapDataset} (see Sections~\ref{ssec:gammapy-makers} and~\ref{ssec:gammapy-datasets}).
-
-A thorough description of the 3D analysis approach and multiple examples that
-use \gammapy can be found in~\cite{Mohrmann2019}. Here we present a short
-example to highlight some of its advantages.
-
-Starting from the \irfs corresponding to the same three simulated \cta
-observations used in Section~\ref{ssec:1d-analysis}, we can create a \code{MapDataset}
-via the \code{MapDatasetMaker}. However, we will not use the simulated event lists
-provided by \cta but instead, use the method \code{MapDataset.fake()} to simulate
-measured counts from the combination of several \code{SkyModel} instances. In this
-way, a DL4 dataset can directly be simulated. In particular we simulate:
-
-\begin{enumerate}
-    \item A point source located at (l=0\textdegree, b=0\textdegree) with a power law
-	      spectral shape.
-    \item An extended source with Gaussian morphology located at (l=0.4\textdegree,
-	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log parabola spectral
-	      shape.
-    \item A large shell-like structure centered around (l=0.06\textdegree,
-	      b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree
-	      respectively and a power law spectral shape.
-\end{enumerate}
-
-The position and sizes of the sources
-have been selected so that their contributions overlap. This can be clearly
-seen in the significance map shown in the left panel of
-Figure~\ref{fig:cube_analysis}. This map was produced with the
-\code{ExcessMapEstimator} (see Section~\ref{ssec:gammapy-estimators}) with a
-correlation radius of 0.1\textdegree.
-
-We can now fit the same model shapes to the simulated data and retrieve the
-best-fit parameters. To check the model agreement, we compute the residual
-significance map after removing the contribution from each model. This is done
-again via the \code{ExcessMapEstimator}. As can be seen in the middle panel of
-Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$,
-meaning that the models describe the data sufficiently well.
-
-As the example above shows, the 3D analysis allows to characterize the
-morphology of the emission and fit it together with the spectral properties of
-the source.  Among the advantages that this provides is the ability to
-disentangle the contribution from overlapping sources to the same spatial
-region. To highlight this, we define a circular \code{RegionGeom} of radius
-0.5\textdegree~ centered around the position of the point source, which is drawn
-in the left panel of Figure~\ref{fig:cube_analysis}. We can now compare the
-measured excess counts integrated in that region to the expected relative
-contribution from each of the three source models. The result can be seen in the left
-panel of Figure~\ref{fig:cube_analysis}.
-
+%
 \begin{figure*}[t]
@@
 \end{figure*}
+%
+The 1D analysis approach is a powerful tool to measure the spectrum of an
+isolated source. However, more complicated situations require a more careful
+treatment. In a field of view containing several overlapping sources, the 1D
+approach cannot disentangle the contribution of each source to the total flux in
+the selected region. Sources with extended or complex morphology can result in
+the measured flux being underestimated, and heavily dependent on the choice of
+extraction region. Additionally, the 1D approach neglects the energy-dependence
+of the PSF.
+
+For such situations a more complex approach is needed, the so-called 3D
+analysis. The three relevant dimensions are the two spatial angular coordinates
+and an energy axis. In this framework, a combined spatial and spectral model
+(that is, a \code{SkyModel}, see Section~\ref{ssec:gammapy-modeling}) is fitted to the
+sky maps that were previously derived from the data reduction step and bundled into a
+\code{MapDataset} (see Sections~\ref{ssec:gammapy-makers} and~\ref{ssec:gammapy-datasets}).
+
+A thorough description of the 3D analysis approach and multiple examples that
+use \gammapy can be found in~\cite{Mohrmann2019}. Here we present a short
+example to highlight some of its advantages.
+
+Starting from the \irfs corresponding to the same three simulated \cta
+observations used in Section~\ref{ssec:1d-analysis}, we can create a \code{MapDataset}
+via the \code{MapDatasetMaker}. However, we will not use the simulated event lists
+provided by \cta but instead, use the method \code{MapDataset.fake()} to simulate
+measured counts from the combination of several \code{SkyModel} instances. In this
+way, a DL4 dataset can directly be simulated. In particular we simulate:
+
+\begin{enumerate}
+    \item A point source located at (l=0\textdegree, b=0\textdegree) with a power law
+	      spectral shape.
+    \item An extended source with Gaussian morphology located at (l=0.4\textdegree,
+	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log parabola spectral
+	      shape.
+    \item A large shell-like structure centered around (l=0.06\textdegree,
+	      b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree
+	      respectively and a power law spectral shape.
+\end{enumerate}
+
+The position and sizes of the sources
+have been selected so that their contributions overlap. This can be clearly
+seen in the significance map shown in the left panel of
+Figure~\ref{fig:cube_analysis}. This map was produced with the
+\code{ExcessMapEstimator} (see Section~\ref{ssec:gammapy-estimators}) with a
+correlation radius of 0.1\textdegree.
+
+We can now fit the same model shapes to the simulated data and retrieve the
+best-fit parameters. To check the model agreement, we compute the residual
+significance map after removing the contribution from each model. This is done
+again via the \code{ExcessMapEstimator}. As can be seen in the middle panel of
+Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$,
+meaning that the models describe the data sufficiently well.
+
+As the example above shows, the 3D analysis allows to characterize the
+morphology of the emission and fit it together with the spectral properties of
+the source.  Among the advantages that this provides is the ability to
+disentangle the contribution from overlapping sources to the same spatial
+region. To highlight this, we define a circular \code{RegionGeom} of radius
+0.5\textdegree~ centered around the position of the point source, which is drawn
+in the left panel of Figure~\ref{fig:cube_analysis}. We can now compare the
+measured excess counts integrated in that region to the expected relative
+contribution from each of the three source models. The result can be seen in the left
+panel of Figure~\ref{fig:cube_analysis}.
 
@@
 
-\begin{table}
-	\import{tables/generated/}{codestats}
-	\caption{
-        Overview of used programming languages and distribution of code across the different file
-        categories in the \gammapy code base. The most right column list the total number of lines
-        in a file. The \textit{comment} column lists the number of comments in the files
-        (including method and class docstrings), the \textit{blank} column lists the
-        number of blank lines in the file. The uppermost rows distinguish between
-        code that implements actual functionality and code the implements tests.
-        All documentataion in \gammapy is implemented as dosctrings, \text{reStructuredText} (RST)
-        files or notebooks.
-    }
-	\label{table:codestats:data}
-\end{table}
+% \begin{table}
+% 	\import{tables/generated/}{codestats}
+% 	\caption{
+%         Overview of used programming languages and distribution of code across the different file
+%         categories in the \gammapy code base. The most right column list the total number of lines
+%         in a file. The \textit{comment} column lists the number of comments in the files
+%         (including method and class docstrings), the \textit{blank} column lists the
+%         number of blank lines in the file. The uppermost rows distinguish between
+%         code that implements actual functionality and code the implements tests.
+%         All documentataion in \gammapy is implemented as dosctrings, \text{reStructuredText} (RST)
+%         files or notebooks.
+%     }
+% 	\label{table:codestats:data}
+% \end{table}
 
@@
 		Overview of used programming languages and distribution of code across the different file
-        categories in the \gammapy code base.
+        categories in the \gammapy code base. The total number of lines is $\approx 50 000$.
     } \label{fig:codestats:lang}

### 2023-01-20 src/figures/big_picture.py
Add big picture figure

@@ -1,0 +1,319 @@
+import logging
+
+import click
+import config
+import matplotlib
+import matplotlib.lines as mlines
+import matplotlib.pyplot as plt
+import matplotlib.transforms as mtrans
+import numpy as np
+from astropy import units as u
+from astropy.table import Table
+from matplotlib.patches import FancyArrow, FancyArrowPatch, PathPatch, Polygon
+from matplotlib.text import TextPath
+from matplotlib.ticker import MultipleLocator
+
+from gammapy.estimators import FluxPoints
+from gammapy.maps import Map
+
+logging.basicConfig(level=logging.INFO)
+log = logging.getLogger(__name__)
+
+plt.rcParams["mathtext.fontset"] = "cm"
+
+FIGSIZE = config.FigureSizeAA(aspect_ratio=1.8, width_aa="two-column")
+
+
+GRAY = (0.7, 0.7, 0.7)
+LIGHT_GRAY = "#ECECEC"
+GP_GRAY = "#3D3D3D"
+GP_ORANGE = "#FC3617"
+
+DOC_ICON = np.array([(0, 0), (0, 0.85), (0.15, 1), (0.75, 1), (0.75, 0)])
+
+
+def axis_to_fig(axis):
+    fig = axis.figure
+
+    def transform(coord):
+        return fig.transFigure.inverted().transform(axis.transData.transform(coord))
+
+    return transform
+
+
+def add_sub_axes(axis, rect):
+    fig = axis.figure
+    left, bottom, width, height = rect
+    trans = axis_to_fig(axis)
+    figleft, figbottom = trans((left, bottom))
+    figwidth, figheight = trans([width, height]) - trans([0, 0])
+    return fig.add_axes([figleft, figbottom, figwidth, figheight])
+
+
+def plot_arrow(ax, offset, dx=10, dy=0, **kwargs):
+    kwargs.setdefault("fc", GP_GRAY)
+    kwargs.setdefault("ec", "None")
+    kwargs.setdefault("head_width", 3)
+    kwargs.setdefault("head_length", 3)
+    kwargs.setdefault("length_includes_head", True)
+    kwargs.setdefault("width", 1)
+
+    arrow = FancyArrow(
+        offset[0], offset[1], dx=dx, dy=dy, transform=ax.transData, **kwargs
+    )
[…]

### 2023-01-23 src/ms-review.tex
Add big picture figure
Add Fig 1 caption

@@
 
-\abstract{
-
-	{Context} Traditionally, the \gammaray universe has been probed
+\abstract
+	{
+		Traditionally, the \gammaray universe has been probed
 		by small collaborations of scientists employing proprietary data and analysis software.
@@
 		of open high-level astronomy software customised for high energy astrophysics.
-
-	{Aims} In this article, we present \gammapy, an open-source python package for the analysis of \gammaray data,
+	}
+	{
+		In this article, we present \gammapy, an open-source python package for the analysis of \gammaray data,
 		and illustrate the functionalities of the first long-term release of the software, version 1.0.
@@
 		with other software.
-
-	{Methods} Starting from event list and instrument response functions",
+	}
+	{
+		Starting from event list and instrument response functions",
 		\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
@@
 		Estimation of flux points, likelihood profiles and light curves are also implemented.
-
-	{Results} After describing the structure of the package, we demonstrate the capabilities of \gammapy
+	}
+	{
+		After describing the structure of the package, we demonstrate the capabilities of \gammapy
 		performing several traditional analyses in gamma-ray astronomy with publicly available data:
@@
 		are simultaneously fitted with a flux model produced by another astrophysical software.
-}
+	}{}
 
@@
 good energy and angular resolution \citep{2015CRPhy..16..610D}.
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/big-picture.pdf}
+	\caption{
+		Core idea and relation of \gammapy to different \gammaray instruments
+		and the gamma astro data formats (GADF). The top left shows the
+		group of current and future pointing instruments based on the 
+		imaging atmospheric Cherenkov technique (IACT). This includes
+		instruments such as the  Cherenkov Telescope Array (CTA),
+		the High Energy Stereoscopic System (H.E.S.S.), the
+		Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC),
+		and the Very Energetic Radiation Imaging Telescope Array System (VERITAS).
+		The lower left shows the group of allsky instruments such as the
+		Fermi Large Area Telescope (Fermi-LAT) amd the High Altitude 
+		Water Cherencov Observatory (HAWC). The calibrated data of all those
+		instruments can be converted and stored into the common GADF data format.
+		\gammapy can read data stored in the GADF format.
+		The \gammapy package is not a part of any instrument, but instead
+		provides a common interface to the data and analysis of all
+		these \gammaray instruments. This way users can also easily combine data from
+		different instruments and perform a joint analysis. 
+	}
+	\label{fig:big_picture}
+
+\end{figure*}
 

### 2023-01-23 src/code-examples/snippets/gp_datasets.py
Fix datasets code example format

@@ -25,6 +25,10 @@ flux_points_dataset = FluxPointsDataset.read(
 )
 
 
-datasets = Datasets([map_dataset, spectrum_dataset, flux_points_dataset])
+datasets = Datasets([
+    map_dataset,
+    spectrum_dataset,
+    flux_points_dataset
+])
 
 print(datasets["map-dataset"])

### 2023-01-23 src/figures/big_picture.py
Adapt Fig 1 arrow positions

@@ -302,7 +302,7 @@ def main(draft=True):
     kwargs["head_length"] = 3
     kwargs["length_includes_head"] = True
     width = 2
-    plot_arrow(ax, offset=(50, 65), dx=15, dy=-10, width=width, fc=GRAY, **kwargs)
+    plot_arrow(ax, offset=(46, 69), dx=19, dy=-14, width=width, fc=GRAY, **kwargs)
 
     plot_arrow(ax, offset=(50, 25), dx=15, dy=20, width=width, fc=GRAY, **kwargs)
 
@@ -367,9 +367,9 @@ def main(draft=True):
     kwargs["head_length"] = 3
     kwargs["length_includes_head"] = True
     width = 2
-    plot_arrow(ax, offset=(130, 55), dx=16, dy=20, width=width, fc=GRAY, **kwargs)
+    plot_arrow(ax, offset=(130, 55), dx=16, dy=15, width=width, fc=GRAY, **kwargs)
     plot_arrow(ax, offset=(130, 50), dx=16, dy=0, width=width, fc=GRAY, **kwargs)
-    plot_arrow(ax, offset=(130, 45), dx=14, dy=-20, width=width, fc=GRAY, **kwargs)
+    plot_arrow(ax, offset=(130, 45), dx=14, dy=-15, width=width, fc=GRAY, **kwargs)
 
     filename = "big-picture.pdf"
     log.info(f"Writing {filename}")

### 2023-01-24 src/ms-review.tex

@@
 \section{Gamma-ray Data Analysis}
+%
+\begin{figure*}[h!]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
+	\caption{
+		\gammapy sub-package structure and data analysis workflow. The top row
+        defines the groups for the different data levels and reduction steps
+        from raw gamma-like events on the left, to high level science products
+        on the right. The direction of the data flow is illustrated with the
+        grey arrows. The gray folder icons represent the different sub-packages
+        in \gammapy and their names. Below each icon there is a list of the most
+        important objects defined in the sub-package.
+    }
+	\label{fig:data_flow}
+\end{figure*}
+%
 \label{sec:gammaray-data-analysis}
@@
 \subsection{Data analysis workflow}
-%
-\begin{figure*}[h!]
-	\centering
-	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
-	\caption{
-		\gammapy sub-package structure and data analysis workflow. The top row
-        defines the groups for the different data levels and reduction steps
-        from raw gamma-like events on the left, to high level science products
-        on the right. The direction of the data flow is illustrated with the
-        grey arrows. The gray folder icons represent the different sub-packages
-        in \gammapy and their names. Below each icon there is a list of the most
-        important objects defined in the sub-package.
-    }
-	\label{fig:data_flow}
-\end{figure*}
-%
-
 The first step in \gammaray data analysis is the selection and extraction of observations

### 2023-01-25 src/ms-review.tex
proof intro
Signed-off-by: Atreyee Sinha <asinha@ucm.es>

@@
 	{
-		Starting from event list and instrument response functions",
+		Starting from event list and "instrument response functions",
 		\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
-		To facilitate the handling of the hadronic background, several techniques for background estimation
+		To facilitate the rejection of the residual hadronic background, several techniques for background estimation
 		are implemented in the package.
@@
 		and assuming a variety of spectral, temporal, and spatial models.
-		Estimation of flux points, likelihood profiles and light curves are also implemented.
+		Estimation of flux points, likelihood profiles and light curves is also implemented.
 	}
@@
 		After describing the structure of the package, we demonstrate the capabilities of \gammapy
-		performing several traditional analyses in gamma-ray astronomy with publicly available data:
+		performing both traditional and novel analyses in gamma-ray astronomy with publicly available data:
 		spectral and spectro-morphological analyses, estimation of the light curve of a source.
@@
 \gammaray astronomy is a rather young field of research. The \gammaray~
-range of the electromagnetic spectrum provides us with insight to the
-most energetic process in the universe such as surroundings of
+range of the electromagnetic spectrum provides us with insight into the
+most energetic processes in the universe such as surroundings of
 black holes and remnants of supernova explosions. As in other
@@
 create a large shower of secondary particles that can be observed from the ground.
-Ground-based \gammaray astronomy relies on this phenomenon to detect the
+Ground-based \gammaray astronomy relies on these extensive air showers to detect the
 primary \gammaray photons and measure their direction and energy.
@@
 		different instruments and perform a joint analysis.
+		\gammapy is built on the scientific python eco-system, and the required dependencies
+		are shown below the \gammapy logo.
 	}
@@
 
-Water Cherenkov observatories detect directly particles from the tail of the
+Water Cherenkov observatories detect particles directly from the tail of the
 shower when it reaches the ground. These instruments have very
@@
 on their own proprietary data and analysis software developed as part of the
-instrument. While this model has been very successful so far, it does not
-permit easy combination of data from several instruments and therefore
+instrument. While this model has been successful so far, it does not
+permit easy combination of data from several instruments and therefore,
 limits the interoperability of existing facilities. This lack of
-interoperability currently limits the full explotation of the
-available \gammaray data, especially because the different detection
+interoperability currently limits the full exploitation of the
+available \gammaray data, especially because the different instruments often have
+complementary sky coverages, and the various detection
 techniques have complementary properties in terms of covered energy rage,
-dutu cycle and spatial resolution.
+duty cycle and spatial resolution.
 
@@
 as an open observatory in the domain. Its high level data (e.g. the event list) will be shared publicly after
-some proprietary period and the software required to analyze it will be distributed
+some proprietary period, and the software required to analyze it will be distributed
 as well. To allow the re-usability of existing instruments and their interoperability
@@
 or light curves, taking into account the observatory specific instrument response functions (IRF).
-One the data is present in the form of a list of events, the information is independent on
+Once the data is present in the form of a list of events, the information is independent of
 the data reduction process, and eventually of the detection technique. This implies,
@@
 initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
-\texttt{gamma-astro-data-format} (\gadf). The latter proposes prototypical
+\texttt{gamma-astro-data-format} (\gadf). This proposes prototypical
 specifications to produce files based on the flexible image transport system
@@
 %% Context: develoment of open software
-Python has become extremely popular as a scientific programming language
-in particular in the field of data sciences. The success is
+Python has become extremely popular as a scientific programming language,
+in particular, in the field of data sciences. The success is
 mostly attributed to the simple and easy to learn syntax, the ability to act as
@@
 The \astropy~\citep{astropy} was created in 2012 to build a community-developed
-Python package for astronomical reasearch. Among other things, it offers functionalities for
+Python package for astronomical research. Among other things, it offers functionalities for
 transforming and representing astronomical coordinates, manipulating physical quantities
@@
 observations taken between 2004 and 2008) based  on the \gadf DL3 format \citep{HESS_DR1}.
-This data release served as a basis for analysis tools validation \cite[see e.g.]{Mohrmann2019}.
+This data release served as a basis for validation of open analysis tools,
+including \gammapy \cite[see e.g.]{Mohrmann2019}.
 
@@
 
-The counts data and the reduced IRFs in the form of maps are bundled into datasets
-that represent the fourth data level (DL4). Those reduced datasets can be written to disk,
+The counts data and the reduced IRFs in the form of maps are bundled into "datasets"
+that represent the fourth data level (DL4). These reduced datasets can be written to disk,
 in a format specific to \gammapy to allow users to read them back at any time later
@@
 individually, or in a joint likelihood analysis. For this purpose \gammapy
-provides a uniform interface to multiple fitting backends. It also provides
-a variety of built in models. This includes spectral,
-spatial and temporal model classes to describe the \gammaray emission in the sky.
-Where spectral models can be simple analytical models or more complex ones from radiation
+provides a uniform interface to multiple fitting backends. In addition to
+providing a variety of built in models, including spectral,
+spatial and temporal model classes to describe the \gammaray emission in the sky,
+custom user-defined models are also supported.
+Spectral models can be simple analytical models or more complex ones from radiation
 mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{o}$ decay).
@@
 \code{gammapy.modeling}, are used to jointly model a combination
-of datasets for example to create source catalogs. Estimator classes,
+of datasets, for example, to create source catalogs. Estimator classes,
 which are contained in \code{gammapy.estimators} are used to

### 2023-01-25 src/ms-review.tex

@@
 \newcommand{\sherpa}{Sherpa\xspace}
+\newcommand{\agnpy}{Agnpy\xspace}
 
@@
 Binned maps and datasets, which represent a collection of binned
-maps are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
+maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
 sub-packages respectively. Parametric models, which are defined in
@@
 DL3 data are typically bundled into individual observations, which
-corresponds to stable periods of data aqusition. For IACT data analysis,
-for which the GADF data model and Gammapy were initially conceived for,
+corresponds to stable periods of data acquisition. For IACT data analysis,
+for which the GADF data model and Gammapy were initially conceived,
 these are usually $20 - 30\,{\rm min}$ long.
@@
 The DL3 level data represented by the \code{Observation} class consist
-of two types of elements: first a list of \gammaray events with relevant physical
+of two types of elements: first, a list of \gammaray events with relevant physical
 quantities such as estimated energy, direction and arrival
-times, which is represented by the \code{EventList} class. Second a set of
+times, which is represented by the \code{EventList} class. Second, a set of
 associated IRFs, providing the response of the system, typically
@@
 (already compliant with the \gadf specifications) and then find the appropriate
-IRF class representing the response functions provided by \fermi, see
+IRF classes representing the response functions provided by \fermi, see
 example in Section~\ref{ssec:multi-instrument-analysis}.
@@
 PSF to represent non-parametric shapes, again depending on true energy
-of offset form the poiting position.
+of offset form the pointing position.
 
@@
 looked up at its current position and converted into a 3d convolution kernel
-which used for the prediction of counts from that model component.
+which is used for the prediction of counts from that model component.
 
@@
 migration parameter ($\mu$), which is defined as the ratio between the
-reconstructed energy and the true energy. By definition the mean of this ratio is
+reconstructed energy and the true energy. By definition, the mean of this ratio is
 close to unity for a small energy bias and its distribution can 
-be typically described by a Gaussian, however more complex
+be typically described by a Gaussian. However, more complex
 shapes are also common. The migration parameter is given at each offset angle and
 reconstructed energy. The main sub-classes are the \code{EnergyDispersion2D} which is
-designed to handle the raw instrument description. Then there is the \code{EDispKernelMap},
+designed to handle the raw instrument description, and the \code{EDispKernelMap},
 which contains an energy disperion matrix per sky position. I.e., a 4-dimensional WCS map
@@
 The latter is a representation of the energy resolution as a function of the
-true energy only repesented by the sub-class \code{EDispKernel}.
+true energy only represented by the sub-class \code{EDispKernel}.
 
 \subsubsection{Instrumental Background}
-The instrumental backgropund rate can be represented in \gammapy as either a 2-dimensional
+The instrumental background rate can be represented in \gammapy as either a 2-dimensional
 data structure (\code{Background2D}) of count rate normalised per steradians and energy at different
@@
 Map axes can have physical units attached to them, as well as define
-non-lineary spaced bins. The special case of time is covered by the
+non-linearly spaced bins. The special case of time is covered by the
 dedicated \code{TimeMapAxis}, which allows time bins to be non-contiguous,
@@
 modeling and fitting purposes. Depending upon the type of analysis and the
-associated statistics, different types of Datasets are supported. \code{MapDataset} is
+associated statistic, different types of Datasets are supported. \code{MapDataset} is
 used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
@@
         the configuration on initialisation of the class. They 
-		also consitently define \code{.run()} methods, which take 
+		also consistently define \code{.run()} methods, which take
 		a dataset object and optionally an \code{Observation} 
@@
 domain is determined by the \code{SafeMaskMaker}. It can be used to limit the
-extent of the field of view used or to limit the energy range to, e.g., a domain
+extent of the field of view used, or to limit the energy range to, e.g., a domain
 where the energy reconstruction bias is below a given value.
@@
 \gammaray spectra caused by the extra-galactic background light (EBL) (\code{EBLAbsorptionNormSpectralModel})
-model. \gammapy supports a variety of EBL absorbtion models, such as
+model. \gammapy supports a variety of EBL absorption models, such as
 \cite{Franceschini2008}, \cite{Finke2010} and \cite{Dominguez2011}.
@@
 package~\citep{naima}. The modeling framework can be easily extended with
-user-defined models. For example agnpy models that describe leptonic radiative
+user-defined models. For example, \agnpy models that describe leptonic radiative
 processes in jetted Active Galactic Nuclei (AGN) can be wrapped into
@@
     parameters can be defined as strings with attached units. The spatial model
-    takes an addtional \code{frame} parameter which allow users to define
+    takes an additional \code{frame} parameter which allow users to define
     the coordinate frame of the position of the model.
@@
 
-Optionally it can also compute more advanced quantities
-such as assymmetric flux errors, flux upper limits
+Optionally, it can also compute more advanced quantities
+such as asymmetric flux errors, flux upper limits
 and one dimensional profiles of the fit statistic,
@@
 the flux norm parameter around the fit minimum.
-This information is useful for inspecting the quality
-of a fit, for which asymptomatically a parabolic
-shape of the profile is expected at the best fit
+This information is useful in inspecting the quality
+of a fit, for which  a parabolic
+shape of the profile is asymptomatically expected at the best fit
 values.
@@
 The actual flux values for each SED type are obtained
-by mutiplication of the norm with the  reference flux.
+by multiplication of the norm with the  reference flux.
 
@@
 computing Lomb-Scargle periodograms or Bayesian
-blocks for time series. So far \gammapy does not
+blocks for time series. So far, \gammapy does not
 support 'unfolding' of \gammaray spectra.
@@
 the \code{TSMapEstimator} objects with a given input \code{MapDataset}.
-In addition to the model it allows to specify the energy
+In addition to the model, it allows to specify the energy
 bins of the resulting flux and TS maps.
@@
 four main steps: data reduction; object detection; model fitting and model
-selection; associations and classification. All steps can be either be done
-with \gammapy directly or by relying on the seemless integration 
+selection; associations and classification. All steps can either be done directly
+with \gammapy or by relying on the seamless integration
 of \gammapy with the scientific Python ecosystem. This allows to rely
-on 3rd functionality wherever needed.
+on 3rd party functionality wherever needed.
 
@@
 of developers from the contributing institutions is in charge of the regular
-development, which benefits from punctual contributions of the community at
+development, which benefits from regular contributions of the community at
 large.
@@
 suite\footnote{\url{https://pytest.org}} using datasets from the
-\textit{gammapy-data} repository\footnote{\url{https://github.com/gammapy/gammapy-data}}. Tests scan not only the codebase but also the
+\textit{gammapy-data} repository\footnote{\url{https://github.com/gammapy/gammapy-data}}.
+Tests scan not only the codebase, but also the
 code snippets present in docstrings of the scripts and in the RST documentation
@@
 
-Other automated tasks, executing in the \textit{gammapy-benchmarks}\footnote{\url{https://github.com/gammapy/gammapy-benchmarks}} repository,
-are responsible for numerical validation tests and benchmarks monitoring. Also
+Other automated tasks, executing in the
+\textit{gammapy-benchmarks}\footnote{\url{https://github.com/gammapy/gammapy-benchmarks}} repository,
+are responsible for numerical validation tests and benchmarks monitoring. Also,
 tasks related with the release process are partially automated, and every
 contribution to the codebase repository triggers the documentation building and
-publishing workflow within the \textit{gammapy-docs} repository\footnote{\url{https://github.com/gammapy/gammapy-docs}}
+publishing workflow within the
+\textit{gammapy-docs} repository\footnote{\url{https://github.com/gammapy/gammapy-docs}}
 (see Sec.~\ref{ssec:software-distribution} and Sec.~\ref{ssec:documentation-and-user-support}).

### 2023-01-26 src/figures/codestats.py
Adjust the fig size
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@ -125,10 +125,10 @@ def make_pie():
     # code
     df = df.sort_values(by=["code"])[::-1]
     sdf = shorthen_df(df)
-    sdf.plot(ax=ax, kind="pie", y="code", autopct=fix_autopct, legend=False, fontsize=8)
+    sdf.plot(ax=ax, kind="pie", y="code", autopct=fix_autopct, legend=False, fontsize=8, radius=0.8)
     plt.ylabel("")
     plt.savefig("codestats.pdf")
-    logging.info("Piecharf file codestats.pdf created.")
+    logging.info("Piechart file codestats.pdf created.")
 
     # files
     # sdf = sdf.sort_values(by=["files"])[::-1]

### 2023-01-26 src/ms-review.tex
Fix typos and links
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 \usepackage[utf8]{inputenc}
+\usepackage{hyperref}
 
@@
 		Traditionally, the \gammaray universe has been probed
-		by small collaborations of scientists employing proprietary data and analysis software.
+		by collaborations of scientists employing proprietary data and analysis software.
 		However, the next generation of \gammaray instruments,
@@
 \gammaray astronomy is a rather young field of research. The \gammaray~
-range of the electromagnetic spectrum provides us with insight into the
+range of the electromagnetic spectrum provides us insights into the
 most energetic processes in the universe such as surroundings of
@@
 		and the Very Energetic Radiation Imaging Telescope Array System (VERITAS).
-		The lower left shows the group of allsky instruments such as the
-		Fermi Large Area Telescope (Fermi-LAT) amd the High Altitude 
+		The lower left shows the group of all-sky instruments such as the
+		Fermi Large Area Telescope (Fermi-LAT) and the High Altitude
 		Water Cherencov Observatory (HAWC). The calibrated data of all those
@@
 The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
-as an open observatory in the domain. Its high level data (e.g. the event list) will be shared publicly after
+as an open observatory in the domain. Its high-level data (e.g. the event list) will be shared publicly after
 some proprietary period, and the software required to analyze it will be distributed
-as well. To allow the re-usability of existing instruments and their interoperability
-requires open data formats and open tools that can support the various analysis methods
+as well. To allow the re-usability of existing instruments and their interoperability,
+it is required to use open data formats and open tools that can support the various analysis methods
 commonly used in the field.
@@
 Python has become extremely popular as a scientific programming language,
-in particular, in the field of data sciences. The success is
+in particular, in the field of data sciences. This success is
 mostly attributed to the simple and easy to learn syntax, the ability to act as
@@
 This data release served as a basis for validation of open analysis tools,
-including \gammapy \cite[see e.g.]{Mohrmann2019}.
+including \gammapy \cite[see e.g.][]{Mohrmann2019}.
 
@@
         defines the groups for the different data levels and reduction steps
-        from raw gamma-like events on the left, to high level science products
+        from raw gamma-like events on the left to high-level science products
         on the right. The direction of the data flow is illustrated with the
@@
 % This might not be the bast place compared to introduction
-The data reduction process in \gammaray astronomy is usually split into two parts.
+The data analysis process in \gammaray astronomy is usually split into two parts.
 The first one deals with the data processing from camera measurement, calibration, event
@@
 into a prediction on the number of gamma-ray events, $N_{pred}$, with their estimated energy $E$  and position $p$, the model
-is convolved through the response function of the instrument.
-
-In the most general way we can write the expected number of detected events from the sky model $\Phi$ at measured position $p$ and energy $E$, for
-a given set of parameters $\hat{\theta}$:
+is convolved through the response functions of the instrument.
+
+In the most general way we can write the expected number of detected events from the sky model $\Phi$ at measured position
+$p$ and energy $E$, for a given set of parameters $\hat{\theta}$:
 \begin{align}
-   N(p, E, \hat{\theta}) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
-   &\times \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} )) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
+   N(p, E, \hat{\theta}) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true}) \nonumber \\
+   &\times \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} ) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
 \end{align}
-where $R(p, E| p_{\rm true}, E_{\rm true}$ is the instrument response and $t_{\rm obs}$ is the observation time
+where $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response and $t_{\rm obs}$ is the observation time
 
@@
 \begin{align}
-   R(p, E|p_{\rm true}, E_{\rm true}) = &A_{\rm eff}(p_{\rm true}, E_{\rm true}) \times\\
-    &PSF(p|p_{\rm true}, E_{\rm true}) \times\\
+   R(p, E|p_{\rm true}, E_{\rm true}) = &A_{\rm eff}(p_{\rm true}, E_{\rm true}) \times \nonumber \\
+    &PSF(p|p_{\rm true}, E_{\rm true}) \times \nonumber \\
     &E_{\rm disp}(E|p_{\rm true}, E_{\rm true})
@@
 corresponding instrument response functions (IRFs). The latter include the effective area ($A_{\rm eff}$),
-point spread function (PSF) and energy dispersion ($E_{\rm disp}$).
-
-An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
+point spread function (PSF) and energy dispersion ($E_{\rm disp}$). In general, they depend on event's detector
+geometrical parameters, e.g. the field-of-view location or the event elevation angle. So they might be parametrised as
+function of such parameters specific to the instrumental technical.
+
+An additional component of DL3 IRFs is the model if residual hadronic background rate, $Bkg$.
 It represents the intensity of charged particles misidentified as gamma-rays that are expected
@@
 \begin{align}
-  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \star \left[ PSF \star \left( A_{\rm eff} \times t_{\rm obs} \times \Phi(\hat{\theta}) \right) \right]\\
-                       & + Bkg(p, E)
+  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \star \left[ PSF \star \left( A_{\rm eff} \times t_{\rm obs} \times \Phi(\hat{\theta}) \right) \right]  \nonumber\\
+                       & + Bkg(p, E) \times t_{\rm obs}
 \end{align}
@@
 Finally, predicted and observed events, $N_{obs}$, can be then combined in a likelihood function,
-$\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\bar{\theta}$.
+$\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model.
 
@@
 background models can be subject to significant systematic uncertainties,
-the background estimated can be improved by taking into account actual data
+these models can be improved by taking into account actual data
 from regions without known \gammaray sources. This includes methods 
@@
 background measurements performed within, e.g. reflected regions~\citep{Berge07}.
-Data measured at the field-of-view or energy boundaries of the instrument is typically
+Data measured at the field-of-view or energy boundaries of the instrument are typically
 associated with a systematic uncertainty in the IRF. For this reason this part 
@@
 of the content of the different sub-packages follows mostly the stages in the
-data reduction workflow described in the previous section. Sub-packages
-either contain data structures representing data at different data reduction
-levels or contain algorithms to transition between the different data reduction
+data analysis workflow described in the previous section. Sub-packages
+either contain data structures representing data at different data analysis
+levels or contain algorithms to transition between the different data analysis
 levels.
@@
 \code{gammapy.modeling}, are used to jointly model a combination
-of datasets, for example, to create source catalogs. Estimator classes,
-which are contained in \code{gammapy.estimators} are used to
+of datasets, for example, to make spectum using data from several facilities. Estimator classes,
+which are contained in \code{gammapy.estimators}, are used to
 compute higher level science products such as flux and signficance maps,
 light curves or flux points. Finally there is a \code{gammapy.analysis}
-sub-package which provides a high level interface for executing analyses
+sub-package which provides a high-level interface for executing analyses
 defined from configuration files. In the following sections we will
-introduce all sub-packages and their functionality in more detail.
+introduce all sub-packages and their functionalities in more detail.
 
@@
 interface to access the lowest data level. \gammapy currently only
-supports data that is compliant with v0.2 of the \gadf data format.
+supports data that is compliant with v0.2 and v0.3 of the \gadf data format.
 DL3 data are typically bundled into individual observations, which
@@
 	\caption{
-		Using \code{gammapy.irf} to read and plot instrument repsonse functions.
+		Using \code{gammapy.irf} to read and plot instrument response functions.
 		Here we show example instrument response functions of some experiments and
         observatories for which \gammapy can analyse data. The \cta IRFs
-        are from the prod5 production. The \hess IRFs are from the DL3 DR1,
-        using observation ID 033787. The point spread function shows the 65\&
+        are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
+        using observation ID 033787. The point spread function shows the 68\%
         containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
@@
 from the \hawc or \fermi observatory. \gammapy natively supports
-the multiscale definiton of the HEALPix pixelisation and thus
+the multiscale definition of the HEALPix pixelisation and thus
 allows for easy up and downsampling of the data. In addition to
@@
 bin with an arbitrary shape, describing a region in the sky with that same
-shape. Typically they are is used together with a non-spatial dimension, for
+shape. Typically they are used together with a non-spatial dimension, for
 example an energy axis, to represent how a quantity varies in that dimension
@@
 done using \code{SpectrumDataset}. While the default statistics for both of these is
-\emph{Cash}}, their corresponding on off versions are adapted for the case where the
-background is measured from real off counts, and support \emph{WStat} statistics. The
+\emph{Cash}}, their corresponding ON/OFF versions are adapted for the case where the
+background is measured from real OFF counts, and support \emph{WStat} statistics. The
 predicted counts are computed by convolution of the models with the associated
 IRFs. Fitting of precomputed flux points is enabled through \code{FluxPointsDataset},
-using chi2 statistics. Multiple datasets of same or different types can be
+using \emph{$\chi^2$} statistics. Multiple datasets of same or different types can be
 bundled together in \code{Datasets} (e.g., Figure \ref{fig*:minted:gp_datasets}),
@@
 		a dataset object and optionally an \code{Observation} 
-		object. This way \code{Maker} classes can be chained
+		object. In this way, \code{Maker} classes can be chained
 		to define more complex data reduction "pipelines".
@@
 \begin{equation}
-    f(l, b, E, t) = F(E)  \cdot G(l, b, E) \cdot  H(t, E)
+    f(l, b, E, t) = F(E)  \times G(l, b, E) \times  H(t, E)
 \end{equation}
 
-Where the spectral model $F$ implicitly includes an \textit{amplitude} parameter
+where the spectral model $F$ implicitly includes an \textit{amplitude} parameter
 for the total flux of the model. The spatial model $G$ optionally depends
@@
 into the following categories:
-
 \begin{itemize}
@@
 These spectral models feature a dimension-less \textit{norm} parameter
-instead of an \text{amplitude} parameter with physical units. They
+instead of an \textit{amplitude} parameter with physical units. They
 must be used along with another spectral model, as a multiplicative correction
@@
 spatial and temporal model components (the spatial and temporal components being
-optional). \code{SkyModel} objects represents additive emission components, usually
+optional). \code{SkyModel} object represents additive emission components, usually
 sources or diffuse emission, although a single source can also be modeled by
@@
 The \code{Fit} class provides a uniform interface to multiple fitting backends:
-
 \begin{itemize}
@@
 
-In addition to the best fit flux norm all estimators compute
+In addition to the best fit flux \textit{norm} all estimators compute
 quantities corresponding to this flux. This includes
@@
 which show how the likelihood functions varies with
-the flux norm parameter around the fit minimum.
+the flux \textit{norm} parameter around the fit minimum.
 This information is useful in inspecting the quality
@@
 The actual flux values for each SED type are obtained
-by multiplication of the norm with the  reference flux.
+by multiplication of the \textit{norm} with the reference flux.
 
@@
     \end{center}
+    \caption{Definition of the different SED types supported in \gammapy.}
     \label{tab:sed_types}
-    \caption{Definition of the different SED types supported in \gammapy.}
 \end{table*}
@@
 the data into multiple formats. This includes the
-\gadf SED (reference?) format, FITS based ND sky-maps
-and formats compatible with Astropy's \code{Table} and
+\gadf SED format \footnote{\url{https://gamma-astro-data-formats.readthedocs.io/en/latest/spectra/flux_points/index.html}},
+FITS based ND sky-maps and formats compatible with Astropy's \code{Table} and
 \code{BinnedTimeSeries} data structures. This allows
@@
 
-The sub-package also provides "matplotlib" implementations of specific
+The sub-package also provides \texttt{matplotlib} implementations of specific
 colormaps for false color image representation. Those colormaps have
-been used historically by larger collaborations in the very high-energy
-domain (such as \milagro or \hess) as 'trademark' colormaps.
+been historically used by larger collaborations in the very high-energy
+domain (such as \milagro or \hess) as "trademark" colormaps.
 While we explicitly discourage the use of those colormaps for publication
@@
     \end{center}
+    \caption{Overview of supported catalogs in \code{gammapy.catalog}.}
     \label{tab:catalogs}
-    \caption{Overview of supported catalogs in \code{gammapy.catalog}.}
 \end{table*}
@@
 
-\gammapy can be used for a variety of science cases by different IACT
-experiments. (Refer to publications). The analysis examples shown in
-the following section are limited by the availability
+\gammapy is in use for a variety of science cases by different IACT
+experiments leading to more than 60 publications
+\footnote{\href{https://ui.adsabs.harvard.edu/search/q=(\%20(citations(doi\%3A\%2210.1051\%2F0004-6361\%2F201834938\%22)\%20OR\%20citations(bibcode\%3A2017ICRC...35..766D))\%20AND\%20year\%3A2014-2023)&sort=date\%20desc\%2C\%20bibcode\%20desc&p_=0}{List on ADS}}.
+The analysis examples shown in the following section are limited by the availability
 of public data. In general, there is no limitation on performing a specific analysis
@@
 measured in a circular aperture centered on the Galactic Center, in
-\gammaray~astronomy often called "on region". For such analysis the users first
+\gammaray~astronomy often called "ON region". For such analysis the users first
 chooses a region of interest and energy binning, both defined by a
@@
 reduced IRFs are bundled into a \code{SpectrumDataset}. To estimate
-the expected background in the ON region a 'reflected regions' background
+the expected background in the ON region a "reflected regions" background
 method was used~\cite{Berge07}, represented in \gammapy by the
@@
 		shows the resulting spectral points and their corresponding log-likelihood
-		profiles.} \label{fig:cta_galactic_center} \end{figure*}
+		profiles.}
+	\label{fig:cta_galactic_center}
+\end{figure*}
 
@@
 	\caption{Example of a 3D analysis for simulated sources with point-like, Gaussian
-		and shell-like morphology. The simulation uses \textit{prod5} \irfs from \cta.
-		The left image shows a significance map where the three simulated sources can be
-		seen. The middle figure shows another significance map, but this time after
+		and shell-like morphologies. The simulation uses \textit{prod5} \irfs from \cta.
+		The left image shows a significance map (using the \emph{Cash} statistics)
+		where the three simulated sources can be seen. The middle figure shows another significance map,
+		but this time after
 		subtracting the best-fit model for each of the sources, which are displayed in
 		black. The right figure shows the contribution of each source model to the
-		circular region of radius 0.5\textdegree drawn in the left image, together with
-		the excess counts inside that region. } \label{fig:cube_analysis}
+		circular region of radius 0.5\textdegree~drawn in the left image, together with
+		the excess counts inside that region. }
+	\label{fig:cube_analysis}
 \end{figure*}
@@
 the measured flux being underestimated, and heavily dependent on the choice of
-extraction region. Additionally, the 1D approach neglects the energy-dependence
-of the PSF.
+extraction region.
 
@@
 way, a DL4 dataset can directly be simulated. In particular we simulate:
-
 \begin{enumerate}
-    \item A point source located at (l=0\textdegree, b=0\textdegree) with a power law
-	      spectral shape.
-    \item An extended source with Gaussian morphology located at (l=0.4\textdegree,
+    \item a point source located at (l=0\textdegree, b=0\textdegree) with a power law
+	      spectral shape,
+    \item an extended source with Gaussian morphology located at (l=0.4\textdegree,
 	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log parabola spectral
-	      shape.
-    \item A large shell-like structure centered around (l=0.06\textdegree,
-	      b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree
+	      shape,
+    \item a large shell-like structure centered on (l=0.06\textdegree,
+	      b=0.6\textdegree) with a radius and width of 0.6\textdegree~and 0.3\textdegree~
 	      respectively and a power law spectral shape.
@@
 measured excess counts integrated in that region to the expected relative
-contribution from each of the three source models. The result can be seen in the left
+contribution from each of the three source models. The result can be seen in the right
 panel of Figure~\ref{fig:cube_analysis}.
@@
 \verb"GAMMAPY_DATA". Each observation is first split into 10 min smaller
-observations, and spectra extracted for each of these within a 0.11\textdegree radius
+observations, and spectra extracted for each of these within a 0.11\textdegree~radius
 around the source. A \code{PowerLawSpectralModel} is fit to all the datasets, leading
 to a reconstructed index of $3.54 \pm 0.02$. With this adjusted spectral model
-the \code{LightCurveEstimator} runs directly for two energy bands, 0.5 - 1.5
-TeV, and 1.5 - 20 TeV, respectively.
+the \code{LightCurveEstimator} runs directly for two energy bands, $0.5\,{\rm TeV} - 1.5\,{\rm TeV}$,
+and $1.5\,{\rm TeV} - 20\,{\rm TeV}$, respectively.
 %
@@
         Binned light curves in two different energy bands for the source
-        PKS~2155-304 in two energy bands, (500 GeV - 1.5 TeV, and 1.5 TeV to 20 TeV)
+        PKS~2155-304 in two energy bands ($0.5\,{\rm TeV} - 1.5\,{\rm TeV}$, and $1.5\,{\rm TeV} - 20\,{\rm TeV}$)
         as observed by the \hess telescopes in 2006. The coloured markers
@@
         error illustrates the width of the time bin of 10~min. The vertical
-        error bars show the associated assymetrical flux errors. The marker
+        error bars show the associated asymmetrical flux errors. The marker
         is set to the center of the time bin.
@@
         the data of the different listed instruments. The horizontal error bar
-        illustrates the width of the chosen energy band $E_{Min}, E_{Max}$.
+        illustrates the width of the chosen energy band ($E_{Min}, E_{Max}$).
         The marker is set to the log-center energy of the band, that is
@@
 users to wrap a given astrophysical emission model from the
-naima package and fit it directly to \gammaray data.
+Naima package and fit it directly to \gammaray data.
 
@@
 dataset described in the previous section and we fit it with an inverse
-Compton model computed with naima and wrapped in the \gammapy fitting
- routine with the NaimaSpectraModel class. We consider a log-parabolic
+Compton model computed with Naima and wrapped in the \gammapy fitting
+ routine with the \code{NaimaSpectraModel} class. We consider a log-parabolic
 electron distribution scattering: the synchrotron radiation produced by
@@
 CTA~\citep{2021arXiv210903729R}. This large increase in the amount of data to analyse
-and increase in complexity of modelling scenarios, requires the high level
+and increase in complexity of modelling scenarios, requires the high-level
 analysis software to be both scalabale as well as performant.
@@
 institutionally driven organisation, the permanent staff and commitment of
-supporting institutes, ensures the continuity of the executive teams. A core team
+supporting institutes ensure the continuity of the executive teams. A core team
 of developers from the contributing institutions is in charge of the regular
@@
 repositories related with the project. The software codebase may be found in
-the \textit{gammapy} repository (see Table~\ref{table:codestats:data} and
+the \textit{gammapy} repository (see
 Figure~\ref{fig:codestats:lang} for code lines statistics). We make extensive
@@
         categories in the \gammapy code base. The total number of lines is $\approx 50 000$.
-    } \label{fig:codestats:lang}
+    }
+	\label{fig:codestats:lang}
 \end{figure}
@@
 Library\footnote{\url{https://ascl.net/1711.014}} and
-Zenodo\footnote{\url{https://zenodo.org/record/5721467o}} digital libraries for
+Zenodo\footnote{\url{https://doi.org/10.5281/zenodo.4701488}} digital libraries for
 software. The Zenodo record is synchronised with the codebase \github repository
@@
 is using the \gammapy SWHIDs to register the releases as scientific
-products~\footnote{\url{https://hal.archives-ouvertes.fr/hal-03713410v1}} of open science.
+products~\footnote{\url{https://hal.science/hal-03885031v1}} of open science.
 
@@
 PIG documents is available in the \gammapy online documentation
-\footnote{\url{https://docs.gammapy.org/0.20/development/pigs/index.html}}.
+\footnote{\url{https://docs.gammapy.org/dev/development/pigs/index.html}}.
 
@@
 hundreds of observations as expected by deep surveys of the CTA
-observatory. In addition the high level interface
+observatory. In addition the high-level interface
 of \gammapy is planned to be developed into a fully configurable
@@
 project, the code base has constantly grown its range of features
-and improved its code quality. With \gammapy being selected as the base library
-for the future science tools for CTA, we expect the community to grow
+and improved its code quality. With \gammapy being officially selected
+in 2021 as the base library for the future science tools for CTA
+\footnote{\href{https://www.cta-observatory.org/ctao-adopts-the-gammapy-software-package-for-science-analysis/}{CTAO Press Release}},
+we expect the community to grow
 even further, providing a stable perspective for further usage,
@@
 by the CTA community \gammapy has already
-been used for analysis of data from the \hess, \magic
-\hawc, \astri and \veritas instruments.
+been used for analysis of data from the \hess, \magic, \astri and \veritas instruments.
 
@@
 
-	Mention Christoph here?
-
 	We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
 	\texttt{Matplotlib} communities for providing their packages which are
-	invaluable to the development of Astropy. We thank the \github team for
+	invaluable to the development of Gammapy. We thank the \github team for
 	providing us with an excellent free development platform. We also are grateful
@@
 	documentation hosting and testing respectively. Finally, we would like to thank
-	all the \gammapy users that have provided feedback and submitted bug reports.
-
-	TODO: copy over stuff from
-	\url{http://docs.gammapy.org/en/latest/about.html#thanks}.
-
-	TODO: add the ANR for Luca (and Atreyee in LUPM?)
-
-	J.E. Ruiz acknowledges financial support from the State Agency for Research of
+	all the \gammapy users that have provided feedback and submitted bug reports. Α
+	special acknowledgment has to be given to our first Lead Developer of \gammapy,
+	Christoph Deil.
+	J.E.~Ruiz acknowledges financial support from the State Agency for Research of
 	the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the
-	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709)
+	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709). L.~Giunti acknowledges
+	financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014).
 

### 2023-01-26 src/ms-review.tex
Fix acknowledgements
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>
Update src/ms-review.tex
Co-authored-by: Atreyee Sinha <asinha@ucm.es>
author review before publication, reached Sect. 3.5

--- 2023-01-25 src/ms-review.tex
@@
 \newcommand{\gammaray}{$\gamma$-ray\xspace}
-\newcommand{\gammarays}{$\gamma$-rays\xspace}
+\newcommand{\gammarays}{$\gamma$ rays\xspace}
 \newcommand{\gadf}{GADF\xspace}
@@
 	{
-		Traditionally, the \gammaray universe has been probed
+		Traditionally, \gammaray astronomy has been conducted
 		by small collaborations of scientists employing proprietary data and analysis software.
@@
 	{
-		Starting from event list and "instrument response functions",
+		Starting from event list and instrument response functions,
 		\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
@@
 %% \gammaray astronomy
+%% CN: I think we should use the expression Water Cherenkov Detectors and use the
+%% abbreviation (WCD) all along the text, later we use "particle samplers"
 \gammaray astronomy is a rather young field of research. The \gammaray~
 range of the electromagnetic spectrum provides us with insight into the
-most energetic processes in the universe such as surroundings of
-black holes and remnants of supernova explosions. As in other
+most energetic processes in the universe such as those accelerating particles in the surroundings of
+black holes, or in remnants of supernova explosions. As in other
 branches of astronomy, \gammarays can be observed by both
 satellite as well as ground based instruments.
-Ground based instrument use the Earth's atmosphere as a particle detector.
-Very high-energy cosmic \gammarays interact in the atmosphere and
+Ground-based instruments use the Earth's atmosphere as a particle detector.
+Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and
 create a large shower of secondary particles that can be observed from the ground.
 Ground-based \gammaray astronomy relies on these extensive air showers to detect the
-primary \gammaray photons and measure their direction and energy.
-It covers the energy range from fews tens of GeV up to the PeV.
-There are two main categories of ground based instruments: 
+primary \gammaray photons and infer their direction and energy.
+VHE \gammaray astronomy covers the energy range from fews tens of ${\rm GeV}$ up to the ${\rm PeV}$.
+There are two main categories of ground-based instruments: 
 Imaging Atmospheric Cherenkov Telescopes (IACT) and 
-Water Cherenkov observatories. IACTs make images of atmospheric showers
+Water Cherenkov observatories. IACTs obtain images of the atmospheric showers
 by detecting the Cherenkov radiation emitted by the cascading charged particles and
@@
 Those instruments have a limited field of view (FoV) and duty cycle, but
-good energy and angular resolution \citep{2015CRPhy..16..610D}.
+good energy and angular resolution.
 
@@
 		and the Very Energetic Radiation Imaging Telescope Array System (VERITAS).
-		The lower left shows the group of allsky instruments such as the
+		The lower left shows the group of all-sky instruments such as the
 		Fermi Large Area Telescope (Fermi-LAT) amd the High Altitude 
-		Water Cherencov Observatory (HAWC). The calibrated data of all those
+		Water Cherenkov Observatory (HAWC). The calibrated data of all those
 		instruments can be converted and stored into the common GADF data format.
@@
 		different instruments and perform a joint analysis.
-		\gammapy is built on the scientific python eco-system, and the required dependencies
+		\gammapy is built on the scientific python ecosystem, and the required dependencies
 		are shown below the \gammapy logo.
@@
 large field-of-view, large duty-cycle but higher energy threshold and
-usually have lower signal to noise ratios compared to IACTs.
+usually have lower signal to noise ratios compared to IACTs \citep{2015CRPhy..16..610D}.
 
 %% Context
-Ground based \gammaray astronomy has been historically structured
-by experiments run by independent collaborations relying
+Ground-based \gammaray astronomy has been historically conducted
+by experiments operated by independent collaborations, each relying
 on their own proprietary data and analysis software developed as part of the
@@
 complementary sky coverages, and the various detection
-techniques have complementary properties in terms of covered energy rage,
+techniques have complementary properties in terms of the energy range covered,
 duty cycle and spatial resolution.
@@
 %TODO: better transition into context
-The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
-as an open observatory in the domain. Its high level data (e.g. the event list) will be shared publicly after
+The Cherenkov Telescope Array (CTA) will be the first ground-based \gammaray instrument to be operated
+as an open observatory. Its high-level data (e.g. the event list) will be shared publicly after
 some proprietary period, and the software required to analyze it will be distributed
@@
 %% Context : formats
+%% CN: particle samplers -> WCD
 In practice, the data reduction workflow of all \gammaray observatories
 is remarkably similar. After data calibration, shower events are reconstructed and
-gamma/hadron separation is applied to build lists of \gammaray like events.
+gamma/hadron separation is applied to build lists of \gammaray-like events.
 The lists of \gammaray events are then used to derive scientific results, such as spectra, sky maps
-or light curves, taking into account the observatory specific instrument response functions (IRF).
-Once the data is present in the form of a list of events, the information is independent of
-the data reduction process, and eventually of the detection technique. This implies,
-for example, that data from IACT and particle samplers can be represented
-within the same model. The efforts to prototype a format usable by various instruments
+or light curves, taking into account the observatory's specific instrument response functions (IRF).
+Once the data is reduced to a list of events, the information is independent of
+the data-reduction process, and, eventually, of the detection technique. This implies,
+for example, that hihg-level data from IACT and particle samplers can be represented
+with the same data model. The efforts to prototype a format usable by various instruments
 converged in the so-called \textit{Data Format for \gammaray Astronomy}
@@
 (energy, direction, arrival time) and a parametrisation of the response of the
-system.
+system. %% where? in the data units of a FITS file.
 
@@
 a 'glue' language between different programming languages and last but not least
-the rich eco-system of packages and its open and supportive community, from
+the rich ecosystem of packages and its open and supportive community, from
 core numerical analysis packages such as \numpy~\citep{numpy} and
 \scipy~\citep{2020SciPy-NMeth}, visualization libraries, e.g. Matplotlib \citep{matplotlib},
-or optimization packages such as \iminuit \citep{iminuit}.
-
-The \astropy~\citep{astropy} was created in 2012 to build a community-developed
+to optimization packages such as \iminuit \citep{iminuit}.
+
+The \astropy~\citep{astropy} project was created in 2012 to build a community-developed
 Python package for astronomical research. Among other things, it offers functionalities for
@@
 efficient software library for very high-energy \gammaray data analysis \citep{gammapy_2015}.
-This is possible thanks to the definition of a common data format such as \gadf, and thanks to
+This is possible thanks to the definition of a standardised common data format such as the \gadf, and thanks to
 an open development with a broad community of contributors. The relation of \gammapy to the
@@
 %% \gammapy: from first developments to validation and selection
+%% CN: what about mentioning the joint Crab? or is it mentioned later?
 The \hess collaboration released a limited test dataset (about 50 hours of
@@
 show how this workflow is reflected in the structure of the \gammapy package 
-in Section~\ref{sec:gammapy-package} and also
-describe the various subpackages it contains. Section~\ref{sec:applications}
+in Section~\ref{sec:gammapy-package}, while also
+describing the various subpackages it contains. Section~\ref{sec:applications}
 presents a number of applications, while Section~\ref{sec:gammapy-project}
@@
 \section{Gamma-ray Data Analysis}
-%
+% CN: gamma-like here, was \gammaray-like in the previous section
 \begin{figure*}[h!]
@@
 		\gammapy sub-package structure and data analysis workflow. The top row
-        defines the groups for the different data levels and reduction steps
-        from raw gamma-like events on the left, to high level science products
-        on the right. The direction of the data flow is illustrated with the
+        defines the different levels of data reduction, from lists of gamma-like
+        events on the left (DL3), to high-level scientific products products
+        (DL5) on the right. The direction of the data flow is illustrated by the
         grey arrows. The gray folder icons represent the different sub-packages
@@
 shared across the field. They also frequently imply joint analysis of multi-instrument data.
+%% CN: I don't understand this: since the high-level methods are the same, then they "imply"
+%% joint analyses?? Maybe they eventually allow or permit?
 
@@
 an analytical model is commonly adopted to describe the intensity of gamma-ray sources as a function of the energy,
-$E_{true}$, and of the position in the field of view, $p_{true}$:
+$E_{\rm true}$, and of the position in the field of view, $p_{\rm true}$:
 $$ \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]} $$
 where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. To convert this analytical flux model
-into a prediction on the number of gamma-ray events, $N_{pred}$, with their estimated energy $E$  and position $p$, the model
+into a prediction on the number of gamma-ray events, $N_{\rm pred}$, with their estimated energy $E$ and position $p$, the model
 is convolved through the response function of the instrument.
 
-In the most general way we can write the expected number of detected events from the sky model $\Phi$ at measured position $p$ and energy $E$, for
-a given set of parameters $\hat{\theta}$:
+%% CN: not sure if we already commented about this, but align is artificially
+%% numbering every new line as a new equation
+%% I think
+%% \begin{equation}
+%%   \begin{split}
+%%     ...
+%%   \begin{split}
+%% \begin{equation}
+%% will avoid to number each new line
+
+In the most general way, we can write the expected number of detected events from the sky model $\Phi$ at measured position $p$ and energy $E$, for
+a given set of parameters $\hat{\theta}$, as
 \begin{align}
-   N(p, E, \hat{\theta}) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
-   &\times \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} )) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
+   N(p, E, \hat{\theta})\,{\rm d}p\,{\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
+   &\times \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} ) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
 \end{align}
-where $R(p, E| p_{\rm true}, E_{\rm true}$ is the instrument response and $t_{\rm obs}$ is the observation time
+where $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response and $t_{\rm obs}$ is the observation time
 
@@
   of the detector collection area times its detection efficiency at true energy $E_{\rm true}$ and position $p_{\rm true}$.
-\item $PSF(p|p_{\rm true}, E_{\rm true})$ is the point spread function. It gives the probability of
+\item $PSF(p|p_{\rm true}, E_{\rm true})$ is the point spread function (PSF). It gives the probability of
   measuring a direction $p$ when the true direction is $p_{\rm true}$ and the true energy is $E_{\rm true}$.
@@
 
+%% CN: except for the figures we never introduced what the DL3 or the Data Level acronym is
+%% maybe add (see Fig.~1)
 \gammaray data at the Data Level 3 (DL3) therefore consist of lists of gamma-like events and their
-corresponding instrument response functions (IRFs). The latter include the effective area ($A_{\rm eff}$),
-point spread function (PSF) and energy dispersion ($E_{\rm disp}$).
+corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),
+point spread function and energy dispersion ($E_{\rm disp}$).
+%% CN: this paragraph repeats what is commented in the previous formula and itemize and can be removed
 
 An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
-It represents the intensity of charged particles misidentified as gamma-rays that are expected
+It represents the intensity of charged particles misidentified as \gammarays that are expected
 during an observation. It is defined as a function of the measured position in the field-of-view
@@
 \end{align}
-
-Finally, predicted and observed events, $N_{obs}$, can be then combined in a likelihood function,
-$\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\bar{\theta}$.
+%% CN: Instead of rewriting this formula and introducing this new notation for the convolution,
+%% can't we just say that, when predicting counts, $Bkg(p, E)$ has to be summed to the convolution
+%% (or integral) in the previous equation?
+
+Finally, predicted and observed events, $N_{obs}$, can then be combined in a likelihood function,
+$\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\hat{\theta}$.
 
@@
 
+%% CN: I would actually distingusih two cases here:
+%% 1) the Bkg is already provided as a parametrisation
+%% 2) the Bkg is not provided and, thus, has to be estimated from the obs.
 After all data has been projected into the same geometry, it is typically
@@
 
+%% CN: for 1D analysis datasets, DL4 can actually be written as OGIP files,
+%% so as reduced datasets in a general format, not specific to Gammapy.
+%% Maybe you can briefly mention that this is due to the fact that the 1D Poisson
+%% spectral analysis is liong consilidated, but this also means that Gammapy 's
+%% dataset can handle lower energy data, e.g. X-ray.
+%% We also said in the abstract that Gammapy is compliant with other specifications
+%% adopted in high-energy astrophysics.
 The counts data and the reduced IRFs in the form of maps are bundled into "datasets"
@@
 for modeling and fitting. Different variations of such datasets support different 
-analysis methods and fit statistics. The datasets are used to perform joint-likelihood
-fitting allowing to combine different measurements, e.g. from different observations
+analysis methods and fit statistics. The datasets can be used to perform a joint-likelihood
+fit, allowing one to combine different measurements, e.g. from different observations
 but also from different instruments or event classes. They can also be used for binned
@@
 provides a uniform interface to multiple fitting backends. In addition to
-providing a variety of built in models, including spectral,
+providing a variety of built-in models, including spectral,
 spatial and temporal model classes to describe the \gammaray emission in the sky,
@@
 re-grouped to compute flux points, light curves and flux as well as significance
-maps in energy bands.
+maps in different energy bands.
 The modelling and fitting functionalities are implemented in the \code{gammapy.modeling},
@@
 The \gammapy package is structured into multiple sub-packages. The definition
-of the content of the different sub-packages follows mostly the stages in the
+of the content of the different sub-packages follows mostly the stages of the
 data reduction workflow described in the previous section. Sub-packages
-either contain data structures representing data at different data reduction
-levels or contain algorithms to transition between the different data reduction
-levels.
+either contain structures representing data at different reduction
+levels or algorithms to transition between these different levels.
 
@@
 event lists and IRFs as well as functionality
-to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
+to read the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
 contains the functionality to reduce the DL3 data to binned maps.
@@
 maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
-sub-packages respectively. Parametric models, which are defined in
+sub-packages, respectively. Parametric models, which are defined in
 \code{gammapy.modeling}, are used to jointly model a combination
-of datasets, for example, to create source catalogs. Estimator classes,
-which are contained in \code{gammapy.estimators} are used to
+of datasets, for example, to create source catalogs.
+%% CN: well models represent the analytical description of the source morphology
+%% and spectra we gave in the first equation, right? I don't understand why we
+%% talk of catalogues here.
+Estimator classes, which are contained in \code{gammapy.estimators} are used to
 compute higher level science products such as flux and signficance maps,
@@
 The \code{gammapy.data} sub-package implements the functionality to select,
-read and represent DL3 \gammaray data in memory. It provides the main user
+read, and represent DL3 \gammaray data in memory. It provides the main user
 interface to access the lowest data level. \gammapy currently only
-supports data that is compliant with v0.2 of the \gadf data format.
+supports data that is compliant with \code{v0.2} of the \gadf data format.
 DL3 data are typically bundled into individual observations, which
@@
 
+%% CN: what is a index file?
 A typical usage example is shown in Figure~\ref{fig*:minted:gp_data}.
@@
 directory, which contains the DL3 data index file. The \code{DataStore}
-object gathers a collection of observations and providing ancillary
+object gathers a collection of observations and provides ancillary
 files containing information about the telescope observation mode and the
@@
 example in Section~\ref{ssec:multi-instrument-analysis}.
-%
+
+%% CN: Shouldn't we display the output of this snippet?
+%% otherwise what's teh point of the `print`' functions?
 \begin{figure}
@@
         are from the prod5 production. The \hess IRFs are from the DL3 DR1,
-        using observation ID 033787. The point spread function shows the 65\&
+        using observation ID 033787. The \magic effective area is computed for a
+        $20\,{\rm min}$ observation at the Crab Nebula coordinates.
+        The point spread function shows the $65\%$
         containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
@@
 %
+%% CN: description of the HAWC IRF missing, what is the difference between the gray
+%% and black effective areas? Where are they taken from?
+
 The \code{gammapy.irf} sub-package contains all classes and functionality
@@
 interpolate and evaluate the quantities of interest on both energy and spatial
-axes, convert their format or units in different kinds, plot or write them into
+axes, convert their format or units, plot or write them into
 output files. In the following, we list the main classes of the
@@
 
+%% CN: ref. for King function https://ui.adsabs.harvard.edu/abs/2011A%26A...534A..34R/abstract
+%% CN: I would not say that the PSFKing takes into account "the gamma and sigma", fo what?
+%% I would put a formula or quickly describe the function (e.g. it is a power-law, an exponential...)
 \subsubsection{Point Spread Function}
@@
 true energy only represented by the sub-class \code{EDispKernel}.
+%% CN: I don't understand what "the latter" refers to.
 
@@
 
-Some example IRFs that are read and plotted with \gammapy are show in Figure~\ref{fig:irfs}.
+Some example IRFs read and plotted with \gammapy are shown in Figure~\ref{fig:irfs}.
 
@@
 dedicated \code{TimeMapAxis}, which allows time bins to be non-contiguous,
-as it is often the case with observation time-stamps. The generic
+as it is often the case with observational times. The generic
 class \code{LabelMapAxis} allows the creation of axes for non-numeric entries.
@@
 independent of the underlying pixelisation scheme.
+%% CN: API acronym not introduced
 
@@
 bin with an arbitrary shape, describing a region in the sky with that same
-shape. Typically they are is used together with a non-spatial dimension, for
+shape. Typically, they are used together with a non-spatial dimension, for
 example an energy axis, to represent how a quantity varies in that dimension
@@
 associated statistic, different types of Datasets are supported. \code{MapDataset} is
-used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
-done using \code{SpectrumDataset}. While the default statistics for both of these is
+employed for 3D (spectral and morphological) fitting, while 1D spectral fitting is
+performed using \code{SpectrumDataset}. While the default statistics for both of these is
 \emph{Cash}}, their corresponding on off versions are adapted for the case where the
@@
 methods.
+%% CN: references missing for Cash and Wstat statistics
+%% CN: what are the "corresponding on off versions"?
 

### 2023-01-26 src/ms-review.tex
Contains corrections on the latest draft. The Cosimo's ones should be merged after approval
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

--- 2023-01-26 src/ms-review.tex
@@
 \usepackage{hyperref}
+
+%% For the review, add the line numbers
+\usepackage[switch]{lineno}
+\linenumbers
 
@@
 	{
-		Traditionally, the \gammaray universe has been probed
+
+		Traditionally, \gammaray astronomy has been conducted
 		by collaborations of scientists employing proprietary data and analysis software.
@@
 %% \gammaray astronomy
+%% CN: I think we should use the expression Water Cherenkov Detectors and use the
+%% abbreviation (WCD) all along the text, later we use "particle samplers"
 \gammaray astronomy is a rather young field of research. The \gammaray~
 range of the electromagnetic spectrum provides us insights into the
-most energetic processes in the universe such as surroundings of
-black holes and remnants of supernova explosions. As in other
+most energetic processes in the universe such as those accelerating particles in the surroundings of
+black holes, and remnants of supernova explosions. As in other
 branches of astronomy, \gammarays can be observed by both
 satellite as well as ground based instruments.
-Ground based instrument use the Earth's atmosphere as a particle detector.
-Very high-energy cosmic \gammarays interact in the atmosphere and
+Ground-based instruments use the Earth's atmosphere as a particle detector.
+Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and
 create a large shower of secondary particles that can be observed from the ground.
 Ground-based \gammaray astronomy relies on these extensive air showers to detect the
-primary \gammaray photons and measure their direction and energy.
-It covers the energy range from fews tens of GeV up to the PeV.
-There are two main categories of ground based instruments: 
+primary \gammaray photons and infer their direction and energy.
+VHE \gammaray astronomy covers the energy range from fews tens of ${\rm GeV}$ up to the ${\rm PeV}$.
+There are two main categories of ground-based instruments: 
 Imaging Atmospheric Cherenkov Telescopes (IACT) and 
-Water Cherenkov observatories. IACTs make images of atmospheric showers
+Water Cherenkov observatories. IACTs obtain images of the atmospheric showers
 by detecting the Cherenkov radiation emitted by the cascading charged particles and
@@
 		Fermi Large Area Telescope (Fermi-LAT) and the High Altitude
-		Water Cherencov Observatory (HAWC). The calibrated data of all those
+		Water Cherenkov Observatory (HAWC). The calibrated data of all those
 		instruments can be converted and stored into the common GADF data format.
@@
 %TODO: better transition into context
-The Cherenkov Telescope Array (CTA) will be the first instrument to be operated
-as an open observatory in the domain. Its high-level data (e.g. the event list) will be shared publicly after
+The Cherenkov Telescope Array (CTA) will be the first ground-based \gammaray instrument to be operated
+as an open observatory. Its high-level data (e.g. the event list) will be shared publicly after
 some proprietary period, and the software required to analyze it will be distributed
@@
 		\gammapy sub-package structure and data analysis workflow. The top row
-        defines the groups for the different data levels and reduction steps
-        from raw gamma-like events on the left to high-level science products
-        on the right. The direction of the data flow is illustrated with the
-        grey arrows. The gray folder icons represent the different sub-packages
+        defines the different levels of data reduction, from lists of gamma-like
+        events on the left (DL3), to high-level scientific products products
+        (DL5) on the right. The direction of the data flow is illustrated with the
+        gray arrows. The gray folder icons represent the different sub-packages
         in \gammapy and their names. Below each icon there is a list of the most
@@
 an analytical model is commonly adopted to describe the intensity of gamma-ray sources as a function of the energy,
-$E_{true}$, and of the position in the field of view, $p_{true}$:
+$E_{\rm true}$, and of the position in the field of view, $p_{\rm true}$:
 $$ \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]} $$
 where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. To convert this analytical flux model
-into a prediction on the number of gamma-ray events, $N_{pred}$, with their estimated energy $E$  and position $p$, the model
-is convolved through the response functions of the instrument.
-
-In the most general way we can write the expected number of detected events from the sky model $\Phi$ at measured position
-$p$ and energy $E$, for a given set of parameters $\hat{\theta}$:
+into a prediction on the number of gamma-ray events, $N_{\rm pred}$, with their estimated energy $E$ and position $p$, the model
+is convolved through the response function of the instrument.
+
+%% CN: not sure if we already commented about this, but align is artificially
+%% numbering every new line as a new equation
+%% I think
+%% \begin{equation}
+%%   \begin{split}
+%%     ...
+%%   \begin{split}
+%% \begin{equation}
+%% will avoid to number each new line
+
+In the most general way, we can write the expected number of detected events from the sky model $\Phi$ at measured position $p$ and energy $E$, for
+a given set of parameters $\hat{\theta}$, as
 \begin{align}
-   N(p, E, \hat{\theta}) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true}) \nonumber \\
+   N(p, E, \hat{\theta})\,{\rm d}p\,{\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true}) \nonumber \\
    &\times \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} ) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
@@
 
+%% CN: except for the figures we never introduced what the DL3 or the Data Level acronym is
+%% maybe add (see Fig.~1)
 \gammaray data at the Data Level 3 (DL3) therefore consist of lists of gamma-like events and their
-corresponding instrument response functions (IRFs). The latter include the effective area ($A_{\rm eff}$),
-point spread function (PSF) and energy dispersion ($E_{\rm disp}$). In general, they depend on event's detector
+corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),
+point spread function and energy dispersion ($E_{\rm disp}$).
+In general, they depend on event's detector
 geometrical parameters, e.g. the field-of-view location or the event elevation angle. So they might be parametrised as
@@
 
-An additional component of DL3 IRFs is the model if residual hadronic background rate, $Bkg$.
-It represents the intensity of charged particles misidentified as gamma-rays that are expected
+%% CN: this paragraph repeats what is commented in the previous formula and itemize and can be removed
+
+An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
+It represents the intensity of charged particles misidentified as \gammarays that are expected
 during an observation. It is defined as a function of the measured position in the field-of-view
@@
 \end{align}
+%% CN: Instead of rewriting this formula and introducing this new notation for the convolution,
+%% can't we just say that, when predicting counts, $Bkg(p, E)$ has to be summed to the convolution
+%% (or integral) in the previous equation?
 
 Finally, predicted and observed events, $N_{obs}$, can be then combined in a likelihood function,
-$\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model.
+$\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\hat{\theta}$.
 
@@
 The \gammapy package is structured into multiple sub-packages. The definition
-of the content of the different sub-packages follows mostly the stages in the
-data analysis workflow described in the previous section. Sub-packages
-either contain data structures representing data at different data analysis
-levels or contain algorithms to transition between the different data analysis
-levels.
+of the content of the different sub-packages follows mostly the stages of the
+data reduction workflow described in the previous section. Sub-packages
+either contain structures representing data at different reduction
+levels or algorithms to transition between these different levels.
 
@@
 maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
-sub-packages respectively. Parametric models, which are defined in
+sub-packages, respectively. Parametric models, which are defined in
 \code{gammapy.modeling}, are used to jointly model a combination
@@
 The \code{gammapy.data} sub-package implements the functionality to select,
-read and represent DL3 \gammaray data in memory. It provides the main user
+read, and represent DL3 \gammaray data in memory. It provides the main user
 interface to access the lowest data level. \gammapy currently only
-supports data that is compliant with v0.2 and v0.3 of the \gadf data format.
+supports data that is compliant with \code{v0.2} and \code{v0.3} of the \gadf data format.
 DL3 data are typically bundled into individual observations, which
@@
         are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
-        using observation ID 033787. The point spread function shows the 68\%
+        using observation ID 033787. The \magic effective area is computed for a
+        $20\,{\rm min}$ observation at the Crab Nebula coordinates.
+        The point spread function shows the $68\%$
         containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
@@
 bin with an arbitrary shape, describing a region in the sky with that same
-shape. Typically they are used together with a non-spatial dimension, for
+shape. Typically, they are used together with a non-spatial dimension, for
 example an energy axis, to represent how a quantity varies in that dimension
@@
 modeling and fitting purposes. Depending upon the type of analysis and the
-associated statistic, different types of Datasets are supported. \code{MapDataset} is
+associated statistic, different types of Datasets are supported. The \code{MapDataset} is
 used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
@@
 	to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
-	documentation hosting and testing respectively. Finally, we would like to thank
-	all the \gammapy users that have provided feedback and submitted bug reports. Α
-	special acknowledgment has to be given to our first Lead Developer of \gammapy,
-	Christoph Deil.
+	documentation hosting and testing respectively. Α special acknowledgment has to be given
+	to our first Lead Developer of \gammapy, Christoph Deil. Finally, we would like to thank
+	all the \gammapy users that have provided feedback and submitted bug reports.
 	J.E.~Ruiz acknowledges financial support from the State Agency for Research of

### 2023-01-26 src/figures/irfs.py
Fix IRF figure HAWC data

@@ -15,7 +15,7 @@ logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 
 fermi_livetime = 5e7 * u.s
-hawc_lifetime = 56.53223 * u.day
+hawc_lifetime = 6.4 * u.h
 
 offset = [1] * u.deg
 
@@ -74,7 +74,7 @@ for nhit_bin in range(5, 10):
     ax_aeff.plot(energy, data, alpha=0.2, color="k")
     aeff_hawc_max.append(data)
 
-aeff_hawc_max = np.stack(aeff_hawc_max).max(axis=0)
+aeff_hawc_max = np.stack(aeff_hawc_max).sum(axis=0)
 
 ax_aeff.plot(
     aeff_hawc.geom.axes["energy_true"].center,

### 2023-01-26 src/ms-review.tex
Address more of CNs comments

@@
 	{
-
 		Traditionally, \gammaray astronomy has been conducted
@@
 	{
-		In this article, we present \gammapy, an open-source python package for the analysis of \gammaray data,
+		In this article, we present \gammapy, an open-source python package for the analysis of astronomical \gammaray data,
 		and illustrate the functionalities of the first long-term release of the software, version 1.0.
 		Built on the modern python scientific ecosystem, \gammapy provides a uniform platform for reducing and
-		modelling data from different gamma-ray instruments. \gammapy complies with several well-established
+		modelling data from different \gammaray instruments for a variety of analysis scenarios. \gammapy complies with several well-established
 		data conventions in high-energy astrophysics, providing serialised data products that are interoperable
@@
 		Starting from event list and instrument response functions,
-		\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
+		\gammapy provides the funcionality for reducing data binned in energy and sky coordinates.
 		To facilitate the rejection of the residual hadronic background, several techniques for background estimation
@@
 		and assuming a variety of spectral, temporal, and spatial models.
-		Estimation of flux points, likelihood profiles and light curves is also implemented.
+		Estimation of flux points, likelihood profiles and light curves is also supported.
 	}
 	{
-		After describing the structure of the package, we demonstrate the capabilities of \gammapy
-		performing both traditional and novel analyses in gamma-ray astronomy with publicly available data:
-		spectral and spectro-morphological analyses, estimation of the light curve of a source.
+		After describing the structure of the package, we show the capabilities of \gammapy
+		in multiple traditional and novel \gammaray astronomy analysis scenarios using publicly available data
+		such as spectral and spectro-morphological modelling as well as estimation of the spectral energy
+		distribution (SED) and light curve of a source.
 		The flexibility and power of the software are displayed in a final multi-instrument example,
-		where data sets from different instruments, at different stages of data reduction,
-		are simultaneously fitted with a flux model produced by another astrophysical software.
+		where datasets from different instruments, at different stages of data reduction,
+		are simultaneously fitted with an astrophysical flux model produced by another astrophysical software.
 	}{}
@@
 %% abbreviation (WCD) all along the text, later we use "particle samplers"
-\gammaray astronomy is a rather young field of research. The \gammaray~
+\gammaray astronomy is a rather young field of research. The \gammaray
 range of the electromagnetic spectrum provides us insights into the
@@
 Ground-based \gammaray astronomy relies on these extensive air showers to detect the
-primary \gammaray photons and infer their direction and energy.
+primary \gammaray photons and infer their incident direction and energy.
 VHE \gammaray astronomy covers the energy range from fews tens of ${\rm GeV}$ up to the ${\rm PeV}$.
@@
 Imaging Atmospheric Cherenkov Telescopes (IACT) and 
-Water Cherenkov observatories. IACTs obtain images of the atmospheric showers
+Water Cherenkov Detectors (WCD). IACTs obtain images of the atmospheric showers
 by detecting the Cherenkov radiation emitted by the cascading charged particles and
@@
 Water Cherenkov observatories detect particles directly from the tail of the
-shower when it reaches the ground. These instruments have very
-large field-of-view, large duty-cycle but higher energy threshold and
+shower when it reaches the ground. These instruments have a very
+large FoV large duty-cycle but higher energy threshold and
 usually have lower signal to noise ratios compared to IACTs \citep{2015CRPhy..16..610D}.
@@
 %% Context : formats
-%% CN: particle samplers -> WCD
 In practice, the data reduction workflow of all \gammaray observatories
@@
 the data-reduction process, and, eventually, of the detection technique. This implies,
-for example, that hihg-level data from IACT and particle samplers can be represented
+for example, that high-level data from IACTs and WCDs can be represented
 with the same data model. The efforts to prototype a format usable by various instruments
@@
 realized by storing a list of gamma-like events with their measured quantities
-(energy, direction, arrival time) and a parametrisation of the response of the
-system. %% where? in the data units of a FITS file.
+such as energy, incident direction and arrival time and a parametrisation of
+the IRFs associated with the event list data. %% where? in the data units of a FITS file.
 
 %% Context: develoment of open software
-Python has become extremely popular as a scientific programming language,
+In the past deaced Python has become extremely popular as a scientific programming language,
 in particular, in the field of data sciences. This success is
 mostly attributed to the simple and easy to learn syntax, the ability to act as
-a 'glue' language between different programming languages and last but not least
+a "glue" language between different programming languages and last but not least
 the rich ecosystem of packages and its open and supportive community, from
@@
 %%% Question: starting date? Is is relevant, what is the real start?
-The \gammapy project started in 2015 with the objective of building a flexible and
+The \gammapy project started based on the same idea as \astropuy with the objective of building a flexible and
 efficient software library for very high-energy \gammaray data analysis \citep{gammapy_2015}.
@@
 reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
-This sequence, sometimes referred to as low-level analysis, is usually very specific to
-a given observation technique and even to a given instrument.
+This part of the data reduction sequence, sometimes referred to as low-level analysis,
+is usually very specific to a given observation technique and even to a given instrument.
 
@@
 light curves and catalogs. The methods applied here are more generic and are broadly
-shared across the field. They also frequently imply joint analysis of multi-instrument data.
-%% CN: I don't understand this: since the high-level methods are the same, then they "imply"
-%% joint analyses?? Maybe they eventually allow or permit?
+shared across the field. The similarity in the high-level analysis would also allow
+for combining data from multiple instruments, but could not be fully exploited, due to
+a lack of common data formats and software tools.
 
@@
 In the most general way, we can write the expected number of detected events from the sky model $\Phi$ at measured position $p$ and energy $E$, for
-a given set of parameters $\hat{\theta}$, as
-\begin{align}
-   N(p, E, \hat{\theta})\,{\rm d}p\,{\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true}) \nonumber \\
+a given set of parameters $\hat{\theta}$, as:
+%
+\begin{equation}
+	\begin{split}
+   		N(p, E, \hat{\theta})\,{\rm d}p\,{\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true}) \\
    		&\times \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} ) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
-\end{align}
+	\end{split}
+\end{equation}
+
 where $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response and $t_{\rm obs}$ is the observation time
@@
 
-\begin{align}
-   R(p, E|p_{\rm true}, E_{\rm true}) = &A_{\rm eff}(p_{\rm true}, E_{\rm true}) \times \nonumber \\
+\begin{equation}
+	\begin{split}
+   R(p, E|p_{\rm true}, E_{\rm true}) = &A_{\rm eff}(p_{\rm true}, E_{\rm true}) \times \\
     &PSF(p|p_{\rm true}, E_{\rm true}) \times \nonumber \\
     &E_{\rm disp}(E|p_{\rm true}, E_{\rm true})
-\end{align}
+	\end{split}
+\end{equation}
+
 where:
@@
 In total, the expected number of events in a \gammaray observation is given by:
-\begin{align}
-  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \star \left[ PSF \star \left( A_{\rm eff} \times t_{\rm obs} \times \Phi(\hat{\theta}) \right) \right]  \nonumber\\
+\begin{equation}
+	\begin{split}
+  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \star \left[ PSF \star \left( A_{\rm eff} \times t_{\rm obs} \times \Phi(\hat{\theta}) \right) \right]\\
                        & + Bkg(p, E) \times t_{\rm obs}
-\end{align}
+	\end{split}
+\end{equation}
+
 %% CN: Instead of rewriting this formula and introducing this new notation for the convolution,
@@
 %% CN: Shouldn't we display the output of this snippet?
-%% otherwise what's teh point of the `print`' functions?
+%% otherwise what's the point of the `print`' functions?
 \begin{figure}
@@
 		Using \code{gammapy.irf} to read and plot instrument response functions.
-		Here we show example instrument response functions of some experiments and
-        observatories for which \gammapy can analyse data. The \cta IRFs
-        are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
+		The left panel shows the effective area as a function of energy for
+		the \cta, \hess, \magic, \hawc and \fermi instruments. The right panel shows
+		the $68\%$ containment radius o as a function of energy for the \cta, \hess
+		and \fermi instruments. These IRFs do not correspond to the latest
+		performance of the instruments, but still are representative of the 
+		detector type and energy range. We also neede to rely on publicly available
+		data. The \cta IRFs are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
         using observation ID 033787. The \magic effective area is computed for a
-        $20\,{\rm min}$ observation at the Crab Nebula coordinates.
-        The point spread function shows the $68\%$
-        containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
+        $20\,{\rm min}$ observation at the Crab Nebula coordinates. The
+		\fermi IRFs use \textit{pass8} data and are also taken at the position of the Crab Nebula.
+		The \hawc effective area is shown for the event classes $N_{Hit}=5 - 9$ as light gray
+		lines along with the sum of all event classes as a black line. The \hawc IRFs are taken from
+		the first public release of event data the \hawc collaboration. All 
+		data is also availabe in the \code{gammapy-data} repository.
     }
@@
 %
-%
-%% CN: description of the HAWC IRF missing, what is the difference between the gray
-%% and black effective areas? Where are they taken from?
 

### 2023-01-26 src/ms-review.tex
Add WStat reference and address more comments by CN

@@
 \subsubsection{Energy Dispersion}
-For \iacts, the energy dispersion is typically parameterised in terms of the so-called
+For \iacts, the energy resolution and bias, or sometimes called energy dispersion,
+is typically parametrised in terms of the so-called
 migration parameter ($\mu$), which is defined as the ratio between the
@@
 designed to handle the raw instrument description, and the \code{EDispKernelMap},
-which contains an energy disperion matrix per sky position. I.e., a 4-dimensional WCS map
-where at each sky-position is associated an energy dispersion matrix.
-The latter is a representation of the energy resolution as a function of the
-true energy only represented by the sub-class \code{EDispKernel}.
-%% CN: I don't understand what "the latter" refers to.
+which contains an energy disperion matrix per sky position. I.e., a 4-dimensional
+sky map where at each position is associated to an energy dispersion matrix.
+The energy dispersion matrix is a representation of the energy resolution
+as a function of the true energy only and implemnted in \gammapy
+by the sub-class \code{EDispKernel}.
 
@@
 
-Some example IRFs read and plotted with \gammapy are shown in Figure~\ref{fig:irfs}.
+Some example IRFs read from public data files and plotted with \gammapy are shown in Figure~\ref{fig:irfs}.
 
@@
 
-The \code{MapAxis} class provides a uniform API for axes representing
+The \code{MapAxis} class provides a uniform application programming interface
+(API) for axes representing
 bins on any physical quantity, such as energy or angular offset.
@@
 independent of the underlying pixelisation scheme.
-%% CN: API acronym not introduced
 
@@
 
-% itemize because it helps me write, could also just be paragraphs...
 \subsubsection{WCS Maps}
@@
 associated statistic, different types of Datasets are supported. The \code{MapDataset} is
-used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
-done using \code{SpectrumDataset}. While the default statistics for both of these is
-\emph{Cash}}, their corresponding ON/OFF versions are adapted for the case where the
-background is measured from real OFF counts, and support \emph{WStat} statistics. The
-predicted counts are computed by convolution of the models with the associated
+used for combined spectral and morphological (3D) fitting, and a 1D spectral fitting is
+done using \code{SpectrumDataset}. While the default fit statistics for both of these
+classes is the \emph{Cash}}~\citep{Cash} statistic, there are other classes which support
+analyses where the background is measured from control regions, so called "off" obervations.
+Those require the use of a different fit statistics, which takes into account the
+uncertainty of the background measurement. This case is covered by the \code{MapDatasetOnOff}
+and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.
+
+The predicted counts are computed by convolution of the models with the associated
 IRFs. Fitting of precomputed flux points is enabled through \code{FluxPointsDataset},
@@
 methods.
-%% CN: references missing for Cash and Wstat statistics
-%% CN: what are the "corresponding on off versions"?
 

### 2023-01-26 src/ms-review.tex
Fix PDF build

@@
 %%% Question: starting date? Is is relevant, what is the real start?
-The \gammapy project started based on the same idea as \astropuy with the objective of building a flexible and
+The \gammapy project started based on the same idea as \astropy with the objective of building a flexible and
 efficient software library for very high-energy \gammaray data analysis \citep{gammapy_2015}.

### 2023-01-27 src/ms-review.tex
review until Sect. 4

@@
 $E_{\rm true}$, and of the position in the field of view, $p_{\rm true}$:
-$$ \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]} $$
+\begin{equation}
+    \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]}
+    \label{eq:general_source_model}
+\end{equation}
 where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. To convert this analytical flux model
@@
 The \code{gammapy.datasets} subpackage contains classes to bundle
-together binned data along with associated models and the likelihood, which
+together binned data along with the associated models and likelihood function, which
 provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
@@
 associated statistic, different types of Datasets are supported. The \code{MapDataset} is
-used for combined spectral and morphological (3D) fitting, and a 1D spectral fitting is
-done using \code{SpectrumDataset}. While the default fit statistics for both of these
-classes is the \emph{Cash}}~\citep{Cash} statistic, there are other classes which support
+used for combined spectral and morphological (3D) fitting, while a 1D spectral 
+fitting can be performed using the \code{SpectrumDataset}.
+While the default fit statistics for both of these classes is the \emph{Cash}}~\citep{Cash}
+statistic, there are other classes which support
 analyses where the background is measured from control regions, so called "off" obervations.
@@
 and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.
+%% CN: Wstat reference not correctly displayed in the PDF
 
@@
 		object. In this way, \code{Maker} classes can be chained
-		to define more complex data reduction "pipelines".
+		to define more complex data reduction pipelines.
     }
@@
 %
-The data reduction step includes all tasks required to process and prepare
-\gammaray data from the DL3 level to modeling and fitting. The \code{gammapy.makers} sub-package
-contains the various classes and functions required to do so. First, events are
-binned and IRFs are interpolated and projected onto the chosen analysis
+The \code{gammapy.makers} sub-package contains the various classes and functions required
+to process and prepare \gammaray data from the DL3 to the DL4, representing the input for modeling and fitting.
+First, events are binned and IRFs are interpolated and projected onto the chosen analysis
 geometry. The end product of the data reduction process are a set of binned counts,
@@
 The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
-responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.
+responsible for this task for 3D and 1D analyses, respectively (see Fig~\ref{ig*:minted:gp_makers}).
 
@@
 Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
-\code{ReflectedRegionsBackgroundMaker} are in charge of this step.
+\code{ReflectedRegionsBackgroundMaker} are in charge of this process.
+%% CN: I would add a single line explaining what each of them do
 
@@
 \label{ssec:gammapy-stats}
-The \code{gammapy.stats} subpackage contains the fit statistics and associated
-statistical estimators that are commonly used in \gammaray astronomy. In
+The \code{gammapy.stats} subpackage contains the fit statistics and the associated
+statistical estimators commonly adopted in \gammaray astronomy. In
 general, \gammaray observations count Poisson-distributed events at various sky
@@
 measurement where only background events are expected is used, the statistic
-function is \emph{WStat}. It is a profile log-likelihood statistic where background
+function is \emph{WStat}. It is a profile log-likelihood statistic where the background
 counts are marginalized parameters. It is used by datasets containing off
@@
 	\label{codeexample:stats} \end{figure}
+%% CN: the figure does not explain what alpha is
 
@@
 \label{sssec:models}
-Source models in \gammapy are four dimensional models which support two
-spatial dimensions define by the sky coordinates $\ell, b$, and energy dimension $E$ as well as
-the time dimension $t$. To simplify the the definition of the
+Source models in \gammapy (Eq.~\ref{eq:general_source_model}) are four-dimensional 
+analytical models which support two spatial dimensions defined by the sky coordinates
+$\ell, b$, an energy dimension $E$, and a time dimension $t$. To simplify the the definition of the
 models, \gammapy uses a factorised representation of the total source
@@
 \begin{equation}
-    f(l, b, E, t) = F(E)  \times G(l, b, E) \times  H(t, E)
+    \phi(\ell, b, E, t) = F(E) \times G(\ell, b, E) \times H(t, E).
+    \label{eq:source_model_dependency}
 \end{equation}
 
-where the spectral model $F$ implicitly includes an \textit{amplitude} parameter
-for the total flux of the model. The spatial model $G$ optionally depends
-on energy and allows to support e.g. energy dependent
-morphology models. The temporal model component $H$
-optionally also supports an energy variable to
-allow for spectral variations of the model with time.
-
-Following the factorisation the models objects are grouped
-into the following categories:
-\begin{itemize}
-	\item \code{SpectralModel}: models to describe spectral shapes of sources,
-	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources,
-	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
-	      light and phase curves.
-\end{itemize}
+The spectral component $F(E)$, described by the \code{SpectralModel} class, always
+includes an \textit{amplitude} parameter to adjust the total flux of the model.
+The spatial component $G(\ell, b, E)$, described by the \code{SpatialModel} class,
+also depends on energy, in order to consider energy-dependent sources morphology.
+Finally, the temporal component $H(t, E)$, described by the \code{TemporalModel}
+class, also supports an energy dependency in order to consider spectral variations
+of the model with time.
 
@@
 instead of an \textit{amplitude} parameter with physical units. They
-must be used along with another spectral model, as a multiplicative correction
-factor according to their spectral shape. They can be typically used for
-adjusting template based models, or adding taking into account
-the absorbtion effect on 
-\gammaray spectra caused by the extra-galactic background light (EBL) (\code{EBLAbsorptionNormSpectralModel})
-model. \gammapy supports a variety of EBL absorption models, such as
-\cite{Franceschini2008}, \cite{Finke2010} and \cite{Dominguez2011}.
-
-The analytic spatial models are all normalized such as they integrate to
-unity over the sky but the template spatial models may not, so in that special
+can be used as an energy-dependent multiplicative correction
+factor to another spectral model. They are typically used for
+adjusting template-based models, or, for example, to take into account
+the absorbtion effect on \gammaray spectra caused by the extra-galactic background
+light (EBL) (\code{EBLAbsorptionNormSpectralModel}). \gammapy supports a variety
+of EBL absorption models, such as those from \cite{Franceschini2008}, \cite{Finke2010},
+and \cite{Dominguez2011}.
+
+The analytical spatial models are all normalized such as they integrate to
+unity over the entire sky. The template spatial models may not, so in that special
 case they have to be combined with a \code{NormSpectralModel}.
 
-The \code{SkyModel} object represents factorised model that combines the spectral,
-spatial and temporal model components (the spatial and temporal components being
-optional). \code{SkyModel} object represents additive emission components, usually
-sources or diffuse emission, although a single source can also be modeled by
-multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
-has a \code{Models} class.
-
+The \code{SkyModel} class represents the factorised model in Eq.~\ref{eq:source_model_dependency}
+(the spatial and temporal components being optional).
+A \code{SkyModel} object can represent the sum of several emission components:
+either, for example, from multiple sources and from a diffuse emission, or from several spectral
+components within the same source. To handle list of multiple \code{SkyModel} objects, \gammapy
+implements a \code{Models} class.
+
+%% CN: a link to the model gallery?
 The model gallery provides a visual overview of the available models in
@@
 package~\citep{naima}. The modeling framework can be easily extended with
-user-defined models. For example, \agnpy models that describe leptonic radiative
-processes in jetted Active Galactic Nuclei (AGN) can be wrapped into
-\gammapy~\citep[see Section 3.5 of ][]{2021arXiv211214573N} .
-
+user-defined models. For example, the radiaitve models of jetted Active Galactic Nuclei (AGN)
+implemented in \agnpy, can be wrapped into \gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}.
+
+%% CN: here again, print() without output. Is it useful?
 \begin{figure}
@@
 
-The \code{Fit} class provides methods to fit i.e., optimise model parameters and estimate
-parameter errors and correlations. It interfaces with a \code{Datasets} object, which
+%% CN: should we mention that the dataset also include the stat function?
+%% and thus the fit interfaces only with the dataset
+The \code{Fit} class provides methods to fit, i.e. optimise, model parameters and estimate
+their errors and correlations. It interfaces with a \code{Datasets} object, which
 in turn is connected to a \code{Models} object containing the model parameters in its
 \code{Parameters} object. Models can be unique for a given dataset, or contribute to
-multiple datasets, allowing e.g., to do a joint fit to
-multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
+multiple datasets, allowing e.g., to perform a joint fit to
+multiple IACT datasets, or to jointly fit IACT and \fermi dataset. Many
 examples are given in the tutorials.
+%% CN: I would write "to perform a joint fit from multiple datasets from the same instruments
+%% (e.g. collected with different configurations) or from multiple datasets from different gamma-ray
+%% instruments (space- and ground-based)."
 
@@
 }
+%% CN: watchout with giving links to notebooks whose position might change or disappear in the future.
 
@@
 \label{ssec:gammapy-estimators}
-By fitting parametric models to the data, the total integrated
-flux and overall temporal, spectral and morphological shape of the
-\gammaray emission can be constrained. In many cases it is useful
-to make a more detailed follow-up analysis by measuring the
+By fitting parametric models to the data, the total \gammaray
+flux and its overall temporal, spectral and morphological components can be constrained.
+In many cases though, it is useful to make a more detailed follow-up analysis by measuring the
 flux in smaller spectral, temporal or spatial bins. This
@@
 model and is fitted in the restricted data range, defined by the 
-bin group, only.
-
-In addition to the best fit flux \textit{norm} all estimators compute
-quantities corresponding to this flux. This includes
+bin group only.
+
+In addition to the best-fit flux \textit{norm}, all estimators compute
+quantities corresponding to this flux. This includes:
 the predicted number of total, signal and background
-counts per flux bin. The total fit statistics
-of the best fit model, the fit statistics of the
-null hypothesis and the difference between both,
+counts per flux bin; the total fit statistics
+of the best fit model; the fit statistics of the
+null hypothesis; and the difference between both,
 the so-called TS value.
-From the TS value the significance of the
-significance of the measured signal and associated flux
+From the TS value the significance of the measured signal and associated flux
 can be derived.
 
-Optionally, it can also compute more advanced quantities
+Optionally, the estimators can also compute more advanced quantities
 such as asymmetric flux errors, flux upper limits
-and one dimensional profiles of the fit statistic,
+and one-dimensional profiles of the fit statistic,
 which show how the likelihood functions varies with
@@
 \gadf SED format \footnote{\url{https://gamma-astro-data-formats.readthedocs.io/en/latest/spectra/flux_points/index.html}},
-FITS based ND sky-maps and formats compatible with Astropy's \code{Table} and
+FITS-based ND sky maps and other formats compatible with Astropy's \code{Table} and
 \code{BinnedTimeSeries} data structures. This allows
-users to directly further analyse the results, e.g.
-standard algorithms for time analysis such as
-computing Lomb-Scargle periodograms or Bayesian
-blocks for time series. So far, \gammapy does not
-support 'unfolding' of \gammaray spectra.
+users to further analyse the results with Astropy, for example using
+standard algorithms for time analysis, such as
+the Lomb-Scargle periodogram or the Bayesian
+blocks. So far, \gammapy does not support unfolding of \gammaray spectra.
 Methods for this will be implemented in a future version of \gammapy.
+%% CN: reference for unfolding https://ui.adsabs.harvard.edu/abs/2007NIMPA.583..494A/abstract
 
@@
 light curves production.
+%% CN: I would not say that these are use cases, rather analysis or data reduction steps
 
@@
 \label{sec:applications}
-
-\gammapy is in use for a variety of science cases by different IACT
-experiments leading to more than 60 publications
+%% CN: I think we never explained what gammapy-data is and we should have at this point 
+%% (it is used without mention also in the TSEstimator example).
+\gammapy is currently used for a variety of analysis by different IACT
+experiments and has already been employed in more than 60 scientific publications
 \footnote{\href{https://ui.adsabs.harvard.edu/search/q=(\%20(citations(doi\%3A\%2210.1051\%2F0004-6361\%2F201834938\%22)\%20OR\%20citations(bibcode\%3A2017ICRC...35..766D))\%20AND\%20year\%3A2014-2023)&sort=date\%20desc\%2C\%20bibcode\%20desc&p_=0}{List on ADS}}.
-The analysis examples shown in the following section are limited by the availability
-of public data. In general, there is no limitation on performing a specific analysis
-on data from a given instrument.
+In this section, we illustrate the capabilities of Gammapy by performing some standard
+analyses cases commonly considered in gamma-ray astronomy.
+The examples shown are limited by the availability of public data,
+with those employed being publicly available data collected within the \code{gammapy-data} repository.
+We remark that, as long as the data are compliant with the GADF specifications,
+and hence with Gammapy's data structures, there is no limitation on performing
+analyses of data from a given instrument.
 

### 2023-01-27 src/ms-review.tex

@@
 %% (it is used without mention also in the TSEstimator example).
-\gammapy is currently used for a variety of analysis by different IACT
+\gammapy is currently used for a variety of analyses by different IACT
 experiments and has already been employed in more than 60 scientific publications
@@
 In this section, we illustrate the capabilities of Gammapy by performing some standard
-analyses cases commonly considered in gamma-ray astronomy.
+analysis cases commonly considered in \gammaray astronomy.
+Beside reproducing standard methodologies, we illustrate the unique data combination
+capabilites of Gammapy by presenting a multi-instrument analysis to date not possible within any
+of the current instrument private software frameworks.
 The examples shown are limited by the availability of public data,
@@
 result of such an analysis performed on three simulated CTA observations is
-shown in Figure~\ref{fig:cta_galactic_center}. In this case the spectrum was
+shown in Fig.~\ref{fig:cta_galactic_center}. In this case the spectrum was
 measured in a circular aperture centered on the Galactic Center, in
@@
 chooses a region of interest and energy binning, both defined by a
-\code{RegionGeom}. In a second step the events and the IRFs are binned
+\code{RegionGeom}. In a second step, the events and the IRFs are binned
 into maps of this geometry, by the \code{SpectrumDatasetMaker}. All the data and
@@
 \code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
-illustrated for all three observations on top of the map of counts. After
-reduction of the data it was modelled using a forward-folding method and a
-power law spectral shape, using the \code{PowerLawSpectralModel} and \code{Fit} class.
-Based on this best fit model the final flux points and corresponding
+illustrated for all three observations overlayed on the counts map in Fig.~\ref{fig:cta_galactic_center}.
+After reduction, the data were modelled using a forward-folding method and assuming
+a point source with a power law spectral shape, using the \code{PowerLawSpectralModel}
+and \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
 log-likelihood profiles are computed using the \code{FluxPointsEstimator}.
+%% CN: maybe say that a SkyModel containing only a PowerLawSpectralModel was associated
+%% with the SpectrumDataset, to be consisted with what was presented in the 
+%% gammapy.models and gammapy.fit subsections?
 
@@
 		Example of 1D spectral analysis of the Galactic Center for three simulated CTA
-		observations for the 1DC dataset. The left image shows the maps of counts with the measurement
+		observations for the 1DC dataset. The left image shows the maps of counts with the signal
 		region in white and background regions overlaid in different colors. The right image
@@
 \end{figure*}
+%% CN: expand 1DC acronym and add a reference, here or in the section text
 
@@
 
-For such situations a more complex approach is needed, the so-called 3D
+For such situations, a more complex approach is needed, the so-called 3D
 analysis. The three relevant dimensions are the two spatial angular coordinates
@@
 
-The \fermi data is introduced at the data level DL4. It is prepared 
-using the standard \textit{fermitools} \citep{Fermitools2019} and
+The \fermi data is introduced at the data level DL4, and directly bundled in a
+\code{MapDataset}. They ahve been prepared using the standard \textit{fermitools} \citep{Fermitools2019} and
 selecting a region of $5^{\circ} \mathrm{x} 4^{\circ}$ around the
@@
 
-The \magic data is included from the data level DL3. It consists of %% shall we explain exactly which type of Map is created?
+The \magic data is included from the data level DL3. Thye consist of two
 observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
@@
 source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
-range spans $80\,{\rm GeV} - 20\,{\rm TeV}$. They are reduced to ON/OFF
-dataset before being fitted. \hawc flux points data are estimated
-in~\cite{hawc_crab_2019} with $2.5\,{\rm years}$ of data and span an energy
-range $300\,{\rm GeV} - 300\,{\rm TeV}$, and directly read with \gammapy.
-
-In the case the \hawc data is included from the DL5 data level, meaning
-flux points and associated errors provided by \cite{hawc_crab_2019}.
-
-\gammapy automatically generates a likelihood including three different types
-of terms, two Poissonian likelihoods for the \fermi map and the
-ON/OFF counts, and a $\chi^2$ accounting for the \hawc flux points. For \fermi, a 
-three-dimensional forward folding of the sky model with the IRF is performed,
-in order to compute the predicted counts in each sky-coordinate and energy bin.
-For \magic, a one-dimensional forward-folding of the spectral model with the
-\irfs is performed to predict the counts in each estimated energy bin. A log
-parabola is fitted to the almost five decades in energy $10\,{\rm GeV} -
-	300\,{\rm TeV}$. %% is the LP formula specified elsewhere?
+range spans $80\,{\rm GeV} - 20\,{\rm TeV}$. They data reduction for the 1D analysis
+is applied, and the data are reduced to a \code{SpectrumDataset} before being fitted.
+
+\hawc data are directly provided as flux points (DL5 data level) and are read
+via Gammapy's \code{FluxPoints} class. They were estimated in ~\cite{hawc_crab_2019}
+with $2.5\,{\rm years}$ of data and span an energy range $300\,{\rm GeV} - 300\,{\rm TeV}$.
+
+Combining the datasets in a \code{Datasets} list, \gammapy automatically generates
+a likelihood including three different types of terms, two Poissonian likelihoods
+for \fermi's \code{MapDataset} and MAGIC's \code{SpectrumDataset}, and a $\chi^2$
+accounting for the \hawc flux points. For \fermi, a three-dimensional forward folding
+of the sky model with the IRF is performed, in order to compute the predicted counts
+in each sky-coordinate and energy bin. For \magic, a one-dimensional forward-folding
+of the spectral model with the \irfs is performed to predict the counts in each estimated energy bin. A log
+parabola is fitted to the almost five decades in energy $10\,{\rm GeV} - 300\,{\rm TeV}$.
+%% CN: is the LP formula specified elsewhere?
 
@@
 dataset described in the previous section and we fit it with an inverse
-Compton model computed with Naima and wrapped in the \gammapy fitting
- routine with the \code{NaimaSpectraModel} class. We consider a log-parabolic
-electron distribution scattering: the synchrotron radiation produced by
-the same electrons; near and far infrared photon fields and the cosmic
+Compton model computed with Naima and wrapped in the \gammapy models
+through the \code{NaimaSpectraModel} class. We describe the gamma-ray emission 
+with an inverse Compton scenario, considering a log-parabolic
+electron distribution that scatters: the synchrotron radiation produced by
+the very same electrons; near and far infrared photon fields and the cosmic
 microwave background (CMB). We adopted the prescription on the target
-photon fields provided in the
-documentation of the \textit{Naima} package \footnote{\url{https://naima.readthedocs.io/en/stable/examples.html\#crab-nebula-ssc-model}}.
+photon fields provided in the documentation of the \textit{Naima}
+package\footnote{\url{https://naima.readthedocs.io/en/stable/examples.html\#crab-nebula-ssc-model}}.
 The best-fit inverse Compton spectrum is represented with a red dashed line in
@@
 source population studies over a large set of coherently detected and modelled objects.
-Early versions of \gammapy were developed in parallel of the preparation of
+Early versions of \gammapy were developed in parallel to the preparation of
 the \hess Galactic plane survey catalog~\citep[HGPS, ][]{2018A&A...612A...1H} and
@@
 
-In short the production of catalogs from \gammaray surveys can be divided in
+In short, the production of catalogs from \gammaray surveys can be divided in
 four main steps: data reduction; object detection; model fitting and model
@@
 
+%% CN: don't like the "a minima in finding local maxima"
 The \iacts data reduction step is done in the same way than described in the 
@@
 the development strategy and organise technical activities. This
-institutionally driven organisation, the permanent staff and commitment of
+institutionally-driven organisation, the permanent staff and commitment of
 supporting institutes ensure the continuity of the executive teams. A core team
@@
 \label{ssec:software-distribution}
-
+%% CN: no mention of ESCAPE? Maybe a little note on the OSSR after metnioning zenodo?
 \gammapy is distributed for Linux, Windows and Mac environments, and installed
@@
 \label{ssec:documentation-and-user-support}
+%% CN: "handwritten" user guide?
 \gammapy provides its user community with a tested and versioned up-to-date
@@
 a developement cycle with major, minor and bugfix releases;
-we basically follow the development cycle of the Astropy
+basically following the development cycle of the Astropy
 project. Thus we expect a major LTS release approximately
@@
 while bug-fix releases will happen as needed. While
-bug-fix releases will not introduce API breaking changes,
+bug-fix releases will not introduce API-breaking changes,
 we will work with a deprecation system for minor releases.
@@
 warnings first and then implemented in the subsequent
-minor release. This approach we consider a fair
+minor release. We consider this approach as a fair
 compromise between the interests of users in a stable
@@
 \textit{showyourwork}~\citep{Luger2021}. This tool coordinates the building
-process and software as well as data dependencies such, that the complete
+process and both software and data dependencies, such that the complete
 manuscript can be reproduced with a single \code{make} command, after

### 2023-01-27 src/ms-review.tex
Update the author list
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

--- 2023-01-26 src/ms-review.tex
@@
 \title{Gammapy: A Python package for gamma-ray astronomy}
-\titlerunning{Gammapy}
-\authorrunning{Deil, Donath, Terrier et al.}
+\titlerunning{The Gammapy library, v1.0}
+\authorrunning{The Gammapy project}
 
 \author{
-	Axel Donath \inst{\ref{inst:6}} \and
-	Christoph Deil \inst{\ref{inst:13}} \and
-	Régis Terrier \inst{\ref{inst:2}} \and
-	Johannes King \inst{\ref{inst:22}} \and
-	Jose Enrique Ruiz \inst{\ref{inst:17}} \and
-	Quentin Remy \inst{\ref{inst:18}} \and
-	Léa Jouvin \inst{\ref{inst:unknown}} \and
-	Atreyee Sinha \inst{\ref{inst:26}} \and
-	Matthew Wood \inst{\ref{inst:11}} \and
-	Fabio Pintore \inst{\ref{inst:14}} \and
-	Manuel Paz Arribas \inst{\ref{inst:unknown}} \and
-	Laura Olivera \inst{\ref{inst:18}} \and
-	Luca Giunti \inst{\ref{inst:2}} \and
-	Bruno Khelifi \inst{\ref{inst:3}} \and
-	Ellis Owen \inst{\ref{inst:21}} \and
-	Brigitta Sipőcz \inst{\ref{inst:5}} \and
-	Olga Vorokh \inst{\ref{inst:unknown}} \and
-	Julien Lefaucheur \inst{\ref{inst:unknown}} \and
-	Fabio Acero \inst{\ref{inst:7}} \and
-	Thomas Robitaille \inst{\ref{inst:1}} \and
-	David Fidalgo \inst{\ref{inst:unknown}} \and
-	Jonathan D. Harris \inst{\ref{inst:unknown}} \and
-	Cosimo Nigro \inst{\ref{inst:15}} \and
-	Lars Mohrmann \inst{\ref{inst:18}} \and
-	Dirk Lennarz \inst{\ref{inst:0}} \and
-	Jalel Eddine Hajlaoui \inst{\ref{inst:2}} \and
-	Alexis de Almeida Coutinho \inst{\ref{inst:27}} \and
-	Matthias Wegenmat \inst{\ref{inst:unknown}} \and
-	Dimitri Papadopoulos \inst{\ref{inst:unknown}} \and
-	Maximilian Nöthe \inst{\ref{inst:25}} \and
-	Nachiketa Chakraborty \inst{\ref{inst:unknown}} \and
-	Michael Droettboom \inst{\ref{inst:20}} \and
-	Helen Poon \inst{\ref{inst:unknown}} \and
-	Arjun Voruganti \inst{\ref{inst:unknown}} \and
-	Jason Watson \inst{\ref{inst:8}} \and
-	Thomas Armstrong \inst{\ref{inst:unknown}} \and
-	Vikas Joshi \inst{\ref{inst:12}} \and
-	Erik Tollerud \inst{\ref{inst:24}} \and
-	Erik M. Bray \inst{\ref{inst:unknown}} \and
-	Domenico Tiziani \inst{\ref{inst:unknown}} \and
-	Gabriel Emery \inst{\ref{inst:unknown}} \and
-	Hubert Siejkowski \inst{\ref{inst:unknown}} \and
-	Kai Brügge \inst{\ref{inst:23}} \and
-	Luigi Tibaldo \inst{\ref{inst:16}} \and
-	Arpit Gogia \inst{\ref{inst:unknown}} \and
-	Ignacio Minaya \inst{\ref{inst:unknown}} \and
-	Marion Spir-Jacob \inst{\ref{inst:unknown}} \and
-	Yves Gallant \inst{\ref{inst:unknown}} \and
-	Andrew W. Chen \inst{\ref{inst:9}} \and
-	Roberta Zanin \inst{\ref{inst:4}} \and
-	Jean-Philippe Lenain \inst{\ref{inst:unknown}} \and
-	Larry Bradley \inst{\ref{inst:24}} \and
-	Kaori Nakashima \inst{\ref{inst:12}} \and
-	Anne Lemière \inst{\ref{inst:2}} \and
-	Mathieu de Bony \inst{\ref{inst:unknown}} \and
-	Matthew Craig \inst{\ref{inst:unknown}} \and
-	Lab Saha \inst{\ref{inst:6}} \and
-	Zé Vinicius \inst{\ref{inst:unknown}} \and
-	Kyle Barbary \inst{\ref{inst:unknown}} \and
-	Thomas Vuillaume \inst{\ref{inst:28}} \and
-	Adam Ginsburg \inst{\ref{inst:unknown}} \and
-	Daniel Morcuende \inst{\ref{inst:unknown}} \and
-	José Luis Contreras \inst{\ref{inst:unknown}} \and
-	Laura Vega Garcia \inst{\ref{inst:unknown}} \and
-	Oscar Blanch Bigas \inst{\ref{inst:unknown}} \and
-	Víctor Zabalza \inst{\ref{inst:unknown}} \and
-	Wolfgang Kerzendorf \inst{\ref{inst:19}} \and
-	Rolf Buehler \inst{\ref{inst:10}} \and
-	Sebastian Panny \inst{\ref{inst:unknown}} \and
-	Silvia Manconi \inst{\ref{inst:unknown}} \and
-	Stefan Klepser \inst{\ref{inst:10}} \and
-	Peter Deiml \inst{\ref{inst:unknown}} \and
-	Johannes Buchner \inst{\ref{inst:unknown}} \and
-	Hugo van Kemenade \inst{\ref{inst:unknown}} \and
-	Eric O. Lebigot \inst{\ref{inst:unknown}} \and
-	Benjamin Alan Weaver \inst{\ref{inst:unknown}} \and
-	Debanjan Bose \inst{\ref{inst:unknown}} \and
-	Rubén López-Coto \inst{\ref{inst:unknown}} \and
-	Sam Carter \inst{\ref{inst:unknown}}
+	{\it Paper Authors} \and
+    Axel \and
+	Régis \and
+	Quentin \and
+	Atreyee \and
+	Cosimo \and
+	Fabio \and
+	Bruno \and
+	Laura \and
+	Jose Enrique \and
+	\\
+	{\it Coordination Committee}\thanks{Corresponding author:
+\href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \and
+	Fabio Acéro \and
+	David Berge \and
+	Catherine Boisson \and
+	Jose Louis Contreras \and
+	Axel Donath \and
+	Stefan Funk \and
+	Christopher van Eldik \and
+	Matthias Fue{\ss}ling \and
+	Jim Hinton \and
+	Bruno Khélifi \and
+	Rub{\'e}n L{\'o}pez-Coto \and
+	Fabio Pintore \and
+	Régis Terrier \and
+	Roberta Zanin \and
+    \\
+	{\it Gammapy Project Contributors} \and
+	Dark Vador \inst{\ref{inst:0}} \and
+	Unknown Contributor \inst{\ref{inst:unknown}}
 }
@@
 \institute{
-	Amazon, Atlanta GA, US \label{inst:0} \and
-	Aperio Software, Insight House, Riverside Business Park, Stoney Common Road, Stansted, Essex, CM24 8PL, UK \label{inst:1} \and
-	Astroparticle and Cosmology Laboratory CNRS, Université de Paris, 10 Rue Alice Domon et Léonie Duquet, 75013 Paris, France \label{inst:2} \and
-	CNRS \label{inst:3} \and
-	CTA Observatory gGmbH, Via Piero Gobetti 93/3 40129 Bologna, Italy \label{inst:4} \and
-	California Institute of Technology, Pasadena CA, US \label{inst:5} \and
-	Center for Astrophysics | Harvard \& Smithsonian, CfA, 60 Garden St., 02138 Cambridge MA, US \label{inst:6} \and
-	DAp/AIM, CEA-Saclay/CNRS, France \label{inst:7} \and
-	DESY \label{inst:8} \and
-	Department of Physics, University of the Free State, PO Box339, Bloemfontein 9300, South Africa \label{inst:9} \and
-	Deutsches Elektronen-Synchrotron, DESY, Platanenallee 6 15738 Zeuthen, Germany \label{inst:10} \and
-	Facebook, 1 Hacker Way, Menlo Park, CA 94025, US \label{inst:11} \and
-	Friedrich-Alexander-Universität Erlangen-Nürnberg, Erlangen Centre for Astroparticle Physics, Erwin-Rommel-Str. 1 91058 Erlangen, Germany \label{inst:12} \and
-	HeidelbergCement AG, Berliner Straße 6, 69120 Heidelberg, Germany \label{inst:13} \and
-	INAF/IASF, via Ugo La Malfa 153,  90146 Palermo, Italy \label{inst:14} \and
-	Institut de Fisica d'altes Energies, IFAE, Edifici Cn, Campus UAB, 08193 Bellaterra (Barcelona), Spain \label{inst:15} \and
-	Institute de Recherche en Astrophysique et Planetologie, IRAP, \label{inst:16} \and
-	Instituto de Astrofísica de Andalucía - CSIC, Gta. de la Astronomía, 18008 Granada, Spain \label{inst:17} \and
-	Max Planck Institut für Kernphysik, MPIK, Saupfercheckweg 1, 69117 Heidelberg, Germany \label{inst:18} \and
-	Michigan State University, Department of Physics and Astronomy, 428 S Shaw Ln East Lansing, MI 48824, US \label{inst:19} \and
-	Mozilla, Mountain View, CA \label{inst:20} \and
-	National Tsing Hua University Institute of Astronomy, Hsinchu, Taiwan \label{inst:21} \and
-	Pamyra \label{inst:22} \and
-	Point 8 GmbH, Rheinlanddamm 201, 44139 Dortmund, Germany \label{inst:23} \and
-	Space Telescope Science Institute, STScI, 3700 San Martin Drive, 21218 Baltimore MD, US \label{inst:24} \and
-	TU Dortmund University, Otto-Hahn-Str. 4a 44227 Dortmund, Germany \label{inst:25} \and
-	Universidad Complutense de Madrid EMFTEL, UCM, Plaza de la Ciencias, 28040 Madrid, Spain \label{inst:26} \and
-	Universidade de São Paulo, Brazil \label{inst:27} \and
-	Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecyde Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:28} \and
+	Fake institute, Vador city, Moon \label{inst:0} \and
 	unknown \label{inst:unknown}

### 2023-01-27 src/ms-review.tex
Reduce the abstract lenght
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 		Traditionally, \gammaray astronomy has been conducted
-		by collaborations of scientists employing proprietary data and analysis software.
+		by experiments employing proprietary data and analysis software.
 		However, the next generation of \gammaray instruments,
-		such as the the Cherenkov Telescope Array (CTA), will be operated as open observatories.
-		Alongside the data, the observatories will make available to the astronomical community
-		software tools for their analysis. This necessity prompted the development, in the last decade,
+		such as the the Cherenkov Telescope Array, will be operated as open observatories.
+		Alongside the data, they will make available to the community
+		software tools for their analysis. This necessity prompted the development
 		of open high-level astronomy software customised for high energy astrophysics.
@@
 	{
-		In this article, we present \gammapy, an open-source python package for the analysis of astronomical \gammaray data,
-		and illustrate the functionalities of the first long-term release of the software, version 1.0.
-		Built on the modern python scientific ecosystem, \gammapy provides a uniform platform for reducing and
-		modelling data from different \gammaray instruments for a variety of analysis scenarios. \gammapy complies with several well-established
-		data conventions in high-energy astrophysics, providing serialised data products that are interoperable
-		with other software.
+		In this article, we present \gammapy, an open-source Python package for the analysis of astronomical \gammaray data,
+		and illustrate the functionalities of its first long-term release, the version 1.0.
+		Built on the modern Python scientific ecosystem, \gammapy provides a uniform platform for reducing and
+		modelling data from different \gammaray instruments for many analysis scenarios. \gammapy complies with
+		several well-established data conventions in high-energy astrophysics, providing serialised data products that
+		are interoperable with other softwares.
 	}
@@
 		Starting from event list and instrument response functions,
-		\gammapy provides the funcionality for reducing data binned in energy and sky coordinates.
-		To facilitate the rejection of the residual hadronic background, several techniques for background estimation
+		\gammapy provides the functionalities for reducing data binned in energy and sky coordinates.
+		To handle the residual hadronic background, several techniques for background estimation
 		are implemented in the package.
@@
 		using Poisson maximum likelihood fitting
-		and assuming a variety of spectral, temporal, and spatial models.
+		and assuming a variety of spectral, temporal and spatial models.
 		Estimation of flux points, likelihood profiles and light curves is also supported.
@@
 		After describing the structure of the package, we show the capabilities of \gammapy
-		in multiple traditional and novel \gammaray astronomy analysis scenarios using publicly available data
-		such as spectral and spectro-morphological modelling as well as estimation of the spectral energy
-		distribution (SED) and light curve of a source.
-		The flexibility and power of the software are displayed in a final multi-instrument example,
+		in multiple traditional and novel \gammaray analysis scenarios using public data
+		such as spectral and spectro-morphological modelling and estimations of a spectral energy
+		distribution and a light curve.
+		Its flexibility and its power are displayed in a final multi-instrument example,
 		where datasets from different instruments, at different stages of data reduction,
-		are simultaneously fitted with an astrophysical flux model produced by another astrophysical software.
+		are simultaneously fitted with an astrophysical flux model.
 	}{}
@@
 		different instruments and perform a joint analysis.
-		\gammapy is built on the scientific python ecosystem, and the required dependencies
+		\gammapy is built on the scientific Python ecosystem, and the required dependencies
 		are shown below the \gammapy logo.
@@
 %% Context: develoment of open software
-In the past deaced Python has become extremely popular as a scientific programming language,
+In the past decade Python has become extremely popular as a scientific programming language,
 in particular, in the field of data sciences. This success is
@@
 
-%\gammapy is built on the scientific Python stack and makes use of Astropy.
-
-%% \gammapy: from first developments to validation and selection
 %% CN: what about mentioning the joint Crab? or is it mentioned later?

### 2023-01-27 src/ms-review.tex
Fix the call of some reference
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>
Remove a comment
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>
Adjust itemize formatting

@@
    		N(p, E, \hat{\theta})\,{\rm d}p\,{\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true}) \\
-   		&\times \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} ) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
+   		&\cdot \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} ) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
 	\end{split}
@@
 	\begin{split}
-   R(p, E|p_{\rm true}, E_{\rm true}) = &A_{\rm eff}(p_{\rm true}, E_{\rm true}) \times \\
-    &PSF(p|p_{\rm true}, E_{\rm true}) \times \nonumber \\
-    &E_{\rm disp}(E|p_{\rm true}, E_{\rm true})
+   R(p, E|p_{\rm true}, E_{\rm true}) = &~A_{\rm eff}(p_{\rm true}, E_{\rm true}) \\
+	& \cdot PSF(p|p_{\rm true}, E_{\rm true})\\
+    & \cdot E_{\rm disp}(E|p_{\rm true}, E_{\rm true})
 	\end{split}
@@
 \begin{itemize}
+\setlength\itemsep{1em}
 \item $A_{\rm eff}(p_{\rm true}, E_{\rm true})$ is the effective collection area of the detector. It is the product
@@
 	\begin{split}
-  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \star \left[ PSF \star \left( A_{\rm eff} \times t_{\rm obs} \times \Phi(\hat{\theta}) \right) \right]\\
-                       & + Bkg(p, E) \times t_{\rm obs}
+  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \star \left[ PSF \star \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
+                       & + Bkg(p, E) \cdot t_{\rm obs}
 	\end{split}
@@
 and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.
-%% CN: Wstat reference not correctly displayed in the PDF
 
@@
 \begin{equation}
-    \phi(\ell, b, E, t) = F(E) \times G(\ell, b, E) \times H(t, E).
+    \phi(\ell, b, E, t) = F(E) \cdot G(\ell, b, E) \cdot H(t, E).
     \label{eq:source_model_dependency}
@@
 \begin{itemize}
+	\setlength\itemsep{1em}
 	\item \iminuit~\citep{iminuit}
@@
 July 29 - 30, 2006~\cite{2009A&A...502..749A}. The data are publicly available 
-as a part of the HESS-DL3-DR1~\cite{HESS-DL3-DR1}, and shipped with
+as a part of the HESS-DL3-DR1~\cite{HESS_DR1}, and shipped with
 \verb"GAMMAPY_DATA". Each observation is first split into 10 min smaller

### 2023-01-27 src/ms-review.tex
Add map class references

@@
 is typically used for smaller regions of interests, such as pointed
-observations.
+observations and is represented by a combination of the
+\code{WcsGeom} and \code{WcsNDMap} class.
 
@@
 on projecting the HEALPix data to a local tangential WCS grid.
+This data structure is represented by the \code{HpxGeom} and \code{HpxNDMap}
+classes.
 
@@
 package \citep{AstropyRegions2022}, which is both used as an API to define regions
-for users as well as handling the underlying geometric operations.
+for users as well as handling the underlying geometric operations. Region based
+maps are represented by the \code{RegionGeom} and \code{RegionNDMap} classes.
 

### 2023-01-27 src/ms-review.tex
Smoothen the introduction a bit

@@
 % \documentclass[]{aa}
-\documentclass[traditabstract, longauth]{aa}
+\documentclass[longauth]{aa}
 
@@
 \newcommand{\agnpy}{Agnpy\xspace}
+\newcommand{\matplotlib}{Matplotlib\xspace}
 
@@
 There are two main categories of ground-based instruments:
-Imaging Atmospheric Cherenkov Telescopes (IACT) and 
-Water Cherenkov Detectors (WCD). IACTs obtain images of the atmospheric showers
+
+\textit{Imaging Atmospheric Cherenkov Telescopes (IACT)} obtain images of the atmospheric showers
 by detecting the Cherenkov radiation emitted by the cascading charged particles and
@@
 good energy and angular resolution.
+
+\textit{Water Cherenkov Detectors (WCD)} detect particles directly from the tail of the
+shower when it reaches the ground. These instruments have a very
+large FoV large duty-cycle but higher energy threshold and
+usually have lower signal to noise ratios compared to IACTs \citep{2015CRPhy..16..610D}.
 
@@
 
-Water Cherenkov observatories detect particles directly from the tail of the
-shower when it reaches the ground. These instruments have a very
-large FoV large duty-cycle but higher energy threshold and
-usually have lower signal to noise ratios compared to IACTs \citep{2015CRPhy..16..610D}.
-
 %% Context
@@
 
-%% Context: develoment of open software
-In the past decade Python has become extremely popular as a scientific programming language,
+%% Context: development of open software
+In the past decade observing the \gammaray sky has transitioned from a niche in the field of
+particle physics to an established branch of astronomy, completing the view of the
+sky in high energies. At the same time \textit{Python}
+has become extremely popular as a scientific programming language,
 in particular, in the field of data sciences. This success is
@@
 a "glue" language between different programming languages and last but not least
-the rich ecosystem of packages and its open and supportive community, from
-core numerical analysis packages such as \numpy~\citep{numpy} and
-\scipy~\citep{2020SciPy-NMeth}, visualization libraries, e.g. Matplotlib \citep{matplotlib},
-to optimization packages such as \iminuit \citep{iminuit}.
-
-The \astropy~\citep{astropy} project was created in 2012 to build a community-developed
-Python package for astronomical research. Among other things, it offers functionalities for
-transforming and representing astronomical coordinates, manipulating physical quantities
-and their units as well as reading and writing FITS files.
+the rich ecosystem of packages and its open and supportive community \citep{Momcheva2015}.
+
+In the sub-field of astronomy, it was the \astropy project \citep{astropy} that 
+was created in 2012 to build a community-developed core Python package for astronomy.
+It offers basic functionalities that astronomers of many fields needs, such as representing
+and transforming astronomical coordinates, manipulating physical quantities includinf units
+as well as reading and writing FITS files.
 
@@
 %%% Question: starting date? Is is relevant, what is the real start?
-The \gammapy project started based on the same idea as \astropy with the objective of building a flexible and
-efficient software library for very high-energy \gammaray data analysis \citep{gammapy_2015}.
-This is possible thanks to the definition of a standardised common data format such as the \gadf, and thanks to
-an open development with a broad community of contributors. The relation of \gammapy to the
-different instruments and the \gadf data format is illustrated in Figure~\ref{fig:big_picture}.
+The \gammapy project was started following the idea of \astropy: the objective of building a common
+software library for very high-energy \gammaray data analysis \citep{gammapy_2015}. 
+The core of the idea is illustrated in Figure~\ref{fig:big_picture}. Various \gammaray instruments
+export their data to a standardised common data format the \gadf. This data can then be combined and
+analysed using a single common software library. This means that the \gammapy package is not a part of
+any instrument, but an independent community developed software project. The \gammapy package is
+is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
+structures, \scipy~\citep{2020SciPy-NMeth} for numerical algorithms, \astropy~\citep{astropy} for
+astronomy-specific functionality, and \matplotlib~\citep{matplotlib} for visualization.
 
 %% CN: what about mentioning the joint Crab? or is it mentioned later?
-The \hess collaboration released a limited test dataset (about 50 hours of
-observations taken between 2004 and 2008) based  on the \gadf DL3 format \citep{HESS_DR1}.
-This data release served as a basis for validation of open analysis tools,
-including \gammapy \cite[see e.g.][]{Mohrmann2019}.
+With the public availability of the \gadf format sepcifications and the 
+\gammapy package, some experiments started to make limited subsets of
+their \gammaray data publicly available for testing and validating
+\gammapy. For example, the \hess collaboration released a limited test
+dataset (about 50 hours of observations taken between 2004 and 2008)
+based  n the \gadf DL3 format \citep{HESS_DR1}. This data release served
+as a basis for validation of open analysis tools, including \gammapy 
+\cite[see e.g.][]{Mohrmann2019}. The \hawc collaboration also released
+a limited test dataset of the Crab Nebula, which was used to validate
+the \gammapy package in \cite{Olivera2022}.
 

### 2023-01-27 src/ms-review.tex
Address simple comments by CN

@@
 
-%% CN: what is a index file?
 A typical usage example is shown in Figure~\ref{fig*:minted:gp_data}.
 First a \code{DataStore} object is created from the path of the data
-directory, which contains the DL3 data index file. The \code{DataStore}
+directory. The directory contains an observation as well as FITS HDU 
+index file which assigns the correct data and IRF FITS files and HDUs
+to the given observation ID. The \code{DataStore}
 object gathers a collection of observations and provides ancillary
@@
 \footnote{\href{https://ui.adsabs.harvard.edu/search/q=(\%20(citations(doi\%3A\%2210.1051\%2F0004-6361\%2F201834938\%22)\%20OR\%20citations(bibcode\%3A2017ICRC...35..766D))\%20AND\%20year\%3A2014-2023)&sort=date\%20desc\%2C\%20bibcode\%20desc&p_=0}{List on ADS}}.
-In this section, we illustrate the capabilities of Gammapy by performing some standard
+In this section, we illustrate the capabilities of \gammapy by performing some standard
 analysis cases commonly considered in \gammaray astronomy.
@@
 result of such an analysis performed on three simulated CTA observations is
-shown in Fig.~\ref{fig:cta_galactic_center}. In this case the spectrum was
+shown in Fiure~\ref{fig:cta_galactic_center}. In this case the spectrum was
 measured in a circular aperture centered on the Galactic Center, in
@@
 \code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
-illustrated for all three observations overlayed on the counts map in Fig.~\ref{fig:cta_galactic_center}.
+illustrated for all three observations overlayed on the counts map in Figure~\ref{fig:cta_galactic_center}.
 After reduction, the data were modelled using a forward-folding method and assuming
-a point source with a power law spectral shape, using the \code{PowerLawSpectralModel}
-and \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
+a point source with a power law spectral shape. The model was defined, using
+the \code{SkyModel} class with a \code{PowerLawSpectralModel} spectral component only.
+This model was then combined with the \code{SpectrumDataset}, which contains the reduced data 
+and fitted using the and \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
 log-likelihood profiles are computed using the \code{FluxPointsEstimator}.
-%% CN: maybe say that a SkyModel containing only a PowerLawSpectralModel was associated
-%% with the SpectrumDataset, to be consisted with what was presented in the 
-%% gammapy.models and gammapy.fit subsections?
 
@@
 	\caption{
-		Example of 1D spectral analysis of the Galactic Center for three simulated CTA
+		Example of a one dimensional spectral analysis of the Galactic Center for three simulated CTA
 		observations for the 1DC dataset. The left image shows the maps of counts with the signal
@@
 
-%% CN: don't like the "a minima in finding local maxima"
 The \iacts data reduction step is done in the same way than described in the 
-previous sections but scale up to few thousands of observations. The object
- detection step consists a minima in
-finding local maxima in the significance (or TS) maps,  given by the
-\code{ExcessMapEstimator} (or \code{TSMapEstimator} respectively).  Further refinements can
+previous sections but scaled up to few thousands of observations. The object
+detection step typically consists in finding local maxima in the significance or TS maps,
+computed by the \code{ExcessMapEstimator} or \code{TSMapEstimator} respectively.
+ Further refinements can
 include for example filtering and detection on these maps with techniques from
@@
 \label{ssec:software-distribution}
-%% CN: no mention of ESCAPE? Maybe a little note on the OSSR after metnioning zenodo?
 \gammapy is distributed for Linux, Windows and Mac environments, and installed
@@
 \label{ssec:documentation-and-user-support}
-%% CN: "handwritten" user guide?
 \gammapy provides its user community with a tested and versioned up-to-date
@@
 codebase Python scripts, as well as a set of RST files and Jupyter notebooks.
-The documentation includes a handwritten user guide, a set of executable
+The documentation includes a user guide, a set of executable
 tutorials, and a reference to the API automatically extracted from the code and

### 2023-01-27 src/figures/big_picture.py

@@ -312,7 +312,7 @@ def main(draft=True):
 
     ypos = 40
     plot_gp_logo(ax=ax, offset=(70, ypos), fontsize=150, sub_title="")
-    plot_gadf_icon(ax=ax, offset=(70, ypos + 2), text="DL3\nGADF", size=18)
+    plot_gadf_icon(ax=ax, offset=(70, ypos + 2), text="GADF", size=18)
 
     ax.tick_params(axis="both", direction="in", pad=-20)
     ax.xaxis.set_minor_locator(MultipleLocator(10))

### 2023-01-27 src/ms-review.tex
Use gamma-ray like consistently

@@
 (FITS) format~\citep{fits} encapsulating this high-level information. This is
-realized by storing a list of gamma-like events with their measured quantities
+realized by storing a list of \gammaray-like events with their measured quantities
 such as energy, incident direction and arrival time and a parametrisation of
@@
 \section{Gamma-ray Data Analysis}
-% CN: gamma-like here, was \gammaray-like in the previous section
 \begin{figure*}[h!]
@@
 		\gammapy sub-package structure and data analysis workflow. The top row
-        defines the different levels of data reduction, from lists of gamma-like
+        defines the different levels of data reduction, from lists of \gammaray-like
         events on the left (DL3), to high-level scientific products products
@@
 %% maybe add (see Fig.~1)
-\gammaray data at the Data Level 3 (DL3) therefore consist of lists of gamma-like events and their
+\gammaray data at the Data Level 3 (DL3) therefore consist of lists of \gammaray-like events and their
 corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),
@@
 
+\appendix
+
 \end{document}

### 2023-01-27 src/code-examples/minted.py
Add code example output

@@ -1,6 +1,6 @@
-from pathlib import Path
-import subprocess
 import logging
+import subprocess
+from pathlib import Path
 
 log = logging.getLogger(__file__)
 logging.basicConfig(level=logging.DEBUG)
@@ -9,11 +9,19 @@ PATH = Path(__file__).parent
 
 SNIPPETS = PATH / "snippets"
 GENERATED = PATH / "generated"
+GENERATED_OUTPUT = PATH / "generated-output"
+
+EXCLUDE_OUTPUT = [
+    "gp_catalogs.py",
+    "gp_estimators.py",
+    "gp_makers.py",
+]
 
 # for example 'frame=single' to frame the code
-OPTIONS = 'frame=lines,style=friendly,linenos=0'
+OPTIONS = "frame=lines,style=friendly,linenos=0"
+OPTIONS_OUTPUT = "frame=lines,style=nord,linenos=0"
 
-if __name__ == '__main__':
+if __name__ == "__main__":
     GENERATED.mkdir(exist_ok=True)
 
     filenames = SNIPPETS.glob("*.py")
@@ -27,3 +35,30 @@ if __name__ == '__main__':
         command += [f"{filename}"]
         log.info(f"Executing {' '.join(command)}")
         subprocess.call(command)
+
+    filenames = SNIPPETS.glob("*.py")
+    GENERATED_OUTPUT.mkdir(exist_ok=True)
+
+    for filename in filenames:
+        if filename.name in EXCLUDE_OUTPUT:
+            continue
+
+        command = ["pygmentize"]
+        command += ["-O", f"verboptions={OPTIONS_OUTPUT}"]
+        command += ["-f", "tex"]
+
+        filename_out = GENERATED_OUTPUT / filename.name.replace(".py", ".tex")
+        command += ["-o", f"{filename_out}"]
+        log.info(f"Executing {' '.join(command)}")
+
+        p = subprocess.Popen(
+            command,
+            stdout=subprocess.PIPE,
+            stdin=subprocess.PIPE,
+            stderr=subprocess.PIPE,
+        )
+
+        proc = subprocess.Popen(["python", str(filename)], stdout=subprocess.PIPE)
+        out = proc.communicate()[0]
+
+        stdout_data = p.communicate(input=out)[0]

### 2023-01-27 src/code-examples/snippets/gp_stats.py
Improve stats code example

@@ -6,12 +6,11 @@ alpha = [0.8, 0.5, 0.1]
 stat = WStatCountsStatistic(n_on, n_off, alpha)
 
 # Excess
-print(stat.n_sig)
+print(f"Excess: {stat.n_sig}")
 
 # Significance
-print(stat.sqrt_ts)
+print(f"Significance: {stat.sqrt_ts}")
 
-# Asymmetrical rrors
-print(stat.compute_errn(1.))
-print(stat.compute_errp(1.))
-
+# Asymmetrical errors
+print(f"Error Neg.: {stat.compute_errn(n_sigma=1.0)}")
+print(f"Error Pos.: {stat.compute_errp(n_sigma=1.0)}")

### 2023-01-27 src/ms-review.tex
Add Appendix with code example output

@@
         as attributes on the \code{Observation} object, such as \code{.events}
-        or \code{.aeff} for the effective area information.
+        or \code{.aeff} for the effective area information. The output
+		of the code example is shown in Figure~\ref{fig:code_example_gp_data}.
     }
@@
 The class functionalities offer the possibility to read from files or to create
-it from scratch. {The \code{EffectiveAreaTable2D} class can also convert, interpolate,
+it from scratch. The \code{EffectiveAreaTable2D} class can also convert, interpolate,
 write, and evaluate the effective area for a given energy and offset angles, or
@@
 the FITS World Coordinate System (WCS), the HEALPix pixelization and
-region-based data structure (see Figure~\ref{ig*:minted:gp_maps}).
+region-based data structure (see Figure~\ref{fig*:minted:gp_maps}).
 This allows uses to perform the same higher level operations on maps
@@
         unit. Region definitions can be passed as strings following
-        the DS9 region specifications \url{http://ds9.si.edu/doc/ref/region.html}.
-        }
-    \label{ig*:minted:gp_maps}
+        the DS9 region specifications \url{http://ds9.si.edu/doc/ref/region.html}.The output
+		of the code example is shown in Figure~\ref{fig:code_example_gp_maps}.
+        }
+    \label{fig*:minted:gp_maps}
 \end{figure}
@@
         environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
-        by \gammapy.
+        by \gammapy. The output
+		of the code example is shown in Figure~\ref{fig:code_example_gp_datasets}.
     }
@@
 fitting can be performed using the \code{SpectrumDataset}.
-While the default fit statistics for both of these classes is the \emph{Cash}}~\citep{Cash}
+While the default fit statistics for both of these classes is the \emph{Cash}~\citep{Cash}
 statistic, there are other classes which support
@@
 		object. In this way, \code{Maker} classes can be chained
-		to define more complex data reduction pipelines.
-    }
-	\label{ig*:minted:gp_makers}
+		to define more complex data reduction pipelines. The output
+		of the code example is shown in Figure~\ref{fig:code_example_gp_makers}.
+    }
+	\label{fig*:minted:gp_makers}
 \end{figure}
@@
 The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
-responsible for this task for 3D and 1D analyses, respectively (see Fig~\ref{ig*:minted:gp_makers}).
+responsible for this task for 3D and 1D analyses, respectively (see Figure~\ref{fig*:minted:gp_makers}).
 
@@
         attributes such as \code{stat.n\_sig} and \code{stat.sqrt\_ts}.
-    }
-	\label{codeexample:stats} \end{figure}
+		The output of the code example is shown in Figure~\ref{fig:code_example_gp_stats}.
+    }
+	\label{fig*:minted:gp_stats}
+\end{figure}
 %% CN: the figure does not explain what alpha is
@@
     takes an additional \code{frame} parameter which allow users to define
-    the coordinate frame of the position of the model.
+    the coordinate frame of the position of the model. The output
+	of the code example is shown in Figure~\ref{fig:code_example_gp_models}.
     }
@@
         and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
-        of the flux error and and flux upper limit maps respectively.
+        of the flux error and and flux upper limit maps respectively. The output
+		of the code example is shown in Figure~\ref{fig:code_example_gp_estimators}.
     }
@@
 	\caption{Using \code{gammapy.catalogs} to access the underlying model, flux points and
-		light-curve from the \fermi 4FGL catalog for the blazar PKS 2155-304}
-	\label{codeexample:data}
+		light-curve from the \fermi 4FGL catalog for the blazar PKS 2155-304. The output
+		of the code example is shown in Figure~\ref{fig:code_example_gp_catalogs}.
+	}
+	\label{fig*:minted:gp_catalogs}
 \end{figure}
@@
 \appendix
+\section{Code Examples Output}
+
+\begin{figure}[!ht]
+	\small
+	\import{code-examples/generated-output/}{gp_data}
+	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_data}}
+	\label{fig:code_example_gp_data}
+\end{figure}
+
+\begin{figure}[!ht]
+	\small
+	\import{code-examples/generated-output/}{gp_datasets}
+	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_datasets}}
+	\label{fig:code_example_gp_datasets}
+\end{figure}
+
+\begin{figure}[!ht]
+	\small
+	\import{code-examples/generated-output/}{gp_maps}
+	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_maps}}
+	\label{fig:code_example_gp_maps}
+\end{figure}
+
+\begin{figure}[!ht]
+	\small
+	\import{code-examples/generated-output/}{gp_stats}
+	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_stats}}
+	\label{fig:code_example_gp_stats}
+\end{figure}
+
+\begin{figure*}[!ht]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/gp_makers.pdf}
+	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_makers}}
+	\label{fig:code_example_gp_makers}
+\end{figure*}
+
+\begin{figure*}[!ht]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/gp_estimators.pdf}
+	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_estimators}}
+	\label{fig:code_example_gp_estimators}
+\end{figure*}
+
+\begin{figure*}[!ht]
+	\centering
+	\includegraphics[width=1.\textwidth]{figures/gp_catalogs.pdf}
+	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_catalogs}}
+	\label{fig:code_example_gp_catalogs}
+\end{figure*}
+
+\begin{figure}[!ht]
+	\small
+	\import{code-examples/generated-output/}{gp_models}
+	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_models}}
+	\label{fig:code_example_gp_models}
+\end{figure}
 

### 2023-01-30 src/ms-review.tex
Fix IRF figure caption

@@
 		the \cta, \hess, \magic, \hawc and \fermi instruments. The right panel shows
-		the $68\%$ containment radius o as a function of energy for the \cta, \hess
-		and \fermi instruments. These IRFs do not correspond to the latest
-		performance of the instruments, but still are representative of the 
-		detector type and energy range. We also neede to rely on publicly available
-		data. The \cta IRFs are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
+		the $68\%$ containment radius of the PSF as a function of energy for the \cta, \hess
+		and \fermi instruments. The \cta IRFs are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
         using observation ID 033787. The \magic effective area is computed for a
@@
 		lines along with the sum of all event classes as a black line. The \hawc IRFs are taken from
-		the first public release of event data the \hawc collaboration. All 
-		data is also availabe in the \code{gammapy-data} repository.
+		the first public release of event data the \hawc collaboration. All IRFs do not correspond
+		to the latest performance of the instruments, but still are representative of the 
+		detector type and energy range. We also exclusively relied on publicly available
+		data provided by the collaborations. The data is also availabe in the
+		\code{gammapy-data} repository.
     }

### 2023-02-07 src/ms-review.tex
Rewording in abstract

@@
 		such as the the Cherenkov Telescope Array, will be operated as open observatories.
-		Alongside the data, they will make available to the community
-		software tools for their analysis. This necessity prompted the development
-		of open high-level astronomy software customised for high energy astrophysics.
+		Alongside the data, they will make software tools for their analysis available to the community.
+    This necessity prompted the development of open, high-level astronomy software customised for high energy astrophysics.
 	}
@@
 		In this article, we present \gammapy, an open-source Python package for the analysis of astronomical \gammaray data,
-		and illustrate the functionalities of its first long-term release, the version 1.0.
+		and illustrate the functionalities of its first long-term-support release, version 1.0.
 		Built on the modern Python scientific ecosystem, \gammapy provides a uniform platform for reducing and
-		modelling data from different \gammaray instruments for many analysis scenarios. \gammapy complies with
-		several well-established data conventions in high-energy astrophysics, providing serialised data products that
-		are interoperable with other softwares.
+		modelling data from different \gammaray instruments for many analysis scenarios.
+    \gammapy complies with several well-established data conventions in high-energy astrophysics, providing serialised data products that
+		are interoperable with other software packages.
 	}

### 2023-02-07 src/ms-review.tex
Review introduction

--- 2023-01-30 src/ms-review.tex
@@
 shower when it reaches the ground. These instruments have a very
-large FoV large duty-cycle but higher energy threshold and
-usually have lower signal to noise ratios compared to IACTs \citep{2015CRPhy..16..610D}.
+large FoV, large duty-cycle but higher energy threshold and
+usually have lower signal to noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
 
@@
 instrument. While this model has been successful so far, it does not
-permit easy combination of data from several instruments and therefore,
+permit easy combination of data from several instruments and therefore
 limits the interoperability of existing facilities. This lack of
@@
 %TODO: better transition into context
-The Cherenkov Telescope Array (CTA) will be the first ground-based \gammaray instrument to be operated
-as an open observatory. Its high-level data (e.g. the event list) will be shared publicly after
+The Cherenkov Telescope Array (CTA) will be the first ground-based \gammaray instrument to be operated as an open observatory.
+Its high-level data\footnote{The lowest reduction level of data published by CTAO will be reconstructed event lists and corresponding instrument response functions.} will be shared publicly after
 some proprietary period, and the software required to analyze it will be distributed
@@
 The lists of \gammaray events are then used to derive scientific results, such as spectra, sky maps
-or light curves, taking into account the observatory's specific instrument response functions (IRF).
-Once the data is reduced to a list of events, the information is independent of
-the data-reduction process, and, eventually, of the detection technique. This implies,
+or light curves, taking into account the observation specific instrument response functions (IRF).
+Once the data is reduced to a list of events with reconstructed physical properties of the primary particle,
+the information is independent of the data-reduction process, and, eventually, of the detection technique. This implies,
 for example, that high-level data from IACTs and WCDs can be represented
-with the same data model. The efforts to prototype a format usable by various instruments
-converged in the so-called \textit{Data Format for \gammaray Astronomy}
-initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
-\texttt{gamma-astro-data-format} (\gadf). This proposes prototypical
+with the same data model.
+The efforts to create a common format usable by various instruments
+converged in the so-called \textit{Data Formats for \gammaray Astronomy}
+initiative~\citep{gadf_proc,gadf_universe}, abbreviated to
+\texttt{gamma-astro-data-formats} (\gadf). This proposes prototypical
 specifications to produce files based on the flexible image transport system
 (FITS) format~\citep{fits} encapsulating this high-level information. This is
-realized by storing a list of \gammaray-like events with their measured quantities
-such as energy, incident direction and arrival time and a parametrisation of
+realized by storing a list of \gammaray-like events with their reconstructed and observed
+quantities such as energy, incident direction and arrival time and a parametrisation of
 the IRFs associated with the event list data. %% where? in the data units of a FITS file.
@@
 has become extremely popular as a scientific programming language,
-in particular, in the field of data sciences. This success is
+in particular in the field of data sciences. This success is
 mostly attributed to the simple and easy to learn syntax, the ability to act as
@@
 was created in 2012 to build a community-developed core Python package for astronomy.
-It offers basic functionalities that astronomers of many fields needs, such as representing
-and transforming astronomical coordinates, manipulating physical quantities includinf units
+It offers basic functionalities that astronomers of many fields need, such as representing
+and transforming astronomical coordinates, manipulating physical quantities including units
 as well as reading and writing FITS files.
@@
 %%% Question: starting date? Is is relevant, what is the real start?
-The \gammapy project was started following the idea of \astropy: the objective of building a common
+The \gammapy project was started following the idea of \astropy with the objective of building a common
 software library for very high-energy \gammaray data analysis \citep{gammapy_2015}. 
 The core of the idea is illustrated in Figure~\ref{fig:big_picture}. Various \gammaray instruments
-export their data to a standardised common data format the \gadf. This data can then be combined and
-analysed using a single common software library. This means that the \gammapy package is not a part of
-any instrument, but an independent community developed software project. The \gammapy package is
-is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
+export their data to a standardised common data format -- the \gadf. This data can then be combined and
+analysed using a single common software library.
+This means that the \gammapy package is not specific to any instrument,
+but an independent community developed software project.
+The \gammapy package is is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
 structures, \scipy~\citep{2020SciPy-NMeth} for numerical algorithms, \astropy~\citep{astropy} for
@@
 dataset (about 50 hours of observations taken between 2004 and 2008)
-based  n the \gadf DL3 format \citep{HESS_DR1}. This data release served
+based on the \gadf DL3 format \citep{HESS_DR1}. This data release served
 as a basis for validation of open analysis tools, including \gammapy 

### 2023-02-14 src/ms-review.tex
fix typo

--- 2023-01-30 src/ms-review.tex
@@
 
-The \magic data is included from the data level DL3. Thye consist of two
+The \magic data is included from the data level DL3. They consist of two
 observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate

### 2023-02-21 src/ms-review.tex
Add authors, affiliations and acknowledgements
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 	{\it Paper Authors} \and
-    Axel \and
-	Régis \and
-	Quentin \and
-	Atreyee \and
-	Cosimo \and
-	Fabio \and
-	Bruno \and
-	Laura \and
-	Jose Enrique \and
+    Axel Donath \and
+	Régis Terrier \inst{\ref{inst:20}} \and
+	Quentin Rémy \inst{\ref{inst:17}} \and
+	Atreyee Sinha \inst{\ref{inst:15}} \and
+	Cosimo Nigro \inst{\ref{inst:24}} \and
+	Fabio Pintore \inst{\ref{inst:26}} \and
+	Bruno Khélifi \inst{\ref{inst:20}} \and
+	Laura Olivera-Nieto \inst{\ref{inst:17}}\and
+	Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
 	\\
@@
 \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \and
-	Fabio Acéro \and
-	David Berge \and
-	Catherine Boisson \and
-	Jose Louis Contreras \and
+	Fabio Acero \inst{\ref{inst:1}} \and
+	David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
+	Catherine Boisson \inst{\ref{inst:9}} \and
+	Jose Louis {Contreras} \inst{\ref{inst:15}} \and
 	Axel Donath \and
-	Stefan Funk \and
-	Christopher van Eldik \and
-	Matthias Fue{\ss}ling \and
-	Jim Hinton \and
-	Bruno Khélifi \and
-	Rub{\'e}n L{\'o}pez-Coto \and
-	Fabio Pintore \and
-	Régis Terrier \and
-	Roberta Zanin \and
+	Stefan Funk \inst{\ref{inst:19}} \and
+	Christopher {van Eldik} \inst{\ref{inst:19}} \and
+	Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
+	Jim Hinton \inst{\ref{inst:17}} \and
+	Bruno Khélifi \inst{\ref{inst:20}} \and
+	Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
+	Fabio Pintore \inst{\ref{inst:26}} \and
+	Régis Terrier \inst{\ref{inst:20}} \and
+	Roberta Zanin \inst{\ref{inst:18}} \and
     \\
 	{\it Gammapy Project Contributors} \and
-	Dark Vador \inst{\ref{inst:0}} \and
-	Unknown Contributor \inst{\ref{inst:unknown}}
+	Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
+	Pooja Bhattacharjee \inst{\ref{inst:8}} \and
+	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
+	Johannes Buchner \inst{\ref{inst:12}} \and
+	David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
+	Andrew Chen \inst{\ref{inst:14}} \and
+	Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
+	José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
+	Christoph Deil \inst{\ref{inst:17}} \and
+	Luca Giunti \inst{\ref{inst:20}} \and
+	Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
+	Jean-Philippe Lenain \inst{\ref{inst:22}} \and
+	Maximilian Linhoff \inst{\ref{inst:11}} \and
+	Lars Mohrmann \inst{\ref{inst:17}} \and
+	Daniel Morcuende \inst{\ref{inst:15}} \and
+	Sebastian Panny \inst{\ref{inst:25}} \and
+	Maxime Regeard \inst{\ref{inst:20}} \and
+	Lab Saha \inst{\ref{inst:15}} \and
+	Hubert Siejkowski \inst{\ref{inst:27}} \and
+	Aneta Siemiginowska \inst{\ref{inst:28}} \and
+	Brigitta M {Sipőcz} \inst{\ref{inst:29}} \and
+	Tim Unbehaun \inst{\ref{inst:19}} \and
+	Thomas Vuillaume \inst{\ref{inst:8}}
 }
@@
 \institute{
-	Fake institute, Vador city, Moon \label{inst:0} \and
-	unknown \label{inst:unknown}
+	Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, F-91191 Gif-sur-Yvette, France \label{inst:1} \and
+	Departament de Física Quàntica i Astrofísica (FQA), Universitat de Barcelona (UB),  c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:2} \and
+	Institut de Ciències del Cosmos (ICCUB), Universitat de Barcelona (UB), c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:3} \and
+	Institut d'Estudis Espacials de Catalunya (IEEC), c. Gran Capità, 2-4, 08034 Barcelona, Spain \label{inst:4} \and
+	Departament de Física Quàntica i Astrofísica, Institut de Ciències del Cosmos, Universitat de Barcelona, IEEC-UB, Martí i Franquès, 1, 08028, Barcelona, Spain \label{inst:5} \and
+	Deutsches Elektronen-Synchrotron (DESY), D-15738 Zeuthen, Germany \label{inst:6} \and
+	Institute of physics, Humboldt-University of Berlin, D-12489 Berlin, Germany \label{inst:7} \and
+	Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecy de Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:8} \and
+	Laboratoire Univers et Théories, Observatoire de Paris, Université PSL, Université Paris Cité, CNRS, F-92190 Meudon, France \label{inst:9} \and
+	Point8 GmbH \label{inst:10} \and
+	Astroparticle Physics, Department of Physics, TU Dortmund University, Otto-Hahn-Str. 4a, D-44227 Dortmund \label{inst:11} \and
+	Max Planck Institute for extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany \label{inst:12} \and
+	Max Planck Computing and Data Facility, Gießenbachstraße 2, 85748 Garching \label{inst:13} \and
+	School of Physics, University of the Witwatersrand, 1 Jan Smuts Avenue, Braamfontein, Johannesburg, 2050 South Africa \label{inst:14} \and
+	IPARCOS Institute and EMFTEL Department, Universidad Complutense de Madrid, E-28040 Madrid, Spain \label{inst:15} \and
+	The Hong Kong University of Science and Technology, Department of Electronic and Computer Engineering \label{inst:16} \and
+	Max-Planck-Institut für Kernphysik, P.O. Box 103980, D 69029 Heidelberg, Germany \label{inst:17} \and
+	Cherenkov Telescope Array Observatory gGmbH (CTAO gGmbH) Saupfercheckweg 1 69117 Heidelberg \label{inst:18} \and
+	Erlangen Centre for Astroparticle Physics (ECAP), Friedrich-Alexander-Universität Erlangen-Nürnberg, Nikolaus-Fiebiger Strasse 2, 91058 Erlangen, Germany \label{inst:19} \and
+	Université de Paris Cité, CNRS, Astroparticule et Cosmologie, F-75013 Paris, France  \label{inst:20} \and
+	Meteo France International \label{inst:21} \and
+	Sorbonne Université, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 place Jussieu, 75005 Paris \label{inst:22} \and
+	Instituto de Astrofísica de Andalucía-CSIC, Glorieta de la Astronomía s/n, 18008, Granada, Spain \label{inst:23} \and
+	Institut de Física d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, Bellaterra, 08193 Barcelona, Spain \label{inst:24} \and
+	Institut für Astro- und Teilchenphysik, Leopold-Franzens-Universität Innsbruck, A-6020 Innsbruck, Austria \label{inst:25} \and
+	INAF/IASF Palermo, Via U. La Malfa, 153, 90146 Palermo PA \label{inst:26} \and
+	Academic Computer Centre Cyfronet, AGH University of Science and Technology, Krakow, Poland \label{inst:27} \and
+	Center for Astrophysics | Harvard and Smithsonian \label{inst:28} \and
+	Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:29}
 }
-
-% \abstract{}{}{}{}{}
-% 5 {} token are mandatory
 
@@
 
-The \magic data is included from the data level DL3. They consist of two
+The \magic data is included from the data level DL3. Thye consist of two
 observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
@@
 	all the \gammapy users that have provided feedback and submitted bug reports.
-	J.E.~Ruiz acknowledges financial support from the State Agency for Research of
-	the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the
-	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709). L.~Giunti acknowledges
-	financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014).
+	A.~Aguasca-Cabot acknowledges the financial support from the Spanish Ministry of Science and Innovation
+	and the Spanish Research State Agency (AEI) under grant PID2019-104114RB-C33/AEI/10.13039/501100011034
+	and the Institute of Cosmos Sciences University of Barcelona (ICCUB, Unidad de Excelencia “María de Maeztu”)
+	through grant CEX2019-000918-M. J.L.~Contreras acknowledges the funding from the ESCAPE H2020 project, GA No 824064.
+	L.~Giunti acknowledges financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014). M. Linhoff
+	acknowledges support by the German BMBF (ErUM) and DFG (SFBs 876 and 1491).
+	R.~López-Coto acknowledges the Ramon y Cajal program through grant RYC-2020-028639-I and the financial support
+	from the grant CEX2021-001131-S funded by MCIN/AEI/ 10.13039/501100011033. C.~Nigro C.N. acknowledges support by
+	the Spanish Ministerio de Ciencia e Innovación (MICINN), the European Union – NextGenerationEU and PRTR  through
+	the programme Juan de la Cierva (grant FJC2020-046063-I), by the the MICINN (grant PID2019-107847RB-C41), and from
+	the CERCA program of the Generalitat de Catalunya. Q.~Remy acknowledges support from the project "European Science
+	Cluster of Astronomy \& Particle Physics ESFRI Research Infrastructures" (ESCAPE), that has received funding from
+	the European Union’s Horizon 2020 research and innovation programme under Grant Agreement no. 824064. J.E.~Ruiz
+	acknowledges financial support from the grant
+	CEX2021-001131-S funded by MCIN/AEI/ 10.13039/501100011033. A.~Siemiginowska was supported by NASA contract
+	NAS8-03060 (Chandra X-ray Center). A.~Sinha acknowledges support from The European Science Cluster of Astronomy \&
+	Particle Physics ESFRI Research Infrastructures  funded by the European Union’s Horizon 2020 research and
+	innovation program under Grant Agreement no. 824064 and from the Spanish Ministry of Universities through the
+	Maria Zambrano Talent Attraction Programme, 2021-2023.
 

### 2023-02-21 src/ms-review.tex
Update
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 	Luca Giunti \inst{\ref{inst:20}} \and
+	Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
 	Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
@@
 	Meteo France International \label{inst:21} \and
-	Sorbonne Université, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 place Jussieu, 75005 Paris \label{inst:22} \and
+	Sorbonne Université, Université Paris Diderot, Sorbonne Paris Cité, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252 Paris, France \label{inst:22} \and
 	Instituto de Astrofísica de Andalucía-CSIC, Glorieta de la Astronomía s/n, 18008, Granada, Spain \label{inst:23} \and
@@
 	Center for Astrophysics | Harvard and Smithsonian \label{inst:28} \and
-	Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:29}
+	Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:29} \and
+	Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:30}
 }

### 2023-02-22 src/ms-review.tex
Add Marianne
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 	Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
+	Marianne Lemoine-Goumard \inst{\ref{inst:31}} \and
 	Jean-Philippe Lenain \inst{\ref{inst:22}} \and
@@
 	Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:29} \and
-	Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:30}
+	Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:30} \and
+	Université Bordeaux, CNRS, LP2I Bordeaux, UMR 5797 \label{inst:31}
 }

### 2023-02-22 src/ms-review.tex
Add the affiliation of Axel
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 	{\it Paper Authors} \and
-    Axel Donath \and
+    Axel Donath \inst{\ref{inst:28}} \and
 	Régis Terrier \inst{\ref{inst:20}} \and
@@
 	Jose Louis {Contreras} \inst{\ref{inst:15}} \and
-	Axel Donath \and
+	Axel Donath \inst{\ref{inst:28}} \and
 	Stefan Funk \inst{\ref{inst:19}} \and

### 2023-02-27 src/ms-review.tex

--- 2023-02-21 src/ms-review.tex
@@
 	{\it Paper Authors} \and
-    Axel Donath \and
-	Régis Terrier \inst{\ref{inst:20}} \and
-	Quentin Rémy \inst{\ref{inst:17}} \and
-	Atreyee Sinha \inst{\ref{inst:15}} \and
-	Cosimo Nigro \inst{\ref{inst:24}} \and
-	Fabio Pintore \inst{\ref{inst:26}} \and
-	Bruno Khélifi \inst{\ref{inst:20}} \and
-	Laura Olivera-Nieto \inst{\ref{inst:17}}\and
-	Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
+    Axel \and
+	Régis \and
+	Quentin \and
+	Atreyee \and
+	Cosimo \and
+	Fabio \and
+	Bruno \and
+	Laura \and
+	Jose Enrique \and
 	\\
@@
 \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \and
-	Fabio Acero \inst{\ref{inst:1}} \and
-	David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
-	Catherine Boisson \inst{\ref{inst:9}} \and
-	Jose Louis {Contreras} \inst{\ref{inst:15}} \and
+	Fabio Acéro \and
+	David Berge \and
+	Catherine Boisson \and
+	Jose Louis Contreras \and
 	Axel Donath \and
-	Stefan Funk \inst{\ref{inst:19}} \and
-	Christopher {van Eldik} \inst{\ref{inst:19}} \and
-	Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
-	Jim Hinton \inst{\ref{inst:17}} \and
-	Bruno Khélifi \inst{\ref{inst:20}} \and
-	Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
-	Fabio Pintore \inst{\ref{inst:26}} \and
-	Régis Terrier \inst{\ref{inst:20}} \and
-	Roberta Zanin \inst{\ref{inst:18}} \and
+	Stefan Funk \and
+	Christopher van Eldik \and
+	Matthias Fue{\ss}ling \and
+	Jim Hinton \and
+	Bruno Khélifi \and
+	Rub{\'e}n L{\'o}pez-Coto \and
+	Fabio Pintore \and
+	Régis Terrier \and
+	Roberta Zanin \and
     \\
 	{\it Gammapy Project Contributors} \and
-	Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
-	Pooja Bhattacharjee \inst{\ref{inst:8}} \and
-	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
-	Johannes Buchner \inst{\ref{inst:12}} \and
-	David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
-	Andrew Chen \inst{\ref{inst:14}} \and
-	Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
-	José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
-	Christoph Deil \inst{\ref{inst:17}} \and
-	Luca Giunti \inst{\ref{inst:20}} \and
-	Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
-	Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
-	Jean-Philippe Lenain \inst{\ref{inst:22}} \and
-	Maximilian Linhoff \inst{\ref{inst:11}} \and
-	Lars Mohrmann \inst{\ref{inst:17}} \and
-	Daniel Morcuende \inst{\ref{inst:15}} \and
-	Sebastian Panny \inst{\ref{inst:25}} \and
-	Maxime Regeard \inst{\ref{inst:20}} \and
-	Lab Saha \inst{\ref{inst:15}} \and
-	Hubert Siejkowski \inst{\ref{inst:27}} \and
-	Aneta Siemiginowska \inst{\ref{inst:28}} \and
-	Brigitta M {Sipőcz} \inst{\ref{inst:29}} \and
-	Tim Unbehaun \inst{\ref{inst:19}} \and
-	Thomas Vuillaume \inst{\ref{inst:8}}
+	Dark Vador \inst{\ref{inst:0}} \and
+	Unknown Contributor \inst{\ref{inst:unknown}}
 }
@@
 \institute{
-	Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, F-91191 Gif-sur-Yvette, France \label{inst:1} \and
-	Departament de Física Quàntica i Astrofísica (FQA), Universitat de Barcelona (UB),  c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:2} \and
-	Institut de Ciències del Cosmos (ICCUB), Universitat de Barcelona (UB), c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:3} \and
-	Institut d'Estudis Espacials de Catalunya (IEEC), c. Gran Capità, 2-4, 08034 Barcelona, Spain \label{inst:4} \and
-	Departament de Física Quàntica i Astrofísica, Institut de Ciències del Cosmos, Universitat de Barcelona, IEEC-UB, Martí i Franquès, 1, 08028, Barcelona, Spain \label{inst:5} \and
-	Deutsches Elektronen-Synchrotron (DESY), D-15738 Zeuthen, Germany \label{inst:6} \and
-	Institute of physics, Humboldt-University of Berlin, D-12489 Berlin, Germany \label{inst:7} \and
-	Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecy de Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:8} \and
-	Laboratoire Univers et Théories, Observatoire de Paris, Université PSL, Université Paris Cité, CNRS, F-92190 Meudon, France \label{inst:9} \and
-	Point8 GmbH \label{inst:10} \and
-	Astroparticle Physics, Department of Physics, TU Dortmund University, Otto-Hahn-Str. 4a, D-44227 Dortmund \label{inst:11} \and
-	Max Planck Institute for extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany \label{inst:12} \and
-	Max Planck Computing and Data Facility, Gießenbachstraße 2, 85748 Garching \label{inst:13} \and
-	School of Physics, University of the Witwatersrand, 1 Jan Smuts Avenue, Braamfontein, Johannesburg, 2050 South Africa \label{inst:14} \and
-	IPARCOS Institute and EMFTEL Department, Universidad Complutense de Madrid, E-28040 Madrid, Spain \label{inst:15} \and
-	The Hong Kong University of Science and Technology, Department of Electronic and Computer Engineering \label{inst:16} \and
-	Max-Planck-Institut für Kernphysik, P.O. Box 103980, D 69029 Heidelberg, Germany \label{inst:17} \and
-	Cherenkov Telescope Array Observatory gGmbH (CTAO gGmbH) Saupfercheckweg 1 69117 Heidelberg \label{inst:18} \and
-	Erlangen Centre for Astroparticle Physics (ECAP), Friedrich-Alexander-Universität Erlangen-Nürnberg, Nikolaus-Fiebiger Strasse 2, 91058 Erlangen, Germany \label{inst:19} \and
-	Université de Paris Cité, CNRS, Astroparticule et Cosmologie, F-75013 Paris, France  \label{inst:20} \and
-	Meteo France International \label{inst:21} \and
-	Sorbonne Université, Université Paris Diderot, Sorbonne Paris Cité, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252 Paris, France \label{inst:22} \and
-	Instituto de Astrofísica de Andalucía-CSIC, Glorieta de la Astronomía s/n, 18008, Granada, Spain \label{inst:23} \and
-	Institut de Física d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, Bellaterra, 08193 Barcelona, Spain \label{inst:24} \and
-	Institut für Astro- und Teilchenphysik, Leopold-Franzens-Universität Innsbruck, A-6020 Innsbruck, Austria \label{inst:25} \and
-	INAF/IASF Palermo, Via U. La Malfa, 153, 90146 Palermo PA \label{inst:26} \and
-	Academic Computer Centre Cyfronet, AGH University of Science and Technology, Krakow, Poland \label{inst:27} \and
-	Center for Astrophysics | Harvard and Smithsonian \label{inst:28} \and
-	Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:29} \and
-	Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:30}
-}
+	Fake institute, Vador city, Moon \label{inst:0} \and
+	unknown \label{inst:unknown}
+}
+
+% \abstract{}{}{}{}{}
+% 5 {} token are mandatory
 
@@
 	all the \gammapy users that have provided feedback and submitted bug reports.
-	A.~Aguasca-Cabot acknowledges the financial support from the Spanish Ministry of Science and Innovation
-	and the Spanish Research State Agency (AEI) under grant PID2019-104114RB-C33/AEI/10.13039/501100011034
-	and the Institute of Cosmos Sciences University of Barcelona (ICCUB, Unidad de Excelencia “María de Maeztu”)
-	through grant CEX2019-000918-M. J.L.~Contreras acknowledges the funding from the ESCAPE H2020 project, GA No 824064.
-	L.~Giunti acknowledges financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014). M. Linhoff
-	acknowledges support by the German BMBF (ErUM) and DFG (SFBs 876 and 1491).
-	R.~López-Coto acknowledges the Ramon y Cajal program through grant RYC-2020-028639-I and the financial support
-	from the grant CEX2021-001131-S funded by MCIN/AEI/ 10.13039/501100011033. C.~Nigro C.N. acknowledges support by
-	the Spanish Ministerio de Ciencia e Innovación (MICINN), the European Union – NextGenerationEU and PRTR  through
-	the programme Juan de la Cierva (grant FJC2020-046063-I), by the the MICINN (grant PID2019-107847RB-C41), and from
-	the CERCA program of the Generalitat de Catalunya. Q.~Remy acknowledges support from the project "European Science
-	Cluster of Astronomy \& Particle Physics ESFRI Research Infrastructures" (ESCAPE), that has received funding from
-	the European Union’s Horizon 2020 research and innovation programme under Grant Agreement no. 824064. J.E.~Ruiz
-	acknowledges financial support from the grant
-	CEX2021-001131-S funded by MCIN/AEI/ 10.13039/501100011033. A.~Siemiginowska was supported by NASA contract
-	NAS8-03060 (Chandra X-ray Center). A.~Sinha acknowledges support from The European Science Cluster of Astronomy \&
-	Particle Physics ESFRI Research Infrastructures  funded by the European Union’s Horizon 2020 research and
-	innovation program under Grant Agreement no. 824064 and from the Spanish Ministry of Universities through the
-	Maria Zambrano Talent Attraction Programme, 2021-2023.
+	J.E.~Ruiz acknowledges financial support from the State Agency for Research of
+	the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the
+	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709). L.~Giunti acknowledges
+	financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014).
 

### 2023-03-03 src/ms-review.tex
Address issue #109
Fix #113

--- 2023-02-27 src/ms-review.tex
@@
 %% abbreviation (WCD) all along the text, later we use "particle samplers"
-\gammaray astronomy is a rather young field of research. The \gammaray
-range of the electromagnetic spectrum provides us insights into the
+The \gammaray range of the electromagnetic spectrum provides us insights into the
 most energetic processes in the universe such as those accelerating particles in the surroundings of
@@
 	\begin{split}
-  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \star \left[ PSF \star \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
+  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \circledast \left[ PSF \circledast \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
                        & + Bkg(p, E) \cdot t_{\rm obs}

### 2023-03-03 src/ms-review.tex
Fix #118
Fix #121

@@
 region-based data structure (see Figure~\ref{fig*:minted:gp_maps}).
-This allows uses to perform the same higher level operations on maps
-independent of the underlying pixelisation scheme.
+This allows users to perform the same higher level operations on maps
+independent of the underlying pixelisation scheme. The \code{gammapy.maps}
+package is also used by external packages such as \textit{FermiPy}~\citep{Wood2017}
 
@@
 	\item \code{scipy.optimize}~\citep{2020SciPy-NMeth}
-	\item \sherpa~\citep{sherpa-2011}
+	\item \sherpa~\citep{sherpa-2011, sherpa-2001}
 \end{itemize}

### 2023-03-03 src/ms-review.tex
Fix #99

@@
 \usepackage{hyperref}
+\usepackage[autostyle]{csquotes}
 
@@
 mostly attributed to the simple and easy to learn syntax, the ability to act as
-a "glue" language between different programming languages and last but not least
+a \enquote{glue} language between different programming languages and last but not least
 the rich ecosystem of packages and its open and supportive community \citep{Momcheva2015}.
@@
 of the data is often excluded from subsequent analysis by defining regions of
- "safe" data in the spatial as well as energy dimension.
+ \enquote{safe} data in the spatial as well as energy dimension.
 All of these data reduction steps are performed by classes and functions
@@
 %% adopted in high-energy astrophysics.
-The counts data and the reduced IRFs in the form of maps are bundled into "datasets"
+The counts data and the reduced IRFs in the form of maps are bundled into datasets
 that represent the fourth data level (DL4). These reduced datasets can be written to disk,
@@
 spherical geometry for regions, the regions are projected onto the local
-tangential plane using a WCS transform. This approach follows Astropy's "regions"
+tangential plane using a WCS transform. This approach follows Astropy's \textit{Regions}
 package \citep{AstropyRegions2022}, which is both used as an API to define regions
@@
 statistic, there are other classes which support
-analyses where the background is measured from control regions, so called "off" obervations.
+analyses where the background is measured from control regions, so called \enquote{off} obervations.
 Those require the use of a different fit statistics, which takes into account the
@@
 larger bins. A multiplicative correction factor (the \textit{norm})
-is applied to the best fit "reference" spectral
+is applied to the best fit reference spectral
 model and is fitted in the restricted data range, defined by the 
@@
 been historically used by larger collaborations in the very high-energy
-domain (such as \milagro or \hess) as "trademark" colormaps.
+domain (such as \milagro or \hess) as \enquote{trademark} colormaps.
 While we explicitly discourage the use of those colormaps for publication
@@
 measured in a circular aperture centered on the Galactic Center, in
-\gammaray~astronomy often called "ON region". For such analysis the users first
+\gammaray~astronomy often called \enquote{on region}. For such analysis the users first
 chooses a region of interest and energy binning, both defined by a
@@
 reduced IRFs are bundled into a \code{SpectrumDataset}. To estimate
-the expected background in the ON region a "reflected regions" background
+the expected background in the \enquote{on region} a \enquote{reflected regions} background
 method was used~\cite{Berge07}, represented in \gammapy by the
@@
 July 29 - 30, 2006~\cite{2009A&A...502..749A}. The data are publicly available 
-as a part of the HESS-DL3-DR1~\cite{HESS_DR1}, and shipped with
-\verb"GAMMAPY_DATA". Each observation is first split into 10 min smaller
+as a part of the HESS-DL3-DR1~\cite{HESS_DR1}. Each observation is first split into 10 min smaller
 observations, and spectra extracted for each of these within a 0.11\textdegree~radius
@@
 include for example filtering and detection on these maps with techniques from
-the "scikit-image" package~\citep{scikit-image}, and outlier detection from
-the "scikit-learn" package~\citep{scikit-learn}. This allows e.g., to 
+the \textit{Scikit-image} package~\citep{scikit-image}, and outlier detection from
+the \textit{Scikit-learn} package~\citep{scikit-learn}. This allows e.g., to 
 reduce the number of spurious detections at this stage using standard
@@
 The resulting web published tutorials also provide links to playground spaces in
-"myBinder"~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
+\textit{myBinder}~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
 on-line in versioned virtual environments hosted in the myBinder
@@
 An important part of \gammapy's development organisation is the support
-for "Proposals for improving \gammapy" (PIG). This system is very much
+for \textit{Proposals for improving \gammapy}(PIG). This system is very much
 inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}
@@
 
-A special category of PIGs are long-term "roadmaps". To develop a common
+A special category of PIGs are long-term \textit{roadmaps}. To develop a common
 vision for all \gammapy project members on the future of the
@@
 	J.E.~Ruiz acknowledges financial support from the State Agency for Research of
-	the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the
+	the Spanish MCIU through the \textit{Center of Excellence Severo Ochoa} award to the
 	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709). L.~Giunti acknowledges

### 2023-03-03 src/ms-review.tex
Fix #91

@@
 \newcommand{\numpy}{Numpy\xspace}
-\newcommand{\iminuit}{IMinuit\xspace}
+\newcommand{\iminuit}{iminuit\xspace}
 \newcommand{\sherpa}{Sherpa\xspace}
@@
 	{
-		Traditionally, \gammaray astronomy has been conducted
+		Traditionally, TeV-\gammaray astronomy has been conducted
 		by experiments employing proprietary data and analysis software.
@@
 
-For the association and classification step, that is tightly connected to the
+For the association and classification step, which is tightly connected to the
 population studies, we can easily compare the fitted models to the set of
@@
 multi-wavelength cross-matches are usually required to characterize the
-sources. This an e.g. easily be achieved by relying on coordinate
-handling from Astropy or affiliated packages such as \textit{AstroML}~\citep{astroML}
-or \textit{Astroquery}~\citep{astroquery}.
+sources. This can e.g. easily be achieved by relying on coordinate
+handling from Astropy in combination with affiliated packages
+\textit{Astroquery}~\citep{astroquery}.
 
@@
 has the potential to further unify the community
-of \gammaray astronomers, by sharing common tools and
+of \gammaray astronomers, by sharing common tools, data formats and
 a common vision of open and reproducible science for the future.

### 2023-03-03 src/ms-review.tex
Fix #95

@@
 black holes, and remnants of supernova explosions. As in other
-branches of astronomy, \gammarays can be observed by both
+branches of astronomy, \gammarays can be observed by
 satellite as well as ground based instruments.
@@
 primary \gammaray photons and infer their incident direction and energy.
-VHE \gammaray astronomy covers the energy range from fews tens of ${\rm GeV}$ up to the ${\rm PeV}$.
+VHE \gammaray astronomy covers the energy range from few tens of ${\rm GeV}$ up to the ${\rm PeV}$.
 There are two main categories of ground-based instruments:
@@
 shower when it reaches the ground. These instruments have a very
-large FoV, large duty-cycle but higher energy threshold and
-usually have lower signal to noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
+large FoV and large duty-cycle, but a higher energy threshold and
+usually lower signal to noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
 
@@
 Ground-based \gammaray astronomy has been historically conducted
-by experiments operated by independent collaborations, each relying
+through experiments operated by independent collaborations, each relying
 on their own proprietary data and analysis software developed as part of the
@@
 complementary sky coverages, and the various detection
-techniques have complementary properties in terms of the energy range covered,
+techniques have complementary properties in terms of energy range covered,
 duty cycle and spatial resolution.
@@
 The core of the idea is illustrated in Figure~\ref{fig:big_picture}. Various \gammaray instruments
-export their data to a standardised common data format -- the \gadf. This data can then be combined and
+export their data to the standardised common \gadf data format. This data can then be combined and
 analysed using a single common software library.
@@
 but an independent community developed software project.
-The \gammapy package is is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
+The \gammapy package is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
 structures, \scipy~\citep{2020SciPy-NMeth} for numerical algorithms, \astropy~\citep{astropy} for
-astronomy-specific functionality, and \matplotlib~\citep{matplotlib} for visualization.
+astronomy-specific functionality, \iminuit~\citep{iminuit} for numerical minimisation
+and \matplotlib~\citep{matplotlib} for visualization.
 
@@
 point spread function and energy dispersion ($E_{\rm disp}$).
-In general, they depend on event's detector
-geometrical parameters, e.g. the field-of-view location or the event elevation angle. So they might be parametrised as
-function of such parameters specific to the instrumental technical.
+In general, IRFs depend on the geometrical parameters of the detector, e.g. location 
+of an event in the FoV or the elevation angle of the event. So IRFs might be parametrised
+as a function of such detector specific coordinates too.
 
@@
 %% 2) the Bkg is not provided and, thus, has to be estimated from the obs.
-After all data has been projected into the same geometry, it is typically
+After all data have been projected into the same geometry, it is typically
 required to improve the residual hadronic background estimate. As residual hadronic
@@
 First a \code{DataStore} object is created from the path of the data
-directory. The directory contains an observation as well as FITS HDU 
+directory. The directory contains an observation as well as a FITS HDU 
 index file which assigns the correct data and IRF FITS files and HDUs
@@
 PSF to represent non-parametric shapes, again depending on true energy
-of offset form the pointing position.
+and offset from the pointing position.
 
@@
 \subsubsection{Instrumental Background}
-The instrumental background rate can be represented in \gammapy as either a 2-dimensional
-data structure (\code{Background2D}) of count rate normalised per steradians and energy at different
-reconstructed energies and offset angles or as rate per steradians and energy, as a
-function of reconstructed energy and detector coordinates (\code{Background3D}).
-In the former, the background is expected to follow a radially symmetric shape,
-while in the latter, it can be more complex.
-
-Some example IRFs read from public data files and plotted with \gammapy are shown in Figure~\ref{fig:irfs}.
+The instrumental background rate can be represented as either a 2-dimensional
+data structure named \code{Background2D} or a 3-dimensional one named \code{Background3D}.
+The background rate is stored as a differential count rate, normalised per solid angle
+and energy at different reconstructed energies. In the first case the background is
+expected to follow a radially symmetric shape and changes only with the offset angle from
+FoV center. In the other case the background is allowed to vary with 
+longitude and latitude of a tangential FoV coordinates system.
+
+Some example IRFs read from public data files and plotted with \gammapy are shown 
+in Figure~\ref{fig:irfs}.
 
@@
 First, events are binned and IRFs are interpolated and projected onto the chosen analysis
-geometry. The end product of the data reduction process are a set of binned counts,
+geometry. The end product of the data reduction process is a set of binned counts,
 background exposure, psf and energy dispersion maps at the DL4 level. 
@@
 likelihood profiles to measure errors and upper limits. The code example
-\ref{codeexample:stats} shows how to compute the Li \& Ma
+\ref{fig*:minted:gp_stats} shows how to compute the Li \& Ma
 significance~\citep{LiMa} of a set of measurements.
@@
 analytical models which support two spatial dimensions defined by the sky coordinates
-$\ell, b$, an energy dimension $E$, and a time dimension $t$. To simplify the the definition of the
+$\ell, b$, an energy dimension $E$, and a time dimension $t$. To simplify the definition of the
 models, \gammapy uses a factorised representation of the total source
@@
 
-The analytical spatial models are all normalized such as they integrate to
+The analytical spatial models are all normalized such that they integrate to
 unity over the entire sky. The template spatial models may not, so in that special
@@
 null hypothesis; and the difference between both,
-the so-called TS value.
-From the TS value the significance of the measured signal and associated flux
+the so-called \textit{TS value}.
+From this \textit{TS value}, a significance of the measured signal and associated flux
 can be derived.
@@
 The sub-package also provides \texttt{matplotlib} implementations of specific
-colormaps for false color image representation. Those colormaps have
-been historically used by larger collaborations in the very high-energy
-domain (such as \milagro or \hess) as \enquote{trademark} colormaps.
-While we explicitly discourage the use of those colormaps for publication
+colormaps. Those colormaps have been historically used by larger collaborations
+in the very high-energy domain (such as \milagro or \hess) as \enquote{trademark}
+colormaps. While we explicitly discourage the use of those colormaps for publication
 of new results, because they do not follow modern visualization
@@
 While the present list of use cases is rather preliminary, this can be enriched
-with time with by users and/or developers according to future needs.
+with time by users and/or developers according to future needs.
 
@@
 source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
-range spans $80\,{\rm GeV} - 20\,{\rm TeV}$. They data reduction for the 1D analysis
+range spans $80\,{\rm GeV} - 20\,{\rm TeV}$. The data reduction for the 1D analysis
 is applied, and the data are reduced to a \code{SpectrumDataset} before being fitted.
@@
 multi-wavelength cross-matches are usually required to characterize the
-sources. This can e.g. easily be achieved by relying on coordinate
+sources. This can easily be achieved by relying on coordinate
 handling from Astropy in combination with affiliated packages
@@
 	\textit{ctools} and \textit{gammapy} packages in order to cross-validate
-	them.}. So we can  improve performances, optimize our analyses strategies, and
-identify the needs in term of parallelisation to process the large datasets
-provided by the surveys.
+	them.}. So we can improve performance, optimize our analyse strategies, and
+identify the needs in terms of parallelisation to process the large datasets
+provided by surveys.
 

### 2023-03-03 src/ms-review.tex
Fix #116

@@
 general, \gammaray observations count Poisson-distributed events at various sky
-positions, and contain both signal and background events. Estimation of the
-number of signal events is done through likelihood maximization. In \gammapy,
-the fit statistics are Poisson log-likelihood functions normalized like
-chi-squares, i.e., they follow the expression $2 \time\cdot \log{\mathcal{L}}$,
-where $\mathcal{L}$ is
-the likelihood function used. When the expected number of background events is known, the used statistic function 
- is the \emph{Cash} statistic
-~\citep{Cash}. It is used by datasets using background templates such as the
-\code{MapDataset}. When the number of background events is unknown and an OFF
+positions and contain both signal and background events.
+To estimate the number of signal events in the observation one typically uses
+Poisson maximum likelihood estimation (MLE). In practice this is done
+by minimizing a fit statistic defined by $-2 \time\cdot \log{\mathcal{L}}$,
+where $\mathcal{L}$ is the likelihood function used. \gammapy uses the convention
+of a factor of 2 in front, such that a difference in log-likelihood will
+approach a $\Chi^2$ distribution in the statistial limit.
+
+When the expected number of background events is known, the statistic function 
+is the so called \emph{Cash} statistic ~\citep{Cash}. It is used by datasets using background
+templates such as the
+\code{MapDataset}. When the number of background events is unknown and an \enquote{off}
 measurement where only background events are expected is used, the statistic
 function is \emph{WStat}. It is a profile log-likelihood statistic where the background
-counts are marginalized parameters. It is used by datasets containing off
+counts are marginalized parameters. It is used by datasets containing \enquote{off}
 counts measurements such as the \code{SpectrumDatasetOnOff}, used for classical

### 2023-03-03 src/ms-review.tex
Fix #96

@@
 
-\textit{Water Cherenkov Detectors (WCD)} detect particles directly from the tail of the
+\textit{Water Cherenkov Detectors (WCDs)} detect particles directly from the tail of the
 shower when it reaches the ground. These instruments have a very
 large FoV and large duty-cycle, but a higher energy threshold and
-usually lower signal to noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
+usually lower signal-to-noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
 
@@
 The lists of \gammaray events are then used to derive scientific results, such as spectra, sky maps
-or light curves, taking into account the observation specific instrument response functions (IRF).
+or light curves, taking into account the observation specific instrument response functions (IRFs).
 Once the data is reduced to a list of events with reconstructed physical properties of the primary particle,
@@
 an analytical model is commonly adopted to describe the intensity of gamma-ray sources as a function of the energy,
-$E_{\rm true}$, and of the position in the field of view, $p_{\rm true}$:
+$E_{\rm true}$, and of the position in the FoV, $p_{\rm true}$:
 \begin{equation}
@@
 corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),
-point spread function and energy dispersion ($E_{\rm disp}$).
+PSF and energy dispersion ($E_{\rm disp}$).
 In general, IRFs depend on the geometrical parameters of the detector, e.g. location 
@@
 It represents the intensity of charged particles misidentified as \gammarays that are expected
-during an observation. It is defined as a function of the measured position in the field-of-view
+during an observation. It is defined as a function of the measured position in the FoV
 and measured energy.
@@
 from regions without known \gammaray sources. This includes methods 
-such as the ring or the field-of-view background techniques or
+such as the ring or the FoV background techniques or
 background measurements performed within, e.g. reflected regions~\citep{Berge07}.
-Data measured at the field-of-view or energy boundaries of the instrument are typically
+Data measured at the FoV or energy boundaries of the instrument are typically
 associated with a systematic uncertainty in the IRF. For this reason this part 
@@
 the common \gammaray \irfs are the effective area, energy dispersion,
-point spread function and background rate. The \code{gammapy.irf}
+PSF and background rate. The \code{gammapy.irf}
 sub-package can open and access specific \irf extensions,
@@
 close to unity for a small energy bias and its distribution can 
-be typically described by a Gaussian. However, more complex
+be typically described by a Gaussian profile. However, more complex
 shapes are also common. The migration parameter is given at each offset angle and
@@
 to correct them from the data themselves. Several techniques are commonly used
-in TeV \gammaray astronomy such as field-of-view background normalization or
+in TeV \gammaray astronomy such as FoV background normalization or
 background measurement in reflected regions, see~\cite{Berge07}.
@@
 domain is determined by the \code{SafeMaskMaker}. It can be used to limit the
-extent of the field of view used, or to limit the energy range to, e.g., a domain
+extent of the FoV used, or to limit the energy range to, e.g., a domain
 where the energy reconstruction bias is below a given value.
@@
 isolated source. However, more complicated situations require a more careful
-treatment. In a field of view containing several overlapping sources, the 1D
+treatment. In a FoV containing several overlapping sources, the 1D
 approach cannot disentangle the contribution of each source to the total flux in
@@
 The \fermi data is introduced at the data level DL4, and directly bundled in a
-\code{MapDataset}. They ahve been prepared using the standard \textit{fermitools} \citep{Fermitools2019} and
+\code{MapDataset}. They have been prepared using the standard \textit{fermitools} \citep{Fermitools2019} and
 selecting a region of $5^{\circ} \mathrm{x} 4^{\circ}$ around the

### 2023-03-03 src/ms-review.tex
Fix #108

@@
 		such as the the Cherenkov Telescope Array, will be operated as open observatories.
-		Alongside the data, they will make software tools for their analysis available to the community.
+		Alongside the data, they will also make associated software tools available to a wider community.
     This necessity prompted the development of open, high-level astronomy software customised for high energy astrophysics.
@@
 
-\textit{Imaging Atmospheric Cherenkov Telescopes (IACT)} obtain images of the atmospheric showers
+\textit{Imaging Atmospheric Cherenkov Telescopes (IACTs)} obtain images of the atmospheric showers
 by detecting the Cherenkov radiation emitted by the cascading charged particles and

### 2023-03-03 src/ms-review.tex
Fix chi command

@@
 of a factor of 2 in front, such that a difference in log-likelihood will
-approach a $\Chi^2$ distribution in the statistial limit.
+approach a $\chi^2$ distribution in the statistial limit.
 

### 2023-03-03 src/ms-review.tex

@@
 	{\it Paper Authors} \and
-    Axel \and
-	Régis \and
-	Quentin \and
-	Atreyee \and
-	Cosimo \and
-	Fabio \and
-	Bruno \and
-	Laura \and
-	Jose Enrique \and
+    Axel Donath \inst{\ref{inst:28}} \and
+	Régis Terrier \inst{\ref{inst:20}} \and
+	Quentin Rémy \inst{\ref{inst:17}} \and
+	Atreyee Sinha \inst{\ref{inst:15}} \and
+	Cosimo Nigro \inst{\ref{inst:24}} \and
+	Fabio Pintore \inst{\ref{inst:26}} \and
+	Bruno Khélifi \inst{\ref{inst:20}} \and
+	Laura Olivera-Nieto \inst{\ref{inst:17}}\and
+	Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
 	\\
@@
 \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \and
-	Fabio Acéro \and
-	David Berge \and
-	Catherine Boisson \and
-	Jose Louis Contreras \and
-	Axel Donath \and
-	Stefan Funk \and
-	Christopher van Eldik \and
-	Matthias Fue{\ss}ling \and
-	Jim Hinton \and
-	Bruno Khélifi \and
-	Rub{\'e}n L{\'o}pez-Coto \and
-	Fabio Pintore \and
-	Régis Terrier \and
-	Roberta Zanin \and
+	Fabio Acero \inst{\ref{inst:1}} \and
+	David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
+	Catherine Boisson \inst{\ref{inst:9}} \and
+	Jose Louis {Contreras} \inst{\ref{inst:15}} \and
+	Axel Donath \inst{\ref{inst:28}} \and
+	Stefan Funk \inst{\ref{inst:19}} \and
+	Christopher {van Eldik} \inst{\ref{inst:19}} \and
+	Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
+	Jim Hinton \inst{\ref{inst:17}} \and
+	Bruno Khélifi \inst{\ref{inst:20}} \and
+	Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
+	Fabio Pintore \inst{\ref{inst:26}} \and
+	Régis Terrier \inst{\ref{inst:20}} \and
+	Roberta Zanin \inst{\ref{inst:18}} \and
     \\
 	{\it Gammapy Project Contributors} \and
-	Dark Vador \inst{\ref{inst:0}} \and
-	Unknown Contributor \inst{\ref{inst:unknown}}
+	Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
+	Pooja Bhattacharjee \inst{\ref{inst:8}} \and
+	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
+	Johannes Buchner \inst{\ref{inst:12}} \and
+	David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
+	Andrew Chen \inst{\ref{inst:14}} \and
+	Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
+	José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
+	Christoph Deil \inst{\ref{inst:17}} \and
+	Luca Giunti \inst{\ref{inst:20}} \and
+	Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
+	Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
+	Marianne Lemoine-Goumard \inst{\ref{inst:31}} \and
+	Jean-Philippe Lenain \inst{\ref{inst:22}} \and
+	Maximilian Linhoff \inst{\ref{inst:11}} \and
+	Lars Mohrmann \inst{\ref{inst:17}} \and
+	Daniel Morcuende \inst{\ref{inst:15}} \and
+	Sebastian Panny \inst{\ref{inst:25}} \and
+	Maxime Regeard \inst{\ref{inst:20}} \and
+	Lab Saha \inst{\ref{inst:15}} \and
+	Hubert Siejkowski \inst{\ref{inst:27}} \and
+	Aneta Siemiginowska \inst{\ref{inst:28}} \and
+	Brigitta M {Sipőcz} \inst{\ref{inst:29}} \and
+	Tim Unbehaun \inst{\ref{inst:19}} \and
+	Thomas Vuillaume \inst{\ref{inst:8}}
 }
@@
 \institute{
-	Fake institute, Vador city, Moon \label{inst:0} \and
-	unknown \label{inst:unknown}
+	Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, F-91191 Gif-sur-Yvette, France \label{inst:1} \and
+	Departament de Física Quàntica i Astrofísica (FQA), Universitat de Barcelona (UB),  c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:2} \and
+	Institut de Ciències del Cosmos (ICCUB), Universitat de Barcelona (UB), c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:3} \and
+	Institut d'Estudis Espacials de Catalunya (IEEC), c. Gran Capità, 2-4, 08034 Barcelona, Spain \label{inst:4} \and
+	Departament de Física Quàntica i Astrofísica, Institut de Ciències del Cosmos, Universitat de Barcelona, IEEC-UB, Martí i Franquès, 1, 08028, Barcelona, Spain \label{inst:5} \and
+	Deutsches Elektronen-Synchrotron (DESY), D-15738 Zeuthen, Germany \label{inst:6} \and
+	Institute of physics, Humboldt-University of Berlin, D-12489 Berlin, Germany \label{inst:7} \and
+	Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecy de Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:8} \and
+	Laboratoire Univers et Théories, Observatoire de Paris, Université PSL, Université Paris Cité, CNRS, F-92190 Meudon, France \label{inst:9} \and
+	Point8 GmbH \label{inst:10} \and
+	Astroparticle Physics, Department of Physics, TU Dortmund University, Otto-Hahn-Str. 4a, D-44227 Dortmund \label{inst:11} \and
+	Max Planck Institute for extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany \label{inst:12} \and
+	Max Planck Computing and Data Facility, Gießenbachstraße 2, 85748 Garching \label{inst:13} \and
+	School of Physics, University of the Witwatersrand, 1 Jan Smuts Avenue, Braamfontein, Johannesburg, 2050 South Africa \label{inst:14} \and
+	IPARCOS Institute and EMFTEL Department, Universidad Complutense de Madrid, E-28040 Madrid, Spain \label{inst:15} \and
+	The Hong Kong University of Science and Technology, Department of Electronic and Computer Engineering \label{inst:16} \and
+	Max-Planck-Institut für Kernphysik, P.O. Box 103980, D 69029 Heidelberg, Germany \label{inst:17} \and
+	Cherenkov Telescope Array Observatory gGmbH (CTAO gGmbH) Saupfercheckweg 1 69117 Heidelberg \label{inst:18} \and
+	Erlangen Centre for Astroparticle Physics (ECAP), Friedrich-Alexander-Universität Erlangen-Nürnberg, Nikolaus-Fiebiger Strasse 2, 91058 Erlangen, Germany \label{inst:19} \and
+	Université de Paris Cité, CNRS, Astroparticule et Cosmologie, F-75013 Paris, France  \label{inst:20} \and
+	Meteo France International \label{inst:21} \and
+	Sorbonne Université, Université Paris Diderot, Sorbonne Paris Cité, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252 Paris, France \label{inst:22} \and
+	Instituto de Astrofísica de Andalucía-CSIC, Glorieta de la Astronomía s/n, 18008, Granada, Spain \label{inst:23} \and
+	Institut de Física d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, Bellaterra, 08193 Barcelona, Spain \label{inst:24} \and
+	Institut für Astro- und Teilchenphysik, Leopold-Franzens-Universität Innsbruck, A-6020 Innsbruck, Austria \label{inst:25} \and
+	INAF/IASF Palermo, Via U. La Malfa, 153, 90146 Palermo PA \label{inst:26} \and
+	Academic Computer Centre Cyfronet, AGH University of Science and Technology, Krakow, Poland \label{inst:27} \and
+	Center for Astrophysics | Harvard and Smithsonian \label{inst:28} \and
+	Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:29} \and
+	Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:30} \and
+	Université Bordeaux, CNRS, LP2I Bordeaux, UMR 5797 \label{inst:31}
 }
-
-% \abstract{}{}{}{}{}
-% 5 {} token are mandatory
 
@@
 	all the \gammapy users that have provided feedback and submitted bug reports.
-	J.E.~Ruiz acknowledges financial support from the State Agency for Research of
-	the Spanish MCIU through the \textit{Center of Excellence Severo Ochoa} award to the
-	Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709). L.~Giunti acknowledges
-	financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014).
+
+	A.~Aguasca-Cabot acknowledges the financial support from the Spanish Ministry of Science and Innovation
+	and the Spanish Research State Agency (AEI) under grant PID2019-104114RB-C33/AEI/10.13039/501100011034
+	and the Institute of Cosmos Sciences University of Barcelona (ICCUB, Unidad de Excelencia “María de Maeztu”)
+	through grant CEX2019-000918-M. J.L.~Contreras acknowledges the funding from the ESCAPE H2020 project, GA No 824064.
+	L.~Giunti acknowledges financial support from the Agence Nationale de la Recherche (ANR-17-CE31-0014). M. Linhoff
+	acknowledges support by the German BMBF (ErUM) and DFG (SFBs 876 and 1491).
+	R.~López-Coto acknowledges the Ramon y Cajal program through grant RYC-2020-028639-I and the financial support
+	from the grant CEX2021-001131-S funded by MCIN/AEI/ 10.13039/501100011033. C.~Nigro C.N. acknowledges support by
+	the Spanish Ministerio de Ciencia e Innovación (MICINN), the European Union – NextGenerationEU and PRTR  through
+	the programme Juan de la Cierva (grant FJC2020-046063-I), by the the MICINN (grant PID2019-107847RB-C41), and from
+	the CERCA program of the Generalitat de Catalunya. Q.~Remy acknowledges support from the project "European Science
+	Cluster of Astronomy \& Particle Physics ESFRI Research Infrastructures" (ESCAPE), that has received funding from
+	the European Union’s Horizon 2020 research and innovation programme under Grant Agreement no. 824064. J.E.~Ruiz
+	acknowledges financial support from the grant
+	CEX2021-001131-S funded by MCIN/AEI/ 10.13039/501100011033. A.~Siemiginowska was supported by NASA contract
+	NAS8-03060 (Chandra X-ray Center). A.~Sinha acknowledges support from The European Science Cluster of Astronomy \&
+	Particle Physics ESFRI Research Infrastructures  funded by the European Union’s Horizon 2020 research and
+	innovation program under Grant Agreement no. 824064 and from the Spanish Ministry of Universities through the
+	Maria Zambrano Talent Attraction Programme, 2021-2023.
 

### 2023-03-06 src/ms-review.tex

@@
 		Alongside the data, they will also make associated software tools available to a wider community.
-    This necessity prompted the development of open, high-level astronomy software customised for high energy astrophysics.
+    This necessity prompted the development of open, high-level astronomy software customised for high-energy astrophysics.
 	}
@@
 	{
-		Starting from event list and instrument response functions,
+		Starting from event lists and instrument response functions,
 		\gammapy provides the functionalities for reducing data binned in energy and sky coordinates.
-		To handle the residual hadronic background, several techniques for background estimation
-		are implemented in the package.
+		Several techniques for background estimation are implemented in the package to handle the residual hadronic background.
 		After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
 		using Poisson maximum likelihood fitting
-		and assuming a variety of spectral, temporal and spatial models.
+		and assuming a variety of spectral, temporal, and spatial models.
 		Estimation of flux points, likelihood profiles and light curves is also supported.
@@
 Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and
-create a large shower of secondary particles that can be observed from the ground.
+create large showers of secondary particles that can be observed from the ground.
 Ground-based \gammaray astronomy relies on these extensive air showers to detect the
@@
 \textit{Imaging Atmospheric Cherenkov Telescopes (IACTs)} obtain images of the atmospheric showers
-by detecting the Cherenkov radiation emitted by the cascading charged particles and
+by detecting the Cherenkov radiation emitted by charged particles in the cascade and
 use these images to reconstruct the properties of the incident particle.
@@
 large FoV and large duty-cycle, but a higher energy threshold and
-usually lower signal-to-noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
+lower signal-to-noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
 
@@
 some proprietary period, and the software required to analyze it will be distributed
-as well. To allow the re-usability of existing instruments and their interoperability,
+as well. To allow the re-usability of data from existing instruments and their interoperability,
 it is required to use open data formats and open tools that can support the various analysis methods
@@
 
-In the sub-field of astronomy, it was the \astropy project \citep{astropy} that 
-was created in 2012 to build a community-developed core Python package for astronomy.
+In the sub-field of astronomy, the \astropy project \citep{astropy} was created in 2012
+to build a community-developed core Python package for astronomy.
 It offers basic functionalities that astronomers of many fields need, such as representing
@@
 %%% Question: starting date? Is is relevant, what is the real start?
-The \gammapy project was started following the idea of \astropy with the objective of building a common
+The \gammapy project was started following the model of \astropy, with the objective of building a common
 software library for very high-energy \gammaray data analysis \citep{gammapy_2015}. 
@@
 export their data to the standardised common \gadf data format. This data can then be combined and
-analysed using a single common software library.
+analysed using a common software library.
 This means that the \gammapy package is not specific to any instrument,
-but an independent community developed software project.
+but an independent community-developed software project.
 The \gammapy package is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
@@
 To extract physically relevant information, such as the flux, spatial or spectral shape of one or more sources,
-an analytical model is commonly adopted to describe the intensity of gamma-ray sources as a function of the energy,
-$E_{\rm true}$, and of the position in the FoV, $p_{\rm true}$:
+an analytical model is commonly adopted to describe the intensity of the radiation from gamma-ray sources
+as a function of the energy, $E_{\rm true}$, and of the position in the FoV, $p_{\rm true}$:
 \begin{equation}
-    \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]}
+    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]}
     \label{eq:general_source_model}
@@
 where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. To convert this analytical flux model
-into a prediction on the number of gamma-ray events, $N_{\rm pred}$, with their estimated energy $E$ and position $p$, the model
-is convolved through the response function of the instrument.
+into a prediction on the number of gamma-ray events detected by an instrument, $N_{\rm pred}$,
+with their estimated energy $E$ and position $p$, the model is convolved with the response function of the instrument.
 
@@
 	\begin{split}
-  N(p, E, \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \circledast \left[ PSF \circledast \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
+  N(p, E; \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \circledast \left[ PSF \circledast \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
                        & + Bkg(p, E) \cdot t_{\rm obs}
@@
 
-Finally, predicted and observed events, $N_{obs}$, can be then combined in a likelihood function,
+Finally, predicted and observed events, $N_{obs}$, can be combined in a likelihood function,
 $\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\hat{\theta}$.
 
-\subsection{Data analysis workflow}
+\subsection{\gammapy data analysis workflow}
 The first step in \gammaray data analysis is the selection and extraction of observations
@@
 Spectral models can be simple analytical models or more complex ones from radiation
-mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{o}$ decay).
+mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{0}$ decay).
 Independently or subsequently to the global modelling, the data can be
@@
 \code{gammapy.modeling}, are used to jointly model a combination
-of datasets, for example, to make spectum using data from several facilities. Estimator classes,
+of datasets, for example, to compute a spectrum using data from several facilities. Estimator classes,
 which are contained in \code{gammapy.estimators}, are used to
@@
 		to the latest performance of the instruments, but still are representative of the 
-		detector type and energy range. We also exclusively relied on publicly available
+		detector type and energy range. We exclusively relied on publicly available
 		data provided by the collaborations. The data is also availabe in the
@@
 
-The \code{gammapy.irf} sub-package contains all classes and functionality
+The \code{gammapy.irf} sub-package contains all classes and functionalities
 to handle IRFs in a variety of formats.
@@
 tables, with quantities expressed in terms of energy (true or reconstructed),
-off-axis angles or cartesian detector coordinates. The main information stored in
+off-axis angles or cartesian detector coordinates. The main quantities stored in
 the common \gammaray \irfs are the effective area, energy dispersion,
@@
 \subsubsection{Point Spread Function}
-\gammapy allows user to treat different kinds of PSFs,
-in particular, parametric multi-dimensional Gaussians (\code{EnergyDependentMultiGaussPSF})
+\gammapy allows users to treat different kinds of PSFs,
+in particular, parametric multi-dimensional Gaussian distributions (\code{EnergyDependentMultiGaussPSF})
 or King profile functions (\code{PSFKing}). The \code{EnergyDependentMultiGaussPSF}
@@
 \subsubsection{Energy Dispersion}
-For \iacts, the energy resolution and bias, or sometimes called energy dispersion,
+For \iacts, the energy resolution and bias, sometimes called energy dispersion,
 is typically parametrised in terms of the so-called
@@
 The background rate is stored as a differential count rate, normalised per solid angle
-and energy at different reconstructed energies. In the first case the background is
-expected to follow a radially symmetric shape and changes only with the offset angle from
-FoV center. In the other case the background is allowed to vary with 
+and energy interval at different reconstructed energies and offset angles.
+In the \code{Background2D} case, the background is expected to follow a radially symmetric shape
+and changes only with the offset angle from FoV center.
+In the \code{Background3D} case, the background is allowed to vary with 
 longitude and latitude of a tangential FoV coordinates system.
@@
 of a geometry instance defining the coordinate system together with a
-Numpy array containing the associated data. All map classes support a basic
-set of arithmetic and boolean operations with  unit support, up- and downsampling
+\numpy array containing the associated data. All map classes support a basic
+set of arithmetic and boolean operations with  unit support, up and downsampling
 along extra axes, interpolation, resampling of extra axes, interactive visualisation
@@
 \subsubsection{WCS Maps}
-The FITS WCS pixelization supports a different number of projections to
+The FITS WCS pixelization supports a number of different projections to
 represent celestial spherical coordinates in a regular rectangular grid.
@@
 bin with an arbitrary shape, describing a region in the sky with that same
-shape. Typically, they are used together with a non-spatial dimension, for
+shape. Region maps are typically used together with a non-spatial dimension, for
 example an energy axis, to represent how a quantity varies in that dimension
@@
         common \code{Datasets} container. All dataset types have an associated
-        name attribute to allow access by name later in the code. The
+        name attribute to allow a later access by name in the code. The
         environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
@@
 
-Because the background models suffer from strong uncertainties it is required
+Because background models usually suffer from strong uncertainties, it is required
 to correct them from the data themselves. Several techniques are commonly used
@@
 templates such as the
-\code{MapDataset}. When the number of background events is unknown and an \enquote{off}
+\code{MapDataset}. When the number of background events is unknown, and an \enquote{off}
 measurement where only background events are expected is used, the statistic
@@
 either, for example, from multiple sources and from a diffuse emission, or from several spectral
-components within the same source. To handle list of multiple \code{SkyModel} objects, \gammapy
+components within the same source. To handle lists of multiple \code{SkyModel} objects, \gammapy
 implements a \code{Models} class.
@@
 package~\citep{naima}. The modeling framework can be easily extended with
-user-defined models. For example, the radiaitve models of jetted Active Galactic Nuclei (AGN)
+user-defined models. For example, the radiative models of jetted Active Galactic Nuclei (AGN)
 implemented in \agnpy, can be wrapped into \gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}.
@@
 Note that, for now, covariance matrix and errors are computed only for the fitting with 
-\iminuit. However depending on
-the problem other optimizers can better perform, so sometimes it can be useful
-to run a pre-fit with alternative optimization methods. In future we plan to
+\iminuit. However, depending on
+the problem other optimizers can perform better, so sometimes it can be useful
+to run a pre-fit with alternative optimization methods. In the future, we plan to
 extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo methods.
@@
 are based on an internal representation of the flux which is
-independent of the Spectral Energy Distribution (SED) type. The flux is represented by a
-the reference spectral model and an array of
+independent of the Spectral Energy Distribution (SED) type. The flux is represented
+by a reference spectral model and an array of
 normalisation values given in energy, time and spatial bins,
@@
 bin from the reference spectral model. This allows
-user to conveniently transform between different
+users to conveniently transform between different
 SED types. Table~\ref{tab:sed_types} shows an
@@
 blocks. So far, \gammapy does not support unfolding of \gammaray spectra.
-Methods for this will be implemented in a future version of \gammapy.
+Methods for this will be implemented in future versions of \gammapy.
 %% CN: reference for unfolding https://ui.adsabs.harvard.edu/abs/2007NIMPA.583..494A/abstract
@@
 workflows driven by parameters declared in a configuration file in YAML format.
-This way, a full analysis can be executed via a single command line taking the
+In this way, a full analysis can be executed via a single command line taking the
 configuration file as input.
@@
 for plotting and visualizing analysis results and \gammapy~data structures.
-This includes for example the visualization of reflected background regions across
-multiple observations or plotting large parameter correlation matrices of
+This includes, for example, the visualization of reflected background regions across
+multiple observations, or plotting large parameter correlation matrices of
 \gammapy models. It also includes a helper class to split
@@
 computes the so called J-factors and the associated \gammaray spectra expected
-from annihilation of dark matter in different channels according to the recipe
+from annihilation of dark matter in different channels, according to the recipe
 described in \cite{2011JCAP...03..051C}.
@@
 \gammapy is currently used for a variety of analyses by different IACT
-experiments and has already been employed in more than 60 scientific publications
+experiments and has already been employed in more than 60 scientific publications as of XX/03/2023
 \footnote{\href{https://ui.adsabs.harvard.edu/search/q=(\%20(citations(doi\%3A\%2210.1051\%2F0004-6361\%2F201834938\%22)\%20OR\%20citations(bibcode\%3A2017ICRC...35..766D))\%20AND\%20year\%3A2014-2023)&sort=date\%20desc\%2C\%20bibcode\%20desc&p_=0}{List on ADS}}.
@@
 result of such an analysis performed on three simulated CTA observations is
-shown in Fiure~\ref{fig:cta_galactic_center}. In this case the spectrum was
+shown in Figure~\ref{fig:cta_galactic_center}. In this case the spectrum was
 measured in a circular aperture centered on the Galactic Center, in
@@
 and fitted using the and \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
-log-likelihood profiles are computed using the \code{FluxPointsEstimator}.
+log-likelihood profiles were computed using the \code{FluxPointsEstimator}.
 
@@
 again via the \code{ExcessMapEstimator}. As can be seen in the middle panel of
-Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$,
+Figure~\ref{fig:cube_analysis}, there are no regions above or below $5\,\sigma$,
 meaning that the models describe the data sufficiently well.
@@
 \label{ssec:temporal-analysis}
-A common use case in most astrophysical scenarios is to study the temporal
+A common use case in many astrophysical scenarios is to study the temporal
 variability of a source. The most basic way to do this is to construct a
@@
 \code{MapDataset}. They have been prepared using the standard \textit{fermitools} \citep{Fermitools2019} and
-selecting a region of $5^{\circ} \mathrm{x} 4^{\circ}$ around the
-position of the Crab Nebula applying the same selection criteria of the 3FHL
+selecting a region of $5^{\circ}\,\times\,4^{\circ}$ around the
+position of the Crab Nebula, applying the same selection criteria of the 3FHL
 catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$,
@@
 and Gamera~\citep{gamera}.
-Tyically those emission models predict broadband emission from
+Typically those emission models predict broadband emission from
 radio, up to the very high-energy \gammaray range.
@@
 the very same electrons; near and far infrared photon fields and the cosmic
-microwave background (CMB). We adopted the prescription on the target
+microwave background (CMB). We adopt the prescription on the target
 photon fields provided in the documentation of the \textit{Naima}
@@
 
-The \iacts data reduction step is done in the same way than described in the 
+The \iacts data reduction step is done in the same way described in the 
 previous sections but scaled up to few thousands of observations. The object
@@
 reduce the number of spurious detections at this stage using standard
-classification algorithms and then speed up the next step
+classification algorithms and then speed up the next step,
 as less objects will have to be fitted simultaneously. During the modelling
@@
 	\textit{ctools} and \textit{gammapy} packages in order to cross-validate
-	them.}. So we can improve performance, optimize our analyse strategies, and
+	them.}. In this way we can improve performance, optimize our analyse strategies, and
 identify the needs in terms of parallelisation to process the large datasets
@@
 
-\section{\gammapy Project} \label{sec:gammapy-project}
+\section{The \gammapy Project} \label{sec:gammapy-project}
 
@@
 actions\footnote{\url{https://github.com/features/actions}}, blocking the
-processes and alerting developers when fails occur. This is the case of the
+processes and alerting developers when failures occur. This is the case of the
 continuous integration workflow, which monitors the execution of the test coverage
@@
 
-\gammapy is indexed in Astronomy Source Code
+\gammapy is indexed in the Astronomy Source Code
 Library\footnote{\url{https://ascl.net/1711.014}} and
@@
 
-We have also set up a solution for users to share recipes as Jupyter notebooks
-that do not fit in the \gammapy core documentation but which may be relevant as
-specific use cases. Contributions happen via pull requests to the
-\textit{gammapy-recipes} \github repository and merged after a short review. All
+We have also set up a solution for users to share recipes
+that do not fit in the \gammapy core documentation, but which may be relevant for
+specific use cases, in the form of Jupyter notebooks. Contributions happen via pull requests to the
+\textit{gammapy-recipes} \github repository and are merged after a short review. All
 notebooks in the repository are tested and published in the \gammapy recipes
@@
 and Astropy's APE \citep{greenfield_perry_2013} system.
-PIG are self-contained documents which outline a set of larger
-changes to the \gammapy code base. This includes larger feature additions,
-code and package restructuring and maintenance as well as changes related
+PIG are self-contained documents which outline a set of significant
+changes to the \gammapy code base. This includes large feature additions,
+code and package restructuring and maintenance, as well as changes related
 to the organisational structure of the \gammapy project. PIGs can be proposed
@@
 
-\section{Reproducibility}
+\section{Paper reproducibility}
 \label{sec:reproducibility}
@@
 data from intermediate level data formats, such as the FITS based
-\gadf. Starting from lists of \gammaray events and corresponding description
+\gadf. Starting from lists of \gammaray events and corresponding descriptions
 of the instrument response users can reduce and project the data
@@
 
-With the v1.0 milestone the \gammapy project enters a new development
+With the v1.0 release, the \gammapy project enters a new development
 phase. Future work will not only include maintenance of the v1.0 release,

### 2023-03-06 src/figures/cta_galactic_center.py
Adapt unit specification in figures

@@ -1,12 +1,14 @@
 import logging
 from pathlib import Path
+
+import config
 import matplotlib.pyplot as plt
 from astropy.visualization import simple_norm
+
 from gammapy.datasets import Datasets
-from gammapy.maps import Map
 from gammapy.estimators import FluxPoints
+from gammapy.maps import Map
 from gammapy.visualization import plot_spectrum_datasets_off_regions
-import config
 
 logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
@@ -24,17 +26,22 @@ def plot_spectrum_and_image():
     rect = (0.05, 0.2, 0.4, 0.75)
     ax = fig.add_axes(rect=rect, projection=wcs)
     counts = counts.smooth("0.03 deg")
-    norm = simple_norm(counts.data, stretch="asinh",  max_cut=15, min_cut=0)
+    norm = simple_norm(counts.data, stretch="asinh", max_cut=15, min_cut=0)
     counts.plot(ax=ax, norm=norm)
 
     datasets[0].counts.geom.region.to_pixel(ax.wcs).plot(ax=ax, edgecolor="white")
-    plot_spectrum_datasets_off_regions(datasets, ax=ax, legend_kwargs={"loc": "lower left", "fontsize": 6})
+    plot_spectrum_datasets_off_regions(
+        datasets, ax=ax, legend_kwargs={"loc": "lower left", "fontsize": 6}
+    )
 
     rect = (0.55, 0.2, 0.4, 0.75)
     ax = fig.add_axes(rect=rect)
-    fp = FluxPoints.read("../data/cta-galactic-center/flux-points.fits", sed_type="likelihood")
+    fp = FluxPoints.read(
+        "../data/cta-galactic-center/flux-points.fits", sed_type="likelihood"
+    )
     fp.plot(ax=ax, sed_type="e2dnde", color="tab:orange")
     fp.plot_ts_profiles(ax=ax, sed_type="e2dnde", rasterized=True)
+    ax.set_xlabel("Energy / TeV")
 
     filename = "cta_galactic_center.pdf"
     log.info(f"Writing {filename}")

### 2023-03-06 src/figures/cube_analysis.py

@@ -1,10 +1,12 @@
 import logging
 from pathlib import Path
+
+import config
 import matplotlib.pyplot as plt
+
 from gammapy.datasets import Datasets
 from gammapy.maps import Map
 from gammapy.modeling.models import Models
-import config
 
 logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
@@ -12,10 +14,10 @@ log = logging.getLogger(__name__)
 path = Path("../data/cube-analysis/")
 significance = Map.read(path / "significance_map.fits")
 residual = Map.read(path / "residual_map.fits")
-excess =Map.read(path / "excess_counts.fits", format="ogip")
-npred_1 =Map.read(path / "npred_1.fits", format="ogip")
-npred_2 =Map.read(path / "npred_2.fits", format="ogip")
-npred_3 =Map.read(path / "npred_3.fits", format="ogip")
+excess = Map.read(path / "excess_counts.fits", format="ogip")
+npred_1 = Map.read(path / "npred_1.fits", format="ogip")
+npred_2 = Map.read(path / "npred_2.fits", format="ogip")
+npred_3 = Map.read(path / "npred_3.fits", format="ogip")
 
 models = Models.read(path / "best-fit-model.yaml")
 
@@ -32,40 +34,47 @@ region = excess.geom.region
 
 rect = (0.06, 0.2, 0.27, 0.75)
 ax = fig.add_axes(rect=rect, projection=wcs)
-significance.plot(ax=ax, stretch='sqrt', add_cbar=True)
+significance.plot(ax=ax, stretch="sqrt", add_cbar=True)
 # ax.images[-1].colorbar.set_label('Significance ($\sigma$)', rotation=270, labelpad=25, fontsize=6)
-ax.set_xlabel('Galactic Longitude', fontsize=fontsize_labels)
-ax.set_ylabel('Galactic Latitude', fontsize=fontsize_labels)
+ax.set_xlabel("Galactic Longitude", fontsize=fontsize_labels)
+ax.set_ylabel("Galactic Latitude", fontsize=fontsize_labels)
 ax.tick_params(labelsize=fontsize_ticks, pad=1, length=2)
 ax.images[-1].colorbar.ax.tick_params(labelsize=6, pad=pad_ticks, length=length_ticks)
[…]

### 2023-03-06 src/figures/irfs.py

@@ -85,6 +85,7 @@ ax_aeff.plot(
 ax_aeff.set_xlim(*xlim)
 ax_aeff.set_yscale("log")
 ax_aeff.set_ylim(1e-1, 8e6)
+ax_aeff.set_xlabel("True Energy / TeV")
 ax_aeff.legend(fontsize=8, ncol=1)
 
 psf_hess = obs_hess.psf.slice_by_idx({"energy_true": slice(10, None)})
@@ -113,7 +114,7 @@ ax_psf.lines[-1].set_label("Fermi-LAT")
 ax_psf.set_yticks([0, 0.1, 0.2, 0.3, 0.4])
 ax_psf.yaxis.set_major_formatter(ticker.FormatStrFormatter("%.1f"))
 ax_psf.set_xlim(*xlim)
-ax_psf.set_xlabel("True Energy [TeV]")
+ax_psf.set_xlabel("True Energy / TeV")
 ax_psf.legend()
 
 # ax_edisp = axes[0, 1]

### 2023-03-06 src/figures/multi_instrument_analysis.py

@@ -14,7 +14,7 @@ from gammapy.modeling.models import SPECTRAL_MODEL_REGISTRY, Models
 sys.path.append("../data/multi-instrument")
 from make import CrabInverseComptonSpectralModel
 
-sed_x_label = r"$E\,/\,{\rm TeV}$"
+sed_x_label = "Energy / TeV"
 sed_y_label = (
     r"$E^2\,{\rm d}\phi/{\rm d}E\,/\,({\rm erg}\,{\rm cm}^{-2}\,{\rm s}^{-1})$"
 )

### 2023-03-06 src/ms-review.tex
Add code stats file and improve plot
Fix #110
Use siunitx package

@@
 \usepackage[autostyle]{csquotes}
+\usepackage{siunitx}
 
@@
 primary \gammaray photons and infer their incident direction and energy.
-VHE \gammaray astronomy covers the energy range from few tens of ${\rm GeV}$ up to the ${\rm PeV}$.
+VHE \gammaray astronomy covers the energy range from few tens of \unit{GeV} up to the \unit{PeV}.
 There are two main categories of ground-based instruments:
@@
 \section{Gamma-ray Data Analysis}
-\begin{figure*}[h!]
+\begin{figure*}[t]
 	\centering
@@
 \begin{equation}
-    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]}
+    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}), [\Phi] = \unit{TeV^{-1}.cm^{-2}.s^{-1}}
     \label{eq:general_source_model}
@@
 %
-\begin{figure*}[ht!]
+\begin{figure*}[t]
 	\centering
@@
          \hline
-         dnde & Differential flux at a given energy & $\mathrm{TeV^{-1}~cm^{-2}~s^{-1}}$ \\
-         e2dnde & Differential flux at a given energy  & $\mathrm{TeV~cm^{-2}~s^{-1}}$ \\
-         flux & Integrated flux in a given energy range & $\mathrm{cm^{-2}~s^{-1}}$ \\
-         eflux & Integrated energy flux in a given energy range & $\mathrm{erg~cm^{-2}~s^{-1}}$\\
+         dnde & Differential flux at a given energy & \unit{TeV^{-1}.cm^{-2}.s^{-1}} \\
+         e2dnde & Differential flux at a given energy  & \unit{TeV.cm^{-2}.s^{-1}} \\
+         flux & Integrated flux in a given energy range & \unit{cm^{-2}.s^{-1}} \\
+         eflux & Integrated energy flux in a given energy range & \unit{erg.cm^{-2}.s^{-1}}\\
          \hline
@@
 to a reconstructed index of $3.54 \pm 0.02$. With this adjusted spectral model
-the \code{LightCurveEstimator} runs directly for two energy bands, $0.5\,{\rm TeV} - 1.5\,{\rm TeV}$,
-and $1.5\,{\rm TeV} - 20\,{\rm TeV}$, respectively.
+the \code{LightCurveEstimator} runs directly for two energy bands,
+\qtyrange{0.5}{1.5}{TeV} and \qtyrange{1.5}{20}{TeV} respectively.
 %
@@
         Binned light curves in two different energy bands for the source
-        PKS~2155-304 in two energy bands ($0.5\,{\rm TeV} - 1.5\,{\rm TeV}$, and $1.5\,{\rm TeV} - 20\,{\rm TeV}$)
+        PKS~2155-304 in two energy bands (\qtyrange{0.5}{1.5}{TeV} and \qtyrange{1.5}{20}{TeV})
         as observed by the \hess telescopes in 2006. The coloured markers
@@
 position of the Crab Nebula, applying the same selection criteria of the 3FHL
-catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$,
+catalog (7 years of data with energy from \qty{10}{GeV} to \qty{2}{TeV},
 ~\citealt{3FHL}).
@@
 source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
-range spans $80\,{\rm GeV} - 20\,{\rm TeV}$. The data reduction for the 1D analysis
+range spans \qty{80}{GeV} to \qty{20}{TeV}. The data reduction for the 1D analysis
 is applied, and the data are reduced to a \code{SpectrumDataset} before being fitted.
@@
 via Gammapy's \code{FluxPoints} class. They were estimated in ~\cite{hawc_crab_2019}
-with $2.5\,{\rm years}$ of data and span an energy range $300\,{\rm GeV} - 300\,{\rm TeV}$.
+with $2.5\,{\rm years}$ of data and span an energy range \qty{300}{GeV} to \qty{300}{TeV}.
 
@@
 of the spectral model with the \irfs is performed to predict the counts in each estimated energy bin. A log
-parabola is fitted to the almost five decades in energy $10\,{\rm GeV} - 300\,{\rm TeV}$.
+parabola is fitted to the almost five decades in energy \qty{10}{GeV} to \qty{300}{TeV}.
 %% CN: is the LP formula specified elsewhere?

### 2023-03-06 src/ms-review.tex
Fix siunitx handling for version 2

@@
 primary \gammaray photons and infer their incident direction and energy.
-VHE \gammaray astronomy covers the energy range from few tens of \unit{GeV} up to the \unit{PeV}.
+VHE \gammaray astronomy covers the energy range from few tens of \si{GeV} up to the \si{PeV}.
 There are two main categories of ground-based instruments:
@@
 \begin{equation}
-    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}), [\Phi] = \unit{TeV^{-1}.cm^{-2}.s^{-1}}
+    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}), [\Phi] = \si{TeV^{-1}.cm^{-2}.s^{-1}}
     \label{eq:general_source_model}
@@
          \hline
-         dnde & Differential flux at a given energy & \unit{TeV^{-1}.cm^{-2}.s^{-1}} \\
-         e2dnde & Differential flux at a given energy  & \unit{TeV.cm^{-2}.s^{-1}} \\
-         flux & Integrated flux in a given energy range & \unit{cm^{-2}.s^{-1}} \\
-         eflux & Integrated energy flux in a given energy range & \unit{erg.cm^{-2}.s^{-1}}\\
+         dnde & Differential flux at a given energy & \si{TeV^{-1}.cm^{-2}.s^{-1}} \\
+         e2dnde & Differential flux at a given energy  & \si{TeV.cm^{-2}.s^{-1}} \\
+         flux & Integrated flux in a given energy range & \si{cm^{-2}.s^{-1}} \\
+         eflux & Integrated energy flux in a given energy range & \si{erg.cm^{-2}.s^{-1}}\\
          \hline
@@
 the \code{LightCurveEstimator} runs directly for two energy bands,
-\qtyrange{0.5}{1.5}{TeV} and \qtyrange{1.5}{20}{TeV} respectively.
+\SI{0.5}{TeV}~to~{1.5}{TeV} and \SI{1.5}{TeV}~to~{20}{TeV} respectively.
 %
@@
         Binned light curves in two different energy bands for the source
-        PKS~2155-304 in two energy bands (\qtyrange{0.5}{1.5}{TeV} and \qtyrange{1.5}{20}{TeV})
+        PKS~2155-304 in two energy bands (\SI{0.5}{TeV}~to~{1.5}{TeV} and \SI{1.5}{TeV}~to~{20}{TeV})
         as observed by the \hess telescopes in 2006. The coloured markers
@@
 position of the Crab Nebula, applying the same selection criteria of the 3FHL
-catalog (7 years of data with energy from \qty{10}{GeV} to \qty{2}{TeV},
+catalog (7 years of data with energy from \SI{10}{GeV} to \SI{2}{TeV},
 ~\citealt{3FHL}).
@@
 source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
-range spans \qty{80}{GeV} to \qty{20}{TeV}. The data reduction for the 1D analysis
+range spans \SI{80}{GeV} to \SI{20}{TeV}. The data reduction for the 1D analysis
 is applied, and the data are reduced to a \code{SpectrumDataset} before being fitted.
@@
 via Gammapy's \code{FluxPoints} class. They were estimated in ~\cite{hawc_crab_2019}
-with $2.5\,{\rm years}$ of data and span an energy range \qty{300}{GeV} to \qty{300}{TeV}.
+with $2.5\,{\rm years}$ of data and span an energy range \SI{300}{GeV} to \SI{300}{TeV}.
 
@@
 of the spectral model with the \irfs is performed to predict the counts in each estimated energy bin. A log
-parabola is fitted to the almost five decades in energy \qty{10}{GeV} to \qty{300}{TeV}.
+parabola is fitted to the almost five decades in energy \SI{10}{GeV} to \SI{300}{TeV}.
 %% CN: is the LP formula specified elsewhere?

### 2023-03-08 src/ms-review.tex
implement Matthias comments

@@
 		However, the next generation of \gammaray instruments,
-		such as the the Cherenkov Telescope Array, will be operated as open observatories.
+		such as the Cherenkov Telescope Array Observatory (CTAO), will be operated as open observatories.
 		Alongside the data, they will also make associated software tools available to a wider community.
@@
 		After describing the structure of the package, we show the capabilities of \gammapy
-		in multiple traditional and novel \gammaray analysis scenarios using public data
+		in multiple traditional and novel \gammaray analysis scenarios using public data, 
 		such as spectral and spectro-morphological modelling and estimations of a spectral energy
@@
 branches of astronomy, \gammarays can be observed by
-satellite as well as ground based instruments.
+satellite as well as ground-based instruments.
 Ground-based instruments use the Earth's atmosphere as a particle detector.
@@
 shower when it reaches the ground. These instruments have a very
-large FoV and large duty-cycle, but a higher energy threshold and
+large FoV, and large duty-cycle, but a higher energy threshold and
 lower signal-to-noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
@@
 		Core idea and relation of \gammapy to different \gammaray instruments
-		and the gamma astro data formats (GADF). The top left shows the
+		and the gamma astro data format (GADF). The top left shows the
 		group of current and future pointing instruments based on the 
 		imaging atmospheric Cherenkov technique (IACT). This includes
-		instruments such as the Cherenkov Telescope Array (CTA),
+		instruments such as the Cherenkov Telescope Array Observatory (CTAO),
 		the High Energy Stereoscopic System (H.E.S.S.), the
@@
 		\gammapy can read data stored in the GADF format.
-		The \gammapy package is not a part of any instrument, but instead
+		The \gammapy package is a community-developed project that
 		provides a common interface to the data and analysis of all
@@
 %TODO: better transition into context
-The Cherenkov Telescope Array (CTA) will be the first ground-based \gammaray instrument to be operated as an open observatory.
+The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based \gammaray instrument to be operated as an open observatory.
 Its high-level data\footnote{The lowest reduction level of data published by CTAO will be reconstructed event lists and corresponding instrument response functions.} will be shared publicly after
@@
 software library for very high-energy \gammaray data analysis \citep{gammapy_2015}. 
-The core of the idea is illustrated in Figure~\ref{fig:big_picture}. Various \gammaray instruments
-export their data to the standardised common \gadf data format. This data can then be combined and
+The core of the idea is illustrated in Figure~\ref{fig:big_picture}. The various \gammaray instruments
+can export their data to a common data format (\gadf) and then these data can be combined and
 analysed using a common software library.
-This means that the \gammapy package is not specific to any instrument,
-but an independent community-developed software project.
+The \gammapy is package an independent community-developed software project, it has been selected to be the core library for the Science Analysis tools of CTAO
+but also involves contributors associated to other instruments.
 The \gammapy package is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
@@
 %% CN: what about mentioning the joint Crab? or is it mentioned later?
-With the public availability of the \gadf format sepcifications and the
+With the public availability of the \gadf format specifications and the
 \gammapy package, some experiments started to make limited subsets of
@@
 the \gammapy package in \cite{Olivera2022}.
+The increased availability of public data that followed the definition of a common data format, and the development of \gammapy as a community-driven open software, led the way toward a more open science in the very-high-energy \gray Astronomy domain.
+In future CTAO will be an open observatory committed to follow the FAIR (Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} that define the key requirements for open science.
 
@@
         defines the different levels of data reduction, from lists of \gammaray-like
-        events on the left (DL3), to high-level scientific products products
+        events on the left (DL3), to high-level scientific products
         (DL5) on the right. The direction of the data flow is illustrated with the
@@
 The data analysis process in \gammaray astronomy is usually split into two parts.
-The first one deals with the data processing from camera measurement, calibration, event
+The first one deals with the data processing from detector measurement, calibration, event
 reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
@@
 shared across the field. The similarity in the high-level analysis would also allow
-for combining data from multiple instruments, but could not be fully exploited, due to
-a lack of common data formats and software tools.
+for combining data from multiple instruments.
 
@@
   measuring a direction $p$ when the true direction is $p_{\rm true}$ and the true energy is $E_{\rm true}$.
-  \gammaray instruments consider the probability density of the angular separation between true and reconstructed directions
-  $\delta p = p_{\rm true} - p$, i.e. $PSF(\delta p|p_{\rm true}, E_{\rm true})$.
+  \gammaray instruments consider $PSF(\delta p|p_{\rm true}, E_{\rm true})$, the probability density of the angular separation between true and reconstructed directions,
+  $\delta p = p_{\rm true} - p$.
 \item $E_{\rm disp}(E|p_{\rm true}, E_{\rm true})$ is the energy dispersion. It gives the probability to
   reconstruct the photon at energy $E$ when the true energy is $E_{\rm true}$ and the true position $p_{\rm true}$.
-  \gammaray instruments consider the probability density of the migration $\mu=\frac{E}{E_{\rm true}}$,
-  i.e. $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$.
+  \gammaray instruments consider $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$, the probability density of the migration, $\mu=\frac{E}{E_{\rm true}}$.
 \end{itemize}
@@
 The first step in \gammaray data analysis is the selection and extraction of observations
-based of their metadata including information such as pointing direction, observation
+based on their metadata including information such as pointing direction, observation
 time and observation conditions. The access to the events data and instrument 
@@
 in a format specific to \gammapy to allow users to read them back at any time later
-for modeling and fitting. Different variations of such datasets support different 
+for modelling and fitting. Different variations of such datasets support different 
 analysis methods and fit statistics. The datasets can be used to perform a joint-likelihood
@@
 Independently or subsequently to the global modelling, the data can be
-re-grouped to compute flux points, light curves and flux as well as significance
+re-grouped to compute flux points, light curves and flux maps as well as significance
 maps in different energy bands.
@@
 sub-package which provides a high-level interface for executing analyses
-defined from configuration files. In the following sections we will
+defined from configuration files. In the following sections, we will
 introduce all sub-packages and their functionalities in more detail.
@@
 supports data that is compliant with \code{v0.2} and \code{v0.3} of the \gadf data format.
-DL3 data are typically bundled into individual observations, which
-corresponds to stable periods of data acquisition. For IACT data analysis,
+DL3 data are typically bundled into individual observations, corresponding to stable periods of data acquisition. For IACT data analysis,
 for which the GADF data model and Gammapy were initially conceived,
@@
 First a \code{DataStore} object is created from the path of the data
-directory. The directory contains an observation as well as a FITS HDU 
+directory. The directory contains an observation as well as a FITS HDU \footnote{Header Data Unit} 
 index file which assigns the correct data and IRF FITS files and HDUs
@@
 		lines along with the sum of all event classes as a black line. The \hawc IRFs are taken from
-		the first public release of event data the \hawc collaboration. All IRFs do not correspond
+		the first public release of events data by the \hawc collaboration. All IRFs do not correspond
 		to the latest performance of the instruments, but still are representative of the 
 		detector type and energy range. We exclusively relied on publicly available
-		data provided by the collaborations. The data is also availabe in the
+		data provided by the collaborations. The data is also available in the
 		\code{gammapy-data} repository.
@@
 it from scratch. The \code{EffectiveAreaTable2D} class can also convert, interpolate,
-write, and evaluate the effective area for a given energy and offset angles, or
+write, and evaluate the effective area for a given energy and offset angle, or
 even plot the multi-dimensional effective area table.
@@
 the \code{PSFMap} class is used. It stores the radial profile of the PSF
-depending on the true energy and position on the sky. During the modeling
+depending on the true energy and position on the sky. During the modelling
 step in the analysis, the PSF profile for each model component is 
@@
 which contains an energy disperion matrix per sky position. I.e., a 4-dimensional
-sky map where at each position is associated to an energy dispersion matrix.
+sky map where each position is associated to an energy dispersion matrix.
 The energy dispersion matrix is a representation of the energy resolution
-as a function of the true energy only and implemnted in \gammapy
+as a function of the true energy only and implemented in \gammapy
 by the sub-class \code{EDispKernel}.
@@
         unit. Region definitions can be passed as strings following
-        the DS9 region specifications \url{http://ds9.si.edu/doc/ref/region.html}.The output
+        the DS9 region specifications \url{http://ds9.si.edu/doc/ref/region.html}. The output
 		of the code example is shown in Figure~\ref{fig:code_example_gp_maps}.
@@
 the multiscale definition of the HEALPix pixelisation and thus
-allows for easy up and downsampling of the data. In addition to
+allows for easy upsampling and downsampling of the data. In addition to
 the all-sky map, \gammapy also supports a local HEALPix
@@
 radius.
-For local neighbourhood operations, such as convolution \gammapy relies
+For local neighbourhood operations, such as convolution, \gammapy relies
 on projecting the HEALPix data to a local tangential WCS grid.
@@
 provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
-modeling and fitting purposes. Depending upon the type of analysis and the
+modelling and fitting purposes. Depending upon the type of analysis and the
 associated statistic, different types of Datasets are supported. The \code{MapDataset} is
@@
 The \code{gammapy.makers} sub-package contains the various classes and functions required
-to process and prepare \gammaray data from the DL3 to the DL4, representing the input for modeling and fitting.
+to process and prepare \gammaray data from the DL3 to the DL4, representing the input for modelling and fitting.
 First, events are binned and IRFs are interpolated and projected onto the chosen analysis
@@
         Using \code{gammapy.stats} to compute statistical quantities
-        such as excess, signficance and assymetric errors
+        such as excess, significance and asymetric errors
         from counts based data. The data is passed on initialisation
@@
 %
-\code{gammapy.modeling} contains all the functionality related to modeling and fitting
+\code{gammapy.modeling} contains all the functionality related to modelling and fitting
 data. This includes spectral, spatial and temporal model classes, as well as
@@
 either, for example, from multiple sources and from a diffuse emission, or from several spectral
-components within the same source. To handle lists of multiple \code{SkyModel} objects, \gammapy
+components within the same source. To handle a list of multiple \code{SkyModel} objects, \gammapy
 implements a \code{Models} class.
@@
 built-in. We also offer a wrapper to radiative models implemented in the Naima
-package~\citep{naima}. The modeling framework can be easily extended with
+package~\citep{naima}. The modelling framework can be easily extended with
 user-defined models. For example, the radiative models of jetted Active Galactic Nuclei (AGN)
@@
 multiple datasets, allowing e.g., to perform a joint fit to
-multiple IACT datasets, or to jointly fit IACT and \fermi dataset. Many
+multiple IACT datasets, or to jointly fit IACT and \fermi datasets. Many
 examples are given in the tutorials.
@@
 counts per flux bin; the total fit statistics
-of the best fit model; the fit statistics of the
-null hypothesis; and the difference between both,
-the so-called \textit{TS value}.
+of the best fit model (for signal and background); the fit statistics of the
+null hypothesis (background only); and the difference between both,
+the so-called test statistic value (\textit{TS}).
 From this \textit{TS value}, a significance of the measured signal and associated flux
@@
 	\caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
-        a flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
+	 flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
         and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
-        of the flux error and and flux upper limit maps respectively. The output
+        of the flux error and flux upper limit maps respectively. The output
 		of the code example is shown in Figure~\ref{fig:code_example_gp_estimators}.
@@
 
-The \code{Analysis} class has the responsibility of orchestrating of the workflow
+The \code{Analysis} class has the responsibility for orchestrating the workflow
 defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
@@
 
-In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modeling
+In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modelling
 galactic \gammaray sources according to simplified physical models, e.g. Supernova Remnant (SNR) evolution
-models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of Pulsar Wind Nebula (PWN) during the
+models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of Pulsar Wind Nebulae (PWNe) during the
 free expansion phase \citep{2006ARA&A..44...17G} or computation
@@
 contains the actual catalog as an Astropy \code{Table} object.
-Objects in the catalog can be accesed by row index, name of the
+Objects in the catalog can be accessed by row index, name of the
 object or any association or alias name listed in the catalog.
@@
 the spatial and spectral models of the source, flux points and
-light curves (if available) for each individual object. This
-module works independently from the rest of the package, and the required
-catalogs are supplied in \code{GAMMAPY\_DATA} repository.
-The overview of currenly supported catalogs, the corresponding
+light curves (if available) for each individual object. Figure ~\ref{fig*:minted:gp_catalogs}
+show how to load a given catalog and access these information for a selected source.
+This module works independently from the rest of the package, and the required
+catalogs are supplied in the \code{GAMMAPY\_DATA} repository.
+The overview of currently supported catalogs, the corresponding
 \gammapy classes and references are shown in Table~\ref{tab:catalogs}.
@@
 of the current instrument private software frameworks.
-The examples shown are limited by the availability of public data,
-with those employed being publicly available data collected within the \code{gammapy-data} repository.
-We remark that, as long as the data are compliant with the GADF specifications,
+The examples shown are based on the data accessible in the \code{gammapy-data} repository,
+and limited by the availability of public data.
+We remark that, as long as the data are compliant with the GADF specifications (or its future evolutions),
 and hence with Gammapy's data structures, there is no limitation on performing
@@
 measured in a circular aperture centered on the Galactic Center, in
-\gammaray~astronomy often called \enquote{on region}. For such analysis the users first
+\gammaray~astronomy often called \enquote{on region}. For such analysis the user first
 chooses a region of interest and energy binning, both defined by a
@@
 the expected background in the \enquote{on region} a \enquote{reflected regions} background
-method was used~\cite{Berge07}, represented in \gammapy by the
+method was used~\citep{Berge07}, represented in \gammapy by the
 \code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
@@
 This model was then combined with the \code{SpectrumDataset}, which contains the reduced data 
-and fitted using the and \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
+and fitted using the \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
 log-likelihood profiles were computed using the \code{FluxPointsEstimator}.
@@
     \item an extended source with Gaussian morphology located at (l=0.4\textdegree,
-	      b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log parabola spectral
+	      b=0.15\textdegree) with $\sigma$=0.2\textdegree~and a log parabola spectral
 	      shape,
@@
 Note that all the models fitted also have a spectral component, from which flux
-points can be derived in a similar way as described in~\ref{ssec:1d-analysis}.
+points can be derived in a similar way as described in Section~\ref{ssec:1d-analysis}.
 %\end{figure*}%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?%
@@
         fit model and the transparent band its $1\sigma$ error range.
-		The band is to small be visible.
+		The band is too small be visible.
     }
@@
 of the spectral model with the \irfs is performed to predict the counts in each estimated energy bin. A log
-parabola is fitted to the almost five decades in energy \SI{10}{GeV} to \SI{300}{TeV}.
+parabola is fitted over almost five decades in energy \SI{10}{GeV} to \SI{300}{TeV}, taking into account all flux points from all three datasets.
 %% CN: is the LP formula specified elsewhere?
@@
 
-\subsection{Broadband SED Modeling}
+\subsection{Broadband SED Modelling}
 \label{ssec:broadband-sed-modeling}
@@
 Compton model computed with Naima and wrapped in the \gammapy models
-through the \code{NaimaSpectraModel} class. We describe the gamma-ray emission 
+through the \code{NaimaSpectralModel} class. We describe the gamma-ray emission 
 with an inverse Compton scenario, considering a log-parabolic
@@
 
-Sky surveys have a large potential for new source detections, and new phenomena
-discovery in \gammaray astronomy. They also offer less selection bias to perform
+Sky surveys have a large potential for new source detections, and discovery of new phenomena
+ in \gammaray astronomy. They also offer less selection bias to perform
 source population studies over a large set of coherently detected and modelled objects.
@@
 determine their optimal parameters, and the best-candidate model. The
-subpackage \code{gammapy.modeling.models} offers a large variety of choice, and the
+subpackage \code{gammapy.modeling.models} offers a large variety of choices, and the
 possibility to add custom models.  Several spatial models (point-source, disk,
@@
 object catalogs, coding sprints and weekly developer calls minutes,
-contributions to conferences, other digital assets, etc.) Finally, third-party
+contributions to conferences, other digital assets, etc). Finally, third-party
 services for code quality metrics are also set and may be found as status
@@
 so that every release triggers the update of the versioned record. In addition,
-the next release of \gammapy will be added to the Open-source scientific
+ \gammapy has been added to the Open-source scientific
 Software and Service Repository\footnote{\url{https://projectescape.eu/ossr}}
@@
 
-In addition \gammapy is also listed in the \textit{SoftWare
+In addition, \gammapy is also listed in the \textit{SoftWare
 Heritage}~\footnote{\url{https://softwareheritage.org}} (SWH) archive~\cite{DiCosmo2020}.
@@
 support forums, providing valuable feedback on the \gammapy functionalities,
-interface and documentation. Other communication channels have been set like
+interface and documentation. Other communication channels have been set such as
 mailing lists, a Twitter account\footnote{\url{https://twitter.com/gammapyST}},
-regular public coding sprint meetings, hands-on session within collaborations,
+regular public coding sprint meetings, hands-on sessions within collaborations,
 weekly development meetings, etc.
@@
 are presented to the \gammapy developer community in a pull request
-on \github and the undergo a review phase in which changes and
+on \github and then undergo a review phase in which changes and
 improvements to the document are proposed and implemented. Once the PIG
@@
 we will work with a deprecation system for minor releases.
-API-breaking changes will be announced to user by runtime
+API-breaking changes will be announced to users by runtime
 warnings first and then implemented in the subsequent
@@
 \gammapy is a Python package for \gammaray astronomy, which relies on the
-scientific Python ecosystem, including Numpy and Scipy and Astropy as
+scientific Python ecosystem, including Numpy, Scipy, and Astropy as
 main dependencies. It also holds the status of an Astropy affiliated

### 2023-03-09 src/ms-review.tex
Add Léa Jouvin
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

--- 2023-03-06 src/ms-review.tex
@@
 	Luca Giunti \inst{\ref{inst:20}} \and
+	Léa Jouvin \inst{\ref{inst:32}} \and
 	Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
@@
 	Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:30} \and
-	Université Bordeaux, CNRS, LP2I Bordeaux, UMR 5797 \label{inst:31}
+	Université Bordeaux, CNRS, LP2I Bordeaux, UMR 5797 \label{inst:31} \and
+	IRFU, CEA, Université Paris-Saclay, F-91191 Gif-sur-Yvette, France \label{inst:32}
 }

### 2023-03-10 src/ms-review.tex

--- 2023-03-08 src/ms-review.tex
@@
 analysed using a common software library.
-The \gammapy is package an independent community-developed software project, it has been selected to be the core library for the Science Analysis tools of CTAO
+The \gammapy package is an independent community-developed software project, it has been selected to be the core library for the Science Analysis tools of CTAO
 but also involves contributors associated to other instruments.

### 2023-03-13 src/ms-review.tex
Add OSSR reference and citation

@@
  \gammapy has been added to the Open-source scientific
-Software and Service Repository\footnote{\url{https://projectescape.eu/ossr}}
+Software and Service Repository\footnote{\url{https://projectescape.eu/ossr}} \citep{10.12688/openreseurope.15692.1}
 and indexed in the European Open Science Cloud

### 2023-03-15 src/ms-review.tex
Address first batch of comments

@@
         gray arrows. The gray folder icons represent the different sub-packages
-        in \gammapy and their names. Below each icon there is a list of the most
-        important objects defined in the sub-package.
+        in \gammapy and names given as the corresponding Python code suffix, e.g. 
+		\code{gammapy.data}. Below each icon there is a list of the most
+        important objects defined in the sub-package. The bottom of the figure
+		shows the 
     }
@@
 
-where $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response and $t_{\rm obs}$ is the observation time
+where $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response and $t_{\rm obs}$ is the observation duration.
 
@@
   reconstruct the photon at energy $E$ when the true energy is $E_{\rm true}$ and the true position $p_{\rm true}$.
-  \gammaray instruments consider $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$, the probability density of the migration, $\mu=\frac{E}{E_{\rm true}}$.
+  \gammaray instruments consider $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$, the probability density of the event migration, $\mu=\frac{E}{E_{\rm true}}$.
 \end{itemize}
@@
 In general, IRFs depend on the geometrical parameters of the detector, e.g. location 
-of an event in the FoV or the elevation angle of the event. So IRFs might be parametrised
-as a function of such detector specific coordinates too.
+of an event in the FoV or the elevation angle of the incoming direction of the event.
+Consequently IRFs might be parametrised as functions of detector specific coordinates too.
 

### 2023-03-15 src/ms-review.tex
Address more review comments

@@
 the \gammapy package in \cite{Olivera2022}.
-The increased availability of public data that followed the definition of a common data format, and the development of \gammapy as a community-driven open software, led the way toward a more open science in the very-high-energy \gray Astronomy domain.
-In future CTAO will be an open observatory committed to follow the FAIR (Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} that define the key requirements for open science.
+The increased availability of public data that followed the definition of
+a common data format, and the development of \gammapy as a community-driven open software,
+led the way toward a more open science in the very-high-energy \gammaray Astronomy domain.
+In future CTAO will be an open observatory committed to follow the FAIR
+(Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} 
+that define the key requirements for open science.
 
@@
 DL3 data are typically bundled into individual observations, corresponding to stable periods of data acquisition. For IACT data analysis,
-for which the GADF data model and Gammapy were initially conceived,
+for which the GADF data model and \gammapy were initially conceived,
 these are usually $20 - 30\,{\rm min}$ long.
@@
 Beside reproducing standard methodologies, we illustrate the unique data combination
-capabilites of Gammapy by presenting a multi-instrument analysis to date not possible within any
+capabilites of \gammapy by presenting a multi-instrument analysis, which is not possible within any
 of the current instrument private software frameworks.
@@
 		Example of a one dimensional spectral analysis of the Galactic Center for three simulated CTA
-		observations for the 1DC dataset. The left image shows the maps of counts with the signal
-		region in white and background regions overlaid in different colors. The right image
-		shows the resulting spectral points and their corresponding log-likelihood
-		profiles.}
+		observations from the 1DC dataset. The left image shows the maps of counts with the signal
+		region in white and the reflected background regions for the three different observations
+		overlaid in different colors. The right image shows the resulting spectral flux points and
+		their corresponding log-likelihood profiles. The flux points are shown in orange, with the
+		horizontal bar illustrating the width of the energy bin and the vertical bar the $1~\sigma$
+		error. The log-likelihood profiles for each enetgy bin are shown in the background. The colormap
+		illustrates the difference of the log-likelihood to the log-likelihood of the best fit value.
+		}
 	\label{fig:cta_galactic_center}
@@
 	\caption{
-        Binned light curves in two different energy bands for the source
-        PKS~2155-304 in two energy bands (\SI{0.5}{TeV}~to~{1.5}{TeV} and \SI{1.5}{TeV}~to~{20}{TeV})
+        Binned PKS~2155-304 light curve in two different energy bands
         as observed by the \hess telescopes in 2006. The coloured markers
-        show the flux points in the different energy bands. The horizontal
-        error illustrates the width of the time bin of 10~min. The vertical
+        show the flux points in the different energy bands:
+		the range from (\SI{0.5}{TeV}~to~{1.5}{TeV} is shown in blue, while
+		the range from \SI{1.5}{TeV}~to~{20}{TeV}) is shown in orange.
+		The horizontal error illustrates the width of the time bin of 10~min. The vertical
         error bars show the associated asymmetrical flux errors. The marker
@@
 By combining \gammapy with astrophysical modelling codes, users can also fit
-astrophysical spectral models to \gammaray data. In \gammaray
-astronomy one typically observes two radiation production
-mechanisms, the so-called hadronic and leptonic scenarios.
+astrophysical spectral models to \gammaray data. 
 There are several Python packages that are able to model
@@
 Typically those emission models predict broadband emission from
-radio, up to the very high-energy \gammaray range.
+radio, up to very high-energy \gammarays.
 By relying on the multiple dataset types in \gammapy those
@@
 
-As an example of this application, we use the same multi-instrument
-dataset described in the previous section and we fit it with an inverse
+As an example application, we use the same multi-instrument
+dataset of the Crab Nebula, described in the previous section,
+and we apply an inverse
 Compton model computed with Naima and wrapped in the \gammapy models
@@
 with an inverse Compton scenario, considering a log-parabolic
-electron distribution that scatters: the synchrotron radiation produced by
-the very same electrons; near and far infrared photon fields and the cosmic
-microwave background (CMB). We adopt the prescription on the target
-photon fields provided in the documentation of the \textit{Naima}
+electron distribution that scatters photons from:
+%
+\begin{itemize}
+	\item the synchrotron radiation produced by
+	the very same electrons
+	\item near and far infrared photon fields
+	\item and the cosmic microwave background (CMB)
+\end{itemize}
+%
+We adopt the prescription on the target photon fields provided in the documentation of the \textit{Naima}
 package\footnote{\url{https://naima.readthedocs.io/en/stable/examples.html\#crab-nebula-ssc-model}}.
@@
 	\texttt{Matplotlib} communities for providing their packages which are
-	invaluable to the development of Gammapy. We thank the \github team for
+	invaluable to the development of \gammapy. We thank the \github team for
 	providing us with an excellent free development platform. We also are grateful

### 2023-03-15 src/code-examples/snippets/gp_estimators.py
Add colorbar to estimator example

@@ -1,10 +1,9 @@
-from gammapy.datasets import MapDataset
-from gammapy.estimators import TSMapEstimator
 from astropy import units as u
 
-dataset = MapDataset.read(
-    "$GAMMAPY_DATA/cta-1dc-gc/cta-1dc-gc.fits.gz"
-)
+from gammapy.datasets import MapDataset
+from gammapy.estimators import TSMapEstimator
+
+dataset = MapDataset.read("$GAMMAPY_DATA/cta-1dc-gc/cta-1dc-gc.fits.gz")
 
 estimator = TSMapEstimator(
     energy_edges=[0.1, 1, 10] * u.TeV,
@@ -13,4 +12,4 @@ estimator = TSMapEstimator(
 )
 
 maps = estimator.run(dataset)
-maps["sqrt_ts"].plot_grid()
+maps["sqrt_ts"].plot_grid(add_cbar=True)

### 2023-03-15 src/ms-review.tex
Fix unit formatting

@@
 the \code{LightCurveEstimator} runs directly for two energy bands,
-\SI{0.5}{TeV}~to~{1.5}{TeV} and \SI{1.5}{TeV}~to~{20}{TeV} respectively.
+\SI{0.5}{TeV}~to~\SI{1.5}{TeV} and \SI{1.5}{TeV}~to~\SI{20}{TeV} respectively.
 %
@@
         show the flux points in the different energy bands:
-		the range from (\SI{0.5}{TeV}~to~{1.5}{TeV} is shown in blue, while
-		the range from \SI{1.5}{TeV}~to~{20}{TeV}) is shown in orange.
+		the range from (\SI{0.5}{TeV}~to~\SI{1.5}{TeV} is shown in blue, while
+		the range from \SI{1.5}{TeV}~to~\SI{20}{TeV}) is shown in orange.
 		The horizontal error illustrates the width of the time bin of 10~min. The vertical

### 2023-03-15 src/figures/data_flow.py
Fix Fig 2 font size and improve caption

@@ -1,19 +1,20 @@
 import logging
+
 import click
-import numpy as np
-import matplotlib.pyplot as plt
+import config
 import matplotlib
 import matplotlib.lines as mlines
+import matplotlib.pyplot as plt
 import matplotlib.transforms as mtrans
-from matplotlib.patches import Polygon, FancyArrow, PathPatch, FancyArrowPatch
-from matplotlib.text import TextPath
-from matplotlib.ticker import MultipleLocator
+import numpy as np
 from astropy import units as u
 from astropy.table import Table
+from matplotlib.patches import FancyArrow, FancyArrowPatch, PathPatch, Polygon
+from matplotlib.text import TextPath
+from matplotlib.ticker import MultipleLocator
+
 from gammapy.estimators import FluxPoints
 from gammapy.maps import Map
-import config
-
 
 logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
@@ -26,9 +27,7 @@ FOLDER_ICON = np.array(
     [(0, 0), (0, 0.8), (0.08, 1), (0.5, 1), (0.58, 0.8), (0.93, 0.8), (0.93, 0)]
 )
 
-DOC_ICON = np.array(
-    [(0, 0), (0, 0.85), (0.15, 1), (0.75, 1), (0.75, 0)]
-)
+DOC_ICON = np.array([(0, 0), (0, 0.85), (0.15, 1), (0.75, 1), (0.75, 0)])
 
 GRAY = "gray"
 LIGHT_GRAY = "#ECECEC"
@@ -58,7 +57,12 @@ def plot_sub_package_icon(
     ax, offset=(0.5, 0.5), name=".makers", size=(22, 14), color=GP_GRAY, classes=[]
 ):
     p = Polygon(
-        offset + size * FOLDER_ICON, fc="None", ec=color, lw=1, transform=ax.transData, zorder=2
+        offset + size * FOLDER_ICON,
+        fc="None",
+        ec=color,
+        lw=1,
+        transform=ax.transData,
+        zorder=2,
     )
     ax.add_artist(p)
 
@@ -72,7 +76,14 @@ def plot_sub_package_icon(
         color=GP_ORANGE,
         zorder=2,
     )
-    ax.text(offset[0] + 6, offset[1] + 5.5, s="$\pi$", size=fontsize_gp, color=color, zorder=2)
+    ax.text(
+        offset[0] + 6,
[…]

### 2023-03-15 src/figures/data_flow.py
Adapt data flow figure

@@ -191,7 +191,7 @@ def plot_catalog(ax):
                 color=GP_GRAY,
                 va="center",
                 ha="center",
-                size=6,
+                size=7,
             )
 
 
@@ -206,6 +206,7 @@ def plot_lightcurve(ax):
     # ax.set_ylim(3e-11, 4e-10)
     # ax.set_xlim(53945.85, 53946.09)
     ax.legend(fontsize=8, labelspacing=0.1)
+    ax.set_xlabel("Time", labelpad=0)
 
 
 def plot_sed(ax):
@@ -224,7 +225,8 @@ def plot_sed(ax):
 
     flux_points.plot_ts_profiles(ax=ax, sed_type="e2dnde", add_cbar=False)
     format_dl5_ax(ax=ax)
-    ax.set_title("SEDs & Lightcurves", color=GP_GRAY, pad=4)
+    ax.set_title("Flux Points", color=GP_GRAY, pad=4)
+    ax.set_xlabel("Energy", labelpad=0)
 
 
 def plot_image(ax):
@@ -232,7 +234,7 @@ def plot_image(ax):
     log.info(f"Reading: {filename}")
     m = Map.read(filename)
     m.plot(ax=ax, cmap="inferno", stretch="sqrt")
-    ax.set_title("Flux & TS Maps", color=GP_GRAY, pad=4)
+    ax.set_title("Sky Maps", color=GP_GRAY, pad=4)
     format_dl5_ax(ax=ax)
 
 
@@ -335,7 +337,7 @@ def main(draft=True):
 
     xpos = 123
     plot_arrow(ax, offset=(xpos, 35), dx=23, width=12, fc=LIGHT_GRAY, **kwargs)
-    plot_arrow(ax, offset=(xpos, 64), dx=23, width=12, fc=LIGHT_GRAY, **kwargs)
+    plot_arrow(ax, offset=(xpos, 68), dx=23, width=12, fc=LIGHT_GRAY, **kwargs)
     plot_arrow(ax, offset=(xpos, 96), dx=23, width=12, fc=LIGHT_GRAY, **kwargs)
 
     classes = ["DataStore", "Observations", "Observation", "GTI"]
@@ -376,13 +378,13 @@ def main(draft=True):
     else:
         ax.set_axis_off()
 
-    ax_image = add_sub_axes(ax, [148, 54, 30, 20])
[…]

### 2023-03-15 src/ms-review.tex
Fix Fig 2 font size and improve caption
Mention time analysis in outlook

@@
 		\code{gammapy.data}. Below each icon there is a list of the most
-        important objects defined in the sub-package. The bottom of the figure
-		shows the 
+        important objects defined in the sub-package. The light grey folder
+		icons show the subpackages for the most fundamental data structures such 
+		as maps and IRFs. The bottom of the figure shows the high-level analysis
+		sub-module with its dependcy on the YAML file format. 
     }
@@
         such as excess, significance and asymetric errors
-        from counts based data. The data is passed on initialisation
-        of the \code{WStatCountsStatistic} class. The quantities
-        are the computed ON excess of the corresponding class
-        attributes such as \code{stat.n\_sig} and \code{stat.sqrt\_ts}.
+        from counts based data. The data array such as \code{counts}, \code{counts_off}
+		and the background efficency ratio \code{alpha} are passed on initialisation
+        of the \code{WStatCountsStatistic} class. The derived quantities
+        are then computed dynamically from the corresponding class
+        attributes such as \code{stat.n\_sig} for the excess
+		and \code{stat.sqrt\_ts} for the significance.
 		The output of the code example is shown in Figure~\ref{fig:code_example_gp_stats}.
@@
 \end{figure}
-%% CN: the figure does not explain what alpha is
 
@@
 and provenance information to track the history of the data reduction
-process from the DL3 to the highest DL5/DL6 data levels.
+process from the DL3 to the highest DL5/DL6 data levels. \gammapy will
+also extend its functionality for time based analyses, including
+tests for variability in lightcurves and phase curves as well as
+improving the interoperabiltiy with other timing packages such
+as \textit{Stingray}~\citep{Stingray2019} and \textit{Astropy's}
+time series classes.
 

### 2023-03-15 src/ms-review.tex
Fix build

@@
 \newcommand{\gammaray}{$\gamma$-ray\xspace}
-\newcommand{\gammarays}{$\gamma$ rays\xspace}
+\newcommand{\gammarays}{$\gamma$-rays\xspace}
 \newcommand{\gadf}{GADF\xspace}
@@
         such as excess, significance and asymetric errors
-        from counts based data. The data array such as \code{counts}, \code{counts_off}
+        from counts based data. The data array such as \code{counts}, \code{counts\_off}
 		and the background efficency ratio \code{alpha} are passed on initialisation

### 2023-03-16 src/ms-review.tex
Fix #112

@@
   of the detector collection area times its detection efficiency at true energy $E_{\rm true}$ and position $p_{\rm true}$.
-\item $PSF(p|p_{\rm true}, E_{\rm true})$ is the point spread function (PSF). It gives the probability of
+\item $PSF(p|p_{\rm true}, E_{\rm true})$ is the point spread function (PSF). It gives the probability density of
   measuring a direction $p$ when the true direction is $p_{\rm true}$ and the true energy is $E_{\rm true}$.
-  \gammaray instruments consider $PSF(\delta p|p_{\rm true}, E_{\rm true})$, the probability density of the angular separation between true and reconstructed directions,
-  $\delta p = p_{\rm true} - p$.
+  \gammaray instruments typically consider radial symmetry of the PSF. With this assumption the probability density 
+  $PSF(\Delta p|p_{\rm true}, E_{\rm true})$ only depends on the angular separation between true
+ and reconstructed direction defined by $\Delta p = p_{\rm true} - p$.  
 \item $E_{\rm disp}(E|p_{\rm true}, E_{\rm true})$ is the energy dispersion. It gives the probability to

### 2023-03-21 src/figures/irfs.py
Update IRF figures and text
Signed-off-by: Fabio Pintore <fabio.pintore@inaf.it>

@@ -7,7 +7,7 @@ import numpy as np
 from astropy import units as u
 
 from gammapy.data import DataStore
-from gammapy.irf import PSFMap
+from gammapy.irf import PSFMap, load_irf_dict_from_file
 from gammapy.maps import Map
 
 logging.basicConfig(level=logging.INFO)
@@ -18,8 +18,12 @@ hawc_lifetime = 6.4 * u.h
 
 offset = [1] * u.deg
 
-data_store = DataStore.from_dir("../data/input/cta-1dc/index/gps")
-obs_cta = data_store.obs(110380)
+#data_store = DataStore.from_dir("../data/input/cta-1dc/index/gps")
+#obs_cta = data_store.obs(110380)
+cta_north = ("../data/cta-caldb/Prod5-North-20deg-AverageAz-4LSTs09MSTs.180000s-v0.1.fits")
+cta_south = ("../data/cta-caldb/Prod5-South-20deg-AverageAz-14MSTs37SSTs.180000s-v0.1.fits")
+irf_cta_north = load_irf_dict_from_file(cta_north)
+irf_cta_south = load_irf_dict_from_file(cta_south)
 
 data_store = DataStore.from_dir("../data/input/hess-dl3-dr1/")
 obs_hess = data_store.obs(33787)
@@ -48,7 +52,7 @@ color = ax_aeff.lines[-1].get_color()
 ax_aeff.text(x=10, y=1e6, s="H.E.S.S.", color=color)
 
 # CTA
-obs_cta.aeff.plot_energy_dependence(ax=ax_aeff, offset=offset, label="CTA", **kwargs)
+irf_cta_south["aeff"].plot_energy_dependence(ax=ax_aeff, offset=offset, label="CTA", **kwargs)
 color = ax_aeff.lines[-1].get_color()
 ax_aeff.text(x=0.06, y=3e5, s="CTAO", color=color)
 
@@ -102,15 +106,10 @@ ax_aeff.get_legend().remove()
 
 # PSF
 psf_hess = obs_hess.psf.slice_by_idx({"energy_true": slice(10, None)})
-psf_cta = obs_cta.psf.slice_by_idx({"energy_true": slice(None, -2)})
+psf_cta = irf_cta_south["psf"].slice_by_idx({"energy_true": slice(1, None)})
 
 ax_psf = axes[1]
 ax_psf.set_title("Point Spread Function")
[…]

### 2023-03-21 src/figures/irfs.py
update irf figures
Signed-off-by: Fabio Pintore <fabio.pintore@inaf.it>

@@ -18,8 +18,6 @@ hawc_lifetime = 6.4 * u.h
 
 offset = [1] * u.deg
 
-#data_store = DataStore.from_dir("../data/input/cta-1dc/index/gps")
-#obs_cta = data_store.obs(110380)
 cta_north = ("../data/cta-caldb/Prod5-North-20deg-AverageAz-4LSTs09MSTs.180000s-v0.1.fits")
 cta_south = ("../data/cta-caldb/Prod5-South-20deg-AverageAz-14MSTs37SSTs.180000s-v0.1.fits")
 irf_cta_north = load_irf_dict_from_file(cta_north)

### 2023-03-21 src/ms-review.tex
Update IRF figures and text
Signed-off-by: Fabio Pintore <fabio.pintore@inaf.it>
Fix the name of Quentin
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 	Régis Terrier \inst{\ref{inst:20}} \and
-	Quentin Rémy \inst{\ref{inst:17}} \and
+	Quentin Remy \inst{\ref{inst:17}} \and
 	Atreyee Sinha \inst{\ref{inst:15}} \and

### 2023-03-21 src/ms-review.tex
Corrections after issue 115
Signed-off-by: Régis Terrier <rterrier@apc.in2p3.fr>

@@
 or King profile functions (\code{PSFKing}). The \code{EnergyDependentMultiGaussPSF}
-class is able to handle up to three
-Gaussians, defined in terms of amplitudes and sigma given for each true energy
-and offset angle bin. Similarly, \code{PSFKing} takes into account the gamma and
-sigma parameters. The general \code{ParametricPSF} class allows users to create a
+class is able to handle up to three Gaussians, defined in terms of amplitudes and sigma given for each true energy
+and offset angle bin. The general \code{ParametricPSF} class allows users to create a
 custom PSF with a parametric representation different from Gaussian(s) or King profile(s).
@@
 is typically parametrised in terms of the so-called
-migration parameter ($\mu$), which is defined as the ratio between the
-reconstructed energy and the true energy. By definition, the mean of this ratio is
-close to unity for a small energy bias and its distribution can 
+migration parameter ($\mu$, see section \label{sec:gammaray-data-analysis}).
+By definition, the mean of this ratio is close to unity for a small energy bias and its distribution can
 be typically described by a Gaussian profile. However, more complex

### 2023-03-21 src/ms-review.tex

--- 2023-03-21 src/ms-review.tex
@@
 \gammapy is currently used for a variety of analyses by different IACT
-experiments and has already been employed in more than 60 scientific publications as of XX/03/2023
+experiments and has already been employed in about 65 scientific publications as of 21/03/2023
 \footnote{\href{https://ui.adsabs.harvard.edu/search/q=(\%20(citations(doi\%3A\%2210.1051\%2F0004-6361\%2F201834938\%22)\%20OR\%20citations(bibcode\%3A2017ICRC...35..766D))\%20AND\%20year\%3A2014-2023)&sort=date\%20desc\%2C\%20bibcode\%20desc&p_=0}{List on ADS}}.

### 2023-03-21 src/ms-review.tex
Proposal for the text about time-based analysis
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

--- 2023-03-21 src/ms-review.tex
@@
 process from the DL3 to the highest DL5/DL6 data levels. \gammapy will
-also extend its functionality for time based analyses, including
-tests for variability in lightcurves and phase curves as well as
-improving the interoperabiltiy with other timing packages such
-as \textit{Stingray}~\citep{Stingray2019} and \textit{Astropy's}
-time series classes.
+also extend its functionalities for time based analyses,
+e.g. tests for variability in light curves, phase curves peak search, 
+as well as improving the interoperability with other timing packages such
+as \textit{Stingray}~\citep{Stingray2019}, \textit{Astropy's}
+time series classes or \textit{pint-pulsar}~\citep{Luo2021}
+ for high-precision pulsar timing.
 

### 2023-03-21 src/ms-review.tex
Update src/ms-review.tex

@@
 as \textit{Stingray}~\citep{Stingray2019}, \textit{Astropy's}
-time series classes or \textit{pint-pulsar}~\citep{Luo2021}
+time series classes and \textit{pint-pulsar}~\citep{Luo2021}
  for high-precision pulsar timing.

### 2023-03-21 src/ms-review.tex
add cta north, change hawc energy range, remove unused white space in psf plot
Signed-off-by: Fabio Pintore <fabio.pintore@inaf.it>

--- 2023-03-21 src/ms-review.tex
@@
 	Régis Terrier \inst{\ref{inst:20}} \and
-	Quentin Remy \inst{\ref{inst:17}} \and
+	Quentin Rémy \inst{\ref{inst:17}} \and
 	Atreyee Sinha \inst{\ref{inst:15}} \and
@@
 		the $68\%$ containment radius of the PSF as a function of energy for the \cta, \hess
-		and \fermi instruments. The \cta IRFs are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
+		and \fermi instruments. The \cta IRFs are from the \textit{prod5} production for the {\it alpha} configuration of the south and north array. The \hess IRFs are from the DL3 DR1,
         using observation ID 033787. The \magic effective area is computed for a
@@
 \gammapy is currently used for a variety of analyses by different IACT
-experiments and has already been employed in about 65 scientific publications as of 21/03/2023
+experiments and has already been employed in more than 60 scientific publications as of XX/03/2023
 \footnote{\href{https://ui.adsabs.harvard.edu/search/q=(\%20(citations(doi\%3A\%2210.1051\%2F0004-6361\%2F201834938\%22)\%20OR\%20citations(bibcode\%3A2017ICRC...35..766D))\%20AND\%20year\%3A2014-2023)&sort=date\%20desc\%2C\%20bibcode\%20desc&p_=0}{List on ADS}}.

### 2023-03-21 src/figures/irfs.py

@@ -47,12 +47,16 @@ ax_aeff.yaxis.set_units(u.Unit("m2"))
 aeff_hess = obs_hess.aeff.slice_by_idx({"energy_true": slice(42, None)})
 aeff_hess.plot_energy_dependence(ax=ax_aeff, offset=offset, label="H.E.S.S.", **kwargs)
 color = ax_aeff.lines[-1].get_color()
-ax_aeff.text(x=10, y=1e6, s="H.E.S.S.", color=color)
+ax_aeff.text(x=10, y=2e5, s="H.E.S.S.", color=color)
 
 # CTA
-irf_cta_south["aeff"].plot_energy_dependence(ax=ax_aeff, offset=offset, label="CTA", **kwargs)
+irf_cta_north["aeff"].plot_energy_dependence(ax=ax_aeff, offset=offset, label="CTA North", **kwargs)
 color = ax_aeff.lines[-1].get_color()
-ax_aeff.text(x=0.06, y=3e5, s="CTAO", color=color)
+ax_aeff.text(x=0.01, y=3e5, s="CTAO South", color=color)
+
+irf_cta_south["aeff"].plot_energy_dependence(ax=ax_aeff, offset=offset, label="CTA South", **kwargs)
+color = ax_aeff.lines[-1].get_color()
+ax_aeff.text(x=0.5, y=3e6, s="CTAO North", color=color)
 
 # Fermi-LAT
 exposure_fermi = Map.read(
@@ -80,15 +84,15 @@ for nhit_bin in range(5, 10):
     aeff_hawc = aeff_hawc_map.to_region_nd_map(func=np.mean) / hawc_lifetime
     data = aeff_hawc.quantity[:, 0, 0]
 
-    energy = aeff_hawc.geom.axes["energy_true"].center
-    ax_aeff.plot(energy, data, alpha=0.2, color="k")
+    energy = aeff_hawc.geom.axes["energy_true"].center[:-30]
+    ax_aeff.plot(energy, data[:-30], alpha=0.2, color="k")
     aeff_hawc_max.append(data)
 
 aeff_hawc_max = np.stack(aeff_hawc_max).sum(axis=0)
 
 ax_aeff.plot(
-    aeff_hawc.geom.axes["energy_true"].center,
-    aeff_hawc_max,
+    aeff_hawc.geom.axes["energy_true"].center[:-26],
+    aeff_hawc_max[:-26],
     color="k",
     **kwargs,
[…]

### 2023-03-21 src/figures/irfs.py
fix bug
Signed-off-by: Fabio Pintore <fabio.pintore@inaf.it>

@@ -52,11 +52,11 @@ ax_aeff.text(x=10, y=2e5, s="H.E.S.S.", color=color)
 # CTA
 irf_cta_north["aeff"].plot_energy_dependence(ax=ax_aeff, offset=offset, label="CTA North", **kwargs)
 color = ax_aeff.lines[-1].get_color()
-ax_aeff.text(x=0.01, y=3e5, s="CTAO South", color=color)
+ax_aeff.text(x=0.01, y=3e5, s="CTAO North", color=color)
 
 irf_cta_south["aeff"].plot_energy_dependence(ax=ax_aeff, offset=offset, label="CTA South", **kwargs)
 color = ax_aeff.lines[-1].get_color()
-ax_aeff.text(x=0.5, y=3e6, s="CTAO North", color=color)
+ax_aeff.text(x=0.5, y=3e6, s="CTAO South", color=color)
 
 # Fermi-LAT
 exposure_fermi = Map.read(

### 2023-03-21 src/ms-review.tex
add magic ex
Signed-off-by: Atreyee Sinha <asinha@ucm.es>

@@
 %% Context: development of open software
-In the past decade observing the \gammaray sky has transitioned from a niche in the field of
+In the past decade, observing the \gammaray sky has transitioned from a niche in the field of
 particle physics to an established branch of astronomy, completing the view of the
@@
 analysed using a common software library.
-The \gammapy package is an independent community-developed software project, it has been selected to be the core library for the Science Analysis tools of CTAO
+The \gammapy package is an independent community-developed software project. It has been selected to be the core library for the Science Analysis tools of CTAO
 but also involves contributors associated to other instruments.
@@
 
-%% CN: what about mentioning the joint Crab? or is it mentioned later?
+They consist of two
+observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
+the performance of the upgraded stereo system~\citep{magic_performance} and
+already included in~\cite{joint_crab}.
+
 With the public availability of the \gadf format specifications and the
@@
 as a basis for validation of open analysis tools, including \gammapy 
-\cite[see e.g.][]{Mohrmann2019}. The \hawc collaboration also released
+\cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have been
+ released by the \magic collaboration~\citep{magic_performance}, using which a
+joint analysis across different gamma-ray instruments was first demonstrated in ~\cite{joint_crab}.
+The \hawc collaboration also released
 a limited test dataset of the Crab Nebula, which was used to validate

### 2023-03-21 src/ms-review.tex
further corrections after issue 115
Signed-off-by: Régis Terrier <rterrier@apc.in2p3.fr>

--- 2023-03-21 src/ms-review.tex
@@
   reconstruct the photon at energy $E$ when the true energy is $E_{\rm true}$ and the true position $p_{\rm true}$.
-  \gammaray instruments consider $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$, the probability density of the event migration, $\mu=\frac{E}{E_{\rm true}}$.
+  \gammaray instruments consider $E_{\rm disp}(\mu|p_{\rm true}, E_{\rm true})$, the probability density of the event
+  migration, $\mu=\frac{E}{E_{\rm true}}$.
 \end{itemize}
@@
 		the $68\%$ containment radius of the PSF as a function of energy for the \cta, \hess
-		and \fermi instruments. The \cta IRFs are from the \textit{prod5} production for the {\it alpha} configuration of the south and north array. The \hess IRFs are from the DL3 DR1,
+		and \fermi instruments. The \cta IRFs are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
         using observation ID 033787. The \magic effective area is computed for a
@@
 The \code{gammapy.irf} sub-package contains all classes and functionalities
-to handle IRFs in a variety of formats.
+to handle IRFs in a variety of functional forms.
 Usually, \irfs store instrument properties in the form of multi-dimensional
@@
 is typically parametrised in terms of the so-called
-migration parameter ($\mu$), which is defined as the ratio between the
-reconstructed energy and the true energy. By definition, the mean of this ratio is
-close to unity for a small energy bias and its distribution can 
-be typically described by a Gaussian profile. However, more complex
-shapes are also common. The migration parameter is given at each offset angle and
-reconstructed energy. The main sub-classes are the \code{EnergyDispersion2D} which is
+migration parameter ($\mu$, see section \label{sec:gammaray-data-analysis}).
+ However, more complex
+shapes are also common. The distribution of the migration parameter is given at each offset angle and
+true energy. The main sub-classes are the \code{EnergyDispersion2D} which is
 designed to handle the raw instrument description, and the \code{EDispKernelMap},
-which contains an energy disperion matrix per sky position. I.e., a 4-dimensional
+which contains an energy disperion matrix per sky position, i.e., a 4-dimensional
 sky map where each position is associated to an energy dispersion matrix.

### 2023-03-21 src/ms-review.tex

--- 2023-03-21 src/ms-review.tex
@@
 process from the DL3 to the highest DL5/DL6 data levels. \gammapy will
-also extend its functionality for time based analyses, including
-tests for variability in lightcurves and phase curves as well as
-improving the interoperabiltiy with other timing packages such
-as \textit{Stingray}~\citep{Stingray2019} and \textit{Astropy's}
-time series classes.
+also extend its functionalities for time based analyses,
+e.g. tests for variability in light curves, phase curves peak search, 
+as well as improving the interoperability with other timing packages such
+as \textit{Stingray}~\citep{Stingray2019}, \textit{Astropy's}
+time series classes and \textit{pint-pulsar}~\citep{Luo2021}
+ for high-precision pulsar timing.
 

### 2023-03-21 src/ms-review.tex
Add some more context to the introduction

@@
 %% \gammaray astronomy
-%% CN: I think we should use the expression Water Cherenkov Detectors and use the
-%% abbreviation (WCD) all along the text, later we use "particle samplers"
-The \gammaray range of the electromagnetic spectrum provides us insights into the
-most energetic processes in the universe such as those accelerating particles in the surroundings of
-black holes, and remnants of supernova explosions. As in other
-branches of astronomy, \gammarays can be observed by
-satellite as well as ground-based instruments.
-Ground-based instruments use the Earth's atmosphere as a particle detector.
+In modern astronomy astrophysical objects are studied across
+all wavelenghts. The \gammaray range of the electromagnetic spectrum 
+provides us insights into the most energetic processes in the universe such as
+those accelerating particles in the surroundings of black holes or remnants of
+supernova explosions.
+
+As in other branches of astronomy, \gammarays can be observed by satellite as
+well as ground-based instruments.
+Space based instruments such as the Fermi Large Area Telescope (LAT)
+rely on the pair-conversion effect to detect \gammarays and track
+the positron-electron pairs created in the detector to reconstruct the incident direction 
+of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
+at the bottom of the instrument. The energy range of \fermi ranges from
+\SI{20}{MeV} to \SI{300}{GeV}.
+
+Ground-based instruments use the Earth's atmosphere as a particle detector instead.
 Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and
@@
 %% Context
-Ground-based \gammaray astronomy has been historically conducted
-through experiments operated by independent collaborations, each relying
+While \fermi data as well as analysis tools have been public from the
+beginning, ground-based \gammaray astronomy has been historically conducted
+through experiments operated by independent collaborations. Each relying
 on their own proprietary data and analysis software developed as part of the
-instrument. While this model has been successful so far, it does not
-permit easy combination of data from several instruments and therefore
-limits the interoperability of existing facilities. This lack of
+instrument. While the latter model has still been successful so far, it does not
+permit easy combination of data from several instruments. This lack of
 interoperability currently limits the full exploitation of the
@@
 %TODO: better transition into context
-The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based \gammaray instrument to be operated as an open observatory.
+The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based
+\gammaray instrument to be operated as an open observatory.
 Its high-level data\footnote{The lowest reduction level of data published by CTAO will be reconstructed event lists and corresponding instrument response functions.} will be shared publicly after
@@
 by the CTA community \gammapy has already
-been used for analysis of data from the \hess, \magic, \astri and \veritas instruments.
+been used for analysis of data from the \hess, \magic, \astri \citep[e.g.][]{Vercellone2022} and \veritas instruments.
 

### 2023-03-22 src/ms-review.tex
Remianing typo
Signed-off-by: Régis Terrier <rterrier@apc.in2p3.fr>

--- 2023-03-21 src/ms-review.tex
@@
 which are contained in \code{gammapy.estimators}, are used to
-compute higher level science products such as flux and signficance maps,
+compute higher level science products such as flux and significance maps,
 light curves or flux points. Finally there is a \code{gammapy.analysis}
@@
 designed to handle the raw instrument description, and the \code{EDispKernelMap},
-which contains an energy disperion matrix per sky position, i.e., a 4-dimensional
+which contains an energy dispersion matrix per sky position, i.e., a 4-dimensional
 sky map where each position is associated to an energy dispersion matrix.
@@
 The background rate is stored as a differential count rate, normalised per solid angle
-and energy interval at different reconstructed energies and offset angles.
+and energy interval at different reconstructed energies and position in the FoV.
 In the \code{Background2D} case, the background is expected to follow a radially symmetric shape

### 2023-03-22 src/ms-review.tex
Remove forward references in section 2.1
Signed-off-by: Régis Terrier <rterrier@apc.in2p3.fr>

@@
 based on their metadata including information such as pointing direction, observation
-time and observation conditions. The access to the events data and instrument 
-reponse per observation is supported by classes and methods
-in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
-(see Section~\ref{ssec:gammapy-irf}) subpackages.
+time and observation conditions.
 
@@
 a spherical projection from celestial coordinates to a pixelised image space
-or a single region on the sky. The \code{gammapy.maps} subpackage provides
-general multidimensional geometry objects and the associated data structures
-(see Section~\ref{ssec:gammapy-maps}).
+or a single region on the sky.
 
@@
  \enquote{safe} data in the spatial as well as energy dimension.
-All of these data reduction steps are performed by classes and functions
-implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).
 
@@
 maps in different energy bands.
-The modelling and fitting functionalities are implemented in the \code{gammapy.modeling},
-\code{gammapy.estimators} and \code{gammapy.stats} subpackages (see respectively
-Section~\ref{ssec:gammapy-modeling}, \ref{ssec:gammapy-estimators} and \ref{ssec:gammapy-stats}).
 

### 2023-03-22 src/ms-review.tex

--- 2023-03-21 src/ms-review.tex
@@
 %% \gammaray astronomy
-In modern astronomy astrophysical objects are studied across
-all wavelenghts. The \gammaray range of the electromagnetic spectrum 
-provides us insights into the most energetic processes in the universe such as
-those accelerating particles in the surroundings of black holes or remnants of
-supernova explosions.
-
-As in other branches of astronomy, \gammarays can be observed by satellite as
-well as ground-based instruments.
-Space based instruments such as the Fermi Large Area Telescope (LAT)
-rely on the pair-conversion effect to detect \gammarays and track
-the positron-electron pairs created in the detector to reconstruct the incident direction 
-of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
-at the bottom of the instrument. The energy range of \fermi ranges from
-\SI{20}{MeV} to \SI{300}{GeV}.
-
-Ground-based instruments use the Earth's atmosphere as a particle detector instead.
+%% CN: I think we should use the expression Water Cherenkov Detectors and use the
+%% abbreviation (WCD) all along the text, later we use "particle samplers"
+The \gammaray range of the electromagnetic spectrum provides us insights into the
+most energetic processes in the universe such as those accelerating particles in the surroundings of
+black holes, and remnants of supernova explosions. As in other
+branches of astronomy, \gammarays can be observed by
+satellite as well as ground-based instruments.
+Ground-based instruments use the Earth's atmosphere as a particle detector.
 Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and
@@
 %% Context
-While \fermi data as well as analysis tools have been public from the
-beginning, ground-based \gammaray astronomy has been historically conducted
-through experiments operated by independent collaborations. Each relying
+Ground-based \gammaray astronomy has been historically conducted
+through experiments operated by independent collaborations, each relying
 on their own proprietary data and analysis software developed as part of the
-instrument. While the latter model has still been successful so far, it does not
-permit easy combination of data from several instruments. This lack of
+instrument. While this model has been successful so far, it does not
+permit easy combination of data from several instruments and therefore
+limits the interoperability of existing facilities. This lack of
 interoperability currently limits the full exploitation of the
@@
 %TODO: better transition into context
-The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based
-\gammaray instrument to be operated as an open observatory.
+The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based \gammaray instrument to be operated as an open observatory.
 Its high-level data\footnote{The lowest reduction level of data published by CTAO will be reconstructed event lists and corresponding instrument response functions.} will be shared publicly after

### 2023-03-22 src/ms-review.tex
Remove the duplicated sentance on the MAGIC dataset
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 	Aneta Siemiginowska \inst{\ref{inst:28}} \and
-	Brigitta M {Sipőcz} \inst{\ref{inst:29}} \and
+	Brigitta M. {Sipőcz} \inst{\ref{inst:29}} \and
 	Tim Unbehaun \inst{\ref{inst:19}} \and
@@
 
-They consist of two
-observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
-the performance of the upgraded stereo system~\citep{magic_performance} and
-already included in~\cite{joint_crab}.
-
 With the public availability of the \gadf format specifications and the

### 2023-03-22 src/ms-review.tex
Fix typos
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

@@
 the \gammapy package in \cite{Olivera2022}.
-The increased availability of public data that followed the definition of
-a common data format, and the development of \gammapy as a community-driven open software,
-led the way toward a more open science in the very-high-energy \gammaray Astronomy domain.
+The increased availability of public data, that followed the definition of
+a common data format, and the development of \gammapy as a community-driven open software
+led the way toward a more open science in the very-high-energy \gammaray astronomy domain.
 In future CTAO will be an open observatory committed to follow the FAIR

### 2023-03-22 src/ms-review.tex

--- 2023-03-22 src/ms-review.tex
@@
 %% \gammaray astronomy
-%% CN: I think we should use the expression Water Cherenkov Detectors and use the
-%% abbreviation (WCD) all along the text, later we use "particle samplers"
-The \gammaray range of the electromagnetic spectrum provides us insights into the
-most energetic processes in the universe such as those accelerating particles in the surroundings of
-black holes, and remnants of supernova explosions. As in other
-branches of astronomy, \gammarays can be observed by
-satellite as well as ground-based instruments.
-Ground-based instruments use the Earth's atmosphere as a particle detector.
+In modern astronomy astrophysical objects are studied across
+all wavelengths. The \gammaray range of the electromagnetic spectrum 
+provides us insights into the most energetic processes in the universe such as
+those accelerating particles in the surroundings of black holes or remnants of
+supernova explosions.
+
+In general \gammaray astronomy relies on the detection of individual 
+photon events and reconstruction of their incident direction as well
+as energy. As in other branches of astronomy, this can be
+achieved by satellite as well as ground-based \gammaray instruments.
+Space based instruments such as the Fermi Large Area Telescope (LAT)
+rely on the pair-conversion effect to detect \gammarays and track
+the positron-electron pairs created in the detector to reconstruct the incident direction 
+of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
+at the bottom of the instrument. The energy range of \fermi ranges from
+\SI{20}{MeV} to \SI{300}{GeV}.
+
+Ground-based instruments use the Earth's atmosphere as a particle detector instead.
 Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and

### 2023-03-22 src/ms-review.tex

--- 2023-03-22 src/ms-review.tex
@@
 is typically parametrised in terms of the so-called
-migration parameter ($\mu$), which is defined as the ratio between the
-reconstructed energy and the true energy. By definition, the mean of this ratio is
-close to unity for a small energy bias and its distribution can 
-be typically described by a Gaussian profile. However, more complex
-shapes are also common. The migration parameter is given at each offset angle and
-reconstructed energy. The main sub-classes are the \code{EnergyDispersion2D} which is
+migration parameter ($\mu$, see section \label{sec:gammaray-data-analysis}).
+ However, more complex
+shapes are also common. The distribution of the migration parameter is given at each offset angle and
+true energy. The main sub-classes are the \code{EnergyDispersion2D} which is
 designed to handle the raw instrument description, and the \code{EDispKernelMap},
-which contains an energy disperion matrix per sky position. I.e., a 4-dimensional
+which contains an energy dispersion matrix per sky position, i.e., a 4-dimensional
 sky map where each position is associated to an energy dispersion matrix.

### 2023-03-22 src/ms-review.tex
Fix some references
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

--- 2023-03-22 src/ms-review.tex
@@
 		The lower left shows the group of all-sky instruments such as the
-		Fermi Large Area Telescope (Fermi-LAT) and the High Altitude
+		Fermi Large Area Telescope (\textit{Fermi}-LAT) and the High Altitude
 		Water Cherenkov Observatory (HAWC). The calibrated data of all those
@@
 light (EBL) (\code{EBLAbsorptionNormSpectralModel}). \gammapy supports a variety
-of EBL absorption models, such as those from \cite{Franceschini2008}, \cite{Finke2010},
+of EBL absorption models, such as those from \cite{Franceschini2008, Franceschini2017}, \cite{Finke2010},
 and \cite{Dominguez2011}.
@@
 user-defined models. For example, the radiative models of jetted Active Galactic Nuclei (AGN)
-implemented in \agnpy, can be wrapped into \gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}.
+implemented in \agnpy~\citep{agnpy2022}, can be wrapped into 
+\gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}.
 
@@
 the \gammaray emission, given a physical scenario. Among those
-packages are Agnpy~\citep{agnpy}, Naima~\citep{naima}, Jetset~\citep{jetset}
+packages are Agnpy~\citep{agnpy2022}, Naima~\citep{naima}, Jetset~\citep{jetset}
 and Gamera~\citep{gamera}.
@@
 simulations, we jump from 78 sources detected by \hess to about 500 detectable by
-CTA~\citep{2021arXiv210903729R}. This large increase in the amount of data to analyse
+CTA~\citep{Remy2021}. This large increase in the amount of data to analyse
 and increase in complexity of modelling scenarios, requires the high-level

### 2023-03-23 src/ms-review.tex
Small typo
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>
final review between submission

@@
 		such as the Cherenkov Telescope Array Observatory (CTAO), will be operated as open observatories.
-		Alongside the data, they will also make associated software tools available to a wider community.
-    This necessity prompted the development of open, high-level astronomy software customised for high-energy astrophysics.
+		Alongside the data, they will also make the associated software tools available to a wider community.
+    This necessity prompted the development of open, high-level, astronomical software customised for high-energy astrophysics.
 	}
@@
 		Starting from event lists and instrument response functions,
-		\gammapy provides the functionalities for reducing data binned in energy and sky coordinates.
-		Several techniques for background estimation are implemented in the package to handle the residual hadronic background.
+		\gammapy provides functionalities to reduce these data by binning them in energy and sky coordinates.
+		Several techniques for background estimation are implemented in the package to handle the residual hadronic background affecting \gammaray instruments.
 		After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
@@
 	{
-		After describing the structure of the package, we show the capabilities of \gammapy
-		in multiple traditional and novel \gammaray analysis scenarios using public data, 
-		such as spectral and spectro-morphological modelling and estimations of a spectral energy
+		After describing the structure of the package, we show, using publicly-available gamma-ray data,
+		the capabilities of \gammapy in multiple traditional and novel \gammaray analysis scenarios
+		such as: spectral and spectro-morphological modelling and estimations of a spectral energy
 		distribution and a light curve.
@@
 %% \gammaray astronomy
-In modern astronomy astrophysical objects are studied across
+Modern astronomy is defined by the possibility to observe and study astrophysical sources across
 all wavelengths. The \gammaray range of the electromagnetic spectrum 
-provides us insights into the most energetic processes in the universe such as
+provides us with insights into the most energetic processes in the universe such as
 those accelerating particles in the surroundings of black holes or remnants of
@@
 
-In general \gammaray astronomy relies on the detection of individual 
+In general, \gammaray astronomy relies on the detection of individual 
 photon events and reconstruction of their incident direction as well
@@
 achieved by satellite as well as ground-based \gammaray instruments.
-Space based instruments such as the Fermi Large Area Telescope (LAT)
+Space-borne instruments such as the Fermi Large Area Telescope (LAT)
 rely on the pair-conversion effect to detect \gammarays and track
@@
 of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
-at the bottom of the instrument. The energy range of \fermi ranges from
-\SI{20}{MeV} to \SI{300}{GeV}.
-
-Ground-based instruments use the Earth's atmosphere as a particle detector instead.
-Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and
-create large showers of secondary particles that can be observed from the ground.
-Ground-based \gammaray astronomy relies on these extensive air showers to detect the
-primary \gammaray photons and infer their incident direction and energy.
-VHE \gammaray astronomy covers the energy range from few tens of \si{GeV} up to the \si{PeV}.
-There are two main categories of ground-based instruments:
+at the bottom of the instrument. The energy range of instruments like \fermi, referred to as
+high-energy (HE), goes approximately from tens of \si{MeV} to hundreds of \si{GeV}.
+
+Ground-based instruments, instead, use the Earth's atmosphere as a particle detector, relying on the fact that
+cosmic \gammarays interacting in the atmosphere create large showers of secondary particles that can be observed from the ground.
+Ground-based \gammaray astronomy relies on these extensive air showers to estimate the
+primary \gammaray photons incident direction and energy.
+These instruments operate in the so-called very-high-energy (VHE) regime,
+covering the energy range from few tens of \si{GeV} up to the \si{PeV}.
+There are two main categories of ground-based instruments.
 
@@
 		Water Cherenkov Observatory (HAWC). The calibrated data of all those
-		instruments can be converted and stored into the common GADF data format.
-		\gammapy can read data stored in the GADF format.
+		instruments can be converted and stored into the common GADF data format, that \gammapy can read.
 		The \gammapy package is a community-developed project that
 		provides a common interface to the data and analysis of all
-		these \gammaray instruments. This way users can also easily combine data from
-		different instruments and perform a joint analysis.
+		these \gammaray instruments, allowing users to easily combine data from
+		different instruments and perform joint analyses.
 		\gammapy is built on the scientific Python ecosystem, and the required dependencies
@@
 %% Context
-While \fermi data as well as analysis tools have been public from the
+%% CN: I think Fermi-LAT data were available from the 2nd year on
+%% https://fermi.gsfc.nasa.gov/ssc/data/policy/
+While \fermi data and analysis tools have been public from the
 beginning, ground-based \gammaray astronomy has been historically conducted
-through experiments operated by independent collaborations. Each relying
+through experiments operated by independent collaborations, each relying
 on their own proprietary data and analysis software developed as part of the
-instrument. While the latter model has still been successful so far, it does not
+instrument. While this model has been so far successful, it does not
 permit easy combination of data from several instruments. This lack of
 interoperability currently limits the full exploitation of the
-available \gammaray data, especially because the different instruments often have
+available \gammaray data, especially in light of the fact that different instruments often have
 complementary sky coverages, and the various detection
@@
 %TODO: better transition into context
+% CN: last-minute transition improvement
 The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based
 \gammaray instrument to be operated as an open observatory.
-Its high-level data\footnote{The lowest reduction level of data published by CTAO will be reconstructed event lists and corresponding instrument response functions.} will be shared publicly after
-some proprietary period, and the software required to analyze it will be distributed
-as well. To allow the re-usability of data from existing instruments and their interoperability,
-it is required to use open data formats and open tools that can support the various analysis methods
-commonly used in the field.
+Its high-level data\footnote{The lowest reduction level of data published by CTAO will be reconstructed event lists and corresponding instrument response functions.}
+will be shared publicly after some proprietary period, along with the software required to analyze them.
+The adoption of an open and standardised \gammaray data format, beside being a necesity for future observatories such as \cta,
+will be greatly beneficial to the current generation of instruments, eventually allowing to exploit their data legacies even
+beyond the end of their scientific operations.
 
 %% Context : formats
-In practice, the data reduction workflow of all \gammaray observatories
-is remarkably similar. After data calibration, shower events are reconstructed and
-gamma/hadron separation is applied to build lists of \gammaray-like events.
-The lists of \gammaray events are then used to derive scientific results, such as spectra, sky maps
-or light curves, taking into account the observation specific instrument response functions (IRFs).
+The usage of a common data format is facilitated by the remarkable similarity of the data reduction workflow of all \gammaray telescopes.
+After data calibration, shower events are reconstructed and
+a gamma / hadron separation is applied to reject cosmic-ray-intiated showers and build lists of \gammaray-like events.
+The latter can then be used, taking into account the observation-specific instrument response functions (IRFs),
+to derive scientific results, such as spectra, sky maps or light curves.
 Once the data is reduced to a list of events with reconstructed physical properties of the primary particle,
@@
 initiative~\citep{gadf_proc,gadf_universe}, abbreviated to
-\texttt{gamma-astro-data-formats} (\gadf). This proposes prototypical
+\texttt{gamma-astro-data-formats} (\gadf). This community-driven intitiative proposes prototypical
 specifications to produce files based on the flexible image transport system
@@
 %% Context: development of open software
+%% CN: I don't see the parallel between gamma-ray astronomy establishing itself and the success of python
+%% maybe this was the introduction of the very first draft?
+%% I would just write: "In the past decade, \textit{Python} has become..."
 In the past decade, observing the \gammaray sky has transitioned from a niche in the field of
@@
 
-In the sub-field of astronomy, the \astropy project \citep{astropy} was created in 2012
+%% CN: astronomy alone not a sub-field
+In the sub-field of computational astronomy, the \astropy project \citep{astropy} was created in 2012
 to build a community-developed core Python package for astronomy.
@@
 The \gammapy project was started following the model of \astropy, with the objective of building a common
-software library for very high-energy \gammaray data analysis \citep{gammapy_2015}. 
+software library for \gammaray data analysis \citep{gammapy_2015}. 
 The core of the idea is illustrated in Figure~\ref{fig:big_picture}. The various \gammaray instruments
-can export their data to a common data format (\gadf) and then these data can be combined and
-analysed using a common software library.
-The \gammapy package is an independent community-developed software project. It has been selected to be the core library for the Science Analysis tools of CTAO
+can export their data to a common format (\gadf) and then combine and analyse
+them using a common software library.
+The \gammapy package is an independent community-developed software project.
+It has been selected to be the core library for the Science Analysis tools of \cta,
 but also involves contributors associated to other instruments.
@@
 and \matplotlib~\citep{matplotlib} for visualization.
+
+%% CN: what's this??? Out of place here! %%%%
+%They consist of two
+%observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
+%the performance of the upgraded stereo system~\citep{magic_performance} and
+%already included in~\cite{joint_crab}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have been
+%% CN: what about VERITAS and FACT?
  released by the \magic collaboration~\citep{magic_performance}, using which a
@@
 the \gammapy package in \cite{Olivera2022}.
-The increased availability of public data, that followed the definition of
-a common data format, and the development of \gammapy as a community-driven open software
+%% CN: I would remark this also demonstrated Gammapy could be applied to WCD
+%% depite having been designed for IACTs initially
+The increased availability of public data that followed the definition of
+a common data format, and the development of \gammapy as a community-driven open software,
 led the way toward a more open science in the very-high-energy \gammaray astronomy domain.
-In future CTAO will be an open observatory committed to follow the FAIR
+The adoption of \gammapy as science tools strengthens the commitment of the future \cta Observatory to the FAIR principles
 (Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} 
@@
 In this article, we describe the general structure of the \gammapy package,
-its main concepts and organisational structure. We start in
+its main concepts, and organisational structure. We start in
 Section~\ref{sec:gammaray-data-analysis} with a general overview
@@
 An important part of \gammapy's development organisation is the support
-for \textit{Proposals for improving \gammapy}(PIG). This system is very much
+for \textit{Proposals for improving \gammapy} (PIG). This system is very much
 inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}

### 2023-03-23 src/ms-review.tex
Update src/ms-review.tex

--- 2023-03-23 src/ms-review.tex
@@
 		After describing the structure of the package, we show, using publicly-available gamma-ray data,
-		the capabilities of \gammapy in multiple traditional and novel \gammaray analysis scenarios
-		such as: spectral and spectro-morphological modelling and estimations of a spectral energy
+		the capabilities of \gammapy in multiple traditional and novel \gammaray analysis scenarios,
+		such as spectral and spectro-morphological modelling and estimations of a spectral energy
 		distribution and a light curve.
@@
 %% \gammaray astronomy
-Modern astronomy is defined by the possibility to observe and study astrophysical sources across
+Modern astronomy offers the possibility to observe and study astrophysical sources across
 all wavelengths. The \gammaray range of the electromagnetic spectrum 

### 2023-03-23 src/ms-review.tex
Update src/ms-review.tex

@@
 \gammaray instrument to be operated as an open observatory.
-Its high-level data\footnote{The lowest reduction level of data published by CTAO will be reconstructed event lists and corresponding instrument response functions.}
+Its high-level data\footnote{The lowest reduction level of data published by \cta will be reconstructed event lists and corresponding instrument response functions.}
 will be shared publicly after some proprietary period, along with the software required to analyze them.

### 2023-03-23 src/ms-review.tex
Add complete data reference for joint crab

@@
 as a basis for validation of open analysis tools, including \gammapy 
-\cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have been
-%% CN: what about VERITAS and FACT?
- released by the \magic collaboration~\citep{magic_performance}, using which a
-joint analysis across different gamma-ray instruments was first demonstrated in ~\cite{joint_crab}.
-The \hawc collaboration also released
-a limited test dataset of the Crab Nebula, which was used to validate
-the \gammapy package in \cite{Olivera2022}.
+\cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have
+been released by the \magic collaboration~\citep{magic_performance}.
+Using these public data from \fermi, \hess, \magic and additional observations
+provided by FACT and \veritas, the authors of \cite{joint_crab} presented
+a combined analysis of \gammaray data from different instruments for the first time.
+Later the \hawc collaboration also released a limited test dataset of the Crab Nebula,
+which was used to validate the \gammapy package in \cite{Olivera2022}.
 %% CN: I would remark this also demonstrated Gammapy could be applied to WCD

### 2023-03-23 src/ms-review.tex

@@
 %% I would just write: "In the past decade, \textit{Python} has become..."
-In the past decade, observing the \gammaray sky has transitioned from a niche in the field of
-particle physics to an established branch of astronomy, completing the view of the
-sky in high energies. At the same time \textit{Python}
-has become extremely popular as a scientific programming language,
+In the past decade \textit{Python} has become extremely popular as a scientific programming language,
 in particular in the field of data sciences. This success is

### 2023-05-22 src/ms-review.tex
Remove line numbers
Change place of definition of DL3 acronym

@@
 \usepackage[switch]{lineno}
-\linenumbers
 
@@
 dataset (about 50 hours of observations taken between 2004 and 2008)
-based on the \gadf DL3 format \citep{HESS_DR1}. This data release served
-as a basis for validation of open analysis tools, including \gammapy 
+based on the \gadf format \citep{HESS_DR1} for data level 3 (DL3) \gammaray data.
+This data release served as a basis for validation of open analysis tools, including \gammapy 
 \cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have
@@
 
-%% CN: except for the figures we never introduced what the DL3 or the Data Level acronym is
-%% maybe add (see Fig.~1)
-\gammaray data at the Data Level 3 (DL3) therefore consist of lists of \gammaray-like events and their
+DL3 \gammaray data at therefore consist of lists of \gammaray-like events and their
 corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),

### 2023-05-22 src/ms-review.tex
Add Fermi-LAT and HEALPix references

@@
 of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
-at the bottom of the instrument. The energy range of instruments like \fermi, referred to as
+at the bottom of the instrument. The energy range of instruments like \fermi \citep{Atwood2009}, referred to as
 high-energy (HE), goes approximately from tens of \si{MeV} to hundreds of \si{GeV}.
@@
 While \fermi data and analysis tools have been public from the
-beginning, ground-based \gammaray astronomy has been historically conducted
+beginning \citep{}, ground-based \gammaray astronomy has been historically conducted
 through experiments operated by independent collaborations, each relying
@@
 \subsubsection{HEALPix Maps}
-This pixelization scheme ~\citep{Calabretta2002} provides a
+This pixelization scheme ~\citep{Calabretta2002, Gorski2005} provides a
 subdivision of a sphere in which each pixel covers the same surface area as

### 2023-05-22 src/ms-review.tex
Rephrase description of observation duration

@@
 supports data that is compliant with \code{v0.2} and \code{v0.3} of the \gadf data format.
-DL3 data are typically bundled into individual observations, corresponding to stable periods of data acquisition. For IACT data analysis,
-for which the GADF data model and \gammapy were initially conceived,
-these are usually $20 - 30\,{\rm min}$ long.
-Each observation is assigned a unique integer ID for reference.
+DL3 data are typically bundled into individual observations, corresponding to
+stable periods of data acquisition. For IACT instrumeents, for which the \gadf
+data model and \gammapy were initially conceived, this duration is typically 
+$20 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
 
@@
 independent of the underlying pixelisation scheme. The \code{gammapy.maps}
-package is also used by external packages such as \textit{FermiPy}~\citep{Wood2017}
+package is also used by external packages such as \textit{FermiPy}~\citep{Wood2017}.
 

### 2023-05-22 src/ms-review.tex
Clarify 1DC acronym

@@
 DL3 data are typically bundled into individual observations, corresponding to
-stable periods of data acquisition. For IACT instrumeents, for which the \gadf
+stable periods of data acquisition. For IACT instruments, for which the \gadf
 data model and \gammapy were initially conceived, this duration is typically 
@@
 		Example of a one dimensional spectral analysis of the Galactic Center for three simulated CTA
-		observations from the 1DC dataset. The left image shows the maps of counts with the signal
+		observations from the first CTA data challenge dataset. The left image shows the maps of counts with the signal
 		region in white and the reflected background regions for the three different observations

### 2023-05-22 src/ms-review.tex
Remove statement on the independence of gammapy.catalog

@@
 class, which has the responsibility to translate the information
-contained in the catalog to other \gammapy objects. This includes
+contained in the catalog to \gammapy objects. This includes
 the spatial and spectral models of the source, flux points and
-light curves (if available) for each individual object. Figure ~\ref{fig*:minted:gp_catalogs}
+light curves (if available) for each individual object. 
+Figure ~\ref{fig*:minted:gp_catalogs}
 show how to load a given catalog and access these information for a selected source.
-This module works independently from the rest of the package, and the required
-catalogs are supplied in the \code{GAMMAPY\_DATA} repository.
+The required catalogs are supplied in the \code{GAMMAPY\_DATA} repository, such that 
+user do not have to download them separately.
 The overview of currently supported catalogs, the corresponding
@@
 	\caption{
-		Example of a one dimensional spectral analysis of the Galactic Center for three simulated CTA
-		observations from the first CTA data challenge dataset. The left image shows the maps of counts with the signal
+		Example of a one dimensional spectral analysis of the Galactic Center for three simulated
+		observations from the first CTA data challenge. The left image shows the maps of counts with the signal
 		region in white and the reflected background regions for the three different observations

### 2023-05-22 src/code-examples/snippets/gp_models.py
Add EBL example to Fig 9

@@ -1,8 +1,10 @@
+from astropy import units as u
 from gammapy.modeling.models import (
-    SkyModel,
-    PowerLawSpectralModel,
-    PointSpatialModel,
     ConstantTemporalModel,
+    EBLAbsorptionNormSpectralModel,
+    PointSpatialModel,
+    PowerLawSpectralModel,
+    SkyModel,
 )
 
 # define a spectral model
@@ -17,6 +19,7 @@ point = PointSpatialModel(
     frame="galactic"
 )
 
+
 # define a temporal model
 constant = ConstantTemporalModel()
 
@@ -28,3 +31,10 @@ model = SkyModel(
     name="my-model",
 )
 print(model)
+
+ebl = EBLAbsorptionNormSpectralModel.read_builtin(
+    reference="dominguez", redshift=0.5
+)
+
+absorbed = pwl * ebl
+absorbed.plot(energy_bounds=(0.1, 100) * u.TeV)

### 2023-05-24 src/ms-review.tex
Add link to model gallery
Add link to custom model examples

@@
 
-%% CN: a link to the model gallery?
-The model gallery provides a visual overview of the available models in
+The model gallery\footnote[number]{\url{https://docs.gammapy.org/1.0/user-guide/model-gallery/index.html}}
+ provides a visual overview of the available models in
 \gammapy. Most of the analytic models commonly used in \gammaray astronomy are
 built-in. We also offer a wrapper to radiative models implemented in the Naima
-package~\citep{naima}. The modelling framework can be easily extended with
+package~\citep{naima}. The modeling framework can be easily extended with
 user-defined models. For example, the radiative models of jetted Active Galactic Nuclei (AGN)
 implemented in \agnpy~\citep{agnpy2022}, can be wrapped into 
-\gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}.
-
-%% CN: here again, print() without output. Is it useful?
+\gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}. We provide 
+more examples of user-defined models, such as a parametric model for energy dependent morphology,
+in the online documentation\footnote[number]{\url{https://docs.gammapy.org/1.0/tutorials/api/models.html#implementing-a-custom-model}}.
+
 \begin{figure}

### 2023-05-24 src/ms-review.tex
Add run times of the examples

@@
 and fitted using the \code{Fit} class. Based on this best-fit model, the final flux points and corresponding
-log-likelihood profiles were computed using the \code{FluxPointsEstimator}.
+log-likelihood profiles were computed using the \code{FluxPointsEstimator}. The
+example takes $<10$ seconds to run on a standard laptop with M1 arm64 CPU.
 
@@
 contribution from each of the three source models. The result can be seen in the right
-panel of Figure~\ref{fig:cube_analysis}.
-
-Note that all the models fitted also have a spectral component, from which flux
-points can be derived in a similar way as described in Section~\ref{ssec:1d-analysis}.
+panel of Figure~\ref{fig:cube_analysis}. Note that all the models fitted also have a
+spectral component, from which flux points can be derived in a similar way as described
+in Section~\ref{ssec:1d-analysis}. The whole example takes $<2$ minutes to run on a standard
+laptop with M1 arm64 CPU.
 %\end{figure*}%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?%
@@
 variability, to each dataset, a joint fit across the datasets will directly
-return the best fit temporal and spectral parameters.
+return the best fit temporal and spectral parameters. The light curve data reduction
+and computation of flux points takes about $0.5$ minutes to run on a standard laptop with M1 arm64 CPU.
 
@@
 reduction, without aiming to provide a new measurement of the Crab Nebula
-spectrum.
+spectrum. The spectral fit takes $<10$ seconds to run on a standard laptop with M1 arm64 CPU.
 
@@
 The best-fit inverse Compton spectrum is represented with a red dashed line in
-Figure~\ref{fig:multi_instrument_analysis}.
+Figure~\ref{fig:multi_instrument_analysis}. The fit of the astrophysical model
+takes $<5$ minutes to run on a standard laptop with M1 arm64 CPU.
 

### 2023-05-24 src/data/lightcurve/make.py

@@ -1,4 +1,5 @@
 import logging
+import time
 from pathlib import Path
 
 import astropy.units as u
@@ -106,6 +107,7 @@ def light_curve(datasets, time_intervals, sky_model):
 
 
 if __name__ == "__main__":
+    t_start = time.time()
     path = Path(".")
     filename = path / "pks2155_flare_lc.fits.gz"
 
@@ -116,3 +118,8 @@ if __name__ == "__main__":
     lc = light_curve(datasets, time_intervals, sky_model)
     log.info(f"Writing {filename}")
     lc.write(filename, format="lightcurve", overwrite=True)
+
+    t_stop = time.time()
+
+    with (path / "../run-times.csv").open("a") as fh:
+        fh.write(f"lightcurve-example: {t_stop - t_start}\n")

### 2023-05-24 src/data/multi-instrument/make.py

@@ -1,5 +1,6 @@
 # reduce the MAGIC data to OGIP files for the 1D analysis
 import logging
+import time
 from pathlib import Path
 
 import astropy.units as u
@@ -128,7 +129,6 @@ def reduce_magic_data():
     datasets = Datasets()
 
     for obs in observations:
-
         # fill the ON counts
         dataset = dataset_maker.run(dataset_empty.copy(name=f"{obs.obs_id}"), obs)
         # fill the OFF counts and set the energy range appropiate for the fit
@@ -180,6 +180,7 @@ def fit_joint_dataset(datasets, models, filename):
 
 if __name__ == "__main__":
     # load the three instruments datasets
+    t_start = time.time()
     fermi_dataset = load_fermi_datasets()
     magic_datasets = reduce_magic_data()
     hawc_dataset = load_hawc_flux_points()
@@ -237,6 +238,12 @@ if __name__ == "__main__":
         "crab-nebula-spectrum-only",
     )
 
+    t_stop = time.time()
+
+    path = Path(".")
+    with (path / "../run-times.csv").open("a") as fh:
+        fh.write(f"multi-istrument-example: {t_stop - t_start}\n")
+
     # fit with the naima IC model
     naima_ic_spectral_model = CrabInverseComptonSpectralModel(
         amplitude=1e32 / u.eV, alpha=2.1, e_0=100 * u.GeV, beta=0.1
@@ -250,3 +257,9 @@ if __name__ == "__main__":
     fit_joint_dataset(
         datasets, models, "results/crab_multi_instrument_fit_naima_ic_model.yaml"
     )
+
+    t_stop = time.time()
+
+    path = Path(".")
+    with (path / "../run-times.csv").open("a") as fh:
+        fh.write(f"multi-istrument-naima-example: {t_stop - t_start}\n")

### 2023-05-24 src/ms-review.tex
Add links to detailed broadband SED fitting examples

@@
 
+More examples for modelling the broadband emission of \gammaray sources, which 
+partly involve \gammpy are available in the online documentation of the
+Agnpy, Naima, Jetset and Gamera packages\footnote{\url{https://agnpy.readthedocs.io/en/latest/tutorials/ssc_gammapy_fit.html}},
+\footnote{\url{https://naima.readthedocs.io/en/stable/tutorial.html}}, 
+\footnote{\url{https://jetset.readthedocs.io/en/stable/user_guide/documentation_notebooks/gammapy_plugin/gammapy_plugin.html}},
+\footnote{\url{http://libgamera.github.io/GAMERA/docs/fitting_data.html}}.
+
 \subsection{Surveys, Catalogs, and Population Studies}

### 2023-05-24 src/ms-review.tex
Partial rewrite of Section 4.6

@@
 \label{ssec:surveys-catalogs-and-population-studies}
-
-Sky surveys have a large potential for new source detections, and discovery of new phenomena
- in \gammaray astronomy. They also offer less selection bias to perform
-source population studies over a large set of coherently detected and modelled objects.
+As a last application example we describe the use of \gammapy for large scale
+analyses such as \gammaray surveys, catalogs and population studies.
 Early versions of \gammapy were developed in parallel to the preparation of
 the \hess Galactic plane survey catalog~\citep[HGPS, ][]{2018A&A...612A...1H} and
-the associated PWN and SNR populations studies~\citep{2018A&A...612A...2H,
-	2018A&A...612A...3H}.
-
-The increase in sensitivity and resolution provided by the new generation of
+the associated PWN and SNR populations studies~\citep{2018A&A...612A...2H,2018A&A...612A...3H}.
+
+The increase in sensitivity and angular resolution provided by the new generation of
 instruments scales up the number of detectable sources and the complexity of 
@@
 In short, the production of catalogs from \gammaray surveys can be divided in
-four main steps: data reduction; object detection; model fitting and model
-selection; associations and classification. All steps can either be done directly
-with \gammapy or by relying on the seamless integration
-of \gammapy with the scientific Python ecosystem. This allows to rely
-on 3rd party functionality wherever needed.
-
-The \iacts data reduction step is done in the same way described in the 
-previous sections but scaled up to few thousands of observations. The object
-detection step typically consists in finding local maxima in the significance or TS maps,
-computed by the \code{ExcessMapEstimator} or \code{TSMapEstimator} respectively.
- Further refinements can
-include for example filtering and detection on these maps with techniques from
-the \textit{Scikit-image} package~\citep{scikit-image}, and outlier detection from
-the \textit{Scikit-learn} package~\citep{scikit-learn}. This allows e.g., to 
-reduce the number of spurious detections at this stage using standard
-classification algorithms and then speed up the next step,
-as less objects will have to be fitted simultaneously. During the modelling
-step each object is alternatively fitted with different models in order to
-determine their optimal parameters, and the best-candidate model. The
-subpackage \code{gammapy.modeling.models} offers a large variety of choices, and the
-possibility to add custom models.  Several spatial models (point-source, disk,
-Gaussian...), and spectral models (power law, log parabola...) may be tested
-for each object, so the complexity of the problem increases rapidly in regions
-crowded with multiple extended sources. Finally an object is discarded if its
-best-fit model is not significantly preferred over the null hypothesis (no
-source) comparing the difference in log likelihood between these two
-hypotheses.
-
-For the association and classification step, which is tightly connected to the
+four main steps: (a) data reduction, (b) object detection, (c) model fitting and model
+selection and (d) associations and classification. All steps can either be done directly
+with \gammapy or by relying on the seamless integration of \gammapy with the
+scientific Python ecosystem. This allows to rely on 3rd party functionality
+wherever needed. A simplifed catalog analysis based on \gammapy typically includes:
+
+\begin{itemize}
+	\item[a] The \iacts data reduction step is done in the same way described in the 
+	previous sections but scaled up to few thousands of observations. This step can be
+	trivially parallelised by deploying the \gammapy package on a cluster.
+	\item[b] The object detection step typically consists in finding local maxima
+	in the significance or TS maps, computed by the \code{ExcessMapEstimator} or
+	\code{TSMapEstimator} respectively. For this \gammapy provides a simple \code{find_peaks}
+	method. For more advanced methods users can rely on 3rd party packages such as
+	\textit{Scikit-image}~\citep{scikit-image}. This packages provide e.g. general
+	blob detection algorithms and image segmentation methods such as hysteresis thresholding
+	or the watershed transform. 	
+	\item[c] During the modelling step each object is alternatively fitted with different
+	models in order to determine their optimal parameters, and the best-candidate model. The
+	subpackage \code{gammapy.modeling.models} offers a large variety of choices for spatial
+	and spectral models as well as the possibility to add custom models. For the model selection
+	\gammapy provides statisticl helper methods to perform likelihood ratio tests.
+	But users can also rely on 3rd party packages such as \textit{Scikit-learn}~\citep{scikit-learn}
+	to compute quantities such as the Akaike information criterion (AIC) or the Bayesian
+	information criterion (BIC), which also allow for model selection.
+	\item[d] For the association and classification step, which is tightly connected to
 	population studies, we can easily compare the fitted models to the set of
@@
 	sources. This can easily be achieved by relying on coordinate
-handling from Astropy in combination with affiliated packages
-\textit{Astroquery}~\citep{astroquery}.
-
-Studies performed on simulations not only offer a first glimpse on what could
-be the sky seen by CTA (according to our current knowledge on source
-populations), but also give us the opportunity to test the software on complex
-use cases\footnote{Note that the CTA-GPS simulations were performed with the
-	\textit{ctools} package~\citep{2016A&A...593A...1K} and analysed with both
-	\textit{ctools} and \textit{gammapy} packages in order to cross-validate
-	them.}. In this way we can improve performance, optimize our analyse strategies, and
-identify the needs in terms of parallelisation to process the large datasets
-provided by surveys.
+	handling from Astropy in combination with affiliated packages such as
+	\textit{Astroquery}~\citep{astroquery}. For more advanced source classification
+	methods users can again rely e.g. \textit{Scikit-learn} to perform supervised
+	or unsupervised clustering.
+\end{itemize}
+
+\gammapy has been succesfully used for catalog studies performed on simulations
+of the future \cta Galactic Plane Survey~\citep{Remy2021}. Besides the scientific
+insights they also gave us the opportunity to test the \gammapy software on complex
+use cases. This resulted in a number of improvements to the \gammapy package, such as
+as improved performance, optimized analysis strategies documented to users, and
+identifying the needs for future developments, including solutions for distributed
+computing. The catalog studies of the \cta Galactic Plane Survey simulations
+also allowed for detailed cross-comparison of the results obtained with the independent
+\gammaray analysis package \textit{ctools}\citep{2016A&A...593A...1K}, with very consistent 
+results.
 

### 2023-05-25 src/ms-review.tex
Add links to online documentation, where more info is available

@@
 introduce all sub-packages and their functionalities in more detail.
+In the online documentation we also provide an overview of all
+the \gammapy sub-packages\footnote[number]{\url{https://docs.gammapy.org/1.0/user-guide/package.html}}.
 
@@
 Some example IRFs read from public data files and plotted with \gammapy are shown 
-in Figure~\ref{fig:irfs}.
+in Figure~\ref{fig:irfs}. More information on \code{gammapy.irf} can be found 
+in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/user-guide/irf/index.html#irf}}.
 
@@
 
+More information on the \code{gammapy.maps} sub-module can be found 
+in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/user-guide/maps/index.html#maps}}.
+
 \subsection{gammapy.datasets}
@@
 methods.
+
+We also refer to our online documentation for more details on \code{gammapy.datasets}
+\footnote{\url{https://docs.gammapy.org/1.0.1/user-guide/datasets/index.html#datasets}}.
 
@@
 
+More detailed information on the \code{gammapy.makers} sub-package is available online\footnote{\url{https://docs.gammapy.org/1.0/user-guide/makers/index.html#makers}}.
+
 \subsection{gammapy.stats}
@@
 
+Our online documentation provides more information on \code{gammapy.stats}
+\footnote{\url{https://docs.gammapy.org/1.0/user-guide/stats/index.html#stats}}.
+
 \subsection{gammapy.modeling}
@@
 bins of the resulting flux and TS maps.
+
+More details on the \code{gammapy.estimators} sub-module are available online \footnote{\url{https://docs.gammapy.org/1.0/user-guide/estimators.html#estimators}}.
 

### 2023-05-25 src/ms-review.tex
Fix build after implementing comments

--- 2023-05-24 src/ms-review.tex
@@
 introduce all sub-packages and their functionalities in more detail.
+In the online documentation we also provide an overview of all
+the \gammapy sub-packages\footnote{\url{https://docs.gammapy.org/1.0/user-guide/package.html}}.q
 
@@
 Some example IRFs read from public data files and plotted with \gammapy are shown 
-in Figure~\ref{fig:irfs}.
+in Figure~\ref{fig:irfs}. More information on \code{gammapy.irf} can be found 
+in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/user-guide/irf/index.html\#irf}}.
 
@@
 
+More information on the \code{gammapy.maps} sub-module can be found 
+in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/user-guide/maps/index.html\#maps}}.
+
 \subsection{gammapy.datasets}
@@
 methods.
+
+We also refer to our online documentation for more details on \code{gammapy.datasets}
+\footnote{\url{https://docs.gammapy.org/1.0/user-guide/datasets/index.html\#datasets}}.
 
@@
 
+More detailed information on the \code{gammapy.makers} sub-package is available online\footnote{\url{https://docs.gammapy.org/1.0/user-guide/makers/index.html\#makers}}.
+
 \subsection{gammapy.stats}
@@
 
+Our online documentation provides more information on \code{gammapy.stats}
+\footnote{\url{https://docs.gammapy.org/1.0/user-guide/stats/index.html\#stats}}.
+
 \subsection{gammapy.modeling}
@@
 
-The model gallery\footnote[number]{\url{https://docs.gammapy.org/1.0/user-guide/model-gallery/index.html}}
+The model gallery\footnote{\url{https://docs.gammapy.org/1.0/user-guide/model-gallery/index.html}}
  provides a visual overview of the available models in
@@
 more examples of user-defined models, such as a parametric model for energy dependent morphology,
-in the online documentation\footnote[number]{\url{https://docs.gammapy.org/1.0/tutorials/api/models.html#implementing-a-custom-model}}.
+in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/tutorials/api/models.html\#implementing-a-custom-model}}.
 
@@
 bins of the resulting flux and TS maps.
+
+More details on the \code{gammapy.estimators} sub-module are available online \footnote{\url{https://docs.gammapy.org/1.0/user-guide/estimators.html\#estimators}}.
 
@@
 More examples for modelling the broadband emission of \gammaray sources, which 
-partly involve \gammpy are available in the online documentation of the
-Agnpy, Naima, Jetset and Gamera packages\footnote{\url{https://agnpy.readthedocs.io/en/latest/tutorials/ssc_gammapy_fit.html}},
+partly involve \gammapy are available in the online documentation of the
+Agnpy, Naima, Jetset and Gamera packages\footnote{\url{https://agnpy.readthedocs.io/en/latest/tutorials/ssc\_gammapy\_fit.html}},
 \footnote{\url{https://naima.readthedocs.io/en/stable/tutorial.html}}, 
-\footnote{\url{https://jetset.readthedocs.io/en/stable/user_guide/documentation_notebooks/gammapy_plugin/gammapy_plugin.html}},
-\footnote{\url{http://libgamera.github.io/GAMERA/docs/fitting_data.html}}.
+\footnote{\url{https://jetset.readthedocs.io/en/stable/user\_guide/documentation\_notebooks/gammapy\_plugin/gammapy\_plugin.html}},
+\footnote{\url{http://libgamera.github.io/GAMERA/docs/fitting\_data.html}}.
 
@@
 	in the significance or TS maps, computed by the \code{ExcessMapEstimator} or
-	\code{TSMapEstimator} respectively. For this \gammapy provides a simple \code{find_peaks}
+	\code{TSMapEstimator} respectively. For this \gammapy provides a simple \code{find\_peaks}
 	method. For more advanced methods users can rely on 3rd party packages such as

### 2023-05-29 src/ms-review.tex
Fix merge conflicts

@@
 \label{sec:introduction}
-
-%% \gammaray astronomy
-Modern astronomy offers the possibility to observe and study astrophysical sources across
-all wavelengths. The \gammaray range of the electromagnetic spectrum 
-provides us with insights into the most energetic processes in the universe such as
-those accelerating particles in the surroundings of black holes or remnants of
-supernova explosions.
-
-In general, \gammaray astronomy relies on the detection of individual 
-photon events and reconstruction of their incident direction as well
-as energy. As in other branches of astronomy, this can be
-achieved by satellite as well as ground-based \gammaray instruments.
-Space-borne instruments such as the Fermi Large Area Telescope (LAT)
-rely on the pair-conversion effect to detect \gammarays and track
-the positron-electron pairs created in the detector to reconstruct the incident direction 
-of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
-at the bottom of the instrument. The energy range of instruments like \fermi \citep{Atwood2009}, referred to as
-high-energy (HE), goes approximately from tens of \si{MeV} to hundreds of \si{GeV}.
-
-Ground-based instruments, instead, use the Earth's atmosphere as a particle detector, relying on the fact that
-cosmic \gammarays interacting in the atmosphere create large showers of secondary particles that can be observed from the ground.
-Ground-based \gammaray astronomy relies on these extensive air showers to estimate the
-primary \gammaray photons incident direction and energy.
-These instruments operate in the so-called very-high-energy (VHE) regime,
-covering the energy range from few tens of \si{GeV} up to the \si{PeV}.
-There are two main categories of ground-based instruments.
-
-\textit{Imaging Atmospheric Cherenkov Telescopes (IACTs)} obtain images of the atmospheric showers
-by detecting the Cherenkov radiation emitted by charged particles in the cascade and
-use these images to reconstruct the properties of the incident particle.
-Those instruments have a limited field of view (FoV) and duty cycle, but
-good energy and angular resolution.
-
-\textit{Water Cherenkov Detectors (WCDs)} detect particles directly from the tail of the
-shower when it reaches the ground. These instruments have a very
-large FoV, and large duty-cycle, but a higher energy threshold and
-lower signal-to-noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
-
+%
 \begin{figure*}[t]
@@
 \end{figure*}
+%
+%% \gammaray astronomy
+Modern astronomy offers the possibility to observe and study astrophysical sources across
+all wavelengths. The \gammaray range of the electromagnetic spectrum 
+provides us with insights into the most energetic processes in the universe such as
+those accelerating particles in the surroundings of black holes or remnants of
+supernova explosions.
+
+In general, \gammaray astronomy relies on the detection of individual 
+photon events and reconstruction of their incident direction as well
+as energy. As in other branches of astronomy, this can be
+achieved by satellite as well as ground-based \gammaray instruments.
+Space-borne instruments such as the Fermi Large Area Telescope (LAT)
+rely on the pair-conversion effect to detect \gammarays and track
+the positron-electron pairs created in the detector to reconstruct the incident direction 
+of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
+at the bottom of the instrument. The energy range of instruments like \fermi \citep{Atwood2009}, referred to as
+high-energy (HE), goes approximately from tens of \si{MeV} to hundreds of \si{GeV}.
+
+Ground-based instruments, instead, use the Earth's atmosphere as a particle detector, relying on the effect that
+cosmic \gammarays interacting in the atmosphere create large showers of secondary particles that can be observed from the ground.
+Ground-based \gammaray astronomy relies on the observation of these extensive air showers to estimate the
+primary \gammaray photons incident direction and energy.
+These instruments operate in the so-called very-high-energy (VHE) regime,
+covering the energy range from few tens of \si{GeV} up to the \si{PeV}.
+There are two main categories of ground-based instruments.
+
+\begin{itemize}
+\setlength\itemsep{1em}
+
+\item \textit{Imaging Atmospheric Cherenkov Telescopes (IACTs)} obtain images of the atmospheric showers
+by detecting the Cherenkov radiation emitted by charged particles in the cascade and
+use these images to reconstruct the properties of the incident particle.
+Those instruments have a limited field of view (FoV) and duty cycle, but
+good energy and angular resolution.
+
+\item \textit{Water Cherenkov Detectors (WCDs)} detect particles directly from the tail of the
+shower when it reaches the ground. These instruments have a very
+large FoV, and large duty-cycle, but a higher energy threshold and
+lower signal-to-noise ratios compared to IACTs~\citep{2015CRPhy..16..610D}.
+
+\end{itemize}
 
@@
 %% https://fermi.gsfc.nasa.gov/ssc/data/policy/
-While \fermi data and analysis tools have been public from the
-beginning \citep{}, ground-based \gammaray astronomy has been historically conducted
+While \fermi data and analysis tools have been public from early years
+of the project \citep{Atwood2009}, ground-based \gammaray astronomy has been historically conducted
 through experiments operated by independent collaborations, each relying
@@
 the rich ecosystem of packages and its open and supportive community \citep{Momcheva2015}.
-
-%% CN: astronomy alone not a sub-field
 In the sub-field of computational astronomy, the \astropy project \citep{astropy} was created in 2012
@@
 \label{sec:gammaray-data-analysis}
-% This might not be the bast place compared to introduction
-The data analysis process in \gammaray astronomy is usually split into two parts.
+The data analysis process in \gammaray astronomy is usually split into two stages.
 The first one deals with the data processing from detector measurement, calibration, event
@@
 
-The other sequence, referred to as high-level analysis, deals with the extraction of physical
-quantities related to \gammaray sources and the production of high-level products such as spectra,
-light curves and catalogs. The methods applied here are more generic and are broadly
-shared across the field. The similarity in the high-level analysis would also allow
-for combining data from multiple instruments.
-
-%\subsection{Predicted counts and Instrument Response Functions}
-
-To extract physically relevant information, such as the flux, spatial or spectral shape of one or more sources,
-an analytical model is commonly adopted to describe the intensity of the radiation from gamma-ray sources
-as a function of the energy, $E_{\rm true}$, and of the position in the FoV, $p_{\rm true}$:
-\begin{equation}
-    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}), [\Phi] = \si{TeV^{-1}.cm^{-2}.s^{-1}}
-    \label{eq:general_source_model}
-\end{equation}
-where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. To convert this analytical flux model
-into a prediction on the number of gamma-ray events detected by an instrument, $N_{\rm pred}$,
-with their estimated energy $E$ and position $p$, the model is convolved with the response function of the instrument.
-
-%% CN: not sure if we already commented about this, but align is artificially
-%% numbering every new line as a new equation
-%% I think
-%% \begin{equation}
-%%   \begin{split}
-%%     ...
-%%   \begin{split}
-%% \begin{equation}
-%% will avoid to number each new line
-
-In the most general way, we can write the expected number of detected events from the sky model $\Phi$ at measured position $p$ and energy $E$, for
-a given set of parameters $\hat{\theta}$, as:
-%
-\begin{equation}
-	\begin{split}
-   		N(p, E, \hat{\theta})\,{\rm d}p\,{\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true}) \\
-   		&\cdot \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} ) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
-	\end{split}
-\end{equation}
-
-where $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response and $t_{\rm obs}$ is the observation duration.
-
-A common assumption is that the instrument response can be simplified as the product
+The second stage, referred to as high-level analysis, deals with the extraction of physical
+quantities related to \gammaray sources and the production of high-level science products
+such as spectra, light curves and catalogs. The core of the analysis consists in predicting
+the result of an observation by modelling the flux distribution of an astrophysical
+object and pass it through a model of the instrument. The methods applied here are more
+generic and are broadly shared across the field. The similarity in the high-level
+analysis conceptionally also allow for easily combining data from multiple instruments.
+This part of the data analysis is supported by \gammapy.
+
+\subsection{DL3: Events And Instrument Response Functions}
+An overview of the typical steps in the high level analysis is shown in the upper
+row of Figure~\ref{fig:data_flow}. The high level analysis starts at the DL3 
+data level, where \gammaray data is represented as lists of \gammaray-like events and their
+corresponding IRFs $R$. DL3 data are typically bundled into individual observations, corresponding to
+stable periods of data acquisition. For IACT instruments, for which the \gadf
+data model and \gammapy were initially conceived, this duration is typically 
+$t_{\rm obs}=20 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
+The event list is just a simple table with one event per row and
+the measured event properties as columns. These properties e.g., include reconstructed
+incident direction and energy, arrival time and reconstruction quality.
+
+A common assumption for the instrument response is that it can be simplified as the product 
 of three independent functions:
@@
 
-where:
+\noindent Where:
 \begin{itemize}
@@
 
-DL3 \gammaray data at therefore consist of lists of \gammaray-like events and their
-corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),
-PSF and energy dispersion ($E_{\rm disp}$).
-In general, IRFs depend on the geometrical parameters of the detector, e.g. location 
-of an event in the FoV or the elevation angle of the incoming direction of the event.
-Consequently IRFs might be parametrised as functions of detector specific coordinates too.
-
-%% CN: this paragraph repeats what is commented in the previous formula and itemize and can be removed
-
-An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
-It represents the intensity of charged particles misidentified as \gammarays that are expected
-during an observation. It is defined as a function of the measured position in the FoV
-and measured energy.
-
-In total, the expected number of events in a \gammaray observation is given by:
-\begin{equation}
-	\begin{split}
-  N(p, E; \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \circledast \left[ PSF \circledast \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
-                       & + Bkg(p, E) \cdot t_{\rm obs}
-	\end{split}
-\end{equation}
-
-%% CN: Instead of rewriting this formula and introducing this new notation for the convolution,
-%% can't we just say that, when predicting counts, $Bkg(p, E)$ has to be summed to the convolution
-%% (or integral) in the previous equation?
-
-Finally, predicted and observed events, $N_{obs}$, can be combined in a likelihood function,
-$\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\hat{\theta}$.
-
-\subsection{\gammapy data analysis workflow}
-The first step in \gammaray data analysis is the selection and extraction of observations
-based on their metadata including information such as pointing direction, observation
-time and observation conditions.
-
+In addition to the instrument characteristics described above, there is also the instrumental
+background, that results from hadronic events being misclassified as \gammaray events. These
+events constitute a uniform background to the \gammaray events For \fermi the residual hadronic background
+is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCTs in contrast
+the background can account for a very large part ($>95\%$) of the events and must be treated
+accordingly in the analysis. As the background is very specific to the instrument, \gammapy typically 
+relies on the background models provided with the DL3 data. The background typically only depends
+on the reconstructed event positon and energy $Bkg(p, E)$. However in general all IRFs depend on the
+geometrical parameters of the detector, e.g. location of an event in the FoV or the elevation
+angle of the incoming direction of the event. Consequently IRFs might be parametrised as functions
+of detector specific coordinates as well.
+
+The first step in \gammaray data analysis is the selection and extraction of a subset of
+observations based on their metadata including information such as pointing direction,
+observation time and observation conditions. All functionality related to representation, 
+access and selection of DL3 data is available in the \code{gammapy.data} and \code{gammapy.irf}
+sub-packages.
+
+\subsection{From DL3 to DL4: Data Reduction}
 The next step of the analysis is the data reduction, where all observation events and instrument
@@
 
-%% CN: I would actually distingusih two cases here:
-%% 1) the Bkg is already provided as a parametrisation
-%% 2) the Bkg is not provided and, thus, has to be estimated from the obs.
 After all data have been projected into the same geometry, it is typically
@@
 from regions without known \gammaray sources. This includes methods 
-such as the ring or the FoV background techniques or
-background measurements performed within, e.g. reflected regions~\citep{Berge07}.
+such as the ring or the FoV background techniques or background measurements
+performed within, e.g. reflected regions~\citep{Berge07}.
+
 Data measured at the FoV or energy boundaries of the instrument are typically
@@
 
-%% CN: for 1D analysis datasets, DL4 can actually be written as OGIP files,
-%% so as reduced datasets in a general format, not specific to Gammapy.
-%% Maybe you can briefly mention that this is due to the fact that the 1D Poisson
-%% spectral analysis is liong consilidated, but this also means that Gammapy 's
-%% dataset can handle lower energy data, e.g. X-ray.
-%% We also said in the abstract that Gammapy is compliant with other specifications
-%% adopted in high-energy astrophysics.
+All the code related to reduce the DL3 data to binned data structures 
+is contained in the \code{gammapy.makers} sub-package.
+
+ \subsubsection{DL4: Binned Data Structures}
  The counts data and the reduced IRFs in the form of maps are bundled into datasets
@@
 
-The next step is then typically to model and fit the datasets, either
-individually, or in a joint likelihood analysis. For this purpose \gammapy
-provides a uniform interface to multiple fitting backends. In addition to
-providing a variety of built-in models, including spectral,
-spatial and temporal model classes to describe the \gammaray emission in the sky,
-custom user-defined models are also supported.
-Spectral models can be simple analytical models or more complex ones from radiation
-mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{0}$ decay).
-Independently or subsequently to the global modelling, the data can be
-re-grouped to compute flux points, light curves and flux maps as well as significance
-maps in different energy bands.
+Binned maps and datasets, which represent a collection of binned
+maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
+sub-packages, respectively.
+
+\subsection{From DL4 to DL5/6: Modeling and Fitting}
+The next step is then typically to model the datasets using binned Poisson maximum likelihood fitting.
+Assuming Poisson statistics per bin the log-likelihood of an observation is given by the Cash statistics\citep{Cash}:
+%
+\begin{equation}
+	\mathcal{C} = \sum_{i=0}^K N_{\mathrm{Pred, i}} - N_{\mathrm{Obs, i}} \log{N_{\mathrm{Pred, i}}} 
+\end{equation}
+
+Where the expected number of events in a \gammaray observation is given by:
+ \begin{equation}
+	 \begin{split}
+		N_{\mathrm{Pred}}(p, E; \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \circledast \left[ PSF \circledast \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
+						& + Bkg(p, E) \cdot t_{\rm obs}
+	 \end{split}
+ \end{equation}
+
+With the IRF components described in the previous section as well as an analytical model to describe the
+intensity of the radiation from gamma-ray sources as a function of the energy, $E_{\rm true}$,
+and of the position in the FoV, $p_{\rm true}$:
+%
+\begin{equation}
+    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}), [\Phi] = \si{TeV^{-1}.cm^{-2}.s^{-1}}
+    \label{eq:general_source_model}
+\end{equation}
+Where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. 
+Observtaions can be either modelled individually, or in a joint likelihood analysis.
+In the latter case the total (jpint) log-likleihood is given by the sum of the log-likelihoods
+per observation $\mathcal{L} = \sum{i=0}^M \mathcal{C_i}$ for M observations. Other fit
+statistics such as \textit{WStat} or a simple $\chi^2$ for flux points are also often used
+and are supported by \gammapy as well. Models can be simple analytical models or more complex
+ones from radiation mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{0}$ decay).
+
+Independently or subsequently to the global modelling, the data can be re-grouped to compute
+flux points, light curves and flux maps as well as significance maps in different energy bands.
+
+Parametric models and all the functionality realted to fitting is implemented in 
+\code{gammapy.modeling} and \code{gammapy.estimators}, where the latter is used to
+compute higher level science products such as flux and significance maps,
+light curves or flux points.
+
+% In the most general way, we can write the expected number of detected events from the sky model $\Phi$ at measured position $p$ and energy $E$, for
+%  a given set of parameters $\hat{\theta}$, as:
+%  %
+% %  \begin{equation}
+% % 	 \begin{split}
+% % 			N_{\mathrm{Pred}}(p, E, \hat{\theta})\,{\rm d}p\,{\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true}) \\
+% % 			&\cdot \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta} ) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
+% % 	 \end{split}
+% %  \end{equation}
+
+%  where $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response and $t_{\rm obs}$ is the observation duration.
+
+%  An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
+%  It represents the intensity of charged particles misidentified as \gammarays that are expected
+%  during an observation. It is defined as a function of the measured position in the FoV
+%  and measured energy.
+
+%  Finally, predicted and observed events, $N_{obs}$, can be combined in a likelihood function,
+%  $\mathcal{L}(\hat{\theta}, N_{obs})$, usually Poissonian, that is maximised to obtain the best-fit parameters of the flux model, $\hat{\theta}$.
 
@@
 %
-%
-The \gammapy package is structured into multiple sub-packages. The definition
+The \gammapy package is structured into multiple sub-packages. 
+Figure~\ref{fig:data_flow} also shows the overview of the different sub-packages and
+their relation to each other. The definition
 of the content of the different sub-packages follows mostly the stages of the
-data reduction workflow described in the previous section. Sub-packages
-either contain structures representing data at different reduction
-levels or algorithms to transition between these different levels.
-
-Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
-their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
-sub-packages define data objects to represent DL3 data, such as
-event lists and IRFs as well as functionality
-to read the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
-contains the functionality to reduce the DL3 data to binned maps.
-Binned maps and datasets, which represent a collection of binned
-maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
-sub-packages, respectively. Parametric models, which are defined in
-\code{gammapy.modeling}, are used to jointly model a combination
-of datasets, for example, to compute a spectrum using data from several facilities. Estimator classes,
-which are contained in \code{gammapy.estimators}, are used to
-compute higher level science products such as flux and significance maps,
-light curves or flux points. Finally there is a \code{gammapy.analysis}
-sub-package which provides a high-level interface for executing analyses
-defined from configuration files. In the following sections, we will
-introduce all sub-packages and their functionalities in more detail.
-In the online documentation we also provide an overview of all
-the \gammapy sub-packages\footnote{\url{https://docs.gammapy.org/1.0/user-guide/package.html}}.q
+data reduction workflow described in the previous section. Sub-packages either
+contain structures representing data at different reduction levels or algorithms
+to transition between these different levels. In the following sections, we will
+introduce all sub-packages and their functionalities in more detail. In the online 
+documentation we also provide an overview of all the \gammapy sub-packages\footnote{\url{https://docs.gammapy.org/1.0/user-guide/package.html}}.
 
@@
 supports data that is compliant with \code{v0.2} and \code{v0.3} of the \gadf data format.
-DL3 data are typically bundled into individual observations, corresponding to
-stable periods of data acquisition. For IACT instruments, for which the \gadf
-data model and \gammapy were initially conceived, this duration is typically 
-$20 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
 
@@
 
-%% CN: Shouldn't we display the output of this snippet?
-%% otherwise what's the point of the `print`' functions?
 \begin{figure}
@@
 	\caption{Example of a 3D analysis for simulated sources with point-like, Gaussian
-		and shell-like morphologies. The simulation uses \textit{prod5} \irfs from \cta.
+		and shell-like morphologies. The simulation uses \textit{prod5} \irfs from \cta
+		\citep{CtaProd5}.
 		The left image shows a significance map (using the \emph{Cash} statistics)

### 2023-05-29 scripts/download.py
Download EBL models

@@ -23,6 +23,8 @@ FILENAMES_FERMI_3FHL_GC = [
 
 FILENAMES_FERMI_CATALOG = ["catalogs/fermi/gll_psc_v28.fit.gz"]
 
+FILENAMES_EBL = ["ebl/ebl_dominguez11.fits.gz"]
+
 FILENAMES_FERMI_3FHL_CRAB = [
     "fermi-3fhl-crab/Fermi-LAT-3FHL_data_Fermi-LAT.fits",
     "fermi-3fhl-crab/Fermi-LAT-3FHL_iem.fits",
@@ -149,6 +151,11 @@ def download_hess_dr1_data():
     download_data_files(FILENAMES_HESS_DR1)
 
 
+def download_ebl_models():
+    """Download EBL models"""
+    download_data_files(FILENAMES_EBL)
+
+
 def download_multi_instrument():
     download_fermi_crab_3fhl()
     download_magic_data()
@@ -161,6 +168,7 @@ DATASETS_REGISTRY = {
     "pks-flare": download_hess_dr1_data,
     "multi-instrument": download_multi_instrument,
     "hawc-dl3": download_hawc_dl3_data,
+    "ebl": download_ebl_models,
 }
 
 

### 2023-05-31 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Atreyee Sinha <asinha@ucm.es>

--- 2023-05-25 src/ms-review.tex
@@
 
-DL3 \gammaray data at therefore consist of lists of \gammaray-like events and their
+DL3 \gammaray data therefore consist of lists of \gammaray-like events and their
 corresponding instrument response functions. The latter include the effective area ($A_{\rm eff}$),
@@
 In the online documentation we also provide an overview of all
-the \gammapy sub-packages\footnote{\url{https://docs.gammapy.org/1.0/user-guide/package.html}}.q
+the \gammapy sub-packages\footnote{\url{https://docs.gammapy.org/1.0/user-guide/package.html}}.
 

### 2023-06-01 src/ms-review.tex
Fix empty reference and observation length range

@@
 While \fermi data and analysis tools have been public from the
-beginning \citep{}, ground-based \gammaray astronomy has been historically conducted
+beginning \citep{Atwood2009}, ground-based \gammaray astronomy has been historically conducted
 through experiments operated by independent collaborations, each relying
@@
 data model and \gammapy were initially conceived, this duration is typically 
-$20 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
+$15 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
 

### 2023-06-01 src/ms-review.tex
Add CTA prod5 reference
Move authors to direct contribution to paper

--- 2023-05-29 src/ms-review.tex
@@
 	Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
+	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
+	Maximilian Linhoff \inst{\ref{inst:11}} \and
+	Jose Louis {Contreras} \inst{\ref{inst:15}} \and
 	\\
@@
 	Pooja Bhattacharjee \inst{\ref{inst:8}} \and
-	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
 	Johannes Buchner \inst{\ref{inst:12}} \and
@@
 	Jean-Philippe Lenain \inst{\ref{inst:22}} \and
-	Maximilian Linhoff \inst{\ref{inst:11}} \and
 	Lars Mohrmann \inst{\ref{inst:17}} \and
@@
 background, that results from hadronic events being misclassified as \gammaray events. These
-events constitute a uniform background to the \gammaray events For \fermi the residual hadronic background
-is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCTs in contrast
+events constitute a uniform background to the \gammaray events. For \fermi the residual hadronic background
+is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCDs in contrast,
 the background can account for a very large part ($>95\%$) of the events and must be treated
@@
 relies on the background models provided with the DL3 data. The background typically only depends
-on the reconstructed event positon and energy $Bkg(p, E)$. However in general all IRFs depend on the
+on the reconstructed event position and energy $Bkg(p, E)$. However in general all IRFs depend on the
 geometrical parameters of the detector, e.g. location of an event in the FoV or the elevation
@@
 
- \subsubsection{DL4: Binned Data Structures}
+ \subsection{DL4: Binned Data Structures}
  The counts data and the reduced IRFs in the form of maps are bundled into datasets
@@
 \begin{equation}
-	\mathcal{C} = \sum_{i=0}^K N_{\mathrm{Pred, i}} - N_{\mathrm{Obs, i}} \log{N_{\mathrm{Pred, i}}} 
+	\mathcal{C} = 2 \sum_{i=0}^K N_{\mathrm{Pred, i}} - N_{\mathrm{Obs, i}} \log{N_{\mathrm{Pred, i}}} 
 \end{equation}
 
-Where the expected number of events in a \gammaray observation is given by:
+Where the expected number of events for the observation is given by forward folding a source model through
+the instrument response:
  \begin{equation}
@@
 
-With the IRF components described in the previous section as well as an analytical model to describe the
-intensity of the radiation from gamma-ray sources as a function of the energy, $E_{\rm true}$,
+The equation includes the IRF components described in the previous section, as well as an analytical model to describe the
+intensity of the radiation from \gammaray sources as a function of the energy, $E_{\rm true}$,
 and of the position in the FoV, $p_{\rm true}$:
@@
 \end{equation}
+
 Where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. 
-Observtaions can be either modelled individually, or in a joint likelihood analysis.
-In the latter case the total (jpint) log-likleihood is given by the sum of the log-likelihoods
+Observations can be either modeled individually, or in a joint likelihood analysis.
+In the latter case the total (joint) log-likelihood is given by the sum of the log-likelihoods
 per observation $\mathcal{L} = \sum{i=0}^M \mathcal{C_i}$ for M observations. Other fit
-statistics such as \textit{WStat} or a simple $\chi^2$ for flux points are also often used
+statistics such as \textit{WStat}, where the background is estimated from an independent
+measurement or a simple $\chi^2$ for flux points are also often used
 and are supported by \gammapy as well. Models can be simple analytical models or more complex
@@
 
-Parametric models and all the functionality realted to fitting is implemented in 
+Parametric models and all the functionality related to fitting is implemented in 
 \code{gammapy.modeling} and \code{gammapy.estimators}, where the latter is used to

### 2023-06-11 src/ms-review.tex
Apply suggestions from code review
Co-authored-by: Régis Terrier <regis.terrier@m4x.org>

@@
 	Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
-	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
-	Maximilian Linhoff \inst{\ref{inst:11}} \and
-	Jose Louis {Contreras} \inst{\ref{inst:15}} \and
 	\\
@@
 	Pooja Bhattacharjee \inst{\ref{inst:8}} \and
+	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
 	Johannes Buchner \inst{\ref{inst:12}} \and
@@
 	Jean-Philippe Lenain \inst{\ref{inst:22}} \and
+	Maximilian Linhoff \inst{\ref{inst:11}} \and
 	Lars Mohrmann \inst{\ref{inst:17}} \and
@@
 events constitute a uniform background to the \gammaray events. For \fermi the residual hadronic background
-is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCDs in contrast,
+is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCTs in contrast
 the background can account for a very large part ($>95\%$) of the events and must be treated
@@
 
- \subsection{DL4: Binned Data Structures}
+ \subsubsection{DL4: Binned Data Structures}
  The counts data and the reduced IRFs in the form of maps are bundled into datasets
@@
 
-Where the expected number of events for the observation is given by forward folding a source model through
-the instrument response:
+Where the expected number of events in a \gammaray observation is given by:
  \begin{equation}
@@
 
-The equation includes the IRF components described in the previous section, as well as an analytical model to describe the
-intensity of the radiation from \gammaray sources as a function of the energy, $E_{\rm true}$,
+With the IRF components described in the previous section as well as an analytical model to describe the
+intensity of the radiation from gamma-ray sources as a function of the energy, $E_{\rm true}$,
 and of the position in the FoV, $p_{\rm true}$:
@@
 \end{equation}
-
 Where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. 
@@
 per observation $\mathcal{L} = \sum{i=0}^M \mathcal{C_i}$ for M observations. Other fit
-statistics such as \textit{WStat}, where the background is estimated from an independent
-measurement or a simple $\chi^2$ for flux points are also often used
+statistics such as \textit{WStat} or a simple $\chi^2$ for flux points are also often used
 and are supported by \gammapy as well. Models can be simple analytical models or more complex

### 2023-06-11 src/ms-review.tex
Apply suggestions from code review
Co-authored-by: Atreyee Sinha <asinha@ucm.es>

@@
 events constitute a uniform background to the \gammaray events. For \fermi the residual hadronic background
-is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCTs in contrast
+is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCDs in contrast,
 the background can account for a very large part ($>95\%$) of the events and must be treated

### 2023-06-12 src/ms-review.tex

@@
 
-Where the expected number of events in a \gammaray observation is given by:
+Where the expected number of events for the observation is given by forward folding a source model through
+the instrument response:
  \begin{equation}
@@
 \end{equation}
+
 Where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. 
@@
 per observation $\mathcal{L} = \sum{i=0}^M \mathcal{C_i}$ for M observations. Other fit
-statistics such as \textit{WStat} or a simple $\chi^2$ for flux points are also often used
+statistics such as \textit{WStat}, where the background is estimated from an independent
+measurement or a simple $\chi^2$ for flux points are also often used
 and are supported by \gammapy as well. Models can be simple analytical models or more complex

### 2023-06-12 src/ms-review.tex
Minor clean-up

@@
 data level, where \gammaray data is represented as lists of \gammaray-like events and their
-corresponding IRFs $R$. DL3 data are typically bundled into individual observations, corresponding to
+corresponding IRFs $R$ and ends at the DL5/6 data level, where the physicallyy relevant 
+quantities such as fluxes, spectra and light curves of sources have been derived. DL3 data are typically 
+bundled into individual observations, corresponding to
 stable periods of data acquisition. For IACT instruments, for which the \gadf
 data model and \gammapy were initially conceived, this duration is typically 
-$t_{\rm obs}=20 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
+$t_{\rm obs}=15 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
 The event list is just a simple table with one event per row and
@@
 accordingly in the analysis. As the background is very specific to the instrument, \gammapy typically 
-relies on the background models provided with the DL3 data. The background typically only depends
+relies on the background models provided with the DL3 data. The background usually only depends
 on the reconstructed event position and energy $Bkg(p, E)$. However in general all IRFs depend on the
@@
 
-After all data have been projected into the same geometry, it is typically
+After all data have been projected onto the same geometry, it is typically
 required to improve the residual hadronic background estimate. As residual hadronic
@@
 Where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit.
+
 Observations can be either modeled individually, or in a joint likelihood analysis.

### 2023-06-13 src/ms-review.tex
Reduce repetition in data reduction description

@@
 from regions without known \gammaray sources. This includes methods 
-such as the ring or the FoV background techniques or background measurements
+such as the ring or the FoV background normalisation techniques or background measurements
 performed within, e.g. reflected regions~\citep{Berge07}.
@@
 per observation $\mathcal{L} = \sum{i=0}^M \mathcal{C_i}$ for M observations. Other fit
-statistics such as \textit{WStat}, where the background is estimated from an independent
+statistics such as \emph{WStat}~\citep{WStat}, where the background is estimated from an independent
 measurement or a simple $\chi^2$ for flux points are also often used
@@
 The DL3 level data represented by the \code{Observation} class consist
-of two types of elements: first, a list of \gammaray events with relevant physical
-quantities such as estimated energy, direction and arrival
-times, which is represented by the \code{EventList} class. Second, a set of
+of two types of elements: first, the list of \gammaray events 
+which is represented by the \code{EventList} class. Second, a set of
 associated IRFs, providing the response of the system, typically
@@
 migration parameter ($\mu$, see section \label{sec:gammaray-data-analysis}).
- However, more complex
-shapes are also common. The distribution of the migration parameter is given at each offset angle and
+The distribution of the migration parameter is given at each offset angle and
 true energy. The main sub-classes are the \code{EnergyDispersion2D} which is
@@
 
-The predicted counts are computed by convolution of the models with the associated
-IRFs. Fitting of precomputed flux points is enabled through \code{FluxPointsDataset},
+Fitting of precomputed flux points is enabled through \code{FluxPointsDataset},
 using \emph{$\chi^2$} statistics. Multiple datasets of same or different types can be
@@
 The \code{gammapy.makers} sub-package contains the various classes and functions required
-to process and prepare \gammaray data from the DL3 to the DL4, representing the input for modelling and fitting.
-First, events are binned and IRFs are interpolated and projected onto the chosen analysis
-geometry. The end product of the data reduction process is a set of binned counts,
-background exposure, psf and energy dispersion maps at the DL4 level. 
+to process and prepare \gammaray data from the DL3 to the DL4.
+The end product of the data reduction process is a set of binned counts,
+background exposure, psf and energy dispersion maps at the DL4 level, bundled
+into a \code{MapDataset} object.
 The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
@@
 
-Because background models usually suffer from strong uncertainties, it is required
-to correct them from the data themselves. Several techniques are commonly used
-in TeV \gammaray astronomy such as FoV background normalization or
-background measurement in reflected regions, see~\cite{Berge07}.
-Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
-\code{ReflectedRegionsBackgroundMaker} are in charge of this process.
+The correction of background models from the data themselves is supported 
+by specific \code{Maker} classes such as the \code{FoVBackgroundMaker} or the
+\code{ReflectedRegionsBackgroundMaker}. The former is used to estimate the
+normalisation of the background model from the data themselves, while the
+latter is used to estimate teh background from regions reflected from the
+poiting position.
 %% CN: I would add a single line explaining what each of them do

### 2023-06-15 src/ms-review.tex

@@
 data level, where \gammaray data is represented as lists of \gammaray-like events and their
-corresponding IRFs $R$ and ends at the DL5/6 data level, where the physicallyy relevant 
+corresponding IRFs $R$ and ends at the DL5/6 data level, where the physically relevant 
 quantities such as fluxes, spectra and light curves of sources have been derived. DL3 data are typically 

### 2023-07-25 src/ms-review.tex
Fix typos and remove comments

@@
 %% Context
-%% CN: I think Fermi-LAT data were available from the 2nd year on
-%% https://fermi.gsfc.nasa.gov/ssc/data/policy/
 While \fermi data and analysis tools have been public from early years
@@
 %TODO: better transition into context
-% CN: last-minute transition improvement
 The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based
@@
 %% Context: development of open software
-%% CN: I don't see the parallel between gamma-ray astronomy establishing itself and the success of python
-%% maybe this was the introduction of the very first draft?
-%% I would just write: "In the past decade, \textit{Python} has become..."
 In the past decade \textit{Python} has become extremely popular as a scientific programming language,
@@
 %% \gammapy: concept and goals
-%%% Question: starting date? Is is relevant, what is the real start?
 The \gammapy project was started following the model of \astropy, with the objective of building a common
@@
 and \matplotlib~\citep{matplotlib} for visualization.
-
-%% CN: what's this??? Out of place here! %%%%
-%They consist of two
-%observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
-%the performance of the upgraded stereo system~\citep{magic_performance} and
-%already included in~\cite{joint_crab}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 which was used to validate the \gammapy package in \cite{Olivera2022}.
-%% CN: I would remark this also demonstrated Gammapy could be applied to WCD
-%% depite having been designed for IACTs initially
+
 The increased availability of public data that followed the definition of
@@
 		as maps and IRFs. The bottom of the figure shows the high-level analysis
-		sub-module with its dependcy on the YAML file format. 
+		sub-module with its dependency on the YAML file format. 
     }
@@
 
-%% CN: ref. for King function https://ui.adsabs.harvard.edu/abs/2011A%26A...534A..34R/abstract
-%% CN: I would not say that the PSFKing takes into account "the gamma and sigma", fo what?
-%% I would put a formula or quickly describe the function (e.g. it is a power-law, an exponential...)
 \subsubsection{Point Spread Function}
@@
         name attribute to allow a later access by name in the code. The
-        environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
+        environment variable \code{\$GAMMAPY\_DATA} is automatically resolved
         by \gammapy. The output
@@
 statistic, there are other classes which support
-analyses where the background is measured from control regions, so called \enquote{off} obervations.
+analyses where the background is measured from control regions, so called \enquote{off} observations.
 Those require the use of a different fit statistics, which takes into account the
@@
 normalisation of the background model from the data themselves, while the
-latter is used to estimate teh background from regions reflected from the
-poiting position.
-%% CN: I would add a single line explaining what each of them do
+latter is used to estimate the background from regions reflected from the
+pointing position.
 
@@
         Using \code{gammapy.stats} to compute statistical quantities
-        such as excess, significance and asymetric errors
+        such as excess, significance and asymmetric errors
         from counts based data. The data array such as \code{counts}, \code{counts\_off}
-		and the background efficency ratio \code{alpha} are passed on initialisation
+		and the background efficiency ratio \code{alpha} are passed on initialisation
         of the \code{WStatCountsStatistic} class. The derived quantities
@@
 adjusting template-based models, or, for example, to take into account
-the absorbtion effect on \gammaray spectra caused by the extra-galactic background
+the absorption effect on \gammaray spectra caused by the extra-galactic background
 light (EBL) (\code{EBLAbsorptionNormSpectralModel}). \gammapy supports a variety
@@
 
-%% CN: should we mention that the dataset also include the stat function?
-%% and thus the fit interfaces only with the dataset
 The \code{Fit} class provides methods to fit, i.e. optimise, model parameters and estimate
@@
 examples are given in the tutorials.
-%% CN: I would write "to perform a joint fit from multiple datasets from the same instruments
-%% (e.g. collected with different configurations) or from multiple datasets from different gamma-ray
-%% instruments (space- and ground-based)."
 
@@
 }
-%% CN: watchout with giving links to notebooks whose position might change or disappear in the future.
 
@@
 \gadf SED format \footnote{\url{https://gamma-astro-data-formats.readthedocs.io/en/latest/spectra/flux_points/index.html}},
-FITS-based ND sky maps and other formats compatible with Astropy's \code{Table} and
+FITS-based nd sky maps and other formats compatible with Astropy's \code{Table} and
 \code{BinnedTimeSeries} data structures. This allows
@@
 Methods for this will be implemented in future versions of \gammapy.
-%% CN: reference for unfolding https://ui.adsabs.harvard.edu/abs/2007NIMPA.583..494A/abstract
 
@@
 light curves production.
-%% CN: I would not say that these are use cases, rather analysis or data reduction steps
 
@@
 \label{sec:applications}
-%% CN: I think we never explained what gammapy-data is and we should have at this point 
-%% (it is used without mention also in the TSEstimator example).
 \gammapy is currently used for a variety of analyses by different IACT
@@
 Beside reproducing standard methodologies, we illustrate the unique data combination
-capabilites of \gammapy by presenting a multi-instrument analysis, which is not possible within any
+capabilities of \gammapy by presenting a multi-instrument analysis, which is not possible within any
 of the current instrument private software frameworks.
@@
 \code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
-illustrated for all three observations overlayed on the counts map in Figure~\ref{fig:cta_galactic_center}.
+illustrated for all three observations overlaid on the counts map in Figure~\ref{fig:cta_galactic_center}.
 After reduction, the data were modelled using a forward-folding method and assuming
@@
 \end{figure*}
-%% CN: expand 1DC acronym and add a reference, here or in the section text
 
@@
 parabola is fitted over almost five decades in energy \SI{10}{GeV} to \SI{300}{TeV}, taking into account all flux points from all three datasets.
-%% CN: is the LP formula specified elsewhere?
 
@@
 scientific Python ecosystem. This allows to rely on 3rd party functionality
-wherever needed. A simplifed catalog analysis based on \gammapy typically includes:
+wherever needed. A simplified catalog analysis based on \gammapy typically includes:
 
@@
 
-\gammapy has been succesfully used for catalog studies performed on simulations
+\gammapy has been successfully used for catalog studies performed on simulations
 of the future \cta Galactic Plane Survey~\citep{Remy2021}. Besides the scientific
@@
 \gammapy is an international open-source project with a broad
-developer base and contributions and commitments from mutiple groups and
+developer base and contributions and commitments from multiple groups and
 leading institutes in the very high-energy astrophysics
@@
 %         code that implements actual functionality and code the implements tests.
-%         All documentataion in \gammapy is implemented as dosctrings, \text{reStructuredText} (RST)
+%         All documentation in \gammapy is implemented as dosctrings, \text{reStructuredText} (RST)
 %         files or notebooks.
@@
 quick feature-driven development to more stable maintenance
-and user support driven developement. After v1.0 we foresee
-a developement cycle with major, minor and bugfix releases;
+and user support driven development. After v1.0 we foresee
+a development cycle with major, minor and bugfix releases;
 basically following the development cycle of the Astropy

### 2023-08-04 src/ms-review.tex
Further language edits

@@
 \usepackage{graphicx}
-\usepackage{url}
+\usepackage{txfonts,textcomp}
 \usepackage{xcolor}
@@
 
-\begin{document}
 \newcommand{\PythonUrl}{\url{http://fits.gsfc.nasa.gov/}\xspace}
@@
 \newcommand{\irfs}{IRFs\xspace}
-\newcommand{\fermi}{\textit{Fermi}-LAT\xspace}
+\newcommand{\fermi}{Fermi-LAT\xspace}
 \newcommand{\gammaray}{$\gamma$-ray\xspace}
@@
 \newcommand{\github}{GitHub\xspace}
+
+\begin{document}
 
@@
                 Alongside the data, they will also make the associated software tools available to a wider community.
-    This necessity prompted the development of open, high-level, astronomical software customised for high-energy astrophysics.
+    This necessity prompted the development of open, high-level, astronomical software customized for high-energy astrophysics.
         }
@@
                 Built on the modern Python scientific ecosystem, \gammapy provides a uniform platform for reducing and
-		modelling data from different \gammaray instruments for many analysis scenarios.
-    \gammapy complies with several well-established data conventions in high-energy astrophysics, providing serialised data products that
+                modeling data from different \gammaray instruments for many analysis scenarios.
+    \gammapy complies with several well-established data conventions in high-energy astrophysics, providing serialized data products that
                 are interoperable with other software packages.
@@
                 and assuming a variety of spectral, temporal, and spatial models.
-		Estimation of flux points, likelihood profiles and light curves is also supported.
+                Estimation of flux points, likelihood profiles, and light curves is also supported.
         }
         {
-		After describing the structure of the package, we show, using publicly-available gamma-ray data,
+                After describing the structure of the package, we show, using publicly available gamma-ray data,
                 the capabilities of \gammapy in multiple traditional and novel \gammaray analysis scenarios,
-		such as spectral and spectro-morphological modelling and estimations of a spectral energy
+                such as spectral and spectro-morphological modeling and estimations of a spectral energy
                 distribution and a light curve.
@@
                 imaging atmospheric Cherenkov technique (IACT). This includes
-		instruments such as the Cherenkov Telescope Array Observatory (CTAO),
-		the High Energy Stereoscopic System (H.E.S.S.), the
-		Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC),
-		and the Very Energetic Radiation Imaging Telescope Array System (VERITAS).
+                instruments such as the Cherenkov telescope array observatory (CTAO),
+                the high energy stereoscopic system (H.E.S.S.), the
+                major atmospheric gamma imaging Cherenkov telescopes (MAGIC),
+                and the very energetic radiation imaging telescope array system (VERITAS).
                 The lower left shows the group of all-sky instruments such as the
-		Fermi Large Area Telescope (\textit{Fermi}-LAT) and the High Altitude
-		Water Cherenkov Observatory (HAWC). The calibrated data of all those
-		instruments can be converted and stored into the common GADF data format, that \gammapy can read.
+                Fermi large area telescope (Fermi-LAT) and the high altitude
+                water Cherenkov observatory (HAWC). The calibrated data of all those
+                instruments can be converted and stored into the common GADF data format, which \gammapy can read.
                 The \gammapy package is a community-developed project that
@@
 all wavelengths. The \gammaray range of the electromagnetic spectrum 
-provides us with insights into the most energetic processes in the universe such as
+provides us with insights into the most energetic processes in the Universe such as
 those accelerating particles in the surroundings of black holes or remnants of
@@
 of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
-at the bottom of the instrument. The energy range of instruments like \fermi \citep{Atwood2009}, referred to as
-high-energy (HE), goes approximately from tens of \si{MeV} to hundreds of \si{GeV}.
-
-Ground-based instruments, instead, use the Earth's atmosphere as a particle detector, relying on the effect that
-cosmic \gammarays interacting in the atmosphere create large showers of secondary particles that can be observed from the ground.
+at the bottom of the instrument. The energy range of instruments such as \fermi \citep{Atwood2009}, referred to as
+\enquote{high energy} (HE), goes approximately from tens of Megaelectronvolts to hundreds of Gigaelectronvolts.
+
+Ground-based instruments, instead, use Earth's atmosphere as a particle detector, relying on the effect that
+cosmic \gammarays interacting in the atmosphere create large cascades of secondary particles, so called \enquote{air showers}, that can be observed from the ground.
 Ground-based \gammaray astronomy relies on the observation of these extensive air showers to estimate the
-primary \gammaray photons incident direction and energy.
-These instruments operate in the so-called very-high-energy (VHE) regime,
-covering the energy range from few tens of \si{GeV} up to the \si{PeV}.
+primary \gammaray photons' incident direction and energy.
+These instruments operate in the so-called \enquote{very high energy} (VHE) regime,
+covering the energy range from a few tens of Gigaelectronvolts up to Petaelectronvolts.
 There are two main categories of ground-based instruments.
 
-\begin{itemize}
-\setlength\itemsep{1em}
-
-\item \textit{Imaging Atmospheric Cherenkov Telescopes (IACTs)} obtain images of the atmospheric showers
+First there are imaging atmospheric Cherenkov telescopes (IACTs), which obtain images of the atmospheric showers
 by detecting the Cherenkov radiation emitted by charged particles in the cascade and
-use these images to reconstruct the properties of the incident particle.
+they use these images to reconstruct the properties of the incident particle.
 Those instruments have a limited field of view (FoV) and duty cycle, but
@@
 
-\item \textit{Water Cherenkov Detectors (WCDs)} detect particles directly from the tail of the
+Second there are water Cherenkov detectors (WCDs), that detect particles directly from the tail of the
 shower when it reaches the ground. These instruments have a very
@@
 
-\end{itemize}
-
 %% Context
-While \fermi data and analysis tools have been public from early years
+While \fermi data and analysis tools have been public since the early years
 of the project \citep{Atwood2009}, ground-based \gammaray astronomy has been historically conducted
@@
 on their own proprietary data and analysis software developed as part of the
-instrument. While this model has been so far successful, it does not
-permit easy combination of data from several instruments. This lack of
+instrument. While this model has been successful so far, it does not
+permit data from several instruments to be combined easily. This lack of
 interoperability currently limits the full exploitation of the
@@
 complementary sky coverages, and the various detection
-techniques have complementary properties in terms of energy range covered,
-duty cycle and spatial resolution.
+techniques have complementary properties in terms of the energy range covered,
+duty cycle, and spatial resolution.
 
@@
 will be shared publicly after some proprietary period, along with the software required to analyze them.
-The adoption of an open and standardised \gammaray data format, beside being a necesity for future observatories such as \cta,
-will be greatly beneficial to the current generation of instruments, eventually allowing to exploit their data legacies even
+The adoption of an open and standardized \gammaray data format, besides being a necessity for future observatories such as \cta,
+will be extremely beneficial to the current generation of instruments, eventually allowing their data legacies to be exploited even
 beyond the end of their scientific operations.
@@
 After data calibration, shower events are reconstructed and
-a gamma / hadron separation is applied to reject cosmic-ray-intiated showers and build lists of \gammaray-like events.
+a gamma-hadron separation is applied to reject cosmic-ray-initiated showers and build lists of \gammaray-like events.
 The latter can then be used, taking into account the observation-specific instrument response functions (IRFs),
-to derive scientific results, such as spectra, sky maps or light curves.
+to derive scientific results, such as spectra, sky maps, or light curves.
 Once the data is reduced to a list of events with reconstructed physical properties of the primary particle,
@@
 The efforts to create a common format usable by various instruments
-converged in the so-called \textit{Data Formats for \gammaray Astronomy}
+converged in the so-called {data formats for \gammaray astronomy}
 initiative~\citep{gadf_proc,gadf_universe}, abbreviated to
-\texttt{gamma-astro-data-formats} (\gadf). This community-driven intitiative proposes prototypical
+\texttt{gamma-astro-data-formats} (\gadf). This community-driven initiative proposes prototypical
 specifications to produce files based on the flexible image transport system
@@
 realized by storing a list of \gammaray-like events with their reconstructed and observed
-quantities such as energy, incident direction and arrival time and a parametrisation of
+quantities such as energy, incident direction and arrival time, and a parameterization of
 the IRFs associated with the event list data. %% where? in the data units of a FITS file.
@@
 %% Context: development of open software
-In the past decade \textit{Python} has become extremely popular as a scientific programming language,
+In the past decade, {Python} has become extremely popular as a scientific programming language,
 in particular in the field of data sciences. This success is
 mostly attributed to the simple and easy to learn syntax, the ability to act as
-a \enquote{glue} language between different programming languages and last but not least
+a \enquote{glue} language between different programming languages, and last but not least
 the rich ecosystem of packages and its open and supportive community \citep{Momcheva2015}.
-In the sub-field of computational astronomy, the \astropy project \citep{astropy} was created in 2012
+In the subfield of computational astronomy, the \astropy project \citep{astropy} was created in 2012
 to build a community-developed core Python package for astronomy.
 It offers basic functionalities that astronomers of many fields need, such as representing
-and transforming astronomical coordinates, manipulating physical quantities including units
+and transforming astronomical coordinates, manipulating physical quantities including units,
 as well as reading and writing FITS files.
@@
 The core of the idea is illustrated in Figure~\ref{fig:big_picture}. The various \gammaray instruments
-can export their data to a common format (\gadf) and then combine and analyse
+can export their data to a common format (\gadf) and then combine and analyze
 them using a common software library.
 The \gammapy package is an independent community-developed software project.
-It has been selected to be the core library for the Science Analysis tools of \cta,
-but also involves contributors associated to other instruments.
-The \gammapy package is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
+It has been selected to be the core library for the science analysis tools of \cta,
+but it also involves contributors associated with other instruments.
+The \gammapy package is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for ND data
 structures, \scipy~\citep{2020SciPy-NMeth} for numerical algorithms, \astropy~\citep{astropy} for
-astronomy-specific functionality, \iminuit~\citep{iminuit} for numerical minimisation
+astronomy-specific functionality, \iminuit~\citep{iminuit} for numerical minimization,
 and \matplotlib~\citep{matplotlib} for visualization.
@@
 With the public availability of the \gadf format specifications and the
-\gammapy package, some experiments started to make limited subsets of
+\gammapy package, some experiments have started to make limited subsets of
 their \gammaray data publicly available for testing and validating
@@
 This data release served as a basis for validation of open analysis tools, including \gammapy 
-\cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have
+\cite[see e.g.,][]{Mohrmann2019}. Two observations of the Crab nebula have
 been released by the \magic collaboration~\citep{magic_performance}.
-Using these public data from \fermi, \hess, \magic and additional observations
+Using these public data from \fermi, \hess, \magic, and additional observations
 provided by FACT and \veritas, the authors of \cite{joint_crab} presented
@@
 a common data format, and the development of \gammapy as a community-driven open software,
-led the way toward a more open science in the very-high-energy \gammaray astronomy domain.
-The adoption of \gammapy as science tools strengthens the commitment of the future \cta Observatory to the FAIR principles
-(Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} 
+led the way toward a more open science in the VHE \gammaray astronomy domain.
+The adoption of \gammapy as science tools strengthens the commitment of the future \cta Observatory to the  findable, accessible, interoperable, and reusable (FAIR) principles \citep{FAIR16, FAIR22} 
 that define the key requirements for open science.
@@
 In this article, we describe the general structure of the \gammapy package,
-its main concepts, and organisational structure. We start in
+its main concepts, and organizational structure. We start in
 Section~\ref{sec:gammaray-data-analysis} with a general overview
-of the data analysis workflow in very high-energy \gammaray astronomy. Then we
+of the data analysis workflow in VHE \gammaray astronomy. Then we
 show how this workflow is reflected in the structure of the \gammapy package 
 in Section~\ref{sec:gammapy-package}, while also
-describing the various subpackages it contains. Section~\ref{sec:applications}
+describing the various sub-packages it contains. Section~\ref{sec:applications}
 presents a number of applications, while Section~\ref{sec:gammapy-project}
@@
 
-\section{Gamma-ray Data Analysis}
+\section{Gamma-ray data analysis}
 \begin{figure*}[t]
@@
         gray arrows. The gray folder icons represent the different sub-packages
-        in \gammapy and names given as the corresponding Python code suffix, e.g. 
+        in \gammapy and names given as the corresponding Python code suffix, e.g., 
                 \code{gammapy.data}. Below each icon there is a list of the most
-        important objects defined in the sub-package. The light grey folder
-		icons show the subpackages for the most fundamental data structures such 
+        important objects defined in the sub-package. The light gray folder
+                icons show the sub-packages for the most fundamental data structures such 
                 as maps and IRFs. The bottom of the figure shows the high-level analysis
@@
 such as spectra, light curves and catalogs. The core of the analysis consists in predicting
-the result of an observation by modelling the flux distribution of an astrophysical
+the result of an observation by modeling the flux distribution of an astrophysical
 object and pass it through a model of the instrument. The methods applied here are more
@@
 The event list is just a simple table with one event per row and
-the measured event properties as columns. These properties e.g., include reconstructed
+the measured event properties as columns. These properties for example, include reconstructed
 incident direction and energy, arrival time and reconstruction quality.
@@
         \end{split}
-\end{equation}
-
-\noindent Where:
+,\end{equation}
+
+\noindent where
 \begin{itemize}
@@
 on the reconstructed event position and energy $Bkg(p, E)$. However in general all IRFs depend on the
-geometrical parameters of the detector, e.g. location of an event in the FoV or the elevation
-angle of the incoming direction of the event. Consequently IRFs might be parametrised as functions
+geometrical parameters of the detector, such as location of an event in the FoV or the elevation
+angle of the incoming direction of the event. Consequently IRFs might be parameterized as functions
 of detector specific coordinates as well.
@@
 defined by a binned energy axis and of spatial dimensions, which either define 
-a spherical projection from celestial coordinates to a pixelised image space
+a spherical projection from celestial coordinates to a pixelized image space
 or a single region on the sky.
@@
 from regions without known \gammaray sources. This includes methods 
-such as the ring or the FoV background normalisation techniques or background measurements
-performed within, e.g. reflected regions~\citep{Berge07}.
+such as the ring or the FoV background normalization techniques or background measurements
+performed for example within reflected regions~\citep{Berge07}.
 
@@
 of the data is often excluded from subsequent analysis by defining regions of
-\enquote{safe} data in the spatial as well as energy dimension.
-
-All the code related to reduce the DL3 data to binned data structures 
-is contained in the \code{gammapy.makers} sub-package.
+\enquote{safe} data in the spatial as well as energy dimension. All the code
+related to reduce the DL3 data to binned data structures is contained in the
+\code{gammapy.makers} sub-package.
 
@@
 in a format specific to \gammapy to allow users to read them back at any time later
-for modelling and fitting. Different variations of such datasets support different 
+for modeling and fitting. Different variations of such datasets support different 
 analysis methods and fit statistics. The datasets can be used to perform a joint-likelihood
-fit, allowing one to combine different measurements, e.g. from different observations
+fit, allowing one to combine different measurements from different observations,
 but also from different instruments or event classes. They can also be used for binned
@@
          \end{split}
- \end{equation}
+ .\end{equation}
 
@@
     \label{eq:general_source_model}
-\end{equation}
-
-Where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit.
+,\end{equation}
+
+where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit.
 
@@
 and are supported by \gammapy as well. Models can be simple analytical models or more complex
-ones from radiation mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{0}$ decay).
-
-Independently or subsequently to the global modelling, the data can be re-grouped to compute
+ones from radiation mechanisms of accelerated particle populations such as inverse Compton or $\pi^{0}$ decay.
+
+Independently or subsequently to the global modeling, the data can be regrouped to compute
 flux points, light curves and flux maps as well as significance maps in different energy bands.
@@
 associated IRFs, providing the response of the system, typically
-factorised in independent components as described in
+factorized in independent components as described in
 Section~\ref{ssec:gammapy-irf}. The separate handling of event lists and IRFs
@@
         \small
-	\import{code-examples/generated/}{gp_data}
+        %Added by TeX Support
+        %\import{code-examples/generated/}{gp_data}
         \caption{
@@
                 the $68\%$ containment radius of the PSF as a function of energy for the \cta, \hess
-		and \fermi instruments. The \cta IRFs are from the \textit{prod5} production for the {\it alpha} configuration of the south and north array. The \hess IRFs are from the DL3 DR1,
+                and \fermi instruments. The \cta IRFs are from the \enquote{prod5} production for the {\it alpha} configuration of the south and north array. The \hess IRFs are from the DL3 DR1,
         using observation ID 033787. The \magic effective area is computed for a
         $20\,{\rm min}$ observation at the Crab Nebula coordinates. The
-		\fermi IRFs use \textit{pass8} data and are also taken at the position of the Crab Nebula.
+                \fermi IRFs use \enquote{pass8} data and are also taken at the position of the Crab Nebula.
                 The \hawc effective area is shown for the event classes $N_{Hit}=5 - 9$ as light gray
@@
 to handle IRFs in a variety of functional forms.
-Usually, \irfs store instrument properties in the form of multi-dimensional
+Usually, \irfs store instrument properties in the form of multidimensional
 tables, with quantities expressed in terms of energy (true or reconstructed),
@@
 write, and evaluate the effective area for a given energy and offset angle, or
-even plot the multi-dimensional effective area table.
+even plot the multidimensional effective area table.
 
@@
 \gammapy allows users to treat different kinds of PSFs,
-in particular, parametric multi-dimensional Gaussian distributions (\code{EnergyDependentMultiGaussPSF})
+in particular, parametric multidimensional Gaussian distributions (\code{EnergyDependentMultiGaussPSF})
 or King profile functions (\code{PSFKing}). The \code{EnergyDependentMultiGaussPSF}
@@
 The generic \code{PSF3D} class stores a radial symmetric profile of a
-PSF to represent non-parametric shapes, again depending on true energy
+PSF to represent nonparametric shapes, again depending on true energy
 and offset from the pointing position.
@@
 the \code{PSFMap} class is used. It stores the radial profile of the PSF
-depending on the true energy and position on the sky. During the modelling
+depending on the true energy and position on the sky. During the modeling
 step in the analysis, the PSF profile for each model component is 
-looked up at its current position and converted into a 3d convolution kernel
+looked up at its current position and converted into a 3D convolution kernel
 which is used for the prediction of counts from that model component.
@@
 For \iacts, the energy resolution and bias, sometimes called energy dispersion,
-is typically parametrised in terms of the so-called
+is typically parameterized in terms of the so-called
 migration parameter ($\mu$, see section \label{sec:gammaray-data-analysis}).
 The distribution of the migration parameter is given at each offset angle and
-true energy. The main sub-classes are the \code{EnergyDispersion2D} which is
+true energy. The main subclasses are the \code{EnergyDispersion2D} which is
 designed to handle the raw instrument description, and the \code{EDispKernelMap},
-which contains an energy dispersion matrix per sky position, i.e., a 4-dimensional
-sky map where each position is associated to an energy dispersion matrix.
+which contains an energy dispersion matrix per sky position, that is, a 4D
+sky map where each position is associated with an energy dispersion matrix.
 The energy dispersion matrix is a representation of the energy resolution
 as a function of the true energy only and implemented in \gammapy
-by the sub-class \code{EDispKernel}.
+by the subclass \code{EDispKernel}.
 
 \subsubsection{Instrumental Background}
-The instrumental background rate can be represented as either a 2-dimensional
-data structure named \code{Background2D} or a 3-dimensional one named \code{Background3D}.
-The background rate is stored as a differential count rate, normalised per solid angle
+The instrumental background rate can be represented as either a 2D
+data structure named \code{Background2D} or a 3D one named \code{Background3D}.
+The background rate is stored as a differential count rate, normalized per solid angle
 and energy interval at different reconstructed energies and position in the FoV.
@@
 structures associated with a set of coordinates or a region on a sphere. In
-addition it allows to handle an arbitrary number of non-spatial data
+addition it allows one to handle an arbitrary number of nonspatial data
 dimensions, such as time or energy. It is organized around three types of
@@
 set of arithmetic and boolean operations with  unit support, up and downsampling
-along extra axes, interpolation, resampling of extra axes, interactive visualisation
+along extra axes, interpolation, resampling of extra axes, interactive visualization
 in notebooks and interpolation onto different geometries.
@@
 Map axes can have physical units attached to them, as well as define
-non-linearly spaced bins. The special case of time is covered by the
-dedicated \code{TimeMapAxis}, which allows time bins to be non-contiguous,
+nonlinearly spaced bins. The special case of time is covered by the
+dedicated \code{TimeMapAxis}, which allows time bins to be noncontiguous,
 as it is often the case with observational times. The generic
@@
 This allows users to perform the same higher level operations on maps
-independent of the underlying pixelisation scheme. The \code{gammapy.maps}
-package is also used by external packages such as \textit{FermiPy}~\citep{Wood2017}.
+independent of the underlying pixelization scheme. The \code{gammapy.maps}
+package is also used by external packages such as \enquote{FermiPy}~\citep{Wood2017}.
 
@@
         \small
-	\import{code-examples/generated/}{gp_maps}
+        %Added by TeX Support
+        %\import{code-examples/generated/}{gp_maps}
 
@@
         Using \code{gammapy.maps} to create a WCS, a HEALPix and a region
-		based data structures. The initialisation parameters include
+                based data structures. The initialization parameters include
         consistently the positions of the center of the map, the pixel
@@
 \gammapy provides full support to data structures using this pixelization
-scheme. For details see ~\cite{Calabretta2002}. This pixelisation
+scheme. For details see ~\cite{Calabretta2002}. This pixelization
 is typically used for smaller regions of interests, such as pointed
@@
 rectangular, or regular.
-This pixelisation is typically used for all-sky data, such as data
+This pixelization is typically used for all-sky data, such as data
 from the \hawc or \fermi observatory. \gammapy natively supports
-the multiscale definition of the HEALPix pixelisation and thus
+the multiscale definition of the HEALPix pixelization and thus
 allows for easy upsampling and downsampling of the data. In addition to
 the all-sky map, \gammapy also supports a local HEALPix
-pixelisation where the size of the map is constrained to a given
+pixelization where the size of the map is constrained to a given
 radius.
-For local neighbourhood operations, such as convolution, \gammapy relies
+For local neighborhood operations, such as convolution, \gammapy relies
 on projecting the HEALPix data to a local tangential WCS grid.
@@
 bin with an arbitrary shape, describing a region in the sky with that same
-shape. Region maps are typically used together with a non-spatial dimension, for
+shape. Region maps are typically used together with a nonspatial dimension, for
 example an energy axis, to represent how a quantity varies in that dimension
@@
 spherical geometry for regions, the regions are projected onto the local
-tangential plane using a WCS transform. This approach follows Astropy's \textit{Regions}
+tangential plane using a WCS transform. This approach follows Astropy's \enquote{Regions}
 package \citep{AstropyRegions2022}, which is both used as an API to define regions
@@
         \small
-	\import{code-examples/generated/}{gp_datasets}
+        %Added by TeX Support
+        %\import{code-examples/generated/}{gp_datasets}
         \caption{
@@
 %
-The \code{gammapy.datasets} subpackage contains classes to bundle
+The \code{gammapy.datasets} sub-package contains classes to bundle
 together binned data along with the associated models and likelihood function, which
 provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
-modelling and fitting purposes. Depending upon the type of analysis and the
+modeling and fitting purposes. Depending upon the type of analysis and the
 associated statistic, different types of Datasets are supported. The \code{MapDataset} is
-used for combined spectral and morphological (3D) fitting, while a 1D spectral 
-fitting can be performed using the \code{SpectrumDataset}.
+used for combined spectral and morphological (3D) fitting, while spectral 
+fitting only can be performed using the \code{SpectrumDataset}.
 While the default fit statistics for both of these classes is the \emph{Cash}~\citep{Cash}
@@
 using \emph{$\chi^2$} statistics. Multiple datasets of same or different types can be
-bundled together in \code{Datasets} (e.g., Figure \ref{fig*:minted:gp_datasets}),
+bundled together in \code{Datasets} (see e.g., Figure \ref{fig*:minted:gp_datasets}),
 where the likelihood from each constituent member is added, thus facilitating
@@
 across different wavelengths. Datasets also provide functionalities for
-manipulating reduced data, e.g. stacking, sub-grouping, plotting. Users can
+manipulating reduced data, for instance stacking, sub-grouping, plotting. Users can
 also create their customized datasets for implementing modified likelihood
@@
         \small
-    \import{code-examples/generated/}{gp_makers}
+        %Added by TeX Support
+    %\import{code-examples/generated/}{gp_makers}
         \caption{
@@
                 a step in the data reduction process. They take
-        the configuration on initialisation of the class. They 
+        the configuration on initialization of the class. They 
                 also consistently define \code{.run()} methods, which take
@@
 The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
-responsible for this task for 3D and 1D analyses, respectively (see Figure~\ref{fig*:minted:gp_makers}).
+responsible for this task for three- and 1D analyses, respectively (see Figure~\ref{fig*:minted:gp_makers}).
 
@@
 \code{ReflectedRegionsBackgroundMaker}. The former is used to estimate the
-normalisation of the background model from the data themselves, while the
+normalization of the background model from the data themselves, while the
 latter is used to estimate the background from regions reflected from the
@@
 domain is determined by the \code{SafeMaskMaker}. It can be used to limit the
-extent of the FoV used, or to limit the energy range to, e.g., a domain
-where the energy reconstruction bias is below a given value.
+extent of the FoV used, or to limit the energy range to a domain
+where the energy reconstruction bias is below a given threshold.
 
@@
         \small
-	\import{code-examples/generated/}{gp_stats}
+        %Added by TeX Support
+        %\import{code-examples/generated/}{gp_stats}
         \caption{
@@
         from counts based data. The data array such as \code{counts}, \code{counts\_off}
-		and the background efficiency ratio \code{alpha} are passed on initialisation
+                and the background efficiency ratio \code{alpha} are passed on initialization
         of the \code{WStatCountsStatistic} class. The derived quantities
@@
 %
-\code{gammapy.modeling} contains all the functionality related to modelling and fitting
+\code{gammapy.modeling} contains all the functionality related to modeling and fitting
 data. This includes spectral, spatial and temporal model classes, as well as
@@
 \label{sssec:models}
-Source models in \gammapy (Eq.~\ref{eq:general_source_model}) are four-dimensional 
+Source models in \gammapy (Eq.~\ref{eq:general_source_model}) are 4D 
 analytical models which support two spatial dimensions defined by the sky coordinates
 $\ell, b$, an energy dimension $E$, and a time dimension $t$. To simplify the definition of the
-models, \gammapy uses a factorised representation of the total source
+models, \gammapy uses a factorized representation of the total source
 model:
@@
 The spectral component $F(E)$, described by the \code{SpectralModel} class, always
-includes an \textit{amplitude} parameter to adjust the total flux of the model.
+includes an amplitude parameter to adjust the total flux of the model.
 The spatial component $G(\ell, b, E)$, described by the \code{SpatialModel} class,
@@
 named using the \code{NormSpectralModel} suffix.
-These spectral models feature a dimension-less \textit{norm} parameter
-instead of an \textit{amplitude} parameter with physical units. They
+These spectral models feature a dimension-less \enquote{norm} parameter
+instead of an amplitude parameter with physical units. They
 can be used as an energy-dependent multiplicative correction
@@
 
-The \code{SkyModel} class represents the factorised model in Eq.~\ref{eq:source_model_dependency}
+The \code{SkyModel} class represents the factorized model in Eq.~\ref{eq:source_model_dependency}
 (the spatial and temporal components being optional).
@@
         \small
-	\import{code-examples/generated/}{gp_models}
+        %Added by TeX Support
+        %\import{code-examples/generated/}{gp_models}
         \caption{Using \code{gammapy.modeling.models} to define a source model with a
@@
 
-The \code{Fit} class provides methods to fit, i.e. optimise, model parameters and estimate
+The \code{Fit} class provides methods to optimize (\enquote{fit}), model parameters and estimate
 their errors and correlations. It interfaces with a \code{Datasets} object, which
-in turn is connected to a \code{Models} object containing the model parameters in its
+in turn is connected to a \code{Models} object containing the model parameters bundled into a
 \code{Parameters} object. Models can be unique for a given dataset, or contribute to
-multiple datasets, allowing e.g., to perform a joint fit to
+multiple datasets, allowing one to perform a joint fit to
 multiple IACT datasets, or to jointly fit IACT and \fermi datasets. Many
@@
 
-Note that, for now, covariance matrix and errors are computed only for the fitting with 
+We note that, for now, covariance matrix and errors are computed only for the fitting with 
 \iminuit. However, depending on
@@
 The initial fine bins of \code{MapDataset} are grouped into
-larger bins. A multiplicative correction factor (the \textit{norm})
+larger bins. A multiplicative correction factor (the norm)
 is applied to the best fit reference spectral
@@
 
-In addition to the best-fit flux \textit{norm}, all estimators compute
+In addition to the best-fit flux norm, all estimators compute
 quantities corresponding to this flux. This includes:
@@
 null hypothesis (background only); and the difference between both,
-the so-called test statistic value (\textit{TS}).
-From this \textit{TS value}, a significance of the measured signal and associated flux
+the so-called test statistic value (TS).
+From this TS value, a significance of the measured signal and associated flux
 can be derived.
@@
 such as asymmetric flux errors, flux upper limits
-and one-dimensional profiles of the fit statistic,
+and 1D profiles of the fit statistic,
 which show how the likelihood functions varies with
-the flux \textit{norm} parameter around the fit minimum.
+the flux norm parameter around the fit minimum.
 This information is useful in inspecting the quality
@@
 by a reference spectral model and an array of
-normalisation values given in energy, time and spatial bins,
-which factorises the deviation of the flux in a given
+normalization values given in energy, time and spatial bins,
+which factorizes the deviation of the flux in a given
 bin from the reference spectral model. This allows
@@
 The actual flux values for each SED type are obtained
-by multiplication of the \textit{norm} with the reference flux.
+by multiplication of the {norm} with the reference flux.
 
@@
 
-Both result objects support the possibility to serialise
+Both result objects support the possibility to serialize
 the data into multiple formats. This includes the
@@
 \code{BinnedTimeSeries} data structures. This allows
-users to further analyse the results with Astropy, for example using
+users to further analyze the results with Astropy, for example using
 standard algorithms for time analysis, such as
@@
 the \code{TSMapEstimator} objects with a given input \code{MapDataset}.
-In addition to the model, it allows to specify the energy
-bins of the resulting flux and TS maps.
+In addition to the model, it allows the energy
+bins of the resulting flux and TS maps to be specified.
 
@@
         \small
-	\import{code-examples/generated/}{gp_estimators}
+        %Added by TeX Support
+        %\import{code-examples/generated/}{gp_estimators}
         \caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
@@
  can be used in Python scripts, notebooks or as commands within \texttt{IPython}
-sessions. The HLI can also be used to automatise
+sessions. The HLI can also be used to automatize
 workflows driven by parameters declared in a configuration file in YAML format.
@@
 colormaps. Those colormaps have been historically used by larger collaborations
-in the very high-energy domain (such as \milagro or \hess) as \enquote{trademark}
+in the VHE domain (such as \milagro or \hess) as \enquote{trademark}
 colormaps. While we explicitly discourage the use of those colormaps for publication
@@
 
-In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modelling
-galactic \gammaray sources according to simplified physical models, e.g. Supernova Remnant (SNR) evolution
-models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of Pulsar Wind Nebulae (PWNe) during the
-free expansion phase \citep{2006ARA&A..44...17G} or computation
+In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modeling
+galactic \gammaray sources according to simplified physical models, for example supernova remnant (SNR) evolution
+models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of pulsar wind nebulae (PWNe) during the
+free expansion phase \citep{2006ARA&A..44...17G}, or computation
 of physical parameters of a pulsar using a simplified dipole spin-down model.
@@
         \small
-	\import{code-examples/generated/}{gp_catalogs}
+        %Added by TeX Support
+        %\import{code-examples/generated/}{gp_catalogs}
         \caption{Using \code{gammapy.catalogs} to access the underlying model, flux points and
@@
 spectrum of a source in a given region defined on the sky, in conventional
-astronomy also called \textit{aperture photometry}. The spectrum is typically measured
+astronomy also called \emph{aperture photometry}. The spectrum is typically measured
 in two steps: first a parametric spectral model is fitted to the data and
-secondly flux points are computed in a pre-defined set of energy bins. The
+secondly flux points are computed in a predefined set of energy bins. The
 result of such an analysis performed on three simulated CTA observations is
@@
 illustrated for all three observations overlaid on the counts map in Figure~\ref{fig:cta_galactic_center}.
-After reduction, the data were modelled using a forward-folding method and assuming
+After reduction, the data were modeled using a forward-folding method and assuming
 a point source with a power law spectral shape. The model was defined, using
@@
         \caption{
-		Example of a one dimensional spectral analysis of the Galactic Center for three simulated
+                Example of a 1D spectral analysis of the Galactic Center for three simulated
                 observations from the first CTA data challenge. The left image shows the maps of counts with the signal
@@
         \caption{Example of a 3D analysis for simulated sources with point-like, Gaussian
-		and shell-like morphologies. The simulation uses \textit{prod5} \irfs from \cta
+                and shell-like morphologies. The simulation uses \enquote{prod5} \irfs from \cta
                 \citep{CtaProd5}.
@@
 
-As the example above shows, the 3D analysis allows to characterize the
-morphology of the emission and fit it together with the spectral properties of
+As the example above shows, the 3D analysis allows the
+morphology of the emission to be characterized and fit it together with the spectral properties of
 the source.  Among the advantages that this provides is the ability to
@@
 contribution from each of the three source models. The result can be seen in the right
-panel of Figure~\ref{fig:cube_analysis}. Note that all the models fitted also have a
+panel of Figure~\ref{fig:cube_analysis}. We note that all the models fitted also have a
 spectral component, from which flux points can be derived in a similar way as described
@@
 variability of a source. The most basic way to do this is to construct a
-light curve, i.e., the flux of a source in each given time bin. In \gammapy, this
-is done by using the \code{LightCurveEstimator} that fits the normalisation of a
+\enquote{light curve}, which corresponds to measuring the flux of a source
+in a set of given time bins. In \gammapy, this
+is done by using the \code{LightCurveEstimator} that fits the normalization of a
 source in each time (and optionally energy) band per observation, keeping constant
@@
         Binned PKS~2155-304 light curve in two different energy bands
-        as observed by the \hess telescopes in 2006. The coloured markers
+        as observed by the \hess telescopes in 2006. The colored markers
         show the flux points in the different energy bands:
@@
 %
-The obtained flux points can be analytically modelled using the available or
+The obtained flux points can be analytically modeled using the available or
 user-implemented temporal models. Alternatively, instead of  extracting a
@@
         \caption{
-        A multi-instrument spectral energy distribution (SED) and combined model fit
+        Multi-instrument spectral energy distribution (SED) and combined model fit
         of the Crab Nebula. The  colored markers show the flux points computed from
@@
 The \fermi data is introduced at the data level DL4, and directly bundled in a
-\code{MapDataset}. They have been prepared using the standard \textit{fermitools} \citep{Fermitools2019} and
+\code{MapDataset}. They have been prepared using the standard \enquote{fermitools} \citep{Fermitools2019} and
 selecting a region of $5^{\circ}\,\times\,4^{\circ}$ around the
@@
 for \fermi's \code{MapDataset} and MAGIC's \code{SpectrumDataset}, and a $\chi^2$
-accounting for the \hawc flux points. For \fermi, a three-dimensional forward folding
+accounting for the \hawc flux points. For \fermi, a 3D forward folding
 of the sky model with the IRF is performed, in order to compute the predicted counts
-in each sky-coordinate and energy bin. For \magic, a one-dimensional forward-folding
+in each sky-coordinate and energy bin. For \magic, a 1D forward-folding
 of the spectral model with the \irfs is performed to predict the counts in each estimated energy bin. A log
@@
 
-\subsection{Broadband SED Modelling}
+\subsection{Broadband SED modeling}
 \label{ssec:broadband-sed-modeling}
-By combining \gammapy with astrophysical modelling codes, users can also fit
+By combining \gammapy with astrophysical modeling codes, users can also fit
 astrophysical spectral models to \gammaray data. 
@@
 %
-We adopt the prescription on the target photon fields provided in the documentation of the \textit{Naima}
+We adopt the prescription on the target photon fields provided in the documentation of the \enquote{Naima}
 package\footnote{\url{https://naima.readthedocs.io/en/stable/examples.html\#crab-nebula-ssc-model}}.
@@
 
-More examples for modelling the broadband emission of \gammaray sources, which 
+More examples for modeling the broadband emission of \gammaray sources, which 
 partly involve \gammapy are available in the online documentation of the
@@
 simulations, we jump from 78 sources detected by \hess to about 500 detectable by
-CTA~\citep{Remy2021}. This large increase in the amount of data to analyse
-and increase in complexity of modelling scenarios, requires the high-level
+CTA~\citep{Remy2021}. This large increase in the amount of data to analyze
+and increase in complexity of modeling scenarios, requires the high-level
 analysis software to be both scalabale as well as performant.
@@
 with \gammapy or by relying on the seamless integration of \gammapy with the
-scientific Python ecosystem. This allows to rely on 3rd party functionality
+scientific Python ecosystem. This allows one to rely on third party functionality
 wherever needed. A simplified catalog analysis based on \gammapy typically includes:
@@
         \item[a] The \iacts data reduction step is done in the same way described in the 
-	previous sections but scaled up to few thousands of observations. This step can be
-	trivially parallelised by deploying the \gammapy package on a cluster.
+        previous sections but scaled up to a few thousand observations. This step can be
+        trivially parallelized by deploying the \gammapy package on a cluster.
         \item[b] The object detection step typically consists in finding local maxima
@@
         \code{TSMapEstimator} respectively. For this \gammapy provides a simple \code{find\_peaks}
-	method. For more advanced methods users can rely on 3rd party packages such as
-	\textit{Scikit-image}~\citep{scikit-image}. This packages provide e.g. general
-	blob detection algorithms and image segmentation methods such as hysteresis thresholding
+        method. For more advanced methods users can rely on third party packages such as
+        \enquote{Scikit-image}~\citep{scikit-image}. This packages provide for example general
+        \enquote{blob detection} algorithms and image segmentation methods such as hysteresis thresholding
         or the watershed transform.     
-	\item[c] During the modelling step each object is alternatively fitted with different
+        \item[c] During the modeling step each object is alternatively fitted with different
         models in order to determine their optimal parameters, and the best-candidate model. The
@@
         \gammapy provides statisticl helper methods to perform likelihood ratio tests.
-	But users can also rely on 3rd party packages such as \textit{Scikit-learn}~\citep{scikit-learn}
+        But users can also rely on third party packages such as \enquote{Scikit-learn}~\citep{scikit-learn}
         to compute quantities such as the Akaike information criterion (AIC) or the Bayesian
@@
         handling from Astropy in combination with affiliated packages such as
-	\textit{Astroquery}~\citep{astroquery}. For more advanced source classification
-	methods users can again rely e.g. \textit{Scikit-learn} to perform supervised
+        \enquote{Astroquery}~\citep{astroquery}. For more advanced source classification
+        methods users can again rely for example on Scikit-learn to perform supervised
         or unsupervised clustering.
@@
 also allowed for detailed cross-comparison of the results obtained with the independent
-\gammaray analysis package \textit{ctools}\citep{2016A&A...593A...1K}, with very consistent 
+\gammaray analysis package \enquote{ctools} \citep{2016A&A...593A...1K}, with very consistent 
 results.
@@
 projects, code review, testing, package distribution and user support, with a
-customized solution for a versioned and thoroughly-tested documentation in the form
+customized solution for a versioned and thoroughly tested documentation in the form
 of user-friendly playable tutorials. This section concludes with an outlook on
-the roadmap for future directions.
+the road map for future directions.
 
@@
 domain\footnote{\url{https://gammapy.org/team.html}}. The main development
-roadmaps are discussed and validated by a \textit{Coordination Committee}, composed of
+road maps are discussed and validated by a \enquote{Coordination Committee}, composed of
 representatives of the main contributing institutions and observatories.
 This committee is
-chaired by a \textit{Project Manager} and his deputy while two \textit{Lead Developers} manage
-the development strategy and organise technical activities. This
-institutionally-driven organisation, the permanent staff and commitment of
+chaired by a \enquote{Project Manager} and his deputy while two \enquote{Lead Developers} manage
+the development strategy and organize technical activities. This
+institutionally driven organization, the permanent staff and commitment of
 supporting institutes ensure the continuity of the executive teams. A core team
@@
 \gammapy follows an open-source and open-contribution development model based on
-the cloud repository service \github. A \github organization
-\textit{gammapy}\footnote{\url{https://github.com/gammapy}} hosts different
+the cloud repository service \github. A \github organization named
+\enquote{gammapy}\footnote{\url{https://github.com/gammapy}} hosts different
 repositories related with the project. The software codebase may be found in
-the \textit{gammapy} repository (see
+the Gammapy repository (see
 Figure~\ref{fig:codestats:lang} for code lines statistics). We make extensive
@@
 suite\footnote{\url{https://pytest.org}} using datasets from the
-\textit{gammapy-data} repository\footnote{\url{https://github.com/gammapy/gammapy-data}}.
+\enquote{gammapy-data} repository\footnote{\url{https://github.com/gammapy/gammapy-data}}.
 Tests scan not only the codebase, but also the
@@
 Other automated tasks, executing in the
-\textit{gammapy-benchmarks}\footnote{\url{https://github.com/gammapy/gammapy-benchmarks}} repository,
+\enquote{gammapy-benchmarks}\footnote{\url{https://github.com/gammapy/gammapy-benchmarks}} repository,
 are responsible for numerical validation tests and benchmarks monitoring. Also,
@@
 publishing workflow within the
-\textit{gammapy-docs} repository\footnote{\url{https://github.com/gammapy/gammapy-docs}}
+\enquote{gammapy-docs} repository\footnote{\url{https://github.com/gammapy/gammapy-docs}}
 (see Sec.~\ref{ssec:software-distribution} and Sec.~\ref{ssec:documentation-and-user-support}).
@@
 Python package index\footnote{\url{https://pypi.org}} and as a binary package
-to the \textit{conda-forge} and \textit{astropy} Anaconda
+to the \enquote{conda-forge} and \enquote{astropy} Anaconda
 repository\footnote{\url{https://anaconda.org/anaconda/repo}} channels. At this
@@
 package\footnote{\url{https://packages.debian.org/sid/python3-gammapy}}. We
-recommend installing the software using the \textit{conda} installation process
+recommend installing the software using the \enquote{conda} installation process
 with an environment definition file that we provide, so to work within a
@@
 Zenodo\footnote{\url{https://doi.org/10.5281/zenodo.4701488}} digital libraries for
-software. The Zenodo record is synchronised with the codebase \github repository
+software. The Zenodo record is synchronized with the codebase \github repository
 so that every release triggers the update of the versioned record. In addition,
@@
 
-In addition, \gammapy is also listed in the \textit{SoftWare
+In addition, \gammapy is also listed in the \enquote{SoftWare
 Heritage}~\footnote{\url{https://softwareheritage.org}} (SWH) archive~\cite{DiCosmo2020}.
 The archive collects, preserves, and shares the source code of publicly available software.
-SWH automatically scans open software repositories, like e.g. GitHub, and projects are archived in SWH by the
+SWH automatically scans open software repositories, such as GitHub, and projects are archived in SWH by the
 means of SoftWare Heritage persistent IDentifiers (SWHID), that are guaranteed to remain stable (persistent)
@@
 The resulting web published tutorials also provide links to playground spaces in
-\textit{myBinder}~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
+\enquote{myBinder}~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
 on-line in versioned virtual environments hosted in the myBinder
@@
 the associated datasets needed and the specific conda computing environment,
-using the \textit{gammapy download} command.
+using the \code{gammapy download} command.
 
@@
 specific use cases, in the form of Jupyter notebooks. Contributions happen via pull requests to the
-\textit{gammapy-recipes} \github repository and are merged after a short review. All
+\enquote{gammapy-recipes} \github repository and are merged after a short review. All
 notebooks in the repository are tested and published in the \gammapy recipes
@@
 \label{ssec:pigs}
-An important part of \gammapy's development organisation is the support
-for \textit{Proposals for improving \gammapy} (PIG). This system is very much
+An important part of \gammapy's development organization is the support
+for \enquote{Proposals for improving \gammapy} (PIG). This system is very much
 inspired by Python's PEP\footnote{\url{https://peps.python.org/pep-0001/}}
@@
 code and package restructuring and maintenance, as well as changes related
-to the organisational structure of the \gammapy project. PIGs can be proposed
+to the organizational structure of the \gammapy project. PIGs can be proposed
 by any person in or outside the project and by multiple authors. They
@@
 
-A special category of PIGs are long-term \textit{roadmaps}. To develop a common
+A special category of PIGs are long-term {road maps}. To develop a common
 vision for all \gammapy project members on the future of the
 project, the main goals regarding planned features, maintenance and
-project organisation are written up as an overview and presented to the
+project organization are written up as an overview and presented to the
 \gammapy community for discussion. The review and acceptance process
-follows the normal PIG guidelines. Typically roadmaps are written
+follows the normal PIG guidelines. Typically road maps are written
 to outline and agree on a common vision for the next long term
@@
 of this manuscript including figures and text, we relied on the tool
-\textit{showyourwork}~\citep{Luger2021}. This tool coordinates the building
+\enquote{showyourwork}~\citep{Luger2021}. This tool coordinates the building
 process and both software and data dependencies, such that the complete
@@
 
-\section{Summary and Outlook}
+\section{Summary and outlook}
 \label{sec:summary-and-outlook}
 %
-In this manuscript we presented the first LTS version of \gammapy.
+In this paper we have presented the first LTS version of \gammapy.
 \gammapy is a Python package for \gammaray astronomy, which relies on the
@@
 \gadf. Starting from lists of \gammaray events and corresponding descriptions
-of the instrument response users can reduce and project the data
-to WCS, HEALPix and region based data structures. The reduced data is bundled
+of the instrument response, users can reduce and project the data
+to WCS, HEALPix, and region-based data structures. The reduced data are bundled
 into datasets, which serve as a basis for Poisson maximum likelihood
-modelling of the data. For this purpose \gammapy provides a wide selection
-of built-in spectral, spatial and temporal models, as well as unified
-fitting interface with connection to multiple optimization backends.
-
-With the v1.0 release, the \gammapy project enters a new development
+modeling of the data. For this purpose \gammapy provides a wide selection
+of built-in spectral, spatial, and temporal models, as well as a unified
+fitting interface with a connection to multiple optimization backends.
+
+With the v1.0 release, the \gammapy project has entered a new development
 phase. Future work will not only include maintenance of the v1.0 release,
-but also parallel development of new features, improved API and data
+but also parallel development of new features, improved API, and data
 model support. While v1.0 provides all the features required for
@@
 we already identified specific improvements to be considered in the
-roadmap for a future v2.0 release. This includes the support for
+road map for a future v2.0 release. This includes the support for
 scalable analyses via distributed computing. This will allow
 users to scale an analysis from a few observations to multiple
-hundreds of observations as expected by deep surveys of the CTA
+hundreds of observations, as expected by deep surveys of the CTA
 observatory. In addition the high-level interface
@@
 API design. This will allow users to define arbitrary complex analysis
-scenarios as YAML files and even extend their workflows by user defined
+scenarios as YAML files and even extend their workflows by user-defined
 analysis steps via a registry system. Another important topic will
@@
 and provenance information to track the history of the data reduction
-process from the DL3 to the highest DL5/DL6 data levels. \gammapy will
-also extend its functionalities for time based analyses,
-e.g. tests for variability in light curves, phase curves peak search, 
+process from the DL3 to the highest DL5 and DL6 data levels. \gammapy will
+also extend its functionalities for time-based analyses,
+for example tests for variability in light curves, phase curves peak search, 
 as well as improving the interoperability with other timing packages such
-as \textit{Stingray}~\citep{Stingray2019}, \textit{Astropy's}
-time series classes and \textit{pint-pulsar}~\citep{Luo2021}
+as \enquote{Stingray}~\citep{Stingray2019}, Astropy's
+time series classes, and \enquote{pint-pulsar}~\citep{Luo2021}
  for high-precision pulsar timing.
 
-Around the core Python package a large diverse community of
+Around the core Python package, a large diverse community of
 users and contributors has developed. With regular developer meetings,
-coding sprints and in-person user tutorials at relevant conferences
+coding sprints, and in-person user tutorials at relevant conferences
 and collaboration meetings, the community has constantly grown.
-So far \gammapy has seen ~80 contributors from ~10 different countries.
-With typically ~10 regular contributors at any given time of the
+So far \gammapy has seen ~80 contributors from ten different countries.
+With typically ten regular contributors at any given time of the
 project, the code base has constantly grown its range of features
@@
 even further, providing a stable perspective for further usage,
-development and maintenance of the project. Besides the future use
-by the CTA community \gammapy has already
-been used for analysis of data from the \hess, \magic, \astri \citep[e.g.][]{Vercellone2022} and \veritas instruments.
+development, and maintenance of the project. In addition to the future use
+by the CTA community, \gammapy has already
+been used for analysis of data from the \hess, \magic, \astri \citep[e.g.][]{Vercellone2022}, and \veritas instruments.
 
@@
 of the future Southern Widefield Gamma Ray Observatory
-(SWGO) and use with data from Large High Altitude Air Shower Observatory (LHAASO) as well. \gammapy
+(SWGO) and use with data from the Large High Altitude Air Shower Observatory (LHAASO) as well. \gammapy
 has the potential to further unify the community
-of \gammaray astronomers, by sharing common tools, data formats and
+of \gammaray astronomers, by sharing common tools, data formats, and
 a common vision of open and reproducible science for the future.
@@
         to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
-	documentation hosting and testing respectively. Α special acknowledgment has to be given
+        documentation hosting and testing respectively. A special acknowledgment has to be given
         to our first Lead Developer of \gammapy, Christoph Deil. Finally, we would like to thank
@@
 \bibliographystyle{aa}
-\bibliography{bib.bib}
+\bibliography{bib}
 
 \appendix
-\section{Code Examples Output}
+\section{Code examples' output}
 
@@
         \small
-	\import{code-examples/generated-output/}{gp_data}
-	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_data}}
+        %Added by TeX Support
+        %\import{code-examples/generated-output/}{gp_data}
+        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_data}.}
         \label{fig:code_example_gp_data}
@@
         \small
-	\import{code-examples/generated-output/}{gp_datasets}
-	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_datasets}}
+        %Added by TeX Support
+        %\import{code-examples/generated-output/}{gp_datasets}
+        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_datasets}.}
         \label{fig:code_example_gp_datasets}
@@
         \small
-	\import{code-examples/generated-output/}{gp_maps}
-	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_maps}}
+        %Added by TeX Support
+        %\import{code-examples/generated-output/}{gp_maps}
+        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_maps}.}
         \label{fig:code_example_gp_maps}
@@
         \small
-	\import{code-examples/generated-output/}{gp_stats}
-	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_stats}}
+        %Added by TeX Support
+        %\import{code-examples/generated-output/}{gp_stats}
+        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_stats}.}
         \label{fig:code_example_gp_stats}
@@
         \includegraphics[width=1.\textwidth]{figures/gp_makers.pdf}
-	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_makers}}
+        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_makers}.}
         \label{fig:code_example_gp_makers}
@@
         \includegraphics[width=1.\textwidth]{figures/gp_estimators.pdf}
-	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_estimators}}
+        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_estimators}.}
         \label{fig:code_example_gp_estimators}
@@
         \includegraphics[width=1.\textwidth]{figures/gp_catalogs.pdf}
-	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_catalogs}}
+        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_catalogs}.}
         \label{fig:code_example_gp_catalogs}
@@
         \small
-	\import{code-examples/generated-output/}{gp_models}
-	\caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_models}}
+        %Added by TeX Support
+        %\import{code-examples/generated-output/}{gp_models}
+        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_models}.}
         \label{fig:code_example_gp_models}

### 2023-08-07 src/ms-review.tex
Remove commented section
Remove single sentence paragraphs
Do not capitalize words in title

@@
 
-\subsection{DL3: Events And Instrument Response Functions}
+\subsection{DL3: events and instrument response functions}
 An overview of the typical steps in the high level analysis is shown in the upper
@@
 
-\subsection{From DL3 to DL4: Data Reduction}
+\subsection{From DL3 to DL4: data reduction}
 The next step of the analysis is the data reduction, where all observation events and instrument
@@
 
-\subsection{DL4: Binned Data Structures}
+\subsection{DL4: binned data structures}
 The counts data and the reduced IRFs in the form of maps are bundled into datasets
@@
 
-\subsection{From DL4 to DL5/6: Modeling and Fitting}
+\subsection{From DL4 to DL5/6: modeling and fitting}
 The next step is then typically to model the datasets using binned Poisson maximum likelihood fitting.
@@
 
-\section{\gammapy Package}
+\section{\gammapy package}
 \label{sec:gammapy-package}
@@
 
-\subsubsection{Effective Area}
+\subsubsection{Effective area}
 \gammapy provides the class \code{EffectiveAreaTable2D} to
@@
 
-\subsubsection{Point Spread Function}
+\subsubsection{Point spread function}
 \gammapy allows users to treat different kinds of PSFs,
@@
 
-\subsubsection{Energy Dispersion}
+\subsubsection{Energy dispersion}
 For \iacts, the energy resolution and bias, sometimes called energy dispersion,
@@
 
-\subsubsection{Instrumental Background}
+\subsubsection{Instrumental background}
 The instrumental background rate can be represented as either a 2D
@@
 
-\subsubsection{WCS Maps}
+\subsubsection{WCS maps}
 The FITS WCS pixelization supports a number of different projections to
@@
 
-\subsubsection{HEALPix Maps}
+\subsubsection{HEALPix maps}
 This pixelization scheme ~\citep{Calabretta2002, Gorski2005} provides a
@@
 
-\subsubsection{Region Maps}
+\subsubsection{Region maps}
 In this case, instead of a fine spatial grid
@@
 maps are represented by the \code{RegionGeom} and \code{RegionNDMap} classes.
-
 More information on the \code{gammapy.maps} sub-module can be found 
@@
 also create their customized datasets for implementing modified likelihood
-methods.
-
-We also refer to our online documentation for more details on \code{gammapy.datasets}
+methods. We also refer to our online documentation for more details on \code{gammapy.datasets}
 \footnote{\url{https://docs.gammapy.org/1.0/user-guide/datasets/index.html\#datasets}}.
@@
 significance~\citep{LiMa} of a set of measurements.
+Our online documentation provides more information on \code{gammapy.stats}
+\footnote{\url{https://docs.gammapy.org/1.0/user-guide/stats/index.html\#stats}}.
 
@@
 \end{figure}
-
-Our online documentation provides more information on \code{gammapy.stats}
-\footnote{\url{https://docs.gammapy.org/1.0/user-guide/stats/index.html\#stats}}.
 
@@
 
-\subsection{1D Analysis}
+\subsection{1D analysis}
 \label{ssec:1d-analysis}
@@
 
-\subsection{3D Analysis}
+\subsection{3D analysis}
 \label{ssec:3d-analysis}
@@
 
-\subsection{Temporal Analysis}
+\subsection{Temporal analysis}
 \label{ssec:temporal-analysis}
@@
 
-\subsection{Multi-instrument Analysis}
+\subsection{Multi-instrument analysis}
 \label{ssec:multi-instrument-analysis}
@@
 
-\subsection{Surveys, Catalogs, and Population Studies}
+\subsection{Surveys, catalogs, and population studies}
 \label{ssec:surveys-catalogs-and-population-studies}
@@
 
-\section{The \gammapy Project} \label{sec:gammapy-project}
+\section{The \gammapy project} \label{sec:gammapy-project}
 
@@
 
-\subsection{Organizational Structure}
+\subsection{Organizational structure}
 \label{ssec:organizational-structure}
@@
 
-\subsection{Technical Infrastructure}
+\subsection{Technical infrastructure}
 \label{ssec:technical-infrastructure}
@@
 use of the pull request system to discuss and review code contributions.
-
-% \begin{table}
-%       \import{tables/generated/}{codestats}
-%       \caption{
-%         Overview of used programming languages and distribution of code across the different file
-%         categories in the \gammapy code base. The most right column list the total number of lines
-%         in a file. The \textit{comment} column lists the number of comments in the files
-%         (including method and class docstrings), the \textit{blank} column lists the
-%         number of blank lines in the file. The uppermost rows distinguish between
-%         code that implements actual functionality and code the implements tests.
-%         All documentation in \gammapy is implemented as dosctrings, \text{reStructuredText} (RST)
-%         files or notebooks.
-%     }
-%       \label{table:codestats:data}
-% \end{table}
 
@@
 
-\subsection{Software Distribution}
+\subsection{Software distribution}
 \label{ssec:software-distribution}
@@
 
-\subsection{Documentation and User-support}
+\subsection{Documentation and user-support}
 \label{ssec:documentation-and-user-support}
@@
 
-\subsection{Proposals for Improving \gammapy}
+\subsection{Proposals for improving \gammapy}
 \label{ssec:pigs}
@@
 
-\subsection{Release Cycle, Versioning, and Long-term Support}
+\subsection{Release cycle, versioning, and long-term support}
 \label{ssec:release-cycle}

### 2023-08-23 src/ms-review.tex
Clean up imports
Remove split author list

@@
 \author{
-        {\it Paper Authors} \and
-    Axel Donath \inst{\ref{inst:28}} \and
+        Axel Donath \thanks{Mail inquiries to:
+        \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \inst{\ref{inst:28}} \and
         Régis Terrier \inst{\ref{inst:20}} \and
@@
         Jose Louis {Contreras} \inst{\ref{inst:15}} \and
-        \\
-        {\it Coordination Committee}\thanks{Corresponding author:
-\href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \and
         Fabio Acero \inst{\ref{inst:1}} \and
+        Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
         David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
-        Catherine Boisson \inst{\ref{inst:9}} \and
-        Jose Louis {Contreras} \inst{\ref{inst:15}} \and
-        Axel Donath \inst{\ref{inst:28}} \and
-        Stefan Funk \inst{\ref{inst:19}} \and
-        Christopher {van Eldik} \inst{\ref{inst:19}} \and
-        Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
-        Jim Hinton \inst{\ref{inst:17}} \and
-        Bruno Khélifi \inst{\ref{inst:20}} \and
-        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
-        Fabio Pintore \inst{\ref{inst:26}} \and
-        Régis Terrier \inst{\ref{inst:20}} \and
-        Roberta Zanin \inst{\ref{inst:18}} \and
-    \\
-        {\it Gammapy Project Contributors} \and
-        Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
         Pooja Bhattacharjee \inst{\ref{inst:8}} \and
         Johannes Buchner \inst{\ref{inst:12}} \and
+        Catherine Boisson \inst{\ref{inst:9}} \and
         David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
@@
         Christoph Deil \inst{\ref{inst:17}} \and
+        Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
+        Stefan Funk \inst{\ref{inst:19}} \and
         Luca Giunti \inst{\ref{inst:20}} \and
+        Jim Hinton \inst{\ref{inst:17}} \and
         Léa Jouvin \inst{\ref{inst:32}} \and
@@
         Jean-Philippe Lenain \inst{\ref{inst:22}} \and
+        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
         Lars Mohrmann \inst{\ref{inst:17}} \and
@@
         Tim Unbehaun \inst{\ref{inst:19}} \and
-        Thomas Vuillaume \inst{\ref{inst:8}}
+        Christopher {van Eldik} \inst{\ref{inst:19}} \and
+        Thomas Vuillaume \inst{\ref{inst:8}} \and
+        Roberta Zanin \inst{\ref{inst:18}}
 }
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated/}{gp_data}
+        \import{code-examples/generated/}{gp_data}
         \caption{
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated/}{gp_maps}
+        \import{code-examples/generated/}{gp_maps}
 
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated/}{gp_datasets}
+        \import{code-examples/generated/}{gp_datasets}
         \caption{
@@
         \small
-        %Added by TeX Support
-    %\import{code-examples/generated/}{gp_makers}
+        \import{code-examples/generated/}{gp_makers}
         \caption{
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated/}{gp_stats}
+        \import{code-examples/generated/}{gp_stats}
         \caption{
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated/}{gp_models}
+        \import{code-examples/generated/}{gp_models}
         \caption{Using \code{gammapy.modeling.models} to define a source model with a
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated/}{gp_estimators}
+        \import{code-examples/generated/}{gp_estimators}
         \caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated/}{gp_catalogs}
+        \import{code-examples/generated/}{gp_catalogs}
         \caption{Using \code{gammapy.catalogs} to access the underlying model, flux points and
@@
 \end{figure}
-
-%\subsection{gammapy.utils}
-%\label{ssec:gammapy-utils}
-%Utility functions...
 
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated-output/}{gp_data}
+    	\import{code-examples/generated-output/}{gp_data}
         \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_data}.}
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated-output/}{gp_datasets}
+        \import{code-examples/generated-output/}{gp_datasets}
         \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_datasets}.}
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated-output/}{gp_maps}
+        \import{code-examples/generated-output/}{gp_maps}
         \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_maps}.}
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated-output/}{gp_stats}
+        \import{code-examples/generated-output/}{gp_stats}
         \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_stats}.}
@@
         \small
-        %Added by TeX Support
-        %\import{code-examples/generated-output/}{gp_models}
+        \import{code-examples/generated-output/}{gp_models}
         \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_models}.}

### 2023-08-23 src/ms-review.tex
Add declaration of contributions

@@
         to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
-        documentation hosting and testing respectively. A special acknowledgment has to be given
-        to our first Lead Developer of \gammapy, Christoph Deil. Finally, we would like to thank
+        documentation hosting and testing respectively. Finally, we would like to thank
         all the \gammapy users that have provided feedback and submitted bug reports.
@@
 
+        A special acknowledgment has to be given to our first lead developer, Christoph Deil, who
+        started the \gammapy project and set the foundation for its future success.
+
+        A. Donath, R. Terrier, Q. Remy, A. Sinha, C. Nigro, F. Pintore, B. Khélifi, L. Olivera-Nieto, J. E. Ruiz,
+        K. Brügge, M. Linhoff and J.L. Contreras contributed to the writing of the manuscript.
+
+        A. Donath, B. Khélifi, C. Boisson, C.Deil, C. van Eldik, D. Berge, E. de Ona Wilhelmi, F. Acero, F. Pintore,
+        M. Cardillo, J. Hinton, J.L. Contreras, M. Fuessling, R. Terrier, R. Zanin, R. López-Coto and S. Funk
+        are current or former members of the Gammapy coordination committee and contributed to promotion, coordination
+        and steering of the \gammapy project.
+
+        A. Aguasca-Cabot, P. Bhattacharjee, K. Brügge, J. Buchner, D. Carreto Fidalgo, A. Chen, M. de Bony de Lavergne,
+        A. Donath, J. V. de Miranda Cardoso, C. Deil, L. Giunti, L. Jouvin, B. Khélifi, J. King, J. Lefaucheur,
+        M. Lemoine-Goumard, J.P. Lenain, M. Linhoff, L. Mohrmann, D. Morcuende, C. Nigro, L. Olivera-Nieto,
+        S. Panny, M. Regeard, Q. Remy, J. E. Ruiz, L. Saha, H. Siejkowski, A. Siemiginowska, A. Sinha,
+        B. M. Sipőcz, R. Terrier, T. Unbehaun, T. Vuillaume contributed to the code development of \gammapy.
+
 \end{acknowledgements}

### 2023-08-25 src/ms-review.tex
Adapt acknowledgements

@@
         to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
-        documentation hosting and testing respectively. Finally, we would like to thank
+        documentation hosting and testing respectively. We would like to thank
         all the \gammapy users that have provided feedback and submitted bug reports.
@@
 
-        A. Donath, R. Terrier, Q. Remy, A. Sinha, C. Nigro, F. Pintore, B. Khélifi, L. Olivera-Nieto, J. E. Ruiz,
-        K. Brügge, M. Linhoff and J.L. Contreras contributed to the writing of the manuscript.
-
-        A. Donath, B. Khélifi, C. Boisson, C.Deil, C. van Eldik, D. Berge, E. de Ona Wilhelmi, F. Acero, F. Pintore,
-        M. Cardillo, J. Hinton, J.L. Contreras, M. Fuessling, R. Terrier, R. Zanin, R. López-Coto and S. Funk
-        are current or former members of the Gammapy coordination committee and contributed to promotion, coordination
-        and steering of the \gammapy project.
-
-        A. Aguasca-Cabot, P. Bhattacharjee, K. Brügge, J. Buchner, D. Carreto Fidalgo, A. Chen, M. de Bony de Lavergne,
-        A. Donath, J. V. de Miranda Cardoso, C. Deil, L. Giunti, L. Jouvin, B. Khélifi, J. King, J. Lefaucheur,
-        M. Lemoine-Goumard, J.P. Lenain, M. Linhoff, L. Mohrmann, D. Morcuende, C. Nigro, L. Olivera-Nieto,
-        S. Panny, M. Regeard, Q. Remy, J. E. Ruiz, L. Saha, H. Siejkowski, A. Siemiginowska, A. Sinha,
-        B. M. Sipőcz, R. Terrier, T. Unbehaun, T. Vuillaume contributed to the code development of \gammapy.
+        For contributing to the writing of the manuscript, we thank A. Donath, R. Terrier, Q. Remy, A. Sinha,
+        C. Nigro, F. Pintore, B. Khélifi, L. Olivera-Nieto, J. E. Ruiz, K. Brügge, M. Linhoff and J.L. Contreras.
+
+        We also thank the current and former members of the Gammapy coordination committee A. Donath, B. Khélifi,
+        C. Boisson, C.Deil, C. van Eldik, D. Berge, E. de Ona Wilhelmi, F. Acero, F. Pintore,
+        M. Cardillo, J. Hinton, J.L. Contreras, M. Fuessling, R. Terrier, R. Zanin, R. López-Coto and S. Funk,
+        who contributed to promotion, coordination and steering of the \gammapy project.
+
+        Finally we would like to thank A. Aguasca-Cabot, P. Bhattacharjee, K. Brügge, J. Buchner, D. Carreto
+        Fidalgo, A. Chen, M. de Bony de Lavergne, A. Donath, J. V. de Miranda Cardoso, C. Deil, L. Giunti,
+        L. Jouvin, B. Khélifi, J. King, J. Lefaucheur, M. Lemoine-Goumard, J.P. Lenain, M. Linhoff,
+        L. Mohrmann, D. Morcuende, C. Nigro, L. Olivera-Nieto, S. Panny, F. Pintore, M. Regeard,
+        Q. Remy, J. E. Ruiz, L. Saha, H. Siejkowski, A. Siemiginowska, A. Sinha, B. M. Sipőcz, R. Terrier,
+        T. Unbehaun, T. Vuillaume and unnamed contributors for contributing to the development of \gammapy.
 

### 2023-08-25 src/ms-review.tex

@@
         Axel Donath \thanks{Mail inquiries to:
-        \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \inst{\ref{inst:28}} \and
-        Régis Terrier \inst{\ref{inst:20}} \and
-        Quentin Remy \inst{\ref{inst:17}} \and
-        Atreyee Sinha \inst{\ref{inst:15}} \and
-        Cosimo Nigro \inst{\ref{inst:24}} \and
-        Fabio Pintore \inst{\ref{inst:26}} \and
-        Bruno Khélifi \inst{\ref{inst:20}} \and
-        Laura Olivera-Nieto \inst{\ref{inst:17}}\and
-        Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
-        Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
-        Maximilian Linhoff \inst{\ref{inst:11}} \and
-        Jose Louis {Contreras} \inst{\ref{inst:15}} \and
-        Fabio Acero \inst{\ref{inst:1}} \and
-        Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
-        David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
-        Pooja Bhattacharjee \inst{\ref{inst:8}} \and
-        Johannes Buchner \inst{\ref{inst:12}} \and
-        Catherine Boisson \inst{\ref{inst:9}} \and
-        David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
-        Andrew Chen \inst{\ref{inst:14}} \and
-        Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
-        José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
-        Christoph Deil \inst{\ref{inst:17}} \and
-        Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
-        Stefan Funk \inst{\ref{inst:19}} \and
-        Luca Giunti \inst{\ref{inst:20}} \and
-        Jim Hinton \inst{\ref{inst:17}} \and
-        Léa Jouvin \inst{\ref{inst:32}} \and
-        Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
-        Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
-        Marianne Lemoine-Goumard \inst{\ref{inst:31}} \and
-        Jean-Philippe Lenain \inst{\ref{inst:22}} \and
-        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
-        Lars Mohrmann \inst{\ref{inst:17}} \and
-        Daniel Morcuende \inst{\ref{inst:15}} \and
-        Sebastian Panny \inst{\ref{inst:25}} \and
-        Maxime Regeard \inst{\ref{inst:20}} \and
-        Lab Saha \inst{\ref{inst:15}} \and
-        Hubert Siejkowski \inst{\ref{inst:27}} \and
-        Aneta Siemiginowska \inst{\ref{inst:28}} \and
-        Brigitta M. {Sipőcz} \inst{\ref{inst:29}} \and
-        Tim Unbehaun \inst{\ref{inst:19}} \and
-        Christopher {van Eldik} \inst{\ref{inst:19}} \and
-        Thomas Vuillaume \inst{\ref{inst:8}} \and
-        Roberta Zanin \inst{\ref{inst:18}}
+        \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \inst{\ref{inst:001}} \and
+        Régis Terrier \inst{\ref{inst:002}} \and
+        Quentin Remy \inst{\ref{inst:003}} \and
+        Atreyee Sinha \inst{\ref{inst:004}} \and
+        Cosimo Nigro \inst{\ref{inst:005}} \and
+        Fabio Pintore \inst{\ref{inst:006}} \and
+        Bruno Khélifi \inst{\ref{inst:002}} \and
+        Laura Olivera-Nieto \inst{\ref{inst:003}}\and
+        Jose Enrique {Ruiz} \inst{\ref{inst:007}} \and
+        Kai Brügge \inst{\ref{inst:008},\ref{inst:009}} \and
+        Maximilian Linhoff \inst{\ref{inst:009}} \and
+        Jose Louis {Contreras} \inst{\ref{inst:004}} \and
+        Fabio Acero \inst{\ref{inst:010}} \and
+        Arnau Aguasca-Cabot \inst{\ref{inst:011}, \ref{inst:012}, \ref{inst:013}, \ref{inst:014}} \and
+        David Berge \inst{\ref{inst:015}, \ref{inst:016}} \and
+        Pooja Bhattacharjee \inst{\ref{inst:017}} \and
+        Johannes Buchner \inst{\ref{inst:018}} \and
+        Catherine Boisson \inst{\ref{inst:019}} \and
+        David {Carreto Fidalgo} \inst{\ref{inst:020}} \and
+        Andrew Chen \inst{\ref{inst:021}} \and
+        Mathieu {de Bony de Lavergne} \inst{\ref{inst:017}} \and
+        José Vinícius {de Miranda Cardoso}\inst{\ref{inst:022}} \and
+        Christoph Deil \inst{\ref{inst:003}} \and
+        Matthias Fü{\ss}ling \inst{\ref{inst:023}} \and
+        Stefan Funk \inst{\ref{inst:024}} \and
+        Luca Giunti \inst{\ref{inst:002}} \and
+        Jim Hinton \inst{\ref{inst:003}} \and
+        Léa Jouvin \inst{\ref{inst:025}} \and
+        Johannes King \inst{\ref{inst:026}, \ref{inst:003}} \and
+        Julien Lefaucheur \inst{\ref{inst:027}, \ref{inst:002}} \and
+        Marianne Lemoine-Goumard \inst{\ref{inst:028}} \and
+        Jean-Philippe Lenain \inst{\ref{inst:029}} \and
+        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:007}} \and
+        Lars Mohrmann \inst{\ref{inst:003}} \and
+        Daniel Morcuende \inst{\ref{inst:004}} \and
+        Sebastian Panny \inst{\ref{inst:032}} \and
+        Maxime Regeard \inst{\ref{inst:002}} \and
+        Lab Saha \inst{\ref{inst:004}} \and
+        Hubert Siejkowski \inst{\ref{inst:030}} \and
+        Aneta Siemiginowska \inst{\ref{inst:001}} \and
+        Brigitta M. {Sipőcz} \inst{\ref{inst:031}} \and
+        Tim Unbehaun \inst{\ref{inst:024}} \and
+        Christopher {van Eldik} \inst{\ref{inst:024}} \and
+        Thomas Vuillaume \inst{\ref{inst:017}} \and
+        Roberta Zanin \inst{\ref{inst:023}}
 }
@@
 \institute{
-        Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, F-91191 Gif-sur-Yvette, France \label{inst:1} \and
-        Departament de Física Quàntica i Astrofísica (FQA), Universitat de Barcelona (UB),  c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:2} \and
-        Institut de Ciències del Cosmos (ICCUB), Universitat de Barcelona (UB), c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:3} \and
-        Institut d'Estudis Espacials de Catalunya (IEEC), c. Gran Capità, 2-4, 08034 Barcelona, Spain \label{inst:4} \and
-        Departament de Física Quàntica i Astrofísica, Institut de Ciències del Cosmos, Universitat de Barcelona, IEEC-UB, Martí i Franquès, 1, 08028, Barcelona, Spain \label{inst:5} \and
-        Deutsches Elektronen-Synchrotron (DESY), D-15738 Zeuthen, Germany \label{inst:6} \and
-        Institute of physics, Humboldt-University of Berlin, D-12489 Berlin, Germany \label{inst:7} \and
-        Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecy de Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:8} \and
-        Laboratoire Univers et Théories, Observatoire de Paris, Université PSL, Université Paris Cité, CNRS, F-92190 Meudon, France \label{inst:9} \and
-        Point8 GmbH \label{inst:10} \and
-        Astroparticle Physics, Department of Physics, TU Dortmund University, Otto-Hahn-Str. 4a, D-44227 Dortmund \label{inst:11} \and
-        Max Planck Institute for extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany \label{inst:12} \and
-        Max Planck Computing and Data Facility, Gießenbachstraße 2, 85748 Garching \label{inst:13} \and
-        School of Physics, University of the Witwatersrand, 1 Jan Smuts Avenue, Braamfontein, Johannesburg, 2050 South Africa \label{inst:14} \and
-        IPARCOS Institute and EMFTEL Department, Universidad Complutense de Madrid, E-28040 Madrid, Spain \label{inst:15} \and
-        The Hong Kong University of Science and Technology, Department of Electronic and Computer Engineering \label{inst:16} \and
-        Max-Planck-Institut für Kernphysik, P.O. Box 103980, D 69029 Heidelberg, Germany \label{inst:17} \and
-        Cherenkov Telescope Array Observatory gGmbH (CTAO gGmbH) Saupfercheckweg 1 69117 Heidelberg \label{inst:18} \and
-        Erlangen Centre for Astroparticle Physics (ECAP), Friedrich-Alexander-Universität Erlangen-Nürnberg, Nikolaus-Fiebiger Strasse 2, 91058 Erlangen, Germany \label{inst:19} \and
-        Université de Paris Cité, CNRS, Astroparticule et Cosmologie, F-75013 Paris, France  \label{inst:20} \and
-        Meteo France International \label{inst:21} \and
-        Sorbonne Université, Université Paris Diderot, Sorbonne Paris Cité, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252 Paris, France \label{inst:22} \and
-        Instituto de Astrofísica de Andalucía-CSIC, Glorieta de la Astronomía s/n, 18008, Granada, Spain \label{inst:23} \and
-        Institut de Física d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, Bellaterra, 08193 Barcelona, Spain \label{inst:24} \and
-        Institut für Astro- und Teilchenphysik, Leopold-Franzens-Universität Innsbruck, A-6020 Innsbruck, Austria \label{inst:25} \and
-        INAF/IASF Palermo, Via U. La Malfa, 153, 90146 Palermo PA \label{inst:26} \and
-        Academic Computer Centre Cyfronet, AGH University of Science and Technology, Krakow, Poland \label{inst:27} \and
-        Center for Astrophysics | Harvard and Smithsonian \label{inst:28} \and
-        Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:29} \and
-        Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:30} \and
-        Université Bordeaux, CNRS, LP2I Bordeaux, UMR 5797 \label{inst:31} \and
-        IRFU, CEA, Université Paris-Saclay, F-91191 Gif-sur-Yvette, France \label{inst:32}
+        Center for Astrophysics | Harvard and Smithsonian \label{inst:001} \and
+        Université de Paris Cité, CNRS, Astroparticule et Cosmologie, F-75013 Paris, France  \label{inst:002} \and
+        Max-Planck-Institut für Kernphysik, P.O. Box 103980, D 69029 Heidelberg, Germany \label{inst:003} \and
+        IPARCOS Institute and EMFTEL Department, Universidad Complutense de Madrid, E-28040 Madrid, Spain \label{inst:004} \and
+        Institut de Física d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, Bellaterra, 08193 Barcelona, Spain \label{inst:005} \and
+        INAF/IASF Palermo, Via U. La Malfa, 153, 90146 Palermo PA \label{inst:006} \and
+        Instituto de Astrofísica de Andalucía-CSIC, Glorieta de la Astronomía s/n, 18008, Granada, Spain \label{inst:007} \and
+        Point8 GmbH \label{inst:008} \and
+        Astroparticle Physics, Department of Physics, TU Dortmund University, Otto-Hahn-Str. 4a, D-44227 Dortmund \label{inst:009} \and
+        Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, F-91191 Gif-sur-Yvette, France \label{inst:010} \and
+        Departament de Física Quàntica i Astrofísica (FQA), Universitat de Barcelona (UB),  c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:011} \and
+        Institut de Ciències del Cosmos (ICCUB), Universitat de Barcelona (UB), c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:012} \and
+        Institut d'Estudis Espacials de Catalunya (IEEC), c. Gran Capità, 2-4, 08034 Barcelona, Spain \label{inst:013} \and
+        Departament de Física Quàntica i Astrofísica, Institut de Ciències del Cosmos, Universitat de Barcelona, IEEC-UB, Martí i Franquès, 1, 08028, Barcelona, Spain \label{inst:014} \and
+        Deutsches Elektronen-Synchrotron (DESY), D-15738 Zeuthen, Germany \label{inst:015} \and
+        Institute of physics, Humboldt-University of Berlin, D-12489 Berlin, Germany \label{inst:016} \and
+        Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecy de Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:017} \and
+        Max Planck Institute for extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany \label{inst:018} \and
+        Laboratoire Univers et Théories, Observatoire de Paris, Université PSL, Université Paris Cité, CNRS, F-92190 Meudon, France \label{inst:019} \and
+        Max Planck Computing and Data Facility, Gießenbachstraße 2, 85748 Garching \label{inst:020} \and
+        School of Physics, University of the Witwatersrand, 1 Jan Smuts Avenue, Braamfontein, Johannesburg, 2050 South Africa \label{inst:021} \and
+        The Hong Kong University of Science and Technology, Department of Electronic and Computer Engineering \label{inst:022} \and
+        Cherenkov Telescope Array Observatory gGmbH (CTAO gGmbH) Saupfercheckweg 1 69117 Heidelberg \label{inst:023} \and
+        Erlangen Centre for Astroparticle Physics (ECAP), Friedrich-Alexander-Universität Erlangen-Nürnberg, Nikolaus-Fiebiger Strasse 2, 91058 Erlangen, Germany \label{inst:024} \and
+        IRFU, CEA, Université Paris-Saclay, F-91191 Gif-sur-Yvette, France \label{inst:025}
+        Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:026} \and
+        Meteo France International \label{inst:027} \and
+        Université Bordeaux, CNRS, LP2I Bordeaux, UMR 5797 \label{inst:028} \and
+        Sorbonne Université, Université Paris Diderot, Sorbonne Paris Cité, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252 Paris, France \label{inst:029} \and
+        Academic Computer Centre Cyfronet, AGH University of Science and Technology, Krakow, Poland \label{inst:030} \and
+        Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:031} \and
+        Institut für Astro- und Teilchenphysik, Leopold-Franzens-Universität Innsbruck, A-6020 Innsbruck, Austria \label{inst:032}
 }

### 2023-08-25 src/ms-review.tex
Update ms-review.tex

@@
         Maximilian Linhoff \inst{\ref{inst:009}} \and
-        Jose Louis {Contreras} \inst{\ref{inst:004}} \and
+        Jose Luis {Contreras} \inst{\ref{inst:004}} \and
         Fabio Acero \inst{\ref{inst:010}} \and
